### 2013-05-13 Tex/1_Theorie.tex
LaTeX: Gerüst und Literaturverzeichnis angelegt

\subsection{Modell}
    Ising Modell \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)\\
    zufälliges Gitter: Gaußverteilt\\
    Kopplungskonstanten abstandsabhängig: \(J_{ij}=e^{(1-\alpha)d_{ij}}\)\\
    Monte Carlo Simulationen:\\
        Wolff-Cluster Algorithmus \cite{Wolff1989} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
        Metropolis Sweep \cite{Metropolis1953} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
        Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\
    Relative Neighborhood Graph \cite{Toussaint1980}\\
    Gabriel Graph \cite{Gabriel1969}\\
        Cell Algorithmus ohne Delaunay Triangulation \cite{RNGCell}

\cite{NewmanBarkema1999}

### 2013-05-14 spin.c
Kommentare und Einrückung angepasst

@@ -539,8 +539,10 @@ void move_graph_nodes(gs_graph_t *g, double (*f)(const gsl_rng *, double), gsl_r
     const int verschiebung_y[9] = {0,1,1,0,-1,-1,-1,0,1};
     for(n=0;n<g->num_nodes; n++)
     {
+        /* Verschiebe Punkte zufällig */
         g->node[n].x += f(rng, sigma);
         g->node[n].y += f(rng, sigma);
+        /* Falls die Punkte aus dem Bereich geschoben werden, schiebe sie periodisch wieder rein */
         g->node[n].x += g->L * verschiebung_x[point_not_in_domain(g->node[n].x, g->node[n].y, g->L)];
         g->node[n].y += g->L * verschiebung_y[point_not_in_domain(g->node[n].x, g->node[n].y, g->L)];
     }
@@ -581,7 +583,7 @@ void create_edges_regular(gs_graph_t *g)
 /*! \fn inline int check_relative_neighborhood(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3)
     \brief Prüft, ob node3 im Lune zwischen node1 und node2 liegt
 
-    \param [in]    dist12   Abstandsquadrat zwischen node1 und node2
+    \param [in]    dist12   Abstand zwischen node1 und node2
     \param [in]    node1    Erster  Knoten
     \param [in]    node2    Zweiter Knoten
     \param [in]    node3    Dritter Knoten
@@ -589,7 +591,7 @@ void create_edges_regular(gs_graph_t *g)
 inline int check_relative_neighborhood(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3)
 {
     double dist13, dist23;
-    dist12*=dist12;
+    dist12*=dist12; /* Mache Abstandsquadrat aus dem Abstand */
     /* Überprüfe diesen Punkte */
     dist13 = (node1.x-node3.x)*(node1.x-node3.x)
             + (node1.y-node3.y)*(node1.y-node3.y);
@@ -614,9 +616,9 @@ inline int check_relative_neighborhood(double dist12, gs_node_t node1, gs_node_t
[…]

### 2013-05-15 spin.c
Parameter im Dateinamen haben feste Längen

@@ -210,7 +210,7 @@ options_t get_cl_args(int argc, char *argv[])
     if(!custom_file_name)
     {
         /* standard Dateiname */
-        snprintf(o.filename, MAX_LEN_FILENAME, "data/data_s_%.1f_x_%d_L_%d_type_%d.dat", o.sigma, o.seed, o.L, o.graph_type);
+        snprintf(o.filename, MAX_LEN_FILENAME, "data/data_s_%.2f_x_%03d_L_%03d_type_%d.dat", o.sigma, o.seed, o.L, o.graph_type);
     }
 
     /* Welchen Algorithmus nutzen? */

### 2013-05-15 auswertung/db.py
Datenbank der Rohdaten jetzt eigenständig und nicht im Memory

@@ -20,7 +20,7 @@ logging.basicConfig(level=logging.INFO,
                 datefmt='%d.%m.%YT%H:%M:%S')
 
 class Database():
-    def __init__(self, dbPath = "data.db", dataPath = "../data", graphType=1):
+    def __init__(self, dbPath="data.db", dbRawPath="dataRaw.db", dataPath="../data", graphType=1):
         """! Constructor
 
             Erstellt eine SQLite Datenbank aus den Daten in dataPath, wenn
@@ -28,28 +28,29 @@ class Database():
             Dateien zum Plotten wichtiger Messgrößen aus.
         """
         self.dbPath = dbPath
+        self.dbRawPath = dbRawPath
         self.graphType = graphType
 
         if not os.path.isfile(self.dbPath):
-            # Generate new Database in memory
-            self.conn = sqlite3.connect(":memory:")
+            try:
+                os.remove(self.dbRawPath)
+            except: pass
+            # Generate new Raw Database
+            self.connRaw = sqlite3.connect(self.dbRawPath)
             self.createNewDatabase(dataPath)
+
+            # Generate new Database
+            self.conn = sqlite3.connect(self.dbPath)
             self.calculateNewDatabase()
-            # Copy Database to file
-            logging.info("copy Database to {0}".format(self.dbPath))
-            new_db = sqlite3.connect(self.dbPath)
-            logging.info("  drop rawdata")
-            self.conn.execute("""DROP TABLE rawdata""")
+
+            # Cleanup Databse
             logging.info("  vacuum")
             self.conn.execute("""VACUUM""")
-            logging.info("  dump")
-            query = "".join(line for line in self.conn.iterdump())
-            logging.info("  create")
-            new_db.executescript(query)
-            logging.info("  finished")
+
+            # Close Databases
+            self.connRaw.close()
             self.conn.close()
 
-        # lade Datenbank und hole sie in den Speicher
         self.conn = sqlite3.connect(self.dbPath)
 
         logging.info("start writing files for Gnuplot")
@@ -64,6 +65,7 @@ class Database():
         logging.info("  Parallel Tempering Akzeptanzraten")
         self.writeParTempForGnuplot()
         logging.info("  finished")
+
         self.conn.close()
 
[…]

### 2013-05-15 auswertung/db.py
Datenbank etwas gesprächiger

@@ -20,7 +20,7 @@ logging.basicConfig(level=logging.INFO,
                 datefmt='%d.%m.%YT%H:%M:%S')
 
 class Database():
-    def __init__(self, dbPath="data.db", dbRawPath="dataRaw.db", dataPath="../data", graphType=1):
+    def __init__(self, dbPath="data.db", dbRawPath="dataRaw.db", dataPath="../data", graphType=1, autocorrFlag=False):
         """! Constructor
 
             Erstellt eine SQLite Datenbank aus den Daten in dataPath, wenn
@@ -30,14 +30,17 @@ class Database():
         self.dbPath = dbPath
         self.dbRawPath = dbRawPath
         self.graphType = graphType
+        self.autocorrFlag = autocorrFlag
 
         if not os.path.isfile(self.dbPath):
-            try:
-                os.remove(self.dbRawPath)
-            except: pass
-            # Generate new Raw Database
-            self.connRaw = sqlite3.connect(self.dbRawPath)
-            self.createNewDatabase(dataPath)
+            if not os.path.isfile(self.dbRawPath):
+                logging.info("Datenbank mit Rohdaten nicht vorhanden!")
+                # Generate new Raw Database
+                self.connRaw = sqlite3.connect(self.dbRawPath)
+                self.createNewDatabase(dataPath)
+            else:
+                logging.info("Datenbank mit Rohdaten gefunden!")
+                self.connRaw = sqlite3.connect(self.dbRawPath)
 
             # Generate new Database
             self.conn = sqlite3.connect(self.dbPath)
@@ -60,8 +63,9 @@ class Database():
         self.writeMeanForGnuplot()
         logging.info("  Wärmekapazität, Suzeptibilität")
         self.writeVarForGnuplot()
-        logging.info("  Autokorrelationszeiten")
-        self.writeAutoForGnuplot()
+        if self.autocorrFlag:
+            logging.info("  Autokorrelationszeiten")
+            self.writeAutoForGnuplot()
         logging.info("  Parallel Tempering Akzeptanzraten")
         self.writeParTempForGnuplot()
         logging.info("  finished")
@@ -308,6 +312,23 @@ class Database():
         self.connRaw.commit()
         self.connRaw.execute("""CREATE INDEX idx_ex1 ON rawdata(sigma,L,T)""")
 
+    def addToDatabase(self, dataPath):
[…]

### 2013-06-03 auswertung/getJ.py
Funktion zum Ermitteln der durchschnittlichen Kantengewichte

@@ -1,0 +1,32 @@
+#!/usr/bin/env python2
+# -*- coding: UTF-8 -*-
+
+import os
+from reader import *
+
+def getJFromDat(dataPath):
+    d = {}
+
+    for f in sorted(os.listdir(dataPath)):
+        if not ".dat" in f:
+            continue
+        if "L_032_" in f:
+            continue
+
+        r = output_reader(os.path.join(dataPath,f))
+        try:
+            d[r.sigma].append(float(r.J))
+        except KeyError:
+            d.update({r.sigma:[float(r.J)]})
+
+    print d
+    for key in d.keys():
+        d[key] = [mean(d[key]), std(d[key])/sqrt(len(d[key]))]
+
+    print dataPath
+    for [key, val] in sorted(d.items()):
+        print key, " : ", val[0], "+-", val[1]
+    print " "
+
+#~ getJFromDat("../data/GG")
+getJFromDat("../data/RNG")

### 2013-06-03 auswertung/reader.py

@@ -28,6 +28,9 @@ class output_reader():
     ## @var sigma
     # Unordnungsparameter (double)
 
+    ## @var J
+    # mittleres J (double)
+
     ## @var x
     # Unordnungsrealisierung (int)
 
@@ -67,6 +70,8 @@ class output_reader():
             self.x = " ".join(header).rpartition("x=")[2].partition (" #")[0]
             self.L = " ".join(header).rpartition("L=")[2].partition (" #")[0]
             self.graphType = " ".join(header).rpartition("type=")[2].partition (" #")[0]
+            self.J = " ".join(header).rpartition("<J>=")[2].partition (" #")[0]
+            if self.J == "# N E M": self.J="0"
 
             # Zwischenspeichern, da Einträge im Reader verbraucht werden
             alle = [i for i in reader]

### 2013-06-03 spin.c

@@ -25,6 +25,8 @@ int main(int argc, char *argv[])
     if(o.verbose)
         fprintf(stdout,"Starte Initialisierung\n");
     list_of_graphs = init_graphs(o);
+    if(o.verbose)
+        fprintf(stdout,"<J> = %f\n", get_mean_weight(list_of_graphs[0]));
 
     if(o.verbose)
         fprintf(stdout,"Starte Monte Carlo Simulation\n");
@@ -392,7 +394,7 @@ void do_mc_simulation(gs_graph_t **list_of_graphs, const options_t o)
         exit(-1);
     }
     /* Schreibe Header */
-    fprintf(data_out_file, "# N E M # sigma=%.2f # x=%d # L=%d # type=%d # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type);
+    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # <J>=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, get_mean_weight(list_of_graphs[0]));
     for(nT=0;nT<o.num_temps;nT++)
         fprintf(data_out_file, "%.3f, ", list_of_graphs[nT]->T);
     fprintf(data_out_file, "\n");
@@ -838,6 +840,27 @@ void create_edges(gs_graph_t *g, options_t o)
     free(cell_list);
 }
 
+/*! \fn double get_mean_weight(gs_graph_t *g)
+    \brief Diese Funktion gibt den Mittelwert der Kantengewichte im
+            Graphen g aus
+
+    \param [in] g Graph über den gemittelt wird
+    \return Mittelwert der Kantengewichte
+*/
+double get_mean_weight(gs_graph_t *g)
+{
+    int n, i;
+    double sum = 0;
+    int count = 0;
+    for(n=0;n<g->num_nodes; n++)
+        for(i=0;i<g->node[n].num_neighbors;i++)
+        {
+            sum += g->node[n].neighbors[i].weight;
+            count++;
+        }
+    /* Es sollte egal sein, dass über jede Kante zweimal summiert wird */
+    return (sum / count);
+}
 
 /*! \fn void init_spins_randomly(gs_graph_t *g, gsl_rng *rng)
     \brief Weist den Spins im gs_graph_t g zufällige Werte zu

### 2013-06-03 spin.h

@@ -86,6 +86,7 @@ inline void get_cell_border_relative_neighborhood(gs_node_t node1, gs_node_t nod
 inline int check_gabriel(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);
 inline void get_cell_border_gabriel(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
 void create_edges(gs_graph_t *g, options_t o);
+double get_mean_weight(gs_graph_t *g);
 
 void init_spins_randomly(gs_graph_t *g, gsl_rng *rng);
 void init_spins_up(gs_graph_t *g);

### 2013-06-03 spin.c
längerer Dateiname für Sigma

@@ -212,7 +212,7 @@ options_t get_cl_args(int argc, char *argv[])
     if(!custom_file_name)
     {
         /* standard Dateiname */
-        snprintf(o.filename, MAX_LEN_FILENAME, "data/data_s_%.2f_x_%03d_L_%03d_type_%d.dat", o.sigma, o.seed, o.L, o.graph_type);
+        snprintf(o.filename, MAX_LEN_FILENAME, "data/data_s_%.3f_x_%03d_L_%03d_type_%d.dat", o.sigma, o.seed, o.L, o.graph_type);
     }
 
     /* Welchen Algorithmus nutzen? */

### 2013-06-03 graph.c
.svg werden jetzt besser dargestellt

@@ -171,7 +171,7 @@ void gs_clear_shallow_graph(gs_graph_t *g)
     free(g);
 }
 
-/*! \fn void svg_circle(double x, double y, int filled, FILE *file)
+/*! \fn void svg_circle(double x, double y, int filled, double scale FILE *file)
     \brief Schreibt einen Kreis in die gegebene Datei im SVG Format
 
     \param x       x-Koordinate des Kreis Mittelpunkts
@@ -179,21 +179,21 @@ void gs_clear_shallow_graph(gs_graph_t *g)
     \param filled  Soll der Kreis gefüllt sein? 1: gefüllt -1: nicht gefüllt
     \param file    File Handler der Output Datei
 */
-void svg_circle(double x, double y, int filled, FILE *file)
+void svg_circle(double x, double y, int filled, double scale, FILE *file)
 {
     if(filled == 1)
         fprintf(file, "<circle cx='%f' cy='%f' r='8' stroke='black'\
-              stroke-width='2' fill='black'/>\n", (x+1)*40, (y+1)*40);
+              stroke-width='2' fill='black'/>\n", (x+1)*scale, (y+1)*scale);
     else if(filled == -1)
         fprintf(file, "<circle cx='%f' cy='%f' r='8' stroke='black'\
-              stroke-width='2' fill='white'/>\n", (x+1)*40, (y+1)*40);
+              stroke-width='2' fill='white'/>\n", (x+1)*scale, (y+1)*scale);
     else
         fprintf(file, "<circle cx='%f' cy='%f' r='8' stroke='black'\
               stroke-width='2' stroke-dasharray='2,3' fill='white'/>\n",
-                                                    (x+1)*40, (y+1)*40);
+                                                    (x+1)*scale, (y+1)*scale);
 }
 
-/*! \fn void svg_circle(double x, double y, int filled, FILE *file)
+/*! \fn void svg_line(double x1, double x2, double y1, double y2, double scale, FILE *file)
     \brief Schreibt einen Kreis in die gegebene Datei im SVG Format
 
     \param x1      x-Anfangspunkt der Linie
@@ -202,11 +202,11 @@ void svg_circle(double x, double y, int filled, FILE *file)
     \param y2      y-Endpunkt der Linie
     \param file    File Handler der Output Datei
 */
[…]

### 2013-06-04 Tex/1_Theorie.tex
mehr Notizen zur Bachelorarbeit

@@
         Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\
+        Erklärung zu Autokorreltationszeit \(\tau\) und Equilibrierungszeit \(t_eq\)\\
+        Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
     Relative Neighborhood Graph \cite{Toussaint1980}\\
     Gabriel Graph \cite{Gabriel1969}\\
-        Cell Algorithmus ohne Delaunay Triangulation \cite{RNGCell}
-
-\cite{NewmanBarkema1999}
+        Cell Algorithmus ohne Delaunay Triangulation \cite{RNGCell}\\
+        <J>(\sigma), Anmerkung zur Anomalie des GG und der ähnlichkeit zu \(T_c\)\\
+    Bestimmung der kritischen Punkte\\
+        Polyfit 4ten Grades durch Binder Kumulante \cite{Binder1981}\\
+        Finite Size Scaling Vergleich der Exponenten (AutoScale \cite{Melchert2009}, Vergleich \cite[S. 59]{Pelissetto2002})\\

### 2013-06-04 Tex/1_Theorie.tex
Text auf Englisch und mehr notizen

--- 2013-05-13 Tex/1_Theorie.tex
@@
-\subsection{Modell}
-    Ising Modell \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)\\
-    zufälliges Gitter: Gaußverteilt\\
-    Kopplungskonstanten abstandsabhängig: \(J_{ij}=e^{(1-\alpha)d_{ij}}\)\\
-    Monte Carlo Simulationen:\\
-        Wolff-Cluster Algorithmus \cite{Wolff1989} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
-        Metropolis Sweep \cite{Metropolis1953} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
-        Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\
-    Relative Neighborhood Graph \cite{Toussaint1980}\\
-    Gabriel Graph \cite{Gabriel1969}\\
-        Cell Algorithmus ohne Delaunay Triangulation \cite{RNGCell}
+\subsection{Model and Implementation}
+    I will desribe the model in this section in a bottom-up fashion.
+    First describing all parts and then connecting them.
+    %~ \subsubsection{Graphs}
+        %~ A graph is a set of nodes \(V\) and edges \(E\).
+    \subsubsection{Gabriel- and Relative Neighborhood Graph}
+        The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
+        Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
+        \(d_{ij}\) are connected with an edge if a circle with it's
+        center on the middlepoint between \(i\) and \(j\) and radius
+        \(r = \frac d 2\) contains no other nodes. This area will be
+        called \emph{lune} in the following. See also Figure
+        \ref{fig:def:GG}.\\
+        The Relative Neighborhood Graph \cite{Toussaint1980} is a
+        subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
+        distance \(d_{ij}\) are connected if no other node is in the
+        \emph{lune}. The lune is defined as the intersection of two
+        circles with radius \(r = d\) and centers on \(i\) and \(j\).
+        See also Figure \ref{fig:def:RNG}.\\\\
+        To construct these graphs the simple way is to test for every
+        pair of nodes for every node if it lies in the lune of the pair.
+        That is of complexity \(\mathchar O (n^3)\).\\
+        To reduce the complexity one can first create a Delaunay
+        Triangulation in complexity \(\mathchar O (n \log n)\)
+        \cite{Leach1992} and test the criterion for each edge, because
+        the Delaunay Triangulation is a supergraph of both. But the
+        implementation of a Delaunay Triangulation algorithm is not
+        trivial and the generation of the graphs is not time critical.\\
+        So a tradeoff is to use basicly the simple method but only test
+        the criterion for nodes which are near to the lune and abort if
+        one node inside the lune is found. Saving the position of every
+        node in a \emph{cell list} according to \cite{RNGCell} and just
+        testing the nodes in the cells which contain the lune speeds
+        things up.
 
-\cite{NewmanBarkema1999}
+    \subsubsection{Model}
+        The used model is a modified 2D Ising model living on a Gabriel
+        or Relative Neighborhood Graph where the nodes are displaced
+        nodes of a square lattice. The displacement is randomly gauss
+        distributed with the standard deviation \(\sigma\). This
+        \(\sigma\) is also called \emph{disturbance paramter} in the
+        following.
+        Each node \(i\) has a spin \(s_i = \pm 1\). Each edge has a
+        weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the distance
+        \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is called
+        \emph{interaction}. The hamiltonian of the Ising model is
+        \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)
+        where \(<i,j>\) means nearest neighbor.
+        For \(\sigma = 0\) this is the standard Ising model with
+        \(J = 1\).\\\\
+
+    \subsubsection{Algorithm}
+        Monte Carlo simulations are used to obtain any properties of the
+        model.
+        \paragraph{Metropolis}
+            A basic Monte Carlo algorithm is the Metropolis algorithm
+            \cite{Metropolis1953} ... [einzelheiten]
+        \paragraph{Wolff}
+            Close to the critical temperature \(T_c\) the Metropolis
+            gets slower. Using a cluster algorithm like the Wolff
+            algorithm \cite{Wolff1989} speeds things up.
+            ... [einzelheiten]
+        \paragraph{Parallel Tempering}
+            The main aim is to obtain the critical temperatures
+            \(T_c\) for different disturbance paramters \(\sigma\).
+            Therefore it is necessary to simulate for many temperatures,
+            so that \emph{Parallel Tempering}\footnote{Before R. H.
+                Swendsen published this paper, a algorithm \(MC^3\) was
+                already published with the same idea. [citation needed]}
+            \cite{ParallelTempering1986} is a suited algorithm. Parallel
+            Tempering simulates many identical systems at different
+            temperatures and periodically swaps the spin configurations
+            between two neighboring temperatures with probability
+            \(\). Some good descriptions are in
+            \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+        \paragraph{Implementation Details}
+            Here a mixture of the above three algorithms is used.
+            Each sweep a Metropolis sweep, a Wolff cluster step and a
+            Parallel Tempering swap are performed.
+        %~ Monte Carlo Simulationen:\\
+            %~ Wolff-Cluster Algorithmus \cite{Wolff1989} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
+            %~ Metropolis Sweep \cite{Metropolis1953} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
+            %~ Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\

### 2013-06-04 Tex/2_Auswertung.tex
Text auf Englisch und mehr notizen

\subsection{Auswertung}
    <J>(\sigma), Anmerkung zur Anomalie des GG und der Ähnlichkeit von <J> zu \(T_c\)\\

    Erklärung zu Autokorreltationszeit \(\tau\) und Equilibrierungszeit \(t_eq\)\\
    Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
    Bestimmung der kritischen Punkte\\
        Polyfit 4ten Grades durch Binder Kumulante \cite{Binder1981}\\
        Finite Size Scaling Vergleich der Exponenten (AutoScale \cite{Melchert2009}, Vergleich \cite[S. 59]{Pelissetto2002})\\

### 2013-06-05 Tex/chapters/model.tex
tex umstrukturiert und erste Bilder hinzugefügt

%~ \subsection{Model and Implementation}
%~ I will desribe the model in this section in a bottom-up fashion.
%~ First describing all parts and then connecting them.

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{sec:graphtypes}
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}.
    \begin{figure}[htbp]
        \centering
        %~ \subfigure{\input{GG_def}}
        %~ \subfigure{\input{RNG_def}}
        \subfigure{\input{images/GG_RNG_def}}
        \subfigure{\includegraphics[width=0.3\textwidth]{images/GGL12S03.pdf}}
        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNGL12S03.pdf}}
        \caption[Definition of the lunes and examples of the Gabriel
                and Relative Neighborhood Graph]
                {Left: Lunes of Gabriel Graph (red) and Relative
                    Neighborhood Graph (blue and red). Middle:
                    Example of a Gabriel Graph. Periodic nodes are
                    dashed. Right: Example of a Relative
                    Neighborhood Graph. Periodic nodes are dashed.}
        \label{fig:lunes}
    \end{figure}

    To construct these graphs the simple way is to test for every
    pair of nodes for every node if it lies in the lune of the pair.
    That is of complexity \(O (n^3)\).\\
    To reduce the complexity one can first create a Delaunay
    Triangulation in complexity \(O (n \log n)\)
    \cite{Leach1992} and test the criterion for each edge, because
    the Delaunay Triangulation is a supergraph of both. But the
    implementation of a Delaunay Triangulation algorithm is not
    trivial and the generation of the graphs is not time critical in
    the scope of this bachelor thesis.\\
    So a tradeoff is to use basicly the simple method but only test
    the criterion for nodes which are near to the lune and abort if
    one node inside the lune is found. To determine which nodes are
    near the lune one can save the position of every node in a
    \emph{cell list} according to \cite{RNGCell} and just test the
    nodes in the cells which contain the lune.

\subsection{Model}
    The used model is a modified 2D Ising model where the sites are
    displaced nodes of a square lattice with periodic boundary
    conditions. The displacement is randomly gauss distributed with the
    standard deviation \(\sigma\). This \(\sigma\) is also called
    \emph{disturbance paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)
    where \(<i,j>\) refers to by edges connected nodes.
    The edges are constructed according to the in section
    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
    called \emph{interaction}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\).

### 2013-06-05 Tex/chapters/monte_carlo.tex
tex umstrukturiert und erste Bilder hinzugefügt

--- 2013-05-13 Tex/1_Theorie.tex
@@
-\subsection{Modell}
-    Ising Modell \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)\\
-    zufälliges Gitter: Gaußverteilt\\
-    Kopplungskonstanten abstandsabhängig: \(J_{ij}=e^{(1-\alpha)d_{ij}}\)\\
-    Monte Carlo Simulationen:\\
-        Wolff-Cluster Algorithmus \cite{Wolff1989} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
-        Metropolis Sweep \cite{Metropolis1953} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
-        Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\
-    Relative Neighborhood Graph \cite{Toussaint1980}\\
-    Gabriel Graph \cite{Gabriel1969}\\
-        Cell Algorithmus ohne Delaunay Triangulation \cite{RNGCell}
-
-\cite{NewmanBarkema1999}
+\subsubsection{Algorithm}
+    Monte Carlo simulations are used to obtain any properties of the
+    model.
+    %Importance Sampling
+    %Detailed Balance
+    %Ergodicity
+    \paragraph{Metropolis}
+        A basic Monte Carlo algorithm is the Metropolis algorithm
+        \cite{Metropolis1953} ... [einzelheiten]
+    \paragraph{Wolff}
+        Close to the critical temperature \(T_c\) the Metropolis
+        gets slower. Using a cluster algorithm like the Wolff
+        algorithm \cite{Wolff1989} speeds things up.
+        ... [einzelheiten]
+    \paragraph{Parallel Tempering}
+        The main aim is to obtain the critical temperatures
+        \(T_c\) for different disturbance paramters \(\sigma\).
+        Therefore it is necessary to simulate for many temperatures,
+        so that \emph{Parallel Tempering}\footnote{Before R. H.
+            Swendsen published this paper, a algorithm \(MC^3\) was
+            already published with the same idea. [citation needed]}
+        \cite{ParallelTempering1986} is a suited algorithm. Parallel
+        Tempering simulates many identical systems at different
+        temperatures and periodically swaps the spin configurations
+        between two neighboring temperatures with probability
+        \(\). Some good descriptions are in
+        \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+    \paragraph{Implementation Details}
+        Here a mixture of the above three algorithms is used.
+        Each sweep a Metropolis sweep, a Wolff cluster step and a
+        Parallel Tempering swap are performed.
+    %~ Monte Carlo Simulationen:\\
+        %~ Wolff-Cluster Algorithmus \cite{Wolff1989} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
+        %~ Metropolis Sweep \cite{Metropolis1953} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
+        %~ Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\

### 2013-06-05 Tex/chapters/model.tex
weiteren Inhalt hinzugefügt

@@
 \subsection{Model}
-    The used model is a modified 2D Ising model where the sites are
-    displaced nodes of a square lattice with periodic boundary
-    conditions. The displacement is randomly gauss distributed with the
-    standard deviation \(\sigma\). This \(\sigma\) is also called
-    \emph{disturbance paramter} in the following.
+    The used model is a modified 2D Ising model where the \(N\)sites are
+    displaced nodes of a square lattice of edgelength \(L\) with
+    periodic boundary conditions. The displacement is randomly gauss
+    distributed with the standard deviation \(\sigma\). This \(\sigma\)
+    is also called \emph{disturbance paramter} in the following.
     The hamiltonian of the Ising model is
@@
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\).
+
+\subsection{Determining the Critical Temperature $T_c$}
+    Because the searched for property -- the critical temperature \(T_c\)
+    -- is only defined for infinite systems, hence every computer
+    simulation will show some \emph{finte size effects}.
+    [vielleicht Bild von intensiver Größe?]
+    Despite of this one can obtain \(T_c\) by finite size scaling
+    methods \cite[S. ??]{Newman1998} which also yield the critical
+    exponents [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
+    die exponenten reproduziert hat].\\
+    Though if one is just interested in the critical Temperature an
+    easier approach is to find the intersections of the binder cumulants
+    \(G\) \cite{Binder1981} for different system sizes \(L=\sqrt N\).\\

### 2013-06-05 auswertung/db.py
Fortschrittsanzeige zur Indexerstellung

@@ -352,10 +352,14 @@ class Database():
             (n blob, sigma real, L integer, x integer, T real, M blob, E blob, A real)""")
 
         self.addToDatabase(dataPath)
-
+        
+        logging.info("start creating indices")
         self.connRaw.execute("""CREATE INDEX idx_ex1 ON rawdata(sigma,L,T)""")
+        logging.info("  s,L,T finished")
         self.connRaw.execute("""CREATE INDEX idx_ex2 ON rawdata(L)""")
+        logging.info("  L finished")
         self.connRaw.execute("""CREATE INDEX idx_ex3 ON rawdata(T)""")
+        logging.info("  T finished")
 
     def addToDatabase(self, dataPath):
         """! Liest die Datendatein aus und sortiert ihre Inhalte in die

### 2013-06-06 auswertung/db.py
Auswertung fit fur parallele RNG und GG Verarbeitung

@@ -29,6 +29,7 @@ class Database():
         """
         self.dbPath = dbPath
         self.dbRawPath = dbRawPath
+        self.dataPath = dataPath
         self.graphType = graphType
         self.autocorrFlag = autocorrFlag
 
@@ -250,7 +251,7 @@ class Database():
 
     def writeFileForScalana(self, name, x, dx):
         """! Schreibt die Datendatei, für Scalada"""
-        directory = "../data/scalana/"
+        directory = os.path.join(self.dataPath,"scalana")
         if not os.path.exists(directory):
             os.makedirs(directory)
 
@@ -265,7 +266,7 @@ class Database():
     def writeFileForGnuplot(self, name, x, dx):
         """! Schreibt die Daten- und Skriptdateien, die die Gnuplot plots
         erstellen """
-        directory = "../data/out/"
+        directory = os.path.join(self.dataPath,"out")
         if not os.path.exists(directory):
             os.makedirs(directory)
 
@@ -306,7 +307,7 @@ class Database():
     def writeFileForGnuplot2(self, name, x, dx):
         """! Schreibt die Daten- und Skriptdateien, die die Gnuplot plots
         erstellen """
-        directory = "../data/out/"
+        directory = os.path.join(self.dataPath,"out")
         if not os.path.exists(directory):
             os.makedirs(directory)
 
@@ -352,7 +353,7 @@ class Database():
             (n blob, sigma real, L integer, x integer, T real, M blob, E blob, A real)""")
 
         self.addToDatabase(dataPath)
-        
+
         logging.info("start creating indices")
         self.connRaw.execute("""CREATE INDEX idx_ex1 ON rawdata(sigma,L,T)""")
         logging.info("  s,L,T finished")
@@ -464,5 +465,5 @@ class Database():
         return mean(E), self.bootstrap_stderr(E, 200, mean)
 
 if __name__ == '__main__':
-    a=Database( dbPath = "data.db", dataPath = "../data", graphType=1)
-    #~ b=Database( dbPath = "dataGG.db", dataPath = "../data", graphType=2)
+    a=Database( dbPath = "dataRNG.db", dataPath = "../dataRNG", graphType=1)
+    b=Database( dbPath = "dataGG.db", dataPath = "../dataGG", graphType=2)

### 2013-06-06 auswertung/fitPolyAndFindIntersection.py

@@ -101,21 +101,45 @@ class BinderIntersections():
             f.write("set key right\n")
 
 if __name__ == "__main__":
-    directory = "../data/binderIntersect/"
-    if not os.path.exists(directory):
-        os.makedirs(directory)
 
-    a = BinderIntersections()
     sizes = [16,32,64,128]
 
     logging.info("possible intersections: " + str([x for x in combinations(sizes, 2)]))
 
-    sigmas = (0.00, 0.03, 0.05, 0.08, 0.10, 0.12, 0.15, 0.20, 0.25, 0.30, 0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1.00, 1.10, 1.20)
-    downs  = (2.25, 2.25, 2.25, 2.23, 2.18, 2.07, 1.85, 1.60, 1.45, 1.38, 1.30, 1.24, 1.22, 1.20, 1.18, 1.17, 1.18, 1.18, 1.18)
-    ups    = (2.30, 2.30, 2.30, 2.30, 2.25, 2.15, 1.95, 1.68, 1.53, 1.45, 1.38, 1.32, 1.30, 1.28, 1.26, 1.26, 1.24, 1.24, 1.24)
+    sigmas    = (0.00, 0.03, 0.05, 0.08, 0.10, 0.12, 0.15, 0.20, 0.25, 0.30, 0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1.00, 1.10, 1.20)
+    downsRNG  = (2.25, 2.25, 2.25, 2.23, 2.18, 2.07, 1.85, 1.60, 1.45, 1.38, 1.30, 1.24, 1.22, 1.20, 1.18, 1.17, 1.18, 1.18, 1.18)
+    upsRNG    = (2.30, 2.30, 2.30, 2.30, 2.25, 2.15, 1.95, 1.68, 1.53, 1.45, 1.38, 1.32, 1.30, 1.28, 1.26, 1.26, 1.24, 1.24, 1.24)
+    downsGG   = (2.25, 2.80, 2.80, 2.80, 2.85, 2.85, 2.85, 2.80, 2.60, 2.50, 2.30, 2.20, 2.15, 2.15, 2.10, 2.10, 2.00, 2.00, 2.00)
[…]

### 2013-06-06 auswertung/getConfig.py
neue Parameter fur GG Graphen

@@ -10,7 +10,8 @@ def getConfig():
 
     sigmas = (0.00, 0.03, 0.05, 0.08, 0.10, 0.12, 0.15, 0.20, 0.25, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2)
 
-    # minimal:
+    ####################################################################
+    # RNG:
     #~ t16=",".join([str(i) for i in arange(0.1,2.0,0.15)]+[str(i) for i in arange(2.0,3.3,0.2)])
     # genug Daten an Tc:
     t16l=",".join([str(i) for i in arange(0.1,1.8,0.15)]+[str(i) for i in arange(1.8,2.4,0.02)]+[str(i) for i in arange(2.4,3.3,0.2)])
@@ -23,6 +24,32 @@ def getConfig():
     t32l=",".join([str(i) for i in arange(0.1,0.9,0.14)]+[str(i) for i in arange(0.9,1.8,0.09)]+[str(i) for i in arange(1.8,2.4,0.02)]+[str(i) for i in arange(2.4,3.3,0.09)])
     t32m=",".join([str(i) for i in arange(0.1,0.9,0.14)]+[str(i) for i in arange(0.9,1.4,0.09)]+[str(i) for i in arange(1.4,2.0,0.02)]+[str(i) for i in arange(2.0,3.3,0.09)])
     t32h=",".join([str(i) for i in arange(0.1,0.9,0.14)]+[str(i) for i in arange(0.9,1.1,0.09)]+[str(i) for i in arange(1.1,1.5,0.02)]+[str(i) for i in arange(1.5,3.3,0.09)])
+    # minimal:
+    #~ t64l=",".join([str(i) for i in arange(0.1,0.9,0.15)]+[str(i) for i in arange(0.9,2.30,0.03)]+[str(i) for i in arange(2.30,3.3,0.05)]) #passend fur 64
+    #~ t64h=",".join([str(i) for i in arange(0.1,0.8,0.08)]+[str(i) for i in arange(0.8,1.50,0.02)]+[str(i) for i in arange(1.5,2.30,0.035)]+[str(i) for i in arange(2.30,3.3,0.07)]) #passend fur 64
+    t64l=",".join([str(i) for i in arange(0.1,0.9,0.15)]+[str(i) for i in arange(0.9,2.30,0.03)]+[str(i) for i in arange(2.30,3.3,0.05)]) #passend fur 64
[…]

### 2013-06-06 spin.c
Funktion yum ermitteln des mittleren Grades des Graphen

@@ -394,7 +394,7 @@ void do_mc_simulation(gs_graph_t **list_of_graphs, const options_t o)
         exit(-1);
     }
     /* Schreibe Header */
-    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # <J>=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, get_mean_weight(list_of_graphs[0]));
+    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # <J>=%.6f # deg=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, get_mean_weight(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]));
     for(nT=0;nT<o.num_temps;nT++)
         fprintf(data_out_file, "%.3f, ", list_of_graphs[nT]->T);
     fprintf(data_out_file, "\n");
@@ -860,6 +860,23 @@ double get_mean_weight(gs_graph_t *g)
         }
     /* Es sollte egal sein, dass über jede Kante zweimal summiert wird */
     return (sum / count);
+}
+
+/*! \fn double get_mean_deg(gs_graph_t *g)
+    \brief Diese Funktion gibt den mittlere Kantenzahl pro Knoten aus
+
+    \param [in] g Graph über den gemittelt wird
+    \return mittlere Kantenzahl pro Knoten aus
+*/
+double get_mean_deg(gs_graph_t *g)
+{
+    int n, i;
+    int count = 0;
+    for(n=0;n<g->num_nodes; n++)
+        for(i=0;i<g->node[n].num_neighbors;i++)
+            count++;
+    /* Korrektur, da über jede Kante zweimal summiert wird */
+    return (count/g->num_nodes/2);
 }
 
 /*! \fn void init_spins_randomly(gs_graph_t *g, gsl_rng *rng)

### 2013-06-06 spin.h

@@ -87,6 +87,7 @@ inline int check_gabriel(double dist12, gs_node_t node1, gs_node_t node2, gs_nod
 inline void get_cell_border_gabriel(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
 void create_edges(gs_graph_t *g, options_t o);
 double get_mean_weight(gs_graph_t *g);
+double get_mean_deg(gs_graph_t *g);
 
 void init_spins_randomly(gs_graph_t *g, gsl_rng *rng);
 void init_spins_up(gs_graph_t *g);

### 2013-06-07 auswertung/getConfig.py
übersichtlicher strukturiert

@@ -11,48 +11,43 @@ def getConfig():
     sigmas = (0.00, 0.03, 0.05, 0.08, 0.10, 0.12, 0.15, 0.20, 0.25, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2)
 
     ####################################################################
-    # RNG:
-    #~ t16=",".join([str(i) for i in arange(0.1,2.0,0.15)]+[str(i) for i in arange(2.0,3.3,0.2)])
-    # genug Daten an Tc:
-    t16l=",".join([str(i) for i in arange(0.1,1.8,0.15)]+[str(i) for i in arange(1.8,2.4,0.02)]+[str(i) for i in arange(2.4,3.3,0.2)])
-    t16m=",".join([str(i) for i in arange(0.1,1.4,0.15)]+[str(i) for i in arange(1.4,2.0,0.02)]+[str(i) for i in arange(2.0,3.3,0.2)])
-    t16h=",".join([str(i) for i in arange(0.1,1.1,0.15)]+[str(i) for i in arange(1.1,1.5,0.02)]+[str(i) for i in arange(1.5,3.3,0.2)])
     # minimal:
+    #~ t16=",".join([str(i) for i in arange(0.1,2.0,0.15)]+[str(i) for i in arange(2.0,3.3,0.2)])
     #~ t32l=",".join([str(i) for i in arange(0.1,0.9,0.14)]+[str(i) for i in arange(0.9,3.3,0.09)])
     #~ t32h=",".join([str(i) for i in arange(0.1,0.9,0.14)]+[str(i) for i in arange(0.9,3.3,0.09)])
-    # genug Daten an Tc:
-    t32l=",".join([str(i) for i in arange(0.1,0.9,0.14)]+[str(i) for i in arange(0.9,1.8,0.09)]+[str(i) for i in arange(1.8,2.4,0.02)]+[str(i) for i in arange(2.4,3.3,0.09)])
-    t32m=",".join([str(i) for i in arange(0.1,0.9,0.14)]+[str(i) for i in arange(0.9,1.4,0.09)]+[str(i) for i in arange(1.4,2.0,0.02)]+[str(i) for i in arange(2.0,3.3,0.09)])
[…]

### 2013-06-07 auswertung/getJ.py
Grad und Summe der J werden gemessen

@@ -5,28 +5,51 @@ import os
 from reader import *
 
 def getJFromDat(dataPath):
-    d = {}
+    J = {}
+    sumJ = {}
+    deg = {}
 
     for f in sorted(os.listdir(dataPath)):
         if not ".dat" in f:
             continue
-        if "L_032_" in f:
+        if not "L_032_" in f:
             continue
 
         r = output_reader(os.path.join(dataPath,f))
         try:
-            d[r.sigma].append(float(r.J))
+            J[r.sigma].append(float(r.J))
         except KeyError:
-            d.update({r.sigma:[float(r.J)]})
+            J.update({r.sigma:[float(r.J)]})
+        try:
+            sumJ[r.sigma].append(float(r.sumJ))
+        except KeyError:
+            sumJ.update({r.sigma:[float(r.sumJ)]})
+        try:
+            deg[r.sigma].append(float(r.deg))
+        except KeyError:
+            deg.update({r.sigma:[float(r.deg)]})
 
-    print d
-    for key in d.keys():
-        d[key] = [mean(d[key]), std(d[key])/sqrt(len(d[key]))]
+    #~ print d
+    for key in J.keys():
+        J[key] = [mean(J[key]), std(J[key])/sqrt(len(J[key]))]
+    for key in sumJ.keys():
+        sumJ[key] = [mean(sumJ[key]), std(sumJ[key])/sqrt(len(sumJ[key]))]
+    for key in deg.keys():
+        deg[key] = [mean(deg[key]), std(deg[key])/sqrt(len(deg[key]))]
 
     print dataPath
-    for [key, val] in sorted(d.items()):
+    print "<J>"
+    for [key, val] in sorted(J.items()):
+        print key, " : ", val[0], "+-", val[1]
+    print " "
+    print "sumJ"
+    for [key, val] in sorted(sumJ.items()):
+        print key, " : ", val[0], "+-", val[1]
+    print " "
+    print "deg"
+    for [key, val] in sorted(deg.items()):
         print key, " : ", val[0], "+-", val[1]
     print " "
 
-#~ getJFromDat("../data/GG")
+#getJFromDat("../data/GG")
 getJFromDat("../data/RNG")

### 2013-06-07 auswertung/reader.py

@@ -71,7 +71,8 @@ class output_reader():
             self.L = " ".join(header).rpartition("L=")[2].partition (" #")[0]
             self.graphType = " ".join(header).rpartition("type=")[2].partition (" #")[0]
             self.J = " ".join(header).rpartition("<J>=")[2].partition (" #")[0]
-            if self.J == "# N E M": self.J="0"
+            self.sumJ = " ".join(header).rpartition("sumJ=")[2].partition (" #")[0]
+            self.deg = " ".join(header).rpartition("deg=")[2].partition (" #")[0]
 
             # Zwischenspeichern, da Einträge im Reader verbraucht werden
             alle = [i for i in reader]

### 2013-06-07 spin.c

@@ -25,8 +25,6 @@ int main(int argc, char *argv[])
     if(o.verbose)
         fprintf(stdout,"Starte Initialisierung\n");
     list_of_graphs = init_graphs(o);
-    if(o.verbose)
-        fprintf(stdout,"<J> = %f\n", get_mean_weight(list_of_graphs[0]));
 
     if(o.verbose)
         fprintf(stdout,"Starte Monte Carlo Simulation\n");
@@ -394,7 +392,7 @@ void do_mc_simulation(gs_graph_t **list_of_graphs, const options_t o)
         exit(-1);
     }
     /* Schreibe Header */
-    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # <J>=%.6f # deg=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, get_mean_weight(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]));
+    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # <J>=%.6f # deg=%.6f # sumJ=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, get_mean_weight(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]), get_sum_weight(list_of_graphs[0]));
     for(nT=0;nT<o.num_temps;nT++)
         fprintf(data_out_file, "%.3f, ", list_of_graphs[nT]->T);
     fprintf(data_out_file, "\n");
@@ -862,6 +860,24 @@ double get_mean_weight(gs_graph_t *g)
     return (sum / count);
 }
 
+/*! \fn double get_sum_weight(gs_graph_t *g)
+    \brief Diese Funktion gibt die Summe der Kantengewichte pro Knoten
+            im Graphen g aus
+
+    \param [in] g Graph der untersucht wird
+    \return Summe der Kantengewichte pro Knoten
+*/
+double get_sum_weight(gs_graph_t *g)
+{
+    int n, i;
+    double sum = 0;
+    for(n=0;n<g->num_nodes; n++)
+        for(i=0;i<g->node[n].num_neighbors;i++)
+            sum += g->node[n].neighbors[i].weight;
+
+    return (sum / g->num_nodes);
+}
+
 /*! \fn double get_mean_deg(gs_graph_t *g)
[…]

### 2013-06-07 spin.h

@@ -88,6 +88,7 @@ inline void get_cell_border_gabriel(gs_node_t node1, gs_node_t node2, double dis
 void create_edges(gs_graph_t *g, options_t o);
 double get_mean_weight(gs_graph_t *g);
 double get_mean_deg(gs_graph_t *g);
+double get_sum_weight(gs_graph_t *g);
 
 void init_spins_randomly(gs_graph_t *g, gsl_rng *rng);
 void init_spins_up(gs_graph_t *g);

### 2013-06-07 spin.c
kritischen Fehler bei Bestimmung des Grades beseitigt

@@ -887,7 +887,7 @@ double get_sum_weight(gs_graph_t *g)
 double get_mean_deg(gs_graph_t *g)
 {
     int n, i;
-    int count = 0;
+    double count = 0;
     for(n=0;n<g->num_nodes; n++)
         for(i=0;i<g->node[n].num_neighbors;i++)
             count++;

### 2013-06-07 auswertung/getJ.py
Dateien werden jetzt automatisch geschrieben

@@ -4,15 +4,17 @@
 import os
 from reader import *
 
-def getJFromDat(dataPath):
+def getJFromDat(dataPath, outPath, L):
     J = {}
     sumJ = {}
     deg = {}
+    if not os.path.exists(outPath):
+        os.makedirs(outPath)
 
     for f in sorted(os.listdir(dataPath)):
         if not ".dat" in f:
             continue
-        if not "L_032_" in f:
+        if not "L_{0:03d}_".format(L) in f:
             continue
 
         r = output_reader(os.path.join(dataPath,f))
@@ -39,17 +41,27 @@ def getJFromDat(dataPath):
 
     print dataPath
     print "<J>"
-    for [key, val] in sorted(J.items()):
-        print key, " : ", val[0], "+-", val[1]
-    print " "
-    print "sumJ"
-    for [key, val] in sorted(sumJ.items()):
-        print key, " : ", val[0], "+-", val[1]
-    print " "
-    print "deg"
-    for [key, val] in sorted(deg.items()):
-        print key, " : ", val[0], "+-", val[1]
+    with open(os.path.join(outPath, "meanJ_L{0}.dat".format(L)), "w") as f:
+        for [key, val] in sorted(J.items()):
+            print key, " : ", val[0], "+-", val[1]
+            f.write("{0} {1} {2}\n".format(key,val[0],val[1]))
     print " "
 
-#getJFromDat("../data/GG")
-getJFromDat("../data/RNG")
+    print "sumJ"
+    with open(os.path.join(outPath, "sumJ_L{0}.dat".format(L)), "w") as f:
+        for [key, val] in sorted(sumJ.items()):
+            print key, " : ", val[0], "+-", val[1]
+            f.write("{0} {1} {2}\n".format(key,val[0],val[1]))
+    print " "
+
+    print "deg"
+    with open(os.path.join(outPath, "deg_L{0}.dat".format(L)), "w") as f:
+        for [key, val] in sorted(deg.items()):
+            print key, " : ", val[0], "+-", val[1]
+            f.write("{0} {1} {2}\n".format(key,val[0],val[1]))
+    print " "
+
+getJFromDat("../data/GG", "GG", 16)
+getJFromDat("../data/RNG", "RNG", 16)
+getJFromDat("../data/GG", "GG", 32)
+getJFromDat("../data/RNG", "RNG", 32)

### 2013-06-07 Tex/chapters/model.tex
Weiter im Text

@@
     \emph{cell list} according to \cite{RNGCell} and just test the
-    nodes in the cells which contain the lune.
+    nodes in the cells which resemble a rectangular bounding box of the
+    lune.
 
@@
     called \emph{interaction}.\\
-    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\).
+    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
+    for which exists an analytical solution \cite{Onsager1944}.\\
 
-\subsection{Determining the Critical Temperature $T_c$}
+    For evaluation the Monte Carlo simulation is is run till the system
+    is equilibrated after \(t_eq\) sweeps. Then the simulation continues
+    and the magnetisation per site \(m\) and energy of the system \(E\)
+    are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
+    denotes the \emph{autocorrelation time} after which two states of
+    the system are not correlated anymore.
+    For every observable \(O\) the expected value \(<O>\) is averaged
+    over different randomly generated lattices \(\overline{<O>}\). The
+    errors are estimated by bootstrapping.
+
+\subsection{Critical Temperature $T_c$ and Critical Exponents}
     Because the searched for property -- the critical temperature \(T_c\)
@@
     methods \cite[S. ??]{Newman1998} which also yield the critical
-    exponents [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
+    exponents. The critical exponents should not be influenced by the
+    disturbance paramter \(\sigma\) [citation needed]. So they will be
+    used for consistency cross checking and comparision with the known
+    exact values.\\
+    [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
     die exponenten reproduziert hat].\\
@@
     easier approach is to find the intersections of the binder cumulants
-    \(G\) \cite{Binder1981} for different system sizes \(L=\sqrt N\).\\
+    \(g = (3-\frac{<m^4>}{2<m^2>^2}\) \cite{Binder1981} of different
+    system sizes \(L=\sqrt N\).\\

### 2013-06-07 Tex/chapters/model.tex
mehr Text und Anmerkungen

@@
     exact values.\\
+    [theorie mit dem Collaps]
+    [Erklärung autoscale]
+    [Am besten hier direkt die ganze Auswertung rein]
     [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
@@
     \(g = (3-\frac{<m^4>}{2<m^2>^2}\) \cite{Binder1981} of different
-    system sizes \(L=\sqrt N\).\\
+    system sizes \(L=\sqrt N\).
+    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
+    the intersection. [vgl. Grafik (villeicht)]
+    %The arithmetic average of the intersections are plotted [hier schon?]
+    [Und den rest der Auswertung]
+    \\

### 2013-06-07 Tex/chapters/model.tex
Besseres Erwartungswert Zeichen

--- 2013-06-07 Tex/chapters/model.tex
@@
     The hamiltonian of the Ising model is
-    \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)
-    where \(<i,j>\) refers to by edges connected nodes.
+    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
+    where \(\avg{i,j}\) refers to by edges connected nodes.
     The edges are constructed according to the in section
@@
     For evaluation the Monte Carlo simulation is is run till the system
-    is equilibrated after \(t_eq\) sweeps. Then the simulation continues
+    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
     and the magnetisation per site \(m\) and energy of the system \(E\)
@@
     the system are not correlated anymore.
-    For every observable \(O\) the expected value \(<O>\) is averaged
-    over different randomly generated lattices \(\overline{<O>}\). The
+    For every observable \(O\) the expected value \(\avg{O}\) is averaged
+    over different randomly generated lattices \(\overline{\avg{O}}\). The
     errors are estimated by bootstrapping.
@@
     used for consistency cross checking and comparision with the known
-    exact values.\\
-    [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
+    exact values \cite[S. 59]{Pelissetto2002}.\\
+    %~ [theorie mit dem Collaps]
+    %~ [Erklärung autoscale]
+    %~ [Am besten hier direkt die ganze Auswertung rein]
+    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
     die exponenten reproduziert hat].\\
@@
     easier approach is to find the intersections of the binder cumulants
-    \(g = (3-\frac{<m^4>}{2<m^2>^2}\) \cite{Binder1981} of different
-    system sizes \(L=\sqrt N\).\\
+    \(g = \brac{3-\frac{\avg{m^4}}{2\avg{m^2}^2}}\) \cite{Binder1981} of different
+    system sizes \(L=\sqrt N\).
+    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
+    the intersection. %[vgl. Grafik (villeicht)]
+    The arithmetic average of the intersections are plotted [hier schon?]
+    %~ [Und den rest der Auswertung]
+    \\

### 2013-06-08 auswertung/getConfig.py
Parameter optimiert

@@ -10,6 +10,13 @@ def getConfig():
 
     sigmas = (0.00, 0.03, 0.05, 0.08, 0.10, 0.12, 0.15, 0.20, 0.25, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2)
 
+    equilibrium             = {16:20*2,  32:50*2,  64:50*2, 128:100*2, 256:300*2}
+    #~ equilibrium             = {16:0,  32:0,  64:0, 128:0, 256:0}
+    autokorr                = {16: 3*2,  32: 5*2,  64: 7*2, 128: 12*2, 256: 16*2}
+    realisierungUnordnung   = {16:100,   32:100,   64:100,  128:100,   256:100}
+    sweeps                  = {16:10000, 32:10000, 64:5000, 128:5000,  256:5000}
+    #~ sweeps                  = {16:0, 32:0, 64:0, 128:0,  256:0}
+
     ####################################################################
     # minimal:
     #~ t16=",".join([str(i) for i in arange(0.1,2.0,0.15)]+[str(i) for i in arange(2.0,3.3,0.2)])
@@ -40,12 +47,29 @@ def getConfig():
     #~ t256l=",".join([str(i) for i in arange(0.1,0.55,0.1)]+[str(i) for i in arange(0.55,1.5,0.06)]+[str(i) for i in arange(1.5,1.8,0.008)]+[str(i) for i in arange(1.8,2.08,0.01)]+[str(i) for i in arange(2.08,2.56,0.007)]+[str(i) for i in arange(2.56,3.3,0.017)]) #passend fur 256
     #~ t256m=",".join([str(i) for i in arange(0.1,0.55,0.1)]+[str(i) for i in arange(0.55,1.5,0.006)]+[str(i) for i in arange(1.5,1.8,0.004)]+[str(i) for i in arange(1.8,2.08,0.01)]+[str(i) for i in arange(2.08,2.44,0.007)]+[str(i) for i in arange(2.44,3.3,0.017)]) #passend fur 256
[…]

### 2013-06-08 auswertung/db.py
Kompression minimal (ca. 3x kleiner als vorher und 3x schneller als standard)

@@ -97,7 +97,7 @@ class Database():
         Speichern in der Datenbank um"""
         a = array.array('d')
         a.extend(x)
-        return buffer(zlib.compress(a.tostring()))
+        return buffer(zlib.compress(a.tostring(),1))
 
     @staticmethod
     def getMean(x,T,L):

### 2013-06-08 call.py
Multiprocessing für lokale Jobbearbeitung

@@ -3,11 +3,15 @@
 
 import os
 from subprocess import call
+from multiprocessing import Process, cpu_count
 from numpy import arange
 from auswertung.getConfig import getConfig
 
 def f(config):
     """Diese Funktion startet die Simulation für verschiedene Parameter"""
+    n=0
+    nWorker = cpu_count()
+    p=[]
     for [s,x,N,l,t,t_eq,tau] in config:
         for x in range(1,x+1):
             opts = ["./ising", "-T{0}".format(t),
@@ -15,9 +19,17 @@ def f(config):
                    "-N{0}".format(t_eq+N*tau),
                    "-v", "-u0", "-x{0}".format(x), "-w", "-p",
                    "-s{0}".format(s), "-a0.5", #"-gOut_s_{0}_x_{1}_L{2}.svg".format(s,x,l),
-                   "-t1", "-i{0}".format(tau)]
+                   "-t2", "-i{0}".format(tau)]
             print " ".join(opts)
-            #~ call(opts)
+
+            if n < nWorker:
+                p.append(Process(target=call, args=(opts,)))
+                p[-1].start()
+                n+=1
+            else:
+                [i.join() for i in p]
+                n=0
+                p=[]
 
 if __name__ == '__main__':
     directory = "data/"

### 2013-06-09 auswertung/fitPolyAndFindIntersection.py
Parameter für GG angepasst

@@ -109,8 +109,8 @@ if __name__ == "__main__":
     sigmas    = (0.00, 0.03, 0.05, 0.08, 0.10, 0.12, 0.15, 0.20, 0.25, 0.30, 0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1.00, 1.10, 1.20)
     downsRNG  = (2.25, 2.25, 2.25, 2.23, 2.18, 2.07, 1.85, 1.60, 1.45, 1.38, 1.30, 1.24, 1.22, 1.20, 1.18, 1.17, 1.18, 1.18, 1.18)
     upsRNG    = (2.30, 2.30, 2.30, 2.30, 2.25, 2.15, 1.95, 1.68, 1.53, 1.45, 1.38, 1.32, 1.30, 1.28, 1.26, 1.26, 1.24, 1.24, 1.24)
-    downsGG   = (2.25, 2.80, 2.80, 2.80, 2.85, 2.85, 2.85, 2.80, 2.60, 2.50, 2.30, 2.20, 2.15, 2.15, 2.10, 2.10, 2.00, 2.00, 2.00)
-    upsGG     = (2.30, 2.95, 2.95, 3.00, 3.00, 3.00, 3.00, 2.90, 2.80, 2.70, 2.40, 2.30, 2.30, 2.30, 2.25, 2.20, 2.20, 2.20, 2.20)
+    downsGG   = (2.25, 2.80, 2.80, 2.80, 2.85, 2.85, 2.85, 2.80, 2.60, 2.48, 2.25, 2.20, 2.15, 2.12, 2.10, 2.08, 2.08, 2.08, 2.08)
+    upsGG     = (2.30, 2.94, 2.95, 2.95, 2.95, 3.00, 3.00, 2.90, 2.75, 2.60, 2.40, 2.30, 2.25, 2.22, 2.22, 2.20, 2.20, 2.20, 2.20)
     results = {}
 
 

### 2013-06-11 Tex/chapters/model.tex
kleinere Korrekturen
Unnötige Klammer, falsche Jahreszahl
nur Notizen

@@
         \centering
-        %~ \subfigure{\input{GG_def}}
-        %~ \subfigure{\input{RNG_def}}
         \subfigure{\input{images/GG_RNG_def}}
-        \subfigure{\includegraphics[width=0.3\textwidth]{images/GGL12S03.pdf}}
-        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNGL12S03.pdf}}
+        \subfigure{\includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}}
+        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}}
         \caption[Definition of the lunes and examples of the Gabriel
@@
     %~ [Am besten hier direkt die ganze Auswertung rein]
-    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
-    die exponenten reproduziert hat].\\
+    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
     Though if one is just interested in the critical Temperature an
     easier approach is to find the intersections of the binder cumulants
-    \(g = \brac{3-\frac{\avg{m^4}}{2\avg{m^2}^2}}\) \cite{Binder1981} of different
+    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
     system sizes \(L=\sqrt N\).
@@
     \\
+
+% Erwahnen, dass T_c Graph so aussieht, wie degree graph
+% mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
+% cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52

### 2013-06-11 Tex/chapters/model.tex
Text

@@
     simulation will show some \emph{finte size effects}.
-    [vielleicht Bild von intensiver Größe?]
+    %[vielleicht Bild von intensiver Größe?]
     Despite of this one can obtain \(T_c\) by finite size scaling
@@
     Though if one is just interested in the critical Temperature an
-    easier approach is to find the intersections of the binder cumulants
+    easier approach is to find the intersections of the Binder cumulants
     \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
@@
     Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
-    the intersection. %[vgl. Grafik (villeicht)]
-    The arithmetic average of the intersections are plotted [hier schon?]
+    the intersection.
+    In figure \ref{fig:binder_fit_s_0} such a fit is plotted for
+    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
+    To determine \(T_c\) the intersections are averaged and the standard
+    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
+    is in very good agreement with the exact solution
+    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
+    \begin{figure}[htbp]
+        \centering
+        \subfigure{\includegraphics[width=0.5\textwidth]{images/binder_fit_s_0}}
+        \caption[Binder cumulant fitted with polynom of degree 4]
+                {Binder cumulant fitted with polynom of degree 4
+                (the errorbars are too small to see)}
+        \label{fig:binder_fit_s_0}
+    \end{figure}%[vgl. Grafik (villeicht)]
+    % The arithmetic average of the intersections are plotted [hier schon?]
     %~ [Und den rest der Auswertung]
-    \\
 

### 2013-06-12 Tex/chapters/introduction.tex
Einleitung: ersten Entwurf geschrieben

The computing capabilities of modern computers enables researchers to
collect and analyse vast amounts of data.
Further statistical systems, for which there exist no analytical soultions
or only for very simplified or special cases, can be simulated.
%~ Simulations also have the advantage to be able to measure some quantities
%~ which are not obtainable by experiment.
For example to examine phasetransitions, which are defined by the abrupt
change of an observable ie. the change of the magnetisation of a
ferromagnet near the Curie temperature or the change of the density of
water near boiling. Unfortunatly the memory of any computer is small in
comparison with the thermodynamic limit.
%~ Of course it is only possible to simulate systems of finite size because
%~ of the finite memory of computers so the thermodynamic limit can not be
%~ simulated directly.
This leads to \emph{finite size effects}. In section \ref{ssec:finitesize}
will be discussed how to manage them.\\

One of the simplest models with a second order phasetransition is the
Ising model \cite{Ising1925} which is a simple model of a ferromagnet
and will be explained in more detail in section \ref{ssec:isingmodel}.
It is analyticaly solved for two dimensions on some regular lattices
\cite{Onsager1944} \cite{Wannier1945}.
In this thesis the critical behavior on some irregular lattices
resembling proximity graphs (see section \ref{ssec:graphtypes}) will be
examined using the Monte Carlo simulations described in section
\ref{sec:montecarlo}.

### 2013-06-12 Tex/chapters/model.tex
Einleitung: ersten Entwurf geschrieben

@@
 \subsection{Gabriel- and Relative Neighborhood Graph}
-\label{sec:graphtypes}
+\label{ssec:graphtypes}
     The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
@@
 \subsection{Model}
+\label{ssec:isingmodel}
     The used model is a modified 2D Ising model where the \(N\)sites are
@@
 \subsection{Critical Temperature $T_c$ and Critical Exponents}
+\label{ssec:finitesize}
     Because the searched for property -- the critical temperature \(T_c\)
@@
         \centering
-        \subfigure{\includegraphics[width=0.5\textwidth]{images/binder_fit_s_0}}
+        \subfigure{\includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}}
         \caption[Binder cumulant fitted with polynom of degree 4]

### 2013-06-12 Tex/chapters/model.tex
weiter im Text

@@
     distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
-    called \emph{interaction}.\\
+    called \emph{coupling constant}.\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),

### 2013-06-12 Tex/chapters/monte_carlo.tex
Einleitung: ersten Entwurf geschrieben
weiter im Text

@@
-\subsubsection{Algorithm}
-    Monte Carlo simulations are used to obtain any properties of the
-    model.
-    %Importance Sampling
-    %Detailed Balance
-    %Ergodicity
+\label{sec:montecarlo}
+Monte Carlo simulations are (probalby) named after the casino in Monaco
+\cite{NewmanBarkema1999} because both rely on randomness.\\
+The idea behind Monte Carlo simulations is to take random samples of
+the observable which should be measured and estimate the observable from
+this samples. In example the Monte Carlo integration chooses random
+points within the bounding box of the fuction and estimates the integral
+as the fraction of points below the function and points above muliplied
+by the area of the bounding box.\\
+%~ To improve this method: \emph{Importance Sampling}
+%~ means that one takes more samples where the contribution of the
+%~ function to the integral is bigger by using random numbers
+%~ distributed........
+It is difficult to create random state of the Ising system in
+equilibrium, hence one uses \emph{Markov Chains} to generate new states
+\(\nu\) from old ones \(\mu\).
+It is important that the transition probabilities \(A(\mu \to \nu)\)
+obey \emph{Detailed Balance}, that the probability to leave a state is
+the same as the probability to enter the state in equilibrium
+\(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\)
+with \(p_\mu\) the probability to be in state \(\mu\), and
+\emph{Ergodicity}, that every possible state is reachable from every
+other state in finite time. \cite{NewmanBarkema1999} \cite{Katzgraber2011}\\
+Otherwise the samples might not be representative for the whole system.
+
+\subsection{Monte Carlo Algorithms}
     \paragraph{Metropolis}
-        A basic Monte Carlo algorithm is the Metropolis algorithm
-        \cite{Metropolis1953} ... [einzelheiten]
+        Let \(\Delta \hat H(\mu,\nu)\) be the energy difference between
+        the states \(\mu\) and \(\nu\)
+        \begin{equation}
+            \Delta \hat H = \hat H(\nu) - \hat H(\mu)
+        \end{equation}
+        The Metropolis algorithm \cite{Metropolis1953} chooses the transition
+        probability like eq. \ref{eq:metropolis}
+        \begin{equation}
+            A(\mu \to \nu)
+            \begin{cases}
+                1                                   & \Delta \hat H \le 0 \\
+                \exp{\brac{-\beta \Delta \hat H}}   & \Delta \hat H > 0
+            \end{cases}
+            \label{eq:metropolis}
+        \end{equation}
+        A Metropolis Monte Carlo simulation of an Ising model will choose a
+        random spin, calculate the energy change \(\Delta \hat H\) that would
+        result from a flip of and excute the flip with the probability \(A\).
+        \cite{NewmanBarkema1999} \cite{Katzgraber2011}
+
     \paragraph{Wolff}
         Close to the critical temperature \(T_c\) the Metropolis
-        gets slower. Using a cluster algorithm like the Wolff
+        gets slower. This is called \emph{critical slowing} down and the
+        cause is beyond the scope of this thesis.\\
+        Using a cluster algorithm like the Wolff
         algorithm \cite{Wolff1989} speeds things up.
-        ... [einzelheiten]
+        For an Ising model the Wolff algorithm builds a cluster of sites
+        starting with an random seed and adding neighboring sites with
+        the same spin with probability
+        \(P_{\mathrm{add}} = 1-\exp\brac{-2\beta J}\)
+        where \(J\) is the coupling constant (explained in section
+        \ref{ssec:isingmodel}). The neighboring sites of the added sites
+        are also considered and so forth. When there are no more sites
+        to add, the spin of every site in the cluster is flipped.
+        \cite[S. ??]{NewmanBarkema1999} \cite[S. 151f]{Katzgraber2011}
+
     \paragraph{Parallel Tempering}
@@
         between two neighboring temperatures with probability
-        \(\). Some good descriptions are in
+        \begin{equation}
+            P((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}}
+        \end{equation}
+        Some good descriptions are in
         \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+
     \paragraph{Implementation Details}
@@
     %~ Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\
+
+\subsection{Equilibration- and Autocorrelation Time}
+    To generate an equilibrium state one starts with an arbitrary state
+    and waits until it is equilibrated. The count of sweeps till
+    equilibrium is called \emph{equilibration time} \(t_{eq}\).
+    All measurement should start after this time.
+    % in meinem fall ... vielleicht bild?
+    \\
+    Because every state is generated from the state before, measurements
+    of subsequent states are correlated. To determine when two states
+    are independet, one calculates the autocorrelation function \(\chi(t)\)
+    and integrates it to get the autocorrelation time \(\tau = \int \chi(t) \de t\).
+    \(\tau\) is an estimate after which time two samples are not
+    correlated anymore. \cite[S. ??]{NewmanBarkema1999} \cite[S. 150f]{Katzgraber2011}.
+    To make sure that the error is not underestimated one should wait
+    \(2\tau\) sweeps between two measurements.

### 2013-06-12 Tex/chapters/model.tex
Bilder in spezifische Unterverzeichnisse verschoben

--- 2013-06-11 Tex/chapters/model.tex
@@
         \centering
+        %~ \subfigure{\input{GG_def}}
+        %~ \subfigure{\input{RNG_def}}
         \subfigure{\input{images/GG_RNG_def}}
@@
     simulation will show some \emph{finte size effects}.
-    %[vielleicht Bild von intensiver Größe?]
+    [vielleicht Bild von intensiver Größe?]
     Despite of this one can obtain \(T_c\) by finite size scaling
@@
     %~ [Am besten hier direkt die ganze Auswertung rein]
-    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
+    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
+    die exponenten reproduziert hat].\\
     Though if one is just interested in the critical Temperature an
-    easier approach is to find the intersections of the Binder cumulants
+    easier approach is to find the intersections of the binder cumulants
     \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
@@
     Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
-    the intersection.
-    In figure \ref{fig:binder_fit_s_0} such a fit is plotted for
-    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
-    To determine \(T_c\) the intersections are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
-    is in very good agreement with the exact solution
-    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
-    \begin{figure}[htbp]
-        \centering
-        \subfigure{\includegraphics[width=0.5\textwidth]{images/binder_fit_s_0}}
-        \caption[Binder cumulant fitted with polynom of degree 4]
-                {Binder cumulant fitted with polynom of degree 4
-                (the errorbars are too small to see)}
-        \label{fig:binder_fit_s_0}
-    \end{figure}%[vgl. Grafik (villeicht)]
-    % The arithmetic average of the intersections are plotted [hier schon?]
+    the intersection. %[vgl. Grafik (villeicht)]
+    The arithmetic average of the intersections are plotted [hier schon?]
     %~ [Und den rest der Auswertung]
-
-% Erwahnen, dass T_c Graph so aussieht, wie degree graph
-% mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
-% cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
+    \\

### 2013-06-12 Tex/chapters/model.tex
weiter im Text

--- 2013-06-12 Tex/chapters/model.tex
@@
 \subsection{Gabriel- and Relative Neighborhood Graph}
-\label{ssec:graphtypes}
+\label{sec:graphtypes}
     The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
@@
 \subsection{Model}
-\label{ssec:isingmodel}
     The used model is a modified 2D Ising model where the \(N\)sites are
@@
 \subsection{Critical Temperature $T_c$ and Critical Exponents}
-\label{ssec:finitesize}
     Because the searched for property -- the critical temperature \(T_c\)
@@
         \centering
-        \subfigure{\includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}}
+        \subfigure{\includegraphics[width=0.3\textwidth]{images/binder_fit_s_0}}
         \caption[Binder cumulant fitted with polynom of degree 4]

### 2013-06-13 Tex/chapters/model.tex
Ausführlichere Beschreibung des Cell Algorithmus

--- 2013-06-12 Tex/chapters/model.tex
@@
     called \emph{lune} in the following. See also Figure
-    \ref{fig:lunes}.\\
+    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
     The Relative Neighborhood Graph \cite{Toussaint1980} is a
@@
     circles with radius \(r = d\) and centers on \(i\) and \(j\).
-    See also Figure \ref{fig:lunes}.
+    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
     \begin{figure}[htbp]
         \centering
-        \subfigure{\input{images/GG_RNG_def}}
-        \subfigure{\includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}}
-        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}}
-        \caption[Definition of the lunes and examples of the Gabriel
-                and Relative Neighborhood Graph]
-                {Left: Lunes of Gabriel Graph (red) and Relative
-                    Neighborhood Graph (blue and red). Middle:
-                    Example of a Gabriel Graph. Periodic nodes are
-                    dashed. Right: Example of a Relative
+        \subfigure[Definition of the lunes][]{
+                \label{sfig:lunes:def}
+                \input{images/GG_RNG_def}
+        }
+        \subfigure[Gabriel graph example][]{
+                \label{sfig:lunes:gg}
+                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
+        }
+        \subfigure[Relative Neighborhood graph example][]{
+                \label{sfig:lunes:rng}
+                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
+        }
+        \caption[Gabriel - and Relative Neighborhood Graph]
+                {\subref{sfig:lunes:def} Lunes of Gabriel Graph (red)
+                    and Relative Neighborhood Graph (blue and red).
+                 \subref{sfig:lunes:gg} Example of a Gabriel Graph.
+                    Periodic nodes are dashed.
+                 \subref{sfig:lunes:def} Example of a Relative
                     Neighborhood Graph. Periodic nodes are dashed.}
         \label{fig:lunes}
+
     \end{figure}
@@
     one node inside the lune is found. To determine which nodes are
-    near the lune one can save the position of every node in a
-    \emph{cell list} according to \cite{RNGCell} and just test the
-    nodes in the cells which resemble a rectangular bounding box of the
-    lune.
+    near the lune one can subdivide the area in \emph{cells} and save
+    for each cell a list with nodes lying inside it \cite{RNGCell}.
+    Now it is just neccessary to test the nodes in the cells which
+    resemble a rectangular bounding box of the lune. Most pairs will be
+    far away from each other and the cells in the middle of the bounding
+    box are completely inside the lune so that only one node has to be
+    tested to discard an edge between them. Connected nodes are near to
+    each other so that only very few cells have to be tested.\\
+    Indeed this method reduced the time needed to construct a Relative
+    Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
+    over \(15\) respectivly \(40\). But no further analysis was made.
 
@@
         \centering
-        \subfigure{\includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}}
+        \subfigure{
+                \label{sfig:binder_fit_s_0}
+                \includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}
+        }
         \caption[Binder cumulant fitted with polynom of degree 4]

### 2013-06-13 Tex/chapters/model.tex
Subfigure: Unterbilder werden nummeriert und im lof angezeigt

@@
     one node inside the lune is found. To determine which nodes are
-    near the lune one can subdivide the area in \emph{cells} and save
-    for each cell a list with nodes lying inside it \cite{RNGCell}.
-    Now it is just neccessary to test the nodes in the cells which
-    resemble a rectangular bounding box of the lune. Most pairs will be
-    far away from each other and the cells in the middle of the bounding
-    box are completely inside the lune so that only one node has to be
-    tested to discard an edge between them. Connected nodes are near to
-    each other so that only very few cells have to be tested.\\
-    Indeed this method reduced the time needed to construct a Relative
-    Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
-    over \(15\) respectivly \(40\). But no further analysis was made.
+    near the lune one can save the position of every node in a
+    \emph{cell list} according to \cite{RNGCell} and just test the
+    nodes in the cells which resemble a rectangular bounding box of the
+    lune.
 

### 2013-06-13 Tex/chapters/model.tex
fehlende Leerzeichen ergänzt

--- 2013-06-13 Tex/chapters/model.tex
@@
 \label{ssec:isingmodel}
-    The used model is a modified 2D Ising model where the \(N\)sites are
-    displaced nodes of a square lattice of edgelength \(L\) with
+    The used model is a modified 2D Ising model where the \(N\) sites
+    are displaced nodes of a square lattice of edge length \(L\) with
     periodic boundary conditions. The displacement is randomly gauss

### 2013-06-13 Tex/chapters/model.tex
Einleitung zu Graphen geschrieben

@@
 \label{ssec:graphtypes}
+    All here mentioned graph types are \emph{proximity graphs}. They are
+    connecting nodes which are by some metric near to each other.
+    Hence they are suited to generalize problems defined on regular
+    lattices with nearest neighbor relationships, like the Ising model
+    which will be described in more detail in section
+    \ref{ssec:isingmodel}.\\
     The Gabriel Graph \cite{Gabriel1969} is a subgraph of the

### 2013-06-13 Tex/chapters/monte_carlo.tex
weiter im Text
Mehr details zu den Monte Carlo algorithmen

@@
         are also considered and so forth. When there are no more sites
-        to add, the spin of every site in the cluster is flipped.
-        \cite[S. ??]{NewmanBarkema1999} \cite[S. 151f]{Katzgraber2011}
+        to add, the spin of every site in the cluster is flipped
+        \cite[S. ??]{NewmanBarkema1999} \cite[S. 151f]{Katzgraber2011}.
+        This leads fast to new uncorrelated states at the critical
+        temperature because big clusters are flipped. But there are not
+        much advantages at high or low temperatures. At low temperatures
+        the cluster will consist of almost all sites such that all but
+        very few spins will be flipped. At high temperatures the cluster
+        will only contain very few sites.
+        Both situaitions have no advantage against the Metropolis algorithm.
 
@@
         temperatures and periodically swaps the spin configurations
-        between two neighboring temperatures with probability
+        between two neighboring temperatures with probability \(P\) from
+        eq. \ref{eq:partemp} \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
         \begin{equation}
             P((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}}
+            \label{eq:partemp}
         \end{equation}
-        Some good descriptions are in
-        \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+        This has the advantages that correlation times of single
+        temperatures are far smaller because their spin configuration
+        get often replaced by other uncorrelated configurations. And in
+        many cases the more important advantage is that a system which
+        is trapped in a local minimum at a given temperature can travel
+        to higher temperatures leave it's local minimum and cool down
+        again in a lower minimum.
 
@@
         Here a mixture of the above three algorithms is used.
-        Each sweep a Metropolis sweep, a Wolff cluster step and a
-        Parallel Tempering swap are performed.
+        Each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
+        and one Parallel Tempering swap are performed.
 %~ Monte Carlo Simulationen:\\

### 2013-06-14 Tex/chapters/monte_carlo.tex
kleinere Korrekturen an autocorr Section

@@
     equilibrium is called \emph{equilibration time} \(t_{eq}\).
-    All measurement should start after this time.
-    % in meinem fall ... vielleicht bild?
-    \\
+    All measurement should start after this time.\\
+    To determine when the system is in equilibrium, one can watch the
+    development of some observables and take the point at which there
+    are no big changes anymore as equilibrium. In fig.
+    \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
+    the equilibrium is reached after approximately \(N=50\) sweeps for
+    either a initial condition of all spins up and all spins random. It
+    does not harm to double that value to be save.
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Example of an equilibrating Ising system][]{
+                \label{sfig:equiandauto:equiE}
+                \includegraphics[width=0.45\textwidth]{plots/equiE}
+        }
+        \subfigure[Example of the autocorrelation of an Ising system][]{
+                \label{sfig:equiandauto:autoM}
+                \includegraphics[width=0.45\textwidth]{plots/autoM}
+        }
+        \caption[Examples for equilibration and autocorrelation]
+                {\subref{sfig:equiandauto:equiE} Example of a Ising
+                    system reaching equilibrium at \(T=2.36\) and
+                 \subref{sfig:equiandauto:autoM} the
+                    autocorrelation of an Ising system at \(T=2.40\)
+                    (only Metropolis sweeps).
+                }
+        \label{fig:equiandauto}
+    \end{figure}
+
     Because every state is generated from the state before, measurements
     of subsequent states are correlated. To determine when two states
-    are independet, one calculates the autocorrelation function \(\chi(t)\)
-    and integrates it to get the autocorrelation time \(\tau = \int \chi(t) \de t\).
+    are independet, one calculates the normalized autocorrelation function
+    \(\frac{\chi(t)}{\chi(0)}\) like in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
+    and integrates it to get the autocorrelation time \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
     \(\tau\) is an estimate after which time two samples are not

### 2013-06-14 Tex/chapters/introduction.tex
Umformulierung, Fehlerbehebung

@@
-The computing capabilities of modern computers enables researchers to
+The computing capabilities of modern computers enable researchers to
 collect and analyse vast amounts of data.
-Further statistical systems, for which there exist no analytical soultions
+Further statistical systems, for which exist no analytical soultions
 or only for very simplified or special cases, can be simulated.
@@
 For example to examine phasetransitions, which are defined by the abrupt
-change of an observable ie. the change of the magnetisation of a
+change of an observable i.e. the change of the magnetisation of a
 ferromagnet near the Curie temperature or the change of the density of
@@
 In this thesis the critical behavior on some irregular lattices
-resembling proximity graphs (see section \ref{ssec:graphtypes}) will be
-examined using the Monte Carlo simulations described in section
+corresponding to proximity graphs (see section \ref{ssec:graphtypes})
+will be examined using the Monte Carlo simulations described in section
 \ref{sec:montecarlo}.

### 2013-06-14 Tex/chapters/model.tex
Umformulierung, Fehlerbehebung

@@
                     and Relative Neighborhood Graph (blue and red).
-                 \subref{sfig:lunes:gg} Example of a Gabriel Graph.
-                    Periodic nodes are dashed.
+                 \subref{sfig:lunes:gg} Example of a Gabriel Graph on
+                    periodic boundary conditions. Periodic nodes are
+                    dashed.
                  \subref{sfig:lunes:def} Example of a Relative
-                    Neighborhood Graph. Periodic nodes are dashed.}
+                    Neighborhood Graph on periodic boundary conditions.
+                    Periodic nodes are dashed.}
         \label{fig:lunes}
@@
     \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
-    where \(\avg{i,j}\) refers to by edges connected nodes.
+    where \(\avg{i,j}\) refers to nodes connected  by edges.
     The edges are constructed according to the in section
-    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
+    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
     proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
     edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
-    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
-    called \emph{coupling constant}.\\
+    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
+    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
@@
     is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
-    and the magnetisation per site \(m\) and energy of the system \(E\)
+    and the magnetisation per site \(m\) and energy per site \(E\)
     are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
@@
 \label{ssec:finitesize}
-    Because the searched for property -- the critical temperature \(T_c\)
+    The searched for property -- the critical temperature \(T_c\)
     -- is only defined for infinite systems, hence every computer
@@
     Despite of this one can obtain \(T_c\) by finite size scaling
-    methods \cite[S. ??]{Newman1998} which also yield the critical
+    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
     exponents. The critical exponents should not be influenced by the
@@
     %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
-    Though if one is just interested in the critical Temperature an
+    Though if one is just interested in the critical Temperature, an
     easier approach is to find the intersections of the Binder cumulants
@@
     the intersection.
-    In figure \ref{fig:binder_fit_s_0} such a fit is plotted for
+    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
     \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).

### 2013-06-14 Tex/chapters/monte_carlo.tex
Umformulierung, Fehlerbehebung

@@
 The idea behind Monte Carlo simulations is to take random samples of
-the observable which should be measured and estimate the observable from
+the observable, which should be measured, and estimate the observable from
 this samples. In example the Monte Carlo integration chooses random
@@
 as the fraction of points below the function and points above muliplied
-by the area of the bounding box.\\
+by the area of the bounding box.
+Of course one wants to sample more points, where the area below the
+function is big. This can be achieved by \emph{Importance Sampling}. One
+generates random numbers according to some probabilty distribution and
+weights the result accordingly.\\
 %~ To improve this method: \emph{Importance Sampling}
@@
 %~ distributed........
-It is difficult to create random state of the Ising system in
+The same principle is used to sample properties of statistical systems
+by generating random states.
+But it is difficult to create random state of the Ising system in
 equilibrium, hence one uses \emph{Markov Chains} to generate new states
@@
 It is important that the transition probabilities \(A(\mu \to \nu)\)
-obey \emph{Detailed Balance}, that the probability to leave a state is
+obey \emph{Detailed Balance} and \emph{Ergodicity}.
+\emph{Detailed Balance} means  that the probability to leave a state is
 the same as the probability to enter the state in equilibrium
-\(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\)
-with \(p_\mu\) the probability to be in state \(\mu\), and
-\emph{Ergodicity}, that every possible state is reachable from every
-other state in finite time. \cite{NewmanBarkema1999} \cite{Katzgraber2011}\\
-Otherwise the samples might not be representative for the whole system.
+\(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\) with \(p_\mu\) the
+probability to be in state \(\mu\).
+And \emph{Ergodicity} requires that every possible state is reachable
+from every other state in finite time. \cite{NewmanBarkema1999} \cite{Katzgraber2011}
+Otherwise the samples might not be representative for the whole system.\\
 
@@
     \paragraph{Metropolis}
-        Let \(\Delta \hat H(\mu,\nu)\) be the energy difference between
-        the states \(\mu\) and \(\nu\)
+        A Metropolis Monte Carlo simulation of an Ising model will
+        choose a random spin, calculate the energy change
+        \(\Delta \hat H\) defined in eq. \eqref{eq:dH} that would result
+        from a flip of and excute the flip with the probability \(A\)
+        eq. \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
         \begin{equation}
-            \Delta \hat H = \hat H(\nu) - \hat H(\mu)
+            \Delta \hat H = \hat H(\nu) - \hat H(\mu)\\
+            \label{eq:dH}
         \end{equation}
-        The Metropolis algorithm \cite{Metropolis1953} chooses the transition
-        probability like eq. \ref{eq:metropolis}
         \begin{equation}
@@
         \end{equation}
-        A Metropolis Monte Carlo simulation of an Ising model will choose a
-        random spin, calculate the energy change \(\Delta \hat H\) that would
-        result from a flip of and excute the flip with the probability \(A\).
-        \cite{NewmanBarkema1999} \cite{Katzgraber2011}
+        So if a transition lowers the energy it is always done. This
+        results in a good ratio between calculations and transitions.
 
@@
         For an Ising model the Wolff algorithm builds a cluster of sites
-        starting with an random seed and adding neighboring sites with
-        the same spin with probability
+        starting with a random site and adding neighboring sites of the
+        same spin with probability
         \(P_{\mathrm{add}} = 1-\exp\brac{-2\beta J}\)
@@
     \paragraph{Parallel Tempering}
-        The main aim is to obtain the critical temperatures
-        \(T_c\) for different disturbance paramters \(\sigma\).
-        Therefore it is necessary to simulate for many temperatures,
-        so that \emph{Parallel Tempering}\footnote{Before R. H.
-            Swendsen published this paper, a algorithm \(MC^3\) was
-            already published with the same idea. [citation needed]}
-        \cite{ParallelTempering1986} is a suited algorithm. Parallel
-        Tempering simulates many identical systems at different
+        %~ The main aim is to obtain the critical temperatures
+        %~ \(T_c\) for different disturbance paramters \(\sigma\).
+        %~ Therefore it is necessary to simulate for many temperatures,
+        %~ so that \emph{Parallel Tempering}\footnote{Before R. H.
+            %~ Swendsen published this paper, a algorithm \(MC^3\) was
+            %~ already published with the same idea. [citation needed]}
+        %~ \cite{ParallelTempering1986} is a suited algorithm.
+        Parallel Tempering simulates many identical systems at different
         temperatures and periodically swaps the spin configurations
         between two neighboring temperatures with probability \(P\) from
-        eq. \ref{eq:partemp} \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+        eq. \eqref{eq:partemp} \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
         \begin{equation}
@@
         temperatures are far smaller because their spin configuration
-        get often replaced by other uncorrelated configurations. And in
-        many cases the more important advantage is that a system which
-        is trapped in a local minimum at a given temperature can travel
-        to higher temperatures leave it's local minimum and cool down
+        gets often replaced by an other uncorrelated configuration. In
+        many cases the more important advantage is, that a system which
+        is trapped in a local minimum at a given temperature, can travel
+        to higher temperatures, leave it's local minimum and cool down
         again in a lower minimum.
@@
     the equilibrium is reached after approximately \(N=50\) sweeps for
-    either a initial condition of all spins up and all spins random. It
+    either an initial condition of all spins up and all spins random. It
     does not harm to double that value to be save.

### 2013-06-14 Tex/chapters/model.tex
kleine Fehler behoben

@@
     %~ [theorie mit dem Collaps]
+    To accomplish the collapse in an semi-automatic and reproduceable
+    way with an error estimate, the programm
+    \texttt{autoscale.py} \cite{autoscale2009} is used.
+
     %~ [Erklärung autoscale]
@@
     %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Example of a datacollapse to determine critical exponents][]{
+                \label{sfig:collapse_s_0}
+                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
+        }
+        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
+                \label{sfig:binder_fit_s_0}
+                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        }
+        \caption[Examples of determining critical temperature and exponents]
+                {\subref{sfig:collapse_s_0}
+                 \subref{sfig:binder_fit_s_0} Binder cumulant fitted with
+                    polynom of degree 4 in vincinity of \(T_c\)
+                    (the errorbars are too small to see)}
+        \label{fig:binder_fit_s_0}
+    \end{figure}
     Though if one is just interested in the critical Temperature, an
@@
     \(T_c = 2.2691...\) \cite{Onsager1944}.\\
-    \begin{figure}[htbp]
-        \centering
-        \subfigure{
-                \label{sfig:binder_fit_s_0}
-                \includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}
-        }
-        \caption[Binder cumulant fitted with polynom of degree 4]
-                {Binder cumulant fitted with polynom of degree 4
-                (the errorbars are too small to see)}
-        \label{fig:binder_fit_s_0}
-    \end{figure}%[vgl. Grafik (villeicht)]
+
     % The arithmetic average of the intersections are plotted [hier schon?]

### 2013-06-14 auswertung/fitPolyAndFindIntersection.py
binder fit: etwas eleganter und sucht auch den y Schnittpunkt

@@ -20,9 +20,9 @@ logging.basicConfig(level=logging.INFO,
 
 class BinderIntersections():
 
-    def __init__(self, database="data.db", deg=4 ):
+    def __init__(self, directory, database="data.db", deg=4 ):
         self.deg = deg
-
+        self.directory = directory
         self.conn = sqlite3.connect(database)
 
     def getBinderForSigmaAndL(self, sigma, L):
@@ -60,32 +60,33 @@ class BinderIntersections():
         if write:
             self.writeForGnuplot(p1, p2, x1, x2, y1, y2, dy1, dy2, L1, L2, sigma)
 
-        result = self.findIntersection(lambda x : numpy.polyval(p1,x), lambda x : numpy.polyval(p2,x), (self.up + self.down)/2)
-        return result
+        x = self.findIntersection(lambda z : numpy.polyval(p1,z), lambda z : numpy.polyval(p2,z), (self.up + self.down)/2)
+        y = numpy.polyval(p1,x)
+        return x,y
 
     def writeForGnuplot(self, p1, p2, x1, x2, y1, y2, dy1, dy2, L1, L2, sigma):
         X = numpy.arange(self.down, self.up, (self.up - self.down)/500)
-        with open(os.path.join(directory,"tmpFit{0}_s_{1:.3f}.dat".format(L1,sigma)), "w") as f:
+        with open(os.path.join(self.directory,"tmpFit{0}_s_{1:.3f}.dat".format(L1,sigma)), "w") as f:
             for x in X:
                 f.write(" ".join([str(x), str(numpy.polyval(p1,x))]))
                 f.write("\n")
 
-        with open(os.path.join(directory,"tmpFit{0}_s_{1:.3f}.dat".format(L2,sigma)), "w") as f:
+        with open(os.path.join(self.directory,"tmpFit{0}_s_{1:.3f}.dat".format(L2,sigma)), "w") as f:
             for x in X:
                 f.write(" ".join([str(x), str(numpy.polyval(p2,x))]))
                 f.write("\n")
 
-        with open(os.path.join(directory,"tmp{0}_s_{1:.3f}.dat".format(L1,sigma)), "w") as f:
[…]

### 2013-06-17 Tex/chapters/model.tex
Caption ergänzt, Bilder umsortiert, Formulierung geändert

@@
         }
+        \subfigure[Relative Neighborhood graph example][]{
+                \label{sfig:lunes:rng}
+                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
+        }
         \subfigure[Gabriel graph example][]{
@@
         }
-        \subfigure[Relative Neighborhood graph example][]{
-                \label{sfig:lunes:rng}
-                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
-        }
         \caption[Gabriel - and Relative Neighborhood Graph]
-                {\subref{sfig:lunes:def} Lunes of Gabriel Graph (red)
-                    and Relative Neighborhood Graph (blue and red).
+                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
+                    Graph (hatched region) and
+                    Gabriel Graph (cross hatched region)
+                 \subref{sfig:lunes:def} Example of a Relative
+                    Neighborhood Graph on periodic boundary conditions.
+                    Periodic nodes are dashed.
                  \subref{sfig:lunes:gg} Example of a Gabriel Graph on
@@
                     dashed.
-                 \subref{sfig:lunes:def} Example of a Relative
-                    Neighborhood Graph on periodic boundary conditions.
-                    Periodic nodes are dashed.}
+                }
         \label{fig:lunes}
@@
         \centering
+        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
+                \label{sfig:binder_fit_s_0}
+                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        }
         \subfigure[Example of a datacollapse to determine critical exponents][]{
@@
         }
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
-                \label{sfig:binder_fit_s_0}
-                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        \caption[Examples of determining critical temperature and exponents]
+                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
+                    with cubic splines (the errorbars are too small to see)
+                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
                 }
-        \caption[Examples of determining critical temperature and exponents]
-                {\subref{sfig:collapse_s_0}
-                 \subref{sfig:binder_fit_s_0} Binder cumulant fitted with
-                    polynom of degree 4 in vincinity of \(T_c\)
-                    (the errorbars are too small to see)}
         \label{fig:binder_fit_s_0}
@@
     system sizes \(L=\sqrt N\).
-    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
-    the intersection.
-    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
+    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+    for the measured points.
+    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
     \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
-    To determine \(T_c\) the intersections are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
-    is in very good agreement with the exact solution
+    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
+    are averaged and the standard
+    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
+    is in good agreement with the exact solution
     \(T_c = 2.2691...\) \cite{Onsager1944}.\\

### 2013-06-17 Tex/chapters/results.tex
Auswertung umbenannt

\subsection{Critical Temperature}
    The evaluation of the intersections of the Binder cumulants, yields
    the

\subsection{Critical Exponents}
    %~ <J>\(\sigma\), Anmerkung zur Anomalie des GG und der Ähnlichkeit von <J> zu \(T_c\)\\
%~
    %~ Erklärung zu Autokorreltationszeit \(\tau\) und Equilibrierungszeit \(t_eq\)\\
    %~ Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
    %~ Bestimmung der kritischen Punkte\\
        %~ Polyfit 4ten Grades durch Binder Kumulante \cite{Binder1981}\\
        %~ Finite Size Scaling Vergleich der Exponenten (AutoScale \cite{Melchert2009}, Vergleich \cite[S. 59]{Pelissetto2002})\\

    \begin{figure}[htbp]
        \centering
        \subfigure{\includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}}
        \subfigure{\includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}}
        \caption[Critical Temperature over different disturbance parameters]
                {normalized critical temperatures over different disturbance parameters}
        \label{fig:Tc}
    \end{figure}

### 2013-06-18 Tex/chapters/results.tex
kritische Exponenten

@@
 \subsection{Critical Temperature}
-    The evaluation of the intersections of the Binder cumulants, yields
-    the
+    The evaluation of the Binder cumulant's intersections, yields the
+    critical temperatures \(T_c\), which are normalized and plotted in
+    fig. \ref{fig:Tc}.
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:Tc:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:Tc:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
+        }
+        \caption[Critical Temperature over different disturbance parameters]
+                {Normalized critical temperatures over different
+                 disturbance parameters for
+                 \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
+                 \subref{sfig:Tc:GG} the Gabriel Graph.
+                }
+        \label{fig:Tc}
+    \end{figure}
+    % I don't know what all that means...
 
 \subsection{Critical Exponents}
+    For \(\sigma \in \{0,0.1,0.5\}\) a finite size scaling analysis was
+    performed to determine the critical exponents \(\beta, \gamma, \nu\)
+    using \texttt{autoscale.py} \cite{autoscale2009}. The values for
+    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
+    values for all other \(\sigma\) should be the same according to ???
+    [citiation needed]. Like in tab. \ref{tab:critExp} to see, most values
+    are matching the expectations. Most \(\beta\) seem to be a bit too
+    big, but they are close enough to the expectations to be explained
+    by the fact that small systems (\(L=32,64\)) were used for the
+    analysis. [citation needed]
+    \begin{table}[htbp]
+        \center
+        \begin{tabular}{l l l l l}
+            \toprule
+             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
+            \midrule
+            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
+            \midrule
+            Gabriel      & 0.0 & 1.008(4) & -1.735(2) & 0.1262(4)\\
+                         & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
+                         & 0.5 & 1.009(8) & -1.75(1)  & 0.125(13)\\
+            \midrule
+            Relative N.  & 0.0 & 1.007(2) & -1.739(2) & 0.130(1) \\
+                         & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
+                         & 0.5 & 1.00(2)  & -1.75(2)  & 0.143(13)\\
+            \bottomrule
+        \end{tabular}
+        \caption{Critical exponents for different \(\sigma\)}
+        \label{tab:critExp}
+    \end{table}
+
     %~ <J>\(\sigma\), Anmerkung zur Anomalie des GG und der Ähnlichkeit von <J> zu \(T_c\)\\
@@
         %~ Finite Size Scaling Vergleich der Exponenten (AutoScale \cite{Melchert2009}, Vergleich \cite[S. 59]{Pelissetto2002})\\
-
-    \begin{figure}[htbp]
-        \centering
-        \subfigure{\includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}}
-        \subfigure{\includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}}
-        \caption[Critical Temperature over different disturbance parameters]
-                {normalized critical temperatures over different disturbance parameters}
-        \label{fig:Tc}
-    \end{figure}

### 2013-06-18 Tex/chapters/model.tex
todo Notiz

@@
     %~ [theorie mit dem Collaps]
+    %~ [Erklaerung: was sind beta, gamma, nu]
     To accomplish the collapse in an semi-automatic and reproduceable
@@
     \texttt{autoscale.py} \cite{autoscale2009} is used.
-
     %~ [Erklärung autoscale]
@@
         \label{fig:binder_fit_s_0}
-    \end{figure}
+    \end{figure}\\
     Though if one is just interested in the critical Temperature, an
@@
     In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
-    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
+    \(\sigma=0\). The cumulants intersect at \(\approx 2.27 k_{B}\). For
+    the sake of simplicity let the Boltzmann constant \(k_{B}=1\) in the
+    following.
     To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
     are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
-    is in good agreement with the exact solution
+    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\),
+    which is in good agreement with the exact solution
     \(T_c = 2.2691...\) \cite{Onsager1944}.\\
+    Because \(T_{c}\) is dependend on \(J\) and hence also on the count
+    of bounds, the values of \(T_{c}\) will be normalized by the mean
+    sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
 

### 2013-06-19 Tex/chapters/model.tex
Bessere Formulierungen und Korrekturen.

@@
                     Gabriel Graph (cross hatched region)
-                 \subref{sfig:lunes:def} Example of a Relative
+                 \subref{sfig:lunes:rng} Example of a Relative
                     Neighborhood Graph on periodic boundary conditions.
@@
 
-\subsection{Model}
+\subsection{The Disturbed Ising Model}
 \label{ssec:isingmodel}
-    The used model is a modified 2D Ising model where the \(N\) sites
+    The used model is a modified 2D Ising model where the \(N=L^2\) sites
     are displaced nodes of a square lattice of edge length \(L\) with
@@
         \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
-                \label{sfig:binder_fit_s_0}
+                \label{sfig:gettingCrit:binder_fit_s_0}
                 \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
@@
         \subfigure[Example of a datacollapse to determine critical exponents][]{
-                \label{sfig:collapse_s_0}
+                \label{sfig:gettingCrit:collapse_s_0}
                 \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
@@
         \caption[Examples of determining critical temperature and exponents]
-                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
-                    with cubic splines (the errorbars are too small to see)
-                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
+                {The Binder cumulant \(g\) of an square lattice Ising model
+                 (\(\sigma=0\))\\
+                 \subref{sfig:gettingCrit:binder_fit_s_0} interpolated
+                    with cubic splines (the errorbars are too small to see)\\
+                 \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
+                    size scaling
                 }
-        \label{fig:binder_fit_s_0}
+        \label{fig:gettingCrit}
     \end{figure}\\
@@
     easier approach is to find the intersections of the Binder cumulants
-    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
-    system sizes \(L=\sqrt N\).
+    \(g\) of different system sizes \(L\).
     Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
     for the measured points.
-    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
-    \(\sigma=0\). The cumulants intersect at \(\approx 2.27 k_{B}\). For
-    the sake of simplicity let the Boltzmann constant \(k_{B}=1\) in the
-    following.
+    In fig. \ref{fig:gettingCrit}\subref{fig:gettingCrit:binder_fit_s_0}
+    such an interpolation is plotted for \(\sigma=0\). The cumulants
+    intersect at \(\approx 2.27 k_{B}\). For the sake of simplicity let
+    the Boltzmann constant \(k_{B}=1\) in the following.
     To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
-    are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\),
-    which is in good agreement with the exact solution
-    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
-    Because \(T_{c}\) is dependend on \(J\) and hence also on the count
-    of bounds, the values of \(T_{c}\) will be normalized by the mean
-    sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
+    are averaged and the standard error is calculated. In this case one
+    gets \(T_c = 2.2689\pm0.0002\), which is in good agreement with the
+    exact solution
+    \begin{equation}
+        T_c = 2J/\ln(1+\sqrt 2) = 2.2691... \cite{Onsager1944}
+        \label{eq:exactTc}
+    \end{equation}
 

### 2013-06-19 Tex/chapters/results.tex
Bessere Formulierungen und Korrekturen.

@@
     The evaluation of the Binder cumulant's intersections, yields the
-    critical temperatures \(T_c\), which are normalized and plotted in
-    fig. \ref{fig:Tc}.
+    critical temperatures \(T_c\), which are plotted in
+    fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.
+    Further in fig. \ref{fig:Tc}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
+    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+    is plotted which is evidently correlated with \(T_c\).
+    That is plausible, because \(T_c\) is dependend on the coupling
+    constant \(J\) (compare \eqref{eq:exactTc}).\\
+    It seems reasonable to normalize the values of \(T_{c}\) by
+    \(\avg{\sum_{\avg{i,j}} J_{ij}}\) which yields the diagramms fig.
+    \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.
+
     \begin{figure}[htbp]
@@
             \label{sfig:Tc:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:Tc:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
+        }
+
+        \subfigure[][]
+        {
+            \label{sfig:sumJ:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:sumJ:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
+        }
+
+        \subfigure[][]
+        {
+            \label{sfig:Tc_norm:RNG}
             \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
@@
         {
-            \label{sfig:Tc:GG}
+            \label{sfig:Tc_norm:GG}
             \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
@@
         \caption[Critical Temperature over different disturbance parameters]
-                {Normalized critical temperatures over different
+                {Top: Critical temperatures over different
                  disturbance parameters for
                  \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
-                 \subref{sfig:Tc:GG} the Gabriel Graph.
+                 \subref{sfig:Tc:GG} the Gabriel Graph.\\
+                 Middle: Degree over different disturbance parameters for
+                 \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
+                 \subref{sfig:deg:GG} the Gabriel Graph.\\
+                 Bottom: Normalized critical temperatures over different
+                 disturbance parameters for
+                 \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
+                 \subref{sfig:Tc_norm:GG} the Gabriel Graph.
                 }

### 2013-06-19 Tex/chapters/model.tex
Finite Size Scaling

@@
     exact values \cite[S. 59]{Pelissetto2002}.\\
+    It is known, that for large \(L\) near the critical temperature the
+    equations \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
+    \eqref{eq:fsscaling:g} apply \cite[p. 145f]{Katzgraber2011}.
+    \begin{align}
+        \label{eq:fsscaling:m}
+        \avg{m_L} &= L^\frac{\beta}{\nu} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:fsscaling:chi}
+        \chi_L    &= L^\frac{\gamma}{\nu} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:fsscaling:g}
+        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
+    \end{align}
+    Where \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} is
+    the Binder cumulant and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
+    are unkown scaling functions. To find the exponents
+    \(\beta, \gamma, \nu\) and the critical temperature \(T_c\), one
+    varies them until the measured values of the observables collapse on
+    one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
+    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
+    Note that \(L=16\) is not used for the collapse, because it is a
+    rather small value such that eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
+    do not apply very good.\\
     %~ [theorie mit dem Collaps]

### 2013-06-19 Tex/chapters/monte_carlo.tex
kleine Fehler behoben
Bessere Formulierungen und Korrekturen.
Autokorrelation etwas verbessert

@@
 \label{sec:montecarlo}
-Monte Carlo simulations are (probalby) named after the casino in Monaco
+Monte Carlo simulations are (probably) named after the casino in Monaco
 \cite{NewmanBarkema1999} because both rely on randomness.\\
@@
         Each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
-        and one Parallel Tempering swap are performed.
+        and one Parallel Tempering swap are performed. Where \(N\) is the
+        count of sites.
 %~ Monte Carlo Simulationen:\\
@@
 \subsection{Equilibration- and Autocorrelation Time}
+\label{ssec:eqtime}
     To generate an equilibrium state one starts with an arbitrary state
@@
                 \label{sfig:equiandauto:equiE}
-                \includegraphics[width=0.45\textwidth]{plots/equiE}
+                \includegraphics[width=0.47\textwidth]{plots/equiE}
         }
@@
                 \label{sfig:equiandauto:autoM}
-                \includegraphics[width=0.45\textwidth]{plots/autoM}
+                \includegraphics[width=0.47\textwidth]{plots/autoM}
         }
@@
     are independet, one calculates the normalized autocorrelation function
-    \(\frac{\chi(t)}{\chi(0)}\) like in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
-    and integrates it to get the autocorrelation time \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
+    \(\frac{\chi(t)}{\chi(0)}\), which should decay exponentially
+    \(\chi(t) \propto \exp(t/\tau)\). This is visible in the half
+    logarithmic plot \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
+    To get the autocorrelation time one can integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
     \(\tau\) is an estimate after which time two samples are not

### 2013-06-19 Tex/chapters/results.tex
Bildcaption korrigiert

@@
     \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.
-
     \begin{figure}[htbp]
@@
                  \subref{sfig:Tc:GG} the Gabriel Graph.\\
-                 Middle: Degree over different disturbance parameters for
-                 \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
-                 \subref{sfig:deg:GG} the Gabriel Graph.\\
+                 Middle: Mean sum of the coupling constants to all
+                 neighbors over different disturbance parameters for
+                 \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
+                 \subref{sfig:sumJ:GG} the Gabriel Graph.\\
                  Bottom: Normalized critical temperatures over different

### 2013-06-19 Tex/chapters/results.tex
Absatz zum Sprung der Tc des GG

@@
         \label{fig:Tc}
-    \end{figure}
+    \end{figure}\\
     % I don't know what all that means...
-
+    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
+    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
+    by the definition of the Gabriel graph and it's aftereffects for
+    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
+    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI}}.
+    To fully understand this, take four nodes forming a square. The edge
+    across does not exist, because the other two nodes are on the edge
+    of the lune. Move one node slightly into the square, causes the lune
+    to get smaller, hence no other nodes are inside or on the edge of
+    the lune anymore and the edge arises.
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:GG_sigma:zero}
+            \includegraphics[width=0.45\textwidth]{images/GG/sigma_e0}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:GG_sigma:notzero}
+            \includegraphics[width=0.45\textwidth]{images/GG/sigma_g0}
+        }
+        \caption[]
+        {
+            Gabriel graph with periodic boundary conditions
+            for \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
+            \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
+        }
+        \label{fig:GG_sigma}
+    \end{figure}\\
 \subsection{Critical Exponents}

### 2013-06-19 Tex/chapters/model.tex
Autokorrelation etwas verbessert
kosmetischer eingriff
Einrückung im Quellcode verbessert

@@
         \caption[Gabriel - and Relative Neighborhood Graph]
-                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
+        {
+            \subref{sfig:lunes:def} Lunes of Relative Neighborhood
                 Graph (hatched region) and
@@
     are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
-    denotes the \emph{autocorrelation time} after which two states of
-    the system are not correlated anymore.
+    denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
     For every observable \(O\) the expected value \(\avg{O}\) is averaged
@@
         \caption[Examples of determining critical temperature and exponents]
-                {The Binder cumulant \(g\) of an square lattice Ising model
+        {
+            The Binder cumulant \(g\) of an square lattice Ising model
             (\(\sigma=0\))\\
@@
     gets \(T_c = 2.2689\pm0.0002\), which is in good agreement with the
-    exact solution
+    exact solution \cite{Onsager1944}
     \begin{equation}
-        T_c = 2J/\ln(1+\sqrt 2) = 2.2691... \cite{Onsager1944}
+        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
         \label{eq:exactTc}

### 2013-06-19 Tex/chapters/results.tex
Einrückung im Quellcode verbessert
Angefangen den Tc_norm Verlauf zu beschreiben

--- 2013-06-19 Tex/chapters/results.tex
@@
         \caption[Critical Temperature over different disturbance parameters]
-                {Top: Critical temperatures over different
+        {
+            Top: Critical temperatures over different
             disturbance parameters for
@@
         \label{fig:Tc}
-    \end{figure}
+    \end{figure}\\
     % I don't know what all that means...
+    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
+    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
+    by the definition of the Gabriel graph and it's aftereffects for
+    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
+    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
+    To fully understand this, take four nodes forming a square. The edge
+    across does not exist, because the other two nodes are on the edge
+    of the lune. Moving one node slightly into the square, causes the lune
+    to get smaller, hence no other nodes are inside or on the edge of
+    the lune anymore and the edge appears.
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:GG_sigma:zero}
+            \includegraphics[width=0.45\textwidth]{images/GG/sigma_e0}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:GG_sigma:notzero}
+            \includegraphics[width=0.45\textwidth]{images/GG/sigma_g0}
+        }
+        \caption[]
+        {
+            Gabriel graph with periodic boundary conditions for
+                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
+                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
+        }
+        \label{fig:GG_sigma}
+    \end{figure}\\
+    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
+    show monotonically decreasing \(T_c\) with increasing disturbance
+    parameter \(\sigma\). The froms of both curves are similar, but the
+    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
+    is generally lower and spans over a bigger temperature range than
+    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
+    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
+    % RNG: laengere Kanten -> weniger lokale effekte?
 

### 2013-06-19 Tex/chapters/results.tex
disturbance parameter in disorder parameter umbenannt

@@
         }
-        \caption[Critical Temperature over different disturbance parameters]
+        \caption[Critical Temperature over different disorder parameters]
         {
             Top: Critical temperatures over different
-            disturbance parameters for
+            disorder parameters for
             \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
@@
             Middle: Mean sum of the coupling constants to all
-            neighbors over different disturbance parameters for
+            neighbors over different disorder parameters for
             \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
@@
             Bottom: Normalized critical temperatures over different
-            disturbance parameters for
+            disorder parameters for
             \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
@@
     Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
-    show monotonically decreasing \(T_c\) with increasing disturbance
+    show monotonically decreasing \(T_c\) with increasing disorder
     parameter \(\sigma\). The froms of both curves are similar, but the

### 2013-06-19 Tex/chapters/monte_carlo.tex
disturbance parameter in disorder parameter umbenannt
an autocorr formulierung gefeilt

@@
         %~ The main aim is to obtain the critical temperatures
-        %~ \(T_c\) for different disturbance paramters \(\sigma\).
+        %~ \(T_c\) for different disorder paramters \(\sigma\).
         %~ Therefore it is necessary to simulate for many temperatures,
@@
         \caption[Examples for equilibration and autocorrelation]
-                {\subref{sfig:equiandauto:equiE} Example of a Ising
-                    system reaching equilibrium at \(T=2.36\) and
-                 \subref{sfig:equiandauto:autoM} the
-                    autocorrelation of an Ising system at \(T=2.40\)
-                    (only Metropolis sweeps).
+        {
+            \subref{sfig:equiandauto:equiE} Example of a Ising system
+                \(L=64\) reaching equilibrium at \(T=2.36\) and
+            \subref{sfig:equiandauto:autoM} the autocorrelation of an
+                Ising system \(L=64\) at \(T=2.40\) (only Metropolis
+                sweeps) on half logarithmic axis.
+                The straight line is a exponential fit \(\exp(-t/\tau)\)
+                with \(\tau = 342(1)\).
         }
         \label{fig:equiandauto}
-    \end{figure}
-
+    \end{figure}\\
     Because every state is generated from the state before, measurements
@@
     logarithmic plot \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
-    To get the autocorrelation time one can integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
+    To get the autocorrelation time one can either fit a exponential
+    function \(\exp(-t/\tau)\) like in fig \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
+    or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
     \(\tau\) is an estimate after which time two samples are not

### 2013-06-19 Tex/chapters/model.tex
disturbance parameter in disorder parameter umbenannt
Fehlerkorrekturen und Formulierungsverbesserungen

@@
         \label{fig:lunes}
-
-    \end{figure}
-
-    To construct these graphs the simple way is to test for every
-    pair of nodes for every node if it lies in the lune of the pair.
-    That is of complexity \(O (n^3)\).\\
+    \end{figure}\\
+    To construct these graphs the simple way is to test for each
+    pair of nodes one has to check for every other node if it lies in
+    the lune of the pair. That is of complexity \(O (N^3)\), because
+    there are \(N(N-1)\) pairs and for each \(N-2\) nodes to test. So
+    the product is of order \(O(N^3)\)\\
     To reduce the complexity one can first create a Delaunay
-    Triangulation in complexity \(O (n \log n)\)
+    Triangulation in complexity \(O (N \log N)\)
     \cite{Leach1992} and test the criterion for each edge, because
@@
     Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
-    over \(15\) respectivly \(40\). But no further analysis was made.
+    over \(15\) respectivly \(40\). Though the complexity is still of
+    order \(O(N^2)\) in the best case, because for every pair at least
+    one check has to be performed.
 
-\subsection{The Disturbed Ising Model}
+\subsection{The Disorderd Ising Model}
 \label{ssec:isingmodel}
@@
     distributed with the standard deviation \(\sigma\). This \(\sigma\)
-    is also called \emph{disturbance paramter} in the following.
+    is also called \emph{disorder paramter} in the following.
     The hamiltonian of the Ising model is
@@
     denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
-    For every observable \(O\) the expected value \(\avg{O}\) is averaged
-    over different randomly generated lattices \(\overline{\avg{O}}\). The
-    errors are estimated by bootstrapping.
+    For every observable \(O\) the expected value \(\avg{O}\) is determined
+    as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
+    \(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
+    random proximity graphs with the same disorder paramter \(\sigma\)
+    are then averaged to \(\overline{\avg{O}}\). The errors are estimated
+    by bootstrapping.
 
@@
     exponents. The critical exponents should not be influenced by the
-    disturbance paramter \(\sigma\) [citation needed]. So they will be
+    disorder paramter \(\sigma\) [citation needed]. So they will be
     used for consistency cross checking and comparision with the known
@@
     \(g\) of different system sizes \(L\).
-    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
-    for the measured points.
-    In fig. \ref{fig:gettingCrit}\subref{fig:gettingCrit:binder_fit_s_0}
+    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+    is calculated for the measured points.
+    In fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
     such an interpolation is plotted for \(\sigma=0\). The cumulants
@@
     gets \(T_c = 2.2689\pm0.0002\), which is in good agreement with the
-    exact solution \cite{Onsager1944}
+    exact solution from eq. \eqref{eq:exactTc} \cite{Onsager1944}.
     \begin{equation}

### 2013-06-21 graph.c
Percolationsübergang hinzugefügt
Mit der Option -r werden solange zufällige Kanten aus dem Graphen
gelöscht, bis der Graph in zwei unzusammenhängende Graphen zerfällt.
Die letzte gelöschte Kante wird dann wieder eingefügt.

@@ -104,6 +104,7 @@ gs_graph_t *gs_deep_copy_graph(gs_graph_t *g)
 */
 void gs_insert_edge(gs_graph_t *g, int from, int to, double weight)
 {
+    printf("add: %d to %d\n",from, to);
     /* durchsuche den Graphen, ob die Kante schon existiert */
     if(gs_edge_exists(g, from, to))
         return;          /*Kante existiert, Also ist der graph fertig */
@@ -140,6 +141,39 @@ int gs_edge_exists(gs_graph_t *g, int from, int to)
             return(1);
     }
     return(0);
+}
+
+/*! \fn void gs_remove_edge(gs_graph_t *g)
+    \brief Löscht eine Kante im Graphen g.
+
+    \param [in,out] g    Graph, der gelöscht werden soll
+    \param [in]     from Nummer des Knoten #1
+    \param [in]     to   Nummer des Knoten #2
+*/
+void gs_remove_edge(gs_graph_t *g, int from, int to)
+{
+    int n;
+    /* durchsuche den Graphen, ob die Kante existiert */
+    if(!gs_edge_exists(g, from, to))
+        return;    /*Kante existiert nicht, Also ist der graph fertig */
+
+    g->node[from].num_neighbors--;
+    for(n=0;n<g->node[from].num_neighbors;n++)
+        if(g->node[from].neighbors[n].index == to)
+        {
+            g->node[from].neighbors[n].index = g->node[from].neighbors[g->node[from].num_neighbors].index;
+            g->node[from].neighbors[n].weight = g->node[from].neighbors[g->node[from].num_neighbors].weight;
+        }
+    g->node[from].neighbors = (gs_edge_t *) realloc (g->node[from].neighbors, g->node[from].num_neighbors * sizeof(gs_edge_t));
+
+    g->node[to].num_neighbors--;
+    for(n=0;n<g->node[to].num_neighbors;n++)
+        if(g->node[to].neighbors[n].index == from)
+        {
+            g->node[to].neighbors[n].index = g->node[to].neighbors[g->node[to].num_neighbors].index;
+            g->node[to].neighbors[n].weight = g->node[to].neighbors[g->node[to].num_neighbors].weight;
+        }
+    g->node[to].neighbors = (gs_edge_t *) realloc (g->node[to].neighbors, g->node[to].num_neighbors * sizeof(gs_edge_t));
 }
 
 /*! \fn void gs_clear_graph(gs_graph_t *g)

### 2013-06-21 graph.h

@@ -55,6 +55,7 @@ void print_graph_svg(gs_graph_t *g, char* svg_filename);
 void gs_clear_graph(gs_graph_t *g);
 void gs_clear_shallow_graph(gs_graph_t *g);
 int gs_edge_exists(gs_graph_t *g, int from, int to);
+void gs_remove_edge(gs_graph_t *g, int from, int to);
 
 int point_not_in_domain(double x, double  y, int L);
 

### 2013-06-21 spin.c

@@ -88,6 +88,8 @@ options_t get_cl_args(int argc, char *argv[])
     o.start_order = 0;
     /* Seed für Zufallsgenerator */
     o.seed = 42;
+    /* soll ein Percolationsübergang erzeugt werden? */
+    o.percolation = 0;
     /* Soll Wolff Algorithmus benutzt werden? */
     wolff_flag = 0;
     /* Soll Parallel Tempering Algorithmus benutzt werden? */
@@ -101,7 +103,7 @@ options_t get_cl_args(int argc, char *argv[])
     o.svg_filename[0]='\0';
 
     opterr = 0;
-    while ((c = getopt (argc, argv, "hvT:L:x:N:e:s:a:o:g:u:i:wpt:z")) != -1)
+    while ((c = getopt (argc, argv, "hvT:L:x:N:e:s:a:o:g:u:i:wpt:zr")) != -1)
         switch (c)
         {
             case 'T':
@@ -169,6 +171,9 @@ options_t get_cl_args(int argc, char *argv[])
             case 'z':
                 o.zip = 1;
                 break;
+            case 'r':
+                o.percolation = 1;
+                break;
             case 'w':
                 wolff_flag = 1;
                 break;
@@ -196,6 +201,7 @@ options_t get_cl_args(int argc, char *argv[])
                 fprintf(stdout,"    -ux    Ordnung x (0: zufällig, 1: alle up)  (int)\n");
                 fprintf(stdout,"    -w     Wolff Algorithmus (statt Metropolis)      \n");
                 fprintf(stdout,"    -p     Parallel Tempering                        \n");
+                fprintf(stdout,"    -r     Percolations Übergang                     \n");
                 fprintf(stdout,"    -z     gzip outputfile                           \n");
                 exit(1);
             default:
@@ -278,6 +284,12 @@ options_t get_cl_args(int argc, char *argv[])
         else
             printf("    Parallel Tempering deaktiviert\n");
 
+        if(o.percolation)
+            printf("    Percolation aktiviert\n");
+
+        if(o.svg_filename[0] != '\0')
+            printf("    Graph SVG: '%s'\n", o.svg_filename);
+
         printf("    Filename: '%s'\n",o.filename);
         printf("    \n");
     }
@@ -310,6 +322,13 @@ gs_graph_t **init_graphs(const options_t o)
     /* Verknüpfe die Knoten */
     //create_edges_regular(g);
[…]

### 2013-06-21 spin.h

@@ -32,6 +32,7 @@
 #include "graph.h"
 #include "stack.h"
 #include "list.h"
+#include "tree.h"
 
 /*! \def MIN(X,Y)
  * Minimum von zwei Zahlen
@@ -68,6 +69,7 @@ typedef struct
     int graph_type;                               //!< Welcher Graph Typ
     int verbose;                                 //!< Gesprächiger Modus
     int zip;                                        //!< gzip Outputfile
+    int percolation;    //!< Soll Percolationsübergang untersucht werden
     char filename[MAX_LEN_FILENAME];               //!< Output Dateiname
     char svg_filename[MAX_LEN_FILENAME];     //!< Graph Output Dateiname
     gsl_rng *rng;                           //!< Random Number Generator
@@ -86,6 +88,9 @@ inline void get_cell_border_relative_neighborhood(gs_node_t node1, gs_node_t nod
 inline int check_gabriel(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);
 inline void get_cell_border_gabriel(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
 void create_edges(gs_graph_t *g, options_t o);
+void delete_random_edges_till_percolation(gs_graph_t *g, gsl_rng *rng);
+int test_connectivity_between_nodes(gs_graph_t *g, int node1, int node2);
+node_t * gs_depth_first_search(gs_graph_t *g, int node, int target, node_t *tree_of_tested_nodes, int *status);
 double get_mean_weight(gs_graph_t *g);
 double get_mean_deg(gs_graph_t *g);
 double get_sum_weight(gs_graph_t *g);

### 2013-06-21 tree.c

@@ -1,0 +1,251 @@
+#include "tree.h"
+
+/*! \fn node_t *remove_node(node_t *tree, int key_rem, node_t **node_p)
+    \brief entfernt einen Knoten ohne die Ordnung zu stören
+
+    \param [in]  tree    erstes Element des Baums
+    \param [in]  key_rem Key, der entfernt werden soll
+    \param [out] node_p  Adresse des zu entfernenden Knotens (NULL, wenn nicht gefunden)
+    \return (new) pointer zur Wurzel
+*/
+node_t *tr_remove_node(node_t *tree, int key_rem, node_t **node_p)
+{
+    int n_childs;
+    node_t *node_rem, *child1 = NULL, *parent, *cur;
+
+    /* Finde Knoten, der entfernt werden soll */
+    node_rem = tr_find_node(tree, key_rem);
+
+    /* Knoten existiert nicht */
+    if(node_rem == NULL)
+    {
+        fprintf(stderr, "Knoten existiert nicht.\n");
+        *node_p = NULL;
+        return(tree);
+    }
+
+    /* Ermittele die Anzahl der Kinder */
+    if(node_rem->left == NULL && node_rem->right == NULL)
+        n_childs = 0;
+    else if(node_rem->left == NULL || node_rem->right == NULL)
+        n_childs = 1;
+    else
+        n_childs = 2;
+
+    /* Finde den Eltern Knoten, damit er die Kinder des gelöschten "adoptiert" */
+    parent = tr_find_parent(tree, node_rem);
+
+    switch(n_childs)
+    {
+        case 2:
+            /* Knoten hat zwei Kinder */
+            /* Wir müssen den Baum etwas drehen. Dazu suche im rechten Unterbaum
+                des Knotens nach dem kleinsten (linkesten) Element, und tausche
+                die Keys mit dem Knoten, fahre beim linkesten fort mit case 1,
+                da dieser nur noch max ein rechtes child haben kann */
+            cur = node_rem->right;
+            while(cur->left != NULL)
+                cur = cur->left;               /* cur wird hier zum linkesten
+                                                         des rechten Teilbaums*/
+            /* Jetzt wird dem zu löschenden Knoten der Key vom linkesten
+                Knoten zugewiesen und der linkeste (cur) gelöscht. Dazu
+                müssen wir vorher noch den Elternknoten von cur finden */
+            parent = tr_find_parent(tree, cur);
+
+            node_rem->key = cur->key;
+
[…]

### 2013-06-21 tree.h

@@ -1,0 +1,26 @@
+#ifndef _TREE_H
+#define _TREE_H
+
+#include <stdio.h>
+#include <stdlib.h>
+
+/* Datenstruktur für einen Konten in einem binären Suchbaum */
+struct node_struct
+{
+    int                   key;    /*Der Inhalt*/
+    struct node_struct  *left;    /*Pointer zum linken  Nachfolger */
+    struct node_struct *right;    /*Pointer zum rechten Nachfolger */
+};
+
+typedef struct node_struct node_t;
+
+void print_tree(node_t *tree);
+node_t *tr_insert_node(node_t *root, node_t *node, int *in_p);
+int tr_delete_node(node_t *node);
+node_t *tr_create_node(int key);
+void clear_tree(node_t *tree);
+node_t *tr_find_node(node_t *tree, int key);
+node_t *tr_remove_node(node_t *tree, int key_rem, node_t **node_p);
+node_t *tr_find_parent(node_t *tree, node_t *node);
+
+#endif /* _TREE_H */

### 2013-06-24 Tex/chapters/model.tex
Kontinuität bei den Fehlerwertangaben
Anmerkung zu k_B = 1 nach vorner verschoben

@@
 
-\subsection{The Disorderd Ising Model}
+\subsection{The Disordered Ising Model}
 \label{ssec:isingmodel}
@@
 \label{ssec:finitesize}
-    The searched for property -- the critical temperature \(T_c\)
-    -- is only defined for infinite systems, hence every computer
-    simulation will show some \emph{finte size effects}.
-    %[vielleicht Bild von intensiver Größe?]
+    The aim of this thesis is to find the critical  temperature \(T_c\)
+    of the disordered Ising model in dependece of the disorder parameter
+    \(\sigma\). At \(T_c\) the magnetisation \(|m|\) of the system will
+    jump and the susceptibility \(\chi_m = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
+    will diverge. But this behaivior is only present in infinite systems,
+    hence every computer simulation will show some \emph{finte size effects}.
+    Because of this all through computer simulations observed phase
+    transitions will be "smeared out".
+    [todo: Bezug zum Bild]
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[todo][]
+        {
+            \label{sfig:smeared_out:meanM}
+            \includegraphics[width=0.45\textwidth]{plots/meanM}
+        }
+        \subfigure[todo][]
+        {
+            \label{sfig:smeared_out:meanM_L}
+            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
+        }
+        \caption[]
+        {
+            todo
+        }
+        \label{fig:smeared_out}
+    \end{figure}\\
     Despite of this one can obtain \(T_c\) by finite size scaling
@@
     such an interpolation is plotted for \(\sigma=0\). The cumulants
-    intersect at \(\approx 2.27 k_{B}\). For the sake of simplicity let
-    the Boltzmann constant \(k_{B}=1\) in the following.
+    intersect at \(\approx 2.27\).
     To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
     are averaged and the standard error is calculated. In this case one
-    gets \(T_c = 2.2689\pm0.0002\), which is in good agreement with the
+    gets \(T_c = 2.2689(2)\), which is in good agreement with the
     exact solution from eq. \eqref{eq:exactTc} \cite{Onsager1944}.

### 2013-06-24 graph.c
unnötige Ausgabe der Simulation gelöscht und Dateinamen angepasst

@@ -104,7 +104,6 @@ gs_graph_t *gs_deep_copy_graph(gs_graph_t *g)
 */
 void gs_insert_edge(gs_graph_t *g, int from, int to, double weight)
 {
-    printf("add: %d to %d\n",from, to);
     /* durchsuche den Graphen, ob die Kante schon existiert */
     if(gs_edge_exists(g, from, to))
         return;          /*Kante existiert, Also ist der graph fertig */

### 2013-06-24 spin.c

@@ -216,7 +216,7 @@ options_t get_cl_args(int argc, char *argv[])
     if(!custom_file_name)
     {
         /* standard Dateiname */
-        snprintf(o.filename, MAX_LEN_FILENAME, "data/data_s_%.3f_x_%03d_L_%03d_type_%d.dat", o.sigma, o.seed, o.L, o.graph_type);
+        snprintf(o.filename, MAX_LEN_FILENAME, "data/data_s_%.3f_x_%03d_L_%03d_type_%d_r%d.dat", o.sigma, o.seed, o.L, o.graph_type, o.percolation);
     }
 
     /* Welchen Algorithmus nutzen? */
@@ -324,11 +324,7 @@ gs_graph_t **init_graphs(const options_t o)
     create_edges(g, o);
 
     if(o.percolation)
-    {
-        init_spins_up(g);
         delete_random_edges_till_percolation(g, o.rng);
-        print_graph_svg(g, "test.svg");
-    }
 
     for(nT=0;nT<o.num_temps;nT++)
     {
@@ -411,7 +407,7 @@ void do_mc_simulation(gs_graph_t **list_of_graphs, const options_t o)
         exit(-1);
     }
     /* Schreibe Header */
-    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # <J>=%.6f # deg=%.6f # sumJ=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, get_mean_weight(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]), get_sum_weight(list_of_graphs[0]));
+    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # r=%d # <J>=%.6f # deg=%.6f # sumJ=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, o.percolation, get_mean_weight(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]), get_sum_weight(list_of_graphs[0]));
     for(nT=0;nT<o.num_temps;nT++)
         fprintf(data_out_file, "%.3f, ", list_of_graphs[nT]->T);
     fprintf(data_out_file, "\n");

### 2013-06-24 Tex/chapters/model.tex
Erläuterung zu finite size effects

@@
     The aim of this thesis is to find the critical temperature \(T_c\)
-    of the disordered Ising model in dependece of the disorder parameter
-    \(\sigma\). At \(T_c\) the magnetisation \(|m|\) of the system will
-    jump and the susceptibility \(\chi_m = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. But this behaivior is only present in infinite systems,
-    hence every computer simulation will show some \emph{finte size effects}.
-    Because of this all through computer simulations observed phase
-    transitions will be "smeared out".
-    [todo: Bezug zum Bild]
+    of the disordered Ising model in dependence of the disorder parameter
+    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of
+    the system will jump and the susceptibility
+    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
+    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}
+    it is easy to see that the jump occurs at lower temperatures \(T\) for higher
+    disorder parameters \(\sigma\) (here with a Relative Neighborhood graph).
     \begin{figure}[htbp]
         \centering
-        \subfigure[todo][]
+        \subfigure[Dependence of the phase transition on $\sigma$][]
+        {
+            \label{sfig:smeared_out:meanM_L}
+            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
+        }
+        \subfigure[Example for finite size effects][]
         {
@@
         }
-        \subfigure[todo][]
+        \caption[Phase Transition and Finite Size Effects]
         {
-            \label{sfig:smeared_out:meanM_L}
-            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
-        }
-        \caption[]
-        {
-            todo
+            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
+            parameter $\sigma$ on the phase transition
+            for an underlying Relative Neighborhood graph with $L=128$.\\
+            \subref{sfig:smeared_out:meanM}: Effects of different system
+            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
         }
@@
     \end{figure}\\
+    But it is also visible, that there occurs no real jump, but a continuous
+    decline. The jump is only present in infinite systems, hence every
+    computer simulation will show some \emph{finte size effects}.
+    These finite size effects cause a "smearing out" of the phase
+    trasition. This is stronger for smaller system sizes, as showed in
+    fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}.\\
     Despite of this one can obtain \(T_c\) by finite size scaling

### 2013-06-24 graph_modify.c
Funktionen für Graphen in eigene Datei ausgelagert

@@ -1,0 +1,564 @@
+#include "graph_modify.h"
+
+/*! \fn gs_graph_t **init_graphs(options_t o)
+    \brief Diese Funktion initialisiert die Graphen mit allen nötigen
+            Informationen
+
+    \param [in] o               struct mit allen wichtigen Informationen
+    \return Array mit den initialisierten Graphen
+*/
+gs_graph_t **init_graphs(const options_t o)
+{
+    gs_graph_t *g;
+    gs_graph_t **list_of_graphs;
+
+    int nT;
+
+    list_of_graphs = (gs_graph_t**) malloc(o.num_temps * sizeof(gs_graph_t*));
+
+    /* Initialisiere den Graphen für die Spins */
+    g = gs_create_graph(o.L);
+
+    /* Verschiebe die Knoten */
+    move_graph_nodes(g, o.moving_fkt, o.rng, o.sigma);
+
+    /* Verknüpfe die Knoten */
+    create_edges(g, o);
+
+    if(o.percolation)
+        delete_random_edges_till_percolation(g, o.rng);
+
+    for(nT=0;nT<o.num_temps;nT++)
+    {
+        /* initialisiere den Status der Spins */
+        if(o.start_order == 1)
+            init_spins_up(g);
+        else
+            init_spins_randomly(g, o.rng);
+
+        /* Berechne Energie des Ising Modells */
+        g->E = calculate_energy(g);
+        /* Berechne Magnetisierung des Ising Modells */
+        g->M = calculate_magnetisation(g);
+
+        /* Speichere eine Kopie des Graphen im Array der Graphen */
+        list_of_graphs[nT] = gs_shallow_copy_graph(g);
+
+        /* Setze Temperatur */
+        list_of_graphs[nT]->T = o.list_of_temps[nT];
+    }
+    gs_clear_shallow_graph(g);
+
+    return(list_of_graphs);
+}
+
+/*! \fn void move_graph_nodes(gs_graph_t *g, double (*f)(const gsl_rng *, double), gsl_rng *rng, const double sigma)
+    \brief Verschiebt die Knoten des Graphen g, wobei die Verschiebung zufällig
+            nach der Verteilung f mit dem Parameter sigma gewählt wird.
+
+    \param [in,out]   g    Graph, dessen Knoten verschoben werden sollen
+    \param [in]       f    Funktion, die Zufallszahlen entsprechend der
+                           gewünschten Verteilung liefert
+    \param [in]   rng      Zufallszahlengenerator
[…]

### 2013-06-24 graph_modify.h

@@ -1,0 +1,43 @@
+/*! \file graph_modify.h */
+
+#ifndef _GRAPH_MODIFIY_H
+#define _GRAPH_MODIFIY_H
+
+#include <stdlib.h>
+#include <math.h>
+#include <gsl/gsl_rng.h>
+
+#include "graph.h"
+#include "spin.h"
+#include "list.h"
+#include "tree.h"
+
+/*! \def MIN(X,Y)
+ * Minimum von zwei Zahlen
+ */
+#define MIN(X,Y) ((X) < (Y) ? (X) : (Y))
+/*! \def MAX(X,Y)
+ * Maximum von zwei Zahlen
+ */
+#define MAX(X,Y) ((X) > (Y) ? (X) : (Y))
+
+gs_graph_t **init_graphs(const options_t options);
+
+void move_graph_nodes(gs_graph_t *g, double (*f)(const gsl_rng *, double), gsl_rng *rng, const double sigma);
+
+void create_edges(gs_graph_t *g, const options_t o);
+inline int check_relative_neighborhood(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);
+inline void get_cell_border_relative_neighborhood(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
+inline int check_gabriel(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);
+inline void get_cell_border_gabriel(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
+void delete_random_edges_till_percolation(gs_graph_t *g, gsl_rng *rng);
+int test_connectivity_between_nodes(gs_graph_t *g, int node1, int node2);
+node_t * gs_depth_first_search(gs_graph_t *g, int node, int target, node_t *tree_of_tested_nodes, int *status);
+double get_mean_weight(gs_graph_t *g);
+double get_mean_deg(gs_graph_t *g);
+double get_sum_weight(gs_graph_t *g);
+
+void init_spins_randomly(gs_graph_t *g, gsl_rng *rng);
+void init_spins_up(gs_graph_t *g);
+
+#endif /*GRAPH_MODIFIY_H*/

### 2013-06-24 spin.c

@@ -297,59 +297,6 @@ options_t get_cl_args(int argc, char *argv[])
     return(o);
 }
 
-/*! \fn gs_graph_t **init_graphs(options_t o)
-    \brief Diese Funktion initialisiert die Graphen mit allen nötigen
-            Informationen
-
-    \param [in] o               struct mit allen wichtigen Informationen
-    \return Array mit den initialisierten Graphen
-*/
-gs_graph_t **init_graphs(const options_t o)
-{
-    gs_graph_t *g;
-    gs_graph_t **list_of_graphs;
-
-    int nT;
-
-    list_of_graphs = (gs_graph_t**) malloc(o.num_temps * sizeof(gs_graph_t*));
-
-    /* Initialisiere den Graphen für die Spins */
-    g = gs_create_graph(o.L);
-
-    /* Verschiebe die Knoten */
-    move_graph_nodes(g, o.moving_fkt, o.rng, o.sigma);
-
-    /* Verknüpfe die Knoten */
-    //create_edges_regular(g);
-    create_edges(g, o);
-
-    if(o.percolation)
-        delete_random_edges_till_percolation(g, o.rng);
-
-    for(nT=0;nT<o.num_temps;nT++)
-    {
-        /* initialisiere den Status der Spins */
-        if(o.start_order == 1)
-            init_spins_up(g);
-        else
-            init_spins_randomly(g, o.rng);
-
-        /* Berechne Energie des Ising Modells */
-        g->E = calculate_energy(g);
-        /* Berechne Magnetisierung des Ising Modells */
-        g->M = calculate_magnetisation(g);
-
-        /* Speichere eine Kopie des Graphen im Array der Graphen */
-        list_of_graphs[nT] = gs_shallow_copy_graph(g);
-
-        /* Setze Temperatur */
-        list_of_graphs[nT]->T = o.list_of_temps[nT];
-    }
-    gs_clear_shallow_graph(g);
-
-    return(list_of_graphs);
-}
-
 /*! \fn void do_mc_simulation(gs_graph_t **list_of_graphs, options_t o)
     \brief Diese Funktion führt die MC Berechnungen durch und speichert die
             Ergebnisse
@@ -535,516 +482,6 @@ void do_mc_simulation(gs_graph_t **list_of_graphs, const options_t o)
 double exponential_decay(const double alpha, const double x)
 {
[…]

### 2013-06-24 spin.h

@@ -30,18 +30,6 @@
 #include <gsl/gsl_randist.h>            //< gsl: für Gausszufallszahlen
 
 #include "graph.h"
-#include "stack.h"
-#include "list.h"
-#include "tree.h"
-
-/*! \def MIN(X,Y)
- * Minimum von zwei Zahlen
- */
-#define MIN(X,Y) ((X) < (Y) ? (X) : (Y))
-/*! \def MAX(X,Y)
- * Maximum von zwei Zahlen
- */
-#define MAX(X,Y) ((X) > (Y) ? (X) : (Y))
 
 /*! \struct options_t;
     \brief Optionen für die MC Simulation, die per Kommandozeilenargument
@@ -76,27 +64,12 @@ typedef struct
 
 } options_t;
 
+#include "graph_modify.h"
+#include "stack.h"
+
 options_t get_cl_args(int argc, char *argv[]);
 
 double exponential_decay(const double alpha, const double x);
-
-gs_graph_t **init_graphs(const options_t options);
-void move_graph_nodes(gs_graph_t *g, double (*f)(const gsl_rng *, double), gsl_rng *rng, const double sigma);
-
-inline int check_relative_neighborhood(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);
-inline void get_cell_border_relative_neighborhood(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
-inline int check_gabriel(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);
-inline void get_cell_border_gabriel(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
-void create_edges(gs_graph_t *g, options_t o);
-void delete_random_edges_till_percolation(gs_graph_t *g, gsl_rng *rng);
-int test_connectivity_between_nodes(gs_graph_t *g, int node1, int node2);
-node_t * gs_depth_first_search(gs_graph_t *g, int node, int target, node_t *tree_of_tested_nodes, int *status);
-double get_mean_weight(gs_graph_t *g);
-double get_mean_deg(gs_graph_t *g);
-double get_sum_weight(gs_graph_t *g);
-
-void init_spins_randomly(gs_graph_t *g, gsl_rng *rng);
-void init_spins_up(gs_graph_t *g);
 
 double calculate_energy(const gs_graph_t *g);
 double calculate_magnetisation(const gs_graph_t *g);

### 2013-06-24 Tex/chapters/model.tex
Kritische Exponenten
warum müssen sie gleich bleiben
mehr messpunkte
etwas interpretation
und Kurvenbeschreibung der normalisierten T_c

@@
     \end{figure}\\
-    But it is also visible, that there occurs no real jump, but a continuous
+    But in the shown plots there occurs no real jump, but a continuous
     decline. The jump is only present in infinite systems, hence every
@@
     These finite size effects cause a "smearing out" of the phase
-    trasition. This is stronger for smaller system sizes, as showed in
-    fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}.\\
+    trasition. This is stronger for smaller system sizes, as is visible
+    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
+    the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
     Despite of this one can obtain \(T_c\) by finite size scaling
     methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
-    exponents. The critical exponents should not be influenced by the
-    disorder paramter \(\sigma\) [citation needed]. So they will be
-    used for consistency cross checking and comparision with the known
-    exact values \cite[S. 59]{Pelissetto2002}.\\
+    exponents.
+    Studies on random lattices with variing coupling constants \(J\)
+    \cite{Lima2000} and without \cite{Janke1994} suggest, that the
+    critical exponents should not be influenced by the disorder paramter
+    \(\sigma\). So they will be used for consistency cross checking and
+    comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\
     It is known, that for large \(L\) near the critical temperature the
@@
     do not apply very good.\\
-    %~ [theorie mit dem Collaps]
-    %~ [Erklaerung: was sind beta, gamma, nu]
     To accomplish the collapse in an semi-automatic and reproduceable
@@
     \texttt{autoscale.py} \cite{autoscale2009} is used.
-    %~ [Erklärung autoscale]
-    %~ [Am besten hier direkt die ganze Auswertung rein]
-    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
     \begin{figure}[htbp]
@@
 
-    % The arithmetic average of the intersections are plotted [hier schon?]
-    %~ [Und den rest der Auswertung]
-
 % Erwahnen, dass T_c Graph so aussieht, wie degree graph

### 2013-06-24 Tex/chapters/results.tex
Kritische Exponenten
warum müssen sie gleich bleiben
mehr messpunkte
etwas interpretation
und Kurvenbeschreibung der normalisierten T_c

@@
             \label{sfig:GG_sigma:zero}
-            \includegraphics[width=0.45\textwidth]{images/GG/sigma_e0}
+            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
         }
@@
             \label{sfig:GG_sigma:notzero}
-            \includegraphics[width=0.45\textwidth]{images/GG/sigma_g0}
+            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
         }
@@
     Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
-    show monotonically decreasing \(T_c\) with increasing disorder
-    parameter \(\sigma\). The froms of both curves are similar, but the
+    shows monotonically decreasing \(T_c\) with increasing disorder
+    parameter \(\sigma\). The forms of both curves are similar, but the
     one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
@@
     % RNG: laengere Kanten -> weniger lokale effekte?
+    For big \(\sigma\) the curve approaches the limit of randomly
+    distributed nodes, hence \(T_c\) is independet of \(\sigma\) for
+    \(\sigma >> 1\).\\
+    Also both graph types have a plateau at \(0 < \sigma < 0.1\). So
+    small disorder has little influence on the normalized critical temperature.
+    But once the degree of the graph and hence the mean sum of the coupling
+    constants decreases, the normalized critical temperature decreases, too.
+    % The author is not sure what it means.
 
 \subsection{Critical Exponents}
-    For \(\sigma \in \{0,0.1,0.5\}\) a finite size scaling analysis was
+    For \(\sigma \in \{0,0.1,0.2,0.3,0.5,1.0\}\) a finite size scaling analysis was
     performed to determine the critical exponents \(\beta, \gamma, \nu\)
@@
     \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
-    values for all other \(\sigma\) should be the same according to ???
-    [citiation needed]. Like in tab. \ref{tab:critExp} to see, most values
+    values for all other \(\sigma\) should be the same as for \(\sigma = 0\)
+    like mentioned before in section \ref{ssec:finitesize}.
+    The values for \(\sigma\) are chosen to represent every interesting
+    region from fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}:
+    the plateau at small \(\sigma\), the steep decline and the plateau at
+    big \(\sigma\).\\
+    Like in tab. \ref{tab:critExp} to see, most values
     are matching the expectations. Most \(\beta\) seem to be a bit too
@@
     by the fact that small systems (\(L=32,64\)) were used for the
-    analysis. [citation needed]
+    analysis.
+    Anyway, two critical exponents are sufficient to determine the universality
+    class. Therefore this disordered Ising modell is in the same universality
+    class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
     \begin{table}[htbp]
@@
                          & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
-                         & 0.5 & 1.009(8) & -1.75(1)  & 0.125(13)\\
+                         & 0.3 & 1.000(5) & -1.724(16)& 0.129(12)\\
+                         & 0.5 & 1.009(8) & -1.750(12)& 0.125(13)\\
+                         & 1.0 & 1.015(22)& -1.743(17)& 0.123(16)\\
             \midrule
@@
                          & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
-                         & 0.5 & 1.00(2)  & -1.75(2)  & 0.143(13)\\
+                         & 0.2 & 1.022(17)& -1.756(14)& 0.123(10)\\
+                         & 0.5 & 1.002(17)& -1.750(16)& 0.143(13)\\
+                         & 1.0 & 1.011(20)& -1.758(16)& 0.138(13)\\
             \bottomrule

### 2013-06-24 Tex/chapters/erklarung.tex
Erklärung über gute wissenschaftliche Praxis hinten angefügt

\thispagestyle{empty}
\addcontentsline{toc}{section}{Erkl\"{a}rung}
Hiermit versichere ich, dass ich diese Arbeit selbstständig verfasst und
keine anderen als die angegebenen Quellen und Hilfsmittel benutzt habe.
Außerdem versichere ich, dass ich die allgemeinen Prinzipien
wissenschaftlicher Arbeit und Veröffentlichung, wie sie in den
Leitlinien guter wissenschaftlicher Praxis der Carl von Ossietzky
Universität Oldenburg festgelegt sind, befolgt habe.

### 2013-06-24 Tex/chapters/model.tex
Umfromulierungen zur Graphen- und Ising Modell Definition

@@
 \label{ssec:graphtypes}
+    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\).\\
     All here mentioned graph types are \emph{proximity graphs}. They are
@@
     which will be described in more detail in section
-    \ref{ssec:isingmodel}.\\
-    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
-    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
+    \ref{ssec:isingmodel}.
+    In this thesis the distance is always determined by the Euclidian
+    metric, though in principle every metric can be used.\\
+
+    The Gabriel graph \cite{Gabriel1969} is a subgraph of the
+    Delaunay triangulation. Two nodes \(i\) and \(j\) with distance
     \(d_{ij}\) are connected with an edge if a circle with it's
@@
     \ref{fig:lunes}\subref{sfig:lunes:def}.\\
-    The Relative Neighborhood Graph \cite{Toussaint1980} is a
-    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
+    The Relative Neighborhood graph \cite{Toussaint1980} is a
+    subgraph of the Gabriel graph. Two nodes \(i\) and \(j\) with
     distance \(d_{ij}\) are connected if no other node is in the
@@
     \cite{Leach1992} and test the criterion for each edge, because
-    the Delaunay Triangulation is a supergraph of both. But the
-    implementation of a Delaunay Triangulation algorithm is not
-    trivial and the generation of the graphs is not time critical in
-    the scope of this bachelor thesis.\\
+    the Delaunay triangulation is a supergraph of both. But the
+    implementation of a Delaunay triangulation algorithm is not trivial
+    and the generation of the graphs is not time critical in the scope
+    of this bachelor thesis.\\
     So a tradeoff is to use basicly the simple method but only test
@@
     near the lune one can subdivide the area in \emph{cells} and save
-    for each cell a list with nodes lying inside it \cite{RNGCell}.
+    for each cell a list with nodes lying inside it like presented in
+    \cite{RNGCell}.
     Now it is just neccessary to test the nodes in the cells which
@@
 \label{ssec:isingmodel}
-    The used model is a modified 2D Ising model where the \(N=L^2\) sites
-    are displaced nodes of a square lattice of edge length \(L\) with
-    periodic boundary conditions. The displacement is randomly gauss
+    The examined model is a modified 2D Ising model where the \(N=L^2\)
+    sites are displaced nodes of a square lattice of edge length \(L\)
+    with periodic boundary conditions. The displacement is randomly gauss
     distributed with the standard deviation \(\sigma\). This \(\sigma\)
     is also called \emph{disorder paramter} in the following.
-    The hamiltonian of the Ising model is
-    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
-    where \(\avg{i,j}\) refers to nodes connected  by edges.
-    The edges are constructed according to the in section
-    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
-    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
-    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
-    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
-    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
+    \begin{equation}
+        \hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - H \sum_i s_i
+        \label{eq:hamiltonian}
+    \end{equation}
+    Equation \eqref{eq:hamiltonian} is the hamiltonian of the Ising model.
+    The magnetic field \(H=0\) in the scope of this thesis.
+    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) connected by an edge \(E_{ij}\).
+    The edges are constructed according to one of the two the in section
+    \ref{ssec:graphtypes} defined rules. So that the lattice represents
+    a proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
+    edge \(E_{ij}\) has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\).
+    \(d_{ij}\) is the Euclidian distance between the nodes \(i\) and
+    \(j\) and \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
@@
     easier approach is to find the intersections of the Binder cumulants
-    \(g\) of different system sizes \(L\).
+    \(g\) of different system sizes \(L\) because they are intersecting
+    at \(T_c\) \cite{Binder1981}.
     Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
     is calculated for the measured points.
-    In fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
-    such an interpolation is plotted for \(\sigma=0\). The cumulants
-    intersect at \(\approx 2.27\).
+    As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.
+    Here such interpolations are plotted for \(\sigma=0\) and are
+    intersecting at \(\approx 2.27\).
     To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}

### 2013-06-25 Tex/chapters/introduction.tex
Ausblick: Code bei Github
Anmerkung zu k_B = 1 nach vorner verschoben
Satyumstellungen und Korrekturen

@@
 For example to examine phasetransitions, which are defined by the abrupt
-change of an observable i.e. the change of the magnetisation of a
-ferromagnet near the Curie temperature or the change of the density of
-water near boiling. Unfortunatly the memory of any computer is small in
+change of an observable i.e. the change of the density of water near
+boiling or the change of the magnetisation of a ferromagnet near the
+Curie temperature. Unfortunatly the memory of any computer is small in
 comparison with the thermodynamic limit.
@@
 will be discussed how to manage them.\\
-
 One of the simplest models with a second order phasetransition is the
@@
 and will be explained in more detail in section \ref{ssec:isingmodel}.
-It is analyticaly solved for two dimensions on some regular lattices
+It is analytically solved for two dimensions on some regular lattices
 \cite{Onsager1944} \cite{Wannier1945}.
@@
 will be examined using the Monte Carlo simulations described in section
-\ref{sec:montecarlo}.
+\ref{sec:montecarlo}. Note that in the scope of this thesis
+the Boltzmann constant \(k_{B}=1\) for the sake of simplicity.
+All source code is available at \url{github [noch hochzuladen]}.

### 2013-06-25 Tex/chapters/model.tex
Satyumstellungen und Korrekturen

@@
     In this thesis the distance is always determined by the Euclidian
-    metric, though in principle every metric can be used.\\
+    metric in two dimensions, though in principle every metric in any
+    dimension can be used.\\
 
@@
     Delaunay triangulation. Two nodes \(i\) and \(j\) with distance
-    \(d_{ij}\) are connected with an edge if a circle with it's
+    \(d_{ij}\) are connected with an edge, if a circle with it's
     center on the middlepoint between \(i\) and \(j\) and radius
@@
     subgraph of the Gabriel graph. Two nodes \(i\) and \(j\) with
-    distance \(d_{ij}\) are connected if no other node is in the
+    distance \(d_{ij}\) are connected, if no other node is in the
     \emph{lune}. The lune is defined as the intersection of two
@@
     \(d_{ij}\) is the Euclidian distance between the nodes \(i\) and
-    \(j\) and \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
+    \(j\) and \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.
+    This is definition is inspired by \cite{Lima2000}.\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),

### 2013-06-25 Tex/chapters/monte_carlo.tex
Fehlerkorrekturen und Formulierungsverbesserungen
Satyumstellungen und Korrekturen

@@
         starting with a random site and adding neighboring sites of the
-        same spin with probability
-        \(P_{\mathrm{add}} = 1-\exp\brac{-2\beta J}\)
-        where \(J\) is the coupling constant (explained in section
+        same spin with probability \(P_{\mathrm{add}}\) from eq. \eqref{eq:wolffAdd}
+        \begin{equation}
+            P_{\mathrm{add}} = 1-\exp\brac{-2\beta J}
+            \label{eq:wolffAdd}
+        \end{equation}
+        Where \(J\) is the coupling constant (explained in section
         \ref{ssec:isingmodel}). The neighboring sites of the added sites
@@
         and one Parallel Tempering swap are performed. Where \(N\) is the
-        count of sites.
+        count of sites. All needed random numbers are generated by the
+        GSL \cite{GSL} implementation of the \emph{Mersenne Twister} \cite{Matsumoto1998}.
 %~ Monte Carlo Simulationen:\\

### 2013-06-25 Tex/chapters/introduction.tex
Grosse Umstrukturierung

@@
 or only for very simplified or special cases, can be simulated.
-%~ Simulations also have the advantage to be able to measure some quantities
-%~ which are not obtainable by experiment.
 For example to examine phasetransitions, which are defined by the abrupt
@@
 boiling or the change of the magnetisation of a ferromagnet near the
-Curie temperature. Unfortunatly the memory of any computer is small in
-comparison with the thermodynamic limit.
-%~ Of course it is only possible to simulate systems of finite size because
-%~ of the finite memory of computers so the thermodynamic limit can not be
-%~ simulated directly.
-This leads to \emph{finite size effects}. In section \ref{ssec:finitesize}
-will be discussed how to manage them.\\
-One of the simplest models with a second order phasetransition is the
-Ising model \cite{Ising1925} which is a simple model of a ferromagnet
-and will be explained in more detail in section \ref{ssec:isingmodel}.
-It is analytically solved for two dimensions on some regular lattices
-\cite{Onsager1944} \cite{Wannier1945}.
-In this thesis the critical behavior on some irregular lattices
-corresponding to proximity graphs (see section \ref{ssec:graphtypes})
-will be examined using the Monte Carlo simulations described in section
-\ref{sec:montecarlo}. Note that in the scope of this thesis
-the Boltzmann constant \(k_{B}=1\) for the sake of simplicity.
-All source code is available at \url{github [noch hochzuladen]}.
+Curie temperature. One of the simplest models with a second order
+phasetransition is the Ising model \cite{Ising1925} which is a simple
+model of a ferromagnet and will be explained in more detail in section
+\ref{ssec:isingmodel}. It is analytically solved for two dimensions on
+some regular lattices \cite{Onsager1944} \cite{Wannier1945}.
+In this thesis it's behavior near the Curie temperature -- also called
+critical temperature -- on some irregular lattices corresponding to
+proximity graphs (see section \ref{ssec:graphtypes}) will be examined
+using the Monte Carlo simulations described in section \ref{sec:montecarlo}.
+
+Unfortunatly the memory of any computer is small in comparison with the
+thermodynamic limit. This leads to \emph{finite size effects}.
+In section \ref{ssec:finitesize} will be discussed how to manage them.\\
+
+Note that in the scope of this thesis the Boltzmann constant \(k_{B}=1\)
+for the sake of simplicity.

### 2013-06-25 Tex/chapters/model.tex
Grosse Umstrukturierung

@@
-%~ \subsection{Model and Implementation}
-%~ I will desribe the model in this section in a bottom-up fashion.
-%~ First describing all parts and then connecting them.
+\subsection{The Disordered Ising Model}
+\label{ssec:isingmodel}
+    The examined model is a modified 2D Ising model.
+    First, let's define the Ising model and then explain the modifications.
+    The Ising model is a square lattice with edge length \(L\) and
+    \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
+    spin can take a value \(s \in {-1,+1}\) and interacts with it's
+    nearest neighbors described by the hamiltonian from eq. \eqref{eq:hamiltonian}
+    \begin{equation}
+        \hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - H \sum_i s_i
+        \label{eq:hamiltonian}
+    \end{equation}
+    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are nearest
+    neighbors. And \(J_{ij}\) is the coupling constant between \(i\) and
+    \(j\). Let the magnetic field \(H=0\).\\
+    In this thesis the sites of the square lattice are displaced. The
+    displacement is randomly gauss distributed with the standard
+    deviation \(\sigma\). This \(\sigma\) is also called
+    \emph{disorder paramter} in the following.
+    To determine nearest neighbors, edges are constructed according to
+    one of the two the in section \ref{ssec:graphtypes} defined rules.
+    So that the lattice represents a proximity graph. Each node \(i\)
+    has a spin \(s_i = \pm 1\). Each edge \(E_{ij}\) has a weight
+    \(J_{ij} = \exp (\alpha (1-d_{ij}))\). \(d_{ij}\) is the Euclidian
+    distance between the nodes \(i\) and \(j\) and \(\alpha = 0.5\).
+    \(J\) is called \emph{coupling constant}. This is definition is
+    inspired by \cite{Lima2000}.\\
+    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
+    for which exists an analytical solution \cite{Onsager1944}.\\
 
-%~ \subsubsection{Graphs}
-    %~ A graph is a set of nodes \(V\) and edges \(E\).
 \subsection{Gabriel- and Relative Neighborhood Graph}
@@
     one check has to be performed.
-
-\subsection{The Disordered Ising Model}
-\label{ssec:isingmodel}
-    The examined model is a modified 2D Ising model where the \(N=L^2\)
-    sites are displaced nodes of a square lattice of edge length \(L\)
-    with periodic boundary conditions. The displacement is randomly gauss
-    distributed with the standard deviation \(\sigma\). This \(\sigma\)
-    is also called \emph{disorder paramter} in the following.
-    \begin{equation}
-        \hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - H \sum_i s_i
-        \label{eq:hamiltonian}
-    \end{equation}
-    Equation \eqref{eq:hamiltonian} is the hamiltonian of the Ising model.
-    The magnetic field \(H=0\) in the scope of this thesis.
-    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) connected by an edge \(E_{ij}\).
-    The edges are constructed according to one of the two the in section
-    \ref{ssec:graphtypes} defined rules. So that the lattice represents
-    a proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
-    edge \(E_{ij}\) has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\).
-    \(d_{ij}\) is the Euclidian distance between the nodes \(i\) and
-    \(j\) and \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.
-    This is definition is inspired by \cite{Lima2000}.\\
-    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
-    for which exists an analytical solution \cite{Onsager1944}.\\
-
-    For evaluation the Monte Carlo simulation is is run till the system
-    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
-    and the magnetisation per site \(m\) and energy per site \(E\)
-    are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
-    denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
-    For every observable \(O\) the expected value \(\avg{O}\) is determined
-    as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
-    \(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
-    random proximity graphs with the same disorder paramter \(\sigma\)
-    are then averaged to \(\overline{\avg{O}}\). The errors are estimated
-    by bootstrapping.
-
-\subsection{Critical Temperature $T_c$ and Critical Exponents}
-\label{ssec:finitesize}
-    The aim of this thesis is to find the critical temperature \(T_c\)
-    of the disordered Ising model in dependence of the disorder parameter
-    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of
-    the system will jump and the susceptibility
-    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}
-    it is easy to see that the jump occurs at lower temperatures \(T\) for higher
-    disorder parameters \(\sigma\) (here with a Relative Neighborhood graph).
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[Dependence of the phase transition on $\sigma$][]
-        {
-            \label{sfig:smeared_out:meanM_L}
-            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
-        }
-        \subfigure[Example for finite size effects][]
-        {
-            \label{sfig:smeared_out:meanM}
-            \includegraphics[width=0.45\textwidth]{plots/meanM}
-        }
-        \caption[Phase Transition and Finite Size Effects]
-        {
-            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
-            parameter $\sigma$ on the phase transition
-            for an underlying Relative Neighborhood graph with $L=128$.\\
-            \subref{sfig:smeared_out:meanM}: Effects of different system
-            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
-        }
-        \label{fig:smeared_out}
-    \end{figure}\\
-    But in the shown plots there occurs no real jump, but a continuous
-    decline. The jump is only present in infinite systems, hence every
-    computer simulation will show some \emph{finte size effects}.
-    These finite size effects cause a "smearing out" of the phase
-    trasition. This is stronger for smaller system sizes, as is visible
-    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
-    the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
-    Despite of this one can obtain \(T_c\) by finite size scaling
-    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
-    exponents.
-    Studies on random lattices with variing coupling constants \(J\)
-    \cite{Lima2000} and without \cite{Janke1994} suggest, that the
-    critical exponents should not be influenced by the disorder paramter
-    \(\sigma\). So they will be used for consistency cross checking and
-    comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\
-    It is known, that for large \(L\) near the critical temperature the
-    equations \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
-    \eqref{eq:fsscaling:g} apply \cite[p. 145f]{Katzgraber2011}.
-    \begin{align}
-        \label{eq:fsscaling:m}
-        \avg{m_L} &= L^\frac{\beta}{\nu} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
-        \label{eq:fsscaling:chi}
-        \chi_L    &= L^\frac{\gamma}{\nu} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
-        \label{eq:fsscaling:g}
-        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
-    \end{align}
-    Where \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} is
-    the Binder cumulant and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
-    are unkown scaling functions. To find the exponents
-    \(\beta, \gamma, \nu\) and the critical temperature \(T_c\), one
-    varies them until the measured values of the observables collapse on
-    one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
-    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
-    Note that \(L=16\) is not used for the collapse, because it is a
-    rather small value such that eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
-    do not apply very good.\\
-    To accomplish the collapse in an semi-automatic and reproduceable
-    way with an error estimate, the programm
-    \texttt{autoscale.py} \cite{autoscale2009} is used.
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
-            \label{sfig:gettingCrit:binder_fit_s_0}
-            \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
-        }
-        \subfigure[Example of a datacollapse to determine critical exponents][]{
-            \label{sfig:gettingCrit:collapse_s_0}
-            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
-        }
-        \caption[Examples of determining critical temperature and exponents]
-        {
-            The Binder cumulant \(g\) of an square lattice Ising model
-            (\(\sigma=0\))\\
-            \subref{sfig:gettingCrit:binder_fit_s_0} interpolated
-                with cubic splines (the errorbars are too small to see)\\
-            \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
-                size scaling
-        }
-        \label{fig:gettingCrit}
-    \end{figure}\\
-    Though if one is just interested in the critical Temperature, an
-    easier approach is to find the intersections of the Binder cumulants
-    \(g\) of different system sizes \(L\) because they are intersecting
-    at \(T_c\) \cite{Binder1981}.
-    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
-    is calculated for the measured points.
-    As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.
-    Here such interpolations are plotted for \(\sigma=0\) and are
-    intersecting at \(\approx 2.27\).
-    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
-    are averaged and the standard error is calculated. In this case one
-    gets \(T_c = 2.2689(2)\), which is in good agreement with the
-    exact solution from eq. \eqref{eq:exactTc} \cite{Onsager1944}.
-    \begin{equation}
-        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
-        \label{eq:exactTc}
-    \end{equation}
-
-% Erwahnen, dass T_c Graph so aussieht, wie degree graph
-% mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
-% cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52

### 2013-06-25 Tex/chapters/monte_carlo.tex
Grosse Umstrukturierung

@@
 \label{sec:montecarlo}
-Monte Carlo simulations are (probably) named after the casino in Monaco
-\cite{NewmanBarkema1999} because both rely on randomness.\\
+%~ Monte Carlo simulations are (probably) named after the casino in Monaco
+%~ \cite{NewmanBarkema1999} because both rely on randomness.\\
 The idea behind Monte Carlo simulations is to take random samples of
@@
 Of course one wants to sample more points, where the area below the
-function is big. This can be achieved by \emph{Importance Sampling}. One
+function is big, because points in areas, where the function does
+contribute little to the integral, contribute little to the integral.
+This can be achieved by \emph{Importance Sampling}. One
 generates random numbers according to some probabilty distribution and
@@
 by generating random states.
-But it is difficult to create random state of the Ising system in
-equilibrium, hence one uses \emph{Markov Chains} to generate new states
-\(\nu\) from old ones \(\mu\).
+But it is difficult to create random state of a physical system i.e. the
+Ising system in equilibrium, hence one uses \emph{Markov Chains} to
+generate new states \(\nu\) from old ones \(\mu\).
 It is important that the transition probabilities \(A(\mu \to \nu)\)
@@
         and one Parallel Tempering swap are performed. Where \(N\) is the
-        count of sites. All needed random numbers are generated by the
-        GSL \cite{GSL} implementation of the \emph{Mersenne Twister} \cite{Matsumoto1998}.
+        count of sites.
 %~ Monte Carlo Simulationen:\\

### 2013-06-25 Tex/chapters/results.tex
Grosse Umstrukturierung

@@
+The generation of the Graphs and the Monte Carlo Simulation are implemented
+in C, all needed random numbers are generated by the GSL \cite{GSL}
+implementation of the \emph{Mersenne Twister} \cite{Matsumoto1998} and
+the generated data is evaluated via Python scripts.
+All source code is available at \url{https://github.com/surt91/IsingFerromagnet}.\\
+
+For evaluation the Monte Carlo simulation is run until the system
+is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
+and the magnetisation per site \(m\) and energy per site \(E\)
+are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
+denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
+For every observable \(O\) the expected value \(\avg{O}\) is determined
+as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
+\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
+random proximity graphs with the same disorder paramter \(\sigma\)
+are then averaged to \(\overline{\avg{O}}\). The errors are estimated
+by bootstrapping \cite{Bootstrap}.
+
+\subsection{Finite Size Effects}
+\label{ssec:finitesize}
+    The aim of this thesis is to find the critical temperature \(T_c\)
+    of the disordered Ising model in dependence of the disorder parameter
+    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of
+    the system will jump and the susceptibility
+    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
+    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}
+    it is easy to see that the jump occurs at lower temperatures \(T\) for higher
+    disorder parameters \(\sigma\) (here with a Relative Neighborhood graph).
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Dependence of the phase transition on $\sigma$][]
+        {
+            \label{sfig:smeared_out:meanM_L}
+            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
+        }
+        \subfigure[Example for finite size effects][]
+        {
+            \label{sfig:smeared_out:meanM}
+            \includegraphics[width=0.45\textwidth]{plots/meanM}
+        }
+        \caption[Phase Transition and Finite Size Effects]
+        {
+            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
+            parameter $\sigma$ on the phase transition
+            for an underlying Relative Neighborhood graph with $L=128$.\\
+            \subref{sfig:smeared_out:meanM}: Effects of different system
+            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
+        }
+        \label{fig:smeared_out}
+    \end{figure}\\
+    But in the shown plots there occurs no real jump, but a continuous
+    decline. The jump is only present in infinite systems, hence every
+    computer simulation will show some \emph{finte size effects}.
+    These finite size effects cause a "smearing out" of the phase
+    trasition. This is stronger for smaller system sizes, as is visible
+    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
+    the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
+    Despite of this one can obtain \(T_c\) by finite size scaling
+    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
+    exponents.
+    Studies on random lattices with variing coupling constants \(J\)
+    \cite{Lima2000} and without \cite{Janke1994} suggest, that the
+    critical exponents should not be influenced by the disorder paramter
+    \(\sigma\). So they will be used for consistency cross checking and
+    comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\
+    It is known, that for large \(L\) near the critical temperature the
+    equations \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
+    \eqref{eq:fsscaling:g} apply \cite[p. 145f]{Katzgraber2011}.
+    \begin{align}
+        \label{eq:fsscaling:m}
+        \avg{m_L} &= L^\frac{\beta}{\nu} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:fsscaling:chi}
+        \chi_L    &= L^\frac{\gamma}{\nu} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:fsscaling:g}
+        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
+    \end{align}
+    Where \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} is
+    the Binder cumulant and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
+    are unkown scaling functions. To find the exponents
+    \(\beta, \gamma, \nu\) and the critical temperature \(T_c\), one
+    varies them until the measured values of the observables collapse on
+    one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
+    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
+    Note that \(L=16\) is not used for the collapse, because it is a
+    rather small value such that eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
+    do not apply very good.\\
+    To accomplish the collapse in an semi-automatic and reproduceable
+    way with an error estimate, the programm
+    \texttt{autoscale.py} \cite{autoscale2009} is used.
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
+            \label{sfig:gettingCrit:binder_fit_s_0}
+            \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        }
+        \subfigure[Example of a datacollapse to determine critical exponents][]{
+            \label{sfig:gettingCrit:collapse_s_0}
+            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
+        }
+        \caption[Examples of determining critical temperature and exponents]
+        {
+            The Binder cumulant \(g\) of an square lattice Ising model
+            (\(\sigma=0\))\\
+            \subref{sfig:gettingCrit:binder_fit_s_0} interpolated
+                with cubic splines (the errorbars are too small to see)\\
+            \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
+                size scaling
+        }
+        \label{fig:gettingCrit}
+    \end{figure}\\
+    Though if one is just interested in the critical Temperature, an
+    easier approach is to find the intersections of the Binder cumulants
+    \(g\) of different system sizes \(L\) because they are intersecting
+    at \(T_c\) \cite{Binder1981}.
+    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+    is calculated for the measured points.
+    As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.
+    Here such interpolations are plotted for \(\sigma=0\) and are
+    intersecting at \(\approx 2.27\).
+    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
+    are averaged and the standard error is calculated. In this case one
+    gets \(T_c = 2.2689(2)\), which is in good agreement with the
+    exact solution from eq. \eqref{eq:exactTc} \cite{Onsager1944}.
+    \begin{equation}
+        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
+        \label{eq:exactTc}
+    \end{equation}
+
 \subsection{Critical Temperature}
@@
     % The author is not sure what it means.
+    % mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
+    % cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
 

### 2013-06-25 Tex/chapters/results.tex
Definitionen hinyugefuegt

@@
 is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
-and the magnetisation per site \(m\) and energy per site \(E\)
-are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
-denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
+and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
+per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
+\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
+(see also \ref{ssec:eqtime}).
 For every observable \(O\) the expected value \(\avg{O}\) is determined

### 2013-06-26 Tex/chapters/results.tex
Korrekturen, Umfärbung
Kurze Beschreibung der g* Werte

@@
     comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\
+    % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
     It is known, that for large \(L\) near the critical temperature the
@@
         \label{eq:fsscaling:g}
-        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
+        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:binderCumulant}
+        g &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}}
     \end{align}
-    Where \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} is
-    the Binder cumulant and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
+    Where \(g\) from eq. \eqref{eq:binderCumulant} is a normalized
+    Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
     are unkown scaling functions. To find the exponents
@@
     intersecting at \(\approx 2.27\).
-    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
+    To determine \(T_c\), the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
     are averaged and the standard error is calculated. In this case one
@@
 \subsection{Critical Temperature}
+\label{ssec:binderIntersections}
     The evaluation of the Binder cumulant's intersections, yields the
@@
 
-    %~ <J>\(\sigma\), Anmerkung zur Anomalie des GG und der Ähnlichkeit von <J> zu \(T_c\)\\
-%~
-    %~ Erklärung zu Autokorreltationszeit \(\tau\) und Equilibrierungszeit \(t_eq\)\\
+\subsection{Critical Value of the Binder Cumulant}
+    The value of the Binder cumulant at the critical point \(g^*\) is
+    depends strongly on boundary conditions but only weakly on the lattice
+    structure \cite{BinderValue}. For periodic boundary conditions on a
+    square lattice it is \(g^* \approx 0.916\) according to \cite{BinderValue}
+        \footnote{Note that \cite{BinderValue} uses an other definition of
+            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
+            to match it's definition in this thesis.}.
+    Because the analysis of section \ref{ssec:binderIntersections}
+    yields \(g^*\) anyway, it is easy to check the consistency and
+    behaivior of \(g^*\) in the disordered Ising modell.\\
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[for a Relative Neighborhood graph][]
+        {
+            \label{sfig:TcG:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
+        }
+        \subfigure[for a Gabriel graph][]
+        {
+            \label{sfig:TcG:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
+        }
+        \caption[Values of the Binder cumulant at the critical point $g^*$]
+        {
+            Values of the Binder cumulant at the critical point \(g^*\)
+            for\\
+            \subref{sfig:TcG:RNG} a Relative Neighborhood graph and\\
+            \subref{sfig:TcG:GG} a Gabriel graph for different \(\sigma\).
+            The dotted line is the reference value for square lattices
+            with periodic boundary conditions \cite{BinderValue}, which
+            corresponds to \(\sigma = 0\).
+        }
+        \label{fig:TcG}
+    \end{figure}\\
+    Considering both plots in fig. \ref{fig:TcG}, \(g^*\) is for low
+    \(\sigma\) obviously always bigger than the known value. Though the
+    deviation is less than \(1\%\). Perhaps this is some inherent flaw
+    of the cubic spline interpolation used to aquire these \(g^*\) values.
+    For bigger \(\sigma\) the uncertainty gets greater, but the values
+    do only differ by a few percent, hence even the big disorder and
+    definition of nearest neighbors via a proximity graph does not change
+    \(g^*\) much, as expected.
+
 %~ Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
-    %~ Bestimmung der kritischen Punkte\\
-        %~ Polyfit 4ten Grades durch Binder Kumulante \cite{Binder1981}\\
-        %~ Finite Size Scaling Vergleich der Exponenten (AutoScale \cite{Melchert2009}, Vergleich \cite[S. 59]{Pelissetto2002})\\

### 2013-06-26 Tex/chapters/results.tex
g* in gc umbenannt

@@
 \subsection{Critical Value of the Binder Cumulant}
-    The value of the Binder cumulant at the critical point \(g^*\) is
+    The value of the Binder cumulant at the critical point \(g_c\) is
     depends strongly on boundary conditions but only weakly on the lattice
     structure \cite{BinderValue}. For periodic boundary conditions on a
-    square lattice it is \(g^* \approx 0.916\) according to \cite{BinderValue}
+    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
         \footnote{Note that \cite{BinderValue} uses an other definition of
@@
     Because the analysis of section \ref{ssec:binderIntersections}
-    yields \(g^*\) anyway, it is easy to check the consistency and
-    behaivior of \(g^*\) in the disordered Ising modell.\\
+    yields \(g_c\) anyway, it is easy to check the consistency and
+    behaivior of \(g_c\) in the disordered Ising modell.\\
     \begin{figure}[htbp]
@@
         }
-        \caption[Values of the Binder cumulant at the critical point $g^*$]
+        \caption[Values of the Binder cumulant at the critical point $g_c$]
         {
-            Values of the Binder cumulant at the critical point \(g^*\)
+            Values of the Binder cumulant at the critical point \(g_c\)
             for\\
@@
     \end{figure}\\
-    Considering both plots in fig. \ref{fig:TcG}, \(g^*\) is for low
+    Considering both plots in fig. \ref{fig:TcG}, \(g_c\) is for low
     \(\sigma\) obviously always bigger than the known value. Though the
     deviation is less than \(1\%\). Perhaps this is some inherent flaw
-    of the cubic spline interpolation used to aquire these \(g^*\) values.
+    of the cubic spline interpolation used to aquire these \(g_c\) values.
     For bigger \(\sigma\) the uncertainty gets greater, but the values
@@
     definition of nearest neighbors via a proximity graph does not change
-    \(g^*\) much, as expected.
+    \(g_c\) much. This is the expected behaivior.
 

### 2013-06-26 Tex/chapters/results.tex
kurze Erklärung zu cubic splines

@@
     at \(T_c\) \cite{Binder1981}.
-    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+    Because  the magnetisation \(m\) is only measured for discrete values
+    of \(T\), \(g\) is also only known for these discrete values and has
+    to be interpolated to find a intersection. Therefore a cubic spline
+    interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
     is calculated for the measured points.
+    Cubic spline interpolation is a piecewise fitting of polynoms of
+    degree three which are joined under the condition to be at least two
+    timescontinuously differentiable.
     As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.

### 2013-06-26 Tex/chapters/results.tex
Referenz fur finite size scaling
Bildunterschrift hinzugefugt, einruckung verbessert

@@
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}
-    it is easy to see that the jump occurs at lower temperatures \(T\) for higher
+    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix for a similar figure for the specific heat.}
+    it is easy to see that the jump of \(\avg{|m|}\)
+    occurs at lower temperatures \(T\) for higher
     disorder parameters \(\sigma\) (here with a Relative Neighborhood graph).
@@
     % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
+    For a more in depth look at finite size scaling, \cite{Norrenbrock2011}
+    offers a explanation.
     It is known, that for large \(L\) near the critical temperature the
     equations \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
-    \eqref{eq:fsscaling:g} apply \cite[p. 145f]{Katzgraber2011}.
+    \eqref{eq:fsscaling:g} apply.
     \begin{align}
@@
         \label{eq:fsscaling:g}
-        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
-        \label{eq:binderCumulant}
-        g &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}}
+        g          &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}} \propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
     \end{align}
-    Where \(g\) from eq. \eqref{eq:binderCumulant} is a normalized
+    Where \(g\) from eq. \eqref{eq:fsscaling:g} is a normalized
     Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
@@
         \centering
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
+        \subfigure[Example of a Binder cumulant to determine the critical temperature][]
+        {
             \label{sfig:gettingCrit:binder_fit_s_0}
@@
         }
-        \subfigure[Example of a datacollapse to determine critical exponents][]{
+        \subfigure[Example of a datacollapse to determine critical exponents][]
+        {
             \label{sfig:gettingCrit:collapse_s_0}
@@
         }
-        \caption[]
+        \caption[Anomaly of the Gabriel graph for small $\sigma$]
         {

### 2013-06-26 Tex/chapters/model.tex
Darstellungsfehler fehlender {} behoben
Ausführlichere Beschreibung des disordered ising modells

@@
     \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
-    spin can take a value \(s \in {-1,+1}\) and interacts with it's
+    spin can take a value \(s \in \{-1,+1\}\) and interacts with it's
     nearest neighbors described by the hamiltonian from eq. \eqref{eq:hamiltonian}
@@
     neighbors. And \(J_{ij}\) is the coupling constant between \(i\) and
-    \(j\). Let the magnetic field \(H=0\).\\
-    In this thesis the sites of the square lattice are displaced. The
+    \(j\). If \(J_{ij} > 0 \forall i,j\) the model resembles a ferromagnet.
+    \(H\) denotes the outer magnetic field.\\
+    In this thesis \(H=0\). The most important modification is, that
+    the sites of the square lattice are displaced. The
     displacement is randomly gauss distributed with the standard
-    deviation \(\sigma\). This \(\sigma\) is also called
-    \emph{disorder paramter} in the following.
-    To determine nearest neighbors, edges are constructed according to
-    one of the two the in section \ref{ssec:graphtypes} defined rules.
-    So that the lattice represents a proximity graph. Each node \(i\)
-    has a spin \(s_i = \pm 1\). Each edge \(E_{ij}\) has a weight
-    \(J_{ij} = \exp (\alpha (1-d_{ij}))\). \(d_{ij}\) is the Euclidian
-    distance between the nodes \(i\) and \(j\) and \(\alpha = 0.5\).
-    \(J\) is called \emph{coupling constant}. This is definition is
-    inspired by \cite{Lima2000}.\\
+    deviation \(\sigma\). That is the \(x\) and \(y\) coordinates of the
+    sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
+    from a Gauß distribution
+    \[f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}\]
+    \[x \to x + \Delta x\]
+    \[y \to y + \Delta y\]
+    This \(\sigma\) is also called \emph{disorder paramter} in the following.
+    Because most sites will only have one nearest neighbor after the
+    displacement, the lattice would collapse to many very small clusters.
+    To avoid this, the new "nearest" neighbors are those sites connected
+    by an edge. The edges are constructed according to
+    one of the two the in section \ref{ssec:graphtypes} defined rules,
+    so that the lattice represents a proximity graph. Note that edges
+    of a proximity graph do not cross each other, hence the 2D character
+    of the lattice is preserved. The coupling constant \(J\) gets
+    identified with edge weights. The weight of an edge \(E_{ij}\) is
+    \(J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidian
+    distance between the nodes \(i\) and \(j\). The free parameter
+    \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
@@
     lattices with nearest neighbor relationships, like the Ising model
-    which will be described in more detail in section
-    \ref{ssec:isingmodel}.
+    from the section \ref{ssec:isingmodel}.
     In this thesis the distance is always determined by the Euclidian

### 2013-06-26 Tex/chapters/monte_carlo.tex
weitere Anmerkungen zu verschiedenen MC algorithmen

@@
         \(\Delta \hat H\) defined in eq. \eqref{eq:dH} that would result
-        from a flip of and excute the flip with the probability \(A\)
+        from a flip of that spin and excute the flip with the probability \(A\)
         eq. \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
@@
         So if a transition lowers the energy it is always done. This
-        results in a good ratio between calculations and transitions.
+        results in a high ratio between chosen spins and flipped spins.
+        Therefore it minimizes the calculations needed for a change of
+        the state.
 
@@
         will only contain very few sites.
-        Both situaitions have no advantage against the Metropolis algorithm.
+        Both situaitions have no advantage against the Metropolis algorithm.\\
+        So one would activate this algorithm near the critical temperature
+        but use a simple Metropolis algorithm at high and low temperatures.
 
@@
         to higher temperatures, leave it's local minimum and cool down
-        again in a lower minimum.
+        again in a lower minimum.\\
+        In the case of a ferromagnetic Ising model the risk to get trapped
+        in an local energy minimum is very low. Though the autocorrelation
+        decreases significantly. In the scope of this thesis this comes
+        for no cost, because one has to simulate for many temperatures
+        to determine the critical temperature. The additional calculations
+        to determine wheather to swap configurations or not are small in
+        comparison with those that would be needed to generate a new
+        uncorrelated state without \emph{parallel tempering}.
 
@@
         Each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
-        and one Parallel Tempering swap are performed. Where \(N\) is the
-        count of sites.
-%~ Monte Carlo Simulationen:\\
-    %~ Wolff-Cluster Algorithmus \cite{Wolff1989} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
-    %~ Metropolis Sweep \cite{Metropolis1953} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
-    %~ Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\
+        and one parallel tempering swap are performed. Where \(N\) is the
+        count of sites.\\
+        Because it is not known before, where the critical temperatures
+        \(T_c\) are located, the Wolff cluster algorithm is used for
+        every temperature. The speed up at criticality is worth the
+        moderate slow down at other temperatures.
 

### 2013-06-28 Tex/chapters/results.tex
Tabelle für autokorr und equilibriums zeiten

@@
 \(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
-(see also \ref{ssec:eqtime}).
+(see also \ref{ssec:eqtime}). The used values for different system sizes
+are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
+these values are generously rounded up to be on the safe side.
+\begin{table}[htbp]
+    \center
+    \begin{tabular}{l r r r r r}
+        \toprule
+        \(L\)    & 16 &  32 &  64 & 128 & 256\\
+        \midrule
+        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
+        \(t_eq\) & 40 & 100 & 100 & 200 & 600\\
+        \bottomrule
+    \end{tabular}
+    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
+    \label{tab:tauAndTeq}
+\end{table}\\
 For every observable \(O\) the expected value \(\avg{O}\) is determined

### 2013-06-28 Tex/chapters/erklarung.tex
Unterschriftfeld mit Datum

@@
 Leitlinien guter wissenschaftlicher Praxis der Carl von Ossietzky
-Universität Oldenburg festgelegt sind, befolgt habe.
+Universität Oldenburg festgelegt sind, befolgt habe.\\[3cm]
+
+\raggedleft
+\hfill Oldenburg den \today, ..............................................\\
+\hfill (Hendrik Schawe)\\

### 2013-06-28 Tex/chapters/monte_carlo.tex
Mehr erläuterungen zur autocorr zeit

@@
     \(2\tau\) sweeps between two measurements.
+    The autocorrelation time is of course dependent on the temperature.
+    At high temperatures the fluctuations are strong and subsequent
+    states are more dissimilar and therefore less correlated than at low
+    temperatures, where less spins are flipping. In this thesis always
+    the longest autocorrelation time \(\tau\) of all simulated
+    temperatures was taken.
+    \[\tau = \max_T \tau_T\]

### 2013-06-28 Tex/chapters/results.tex
List of Tables für die Vollständigkeit
Mehr erläuterungen zur autocorr zeit

@@
 \end{table}\\
+Obiviously the autocorrelation time \(\tau\) increases with the system
+size. In fact it obeys a power law as clearly visible in fig.
+\ref{fig:autocorrPowerLaw}.
+% sagen, dass das bekanntes verhalten ist
+% als cross check behandeln
+% [citation needed]
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.45\textwidth]{plots/autocorr}
+    \caption
+    {
+        Dependece of the autocorrelation time $\tau$ on the system size $L$
+    }
+    \label{fig:autocorrPowerLaw}
+\end{figure}\\
 For every observable \(O\) the expected value \(\avg{O}\) is determined
-as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
-\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
-random proximity graphs with the same disorder paramter \(\sigma\)
-are then averaged to \(\overline{\avg{O}}\). The errors are estimated
-by bootstrapping \cite{Bootstrap}.
+as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
+or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
+calculated sweeps totals to
+\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
+The expected values \(\avg{O}\) for \(100\) different random proximity
+graphs with the same disorder paramter \(\sigma\) are then averaged to
+\(\overline{\avg{O}}\).
+The errors are estimated by bootstrapping \cite{Bootstrap}.
 
@@
         \end{tabular}
-        \caption{Critical exponents for different \(\sigma\)}
+        \caption{Critical exponents for different $\sigma$}
         \label{tab:critExp}

### 2013-06-28 Tex/chapters/erklarung.tex
Viele kleiner verbesserungen, umformulierengen präzisierungen

@@
 keine anderen als die angegebenen Quellen und Hilfsmittel benutzt habe.
-Außerdem versichere ich, dass ich die allgemeinen Prinzipien
+Außerdem ver\-sichere ich, dass ich die allgemeinen Prinzipien
 wissenschaftlicher Arbeit und Veröffentlichung, wie sie in den

### 2013-06-28 Tex/chapters/model.tex
Viele kleiner verbesserungen, umformulierengen präzisierungen

@@
     displacement is randomly gauss distributed with the standard
-    deviation \(\sigma\). That is the \(x\) and \(y\) coordinates of the
+    deviation \(\sigma\). That is, the \(x\) and \(y\) coordinates of the
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
@@
     by an edge. The edges are constructed according to
-    one of the two the in section \ref{ssec:graphtypes} defined rules,
+    one of the two in section \ref{ssec:graphtypes} defined rules,
     so that the lattice represents a proximity graph. Note that edges
@@
     distance between the nodes \(i\) and \(j\). The free parameter
-    \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.\\
+    \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.
+    The boundary is periodic i.e. nodes near the right edge can be
+    connected to nodes near the left edge and vice versa. Analogous the
+    top and bottom edges are connected. One can imagine that the model
+    lives on the surface of a torus.\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
-    for which exists an analytical solution \cite{Onsager1944}.\\
+    for which exists an analytical solution \cite{Onsager1944}. And for
+    \(\sigma \gtrsim 1\) the nodes are distributed randomly. This case
+    is studied for constant \(J\) on the Delaunay triangulation\cite{Janke1994}.\\
 

### 2013-06-28 Tex/chapters/results.tex
Viele kleiner verbesserungen, umformulierengen präzisierungen

@@
 are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
-these values are generously rounded up to be on the safe side.
+the \(t_{eq}\) values are generously rounded up to be on the safe side
+and the \(\tau\) values are determined as the maximum \(\tau\) over all
+simulated temperatures.
+\[\tau = \max_T \tau_T\]
 \begin{table}[htbp]
@@
 Obiviously the autocorrelation time \(\tau\) increases with the system
-size. In fact it obeys a power law as clearly visible in fig.
-\ref{fig:autocorrPowerLaw}.
-% sagen, dass das bekanntes verhalten ist
-% als cross check behandeln
-% [citation needed]
+size. In fact it obeys a power law, which is the expected bahaivior as
+mentioned in section \ref{ssec:eqtime}. In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
+the dynamical critical exponent \(z\) is determined as \(z=0.57(4)\).
+This exponent is much higher than the expectation. For the Wolff cluster
+algorithm at criticality, one would expect \(z=0.25\)\cite{NewmanBarkema1999}.
+This suggests that \emph{critical slowing down} is not an issue in this
+case and the autocorrelation time is limited by the slow decorrelation
+at low temperatures. A direct proof is given by fig. \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
+Apparently even parallel tempering can not compensate that. Probably
+because only one configuration swap between neighboring temperatures is
+performed each sweep. Those neighboring configurations at low temperatures
+have a magnetisation per site of \(m \approx \pm 1\), so there is a good
+chance, that the exchange does not change \(m\) (in case of same sign)
+and thus does not lower the autocorrelation function.
 \begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.45\textwidth]{plots/autocorr}
-    \caption
+    \subfigure[in dependence on the system size $L$][]
     {
-        Dependece of the autocorrelation time $\tau$ on the system size $L$
+        \label{fig:autocorr:powerLaw}
+        \includegraphics[width=0.45\textwidth]{plots/autocorrL}
     }
-    \label{fig:autocorrPowerLaw}
+    \subfigure[in dependence on the temperature $T$][]
+    {
+        \label{fig:autocorr:temperatures}
+        \includegraphics[width=0.45\textwidth]{plots/autocorrT}
+    }
+    \caption[The autocorrelation time $\tau$]
+    {
+        Dependece of the autocorrelation time $\tau$ on\\
+        \subref{fig:autocorr:powerLaw} the system size $L$\\
+        \subref{fig:autocorr:temperatures} the temperature $T$
+    }
+    \label{fig:autocorr}
 \end{figure}\\
@@
 \(\overline{\avg{O}}\).
-The errors are estimated by bootstrapping \cite{Bootstrap}.
+The errors are estimated by bootstrapping \cite{Bootstrap} with 200
+bootstrap samples.
 
@@
     exponents.
-    Studies on random lattices with variing coupling constants \(J\)
-    \cite{Lima2000} and without \cite{Janke1994} suggest, that the
+    Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
+    variing coupling constants \(J\) suggest, that the
     critical exponents should not be influenced by the disorder paramter

### 2013-06-28 Tex/chapters/introduction.tex
Viele kleiner verbesserungen, umformulierengen präzisierungen
weitere Korrekturen und Umformulierungen

@@
 
-Unfortunatly the memory of any computer is small in comparison with the
-thermodynamic limit. This leads to \emph{finite size effects}.
-In section \ref{ssec:finitesize} will be discussed how to manage them.\\
+Unfortunately the memory of any computer is small in comparison with the
+thermodynamic limit. This leads to deviations from the real behavior of
+the system in the thermodynamic limit. These deviations are called
+\emph{finite size effects} and in section \ref{ssec:finitesize} will be
+discussed how to manage them.\\
 

### 2013-06-28 Tex/chapters/monte_carlo.tex
weitere Korrekturen und Umformulierungen

@@
 This can be achieved by \emph{Importance Sampling}. One
-generates random numbers according to some probabilty distribution and
-weights the result accordingly.\\
+generates random numbers according to some probabilty distribution, which
+yields more numbers in the range where the function to ingegrate has high
+values and weights the result accordingly.\\
 %~ To improve this method: \emph{Importance Sampling}
@@
 by generating random states.
-But it is difficult to create random state of a physical system i.e. the
+But it is difficult to create a random state of a physical system i.e. the
 Ising system in equilibrium, hence one uses \emph{Markov Chains} to
@@
 \subsection{Monte Carlo Algorithms}
-    \paragraph{Metropolis}
-        A Metropolis Monte Carlo simulation of an Ising model will
-        choose a random spin, calculate the energy change
+    \subsubsection{Metropolis}
+        A Metropolis Monte Carlo\cite{Metropolis1953} simulation of an
+        Ising model will choose a random spin, calculate the energy change
         \(\Delta \hat H\) defined in eq. \eqref{eq:dH} that would result
@@
 
-    \paragraph{Wolff}
+    \subsubsection{Wolff}
         Close to the critical temperature \(T_c\) the Metropolis
@@
 
-    \paragraph{Parallel Tempering}
+    \subsubsection{Parallel Tempering}
         %~ The main aim is to obtain the critical temperatures
@@
         %~ \cite{ParallelTempering1986} is a suited algorithm.
-        Parallel Tempering simulates many identical systems at different
+        Parallel Tempering\cite{ParallelTempering1986} simulates many identical systems at different
         temperatures and periodically swaps the spin configurations
@@
 
-    \paragraph{Implementation Details}
+    \subsubsection{Implementation Details}
         Here a mixture of the above three algorithms is used.
@@
                 Ising system \(L=64\) at \(T=2.40\) (only Metropolis
-                sweeps) on half logarithmic axis.
+                sweeps -- otherwise the decline is too steep to show)
+                on half logarithmic axis.
                 The straight line is a exponential fit \(\exp(-t/\tau)\)
@@
     states are more dissimilar and therefore less correlated than at low
-    temperatures, where less spins are flipping. In this thesis always
-    the longest autocorrelation time \(\tau\) of all simulated
-    temperatures was taken.
-    \[\tau = \max_T \tau_T\]
+    temperatures, where less spins are flipping. But the longest
+    autocorrelation times are encountered at the critical temperature.
+    This effect is called \emph{critical slowing down} and is
+    characterized by the \emph{dynamical critical exponent} \(z\)
+    \cite{SwendsenWang1987}. The dependence of the autocorrelation time
+    \(\tau\) on the system size \(L\) is then given by \(\tau \propto L^z\).

### 2013-06-28 Tex/chapters/results.tex
weitere Korrekturen und Umformulierungen

@@
 and the \(\tau\) values are determined as the maximum \(\tau\) over all
-simulated temperatures.
-\[\tau = \max_T \tau_T\]
+simulated temperatures \(\tau = \max_T \tau_T\) and rounded to the next
+integer.
 \begin{table}[htbp]
@@
         \(\tau\) &  3 &   5 &   7 &  12 &  16\\
-        \(t_eq\) & 40 & 100 & 100 & 200 & 600\\
+        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
         \bottomrule
@@
     But in the shown plots there occurs no real jump, but a continuous
-    decline. The jump is only present in infinite systems, hence every
-    computer simulation will show some \emph{finte size effects}.
+    decline. The jump is only present in infinite systems, hence no
+    computer simulation will show the exact behaivior in the
+    thermodynamic limit. It will always show some \emph{finte size effects}.
     These finite size effects cause a "smearing out" of the phase

### 2013-07-01 Tex/chapters/results.tex
Rundungsfehler

--- 2013-06-28 Tex/chapters/results.tex
@@
 are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
-these values are generously rounded up to be on the safe side.
+the \(t_{eq}\) values are generously rounded up to be on the safe side
+and the \(\tau\) values are determined as the maximum \(\tau\) over all
+simulated temperatures and disorder parameters \(\tau = \max_{T,\sigma} \tau_{T,\sigma}\)
+and rounded up to the next integer. In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
+the autocorrelation time for \(\sigma=0\) is plotted.
+%The \emph{critical slowing down} is visible as a peak.
+The plateau at low temperatures is easy to understand considering the
+effects of the wolff algorithm. At low temperatures it flips nearly every
+spin in every step, thus the correlation drops to zero after one sweep.
+Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
+temperature. The cause is probably the effectiveness of the Wolff cluster
+algorithm at \(T_c\).
 \begin{table}[htbp]
@@
 Obiviously the autocorrelation time \(\tau\) increases with the system
-size. In fact it obeys a power law as clearly visible in fig.
-\ref{fig:autocorrPowerLaw}.
-% sagen, dass das bekanntes verhalten ist
-% als cross check behandeln
-% [citation needed]
+size. In fact it obeys a power law, which is the expected behaivior of
+a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
+In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
+over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
+This exponent is much higher than the one of Wolff cluster
+algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
+So it represents the dynamical exponent for parallel tempering with
+Metropolis above criticality and thus is not exactly a critical exponent.
+Nevertheless it is interesting, that it obeys a power law just the same.
+Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
+at criticality.
 \begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.45\textwidth]{plots/autocorr}
-    \caption
+    \subfigure[in dependence on the temperature $T$][]
     {
-        Dependece of the autocorrelation time $\tau$ on the system size $L$
+        \label{fig:autocorr:temperatures}
+        \includegraphics[width=0.45\textwidth]{plots/autocorrT}
     }
-    \label{fig:autocorrPowerLaw}
+    \subfigure[in dependence on the system size $L$][]
+    {
+        \label{fig:autocorr:powerLaw}
+        \includegraphics[width=0.45\textwidth]{plots/autocorrL}
+    }
+    \caption[The autocorrelation time $\tau$]
+    {
+        Dependece of the autocorrelation time $\tau$ on
+        \subref{fig:autocorr:temperatures} the temperature $T$ for
+            $\sigma=0$ and
+        \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
+            are the standard error determined by bootstrapping)
+    }
+    \label{fig:autocorr}
 \end{figure}\\
@@
 \(\overline{\avg{O}}\).
-The errors are estimated by bootstrapping \cite{Bootstrap}.
+All errorbars are estimated by bootstrapping\cite{Bootstrap} with 200
+bootstrap samples if not noted otherwise.
 
@@
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix for a similar figure for the specific heat.}
+    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}
     it is easy to see that the jump of \(\avg{|m|}\)
@@
     one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
-    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
+    collapse in fig.
+\ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
     Note that \(L=16\) is not used for the collapse, because it is a
@@
             \midrule
-            Relative N.  & 0.0 & 1.007(2) & -1.739(2) & 0.130(1) \\
+            Relative N.  & 0.0 & 1.007(2) & -1.740(2) & 0.130(1) \\
                          & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\

### 2013-07-01 Tex/chapters/model.tex
Korrekturen

@@
     To construct these graphs the simple way is to test for each
-    pair of nodes one has to check for every other node if it lies in
+    pair of nodes if any other node lies in
     the lune of the pair. That is of complexity \(O (N^3)\), because
@@
     Triangulation in complexity \(O (N \log N)\)
-    \cite{Leach1992} and test the criterion for each edge, because
+    \cite{RNGCell} and test the criterion for each edge, because
     the Delaunay triangulation is a supergraph of both. But the

### 2013-07-01 Tex/chapters/monte_carlo.tex
Korrekturen

@@
     \subsubsection{Wolff}
+    \label{sssec:wolff}
         Close to the critical temperature \(T_c\) the Metropolis
@@
                 on half logarithmic axis.
-                The straight line is a exponential fit \(\exp(-t/\tau)\)
+                The straight line is an exponential fit \(\exp(-t/\tau)\)
                 with \(\tau = 342(1)\).
@@
     of subsequent states are correlated. To determine when two states
-    are independet, one calculates the normalized autocorrelation function
+    are independent, one calculates the normalized autocorrelation function
     \(\frac{\chi(t)}{\chi(0)}\), which should decay exponentially
@@
     The autocorrelation time is of course dependent on the temperature.
-    At high temperatures the fluctuations are strong and subsequent
+    For example for the standard Metropolis algorithm the fluctuations
+    are strong at high temperatures and subsequent
     states are more dissimilar and therefore less correlated than at low
@@
     \(\tau\) on the system size \(L\) is then given by \(\tau \propto L^z\).
+    As mentioned in section \ref{sssec:wolff}, the Wolff cluster algorithm
+    decreases \(z\) dramatically. This causes the course of the autocorrelation
+    time in dependence on temperature to change significantly as shown in
+    section \ref{sec:results}.

### 2013-07-01 Tex/chapters/conclusion.tex
Angefangen mit conclusion

In this thesis the propertys of the disordered Ising ferromagnet on two
proximity graphs was studied. This model is within the universality of
the standard Ising ferromagnet. Further the critical temperature depends
on the one hand on the

\subsection{Outlook}
    The behavior of the normalized critical temperatures in dependence
    on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
    are qualitative similar to each other. One could study the behavior
    of other proximity graphs like the minimum spanning tree or the
    Delauney triangulation, to examine if it is also similar. Further
    one could examine other graph ensembles to determine, if this is a
    more universal property.\\
    Also it would be interesting to compare this results with a the
    results obtained by the same experiments with \(\alpha = 0\), which
    implies that the coupling constant is independent from the distance
    on the sites. That way the critical temperature would be more
    straight forward normalized by the degree of the graph. This way it
    could be determined if the qualitative similarities of the
    normalized temperatures over the disorder paramter of different
    graph types are related to the choice of the function determinig the
    coupling constant.

### 2013-07-01 Tex/chapters/results.tex
Angefangen mit conclusion

@@
     small disorder has little influence on the normalized critical temperature.
-    But once the degree of the graph and hence the mean sum of the coupling
-    constants decreases, the normalized critical temperature decreases, too.
+    But once the degree -- also called \emph{coordination number} -- of
+    the graph and hence the mean sum of the coupling constants decreases,
+    the normalized critical temperature decreases, too.\\
+    In conclusion the critical temperature depends on the averaged sum
+    of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
+    normalizing it with this, the plots for both proximity graphs look
+    similar.
     % The author is not sure what it means.

### 2013-07-01 Tex/chapters/conclusion.tex
Rechtschreibkontrolle aspell entdeckt

@@
-In this thesis the propertys of the disordered Ising ferromagnet on two
+In this thesis the properties of the disordered Ising ferromagnet on two
 proximity graphs was studied. This model is within the universality of
@@
     of other proximity graphs like the minimum spanning tree or the
-    Delauney triangulation, to examine if it is also similar. Further
+    Delaunay triangulation, to examine if it is also similar. Further
     one could examine other graph ensembles to determine, if this is a
@@
     could be determined if the qualitative similarities of the
-    normalized temperatures over the disorder paramter of different
-    graph types are related to the choice of the function determinig the
+    normalized temperatures over the disorder parameter of different
+    graph types are related to the choice of the function determining the
     coupling constant.

### 2013-07-01 Tex/chapters/introduction.tex
Rechtschreibkontrolle aspell entdeckt

@@
 The computing capabilities of modern computers enable researchers to
-collect and analyse vast amounts of data.
-Further statistical systems, for which exist no analytical soultions
+collect and analyze vast amounts of data.
+Further statistical systems, for which exist no analytic solutions
 or only for very simplified or special cases, can be simulated.
-For example to examine phasetransitions, which are defined by the abrupt
+For example to examine phase transitions, which are defined by the abrupt
 change of an observable i.e. the change of the density of water near
-boiling or the change of the magnetisation of a ferromagnet near the
+boiling or the change of the magnetization of a ferromagnet near the
 Curie temperature. One of the simplest models with a second order
-phasetransition is the Ising model \cite{Ising1925} which is a simple
+phase transition is the Ising model \cite{Ising1925} which is a simple
 model of a ferromagnet and will be explained in more detail in section

### 2013-07-01 Tex/chapters/model.tex
Rechtschreibkontrolle aspell entdeckt

@@
     spin can take a value \(s \in \{-1,+1\}\) and interacts with it's
-    nearest neighbors described by the hamiltonian from eq. \eqref{eq:hamiltonian}
+    nearest neighbors described by the Hamiltonian from eq. \eqref{eq:hamiltonian}
     \begin{equation}
@@
     the sites of the square lattice are displaced. The
-    displacement is randomly gauss distributed with the standard
+    displacement is randomly Gauß distributed with the standard
     deviation \(\sigma\). That is, the \(x\) and \(y\) coordinates of the
@@
     \[y \to y + \Delta y\]
-    This \(\sigma\) is also called \emph{disorder paramter} in the following.
+    This \(\sigma\) is also called \emph{disorder parameter} in the following.
     Because most sites will only have one nearest neighbor after the
@@
     identified with edge weights. The weight of an edge \(E_{ij}\) is
-    \(J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidian
+    \(J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean
     distance between the nodes \(i\) and \(j\). The free parameter
@@
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
-    for which exists an analytical solution \cite{Onsager1944}. And for
+    for which exists an analytic solution \cite{Onsager1944}. And for
     \(\sigma \gtrsim 1\) the nodes are distributed randomly. This case
@@
     from the section \ref{ssec:isingmodel}.
-    In this thesis the distance is always determined by the Euclidian
+    In this thesis the distance is always determined by the Euclidean
     metric in two dimensions, though in principle every metric in any
@@
     \(d_{ij}\) are connected with an edge, if a circle with it's
-    center on the middlepoint between \(i\) and \(j\) and radius
+    center on half way between \(i\) and \(j\) and radius
     \(r = \frac d 2\) contains no other nodes. This area will be
@@
     of this bachelor thesis.\\
-    So a tradeoff is to use basicly the simple method but only test
+    So a trade off is to use basically the simple method but only test
     the criterion for nodes which are near to the lune and abort if
@@
     \cite{RNGCell}.
-    Now it is just neccessary to test the nodes in the cells which
+    Now it is just necessary to test the nodes in the cells which
     resemble a rectangular bounding box of the lune. Most pairs will be
@@
     Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
-    over \(15\) respectivly \(40\). Though the complexity is still of
+    over \(15\) respectively \(40\). Though the complexity is still of
     order \(O(N^2)\) in the best case, because for every pair at least

### 2013-07-01 Tex/chapters/monte_carlo.tex
Rechtschreibkontrolle aspell entdeckt

@@
 this samples. In example the Monte Carlo integration chooses random
-points within the bounding box of the fuction and estimates the integral
-as the fraction of points below the function and points above muliplied
+points within the bounding box of the function and estimates the integral
+as the fraction of points below the function and points above multiplied
 by the area of the bounding box.
@@
 This can be achieved by \emph{Importance Sampling}. One
-generates random numbers according to some probabilty distribution, which
-yields more numbers in the range where the function to ingegrate has high
+generates random numbers according to some probability distribution, which
+yields more numbers in the range where the function to integrate has high
 values and weights the result accordingly.\\
@@
         \(\Delta \hat H\) defined in eq. \eqref{eq:dH} that would result
-        from a flip of that spin and excute the flip with the probability \(A\)
+        from a flip of that spin and execute the flip with the probability \(A\)
         eq. \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
@@
         will only contain very few sites.
-        Both situaitions have no advantage against the Metropolis algorithm.\\
+        Both situations have no advantage against the Metropolis algorithm.\\
         So one would activate this algorithm near the critical temperature
@@
         to determine the critical temperature. The additional calculations
-        to determine wheather to swap configurations or not are small in
+        to determine weather to swap configurations or not are small in
         comparison with those that would be needed to generate a new

### 2013-07-01 Tex/chapters/results.tex
Rechtschreibkontrolle aspell entdeckt

--- 2013-07-01 Tex/chapters/results.tex
@@
 is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
-and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
+and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
 per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
@@
 and the \(\tau\) values are determined as the maximum \(\tau\) over all
-simulated temperatures and disorder parameters \(\tau = \max_{T,\sigma} \tau_{T,\sigma}\)
-and rounded up to the next integer. In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
-the autocorrelation time for \(\sigma=0\) is plotted.
-%The \emph{critical slowing down} is visible as a peak.
-The plateau at low temperatures is easy to understand considering the
-effects of the wolff algorithm. At low temperatures it flips nearly every
-spin in every step, thus the correlation drops to zero after one sweep.
-Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
-temperature. The cause is probably the effectiveness of the Wolff cluster
-algorithm at \(T_c\).
+simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
+and rounded up to the next integer.
 \begin{table}[htbp]
@@
 \end{table}\\
-Obiviously the autocorrelation time \(\tau\) increases with the system
+In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
+the autocorrelation time for \(\sigma=0\) is plotted.
+%The \emph{critical slowing down} is visible as a peak.
+The plateau at low temperatures is easy to understand considering the
+effects of the Wolff algorithm. At low temperatures it flips nearly every
+spin in every step, thus the correlation drops to zero after one sweep.
+Alternatively the parallel tempering algorithm swaps spin configurations
+with possibly different signs, thus having the same effect.
+Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
+temperature. The cause is probably the effectiveness of the Wolff cluster
+algorithm at \(T_c\).
+Obviously the autocorrelation time \(\tau\) increases with the system
 size. In fact it obeys a power law, which is the expected behaivior of
@@
 The expected values \(\avg{O}\) for \(100\) different random proximity
-graphs with the same disorder paramter \(\sigma\) are then averaged to
+graphs with the same disorder parameter \(\sigma\) are then averaged to
 \(\overline{\avg{O}}\).
-All errorbars are estimated by bootstrapping\cite{Bootstrap} with 200
+All error bars are estimated by bootstrapping\cite{Bootstrap} with 200
 bootstrap samples if not noted otherwise.
@@
     of the disordered Ising model in dependence of the disorder parameter
-    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of
+    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
     the system will jump and the susceptibility
@@
     decline. The jump is only present in infinite systems, hence no
-    computer simulation will show the exact behaivior in the
+    computer simulation will show the exact behavior in the
     thermodynamic limit. It will always show some \emph{finte size effects}.
     These finite size effects cause a "smearing out" of the phase
-    trasition. This is stronger for smaller system sizes, as is visible
+    transition. This is stronger for smaller system sizes, as is visible
     in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
@@
     Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
-    variing coupling constants \(J\) suggest, that the
-    critical exponents should not be influenced by the disorder paramter
+    varying coupling constants \(J\) suggest, that the
+    critical exponents should not be influenced by the disorder parameter
     \(\sigma\). So they will be used for consistency cross checking and
-    comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\
+    comparison with the known exact values \cite[S. 59]{Pelissetto2002}.\\
     % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
@@
     Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
-    are unkown scaling functions. To find the exponents
+    are unknown scaling functions. To find the exponents
     \(\beta, \gamma, \nu\) and the critical temperature \(T_c\), one
@@
     To accomplish the collapse in an semi-automatic and reproduceable
-    way with an error estimate, the programm
+    way with an error estimate, the program
     \texttt{autoscale.py} \cite{autoscale2009} is used.
@@
     at \(T_c\) \cite{Binder1981}.
-    Because  the magnetisation \(m\) is only measured for discrete values
+    Because  the magnetization \(m\) is only measured for discrete values
     of \(T\), \(g\) is also only known for these discrete values and has
@@
     is calculated for the measured points.
-    Cubic spline interpolation is a piecewise fitting of polynoms of
+    Cubic spline interpolation is a piece wise fitting of polynoms of
     degree three which are joined under the condition to be at least two
-    timescontinuously differentiable.
+    times continuously differentiable.
     As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.
@@
     The evaluation of the Binder cumulant's intersections, yields the
-    critical temperatures \(T_c\), which are plotted in
-    fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.
-    Further in fig. \ref{fig:Tc}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
-    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
-    is plotted which is evidently correlated with \(T_c\).
-    That is plausible, because \(T_c\) is dependend on the coupling
-    constant \(J\) (compare \eqref{eq:exactTc}).\\
-    It seems reasonable to normalize the values of \(T_{c}\) by
-    \(\avg{\sum_{\avg{i,j}} J_{ij}}\) which yields the diagramms fig.
-    \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.
+    critical temperatures \(T_c\).
+    In this section these \(T_c\) on either the Relative Neighborhood
+    graph or the Gabriel graph are compared. In the following figures,
+    the Relative Neighborhood graph will always be on the left side
+    and the Gabriel graph on the right side.
+    In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).
     \begin{figure}[htbp]
@@
         }
-
+        \caption[Critical Temperature over different disorder parameters]
+        {
+            Critical temperatures \(T_c\) over different
+            disorder parameters \(\sigma\) for
+            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc:GG} the Gabriel Graph.\\
+        }
+        \label{fig:Tc}
+    \end{figure}\\
+    One sees that the Relative Neighborhood graph on the left has
+    generally a lower critical temperature than the Gabriel. Also \(T_c\)
+    of the Relative Neighborhood graph decreases
+    monotonically while \(T_c\) of the Gabriel rises at first.
+    For big \(\sigma\) the displaced nodes approach the limit of randomly
+    distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
+    \(\sigma >> 1\).\\
+    A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
+    of \(T_c\) on the Gabriel graph. To understand that, one has to
+    consider the influence of the graph properties on the critical
+    temperature.\\
+    A characteristic property of a graph is it's degree \(K\).
+    The degree \(K\) of a graph -- sometimes called \emph{coordination number} --
+    is defined as the mean count of neighbors per node
+    \begin{equation}
+        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}
+        \label{eq:degree}
+    \end{equation}
+    Therefore the degree of the graphs at different \(\sigma\) is
+    plotted in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}.
+    \begin{figure}[htbp]
+        \centering
         \subfigure[][]
         {
-            \label{sfig:sumJ:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
+            \label{sfig:deg:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
         }
@@
         {
-            \label{sfig:sumJ:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
+            \label{sfig:deg:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_deg}
         }
@@
         {
-            \label{sfig:Tc_norm:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
+            \label{sfig:Tc_norm_deg:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg}
         }
@@
         {
-            \label{sfig:Tc_norm:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
+            \label{sfig:Tc_norm_deg:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
         }
+
         \caption[Critical Temperature over different disorder parameters]
         {
-            Top: Critical temperatures over different
+            Top: Degree \(K\) of graph over different
+            disorder parameters \(\sigma\) for
+            \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:deg:GG} the Gabriel Graph.\\
+            Bottom: Critical temperatures normalized by degree over different
             disorder parameters for
-            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc:GG} the Gabriel Graph.\\
-            Middle: Mean sum of the coupling constants to all
-            neighbors over different disorder parameters for
-            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
-            Bottom: Normalized critical temperatures over different
-            disorder parameters for
-            \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc_norm:GG} the Gabriel Graph.
+            \subref{sfig:Tc_norm_deg:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc_norm_deg:GG} the Gabriel Graph.
         }
-        \label{fig:Tc}
+        \label{fig:Tc_deg}
     \end{figure}\\
-    % I don't know what all that means...
-    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
-    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
+    \(T_c\) and \(K\) are evidently correlated. This is not
+    unexpected. For example the Honeycomb lattice is of degree \(K=3\)
+    and for which exists an analytic solution \cite{Wannier1945}.
+    It has a critical temperature of
+    \begin{equation}
+        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
+        \label{eq:exactHCTc}
+    \end{equation}
+    This is lower than for the square lattice with degree 4.\\
+    It seems reasonable to normalize \(T_c\) by the degree of the underlying
+    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
+    Indeed the normalization eliminates the jump and reduces the
+    slope of the rising on the Gabriel graph. Hence it reduces differences
+    between the Relative Neighborhood graph and the Gabriel graph.\\
+    % Zitat, dass Janke das auch gemacht hat .. nochmal nachlesen
+    The jump of \(K\) and therefore the jump of \(T_c\) on the Gabriel graph is easily explained
     by the definition of the Gabriel graph and it's aftereffects for
     the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
-    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
+    a small change of sigma causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
     To fully understand this, take four nodes forming a square. The edge
@@
     \end{figure}\\
-    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
-    shows monotonically decreasing \(T_c\) with increasing disorder
-    parameter \(\sigma\). The forms of both curves are similar, but the
-    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
+    But the degree does not alone influence the behavior of \(T_c\).
+    Further \(T_c\) depends on the coupling
+    constant \(J\), which is obvious in eq. \eqref{eq:exactTc} and
+    \eqref{eq:exactHCTc}. Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
+    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+    is plotted. This is a number which should combine the dependence on
+    the degree and the coupling constant, which is not equal for
+    every edge in this case.
+    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
+    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:sumJ:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:sumJ:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
+        }
+
+        \subfigure[][]
+        {
+            \label{sfig:Tc_normJ:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_normJ}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:Tc_normJ:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_normJ}
+        }
+
+        \caption[Critical Temperature over different disorder parameters]
+        {
+            Top: Mean sum of the coupling constants to all
+            neighbors over different disorder parameters for
+            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
+            Bottom: Critical temperatures normalized by mean sum of the
+            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
+            disorder parameters for
+            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
+        }
+        \label{fig:TcJ}
+    \end{figure}\\
+    % I don't know what all that means...
+    If on normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
+    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
+    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
+    decreasing with increasing disorder parameter \(\sigma\). Moreover
+    the forms of both curves are quite similar, but the
+    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
     is generally lower and spans over a bigger temperature range than
-    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
+    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
     % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
     % RNG: laengere Kanten -> weniger lokale effekte?
-    For big \(\sigma\) the curve approaches the limit of randomly
-    distributed nodes, hence \(T_c\) is independet of \(\sigma\) for
-    \(\sigma >> 1\).\\
-    Also both graph types have a plateau at \(0 < \sigma < 0.1\). So
-    small disorder has little influence on the normalized critical temperature.
-    But once the degree of the graph and hence the mean sum of the coupling
-    constants decreases, the normalized critical temperature decreases, too.
+    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
+    disorder has little influence on this normalized critical temperature.
+    Also both graph types have a steep decline after the plateau before
+    they approach an asymptotic limit for \(\sigma >> 1\)\\\\
+
+    %~ But once the degree of
+    %~ the graph and hence the mean sum of the coupling constants decreases,
+    %~ the normalized critical temperature decreases, too.\\
+    %~ In conclusion the critical temperature depends on the averaged sum
+    %~ of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
+    %~ normalizing it with this, the plots for both proximity graphs look
+    %~ similar.
     % The author is not sure what it means.
-    % mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
-    % cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
 
@@
     Anyway, two critical exponents are sufficient to determine the universality
-    class. Therefore this disordered Ising modell is in the same universality
+    class. Therefore this disordered Ising model is in the same universality
     class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
@@
     yields \(g_c\) anyway, it is easy to check the consistency and
-    behaivior of \(g_c\) in the disordered Ising modell.\\
+    behavior of \(g_c\) in the disordered Ising model.\\
     \begin{figure}[htbp]
@@
     deviation is less than \(1\%\). Perhaps this is some inherent flaw
-    of the cubic spline interpolation used to aquire these \(g_c\) values.
+    of the cubic spline interpolation used to acquire these \(g_c\) values.
     For bigger \(\sigma\) the uncertainty gets greater, but the values
@@
     definition of nearest neighbors via a proximity graph does not change
-    \(g_c\) much. This is the expected behaivior.
+    \(g_c\) much. This is the expected behavior.
 

### 2013-07-01 Tex/chapters/model.tex
Skizze zur Art des Displacements

@@
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
-    from a Gauß distribution
-    \[f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}\]
+    from a Gauß distribution eq. \eqref{eq:gauss}.
+    This is sketched in fig. \ref{fig:displacement}.
+    \begin{equation}
+        f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}
+        \label{eq:gauss}
+    \end{equation}
     \[x \to x + \Delta x\]
     \[y \to y + \Delta y\]
+    \begin{figure}[htbp]
+        \centering
+        \input{images/Displacement}
+        \caption[Sketch how the displacement works]
+        {
+            Sketch how the displacement of the nodes works. Two nodes
+            get displaced by \(\Delta x\) and \(\Delta y\) drawn from the
+            distributions displayed next to the points.
+        }
+        \label{fig:displacement}
+    \end{figure}\\
     This \(\sigma\) is also called \emph{disorder parameter} in the following.

### 2013-07-02 Tex/chapters/results.tex
Einzelner Tippfehler
Autokorrelation und Fehlerabschätzung aus-/umformuliert

@@
 For evaluation the Monte Carlo simulation is run until the system
-is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
+is equilibrated after \(t_{eq}\) sweeps. Then the simulation conti <nues
 and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
@@
 \end{table}\\
+For every observable \(O\) the expected value \(\avg{O}\) is determined
+as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
+or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
+calculated sweeps totals to
+\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
+The expected values \(\avg{O}\) for \(100\) different random proximity
+graphs with the same disorder parameter \(\sigma\) are then averaged to
+\(\overline{\avg{O}}\). Not only the seed to generate the new random
+realization of the proximity graph gets changed, but also the seed for
+the random numbers used in the Monte Carlo simulation and during the
+generation of the random start configuration of the spins.\\
+The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
+\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
+Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
+\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
+over different realizations of the random proximity graph, which are
+surely uncorrelated.
+Because every error mentioned in this thesis is of this type, it is not
+necessary to determine \(\tau\) for each observable. Therefore a good
+error estimate can be achieved by simple bootstrapping. Though one has
+to simulate enough uncorrelated states for each realization, to keep
+the \(\Delta \overline{\avg{O}}\) small.
+
+\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
+    % Sollte das hier rein?
+    Before the results are presented, a short analysis of the
+    autocorrelation time \(\tau\) is given, to illustrate the benefits
+    of the used Wolff cluster algorithm.\\
     In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
-the autocorrelation time for \(\sigma=0\) is plotted.
-%The \emph{critical slowing down} is visible as a peak.
-The plateau at low temperatures is easy to understand considering the
-effects of the Wolff algorithm. At low temperatures it flips nearly every
-spin in every step, thus the correlation drops to zero after one sweep.
-Alternatively the parallel tempering algorithm swaps spin configurations
-with possibly different signs, thus having the same effect.
-Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
-temperature. The cause is probably the effectiveness of the Wolff cluster
-algorithm at \(T_c\).
-Obviously the autocorrelation time \(\tau\) increases with the system
-size. In fact it obeys a power law, which is the expected behaivior of
-a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
-In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
-over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
-This exponent is much higher than the one of Wolff cluster
-algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
-So it represents the dynamical exponent for parallel tempering with
-Metropolis above criticality and thus is not exactly a critical exponent.
-Nevertheless it is interesting, that it obeys a power law just the same.
-Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
-at criticality.
+    the autocorrelation time for the magnetization per site \(m\) at \(\sigma=0\) is plotted.
     \begin{figure}[htbp]
@@
         \label{fig:autocorr}
-\end{figure}\\
-For every observable \(O\) the expected value \(\avg{O}\) is determined
-as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
-or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
-calculated sweeps totals to
-\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
-The expected values \(\avg{O}\) for \(100\) different random proximity
-graphs with the same disorder parameter \(\sigma\) are then averaged to
-\(\overline{\avg{O}}\).
-All error bars are estimated by bootstrapping\cite{Bootstrap} with 200
-bootstrap samples if not noted otherwise.
+    \end{figure}
+    The plateau at low temperatures is easy to understand considering the
+    effects of the Wolff algorithm. At low temperatures it flips nearly every
+    spin in every step, thus the correlation drops to zero after one sweep.
+    Alternatively the parallel tempering algorithm swaps spin configurations
+    with possibly different signs, thus having the same effect.
+    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
+    temperature. The cause is probably the effectiveness of the Wolff cluster
+    algorithm at \(T_c\).
+    Obviously the autocorrelation time \(\tau\) increases with the system
+    size. In fact it obeys a power law, which is the expected behaivior of
+    a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
+    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
+    over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
+    This exponent is much higher than the one of Wolff cluster
+    algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
+    So it represents the dynamical exponent for parallel tempering with
+    Metropolis above criticality and thus is not exactly a critical exponent.
+    Nevertheless it is interesting, that it obeys a power law just the same.
+    Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
+    at criticality.
 
@@
     % I don't know what all that means...
-    If on normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
+    If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
     \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the

### 2013-07-02 Tex/chapters/results.tex
Captions korrigiert

@@
 
-        \caption[Critical Temperature over different disorder parameters]
+        \caption[Critical Temperature normalized by Degree of the Graph]
         {
@@
 
-        \caption[Critical Temperature over different disorder parameters]
+        \caption[Critical Temperature normalized by Mean Sum of the Coupling Constants]
         {

### 2013-07-02 Tex/chapters/appendix.tex
Fehlerkorrekturen

\section{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In fig. \ref{fig:smeared_out_appendix} the specific heat
    \[C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}\]
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite, and gets shallower with smaller \(L\). Besides
    the maximum moves away from the critical temperature with smaller \(L\).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            Effects of different system sizes at \(\sigma = 0\). Dotted lines
            are guides to the eye.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

\section{Finite Size Scaling at the Example of the Susceptibility and Magnetisation}
\label{appendix:finiteSizeScaling}
    In fig. \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:s_0_sus}
    the magnetic susceptibility
    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
    is plotted and in \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:collapse_s_0_sus}
    collapsed to determine the critical exponent \(\beta\).
    Analog for the mean absolute magnetisation \(\avg{\abs{m}}\) in fig \ref{fig:gettingCrit:appendix}
    \subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
    to determine the critical exponent \(\gamma\).
    Both are at \(\sigma=0\) and
    both collapses reproduce the  critical exponent \(\nu\) and the
    critical temperature \(T_c\) in good agreement with the before determined
    values from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
    and the analytically known values. This is a good cross check
    for consistency.
    \begin{figure}[htbp]
        \centering
        \subfigure[Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
        }
        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
        }
        \subfigure[Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
        }
        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
        }
        \caption[Examples of determining critical temperature and exponents]
        {
            Examples for finite size scaling.
        }
        \label{fig:gettingCrit:appendix}
    \end{figure}

### 2013-07-02 Tex/chapters/results.tex
Fehlerkorrekturen

@@
 For evaluation the Monte Carlo simulation is run until the system
-is equilibrated after \(t_{eq}\) sweeps. Then the simulation conti <nues
+is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
 and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy

### 2013-07-05 Tex/chapters/model.tex
Tippfehler Korrekturen

@@
     displacement is randomly Gauß distributed with the standard
-    deviation \(\sigma\). That is, the \(x\) and \(y\) coordinates of the
+    deviation \(\sigma\), i.e. the \(x\) and \(y\) coordinates of the
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
@@
     \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.
-    The boundary is periodic i.e. nodes near the right edge can be
+    The boundary is periodic e.g. nodes near the right edge can be
     connected to nodes near the left edge and vice versa. Analogous the

### 2013-07-05 Tex/chapters/results.tex
Tippfehler Korrekturen
Fehlerkorrekturen, Umformulierungen

@@
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}
+    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
     it is easy to see that the jump of \(\avg{|m|}\)
@@
     transition. This is stronger for smaller system sizes, as is visible
-    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
-    the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
+    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
+    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
     Despite of this one can obtain \(T_c\) by finite size scaling
@@
     For a more in depth look at finite size scaling, \cite{Norrenbrock2011}
-    offers a explanation.
+    offers an explanation.
     It is known, that for large \(L\) near the critical temperature the
@@
     temperature.\\
-    A characteristic property of a graph is it's degree \(K\).
-    The degree \(K\) of a graph -- sometimes called \emph{coordination number} --
-    is defined as the mean count of neighbors per node
+    One basic property of a graph is it's degree \(K\) -- sometimes
+    called \emph{coordination number} -- is defined as the mean count of
+    neighbors per node
     \begin{equation}
@@
     \end{equation}
-    Therefore the degree of the graphs at different \(\sigma\) is
-    plotted in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}.
+    It is known, that the degree has an impact on the critical Temperature.
+    For example the Honeycomb lattice is of degree \(K=3\)
+    and there exists an analytic solution \cite{Wannier1945}.
+    It's a critical temperature is determined by eq. \eqref{eq:exactHCTc}.
+    \begin{equation}
+        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
+        \label{eq:exactHCTc}
+    \end{equation}
+    This is lower than for the square lattice with degree 4.\\
+    If one plots the degree of the graphs at different \(\sigma\) like
+    in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
+    one recognizes, that \(T_c\) and \(K\) are evidently correlated.
+    It seems reasonable to normalize \(T_c\) by the degree of the underlying
+    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
+    Indeed the normalization eliminates the jump and reduces the
+    slope of the rising on the Gabriel graph. Hence it reduces differences
+    between the Relative Neighborhood graph and the Gabriel graph.
     \begin{figure}[htbp]
@@
     \end{figure}\\
-    \(T_c\) and \(K\) are evidently correlated. This is not
-    unexpected. For example the Honeycomb lattice is of degree \(K=3\)
-    and for which exists an analytic solution \cite{Wannier1945}.
-    It has a critical temperature of
-    \begin{equation}
-        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
-        \label{eq:exactHCTc}
-    \end{equation}
-    This is lower than for the square lattice with degree 4.\\
-    It seems reasonable to normalize \(T_c\) by the degree of the underlying
-    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
-    Indeed the normalization eliminates the jump and reduces the
-    slope of the rising on the Gabriel graph. Hence it reduces differences
-    between the Relative Neighborhood graph and the Gabriel graph.\\
-    % Zitat, dass Janke das auch gemacht hat .. nochmal nachlesen
-    The jump of \(K\) and therefore the jump of \(T_c\) on the Gabriel graph is easily explained
+    To understand the jump of \(T_c\), it seems to be sufficient to
+    understand the jump of \(K\), which is easily explained
     by the definition of the Gabriel graph and it's aftereffects for
     the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
-    a small change of sigma causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
+    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
     To fully understand this, take four nodes forming a square. The edge
@@
     But the degree does not alone influence the behavior of \(T_c\).
-    Further \(T_c\) depends on the coupling
-    constant \(J\), which is obvious in eq. \eqref{eq:exactTc} and
-    \eqref{eq:exactHCTc}. Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
+    Further \(T_c\) depends on the coupling constant \(J\), which is
+    obvious in eq. \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
+    coupling constant in turn is depending on the length of the edges,
+    which changes with \(\sigma\).
+    Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
     the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
     is plotted. This is a number which should combine the dependence on
-    the degree and the coupling constant, which is not equal for
-    every edge in this case.
+    the degree and the coupling constant.
     The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
@@
     \end{figure}\\
-    % I don't know what all that means...
     If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
@@
     the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
-    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
-    % RNG: laengere Kanten -> weniger lokale effekte?
     Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
@@
 
-    %~ But once the degree of
-    %~ the graph and hence the mean sum of the coupling constants decreases,
-    %~ the normalized critical temperature decreases, too.\\
-    %~ In conclusion the critical temperature depends on the averaged sum
-    %~ of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
-    %~ normalizing it with this, the plots for both proximity graphs look
-    %~ similar.
-    % The author is not sure what it means.
-
 \subsection{Critical Exponents}
-    For \(\sigma \in \{0,0.1,0.2,0.3,0.5,1.0\}\) a finite size scaling analysis was
+    A finite size scaling analysis was
     performed to determine the critical exponents \(\beta, \gamma, \nu\)
@@
     \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
-    values for all other \(\sigma\) should be the same as for \(\sigma = 0\)
-    like mentioned before in section \ref{ssec:finitesize}.
-    The values for \(\sigma\) are chosen to represent every interesting
-    region from fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}:
-    the plateau at small \(\sigma\), the steep decline and the plateau at
-    big \(\sigma\).\\
-    Like in tab. \ref{tab:critExp} to see, most values
-    are matching the expectations. Most \(\beta\) seem to be a bit too
-    big, but they are close enough to the expectations to be explained
-    by the fact that small systems (\(L=32,64\)) were used for the
-    analysis.
-    Anyway, two critical exponents are sufficient to determine the universality
-    class. Therefore this disordered Ising model is in the same universality
-    class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
+    values for all other \(\sigma\) are expected be the same as for
+    \(\sigma = 0\) like mentioned before in section \ref{ssec:finitesize}.
+    Therefore it is sufficient to take a few samples to test if the
+    expectations are met. Hence 5 values of \(\sigma\) are analyzed,
+    which are chosen to represent every interesting region from fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}:
+    the analytically known value for \(\sigma = 0\), the in \cite{Janke1994}
+    examined limit for \(\sigma \gtrsim 1\), the plateau at small
+    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).\\
     \begin{table}[htbp]
@@
     \(\sigma\) obviously always bigger than the known value. Though the
-    deviation is less than \(1\%\). Perhaps this is some inherent flaw
-    of the cubic spline interpolation used to acquire these \(g_c\) values.
+    deviations are only very small. Perhaps this overestimation is caused
+    by the cubic spline interpolation used to acquire these \(g_c\) values.
     For bigger \(\sigma\) the uncertainty gets greater, but the values
@@
     definition of nearest neighbors via a proximity graph does not change
-    \(g_c\) much. This is the expected behavior.
-
-%~ Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
+    \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
+    lattice structure has a minor effect on \(g_c\), the uncertainty of
+    \(g_c\) is too big, to show it. For a more in depth analysis, new
+    Monte Carlo simulations at \(T_c\) would be needed. But this is
+    beyond the scope of this thesis. Anyway the results are the expected
+    behaivior, because no major deviations from the value of \(g_c\) at
+    \(\sigma = 0\) occur at larger \(\sigma\).

### 2013-07-05 Tex/chapters/monte_carlo.tex
Tippfehler Korrekturen
Equilibrium und Monte Carlo weiter ausformuliert

--- 2013-06-28 Tex/chapters/monte_carlo.tex
@@
 \label{sec:montecarlo}
-%~ Monte Carlo simulations are (probably) named after the casino in Monaco
-%~ \cite{NewmanBarkema1999} because both rely on randomness.\\
+Monte Carlo simulations are (probalby) named after the casino in Monaco
+\cite{NewmanBarkema1999} because both rely on randomness.\\
 The idea behind Monte Carlo simulations is to take random samples of
-the observable, which should be measured, and estimate the observable from
+the observable which should be measured and estimate the observable from
 this samples. In example the Monte Carlo integration chooses random
@@
 as the fraction of points below the function and points above muliplied
-by the area of the bounding box.
-Of course one wants to sample more points, where the area below the
-function is big, because points in areas, where the function does
-contribute little to the integral, contribute little to the integral.
-This can be achieved by \emph{Importance Sampling}. One
-generates random numbers according to some probabilty distribution, which
-yields more numbers in the range where the function to ingegrate has high
-values and weights the result accordingly.\\
+by the area of the bounding box.\\
 %~ To improve this method: \emph{Importance Sampling}
@@
 %~ distributed........
-The same principle is used to sample properties of statistical systems
-by generating random states.
-But it is difficult to create a random state of a physical system i.e. the
-Ising system in equilibrium, hence one uses \emph{Markov Chains} to
-generate new states \(\nu\) from old ones \(\mu\).
+It is difficult to create random state of the Ising system in
+equilibrium, hence one uses \emph{Markov Chains} to generate new states
+\(\nu\) from old ones \(\mu\).
 It is important that the transition probabilities \(A(\mu \to \nu)\)
-obey \emph{Detailed Balance} and \emph{Ergodicity}.
-\emph{Detailed Balance} means  that the probability to leave a state is
+obey \emph{Detailed Balance}, that the probability to leave a state is
 the same as the probability to enter the state in equilibrium
-\(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\) with \(p_\mu\) the
-probability to be in state \(\mu\).
-And \emph{Ergodicity} requires that every possible state is reachable
-from every other state in finite time. \cite{NewmanBarkema1999} \cite{Katzgraber2011}
-Otherwise the samples might not be representative for the whole system.\\
+\(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\)
+with \(p_\mu\) the probability to be in state \(\mu\), and
+\emph{Ergodicity}, that every possible state is reachable from every
+other state in finite time. \cite{NewmanBarkema1999} \cite{Katzgraber2011}\\
+Otherwise the samples might not be representative for the whole system.
 
 \subsection{Monte Carlo Algorithms}
-    \subsubsection{Metropolis}
-        A Metropolis Monte Carlo\cite{Metropolis1953} simulation of an
-        Ising model will choose a random spin, calculate the energy change
-        \(\Delta \hat H\) defined in eq. \eqref{eq:dH} that would result
-        from a flip of that spin and excute the flip with the probability \(A\)
-        eq. \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
+    \paragraph{Metropolis}
+        Let \(\Delta \hat H(\mu,\nu)\) be the energy difference between
+        the states \(\mu\) and \(\nu\)
         \begin{equation}
-            \Delta \hat H = \hat H(\nu) - \hat H(\mu)\\
-            \label{eq:dH}
+            \Delta \hat H = \hat H(\nu) - \hat H(\mu)
         \end{equation}
+        The Metropolis algorithm \cite{Metropolis1953} chooses the transition
+        probability like eq. \ref{eq:metropolis}
         \begin{equation}
@@
         \end{equation}
-        So if a transition lowers the energy it is always done. This
-        results in a high ratio between chosen spins and flipped spins.
-        Therefore it minimizes the calculations needed for a change of
-        the state.
+        A Metropolis Monte Carlo simulation of an Ising model will choose a
+        random spin, calculate the energy change \(\Delta \hat H\) that would
+        result from a flip of and excute the flip with the probability \(A\).
+        \cite{NewmanBarkema1999} \cite{Katzgraber2011}
 
-    \subsubsection{Wolff}
+    \paragraph{Wolff}
         Close to the critical temperature \(T_c\) the Metropolis
@@
         For an Ising model the Wolff algorithm builds a cluster of sites
-        starting with a random site and adding neighboring sites of the
-        same spin with probability \(P_{\mathrm{add}}\) from eq. \eqref{eq:wolffAdd}
-        \begin{equation}
-            P_{\mathrm{add}} = 1-\exp\brac{-2\beta J}
-            \label{eq:wolffAdd}
-        \end{equation}
-        Where \(J\) is the coupling constant (explained in section
+        starting with an random seed and adding neighboring sites with
+        the same spin with probability
+        \(P_{\mathrm{add}} = 1-\exp\brac{-2\beta J}\)
+        where \(J\) is the coupling constant (explained in section
         \ref{ssec:isingmodel}). The neighboring sites of the added sites
@@
         will only contain very few sites.
-        Both situaitions have no advantage against the Metropolis algorithm.\\
-        So one would activate this algorithm near the critical temperature
-        but use a simple Metropolis algorithm at high and low temperatures.
+        Both situaitions have no advantage against the Metropolis algorithm.
 
-    \subsubsection{Parallel Tempering}
-        %~ The main aim is to obtain the critical temperatures
-        %~ \(T_c\) for different disorder paramters \(\sigma\).
-        %~ Therefore it is necessary to simulate for many temperatures,
-        %~ so that \emph{Parallel Tempering}\footnote{Before R. H.
-            %~ Swendsen published this paper, a algorithm \(MC^3\) was
-            %~ already published with the same idea. [citation needed]}
-        %~ \cite{ParallelTempering1986} is a suited algorithm.
-        Parallel Tempering\cite{ParallelTempering1986} simulates many identical systems at different
+    \paragraph{Parallel Tempering}
+        The main aim is to obtain the critical temperatures
+        \(T_c\) for different disturbance paramters \(\sigma\).
+        Therefore it is necessary to simulate for many temperatures,
+        so that \emph{Parallel Tempering}\footnote{Before R. H.
+            Swendsen published this paper, a algorithm \(MC^3\) was
+            already published with the same idea. [citation needed]}
+        \cite{ParallelTempering1986} is a suited algorithm. Parallel
+        Tempering simulates many identical systems at different
         temperatures and periodically swaps the spin configurations
         between two neighboring temperatures with probability \(P\) from
-        eq. \eqref{eq:partemp} \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+        eq. \ref{eq:partemp} \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
         \begin{equation}
@@
         temperatures are far smaller because their spin configuration
-        gets often replaced by an other uncorrelated configuration. In
-        many cases the more important advantage is, that a system which
-        is trapped in a local minimum at a given temperature, can travel
-        to higher temperatures, leave it's local minimum and cool down
-        again in a lower minimum.\\
-        In the case of a ferromagnetic Ising model the risk to get trapped
-        in an local energy minimum is very low. Though the autocorrelation
-        decreases significantly. In the scope of this thesis this comes
-        for no cost, because one has to simulate for many temperatures
-        to determine the critical temperature. The additional calculations
-        to determine wheather to swap configurations or not are small in
-        comparison with those that would be needed to generate a new
-        uncorrelated state without \emph{parallel tempering}.
+        get often replaced by other uncorrelated configurations. And in
+        many cases the more important advantage is that a system which
+        is trapped in a local minimum at a given temperature can travel
+        to higher temperatures leave it's local minimum and cool down
+        again in a lower minimum.
 
-    \subsubsection{Implementation Details}
+    \paragraph{Implementation Details}
         Here a mixture of the above three algorithms is used.
         Each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
-        and one parallel tempering swap are performed. Where \(N\) is the
-        count of sites.\\
-        Because it is not known before, where the critical temperatures
-        \(T_c\) are located, the Wolff cluster algorithm is used for
-        every temperature. The speed up at criticality is worth the
-        moderate slow down at other temperatures.
+        and one Parallel Tempering swap are performed.
+%~ Monte Carlo Simulationen:\\
+    %~ Wolff-Cluster Algorithmus \cite{Wolff1989} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
+    %~ Metropolis Sweep \cite{Metropolis1953} (siehe auch \cite[S. xx]{NewmanBarkema1999}),
+    %~ Parallel Tempering \cite{ParallelTempering1986} (siehe auch \cite[S. xx]{NewmanBarkema1999} \cite[S. xx]{Katzgraber2011})\\
 
 \subsection{Equilibration- and Autocorrelation Time}
-\label{ssec:eqtime}
     To generate an equilibrium state one starts with an arbitrary state
@@
     the equilibrium is reached after approximately \(N=50\) sweeps for
-    either an initial condition of all spins up and all spins random. It
-    does not harm to double that value to be save.
+    either a initial condition of all spins up and all spins random. It
+    does no harm to double that value to be save.
     \begin{figure}[htbp]
@@
                 \label{sfig:equiandauto:equiE}
-                \includegraphics[width=0.47\textwidth]{plots/equiE}
+                \includegraphics[width=0.45\textwidth]{plots/equiE}
         }
@@
                 \label{sfig:equiandauto:autoM}
-                \includegraphics[width=0.47\textwidth]{plots/autoM}
+                \includegraphics[width=0.45\textwidth]{plots/autoM}
         }
         \caption[Examples for equilibration and autocorrelation]
-        {
-            \subref{sfig:equiandauto:equiE} Example of a Ising system
-                \(L=64\) reaching equilibrium at \(T=2.36\) and
-            \subref{sfig:equiandauto:autoM} the autocorrelation of an
-                Ising system \(L=64\) at \(T=2.40\) (only Metropolis
-                sweeps -- otherwise the decline is too steep to show)
-                on half logarithmic axis.
-                The straight line is a exponential fit \(\exp(-t/\tau)\)
-                with \(\tau = 342(1)\).
+                {\subref{sfig:equiandauto:equiE} Example of a Ising
+                    system reaching equilibrium at \(T=2.36\) and
+                 \subref{sfig:equiandauto:autoM} the
+                    autocorrelation of an Ising system at \(T=2.40\)
+                    (only Metropolis sweeps).
                 }
         \label{fig:equiandauto}
-    \end{figure}\\
+    \end{figure}
+
     Because every state is generated from the state before, measurements
     of subsequent states are correlated. To determine when two states
-    are independet, one calculates the normalized autocorrelation function
-    \(\frac{\chi(t)}{\chi(0)}\), which should decay exponentially
-    \(\chi(t) \propto \exp(t/\tau)\). This is visible in the half
-    logarithmic plot \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
-    To get the autocorrelation time one can either fit a exponential
-    function \(\exp(-t/\tau)\) like in fig \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
-    or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
+    are independet, one calculates the autocorrelation function
+    \(\chi(t)\) like in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
+    and integrates it to get the autocorrelation time \(\tau = \int \chi(t) \de t\).
     \(\tau\) is an estimate after which time two samples are not
@@
     \(2\tau\) sweeps between two measurements.
-    The autocorrelation time is of course dependent on the temperature.
-    At high temperatures the fluctuations are strong and subsequent
-    states are more dissimilar and therefore less correlated than at low
-    temperatures, where less spins are flipping. But the longest
-    autocorrelation times are encountered at the critical temperature.
-    This effect is called \emph{critical slowing down} and is
-    characterized by the \emph{dynamical critical exponent} \(z\)
-    \cite{SwendsenWang1987}. The dependence of the autocorrelation time
-    \(\tau\) on the system size \(L\) is then given by \(\tau \propto L^z\).

### 2013-07-05 Tex/chapters/model.tex
Displacement Skizze verbessert
plots etwas getweakt

--- 2013-07-01 Tex/chapters/model.tex
@@
-\subsection{The Disordered Ising Model}
-\label{ssec:isingmodel}
-    The examined model is a modified 2D Ising model.
-    First, let's define the Ising model and then explain the modifications.
-    The Ising model is a square lattice with edge length \(L\) and
-    \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
-    spin can take a value \(s \in \{-1,+1\}\) and interacts with it's
-    nearest neighbors described by the Hamiltonian from eq. \eqref{eq:hamiltonian}
-    \begin{equation}
-        \hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - H \sum_i s_i
-        \label{eq:hamiltonian}
-    \end{equation}
-    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are nearest
-    neighbors. And \(J_{ij}\) is the coupling constant between \(i\) and
-    \(j\). If \(J_{ij} > 0 \forall i,j\) the model resembles a ferromagnet.
-    \(H\) denotes the outer magnetic field.\\
-    In this thesis \(H=0\). The most important modification is, that
-    the sites of the square lattice are displaced. The
-    displacement is randomly Gauß distributed with the standard
-    deviation \(\sigma\). That is, the \(x\) and \(y\) coordinates of the
-    sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
-    from a Gauß distribution
-    \[f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}\]
-    \[x \to x + \Delta x\]
-    \[y \to y + \Delta y\]
-    This \(\sigma\) is also called \emph{disorder parameter} in the following.
-    Because most sites will only have one nearest neighbor after the
-    displacement, the lattice would collapse to many very small clusters.
-    To avoid this, the new "nearest" neighbors are those sites connected
-    by an edge. The edges are constructed according to
-    one of the two in section \ref{ssec:graphtypes} defined rules,
-    so that the lattice represents a proximity graph. Note that edges
-    of a proximity graph do not cross each other, hence the 2D character
-    of the lattice is preserved. The coupling constant \(J\) gets
-    identified with edge weights. The weight of an edge \(E_{ij}\) is
-    \(J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean
-    distance between the nodes \(i\) and \(j\). The free parameter
-    \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.
-    The boundary is periodic i.e. nodes near the right edge can be
-    connected to nodes near the left edge and vice versa. Analogous the
-    top and bottom edges are connected. One can imagine that the model
-    lives on the surface of a torus.\\
-    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
-    for which exists an analytic solution \cite{Onsager1944}. And for
-    \(\sigma \gtrsim 1\) the nodes are distributed randomly. This case
-    is studied for constant \(J\) on the Delaunay triangulation\cite{Janke1994}.\\
+%~ \subsection{Model and Implementation}
+%~ I will desribe the model in this section in a bottom-up fashion.
+%~ First describing all parts and then connecting them.
 
+%~ \subsubsection{Graphs}
+    %~ A graph is a set of nodes \(V\) and edges \(E\).
 \subsection{Gabriel- and Relative Neighborhood Graph}
 \label{ssec:graphtypes}
-    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\).\\
     All here mentioned graph types are \emph{proximity graphs}. They are
@@
     lattices with nearest neighbor relationships, like the Ising model
-    from the section \ref{ssec:isingmodel}.
-    In this thesis the distance is always determined by the Euclidean
-    metric in two dimensions, though in principle every metric in any
-    dimension can be used.\\
-
-    The Gabriel graph \cite{Gabriel1969} is a subgraph of the
-    Delaunay triangulation. Two nodes \(i\) and \(j\) with distance
-    \(d_{ij}\) are connected with an edge, if a circle with it's
-    center on half way between \(i\) and \(j\) and radius
+    which will be described in more detail in section
+    \ref{ssec:isingmodel}.\\
+    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
+    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
+    \(d_{ij}\) are connected with an edge if a circle with it's
+    center on the middlepoint between \(i\) and \(j\) and radius
     \(r = \frac d 2\) contains no other nodes. This area will be
@@
     \ref{fig:lunes}\subref{sfig:lunes:def}.\\
-    The Relative Neighborhood graph \cite{Toussaint1980} is a
-    subgraph of the Gabriel graph. Two nodes \(i\) and \(j\) with
-    distance \(d_{ij}\) are connected, if no other node is in the
+    The Relative Neighborhood Graph \cite{Toussaint1980} is a
+    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
+    distance \(d_{ij}\) are connected if no other node is in the
     \emph{lune}. The lune is defined as the intersection of two
@@
         }
+        \subfigure[Gabriel graph example][]{
+                \label{sfig:lunes:gg}
+                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
+        }
         \subfigure[Relative Neighborhood graph example][]{
@@
         }
-        \subfigure[Gabriel graph example][]{
-            \label{sfig:lunes:gg}
-            \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
-        }
         \caption[Gabriel - and Relative Neighborhood Graph]
-        {
-            \subref{sfig:lunes:def} Lunes of Relative Neighborhood
-                Graph (hatched region) and
-                Gabriel Graph (cross hatched region)
-            \subref{sfig:lunes:rng} Example of a Relative
-                Neighborhood Graph on periodic boundary conditions.
-                Periodic nodes are dashed.
+                {\subref{sfig:lunes:def} Lunes of Gabriel Graph (red)
+                    and Relative Neighborhood Graph (blue and red).
                  \subref{sfig:lunes:gg} Example of a Gabriel Graph on
@@
                     dashed.
-        }
+                 \subref{sfig:lunes:def} Example of a Relative
+                    Neighborhood Graph on periodic boundary conditions.
+                    Periodic nodes are dashed.}
         \label{fig:lunes}
-    \end{figure}\\
-    To construct these graphs the simple way is to test for each
-    pair of nodes if any other node lies in
-    the lune of the pair. That is of complexity \(O (N^3)\), because
-    there are \(N(N-1)\) pairs and for each \(N-2\) nodes to test. So
-    the product is of order \(O(N^3)\)\\
+
+    \end{figure}
+
+    To construct these graphs the simple way is to test for every
+    pair of nodes for every node if it lies in the lune of the pair.
+    That is of complexity \(O (n^3)\).\\
     To reduce the complexity one can first create a Delaunay
-    Triangulation in complexity \(O (N \log N)\)
-    \cite{RNGCell} and test the criterion for each edge, because
-    the Delaunay triangulation is a supergraph of both. But the
-    implementation of a Delaunay triangulation algorithm is not trivial
-    and the generation of the graphs is not time critical in the scope
-    of this bachelor thesis.\\
-    So a trade off is to use basically the simple method but only test
+    Triangulation in complexity \(O (n \log n)\)
+    \cite{Leach1992} and test the criterion for each edge, because
+    the Delaunay Triangulation is a supergraph of both. But the
+    implementation of a Delaunay Triangulation algorithm is not
+    trivial and the generation of the graphs is not time critical in
+    the scope of this bachelor thesis.\\
+    So a tradeoff is to use basicly the simple method but only test
     the criterion for nodes which are near to the lune and abort if
@@
     near the lune one can subdivide the area in \emph{cells} and save
-    for each cell a list with nodes lying inside it like presented in
-    \cite{RNGCell}.
-    Now it is just necessary to test the nodes in the cells which
+    for each cell a list with nodes lying inside it \cite{RNGCell}.
+    Now it is just neccessary to test the nodes in the cells which
     resemble a rectangular bounding box of the lune. Most pairs will be
@@
     Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
-    over \(15\) respectively \(40\). Though the complexity is still of
-    order \(O(N^2)\) in the best case, because for every pair at least
-    one check has to be performed.
+    over \(15\) respectivly \(40\). But no further analysis was made.
+
+\subsection{Model}
+\label{ssec:isingmodel}
+    The used model is a modified 2D Ising model where the \(N\) sites
+    are displaced nodes of a square lattice of edge length \(L\) with
+    periodic boundary conditions. The displacement is randomly gauss
+    distributed with the standard deviation \(\sigma\). This \(\sigma\)
+    is also called \emph{disturbance paramter} in the following.
+    The hamiltonian of the Ising model is
+    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
+    where \(\avg{i,j}\) refers to nodes connected  by edges.
+    The edges are constructed according to the in section
+    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
+    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
+    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
+    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
+    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
+    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
+    for which exists an analytical solution \cite{Onsager1944}.\\
+
+    For evaluation the Monte Carlo simulation is is run till the system
+    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
+    and the magnetisation per site \(m\) and energy per site \(E\)
+    are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
+    denotes the \emph{autocorrelation time} after which two states of
+    the system are not correlated anymore.
+    For every observable \(O\) the expected value \(\avg{O}\) is averaged
+    over different randomly generated lattices \(\overline{\avg{O}}\). The
+    errors are estimated by bootstrapping.
+
+\subsection{Critical Temperature $T_c$ and Critical Exponents}
+\label{ssec:finitesize}
+    The searched for property -- the critical temperature \(T_c\)
+    -- is only defined for infinite systems, hence every computer
+    simulation will show some \emph{finte size effects}.
+    %[vielleicht Bild von intensiver Größe?]
+    Despite of this one can obtain \(T_c\) by finite size scaling
+    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
+    exponents. The critical exponents should not be influenced by the
+    disturbance paramter \(\sigma\) [citation needed]. So they will be
+    used for consistency cross checking and comparision with the known
+    exact values \cite[S. 59]{Pelissetto2002}.\\
+    %~ [theorie mit dem Collaps]
+    %~ [Erklärung autoscale]
+    %~ [Am besten hier direkt die ganze Auswertung rein]
+    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Example of a datacollapse to determine critical exponents][]{
+                \label{sfig:collapse_s_0}
+                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
+        }
+        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
+                \label{sfig:binder_fit_s_0}
+                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        }
+        \caption[Examples of determining critical temperature and exponents]
+                {\subref{sfig:collapse_s_0}
+                 \subref{sfig:binder_fit_s_0} Binder cumulant fitted with
+                    polynom of degree 4 in vincinity of \(T_c\)
+                    (the errorbars are too small to see)}
+        \label{fig:binder_fit_s_0}
+    \end{figure}
+    Though if one is just interested in the critical Temperature, an
+    easier approach is to find the intersections of the Binder cumulants
+    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
+    system sizes \(L=\sqrt N\).
+    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
+    the intersection.
+    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
+    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
+    To determine \(T_c\) the intersections are averaged and the standard
+    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
+    is in very good agreement with the exact solution
+    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
+
+    % The arithmetic average of the intersections are plotted [hier schon?]
+    %~ [Und den rest der Auswertung]
+
+% Erwahnen, dass T_c Graph so aussieht, wie degree graph
+% mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
+% cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52

### 2013-07-05 Tex/chapters/monte_carlo.tex
plots etwas getweakt

@@
     the equilibrium is reached after approximately \(N=50\) sweeps for
-    either a initial condition of all spins up and all spins random. It
-    does no harm to double that value to be save.
+    either an initial condition of all spins up and all spins random. It
+    does not harm to double that value to be save.
     \begin{figure}[htbp]
@@
     of subsequent states are correlated. To determine when two states
-    are independet, one calculates the autocorrelation function
-    \(\chi(t)\) like in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
-    and integrates it to get the autocorrelation time \(\tau = \int \chi(t) \de t\).
+    are independet, one calculates the normalized autocorrelation function
+    \(\frac{\chi(t)}{\chi(0)}\) like in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
+    and integrates it to get the autocorrelation time \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
     \(\tau\) is an estimate after which time two samples are not

### 2013-07-05 Tex/chapters/model.tex
Alternative zum Poly deg 4 Fit: Spline
sieht besser aus, liefert aber nicht viel bessere Ergebnisse
sollte aber robuster sein

@@
                 {\subref{sfig:collapse_s_0}
-                 \subref{sfig:binder_fit_s_0} Binder cumulant fitted with
-                    polynom of degree 4 in vincinity of \(T_c\)
-                    (the errorbars are too small to see)}
+                 \subref{sfig:binder_fit_s_0} Binder cumulant interpolated
+                    with cubic splines (the errorbars are too small to see)}
         \label{fig:binder_fit_s_0}
@@
     system sizes \(L=\sqrt N\).
-    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
-    the intersection.
-    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
+    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+    for the measured points.
+    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
     \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
-    To determine \(T_c\) the intersections are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
+    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
+    are averaged and the standard
+    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
     is in very good agreement with the exact solution

### 2013-07-05 auswertung/fitPolyAndFindIntersectionSpline.py

@@ -1,0 +1,155 @@
+#!/usr/bin/env python2
+# -*- coding: UTF-8 -*-
+
+import sqlite3
+import numpy as np
+from subprocess import call
+import os
+import logging
+from itertools import combinations
+from scipy import interpolate
+from scipy import optimize
+
+import warnings
+warnings.simplefilter('ignore', np.RankWarning)
+np.seterr(all='ignore')
+
+logging.basicConfig(level=logging.INFO,
+                format='%(asctime)s -- %(levelname)s :: %(message)s',
+                datefmt='%d.%m.%YT%H:%M:%S')
+
+class BinderIntersections():
+
+    def __init__(self, directory, database="data.db", deg=4 ):
+        self.deg = deg
+        self.directory = directory
+        self.conn = sqlite3.connect(database)
+
+    def getBinderForSigmaAndL(self, sigma, L):
+        c = self.conn.cursor()
+        c.execute('SELECT T,binder,binderErr FROM calculated_data\
+            WHERE sigma = ? AND L = ? ORDER BY T ASC',
+                                         (sigma, L))
+
+        x = c.fetchall()
+
+        dy = [i[2] for i in x if i[1]]
+        y = [i[1] for i in x if i[1]]
+        x = [i[0] for i in x if i[1]]
+        return x, y, dy
+
+    def findIntersection(self, f, x_down, x_up):
+        return optimize.brentq(f, x_down, x_up)
+
+    def getIntersection(self, sigma, L1, L2, write=True, down=2.15, up=2.4):
+        self.down = down
+        self.up = up
+
+        x1,y1,dy1 = self.getBinderForSigmaAndL(sigma, L1)
+        x2,y2,dy2 = self.getBinderForSigmaAndL(sigma, L2)
+        f1 = interpolate.interp1d(x1,y1,kind="cubic")
+        f2 = interpolate.interp1d(x2,y2,kind="cubic")
+
+        if write:
+            self.writeForGnuplot(f1, f2, x1, x2, y1, y2, dy1, dy2, L1, L2, sigma)
+
+        x = self.findIntersection(lambda x: f1(x) - f2(x), down, up)
+        y = f1(x)
+        return x,y
+
+    def writeForGnuplot(self, f1, f2, x1, x2, y1, y2, dy1, dy2, L1, L2, sigma):
[…]

### 2013-07-05 Tex/chapters/model.tex
normierte T_c

@@
         }
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
-                \label{sfig:binder_fit_s_0}
-                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        \caption[Examples of determining critical temperature and exponents]
+                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
+                    with cubic splines (the errorbars are too small to see)
+                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
                 }
-        \caption[Examples of determining critical temperature and exponents]
-                {\subref{sfig:collapse_s_0}
-                 \subref{sfig:binder_fit_s_0} Binder cumulant interpolated
-                    with cubic splines (the errorbars are too small to see)}
         \label{fig:binder_fit_s_0}
@@
     In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
-    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
+    \(\sigma=0\). The cumulants intersect at \(\approx 2.27 k_{B}\). For
+    the sake of simplicity let the Boltzmann constant \(k_{B}=1\) in the
+    following.
     To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
     are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
-    is in very good agreement with the exact solution
+    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\),
+    which is in good agreement with the exact solution
     \(T_c = 2.2691...\) \cite{Onsager1944}.\\
+    Because \(T_{c}\) is dependend on \(J\) and hence also on the count
+    of bounds, the values of \(T_{c}\) will be normalized by the mean
+    sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
 

### 2013-07-05 Tex/chapters/model.tex
Bild als Beispiel zum finite size smear out und für sich ändernde Tc

--- 2013-07-05 Tex/chapters/model.tex
@@
         \caption[Gabriel - and Relative Neighborhood Graph]
-                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
+        {
+            \subref{sfig:lunes:def} Lunes of Relative Neighborhood
                 Graph (hatched region) and
                 Gabriel Graph (cross hatched region)
-                 \subref{sfig:lunes:def} Example of a Relative
+            \subref{sfig:lunes:rng} Example of a Relative
                 Neighborhood Graph on periodic boundary conditions.
@@
     Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
-    over \(15\) respectivly \(40\). But no further analysis was made.
+    over \(15\) respectivly \(40\). Though the complexity is still of
+    order \(O(N^2)\) in the best case, because for every pair at least
+    one check has to be performed.
 
-\subsection{Model}
+\subsection{The Disordered Ising Model}
 \label{ssec:isingmodel}
-    The used model is a modified 2D Ising model where the \(N\) sites
+    The used model is a modified 2D Ising model where the \(N=L^2\) sites
     are displaced nodes of a square lattice of edge length \(L\) with
@@
     are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
-    denotes the \emph{autocorrelation time} after which two states of
-    the system are not correlated anymore.
-    For every observable \(O\) the expected value \(\avg{O}\) is averaged
-    over different randomly generated lattices \(\overline{\avg{O}}\). The
-    errors are estimated by bootstrapping.
+    denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
+    For every observable \(O\) the expected value \(\avg{O}\) is determined
+    as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
+    \(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
+    random proximity graphs with the same disorder paramter \(\sigma\)
+    are then averaged to \(\overline{\avg{O}}\). The errors are estimated
+    by bootstrapping.
 
@@
     exponents. The critical exponents should not be influenced by the
-    disturbance paramter \(\sigma\) [citation needed]. So they will be
+    disorder paramter \(\sigma\) [citation needed]. So they will be
     used for consistency cross checking and comparision with the known
     exact values \cite[S. 59]{Pelissetto2002}.\\
+    It is known, that for large \(L\) near the critical temperature the
+    equations \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
+    \eqref{eq:fsscaling:g} apply \cite[p. 145f]{Katzgraber2011}.
+    \begin{align}
+        \label{eq:fsscaling:m}
+        \avg{m_L} &= L^\frac{\beta}{\nu} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:fsscaling:chi}
+        \chi_L    &= L^\frac{\gamma}{\nu} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:fsscaling:g}
+        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
+    \end{align}
+    Where \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} is
+    the Binder cumulant and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
+    are unkown scaling functions. To find the exponents
+    \(\beta, \gamma, \nu\) and the critical temperature \(T_c\), one
+    varies them until the measured values of the observables collapse on
+    one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
+    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
+    Note that \(L=16\) is not used for the collapse, because it is a
+    rather small value such that eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
+    do not apply very good.\\
     %~ [theorie mit dem Collaps]
+    %~ [Erklaerung: was sind beta, gamma, nu]
     To accomplish the collapse in an semi-automatic and reproduceable
@@
         \centering
+        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
+            \label{sfig:gettingCrit:binder_fit_s_0}
+            \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        }
         \subfigure[Example of a datacollapse to determine critical exponents][]{
-                \label{sfig:collapse_s_0}
+            \label{sfig:gettingCrit:collapse_s_0}
             \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
         }
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
-                \label{sfig:binder_fit_s_0}
-                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        \caption[Examples of determining critical temperature and exponents]
+        {
+            The Binder cumulant \(g\) of an square lattice Ising model
+            (\(\sigma=0\))\\
+            \subref{sfig:gettingCrit:binder_fit_s_0} interpolated
+                with cubic splines (the errorbars are too small to see)\\
+            \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
+                size scaling
         }
-        \caption[Examples of determining critical temperature and exponents]
-                {\subref{sfig:collapse_s_0}
-                 \subref{sfig:binder_fit_s_0} Binder cumulant fitted with
-                    polynom of degree 4 in vincinity of \(T_c\)
-                    (the errorbars are too small to see)}
-        \label{fig:binder_fit_s_0}
-    \end{figure}
+        \label{fig:gettingCrit}
+    \end{figure}\\
     Though if one is just interested in the critical Temperature, an
     easier approach is to find the intersections of the Binder cumulants
-    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
-    system sizes \(L=\sqrt N\).
-    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
-    the intersection.
-    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
-    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
-    To determine \(T_c\) the intersections are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
-    is in very good agreement with the exact solution
-    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
+    \(g\) of different system sizes \(L\).
+    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+    is calculated for the measured points.
+    In fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
+    such an interpolation is plotted for \(\sigma=0\). The cumulants
+    intersect at \(\approx 2.27 k_{B}\). For the sake of simplicity let
+    the Boltzmann constant \(k_{B}=1\) in the following.
+    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
+    are averaged and the standard error is calculated. In this case one
+    gets \(T_c = 2.2689(2)\), which is in good agreement with the
+    exact solution from eq. \eqref{eq:exactTc} \cite{Onsager1944}.
+    \begin{equation}
+        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
+        \label{eq:exactTc}
+    \end{equation}
 

### 2013-07-05 Tex/chapters/results.tex
Einleitung zu Binder Werten bei Tc: g*

--- 2013-07-02 Tex/chapters/results.tex
@@
 is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
-and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
+and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
 per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
 \(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
-(see also \ref{ssec:eqtime}). The used values for different system sizes
-are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
-the \(t_{eq}\) values are generously rounded up to be on the safe side
-and the \(\tau\) values are determined as the maximum \(\tau\) over all
-simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
-and rounded up to the next integer.
-\begin{table}[htbp]
-    \center
-    \begin{tabular}{l r r r r r}
-        \toprule
-        \(L\)    & 16 &  32 &  64 & 128 & 256\\
-        \midrule
-        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
-        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
-        \bottomrule
-    \end{tabular}
-    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
-    \label{tab:tauAndTeq}
-\end{table}\\
+(see also \ref{ssec:eqtime}).
 For every observable \(O\) the expected value \(\avg{O}\) is determined
-as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
-or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
-calculated sweeps totals to
-\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
-The expected values \(\avg{O}\) for \(100\) different random proximity
-graphs with the same disorder parameter \(\sigma\) are then averaged to
-\(\overline{\avg{O}}\). Not only the seed to generate the new random
-realization of the proximity graph gets changed, but also the seed for
-the random numbers used in the Monte Carlo simulation and during the
-generation of the random start configuration of the spins.\\
-The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
-\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
-Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
-\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
-over different realizations of the random proximity graph, which are
-surely uncorrelated.
-Because every error mentioned in this thesis is of this type, it is not
-necessary to determine \(\tau\) for each observable. Therefore a good
-error estimate can be achieved by simple bootstrapping. Though one has
-to simulate enough uncorrelated states for each realization, to keep
-the \(\Delta \overline{\avg{O}}\) small.
-
-\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
-    % Sollte das hier rein?
-    Before the results are presented, a short analysis of the
-    autocorrelation time \(\tau\) is given, to illustrate the benefits
-    of the used Wolff cluster algorithm.\\
-    In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
-    the autocorrelation time for the magnetization per site \(m\) at \(\sigma=0\) is plotted.
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[in dependence on the temperature $T$][]
-        {
-            \label{fig:autocorr:temperatures}
-            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
-        }
-        \subfigure[in dependence on the system size $L$][]
-        {
-            \label{fig:autocorr:powerLaw}
-            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
-        }
-        \caption[The autocorrelation time $\tau$]
-        {
-            Dependece of the autocorrelation time $\tau$ on
-            \subref{fig:autocorr:temperatures} the temperature $T$ for
-                $\sigma=0$ and
-            \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
-                are the standard error determined by bootstrapping)
-        }
-        \label{fig:autocorr}
-    \end{figure}
-    The plateau at low temperatures is easy to understand considering the
-    effects of the Wolff algorithm. At low temperatures it flips nearly every
-    spin in every step, thus the correlation drops to zero after one sweep.
-    Alternatively the parallel tempering algorithm swaps spin configurations
-    with possibly different signs, thus having the same effect.
-    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
-    temperature. The cause is probably the effectiveness of the Wolff cluster
-    algorithm at \(T_c\).
-    Obviously the autocorrelation time \(\tau\) increases with the system
-    size. In fact it obeys a power law, which is the expected behaivior of
-    a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
-    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
-    over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
-    This exponent is much higher than the one of Wolff cluster
-    algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
-    So it represents the dynamical exponent for parallel tempering with
-    Metropolis above criticality and thus is not exactly a critical exponent.
-    Nevertheless it is interesting, that it obeys a power law just the same.
-    Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
-    at criticality.
+as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
+\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
+random proximity graphs with the same disorder paramter \(\sigma\)
+are then averaged to \(\overline{\avg{O}}\). The errors are estimated
+by bootstrapping \cite{Bootstrap}.
 
@@
     of the disordered Ising model in dependence of the disorder parameter
-    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
+    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of
     the system will jump and the susceptibility
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}
-    it is easy to see that the jump of \(\avg{|m|}\)
-    occurs at lower temperatures \(T\) for higher
+    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}
+    it is easy to see that the jump occurs at lower temperatures \(T\) for higher
     disorder parameters \(\sigma\) (here with a Relative Neighborhood graph).
@@
     But in the shown plots there occurs no real jump, but a continuous
-    decline. The jump is only present in infinite systems, hence no
-    computer simulation will show the exact behavior in the
-    thermodynamic limit. It will always show some \emph{finte size effects}.
+    decline. The jump is only present in infinite systems, hence every
+    computer simulation will show some \emph{finte size effects}.
     These finite size effects cause a "smearing out" of the phase
-    transition. This is stronger for smaller system sizes, as is visible
+    trasition. This is stronger for smaller system sizes, as is visible
     in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
@@
     exponents.
-    Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
-    varying coupling constants \(J\) suggest, that the
-    critical exponents should not be influenced by the disorder parameter
+    Studies on random lattices with variing coupling constants \(J\)
+    \cite{Lima2000} and without \cite{Janke1994} suggest, that the
+    critical exponents should not be influenced by the disorder paramter
     \(\sigma\). So they will be used for consistency cross checking and
-    comparison with the known exact values \cite[S. 59]{Pelissetto2002}.\\
+    comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\
     % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
-    For a more in depth look at finite size scaling, \cite{Norrenbrock2011}
-    offers a explanation.
     It is known, that for large \(L\) near the critical temperature the
     equations \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
-    \eqref{eq:fsscaling:g} apply.
+    \eqref{eq:fsscaling:g} apply \cite[p. 145f]{Katzgraber2011}.
     \begin{align}
@@
         \label{eq:fsscaling:g}
-        g          &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}} \propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
+        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \label{eq:binderCumulant}
+        g &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}}
     \end{align}
-    Where \(g\) from eq. \eqref{eq:fsscaling:g} is a normalized
+    Where \(g\) from eq. \eqref{eq:binderCumulant} is a normalized
     Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
-    are unknown scaling functions. To find the exponents
+    are unkown scaling functions. To find the exponents
     \(\beta, \gamma, \nu\) and the critical temperature \(T_c\), one
@@
     one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
-    collapse in fig.
-\ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
+    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
     Note that \(L=16\) is not used for the collapse, because it is a
@@
     To accomplish the collapse in an semi-automatic and reproduceable
-    way with an error estimate, the program
+    way with an error estimate, the programm
     \texttt{autoscale.py} \cite{autoscale2009} is used.
@@
         \centering
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]
-        {
+        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
             \label{sfig:gettingCrit:binder_fit_s_0}
@@
         }
-        \subfigure[Example of a datacollapse to determine critical exponents][]
-        {
+        \subfigure[Example of a datacollapse to determine critical exponents][]{
             \label{sfig:gettingCrit:collapse_s_0}
@@
     at \(T_c\) \cite{Binder1981}.
-    Because  the magnetization \(m\) is only measured for discrete values
-    of \(T\), \(g\) is also only known for these discrete values and has
-    to be interpolated to find a intersection. Therefore a cubic spline
-    interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
     is calculated for the measured points.
-    Cubic spline interpolation is a piece wise fitting of polynoms of
-    degree three which are joined under the condition to be at least two
-    times continuously differentiable.
     As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.
@@
     The evaluation of the Binder cumulant's intersections, yields the
-    critical temperatures \(T_c\).
-    In this section these \(T_c\) on either the Relative Neighborhood
-    graph or the Gabriel graph are compared. In the following figures,
-    the Relative Neighborhood graph will always be on the left side
-    and the Gabriel graph on the right side.
-    In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).
+    critical temperatures \(T_c\), which are plotted in
+    fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.
+    Further in fig. \ref{fig:Tc}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
+    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+    is plotted which is evidently correlated with \(T_c\).
+    That is plausible, because \(T_c\) is dependend on the coupling
+    constant \(J\) (compare \eqref{eq:exactTc}).\\
+    It seems reasonable to normalize the values of \(T_{c}\) by
+    \(\avg{\sum_{\avg{i,j}} J_{ij}}\) which yields the diagramms fig.
+    \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.
     \begin{figure}[htbp]
@@
         }
-        \caption[Critical Temperature over different disorder parameters]
-        {
-            Critical temperatures \(T_c\) over different
-            disorder parameters \(\sigma\) for
-            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc:GG} the Gabriel Graph.\\
-        }
-        \label{fig:Tc}
-    \end{figure}\\
-    One sees that the Relative Neighborhood graph on the left has
-    generally a lower critical temperature than the Gabriel. Also \(T_c\)
-    of the Relative Neighborhood graph decreases
-    monotonically while \(T_c\) of the Gabriel rises at first.
-    For big \(\sigma\) the displaced nodes approach the limit of randomly
-    distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
-    \(\sigma >> 1\).\\
-    A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
-    of \(T_c\) on the Gabriel graph. To understand that, one has to
-    consider the influence of the graph properties on the critical
-    temperature.\\
-    A characteristic property of a graph is it's degree \(K\).
-    The degree \(K\) of a graph -- sometimes called \emph{coordination number} --
-    is defined as the mean count of neighbors per node
-    \begin{equation}
-        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}
-        \label{eq:degree}
-    \end{equation}
-    Therefore the degree of the graphs at different \(\sigma\) is
-    plotted in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}.
-    \begin{figure}[htbp]
-        \centering
+
         \subfigure[][]
         {
-            \label{sfig:deg:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
+            \label{sfig:sumJ:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
         }
@@
         {
-            \label{sfig:deg:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GG_deg}
+            \label{sfig:sumJ:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
         }
@@
         {
-            \label{sfig:Tc_norm_deg:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg}
+            \label{sfig:Tc_norm:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
         }
@@
         {
-            \label{sfig:Tc_norm_deg:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
+            \label{sfig:Tc_norm:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
         }
-
-        \caption[Critical Temperature normalized by Degree of the Graph]
+        \caption[Critical Temperature over different disorder parameters]
         {
-            Top: Degree \(K\) of graph over different
-            disorder parameters \(\sigma\) for
-            \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:deg:GG} the Gabriel Graph.\\
-            Bottom: Critical temperatures normalized by degree over different
+            Top: Critical temperatures over different
             disorder parameters for
-            \subref{sfig:Tc_norm_deg:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc_norm_deg:GG} the Gabriel Graph.
+            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc:GG} the Gabriel Graph.\\
+            Middle: Mean sum of the coupling constants to all
+            neighbors over different disorder parameters for
+            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
+            Bottom: Normalized critical temperatures over different
+            disorder parameters for
+            \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc_norm:GG} the Gabriel Graph.
         }
-        \label{fig:Tc_deg}
+        \label{fig:Tc}
     \end{figure}\\
-    \(T_c\) and \(K\) are evidently correlated. This is not
-    unexpected. For example the Honeycomb lattice is of degree \(K=3\)
-    and for which exists an analytic solution \cite{Wannier1945}.
-    It has a critical temperature of
-    \begin{equation}
-        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
-        \label{eq:exactHCTc}
-    \end{equation}
-    This is lower than for the square lattice with degree 4.\\
-    It seems reasonable to normalize \(T_c\) by the degree of the underlying
-    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
-    Indeed the normalization eliminates the jump and reduces the
-    slope of the rising on the Gabriel graph. Hence it reduces differences
-    between the Relative Neighborhood graph and the Gabriel graph.\\
-    % Zitat, dass Janke das auch gemacht hat .. nochmal nachlesen
-    The jump of \(K\) and therefore the jump of \(T_c\) on the Gabriel graph is easily explained
+    % I don't know what all that means...
+    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
+    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
     by the definition of the Gabriel graph and it's aftereffects for
     the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
-    a small change of sigma causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
+    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
     To fully understand this, take four nodes forming a square. The edge
@@
         }
-        \caption[Anomaly of the Gabriel graph for small $\sigma$]
+        \caption[]
         {
@@
     \end{figure}\\
-    But the degree does not alone influence the behavior of \(T_c\).
-    Further \(T_c\) depends on the coupling
-    constant \(J\), which is obvious in eq. \eqref{eq:exactTc} and
-    \eqref{eq:exactHCTc}. Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
-    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
-    is plotted. This is a number which should combine the dependence on
-    the degree and the coupling constant, which is not equal for
-    every edge in this case.
-    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
-    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[][]
-        {
-            \label{sfig:sumJ:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
-        }
-        \subfigure[][]
-        {
-            \label{sfig:sumJ:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
-        }
-
-        \subfigure[][]
-        {
-            \label{sfig:Tc_normJ:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_normJ}
-        }
-        \subfigure[][]
-        {
-            \label{sfig:Tc_normJ:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_normJ}
-        }
-
-        \caption[Critical Temperature normalized by Mean Sum of the Coupling Constants]
-        {
-            Top: Mean sum of the coupling constants to all
-            neighbors over different disorder parameters for
-            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
-            Bottom: Critical temperatures normalized by mean sum of the
-            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
-            disorder parameters for
-            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
-        }
-        \label{fig:TcJ}
-    \end{figure}\\
-    % I don't know what all that means...
-    If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
-    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
-    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
-    decreasing with increasing disorder parameter \(\sigma\). Moreover
-    the forms of both curves are quite similar, but the
-    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
+    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
+    shows monotonically decreasing \(T_c\) with increasing disorder
+    parameter \(\sigma\). The forms of both curves are similar, but the
+    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
     is generally lower and spans over a bigger temperature range than
-    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
+    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
     % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
     % RNG: laengere Kanten -> weniger lokale effekte?
-    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
-    disorder has little influence on this normalized critical temperature.
-    Also both graph types have a steep decline after the plateau before
-    they approach an asymptotic limit for \(\sigma >> 1\)\\\\
-
-    %~ But once the degree of
-    %~ the graph and hence the mean sum of the coupling constants decreases,
-    %~ the normalized critical temperature decreases, too.\\
-    %~ In conclusion the critical temperature depends on the averaged sum
-    %~ of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
-    %~ normalizing it with this, the plots for both proximity graphs look
-    %~ similar.
+    For big \(\sigma\) the curve approaches the limit of randomly
+    distributed nodes, hence \(T_c\) is independet of \(\sigma\) for
+    \(\sigma >> 1\).\\
+    Also both graph types have a plateau at \(0 < \sigma < 0.1\). So
+    small disorder has little influence on the normalized critical temperature.
+    But once the degree of the graph and hence the mean sum of the coupling
+    constants decreases, the normalized critical temperature decreases, too.
     % The author is not sure what it means.
+    % mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
+    % cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
 
@@
     Anyway, two critical exponents are sufficient to determine the universality
-    class. Therefore this disordered Ising model is in the same universality
+    class. Therefore this disordered Ising modell is in the same universality
     class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
@@
             \midrule
-            Relative N.  & 0.0 & 1.007(2) & -1.740(2) & 0.130(1) \\
+            Relative N.  & 0.0 & 1.007(2) & -1.739(2) & 0.130(1) \\
                          & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
@@
         \end{tabular}
-        \caption{Critical exponents for different $\sigma$}
+        \caption{Critical exponents for different \(\sigma\)}
         \label{tab:critExp}
@@
 \subsection{Critical Value of the Binder Cumulant}
-    The value of the Binder cumulant at the critical point \(g_c\) is
+    The value of the Binder cumulant at the critical point \(g^*\) is
     depends strongly on boundary conditions but only weakly on the lattice
     structure \cite{BinderValue}. For periodic boundary conditions on a
-    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
+    square lattice it is \(g^* \approx 0.916\) according to \cite{BinderValue}
         \footnote{Note that \cite{BinderValue} uses an other definition of
@@
     Because the analysis of section \ref{ssec:binderIntersections}
-    yields \(g_c\) anyway, it is easy to check the consistency and
-    behavior of \(g_c\) in the disordered Ising model.\\
+    yields \(g^*\) anyway, it is easy to check the consistency and
+    behaivior of \(g^*\) in the disordered Ising modell.\\
     \begin{figure}[htbp]
@@
         }
-        \caption[Values of the Binder cumulant at the critical point $g_c$]
+        \caption[Values of the Binder cumulant at the critical point $g^*$]
         {
-            Values of the Binder cumulant at the critical point \(g_c\)
+            Values of the Binder cumulant at the critical point \(g^*\)
             for\\
@@
     \end{figure}\\
-    Considering both plots in fig. \ref{fig:TcG}, \(g_c\) is for low
-    \(\sigma\) obviously always bigger than the known value. Though the
-    deviation is less than \(1\%\). Perhaps this is some inherent flaw
-    of the cubic spline interpolation used to acquire these \(g_c\) values.
-    For bigger \(\sigma\) the uncertainty gets greater, but the values
-    do only differ by a few percent, hence even the big disorder and
-    definition of nearest neighbors via a proximity graph does not change
-    \(g_c\) much. This is the expected behavior.
 

### 2013-07-05 Tex/chapters/appendix.tex
Weiteres finite Size Beispiel fur den Anhang

@@
 \section{Finite Size Effects at the Example of the Specific Heat}
-\label{appendix:finiteSizeEffects}
 In fig. \ref{fig:smeared_out_appendix} the specific heat
@@
 \end{figure}
-
-\section{Finite Size Scaling at the Example of the Susceptibility and Magnetisation}
-\label{appendix:finiteSizeScaling}
-    In fig. \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:s_0_sus}
-    the magnetic susceptibility
-    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
-    is plotted and in \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:collapse_s_0_sus}
-    collapsed to determine the critical exponent \(\beta\).
-    Analog for the mean absolute magnetisation \(\avg{\abs{m}}\) in fig \ref{fig:gettingCrit:appendix}
-    \subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
-    to determine the critical exponent \(\gamma\).
-    Both are at \(\sigma=0\) and
-    both collapses reproduce the  critical exponent \(\nu\) and the
-    critical temperature \(T_c\) in good agreement with the before determined
-    values from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
-    and the analytically known values. This is a good cross check
-    for consistency.
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[Susceptibility $\chi$][]
-        {
-            \label{sfig:gettingCrit:s_0_sus}
-            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
-        }
-        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
-        {
-            \label{sfig:gettingCrit:collapse_s_0_sus}
-            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
-        }
-        \subfigure[Magnetisation $\avg{\abs{m}}$][]
-        {
-            \label{sfig:gettingCrit:s_0_meanM}
-            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
-        }
-        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
-        {
-            \label{sfig:gettingCrit:collapse_s_0_meanM}
-            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
-        }
-        \caption[Examples of determining critical temperature and exponents]
-        {
-            Examples for finite size scaling.
-        }
-        \label{fig:gettingCrit:appendix}
-    \end{figure}

### 2013-07-05 Tex/chapters/results.tex
Weiteres finite Size Beispiel fur den Anhang

@@
     \end{figure}\\
+    Considering both plots in fig. \ref{fig:TcG}, \(g_c\) is for low
+    \(\sigma\) obviously always bigger than the known value. Though the
+    deviation is less than \(1\%\). Perhaps this is some inherent flaw
+    of the cubic spline interpolation used to aquire these \(g_c\) values.
+    For bigger \(\sigma\) the uncertainty gets greater, but the values
+    do only differ by a few percent, hence even the big disorder and
+    definition of nearest neighbors via a proximity graph does not change
+    \(g_c\) much. This is the expected behaivior.
 

### 2013-07-05 Tex/chapters/monte_carlo.tex
Weitere Ausfuehrung zur autokorrelation, todo: plot tau uber T

--- 2013-07-01 Tex/chapters/monte_carlo.tex
@@
 this samples. In example the Monte Carlo integration chooses random
-points within the bounding box of the function and estimates the integral
-as the fraction of points below the function and points above multiplied
+points within the bounding box of the fuction and estimates the integral
+as the fraction of points below the function and points above muliplied
 by the area of the bounding box.
@@
 This can be achieved by \emph{Importance Sampling}. One
-generates random numbers according to some probability distribution, which
-yields more numbers in the range where the function to integrate has high
-values and weights the result accordingly.\\
+generates random numbers according to some probabilty distribution and
+weights the result accordingly.\\
 %~ To improve this method: \emph{Importance Sampling}
@@
 by generating random states.
-But it is difficult to create a random state of a physical system i.e. the
+But it is difficult to create random state of a physical system i.e. the
 Ising system in equilibrium, hence one uses \emph{Markov Chains} to
@@
 \subsection{Monte Carlo Algorithms}
-    \subsubsection{Metropolis}
-        A Metropolis Monte Carlo\cite{Metropolis1953} simulation of an
-        Ising model will choose a random spin, calculate the energy change
+    \paragraph{Metropolis}
+        A Metropolis Monte Carlo simulation of an Ising model will
+        choose a random spin, calculate the energy change
         \(\Delta \hat H\) defined in eq. \eqref{eq:dH} that would result
-        from a flip of that spin and execute the flip with the probability \(A\)
+        from a flip of that spin and excute the flip with the probability \(A\)
         eq. \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
@@
 
-    \subsubsection{Wolff}
-    \label{sssec:wolff}
+    \paragraph{Wolff}
         Close to the critical temperature \(T_c\) the Metropolis
@@
         will only contain very few sites.
-        Both situations have no advantage against the Metropolis algorithm.\\
+        Both situaitions have no advantage against the Metropolis algorithm.\\
         So one would activate this algorithm near the critical temperature
@@
 
-    \subsubsection{Parallel Tempering}
+    \paragraph{Parallel Tempering}
         %~ The main aim is to obtain the critical temperatures
@@
         %~ \cite{ParallelTempering1986} is a suited algorithm.
-        Parallel Tempering\cite{ParallelTempering1986} simulates many identical systems at different
+        Parallel Tempering simulates many identical systems at different
         temperatures and periodically swaps the spin configurations
@@
         to determine the critical temperature. The additional calculations
-        to determine weather to swap configurations or not are small in
+        to determine wheather to swap configurations or not are small in
         comparison with those that would be needed to generate a new
@@
 
-    \subsubsection{Implementation Details}
+    \paragraph{Implementation Details}
         Here a mixture of the above three algorithms is used.
@@
                 on half logarithmic axis.
-                The straight line is an exponential fit \(\exp(-t/\tau)\)
+                The straight line is a exponential fit \(\exp(-t/\tau)\)
                 with \(\tau = 342(1)\).
@@
     of subsequent states are correlated. To determine when two states
-    are independent, one calculates the normalized autocorrelation function
+    are independet, one calculates the normalized autocorrelation function
     \(\frac{\chi(t)}{\chi(0)}\), which should decay exponentially
@@
     The autocorrelation time is of course dependent on the temperature.
-    For example for the standard Metropolis algorithm the fluctuations
-    are strong at high temperatures and subsequent
+    At high temperatures the fluctuations are strong and subsequent
     states are more dissimilar and therefore less correlated than at low
@@
     \(\tau\) on the system size \(L\) is then given by \(\tau \propto L^z\).
-    As mentioned in section \ref{sssec:wolff}, the Wolff cluster algorithm
-    decreases \(z\) dramatically. This causes the course of the autocorrelation
-    time in dependence on temperature to change significantly as shown in
-    section \ref{sec:results}.

### 2013-07-05 Tex/chapters/results.tex
Weitere Ausfuehrung zur autokorrelation, todo: plot tau uber T

@@
 \(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
-(see also \ref{ssec:eqtime}).
+(see also \ref{ssec:eqtime}). The used values for different system sizes
+are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
+the \(t_{eq}\) values are generously rounded up to be on the safe side
+and the \(\tau\) values are determined as the maximum \(\tau\) over all
+simulated temperatures.
+\[\tau = \max_T \tau_T\]
+\begin{table}[htbp]
+    \center
+    \begin{tabular}{l r r r r r}
+        \toprule
+        \(L\)    & 16 &  32 &  64 & 128 & 256\\
+        \midrule
+        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
+        \(t_eq\) & 40 & 100 & 100 & 200 & 600\\
+        \bottomrule
+    \end{tabular}
+    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
+    \label{tab:tauAndTeq}
+\end{table}\\
+Obiviously the autocorrelation time \(\tau\) increases with the system
+size. In fact it obeys a power law, which is the expected bahaivior as
+mentioned in section \ref{ssec:eqtime}. In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
+the dynamical critical exponent \(z\) is determined as \(z=0.57(4)\).
+This exponent is much higher than the expectation. For the Wolff cluster
+algorithm at criticality, one would expect \(z=0.25\)\cite{NewmanBarkema1999}.
+This suggests that \emph{critical slowing down} is not an issue in this
+case and the autocorrelation time is limited by the slow decorrelation
+at low temperatures. A direct proof is given by fig. \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
+Apparently even parallel tempering can not compensate that. Probably
+because only one configuration swap between neighboring temperatures is
+performed each sweep. Those neighboring configurations at low temperatures
+have a magnetisation per site of \(m \approx \pm 1\), so there is a good
+chance, that the exchange does not change \(m\) (in case of same sign)
+and thus does not lower the autocorrelation function.
+\begin{figure}[htbp]
+    \centering
+    \subfigure[in dependence on the system size $L$][]
+    {
+        \label{fig:autocorr:powerLaw}
+        \includegraphics[width=0.45\textwidth]{plots/autocorrL}
+    }
+    \subfigure[in dependence on the temperature $T$][]
+    {
+        \label{fig:autocorr:temperatures}
+        \includegraphics[width=0.45\textwidth]{plots/autocorrT}
+    }
+    \caption[The autocorrelation time $\tau$]
+    {
+        Dependece of the autocorrelation time $\tau$ on\\
+        \subref{fig:autocorr:powerLaw} the system size $L$\\
+        \subref{fig:autocorr:temperatures} the temperature $T$
+    }
+    \label{fig:autocorr}
+\end{figure}\\
 For every observable \(O\) the expected value \(\avg{O}\) is determined
-as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
-\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
-random proximity graphs with the same disorder paramter \(\sigma\)
-are then averaged to \(\overline{\avg{O}}\). The errors are estimated
-by bootstrapping \cite{Bootstrap}.
+as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
+or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
+calculated sweeps totals to
+\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
+The expected values \(\avg{O}\) for \(100\) different random proximity
+graphs with the same disorder paramter \(\sigma\) are then averaged to
+\(\overline{\avg{O}}\).
+The errors are estimated by bootstrapping \cite{Bootstrap}.
 

### 2013-07-05 Tex/chapters/monte_carlo.tex
Autokorrelationsfunktions Beschreibung vervollständigt

@@
 
-    \paragraph{Wolff}
+    \subsubsection{Wolff}
+    \label{sssec:wolff}
         Close to the critical temperature \(T_c\) the Metropolis

### 2013-07-05 Tex/chapters/results.tex
Autokorrelationsfunktions Beschreibung vervollständigt

@@
 and the \(\tau\) values are determined as the maximum \(\tau\) over all
-simulated temperatures.
-\[\tau = \max_T \tau_T\]
+simulated temperatures and disorder parameters \(\tau = \max_{T,\sigma} \tau_{T,\sigma}\)
+and rounded up to the next integer. In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
+the autocorrelation time for \(\sigma=0\) is plotted.
+%The \emph{critical slowing down} is visible as a peak.
+The plateau at low temperatures is easy to understand considering the
+effects of the wolff algorithm. At low temperatures it flips nearly every
+spin in every step, thus the correlation drops to zero after one sweep.
+Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
+temperature. The cause is probably the effectiveness of the Wolff cluster
+algorithm at \(T_c\).
 \begin{table}[htbp]
@@
 Obiviously the autocorrelation time \(\tau\) increases with the system
-size. In fact it obeys a power law, which is the expected bahaivior as
-mentioned in section \ref{ssec:eqtime}. In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
-the dynamical critical exponent \(z\) is determined as \(z=0.57(4)\).
-This exponent is much higher than the expectation. For the Wolff cluster
-algorithm at criticality, one would expect \(z=0.25\)\cite{NewmanBarkema1999}.
-This suggests that \emph{critical slowing down} is not an issue in this
-case and the autocorrelation time is limited by the slow decorrelation
-at low temperatures. A direct proof is given by fig. \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
-Apparently even parallel tempering can not compensate that. Probably
-because only one configuration swap between neighboring temperatures is
-performed each sweep. Those neighboring configurations at low temperatures
-have a magnetisation per site of \(m \approx \pm 1\), so there is a good
-chance, that the exchange does not change \(m\) (in case of same sign)
-and thus does not lower the autocorrelation function.
+size. In fact it obeys a power law, which is the expected behaivior of
+a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
+In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
+over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
+This exponent is much higher than the one of Wolff cluster
+algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
+So it represents the dynamical exponent for parallel tempering with
+Metropolis above criticality and thus is not exactly a critical exponent.
+Nevertheless it is interesting, that it obeys a power law just the same.
+Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
+at criticality.
 \begin{figure}[htbp]
     \centering
+    \subfigure[in dependence on the temperature $T$][]
+    {
+        \label{fig:autocorr:temperatures}
+        \includegraphics[width=0.45\textwidth]{plots/autocorrT}
+    }
     \subfigure[in dependence on the system size $L$][]
@@
     }
-    \subfigure[in dependence on the temperature $T$][]
-    {
-        \label{fig:autocorr:temperatures}
-        \includegraphics[width=0.45\textwidth]{plots/autocorrT}
-    }
     \caption[The autocorrelation time $\tau$]
     {
-        Dependece of the autocorrelation time $\tau$ on\\
-        \subref{fig:autocorr:powerLaw} the system size $L$\\
-        \subref{fig:autocorr:temperatures} the temperature $T$
+        Dependece of the autocorrelation time $\tau$ on
+        \subref{fig:autocorr:temperatures} the temperature $T$ for
+            $\sigma=0$ and
+        \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
+            are the standard error determined by bootstrapping)
     }

### 2013-07-05 Tex/chapters/appendix.tex
Weitere Plots in den Anhang gehängt

--- 2013-07-02 Tex/chapters/appendix.tex
@@
     the magnetic susceptibility
-    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
+    \[\chi = \frac{1}{TN}\avg{\avg{E^2} - \avg{E}^2}\]
     is plotted and in \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:collapse_s_0_sus}

### 2013-07-05 Tex/chapters/results.tex
Große Umstrukturierung der Tc über Sigma section

@@
 \end{table}\\
+In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
+the autocorrelation time for \(\sigma=0\) is plotted.
+%The \emph{critical slowing down} is visible as a peak.
+The plateau at low temperatures is easy to understand considering the
+effects of the Wolff algorithm. At low temperatures it flips nearly every
+spin in every step, thus the correlation drops to zero after one sweep.
+Alternatively the parallel tempering algorithm swaps spin configurations
+with possibly different signs, thus having the same effect.
+Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
+temperature. The cause is probably the effectiveness of the Wolff cluster
+algorithm at \(T_c\).
 Obiviously the autocorrelation time \(\tau\) increases with the system
@@
         }
-
+        \caption[Critical Temperature over different disorder parameters]
+        {
+            Critical temperatures \(T_c\) over different
+            disorder parameters \(\sigma\) for
+            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc:GG} the Gabriel Graph.\\
+        }
+        \label{fig:Tc}
+    \end{figure}\\
+    One sees that the Relative Neighborhood graph on the left has
+    generally a lower critical temperature than the Gabriel. Also \(T_c\)
+    of the Relative Neighborhood graph decreases
+    monotonically while \(T_c\) of the Gabriel rises at first.
+    For big \(\sigma\) the displaced nodes approache the limit of randomly
+    distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
+    \(\sigma >> 1\).\\
+    A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
+    of \(T_c\) on the Gabriel graph. To understand that, one has to
+    consider the influence of the graph properties on the critical
+    temperature.\\
+    A characteristic property of a graph is it's degree \(K\).
+    The degree \(K\) of a graph -- sometimes called \emph{coordination number} --
+    is defined as the mean count of neighbors per node
+    \begin{equation}
+        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}
+        \label{eq:degree}
+    \end{equation}
+    Therefore the degree of the graphs at different \(\sigma\) is
+    plotted in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}.
+    \begin{figure}[htbp]
+        \centering
         \subfigure[][]
         {
-            \label{sfig:sumJ:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
+            \label{sfig:deg:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
         }
@@
         {
-            \label{sfig:Tc_norm:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
+            \label{sfig:Tc_norm_deg:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
         }
+
         \caption[Critical Temperature over different disorder parameters]
         {
-            Top: Critical temperatures over different
+            Top: Degree \(K\) of graph over different
+            disorder parameters \(\sigma\) for
+            \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:deg:GG} the Gabriel Graph.\\
+            Bottom: Critical temperatures normalized by degree over different
             disorder parameters for
-            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc:GG} the Gabriel Graph.\\
-            Middle: Mean sum of the coupling constants to all
-            neighbors over different disorder parameters for
-            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
-            Bottom: Normalized critical temperatures over different
-            disorder parameters for
-            \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc_norm:GG} the Gabriel Graph.
+            \subref{sfig:Tc_norm_deg:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc_norm_deg:GG} the Gabriel Graph.
         }
-        \label{fig:Tc}
+        \label{fig:Tc_deg}
     \end{figure}\\
-    % I don't know what all that means...
-    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
-    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
+    \(T_c\) and \(K\) are evidently correlated. This is not
+    unexpected. For example the Honeycomb lattice, for which exsists an
+    anlytical solution \cite{Wannier1945} and has a degree of 3, has a
+    critical temperature of
+    \begin{equation}
+        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
+        \label{eq:exactHCTc}
+    \end{equation}
+    This is lower than for the square lattice with degree 4.\\
+    It seems resonable to normalize \(T_c\) by the degree of the underlying
+    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
+    Indeed the normalisation eliminates the jump and reduces the
+    slope of the rising on the Gabriel graph. Hence it reduces differences
+    between the Relative Neighborhood graph and the Gabriel graph.\\
+    % Zitat, dass Janke das auch gemacht hat .. nochmal nachlesen
+    The jump of \(K\) and therefore the jump of \(T_c\) on the Gabriel graph is easily explained
     by the definition of the Gabriel graph and it's aftereffects for
@@
     \end{figure}\\
-    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
-    shows monotonically decreasing \(T_c\) with increasing disorder
-    parameter \(\sigma\). The forms of both curves are similar, but the
-    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
+    But the degree does not alone influence the behavior of \(T_c\).
+    Further \(T_c\) depends on the coupling
+    constant \(J\), which is obvious in eq. \eqref{eq:exactTc} and
+    \eqref{eq:exactHCTc}. Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
+    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+    is plotted. This is a number which should combine the dependence on
+    the degree and the coupling constant, which is not equal for
+    every edge in this case.
+    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
+    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:sumJ:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:sumJ:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
+        }
+
+        \subfigure[][]
+        {
+            \label{sfig:Tc_normJ:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_normJ}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:Tc_normJ:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_normJ}
+        }
+
+        \caption[Critical Temperature over different disorder parameters]
+        {
+            Top: Mean sum of the coupling constants to all
+            neighbors over different disorder parameters for
+            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
+            Bottom: Critical temperatures normalized by mean sum of the
+            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
+            disorder parameters for
+            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
+            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
+        }
+        \label{fig:TcJ}
+    \end{figure}\\
+    % I don't know what all that means...
+    If on normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
+    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
+    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
+    decreasing with increasing disorder parameter \(\sigma\). Moreover
+    the forms of both curves are quite similar, but the
+    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
     is generally lower and spans over a bigger temperature range than
-    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
+    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
     % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
     % RNG: laengere Kanten -> weniger lokale effekte?
-    For big \(\sigma\) the curve approaches the limit of randomly
-    distributed nodes, hence \(T_c\) is independet of \(\sigma\) for
-    \(\sigma >> 1\).\\
-    Also both graph types have a plateau at \(0 < \sigma < 0.1\). So
-    small disorder has little influence on the normalized critical temperature.
-    But once the degree of the graph and hence the mean sum of the coupling
-    constants decreases, the normalized critical temperature decreases, too.
+    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
+    disorder has little influence on this normalized critical temperature.
+    Also both graph types have a steep decline after the plateau before
+    they approache an asymptotic limit for \(\sigma >> 1\)\\\\
+
+    %~ But once the degree of
+    %~ the graph and hence the mean sum of the coupling constants decreases,
+    %~ the normalized critical temperature decreases, too.\\
+    %~ In conclusion the critical temperature depends on the averaged sum
+    %~ of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
+    %~ normalizing it with this, the plots for both proximity graphs look
+    %~ similar.
     % The author is not sure what it means.
-    % mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
-    % cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
 

### 2013-07-05 Tex/chapters/results.tex
gamma ermitteln, durch powerlaw fit durch chi_max

@@
 \end{table}\\
+For every observable \(O\) the expected value \(\avg{O}\) is determined
+as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
+or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
+calculated sweeps totals to
+\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
+The expected values \(\avg{O}\) for \(100\) different random proximity
+graphs with the same disorder parameter \(\sigma\) are then averaged to
+\(\overline{\avg{O}}\). Not only the seed to generate the new random
+realization of the proximity graph gets changed, but also the seed for
+the random numbers used in the Monte Carlo simulation and during the
+generation of the random start configuration of the spins.\\
+The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
+\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
+Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
+\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
+over different realizations of the random proximity graph, which are
+surely uncorrelated.
+Because every error mentioned in this thesis is of this type, it is not
+necessary to determine \(\tau\) for each observable. Therefore a good
+error estimate can be achieved by simple bootstrapping. Though one has
+to simulate enough uncorrelated states for each realization, to keep
+the \(\Delta \overline{\avg{O}}\) small.
+
+\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
+    % Sollte das hier rein?
+    Before the results are presented, a short analysis of the
+    autocorrelation time \(\tau\) is given, to illustrate the benefits
+    of the used Wolff cluster algorithm.\\
     In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
-the autocorrelation time for \(\sigma=0\) is plotted.
-%The \emph{critical slowing down} is visible as a peak.
-The plateau at low temperatures is easy to understand considering the
-effects of the Wolff algorithm. At low temperatures it flips nearly every
-spin in every step, thus the correlation drops to zero after one sweep.
-Alternatively the parallel tempering algorithm swaps spin configurations
-with possibly different signs, thus having the same effect.
-Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
-temperature. The cause is probably the effectiveness of the Wolff cluster
-algorithm at \(T_c\).
-Obiviously the autocorrelation time \(\tau\) increases with the system
-size. In fact it obeys a power law, which is the expected behaivior of
-a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
-In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
-over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
-This exponent is much higher than the one of Wolff cluster
-algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
-So it represents the dynamical exponent for parallel tempering with
-Metropolis above criticality and thus is not exactly a critical exponent.
-Nevertheless it is interesting, that it obeys a power law just the same.
-Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
-at criticality.
+    the autocorrelation time for the magnetization per site \(m\) at \(\sigma=0\) is plotted.
     \begin{figure}[htbp]
@@
         \label{fig:autocorr}
-\end{figure}\\
-For every observable \(O\) the expected value \(\avg{O}\) is determined
-as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
-or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
-calculated sweeps totals to
-\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
-The expected values \(\avg{O}\) for \(100\) different random proximity
-graphs with the same disorder paramter \(\sigma\) are then averaged to
-\(\overline{\avg{O}}\).
-All errorbars are estimated by bootstrapping\cite{Bootstrap} with 200
-bootstrap samples if not noted otherwise.
+    \end{figure}
+    The plateau at low temperatures is easy to understand considering the
+    effects of the Wolff algorithm. At low temperatures it flips nearly every
+    spin in every step, thus the correlation drops to zero after one sweep.
+    Alternatively the parallel tempering algorithm swaps spin configurations
+    with possibly different signs, thus having the same effect.
+    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
+    temperature. The cause is probably the effectiveness of the Wolff cluster
+    algorithm at \(T_c\).
+    Obviously the autocorrelation time \(\tau\) increases with the system
+    size. In fact it obeys a power law, which is the expected behaivior of
+    a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
+    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
+    over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
+    This exponent is much higher than the one of Wolff cluster
+    algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
+    So it represents the dynamical exponent for parallel tempering with
+    Metropolis above criticality and thus is not exactly a critical exponent.
+    Nevertheless it is interesting, that it obeys a power law just the same.
+    Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
+    at criticality.
 
@@
     of the disordered Ising model in dependence of the disorder parameter
-    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of
+    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
     the system will jump and the susceptibility
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}
+    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
     it is easy to see that the jump of \(\avg{|m|}\)
@@
     decline. The jump is only present in infinite systems, hence no
-    computer simulation will show the exact behaivior in the
+    computer simulation will show the exact behavior in the
     thermodynamic limit. It will always show some \emph{finte size effects}.
     These finite size effects cause a "smearing out" of the phase
-    trasition. This is stronger for smaller system sizes, as is visible
-    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
-    the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
+    transition. This is stronger for smaller system sizes, as is visible
+    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
+    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
     Despite of this one can obtain \(T_c\) by finite size scaling
@@
     Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
-    variing coupling constants \(J\) suggest, that the
-    critical exponents should not be influenced by the disorder paramter
+    varying coupling constants \(J\) suggest, that the
+    critical exponents should not be influenced by the disorder parameter
     \(\sigma\). So they will be used for consistency cross checking and
-    comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\
+    comparison with the known exact values \cite[S. 59]{Pelissetto2002}.\\
     % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
     For a more in depth look at finite size scaling, \cite{Norrenbrock2011}
-    offers a explanation.
+    offers an explanation.
     It is known, that for large \(L\) near the critical temperature the
@@
     monotonically while \(T_c\) of the Gabriel rises at first.
-    For big \(\sigma\) the displaced nodes approache the limit of randomly
+    For big \(\sigma\) the displaced nodes approach the limit of randomly
     distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
@@
     \end{figure}\\
-    \(T_c\) and \(K\) are evidently correlated. This is not
-    unexpected. For example the Honeycomb lattice, for which exsists an
-    anlytical solution \cite{Wannier1945} and has a degree of 3, has a
-    critical temperature of
-    \begin{equation}
-        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
-        \label{eq:exactHCTc}
-    \end{equation}
-    This is lower than for the square lattice with degree 4.\\
-    It seems resonable to normalize \(T_c\) by the degree of the underlying
-    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
-    Indeed the normalisation eliminates the jump and reduces the
-    slope of the rising on the Gabriel graph. Hence it reduces differences
-    between the Relative Neighborhood graph and the Gabriel graph.\\
-    % Zitat, dass Janke das auch gemacht hat .. nochmal nachlesen
-    The jump of \(K\) and therefore the jump of \(T_c\) on the Gabriel graph is easily explained
+    To understand the jump of \(T_c\), it seems to be sufficient to
+    understand the jump of \(K\), which is easily explained
     by the definition of the Gabriel graph and it's aftereffects for
     the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
-    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
+    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
     To fully understand this, take four nodes forming a square. The edge
@@
     \end{figure}\\
-    % I don't know what all that means...
-    If on normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
+    If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
     \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
@@
     Also both graph types have a steep decline after the plateau before
-    they approache an asymptotic limit for \(\sigma >> 1\)\\\\
-
-    %~ But once the degree of
-    %~ the graph and hence the mean sum of the coupling constants decreases,
-    %~ the normalized critical temperature decreases, too.\\
-    %~ In conclusion the critical temperature depends on the averaged sum
-    %~ of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
-    %~ normalizing it with this, the plots for both proximity graphs look
-    %~ similar.
-    % The author is not sure what it means.
+    they approach an asymptotic limit for \(\sigma >> 1\)\\\\
 
 \subsection{Critical Exponents}
-    For \(\sigma \in \{0,0.1,0.2,0.3,0.5,1.0\}\) a finite size scaling analysis was
+    A finite size scaling analysis was
     performed to determine the critical exponents \(\beta, \gamma, \nu\)
@@
     \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
-    values for all other \(\sigma\) should be the same as for \(\sigma = 0\)
-    like mentioned before in section \ref{ssec:finitesize}.
-    The values for \(\sigma\) are chosen to represent every interesting
-    region from fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}:
-    the plateau at small \(\sigma\), the steep decline and the plateau at
-    big \(\sigma\).\\
-    Like in tab. \ref{tab:critExp} to see, most values
-    are matching the expectations. Most \(\beta\) seem to be a bit too
-    big, but they are close enough to the expectations to be explained
-    by the fact that small systems (\(L=32,64\)) were used for the
-    analysis.
-    Anyway, two critical exponents are sufficient to determine the universality
-    class. Therefore this disordered Ising modell is in the same universality
-    class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
+    values for all other \(\sigma\) are expected be the same as for
+    \(\sigma = 0\) like mentioned before in section \ref{ssec:finitesize}.
+    Therefore it is sufficient to take a few samples to test if the
+    expectations are met. Hence 5 values of \(\sigma\) are analyzed,
+    which are chosen to represent every interesting region from fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}:
+    the analytically known value for \(\sigma = 0\), the in \cite{Janke1994}
+    examined limit for \(\sigma \gtrsim 1\), the plateau at small
+    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).\\
     \begin{table}[htbp]
@@
         \label{tab:critExp}
-    \end{table}
+    \end{table}\\
+    Like in tab. \ref{tab:critExp} to see, most values
+    are matching the expectations. Especially \(\nu\) and \(gamma\)
+    are always in very good agreement with their exact values. Because
+    there can never be to much cross and consistency checks, the ratio
+    \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
+    the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
+    The results are displayed in fig. \ref{fig:susCrossCheck}. The by this
+    method determined ratios confirm the by collapse obtained values.
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:susCrossCheck:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:susCrossCheck:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
+        }
+        \caption[Alternative Way Determining $\gamma$]
+        {
+            Cross checking the critical exponent $\gamma$ for
+                \subref{sfig:susCrossCheck:RNG} the Relative Neighborhood graph and
+                \subref{sfig:susCrossCheck:GG} the Gabriel graph.
+            Dotted lines are power law fits.
+        }
+        \label{fig:susCrossCheck}
+    \end{figure}\\
+    Despite the very good results for \(\nu\) and \(\gamma\), most of the
+    \(\beta\) seem to be a bit too big, but they are close enough to the
+    expectations to be consistent.
+    Maybe their deviations can be explained by the fact that small
+    systems (\(L=32,64\)) were used for the analysis, which introduce
+    some deviations, because the collapse works best for big system sizes.
+    Anyway, two critical exponents are sufficient to determine the
+    universality class \cite[p. 145]{Katzgraber2011}. Therefore this
+    disordered Ising model is in the same universality class as the
+    standard Ising ferromagnet.
 
@@
     \(\sigma\) obviously always bigger than the known value. Though the
-    deviation is less than \(1\%\). Perhaps this is some inherent flaw
-    of the cubic spline interpolation used to aquire these \(g_c\) values.
+    deviations are only very small. Perhaps this overestimation is caused
+    by the cubic spline interpolation used to acquire these \(g_c\) values.
     For bigger \(\sigma\) the uncertainty gets greater, but the values
@@
     definition of nearest neighbors via a proximity graph does not change
-    \(g_c\) much. This is the expected behaivior.
-
-%~ Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
+    \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
+    lattice structure has a minor effect on \(g_c\), the uncertainty of
+    \(g_c\) is too big, to show it. For a more in depth analysis, new
+    Monte Carlo simulations at \(T_c\) would be needed. But this is
+    beyond the scope of this thesis. Anyway the results are the expected
+    behaivior, because no major deviations from the value of \(g_c\) at
+    \(\sigma = 0\) occur at larger \(\sigma\).

### 2013-07-05 auswertung/db.py

@@ -153,7 +153,7 @@ class Database():
             Summation genau genug sein) der Autokorrelationsfunktion.
             vgl. \cite newman1999monte S. 62 (3.20)
         """
-        auto = numpy.correlate(m, m, mode='full')[len(m)-1:]
+        auto = numpy.correlate(m, m, mode='same')[len(m)-1:]
         x0 = auto[0]
         tau = sum(auto)/x0
         return tau
@@ -162,6 +162,39 @@ class Database():
     def bootstrap_stderr(x, n_resample, f):
         h = [f([choice(x) for _ in x]) for _ in range(n_resample)]
         return std(h)
+
+    def writeMax(self, name, val, valErr):
+        """! Sucht die T an den Maxima der Observalbe "val" """
+        directory = os.path.join(self.dataPath,"out")
+        if not os.path.exists(directory):
+            os.makedirs(directory)
+
+        c = self.conn.cursor()
+        Ts = sorted(self.getDifferent("T"))
+        Ls = sorted(self.getDifferent("L"))
+        Ss = sorted(self.getDifferent("sigma"))
+        numT = len(Ts)
+
+        for s in Ss:
+            with open(os.path.join(directory,name+"_s_"+str(s)+".dat"), "w") as f:
+                f.write("# L chi_max dChi_max\n")
+                for l in Ls:
+                    if valErr:
+                        c.execute('SELECT {0},{1} FROM calculated_data WHERE sigma = ? AND L = ? ORDER BY T ASC'.format(val, valErr), (s,l))
+                    else:
+                        c.execute('SELECT {0} FROM calculated_data WHERE sigma = ? AND L = ? ORDER BY T ASC'.format(val), (s,l))
+                    x = c.fetchall()
+                    if valErr:
+                        dx = [i[1] for i in x]
+                    else:
+                        dx = [0 for i in x]
+                    x = [i[0] for i in x]
+
+                    dx = [dx[j] for j in range(numT) if x[j]]
+                    x = [x[j] for j in range(numT) if x[j]]
+                    x_max = max(x)
+                    dx_max = dx[x.index(x_max)]
+                    f.write("{0} {1} {2}\n".format(l, x_max, dx_max))
 
     def writeForScalana(self, name, val, valErr):
         """! Sammelt die Werte die für Scalana und gibt sie
@@ -235,6 +268,7 @@ class Database():
 
     def writeVarForGnuplot(self):
[…]

### 2013-07-05 Tex/chapters/model.tex
Statt Bildern werden jetzt die Quelldateien verfolgt
makefile kümmert sich nun um Plot Erstellung, indem sie die
datendateien mit gnuplot zeichnet und mit eps2pdf für
pdflatex aufbereitet

--- 2013-07-05 Tex/chapters/model.tex
@@
 \subsection{Gabriel- and Relative Neighborhood Graph}
-\label{ssec:graphtypes}
-    All here mentioned graph types are \emph{proximity graphs}. They are
-    connecting nodes which are by some metric near to each other.
-    Hence they are suited to generalize problems defined on regular
-    lattices with nearest neighbor relationships, like the Ising model
-    which will be described in more detail in section
-    \ref{ssec:isingmodel}.\\
+\label{sec:graphtypes}
     The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
@@
     called \emph{lune} in the following. See also Figure
-    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
+    \ref{fig:lunes}.\\
     The Relative Neighborhood Graph \cite{Toussaint1980} is a
@@
     circles with radius \(r = d\) and centers on \(i\) and \(j\).
-    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
+    See also Figure \ref{fig:lunes}.
     \begin{figure}[htbp]
         \centering
-        \subfigure[Definition of the lunes][]{
-                \label{sfig:lunes:def}
-                \input{images/GG_RNG_def}
-        }
-        \subfigure[Relative Neighborhood graph example][]{
-                \label{sfig:lunes:rng}
-                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
-        }
-        \subfigure[Gabriel graph example][]{
-                \label{sfig:lunes:gg}
-                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
-        }
-        \caption[Gabriel - and Relative Neighborhood Graph]
-                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
-                    Graph (hatched region) and
-                    Gabriel Graph (cross hatched region)
-                 \subref{sfig:lunes:def} Example of a Relative
-                    Neighborhood Graph on periodic boundary conditions.
-                    Periodic nodes are dashed.
-                 \subref{sfig:lunes:gg} Example of a Gabriel Graph on
-                    periodic boundary conditions. Periodic nodes are
-                    dashed.
-                }
+        \subfigure{\input{images/GG_RNG_def}}
+        \subfigure{\includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}}
+        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}}
+        \caption[Definition of the lunes and examples of the Gabriel
+                and Relative Neighborhood Graph]
+                {Left: Lunes of Gabriel Graph (red) and Relative
+                    Neighborhood Graph (blue and red). Middle:
+                    Example of a Gabriel Graph. Periodic nodes are
+                    dashed. Right: Example of a Relative
+                    Neighborhood Graph. Periodic nodes are dashed.}
         \label{fig:lunes}
-
     \end{figure}
@@
     one node inside the lune is found. To determine which nodes are
-    near the lune one can subdivide the area in \emph{cells} and save
-    for each cell a list with nodes lying inside it \cite{RNGCell}.
-    Now it is just neccessary to test the nodes in the cells which
-    resemble a rectangular bounding box of the lune. Most pairs will be
-    far away from each other and the cells in the middle of the bounding
-    box are completely inside the lune so that only one node has to be
-    tested to discard an edge between them. Connected nodes are near to
-    each other so that only very few cells have to be tested.\\
-    Indeed this method reduced the time needed to construct a Relative
-    Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
-    over \(15\) respectivly \(40\). But no further analysis was made.
+    near the lune one can save the position of every node in a
+    \emph{cell list} according to \cite{RNGCell} and just test the
+    nodes in the cells which resemble a rectangular bounding box of the
+    lune.
 
 \subsection{Model}
-\label{ssec:isingmodel}
-    The used model is a modified 2D Ising model where the \(N\) sites
-    are displaced nodes of a square lattice of edge length \(L\) with
+    The used model is a modified 2D Ising model where the \(N\)sites are
+    displaced nodes of a square lattice of edgelength \(L\) with
     periodic boundary conditions. The displacement is randomly gauss
@@
     \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
-    where \(\avg{i,j}\) refers to nodes connected  by edges.
+    where \(\avg{i,j}\) refers to by edges connected nodes.
     The edges are constructed according to the in section
-    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
+    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
     proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
     edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
-    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
-    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
+    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
+    called \emph{interaction}.\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
@@
     is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
-    and the magnetisation per site \(m\) and energy per site \(E\)
+    and the magnetisation per site \(m\) and energy of the system \(E\)
     are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
@@
 \subsection{Critical Temperature $T_c$ and Critical Exponents}
-\label{ssec:finitesize}
-    The searched for property -- the critical temperature \(T_c\)
+    Because the searched for property -- the critical temperature \(T_c\)
     -- is only defined for infinite systems, hence every computer
@@
     Despite of this one can obtain \(T_c\) by finite size scaling
-    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
+    methods \cite[S. ??]{Newman1998} which also yield the critical
     exponents. The critical exponents should not be influenced by the
@@
     %~ [theorie mit dem Collaps]
-    To accomplish the collapse in an semi-automatic and reproduceable
-    way with an error estimate, the programm
-    \texttt{autoscale.py} \cite{autoscale2009} is used.
-
     %~ [Erklärung autoscale]
@@
     %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[Example of a datacollapse to determine critical exponents][]{
-                \label{sfig:collapse_s_0}
-                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
-        }
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
-                \label{sfig:binder_fit_s_0}
-                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
-        }
-        \caption[Examples of determining critical temperature and exponents]
-                {\subref{sfig:collapse_s_0}
-                 \subref{sfig:binder_fit_s_0} Binder cumulant interpolated
-                    with cubic splines (the errorbars are too small to see)}
-        \label{fig:binder_fit_s_0}
-    \end{figure}
-    Though if one is just interested in the critical Temperature, an
+    Though if one is just interested in the critical Temperature an
     easier approach is to find the intersections of the Binder cumulants
@@
     system sizes \(L=\sqrt N\).
-    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
-    for the measured points.
-    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
+    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
+    the intersection.
+    In figure \ref{fig:binder_fit_s_0} such a fit is plotted for
     \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
-    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
-    are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
+    To determine \(T_c\) the intersections are averaged and the standard
+    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
     is in very good agreement with the exact solution
     \(T_c = 2.2691...\) \cite{Onsager1944}.\\
-
+    \begin{figure}[htbp]
+        \centering
+        \subfigure{\includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}}
+        \caption[Binder cumulant fitted with polynom of degree 4]
+                {Binder cumulant fitted with polynom of degree 4
+                (the errorbars are too small to see)}
+        \label{fig:binder_fit_s_0}
+    \end{figure}%[vgl. Grafik (villeicht)]
     % The arithmetic average of the intersections are plotted [hier schon?]

### 2013-07-16 Tex/chapters/results.tex
nu durch Mittelung bestimmt, und etwas ausführlicher beschrieben

@@
     collapse in fig.
-\ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
+\ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}%\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
     Note that \(L=16\) is not used for the collapse, because it is a
@@
     performed to determine the critical exponents \(\beta, \gamma, \nu\)
-    using \texttt{autoscale.py} \cite{autoscale2009}. The values for
+    using \texttt{autoscale.py} \cite{autoscale2009} and eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
+    The values for \(\nu\) are yielded by every collapse and are therefore
+    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_sus}\subref{sfig:gettingCrit:collapse_s_0_sus}
+    show an example collapse for \(\sigma=0\) of the magnetic susceptibility
+    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
+    This way the exponents \(\gamma\) and \(\nu\) are determined.
+    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
+    shows the collapse for the mean absolute magnetisation per site \(\avg{\abs{m}}\) for \(\sigma=0\),
+    to determine the exponents \(\beta\) and \(\nu\).
+    Also the collapse of the binder cumulant as mentioned before and shown
+    in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
+    is used to get a further value of \(\nu\).
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Susceptibility $\chi$][]
+        {
+            \label{sfig:gettingCrit:s_0_sus}
+            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
+        }
+        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
+        {
+            \label{sfig:gettingCrit:collapse_s_0_sus}
+            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
+        }
+        \subfigure[Magnetisation $\avg{\abs{m}}$][]
+        {
+            \label{sfig:gettingCrit:s_0_meanM}
+            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
+        }
+        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
+        {
+            \label{sfig:gettingCrit:collapse_s_0_meanM}
+            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
+        }
+        \caption[Examples of determining critical temperature and exponents]
+        {
+            Examples for finite size scaling.
+        }
+        \label{fig:gettingCrit2}
+    \end{figure}\\
+    The values for
     \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
@@
     examined limit for \(\sigma \gtrsim 1\), the plateau at small
-    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).\\
+    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).
+    The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
+    and the error of \(\nu\) is the standard deviation of the three obtained
+    values of \(\nu\).\\
     \begin{table}[htbp]
@@
             \midrule
-            Gabriel      & 0.0 & 1.008(4) & -1.735(2) & 0.1262(4)\\
-                         & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
-                         & 0.3 & 1.000(5) & -1.724(16)& 0.129(12)\\
-                         & 0.5 & 1.009(8) & -1.750(12)& 0.125(13)\\
-                         & 1.0 & 1.015(22)& -1.743(17)& 0.123(16)\\
+            Gabriel      & 0.0 & 0.998(8) & -1.735(2) & 0.1262(4)\\
+                         & 0.1 & 0.999(19)& -1.744(5) & 0.133(6) \\
+                         & 0.3 & 1.029(30)& -1.724(16)& 0.129(12)\\
+                         & 0.5 & 1.006(5) & -1.750(12)& 0.125(13)\\
+                         & 1.0 & 1.038(32)& -1.743(17)& 0.123(16)\\
             \midrule
-            Relative N.  & 0.0 & 1.007(2) & -1.740(2) & 0.130(1) \\
-                         & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
-                         & 0.2 & 1.022(17)& -1.756(14)& 0.123(10)\\
-                         & 0.5 & 1.002(17)& -1.750(16)& 0.143(13)\\
-                         & 1.0 & 1.011(20)& -1.758(16)& 0.138(13)\\
+            Relative N.  & 0.0 & 0.992(11)& -1.740(2) & 0.130(1) \\
+                         & 0.1 & 0.987(12)& -1.746(5) & 0.133(4) \\
+                         & 0.2 & 1.010(9) & -1.756(14)& 0.123(10)\\
+                         & 0.5 & 1.010(16)& -1.750(16)& 0.143(13)\\
+                         & 1.0 & 1.013(6) & -1.758(16)& 0.138(13)\\
             \bottomrule

### 2013-07-16 Tex/chapters/results.tex
kleine Ergänzung zu den Abweichungen des beta

@@
     Despite the very good results for \(\nu\) and \(\gamma\), most of the
-    \(\beta\) seem to be a bit too big, but they are close enough to the
-    expectations to be consistent.
+    \(\beta\) seem to be a bit too big -- especially for the Relative
+    Neighborhood grap -- but they are close enough to the expectations
+    to be consistent. At least the expectations are always within two
+    times the uncertainty.
     Maybe their deviations can be explained by the fact that small
@@
     universality class \cite[p. 145]{Katzgraber2011}. Therefore this
-    disordered Ising model is in the same universality class as the
-    standard Ising ferromagnet.
+    disordered Ising model is for every \(\sigma\)in the same universality
+    class as the standard Ising ferromagnet.
 

### 2013-07-16 Tex/chapters/model.tex
Abkürzungen RNG und GG eingeführt

@@
-%~ \subsection{Model and Implementation}
-%~ I will desribe the model in this section in a bottom-up fashion.
-%~ First describing all parts and then connecting them.
+\subsection{The Disordered Ising Model}
+\label{ssec:isingmodel}
+    The examined model is a modified 2D Ising model.
+    First, let's define the Ising model and then explain the modifications.
+    The Ising model is a square lattice with edge length \(L\) and
+    \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
+    spin can take a value \(s \in \{-1,+1\}\) and interacts with it's
+    nearest neighbors described by the Hamiltonian from eq. \eqref{eq:hamiltonian}
+    \begin{equation}
+        \hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - H \sum_i s_i
+        \label{eq:hamiltonian}
+    \end{equation}
+    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are nearest
+    neighbors. And \(J_{ij}\) is the coupling constant between \(i\) and
+    \(j\). If \(J_{ij} > 0 \forall i,j\) the model resembles a ferromagnet.
+    \(H\) denotes the outer magnetic field.\\
+    In this thesis \(H=0\). The most important modification is, that
+    the sites of the square lattice are displaced. The
+    displacement is randomly Gauß distributed with the standard
+    deviation \(\sigma\), i.e. the \(x\) and \(y\) coordinates of the
+    sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
+    from a Gauß distribution eq. \eqref{eq:gauss}.
+    This is sketched in fig. \ref{fig:displacement}.
+    \begin{equation}
+        f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}
+        \label{eq:gauss}
+    \end{equation}
+    \[x \to x + \Delta x\]
+    \[y \to y + \Delta y\]
+    \begin{figure}[htbp]
+        \centering
+        \input{images/Displacement}
+        \caption[Sketch how the displacement works]
+        {
+            Sketch how the displacement of the nodes works. The nodes
+            get displaced by \(\Delta x\) and \(\Delta y\) drawn from the
+            distributions displayed next to the points. The original
+            square lattice is indicated by dashed lines.
+        }
+        \label{fig:displacement}
+    \end{figure}\\
+    This \(\sigma\) is also called \emph{disorder parameter} in the following.
+    Because most sites will only have one nearest neighbor after the
+    displacement, the lattice would collapse to many very small clusters.
+    To avoid this, the new "nearest" neighbors are those sites connected
+    by an edge. The edges are constructed according to
+    one of the two in section \ref{ssec:graphtypes} defined rules,
+    so that the lattice represents a proximity graph. Note that edges
+    of a proximity graph do not cross each other, hence the 2D character
+    of the lattice is preserved. The coupling constant \(J\) gets
+    identified with edge weights. The weight of an edge \(E_{ij}\) is
+    \(J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean
+    distance between the nodes \(i\) and \(j\). The free parameter
+    \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.
+    The boundary is periodic e.g. nodes near the right edge can be
+    connected to nodes near the left edge and vice versa. Analogous the
+    top and bottom edges are connected. One can imagine that the model
+    lives on the surface of a torus.\\
+    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
+    for which exists an analytic solution \cite{Onsager1944}. And for
+    \(\sigma \gtrsim 1\) the nodes are distributed randomly. This case
+    is studied for constant \(J\) on the Delaunay triangulation\cite{Janke1994}.\\
 
-%~ \subsubsection{Graphs}
-    %~ A graph is a set of nodes \(V\) and edges \(E\).
 \subsection{Gabriel- and Relative Neighborhood Graph}
-\label{sec:graphtypes}
-    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
-    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
-    \(d_{ij}\) are connected with an edge if a circle with it's
-    center on the middlepoint between \(i\) and \(j\) and radius
+\label{ssec:graphtypes}
+    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\).\\
+    All here mentioned graph types are \emph{proximity graphs}. They are
+    connecting nodes which are by some metric near to each other.
+    Hence they are suited to generalize problems defined on regular
+    lattices with nearest neighbor relationships, like the Ising model
+    from the section \ref{ssec:isingmodel}.
+    In this thesis the distance is always determined by the Euclidean
+    metric in two dimensions, though in principle every metric in any
+    dimension can be used.\\
+
+    The Gabriel graph (GG) \cite{Gabriel1969} is a subgraph of the
+    Delaunay triangulation. Two nodes \(i\) and \(j\) with distance
+    \(d_{ij}\) are connected with an edge, if a circle with it's
+    center on half way between \(i\) and \(j\) and radius
     \(r = \frac d 2\) contains no other nodes. This area will be
     called \emph{lune} in the following. See also Figure
-    \ref{fig:lunes}.\\
-    The Relative Neighborhood Graph \cite{Toussaint1980} is a
-    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
-    distance \(d_{ij}\) are connected if no other node is in the
+    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
+    The Relative Neighborhood graph (RNG) \cite{Toussaint1980} is a
+    subgraph of the GG. Two nodes \(i\) and \(j\) with
+    distance \(d_{ij}\) are connected, if no other node is in the
     \emph{lune}. The lune is defined as the intersection of two
     circles with radius \(r = d\) and centers on \(i\) and \(j\).
-    See also Figure \ref{fig:lunes}.
+    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
     \begin{figure}[htbp]
         \centering
-        \subfigure{\input{images/GG_RNG_def}}
-        \subfigure{\includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}}
-        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}}
-        \caption[Definition of the lunes and examples of the Gabriel
-                and Relative Neighborhood Graph]
-                {Left: Lunes of Gabriel Graph (red) and Relative
-                    Neighborhood Graph (blue and red). Middle:
-                    Example of a Gabriel Graph. Periodic nodes are
-                    dashed. Right: Example of a Relative
-                    Neighborhood Graph. Periodic nodes are dashed.}
+        \subfigure[Definition of the lunes][]{
+            \label{sfig:lunes:def}
+            \input{images/GG_RNG_def}
+        }
+        \subfigure[RNG example][]{
+            \label{sfig:lunes:rng}
+            \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
+        }
+        \subfigure[GG example][]{
+            \label{sfig:lunes:gg}
+            \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
+        }
+        \caption[Gabriel - and Relative Neighborhood Graph]
+        {
+            \subref{sfig:lunes:def} Lunes of RNG (hatched region) and
+                GG (cross hatched region)
+            \subref{sfig:lunes:rng} Example of a RNG on periodic
+                boundary conditions. Periodic nodes are dashed.
+            \subref{sfig:lunes:gg} Example of a GG on
+                periodic boundary conditions. Periodic nodes are dashed.
+        }
         \label{fig:lunes}
-    \end{figure}
-
-    To construct these graphs the simple way is to test for every
-    pair of nodes for every node if it lies in the lune of the pair.
-    That is of complexity \(O (n^3)\).\\
+    \end{figure}\\
+    To construct these graphs the simple way is to test for each
+    pair of nodes if any other node lies in
+    the lune of the pair. That is of complexity \(O (N^3)\), because
+    there are \(N(N-1)\) pairs and for each \(N-2\) nodes to test. So
+    the product is of order \(O(N^3)\)\\
     To reduce the complexity one can first create a Delaunay
-    Triangulation in complexity \(O (n \log n)\)
-    \cite{Leach1992} and test the criterion for each edge, because
-    the Delaunay Triangulation is a supergraph of both. But the
-    implementation of a Delaunay Triangulation algorithm is not
-    trivial and the generation of the graphs is not time critical in
-    the scope of this bachelor thesis.\\
-    So a tradeoff is to use basicly the simple method but only test
+    Triangulation in complexity \(O (N \log N)\)
+    \cite{RNGCell} and test the criterion for each edge, because
+    the Delaunay triangulation is a supergraph of both. But the
+    implementation of a Delaunay triangulation algorithm is not trivial
+    and the generation of the graphs is not time critical in the scope
+    of this bachelor thesis.\\
+    So a trade off is to use basically the simple method but only test
     the criterion for nodes which are near to the lune and abort if
     one node inside the lune is found. To determine which nodes are
-    near the lune one can save the position of every node in a
-    \emph{cell list} according to \cite{RNGCell} and just test the
-    nodes in the cells which resemble a rectangular bounding box of the
-    lune.
-
-\subsection{Model}
-    The used model is a modified 2D Ising model where the \(N\)sites are
-    displaced nodes of a square lattice of edgelength \(L\) with
-    periodic boundary conditions. The displacement is randomly gauss
-    distributed with the standard deviation \(\sigma\). This \(\sigma\)
-    is also called \emph{disturbance paramter} in the following.
-    The hamiltonian of the Ising model is
-    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
-    where \(\avg{i,j}\) refers to by edges connected nodes.
-    The edges are constructed according to the in section
-    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
-    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
-    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
-    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
-    called \emph{interaction}.\\
-    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
-    for which exists an analytical solution \cite{Onsager1944}.\\
-
-    For evaluation the Monte Carlo simulation is is run till the system
-    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
-    and the magnetisation per site \(m\) and energy of the system \(E\)
-    are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
-    denotes the \emph{autocorrelation time} after which two states of
-    the system are not correlated anymore.
-    For every observable \(O\) the expected value \(\avg{O}\) is averaged
-    over different randomly generated lattices \(\overline{\avg{O}}\). The
-    errors are estimated by bootstrapping.
-
-\subsection{Critical Temperature $T_c$ and Critical Exponents}
-    Because the searched for property -- the critical temperature \(T_c\)
-    -- is only defined for infinite systems, hence every computer
-    simulation will show some \emph{finte size effects}.
-    %[vielleicht Bild von intensiver Größe?]
-    Despite of this one can obtain \(T_c\) by finite size scaling
-    methods \cite[S. ??]{Newman1998} which also yield the critical
-    exponents. The critical exponents should not be influenced by the
-    disturbance paramter \(\sigma\) [citation needed]. So they will be
-    used for consistency cross checking and comparision with the known
-    exact values \cite[S. 59]{Pelissetto2002}.\\
-    %~ [theorie mit dem Collaps]
-    %~ [Erklärung autoscale]
-    %~ [Am besten hier direkt die ganze Auswertung rein]
-    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
-    Though if one is just interested in the critical Temperature an
-    easier approach is to find the intersections of the Binder cumulants
-    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
-    system sizes \(L=\sqrt N\).
-    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
-    the intersection.
-    In figure \ref{fig:binder_fit_s_0} such a fit is plotted for
-    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
-    To determine \(T_c\) the intersections are averaged and the standard
-    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
-    is in very good agreement with the exact solution
-    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
-    \begin{figure}[htbp]
-        \centering
-        \subfigure{\includegraphics[width=0.45\textwidth]{plots/binder_fit_s_0}}
-        \caption[Binder cumulant fitted with polynom of degree 4]
-                {Binder cumulant fitted with polynom of degree 4
-                (the errorbars are too small to see)}
-        \label{fig:binder_fit_s_0}
-    \end{figure}%[vgl. Grafik (villeicht)]
-    % The arithmetic average of the intersections are plotted [hier schon?]
-    %~ [Und den rest der Auswertung]
-
-% Erwahnen, dass T_c Graph so aussieht, wie degree graph
-% mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
-% cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
+    near the lune one can subdivide the area in \emph{cells} and save
+    for each cell a list with nodes lying inside it like presented in
+    \cite{RNGCell}.
+    Now it is just necessary to test the nodes in the cells which
+    resemble a rectangular bounding box of the lune. Most pairs will be
+    far away from each other and the cells in the middle of the bounding
+    box are completely inside the lune so that only one node has to be
+    tested to discard an edge between them. Connected nodes are near to
+    each other so that only very few cells have to be tested.\\
+    Indeed this method reduced the time needed to construct a RNG with
+    \(N=32^2\) and \(N=64^2\) by a factor of
+    over \(15\) respectively \(40\). Though the complexity is still of
+    order \(O(N^2)\) in the best case, because for every pair at least
+    one check has to be performed.

### 2013-07-16 Tex/chapters/results.tex
Abkürzungen RNG und GG eingeführt

@@
     occurs at lower temperatures \(T\) for higher
-    disorder parameters \(\sigma\) (here with a Relative Neighborhood graph).
+    disorder parameters \(\sigma\) (here with a RNG).
     \begin{figure}[htbp]
@@
             parameter $\sigma$ on the phase transition
-            for an underlying Relative Neighborhood graph with $L=128$.\\
+            for an underlying RNG with $L=128$.\\
             \subref{sfig:smeared_out:meanM}: Effects of different system
@@
     critical temperatures \(T_c\).
-    In this section these \(T_c\) on either the Relative Neighborhood
-    graph or the Gabriel graph are compared. In the following figures,
-    the Relative Neighborhood graph will always be on the left side
-    and the Gabriel graph on the right side.
+    In this section these \(T_c\) on either the RNG or the GG are
+    compared. In the following figures, the RNG will always be on the
+    left side and the GG on the right side.
     In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).
@@
             disorder parameters \(\sigma\) for
-            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc:GG} the Gabriel Graph.\\
+            \subref{sfig:Tc:RNG} the RNG and
+            \subref{sfig:Tc:GG} the GG.\\
         }
@@
     \end{figure}\\
-    One sees that the Relative Neighborhood graph on the left has
-    generally a lower critical temperature than the Gabriel. Also \(T_c\)
-    of the Relative Neighborhood graph decreases
-    monotonically while \(T_c\) of the Gabriel rises at first.
+    One sees that the RNG on the left has
+    generally a lower critical temperature than the GG. Also \(T_c\)
+    of the RNG decreases
+    monotonically while \(T_c\) of the GG rises at first.
     For big \(\sigma\) the displaced nodes approach the limit of randomly
@@
     A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
-    of \(T_c\) on the Gabriel graph. To understand that, one has to
+    of \(T_c\) on the GG. To understand that, one has to
     consider the influence of the graph properties on the critical
@@
     Indeed the normalization eliminates the jump and reduces the
-    slope of the rising on the Gabriel graph. Hence it reduces differences
-    between the Relative Neighborhood graph and the Gabriel graph.
+    slope of the rising on the GG. Hence it reduces differences
+    between the RNG and the GG.
     \begin{figure}[htbp]
@@
             disorder parameters \(\sigma\) for
-            \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:deg:GG} the Gabriel Graph.\\
+            \subref{sfig:deg:RNG} the RNG and
+            \subref{sfig:deg:GG} the GG.\\
             Bottom: Critical temperatures normalized by degree over different
             disorder parameters for
-            \subref{sfig:Tc_norm_deg:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc_norm_deg:GG} the Gabriel Graph.
+            \subref{sfig:Tc_norm_deg:RNG} the RNG and
+            \subref{sfig:Tc_norm_deg:GG} the GG.
         }
@@
     understand the jump of \(K\), which is easily explained
-    by the definition of the Gabriel graph and it's aftereffects for
+    by the definition of the GG and it's aftereffects for
     the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
@@
         }
-        \caption[Anomaly of the Gabriel graph for small $\sigma$]
+        \caption[Anomaly of the GG for small $\sigma$]
         {
-            Gabriel graph with periodic boundary conditions for
+            GG with periodic boundary conditions for
                 \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
@@
             neighbors over different disorder parameters for
-            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
+            \subref{sfig:sumJ:RNG} the RNG and
+            \subref{sfig:sumJ:GG} the GG.\\
             Bottom: Critical temperatures normalized by mean sum of the
@@
             disorder parameters for
-            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
-            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
+            \subref{sfig:Tc_normJ:RNG} the RNG and
+            \subref{sfig:Tc_normJ:GG} the GG.
         }
@@
     \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
-    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
+    jump on the GG arises again, but \(T_c\) is now monotonically
     decreasing with increasing disorder parameter \(\sigma\). Moreover
     the forms of both curves are quite similar, but the
-    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
+    one for the RNG \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
     is generally lower and spans over a bigger temperature range than
-    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
+    the curve of the GG \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
     Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
@@
             \midrule
-            Gabriel      & 0.0 & 0.998(8) & -1.735(2) & 0.1262(4)\\
+            GG           & 0.0 & 0.998(8) & -1.735(2) & 0.1262(4)\\
                          & 0.1 & 0.999(19)& -1.744(5) & 0.133(6) \\
@@
             \midrule
-            Relative N.  & 0.0 & 0.992(11)& -1.740(2) & 0.130(1) \\
+            RNG          & 0.0 & 0.992(11)& -1.740(2) & 0.130(1) \\
                          & 0.1 & 0.987(12)& -1.746(5) & 0.133(4) \\
@@
             Cross checking the critical exponent $\gamma$ for
-                \subref{sfig:susCrossCheck:RNG} the Relative Neighborhood graph and
-                \subref{sfig:susCrossCheck:GG} the Gabriel graph.
+                \subref{sfig:susCrossCheck:RNG} the RNG and
+                \subref{sfig:susCrossCheck:GG} the GG.
             Dotted lines are power law fits.
@@
     Despite the very good results for \(\nu\) and \(\gamma\), most of the
-    \(\beta\) seem to be a bit too big -- especially for the Relative
-    Neighborhood grap -- but they are close enough to the expectations
+    \(\beta\) seem to be a bit too big -- especially for the RNG -- but
+    they are close enough to the expectations
     to be consistent. At least the expectations are always within two
@@
         \centering
-        \subfigure[for a Relative Neighborhood graph][]
+        \subfigure[for a RNG][]
         {
@@
         }
-        \subfigure[for a Gabriel graph][]
+        \subfigure[for a GG][]
         {
@@
             for\\
-            \subref{sfig:TcG:RNG} a Relative Neighborhood graph and\\
-            \subref{sfig:TcG:GG} a Gabriel graph for different \(\sigma\).
+            \subref{sfig:TcG:RNG} a RNG and\\
+            \subref{sfig:TcG:GG} a GG for different \(\sigma\).
             The dotted line is the reference value for square lattices

### 2013-07-16 Tex/chapters/introduction.tex
Tippfehler Korrekturen
Introduction ausgebaut

@@
 The computing capabilities of modern computers enable researchers to
-collect and analyze vast amounts of data.
-Further statistical systems, for which exist no analytic solutions
-or only for very simplified or special cases, can be simulated.
+collect and analyze vast amounts of data. The prime example for is fact
+is the LHC, where petabytes of particle collision data is collected and
+processed. But computers are not only able to process measured data, but
+also to generate data by simulations of e.g. statistical systems, where
+the rules for each subsystem are well defined but the behavior of the
+whole system is not easy to predict, beacause of the interactions of the
+subsystems. For those systems there often exist no analytic solutions
+or only for very simplified or special cases. But one can simulate all
+the interactions of the subsystems and observe the behavior of the whole
+system.
 For example to examine phase transitions, which are defined by the abrupt
-change of an observable i.e. the change of the density of water near
+change of an observable e.g. the change of the density of water near
 boiling or the change of the magnetization of a ferromagnet near the
@@
 some regular lattices \cite{Onsager1944} \cite{Wannier1945}.
-In this thesis it's behavior near the Curie temperature -- also called
-critical temperature -- on some irregular lattices corresponding to
-proximity graphs (see section \ref{ssec:graphtypes}) will be examined
-using the Monte Carlo simulations described in section \ref{sec:montecarlo}.
+In this thesis its behavior near the Curie temperature -- also called
+critical temperature -- and the behavior of the Curie temperature itself
+on some irregular lattices corresponding to proximity graphs
+(see section \ref{ssec:graphtypes}) will be examined using the Monte
+Carlo simulations described in section \ref{sec:montecarlo}.
 
 Unfortunately the memory of any computer is small in comparison with the
-thermodynamic limit. This leads to deviations from the real behavior of
-the system in the thermodynamic limit. These deviations are called
+thermodynamic limit. So there can only be a very small number of
+subsystems simulated in comparison to the actual number of subsystems
+of the system in nature. This leads to deviations from the real behavior
+of the system in the thermodynamic limit. These deviations are called
 \emph{finite size effects} and in section \ref{ssec:finitesize} will be

### 2013-07-16 Tex/chapters/model.tex
it\'s zu its korrigiert

@@
     The examined model is a modified 2D Ising model.
-    First, let's define the Ising model and then explain the modifications.
+    First, let us define the Ising model and then explain the modifications.
     The Ising model is a square lattice with edge length \(L\) and
     \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
-    spin can take a value \(s \in \{-1,+1\}\) and interacts with it's
+    spin can take a value \(s \in \{-1,+1\}\) and interacts with its
     nearest neighbors described by the Hamiltonian from eq. \eqref{eq:hamiltonian}
@@
     Delaunay triangulation. Two nodes \(i\) and \(j\) with distance
-    \(d_{ij}\) are connected with an edge, if a circle with it's
+    \(d_{ij}\) are connected with an edge, if a circle with its
     center on half way between \(i\) and \(j\) and radius

### 2013-07-16 Tex/chapters/monte_carlo.tex
it\'s zu its korrigiert

@@
 by generating random states.
-But it is difficult to create a random state of a physical system i.e. the
+But it is difficult to create a random state of a physical system e.g. the
 Ising system in equilibrium, hence one uses \emph{Markov Chains} to
@@
         is trapped in a local minimum at a given temperature, can travel
-        to higher temperatures, leave it's local minimum and cool down
+        to higher temperatures, leave its local minimum and cool down
         again in a lower minimum.\\

### 2013-07-16 Tex/chapters/results.tex
it\'s zu its korrigiert

@@
     temperature.\\
-    One basic property of a graph is it's degree \(K\) -- sometimes
+    One basic property of a graph is its degree \(K\) -- sometimes
     called \emph{coordination number} -- is defined as the mean count of
@@
     and there exists an analytic solution \cite{Wannier1945}.
-    It's a critical temperature is determined by eq. \eqref{eq:exactHCTc}.
+    Its a critical temperature is determined by eq. \eqref{eq:exactHCTc}.
     \begin{equation}
@@
     understand the jump of \(K\), which is easily explained
-    by the definition of the GG and it's aftereffects for
+    by the definition of the GG and its aftereffects for
     the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
@@
             the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
-            to match it's definition in this thesis.}.
+            to match its definition in this thesis.}.
     Because the analysis of section \ref{ssec:binderIntersections}

### 2013-07-16 Tex/chapters/results.tex
Erweiterungen zum GG Maximum

@@
     \end{figure}\\
-    One sees that the RNG on the left has
-    generally a lower critical temperature than the GG. Also \(T_c\)
-    of the RNG decreases
-    monotonically while \(T_c\) of the GG rises at first.
+    One sees that the RNG on the left has generally a lower critical
+    temperature than the GG. Also \(T_c\) of the RNG decreases
+    monotonically while \(T_c\) of the GG rises at first. Naively one would
+    expect, that while changing the displacement of the nodes monotonically,
+    the properties of the system will also change monotonically. The
+    maximum at \(\sigma \approx 0.15\) on the GG will be discussed later.
     For big \(\sigma\) the displaced nodes approach the limit of randomly
     distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
-    \(\sigma >> 1\).\\
-    A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
+    \(\sigma \gg 1\).\\
+    Another strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
     of \(T_c\) on the GG. To understand that, one has to
@@
     and there exists an analytic solution \cite{Wannier1945}.
-    Its a critical temperature is determined by eq. \eqref{eq:exactHCTc}.
+    Its critical temperature is determined by eq. \eqref{eq:exactHCTc}.
     \begin{equation}
@@
     by the definition of the GG and its aftereffects for
-    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
+    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
     a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
@@
     to get smaller, hence no other nodes are inside or on the edge of
-    the lune anymore and the edge appears.
+    the lune anymore and the edge appears.\\
+    Further the increase of \(T_c\) on the GG can be made plausible.
+    Though it is not removed by the normalization, it is reduced. Also
+    the maximum of the \(K\) is at the same \(\sigma\), as the maximum
+    of \(T_c\). So while displacing the nodes, there arise more edges
+    than edges are vanishing until \(\sigma \approx 0.15\) is reached.
+    Then more edges disappear, than appear at further displacement. This
+    can is not an obvious effect, but can be seen in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
     \begin{figure}[htbp]
-        \centering
-        \subfigure[][]
+        \subfigure[][$\sigma = 0.00$]
         {
-            \label{sfig:GG_sigma:zero}
-            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
+            \label{sfig:GG_sigma:0.00}
+            \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
         }
-        \subfigure[][]
+        \subfigure[][$\sigma = 0.01$]
         {
-            \label{sfig:GG_sigma:notzero}
-            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
+            \label{sfig:GG_sigma:0.01}
+            \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
         }
+
+        \subfigure[][$\sigma = 0.09$]
+        {
+            \label{sfig:GG_sigma:0.09}
+            \includegraphics[width=0.30\textwidth]{images/GG/out009}
+        }
+        \subfigure[][$\sigma = 0.15$]
+        {
+            \label{sfig:GG_sigma:0.15}
+            \includegraphics[width=0.30\textwidth]{images/GG/out015}
+        }
+        \subfigure[][$\sigma = 0.21$]
+        {
+            \label{sfig:GG_sigma:0.21}
+            \includegraphics[width=0.30\textwidth]{images/GG/out021}
+        }
+
         \caption[Anomaly of the GG for small $\sigma$]
         {
-            GG with periodic boundary conditions for
-                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
-                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
+            GG with periodic boundary conditions for different \(\sigma = 0\)
         }
@@
     \end{figure}\\
+    The explanation for the plateau of the RNG at low \(\sigma\) is similar.
+    On the RNG no new edges arise at small displacements of the nodes\footnote{See \ref{appendix:RNGDisplacement} for a graphic.}\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.}.
     But the degree does not alone influence the behavior of \(T_c\).
@@
     \end{figure}\\
-    If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
+    Though the eq. \eqref{eq:exactHCTc} shows, that there does not have
+    to be a linear connection between \(J\) and \(T_c\), the best guess
+    is a linear connection, because this model is derived from the
+    square lattice, where the connection is linear. Therefore, one
+    normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
     \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
     jump on the GG arises again, but \(T_c\) is now monotonically
-    decreasing with increasing disorder parameter \(\sigma\). Moreover
-    the forms of both curves are quite similar, but the
-    one for the RNG \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
+    decreasing with increasing disorder parameter \(\sigma\).
+    %~ This is a strong hint, that the change of the \(T_c\) with changing
+    %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
+    %~ expected conclusion.\\
+    Moreover the forms of both curves are quite similar, but the
+    one for the RNG \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
     is generally lower and spans over a bigger temperature range than
-    the curve of the GG \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
+    the curve of the GG \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
     Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
@@
     Also both graph types have a steep decline after the plateau before
-    they approach an asymptotic limit for \(\sigma >> 1\)\\\\
+    they approach an asymptotic limit for \(\sigma \gg 1\)\\\\
 

### 2013-07-16 Tex/chapters/conclusion.tex
kurze conclusion

@@
 proximity graphs was studied. This model is within the universality of
-the standard Ising ferromagnet. Further the critical temperature depends
-on the one hand on the
+the standard Ising ferromagnet. Its critical temperature decreases with
+increasing disorder on a RNG. On a GG it first jumps, increases up to
+a maximum and decreases after that. The course of the critical
+temperatures can be made plausible observing the degree of the underlying
+graph, but no explicit formular was found.
 

### 2013-07-18 Tex/chapters/results.tex
corrections to scaling

@@
     Note that \(L=16\) is not used for the collapse, because it is a
-    rather small value such that eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
-    do not apply very good.\\
+    rather small value. Eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
+    are approximations for big \(L\). For small \(L\) one needs some
+    \emph{corrections to scaling} terms, which are not considered here.\\
     To accomplish the collapse in an semi-automatic and reproduceable
@@
     \(\beta\) seem to be a bit too big -- especially for the RNG -- but
-    they are close enough to the expectations
-    to be consistent. At least the expectations are always within two
-    times the uncertainty.
+    they are close enough to the expectations to be consistent. At least
+    the expectations are always within two times the uncertainty.
     Maybe their deviations can be explained by the fact that small
-    systems (\(L=32,64\)) were used for the analysis, which introduce
-    some deviations, because the collapse works best for big system sizes.
+    systems (\(L=32,64\)) were used for the analysis, and no corrections
+    to scaling terms were considered.
     Anyway, two critical exponents are sufficient to determine the

### 2013-07-18 Tex/chapters/introduction.tex
Theorieteil zu Monte Carlo hinzugefügt

@@
 (see section \ref{ssec:graphtypes}) will be examined using the Monte
-Carlo simulations described in section \ref{sec:montecarlo}.
+Carlo simulations described in section \ref{ssec:montecarlo}.
 

### 2013-07-18 Tex/chapters/methods.tex
Theorieteil zu Monte Carlo hinzugefügt

--- 2013-07-16 Tex/chapters/monte_carlo.tex
@@
-\label{sec:montecarlo}
-%~ Monte Carlo simulations are (probably) named after the casino in Monaco
-%~ \cite{NewmanBarkema1999} because both rely on randomness.\\
+\subsection{Thermodynamic Theory}
+\label{ssec:theory}
+    To examine the disordered Ising model in Equilibrium,
+    Its temperature \(T\),
+    volume and number of particles \(N\) are constant, so that it is a canonical
+    ensemble. In a canonical ensemble the probability \(p_i\) of a state
+    \(i\) is distributed according to a Boltzman distribution
+    \[p_i \propto e^{-\frac{\hat{H}}{k_B T}}\]
+    Further the free energy \(F\) of an canonical
+    ensemble is minimized and all observables can be derived from \(F\)
+    in a straight forward way, as stated in every textbook about
+    statistical physics (e.g. \cite{nolting2005}).
+    To determine \(F\), one has to know the partition function
+    \[Z=\sum_i e^{-\frac{\hat{H}_i}{kT}}\]
+    where the sum goes over all possible states \(i\) of the system.
+    For small \(N\) the partition function is computable, but the system
+    may show very different properties than in the thermodynamic limit.
+    To minimize these finite size effects, it is desirable to examine
+    systems with large \(N\). But then there are of course next to
+    infinity many different states, such that it is unfeasible to
+    calculate the energy for each state, except for cases, where it is
+    possible to solve it analytically.\\
+    If not, one can get estimates of the observables for big \(N\) using
+    Monte Carlo simulations.\\
+
+\subsection{Monte Carlo Simulations}
+\label{ssec:montecarlo}
     The idea behind Monte Carlo simulations is to take random samples of
@@
     values and weights the result accordingly.\\
-%~ To improve this method: \emph{Importance Sampling}
-%~ means that one takes more samples where the contribution of the
-%~ function to the integral is bigger by using random numbers
-%~ distributed........
-The same principle is used to sample properties of statistical systems
-by generating random states.
+    The same principle is used to sample properties of statistical
+    systems by generating random states.
+    As noted before the system under scrutiny is canonical and therefore
+    the states are distributed according to the Boltzman distribution.
+    Hence importance sampling can be utilized.\\
     But it is difficult to create a random state of a physical system e.g. the
@@
     Otherwise the samples might not be representative for the whole system.\\
+    In this thesis three algorithms, which fulfill all requirements,
+    were used. They will be shortly described in the following subsections.
 
-\subsection{Monte Carlo Algorithms}
     \subsubsection{Metropolis}
@@
 
-\subsection{Equilibration- and Autocorrelation Time}
-\label{ssec:eqtime}
+    \subsubsection{Equilibration- and Autocorrelation Time}
+    \label{sssec:eqtime}
         To generate an equilibrium state one starts with an arbitrary state

### 2013-07-18 Tex/chapters/results.tex
Tippfehler beseitigt
Cubic spline ausgeführt

@@
     Because the magnetization \(m\) is only measured for discrete values
-    of \(T\), \(g\) is also only known for these discrete values and has
-    to be interpolated to find a intersection. Therefore a cubic spline
+    of \(T\), \(g\) is also only known for these discrete values and the
+    analytical course of the curve is not known, and hence has
+    to be interpolated to find the intersection. Therefore a \emph{cubic spline}
     interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
@@
     degree three which are joined under the condition to be at least two
-    times continuously differentiable.
+    times continuously differentiable. This interpolation type has the
+    advantage, that it is only influenced by local points so that the
+    plateaus at low and high \(T\) do not influence the interpolation in
+    the vicinity of \(T_c\) -- in contrast to e.g. an polynom fit of
+    degree 4, which has to be restricted to the vincinity of \(T_c\) to
+    yield meaningful results.
     As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.
@@
     \end{equation}
+    This test suggests, that measuring \(T_c\) this way is yields
+    adequat results and the interpolation does not lead to major
+    deviations.
 
@@
     Then more edges disappear, than appear at further displacement. This
-    can is not an obvious effect, but can be seen in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
+    is not an obvious effect, but can be seen in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
     \begin{figure}[htbp]

### 2013-07-18 Tex/chapters/results.tex
kleine Umformulierung
Reihenfolge verändert

@@
     exponents.
+
+\subsection{Critical Exponents}
     Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
@@
     varies them until the measured values of the observables collapse on
-    one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}
-    collapse in fig.
-\ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}%\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
+    one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
+    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
+    %\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
     Note that \(L=16\) is not used for the collapse, because it is a
@@
         \centering
-        \subfigure[Example of a Binder cumulant to determine the critical temperature][]
+        \subfigure[Binder Cumulant $g$][]
         {
-            \label{sfig:gettingCrit:binder_fit_s_0}
-            \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+            \label{sfig:gettingCrit:binder_s_0}
+            \includegraphics[width=0.47\textwidth]{plots/binder_s_0}
         }
-        \subfigure[Example of a datacollapse to determine critical exponents][]
+        \subfigure[Finite Size Scaling of the Binder Cumulant $g$][]
         {
@@
         {
-            The Binder cumulant \(g\) of an square lattice Ising model
-            (\(\sigma=0\))\\
-            \subref{sfig:gettingCrit:binder_fit_s_0} interpolated
-                with cubic splines (the errorbars are too small to see)\\
+            \subref{sfig:gettingCrit:binder_s_0} The Binder cumulant \(g\)
+                of an square lattice Ising model (\(\sigma=0\))\\
             \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
@@
     \end{figure}\\
+
+    A finite size scaling analysis was
+    performed to determine the critical exponents \(\beta, \gamma, \nu\)
+    using \texttt{autoscale.py} \cite{autoscale2009} and eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
+    The values for \(\nu\) are yielded by every collapse and are therefore
+    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_sus}\subref{sfig:gettingCrit:collapse_s_0_sus}
+    show an example collapse for \(\sigma=0\) of the magnetic susceptibility
+    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
+    This way the exponents \(\gamma\) and \(\nu\) are determined.
+    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
+    shows the collapse for the mean absolute magnetisation per site \(\avg{\abs{m}}\) for \(\sigma=0\),
+    to determine the exponents \(\beta\) and \(\nu\).
+    Also the collapse of the binder cumulant as mentioned before and shown
+    in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
+    is used to get a further value of \(\nu\).
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Susceptibility $\chi$][]
+        {
+            \label{sfig:gettingCrit:s_0_sus}
+            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
+        }
+        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
+        {
+            \label{sfig:gettingCrit:collapse_s_0_sus}
+            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
+        }
+        \subfigure[Magnetisation $\avg{\abs{m}}$][]
+        {
+            \label{sfig:gettingCrit:s_0_meanM}
+            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
+        }
+        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
+        {
+            \label{sfig:gettingCrit:collapse_s_0_meanM}
+            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
+        }
+        \caption[Examples of determining critical temperature and exponents]
+        {
+            Examples for finite size scaling.
+        }
+        \label{fig:gettingCrit2}
+    \end{figure}\\
+    The values for
+    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
+    values for all other \(\sigma\) are expected be the same as for
+    \(\sigma = 0\) like mentioned before in section \ref{ssec:finitesize}.
+    Therefore it is sufficient to take a few samples to test if the
+    expectations are met. Hence 5 values of \(\sigma\) are analyzed.
+    The analytically known values for \(\sigma = 0\) and the in \cite{Janke1994}
+    examined limit of an random lattice \(\sigma \gtrsim 1\) are natural
+    choices.
+    The other \(\sigma\) are chosen to represent regions, where the behavior of
+    \(T_c\) shows some characteristics. (Namely there is a plateau at small
+    \(\sigma\), a steep decline at medium \(\sigma\) and a shallow
+    decline at \(\sigma = 0.5\). This will be shown in the next
+    chapter in fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
+    The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
+    and the error of \(\nu\) is the standard deviation of the three obtained
+    values of \(\nu\).\\
+    \begin{table}[htbp]
+        \center
+        \begin{tabular}{l l l l l}
+            \toprule
+             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
+            \midrule
+            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
+            \midrule
+            GG           & 0.0 & 0.998(8) & -1.735(2) & 0.1262(4)\\
+                         & 0.1 & 0.999(19)& -1.744(5) & 0.133(6) \\
+                         & 0.3 & 1.029(30)& -1.724(16)& 0.129(12)\\
+                         & 0.5 & 1.006(5) & -1.750(12)& 0.125(13)\\
+                         & 1.0 & 1.038(32)& -1.743(17)& 0.123(16)\\
+            \midrule
+            RNG          & 0.0 & 0.992(11)& -1.740(2) & 0.130(1) \\
+                         & 0.1 & 0.987(12)& -1.746(5) & 0.133(4) \\
+                         & 0.2 & 1.010(9) & -1.756(14)& 0.123(10)\\
+                         & 0.5 & 1.010(16)& -1.750(16)& 0.143(13)\\
+                         & 1.0 & 1.013(6) & -1.758(16)& 0.138(13)\\
+            \bottomrule
+        \end{tabular}
+        \caption{Critical exponents for different $\sigma$}
+        \label{tab:critExp}
+    \end{table}\\
+    Like in tab. \ref{tab:critExp} to see, most values
+    are matching the expectations. Especially \(\nu\) and \(\gamma\)
+    are always in very good agreement with their exact values. Because
+    there can never be to much cross and consistency checks, the ratio
+    \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
+    the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
+    The results are displayed in fig. \ref{fig:susCrossCheck}. The ratios
+    determined by this method confirm the values obtained by collapse.
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:susCrossCheck:RNG}
+            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:susCrossCheck:GG}
+            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
+        }
+        \caption[Alternative Way Determining $\gamma$]
+        {
+            Cross checking the critical exponent $\gamma$ for
+                \subref{sfig:susCrossCheck:RNG} the RNG and
+                \subref{sfig:susCrossCheck:GG} the GG.
+            Dotted lines are power law fits.
+        }
+        \label{fig:susCrossCheck}
+    \end{figure}\\
+    Despite the very good results for \(\nu\) and \(\gamma\), most of the
+    \(\beta\) seem to be a bit too big -- especially for the RNG -- but
+    they are close enough to the expectations to be consistent. At least
+    the expectations are always within two times the uncertainty.
+    Maybe their deviations can be explained by the fact that small
+    systems (\(L=32,64\)) were used for the analysis, and no corrections
+    to scaling terms were considered.
+    Anyway, two critical exponents are sufficient to determine the
+    universality class \cite[p. 145]{Katzgraber2011}. Therefore this
+    disordered Ising model is for every \(\sigma\) in the same universality
+    class as the standard Ising ferromagnet.
+
+\subsection{Critical Temperature}
+\label{ssec:binderIntersections}
     Though if one is just interested in the critical Temperature, an
     easier approach is to find the intersections of the Binder cumulants
-    \(g\) of different system sizes \(L\) because they are intersecting
-    at \(T_c\) \cite{Binder1981}.
+    \(g\) of different system sizes \(L\) which are intersecting at
+    \(T_c\) \cite{Binder1981}.
     Because the magnetization \(m\) is only measured for discrete values
@@
     yield meaningful results.
-    As an example take fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_fit_s_0}.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
+        \caption[Example of a Binder cumulant to determine the critical temperature]
+        {
+            The Binder cumulant \(g\) of an square lattice Ising model
+            (\(\sigma=0\)) interpolated with cubic splines
+            (the errorbars are too small to see)\\
+        }
+        \label{fig:gettingCrit:binder_fit_s_0}
+    \end{figure}\\
+    As an example take fig. \ref{fig:gettingCrit:binder_fit_s_0}.
     Here such interpolations are plotted for \(\sigma=0\) and are
@@
     adequat results and the interpolation does not lead to major
-    deviations.
-
-\subsection{Critical Temperature}
-\label{ssec:binderIntersections}
-    The evaluation of the Binder cumulant's intersections, yields the
-    critical temperatures \(T_c\).
+    deviations.\\
     In this section these \(T_c\) on either the RNG or the GG are
@@
 
-\subsection{Critical Exponents}
-    A finite size scaling analysis was
-    performed to determine the critical exponents \(\beta, \gamma, \nu\)
-    using \texttt{autoscale.py} \cite{autoscale2009} and eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
-    The values for \(\nu\) are yielded by every collapse and are therefore
-    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_sus}\subref{sfig:gettingCrit:collapse_s_0_sus}
-    show an example collapse for \(\sigma=0\) of the magnetic susceptibility
-    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
-    This way the exponents \(\gamma\) and \(\nu\) are determined.
-    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
-    shows the collapse for the mean absolute magnetisation per site \(\avg{\abs{m}}\) for \(\sigma=0\),
-    to determine the exponents \(\beta\) and \(\nu\).
-    Also the collapse of the binder cumulant as mentioned before and shown
-    in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
-    is used to get a further value of \(\nu\).
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[Susceptibility $\chi$][]
-        {
-            \label{sfig:gettingCrit:s_0_sus}
-            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
-        }
-        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
-        {
-            \label{sfig:gettingCrit:collapse_s_0_sus}
-            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
-        }
-        \subfigure[Magnetisation $\avg{\abs{m}}$][]
-        {
-            \label{sfig:gettingCrit:s_0_meanM}
-            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
-        }
-        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
-        {
-            \label{sfig:gettingCrit:collapse_s_0_meanM}
-            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
-        }
-        \caption[Examples of determining critical temperature and exponents]
-        {
-            Examples for finite size scaling.
-        }
-        \label{fig:gettingCrit2}
-    \end{figure}\\
-    The values for
-    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
-    values for all other \(\sigma\) are expected be the same as for
-    \(\sigma = 0\) like mentioned before in section \ref{ssec:finitesize}.
-    Therefore it is sufficient to take a few samples to test if the
-    expectations are met. Hence 5 values of \(\sigma\) are analyzed,
-    which are chosen to represent every interesting region from fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}:
-    the analytically known value for \(\sigma = 0\), the in \cite{Janke1994}
-    examined limit for \(\sigma \gtrsim 1\), the plateau at small
-    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).
-    The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
-    and the error of \(\nu\) is the standard deviation of the three obtained
-    values of \(\nu\).\\
-    \begin{table}[htbp]
-        \center
-        \begin{tabular}{l l l l l}
-            \toprule
-             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
-            \midrule
-            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
-            \midrule
-            GG           & 0.0 & 0.998(8) & -1.735(2) & 0.1262(4)\\
-                         & 0.1 & 0.999(19)& -1.744(5) & 0.133(6) \\
-                         & 0.3 & 1.029(30)& -1.724(16)& 0.129(12)\\
-                         & 0.5 & 1.006(5) & -1.750(12)& 0.125(13)\\
-                         & 1.0 & 1.038(32)& -1.743(17)& 0.123(16)\\
-            \midrule
-            RNG          & 0.0 & 0.992(11)& -1.740(2) & 0.130(1) \\
-                         & 0.1 & 0.987(12)& -1.746(5) & 0.133(4) \\
-                         & 0.2 & 1.010(9) & -1.756(14)& 0.123(10)\\
-                         & 0.5 & 1.010(16)& -1.750(16)& 0.143(13)\\
-                         & 1.0 & 1.013(6) & -1.758(16)& 0.138(13)\\
-            \bottomrule
-        \end{tabular}
-        \caption{Critical exponents for different $\sigma$}
-        \label{tab:critExp}
-    \end{table}\\
-    Like in tab. \ref{tab:critExp} to see, most values
-    are matching the expectations. Especially \(\nu\) and \(gamma\)
-    are always in very good agreement with their exact values. Because
-    there can never be to much cross and consistency checks, the ratio
-    \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
-    the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
-    The results are displayed in fig. \ref{fig:susCrossCheck}. The by this
-    method determined ratios confirm the by collapse obtained values.
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[][]
-        {
-            \label{sfig:susCrossCheck:RNG}
-            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
-        }
-        \subfigure[][]
-        {
-            \label{sfig:susCrossCheck:GG}
-            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
-        }
-        \caption[Alternative Way Determining $\gamma$]
-        {
-            Cross checking the critical exponent $\gamma$ for
-                \subref{sfig:susCrossCheck:RNG} the RNG and
-                \subref{sfig:susCrossCheck:GG} the GG.
-            Dotted lines are power law fits.
-        }
-        \label{fig:susCrossCheck}
-    \end{figure}\\
-    Despite the very good results for \(\nu\) and \(\gamma\), most of the
-    \(\beta\) seem to be a bit too big -- especially for the RNG -- but
-    they are close enough to the expectations to be consistent. At least
-    the expectations are always within two times the uncertainty.
-    Maybe their deviations can be explained by the fact that small
-    systems (\(L=32,64\)) were used for the analysis, and no corrections
-    to scaling terms were considered.
-    Anyway, two critical exponents are sufficient to determine the
-    universality class \cite[p. 145]{Katzgraber2011}. Therefore this
-    disordered Ising model is for every \(\sigma\)in the same universality
-    class as the standard Ising ferromagnet.
-
 \subsection{Critical Value of the Binder Cumulant}

### 2013-07-18 Tex/chapters/results.tex
Footnote ergänzt

@@
     The explanation for the plateau of the RNG at low \(\sigma\) is similar.
-    On the RNG no new edges arise at small displacements of the nodes\footnote{See \ref{appendix:RNGDisplacement} for a graphic.}\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.}.
+    On the RNG no new edges arise at small displacements of the nodes\footnote{See appendix \ref{appendix:RNGDisplacement} for a graphic.}\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.}.
     But the degree does not alone influence the behavior of \(T_c\).

### 2013-07-18 Tex/chapters/results.tex
Bildunterschrift ausführlicher gestaltet
Bildunterschriften in einheitlichem case

@@
         \centering
-        \subfigure[in dependence on the temperature $T$][]
+        \subfigure[in Dependence on the Temperature $T$][]
         {
@@
         }
-        \subfigure[in dependence on the system size $L$][]
+        \subfigure[in Dependence on the System Size $L$][]
         {
@@
         }
-        \caption[The autocorrelation time $\tau$]
+        \caption[The Autocorrelation Time $\tau$]
         {
@@
         \centering
-        \subfigure[Dependence of the phase transition on $\sigma$][]
+        \subfigure[Dependence of the Phase Transition on $\sigma$][]
         {
@@
         }
-        \subfigure[Example for finite size effects][]
+        \subfigure[Example for Finite Size Effects][]
         {
@@
         }
-        \caption[Examples of determining critical temperature and exponents]
+        \caption[Examples of Determining Critical Temperature and Exponents]
         {
@@
         }
-        \caption[Examples of determining critical temperature and exponents]
+        \caption[Examples of Determining Critical Temperature and Exponents]
         {
-            Examples for finite size scaling.
+            \subref{sfig:gettingCrit:s_0_sus} The susceptibility \(\chi\)
+                of an square lattice Ising model (\(\sigma=0\))\\
+            \subref{sfig:gettingCrit:collapse_s_0_sus} collapsed by finite
+                size scaling\\
+            \subref{sfig:gettingCrit:s_0_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
+                of an square lattice Ising model (\(\sigma=0\))\\
+            \subref{sfig:gettingCrit:collapse_s_0_meanM} collapsed by finite
+                size scaling
         }
@@
         \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
-        \caption[Example of a Binder cumulant to determine the critical temperature]
+        \caption[Example of a Binder Cumulant to Determine the Critical Temperature]
         {
@@
         }
-        \caption[Critical Temperature over different disorder parameters]
+        \caption[Critical Temperature over Different Disorder Parameters]
         {
@@
 
-        \caption[Critical Temperature normalized by Degree of the Graph]
+        \caption[Critical Temperature Normalized by Degree of the Graph]
         {
@@
 
-        \caption[Anomaly of the GG for small $\sigma$]
+        \caption[Anomaly of the GG for Small $\sigma$]
         {
@@
 
-        \caption[Critical Temperature normalized by Mean Sum of the Coupling Constants]
+        \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
         {
@@
         }
-        \caption[Values of the Binder cumulant at the critical point $g_c$]
+        \caption[Values of the Binder Cumulant at the Critical Point $g_c$]
         {

### 2013-07-22 Tex/chapters/model.tex
Bildunterschriften in einheitlichem case
Hamilton Operator ist jetzt eine Hamilton Funktion

@@
     \begin{equation}
-        \hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - H \sum_i s_i
+        H = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \tilde{H} \sum_i s_i
         \label{eq:hamiltonian}
@@
     \(j\). If \(J_{ij} > 0 \forall i,j\) the model resembles a ferromagnet.
-    \(H\) denotes the outer magnetic field.\\
-    In this thesis \(H=0\). The most important modification is, that
+    \(\tilde{H}\) denotes the outer magnetic field.\\
+    In this thesis \(\tilde{H}=0\). The most important modification is, that
     the sites of the square lattice are displaced. The
@@
         \input{images/Displacement}
-        \caption[Sketch how the displacement works]
+        \caption[Sketch how the Displacement Works]
         {
@@
         \centering
-        \subfigure[Definition of the lunes][]{
+        \subfigure[Definition of the Lunes][]{
             \label{sfig:lunes:def}

### 2013-07-22 Tex/chapters/results.tex
Hamilton Operator ist jetzt eine Hamilton Funktion

@@
 and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
-per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
+per site \(E=\frac{1}{N} H\) are calculated and saved for every
 \(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}

### 2013-07-22 Tex/chapters/methods.tex
Bildunterschriften in einheitlichem case
Ergänzung zu themodyn. Theorie

@@
 \label{ssec:theory}
-    To examine the disordered Ising model in Equilibrium,
-    Its temperature \(T\),
-    volume and number of particles \(N\) are constant, so that it is a canonical
-    ensemble. In a canonical ensemble the probability \(p_i\) of a state
+    %~ To examine the disordered Ising model in Equilibrium,
+    %~ Its temperature \(T\),
+    %~ volume and number of particles \(N\) are constant, so that it is a canonical
+    %~ ensemble.
+    In a canonical ensemble the probability \(p_i\) of a state
     \(i\) is distributed according to a Boltzman distribution
@@
     in a straight forward way, as stated in every textbook about
-    statistical physics (e.g. \cite{nolting2005}).
-    To determine \(F\), one has to know the partition function
-    \[Z=\sum_i e^{-\frac{\hat{H}_i}{kT}}\]
+    statistical physics (e.g. \cite{nolting2005}).\\
+    Because of \(F=U-TS\) where \(U=\avg{H}\) is the internal energy and
+    \(S\) entropy, one can guess, that for low \(T\) the internal energy
+    will be low, and for big \(T\) the entropy will be high, to minimize
+    \(F\). The Hamiltonian of the Ising model creates an conflict between
+    \(U\) and \(S\) by assigning low energies to states with high order.
+    So \(U\) is low if all spins are aligned, where \(S\) as a measure of
+    disorder is low. This preliminary considerations make a phase
+    transition at some \(T\), where a high entropy lowers \(F\) more than
+    a low internal energy, very plausible.\\\
+    To determine
+    \[F=-k_{B}T \ln{Z}\]
+    one has to know the partition function
+    \[Z=\sum_i e^{-\frac{\hat{H}_i}{k_{B}T}}\]
     where the sum goes over all possible states \(i\) of the system.
@@
             \centering
-            \subfigure[Example of an equilibrating Ising system][]{
+            \subfigure[Example of an Equilibrating Ising System][]{
                     \label{sfig:equiandauto:equiE}
@@
             }
-            \subfigure[Example of the autocorrelation of an Ising system][]{
+            \subfigure[Example of the Autocorrelation of an Ising System][]{
                     \label{sfig:equiandauto:autoM}
@@
             }
-            \caption[Examples for equilibration and autocorrelation]
+            \caption[Examples for Equilibration and Autocorrelation]
             {

### 2013-07-23 Tex/chapters/methods.tex
Korrekturen betreffend H (\hat H)

@@
     \(i\) is distributed according to a Boltzman distribution
-    \[p_i \propto e^{-\frac{\hat{H}}{k_B T}}\]
+    \[p_i \propto e^{-\frac{H_i}{k_B T}}\]
     Further the free energy \(F\) of an canonical
@@
     one has to know the partition function
-    \[Z=\sum_i e^{-\frac{\hat{H}_i}{k_{B}T}}\]
+    \[Z=\sum_i e^{-\frac{H_i}{k_{B}T}}\]
     where the sum goes over all possible states \(i\) of the system.
@@
         Ising model will choose a random spin, calculate the energy change
-        \(\Delta \hat H\) defined in eq. \eqref{eq:dH} that would result
+        \(\Delta H\) defined in eq. \eqref{eq:dH} that would result
         from a flip of that spin and execute the flip with the probability \(A\)
@@
         \begin{equation}
-            \Delta \hat H = \hat H(\nu) - \hat H(\mu)\\
+            \Delta H = H(\nu) - H(\mu)\\
             \label{eq:dH}
@@
             \begin{cases}
-                1                                 & \Delta \hat H \le 0 \\
-                \exp{\brac{-\beta \Delta \hat H}} & \Delta \hat H > 0
+                1                            & \Delta H \le 0 \\
+                \exp{\brac{-\beta \Delta H}} & \Delta H > 0
             \end{cases}

### 2013-07-23 Tex/chapters/model.tex
Korrekturen betreffend H (\hat H)

@@
     \begin{equation}
-        H = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \tilde{H} \sum_i s_i
+        H = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i \tilde{H}_i s_i
         \label{eq:hamiltonian}
@@
     neighbors. And \(J_{ij}\) is the coupling constant between \(i\) and
-    \(j\). If \(J_{ij} > 0 \forall i,j\) the model resembles a ferromagnet.
-    \(\tilde{H}\) denotes the outer magnetic field.\\
-    In this thesis \(\tilde{H}=0\). The most important modification is, that
-    the sites of the square lattice are displaced. The
-    displacement is randomly Gauß distributed with the standard
+    \(j\). If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
+    \(\tilde{H}_i\) denotes the outer magnetic field at the position of
+    site \(i\).\\
+    In this thesis \(\tilde{H}_i=0 \ \forall i\). The most important
+    modification is, that the sites of the square lattice are displaced.
+    The displacement is randomly Gauß distributed with the standard
     deviation \(\sigma\), i.e. the \(x\) and \(y\) coordinates of the

### 2013-07-23 Tex/chapters/results.tex
Kleinigkeiten vervollständigt

@@
     are always in very good agreement with their exact values. Because
-    there can never be to much cross and consistency checks, the ratio
+    there can never be to much cross- and consistency checks, the ratio
     \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
@@
         \centering
-        \subfigure[][]
+        \subfigure[for a RNG][]
         {
@@
         }
-        \subfigure[][]
+        \subfigure[for a GG][]
         {
@@
             Cross checking the critical exponent $\gamma$ for
-                \subref{sfig:susCrossCheck:RNG} the RNG and
-                \subref{sfig:susCrossCheck:GG} the GG.
+                \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
+                \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
             Dotted lines are power law fits.

### 2013-07-23 Tex/chapters/introduction.tex
Tippfehler beseitigt

@@
 Curie temperature. One of the simplest models with a second order
-phase transition is the Ising model \cite{Ising1925} which is a simple
+phase transition, i.e. a continuous transition without discontinuities of
+the order parameter, is the Ising model \cite{Ising1925} in \(d \ge 2\)
+dimensions. This is a simple
 model of a ferromagnet and will be explained in more detail in section

### 2013-07-23 Tex/chapters/methods.tex
Tippfehler beseitigt

@@
         temperatures are far smaller because their spin configuration
-        gets often replaced by an other uncorrelated configuration. In
+        gets often replaced by another uncorrelated configuration. In
         many cases the more important advantage is, that a system which

### 2013-07-23 Tex/chapters/results.tex
Tippfehler beseitigt

@@
     square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
-        \footnote{Note that \cite{BinderValue} uses an other definition of
+        \footnote{Note that \cite{BinderValue} uses another definition of
             the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)

### 2013-07-23 Tex/chapters/model.tex
kleine Erweiterungen zu Ising, TODO: Torus mit RNG Bild

@@
     The examined model is a modified 2D Ising model.
-    First, let us define the Ising model and then explain the modifications.
-    The Ising model is a square lattice with edge length \(L\) and
+    The most common definition of the Ising model, to which will be referred
+    as the \emph{standard Ising model}, is a square lattice with edge length \(L\) and
     \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
@@
     top and bottom edges are connected. One can imagine that the model
-    lives on the surface of a torus.\\
+    lives on the surface of a torus like in fig. \ref{fig:torusRNG}.
+    In subsequent graphics, the graphs will be unrolled and shown as a
+    planar projection. Connections which cross a periodic boundary are
+    indicated by edges which connect to an dashed node.
+    \begin{figure}[htbp]
+        \centering
+        %~ \includegraphics[width=0.3\textwidth]{images/torusRNG.pdf}
+        \caption[A Graph on a Torus to Visualise Periodic Boundary Conditions]
+        {
+            A graph on a torus to visualise periodic boundary conditions.
+        }
+        \label{fig:torusRNG}
+    \end{figure}\\
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),

### 2013-07-23 Tex/chapters/methods.tex
Ergänzungen zu Theorie und MC

@@
 \label{ssec:theory}
-    %~ To examine the disordered Ising model in Equilibrium,
-    %~ Its temperature \(T\),
-    %~ volume and number of particles \(N\) are constant, so that it is a canonical
-    %~ ensemble.
+    To examine the disordered Ising model in Equilibrium, one can use
+    methods of statistical physics. It is a canonical ensemble i.e. the
+    temperature \(T\) is kept constant e.g. by a heat bath.
     In a canonical ensemble the probability \(p_i\) of a state
     \(i\) is distributed according to a Boltzman distribution
-    \[p_i \propto e^{-\frac{H_i}{k_B T}}\]
+    \begin{equation}
+        p_i \propto e^{-\beta H_i}
+    \end{equation}
+    \begin{equation}
+        \beta = \frac{1}{k_B T}
+    \end{equation}
     Further the free energy \(F\) of an canonical
@@
     To determine
-    \[F=-k_{B}T \ln{Z}\]
+    \begin{equation}
+        F=-k_{B}T \ln{Z}
+    \end{equation}
     one has to know the partition function
-    \[Z=\sum_i e^{-\frac{H_i}{k_{B}T}}\]
+    \begin{equation}
+        Z = \sum_i p_i = \sum_i e^{-\beta H_i}
+    \end{equation}
     where the sum goes over all possible states \(i\) of the system.
-    For small \(N\) the partition function is computable, but the system
+    Because every site can have two states, there are \(2^N\) different
+    states of the system, which have to be summed up to gain \(Z\).
+    Hence for small \(N\) the partition function is computable, but the system
     may show very different properties than in the thermodynamic limit.
     To minimize these finite size effects, it is desirable to examine
-    systems with large \(N\). But then there are of course next to
-    infinity many different states, such that it is unfeasible to
-    calculate the energy for each state, except for cases, where it is
-    possible to solve it analytically.\\
+    systems with large \(N\). But \(2^N\) is a very rapidly increasing
+    number, so there are next to infinity many different states, such
+    that it is unfeasible to calculate the energy for each state, except
+    for cases, where it is possible to solve it analytically.\\
     If not, one can get estimates of the observables for big \(N\) using
@@
     The idea behind Monte Carlo simulations is to take random samples of
-    the observable, which should be measured, and estimate the observable from
+    the observable, which should be measured, and estimate the mean of the observable from
     this samples. In example the Monte Carlo integration chooses random
@@
     as the fraction of points below the function and points above multiplied
-    by the area of the bounding box.
-    Of course one wants to sample more points, where the area below the
-    function is big, because points in areas, where the function does
-    contribute little to the integral, contribute little to the integral.
-    This can be achieved by \emph{Importance Sampling}. One
-    generates random numbers according to some probability distribution, which
-    yields more numbers in the range where the function to integrate has high
-    values and weights the result accordingly.\\
-    The same principle is used to sample properties of statistical
-    systems by generating random states.
+    by the area of the bounding box \cite{Katzgraber2011}.\\
+    Analogical the technique can be applied to statistical ensembles,
+    but instead of sampling points on an area, one samples states of the
+    system.\\
+    In statistical physics the expected value of an observable \(O\)
+    is calculated by
+    \begin{equation}
+        \avg{O} = \frac{1}{Z} \sum_i p_i O_i
+    \end{equation}
+    It is however possible, that there are few states that contribute
+    massively more than others. Think of a canonical system at low \(T\),
+    where \(p_i\) with low \(H_i\) contribute much more than high \(H_i\).
+    But if one samples the \(2^N\) states evenly, it is probable to miss
+    them, which possibly introduces big errors to the estimate of \(\avg{O}\).
+    It is therefore desirable to sample only the states with high
+    contributions to the sum.
     As noted before the system under scrutiny is canonical and therefore
-    the states are distributed according to the Boltzman distribution.
-    Hence importance sampling can be utilized.\\
+    \(p_i\) is known. The states are distributed according to the Boltzman
+    distribution. Hence \emph{Importance Sampling} can be utilized.\\
+    Instead of sampling uniformly distributed random states, one samples
+    states, which energies are distributed according to a Boltzman distribution.
+    In fact this reduces the estimator to
+    \begin{equation}
+        O_M = \frac{1}{M} \sum_{i=0}^M O_i
+    \end{equation}
+    as shown in \cite{NewmanBarkema1999}. This is a very convenient form.\\
     But it is difficult to create a random state of a physical system e.g. the
-    Ising system in equilibrium, hence one uses \emph{Markov Chains} to
-    generate new states \(\nu\) from old ones \(\mu\).
-    It is important that the transition probabilities \(A(\mu \to \nu)\)
-    obey \emph{Detailed Balance} and \emph{Ergodicity}.
+    Ising system in equilibrium, according to a given distribution.
+    Hence one uses \emph{Markov Chains} to generate new states \(\nu\)
+    from old ones \(\mu\). It is important that the transition probabilities
+    \(A(\mu \to \nu)\) obey \emph{Detailed Balance} and \emph{Ergodicity}.
     \emph{Detailed Balance} means that the probability to leave a state is
@@
     \(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\) with \(p_\mu\) the
-    probability to be in state \(\mu\).
+    probability to be in state \(\mu\). This ensures that the system can
+    equilibrate and that the states are distributed according to the
+    desired distribution in equilibrium \cite{NewmanBarkema1999}.
     And \emph{Ergodicity} requires that every possible state is reachable
@@
     \subsubsection{Parallel Tempering}
-        %~ The main aim is to obtain the critical temperatures
-        %~ \(T_c\) for different disorder paramters \(\sigma\).
-        %~ Therefore it is necessary to simulate for many temperatures,
-        %~ so that \emph{Parallel Tempering}\footnote{Before R. H.
-            %~ Swendsen published this paper, a algorithm \(MC^3\) was
-            %~ already published with the same idea. [citation needed]}
-        %~ \cite{ParallelTempering1986} is a suited algorithm.
         Parallel Tempering\cite{ParallelTempering1986} simulates many identical systems at different

### 2013-07-23 Tex/chapters/appendix.tex
nu durch Mittelung bestimmt, und etwas ausführlicher beschrieben
Erweiterungen zum GG Maximum
kleine Umformulierung
\[ durch equation ersetzt

--- 2013-07-05 Tex/chapters/appendix.tex
@@
 \section{Finite Size Effects at the Example of the Specific Heat}
+\label{appendix:finiteSizeEffects}
     In fig. \ref{fig:smeared_out_appendix} the specific heat
-\[C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}\]
+    \begin{equation}
+        C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
+    \end{equation}
     is plotted for different system sizes. The finite size effects are obvious.
@@
     \end{figure}
+
+\section{Effect of $\sigma$ on the RNG}
+\label{appendix:RNGDisplacement}
+    todo: RNG Bilder mit versch. sigma

### 2013-07-23 Tex/chapters/results.tex
\[ durch equation ersetzt
Referenzen repariert

@@
 \(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
-(see also \ref{ssec:eqtime}). The used values for different system sizes
+(see also \ref{sssec:eqtime}). The used values for different system sizes
 are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
@@
     size. In fact it obeys a power law, which is the expected behaivior of
-    a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
+    a dynamical critical exponent \(z\) as mentioned in section \ref{sssec:eqtime}.
     In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
@@
     show an example collapse for \(\sigma=0\) of the magnetic susceptibility
-    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
+    \begin{equation}
+        \chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}
+    \end{equation}
     This way the exponents \(\gamma\) and \(\nu\) are determined.

### 2013-07-23 Tex/chapters/methods.tex
Gleichheitszeichen ergänzt
Fehlerkorrekturen

@@
     transition at some \(T\), where a high entropy lowers \(F\) more than
-    a low internal energy, very plausible.\\\
+    a low internal energy, very plausible.\\
     To determine
@@
     If not, one can get estimates of the observables for big \(N\) using
-    Monte Carlo simulations.\\
+    Monte Carlo simulations, which are introduced in the next chapter.\\
+    %~ Once one has obtained values for e.g. the magnetization \(m\), one
+    %~ can easily calculate the susceptibility
+    %~ \begin{equation}
+        %~ \chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}
+    %~ \end{equation}
+    % Bisschen erklæren, dass man aus m auch chi machen kann und auf literatur verweisen
 
@@
     But it is difficult to create a random state of a physical system e.g. the
-    Ising system in equilibrium, according to a given distribution.
+    Ising system in equilibrium according to a given distribution.
     Hence one uses \emph{Markov Chains} to generate new states \(\nu\)
@@
         \begin{equation}
-            A(\mu \to \nu)
+            A(\mu \to \nu) =
             \begin{cases}

### 2013-07-23 Tex/chapters/results.tex
Fehlerkorrekturen

@@
     \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
-    the system will jump and the susceptibility
+    the system will show a steep decline to zero and the susceptibility
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
     will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
-    it is easy to see that the jump of \(\avg{|m|}\)
+    it is easy to see that the steep decline of \(\avg{|m|}\)
     occurs at lower temperatures \(T\) for higher
@@
     \end{figure}\\
-    But in the shown plots there occurs no real jump, but a continuous
-    decline. The jump is only present in infinite systems, hence no
-    computer simulation will show the exact behavior in the
+    But in the shown plots there occurs no steep decline to zero, but a
+    smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
+    systems, hence no computer simulation will show the exact behavior in the
     thermodynamic limit. It will always show some \emph{finte size effects}.

### 2013-07-23 Tex/chapters/model.tex
Fehler bei Definition der Hamilton Funktion
Torus hinzugefügt

@@
     \begin{equation}
-        H = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i \tilde{H}_i s_i
+        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i \tilde{H}_i s_i
         \label{eq:hamiltonian}
@@
     lives on the surface of a torus like in fig. \ref{fig:torusRNG}.
-    In subsequent graphics, the graphs will be unrolled and shown as a
-    planar projection. Connections which cross a periodic boundary are
-    indicated by edges which connect to an dashed node.
+    In subsequent graphics, the graphs will be unwrapped to rectangular
+    shapes. Connections which cross a periodic boundary are indicated
+    by edges which connect to an dashed node.
     \begin{figure}[htbp]
         \centering
-        %~ \includegraphics[width=0.3\textwidth]{images/torusRNG.pdf}
+        \includegraphics[width=0.45\textwidth]{images/torus}
         \caption[A Graph on a Torus to Visualise Periodic Boundary Conditions]
         {
-            A graph on a torus to visualise periodic boundary conditions.
+            A graph on a torus to visualize periodic boundary conditions.
+            Note that the lattice on this torus is not a square but has
+            a height to width ratio of 1:4. At 1:1 the torus would cut
+            itself. Also the shades are of course only a guide to the eye.
         }

### 2013-07-24 Tex/chapters/introduction.tex
Warum sind Phasenübergänge wichtig?

@@
 boiling or the change of the magnetization of a ferromagnet near the
-Curie temperature. One of the simplest models with a second order
+Curie temperature.
+Different phases of an material and the transitions between them were
+always of greatest interest. The ancient greek thought, that everything
+consists of fire, water, air and earth, which are the archetypes of
+phases. Still phase transitions are alone on the basis of their ubiquity
+important phenomenons. The understanding allows applications from the
+condensing boiler to shatter resistant mobile phone glass \cite{PJournalGlass}.
+One of the simplest models with a second order
 phase transition, i.e. a continuous transition without discontinuities of

### 2013-07-24 Tex/chapters/introduction.tex
Korrekturen, Ergänzungen, Umformulierungen

@@
 The computing capabilities of modern computers enable researchers to
-collect and analyze vast amounts of data. The prime example for is fact
-is the LHC, where petabytes of particle collision data is collected and
-processed. But computers are not only able to process measured data, but
+collect and analyze vast amounts of data. The prime example for this fact
+is the LHC, where petabytes of particle collision data are collected,
+processed and discarded or kept every second \cite{LHC}.
+But computers are not only able to process measured data, but
 also to generate data by simulations of e.g. statistical systems, where
 the rules for each subsystem are well defined but the behavior of the
-whole system is not easy to predict, beacause of the interactions of the
+whole system is not easy to predict because of the interactions of the
 subsystems. For those systems there often exist no analytic solutions

### 2013-07-24 Tex/chapters/methods.tex
Korrekturen, Ergänzungen, Umformulierungen

@@
     \end{equation}
-    Further the free energy \(F\) of an canonical
+    Further the free energy \(F\) of a canonical
     ensemble is minimized and all observables can be derived from \(F\)
@@
     \(U\) and \(S\) by assigning low energies to states with high order.
-    So \(U\) is low if all spins are aligned, where \(S\) as a measure of
+    So \(U\) is low if all spins are aligned, while \(S\) as a measure of
     disorder is low. This preliminary considerations make a phase
@@
     as shown in \cite{NewmanBarkema1999}. This is a very convenient form.\\
-    But it is difficult to create a random state of a physical system e.g. the
-    Ising system in equilibrium according to a given distribution.
+    But it is difficult to create a random state of a physical system
+    e.g. the Ising system according to a given distribution. The simple
+    method of creating uniformly distributed random states and reject
+    them with probability \(p_i^{-1}\) depending on their energy is not
+    efficient, because many generated states will be discarded and the
+    computing time to generate them and caluculating their energy will
+    be wasted.
     Hence one uses \emph{Markov Chains} to generate new states \(\nu\)
@@
         Therefore it minimizes the calculations needed for a change of
-        the state.
+        the state. Also note that \(\Delta H\) is easy to calculate,
+        because it is only affected by the spin of the neighbors of the
+        chosen site.
 
@@
         Close to the critical temperature \(T_c\) the Metropolis
-        gets slower. This is called \emph{critical slowing} down and the
-        cause is beyond the scope of this thesis.\\
+        gets slower. This is called \emph{critical slowing} down.\\
         Using a cluster algorithm like the Wolff
@@
     \label{sssec:eqtime}
-        To generate an equilibrium state one starts with an arbitrary state
-        and waits until it is equilibrated. The count of sweeps till
+        To generate states acoording to the Boltzman distribution at a
+        given temperature \(T\), one starts with an arbitrary state
+        and waits until it reaches thermal \emph{equilibrium}. Thermal
+        equilibrium denotes the condition, that the system under scrutiny
+        has reached the temperature of the heat bath. This is the case,
+        once no energy is exchanged between them, such that the energy
+        of the simulated system reaches a steady state as pictured in
+        fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
+        The count of sweeps till
         equilibrium is called \emph{equilibration time} \(t_{eq}\).
-        All measurement should start after this time.\\
-        To determine when the system is in equilibrium, one can watch the
-        development of some observables and take the point at which there
-        are no big changes anymore as equilibrium. In fig.
-        \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
+        All measurements should start after this time.\\
+        In fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
         the equilibrium is reached after approximately \(N=50\) sweeps for
         either an initial condition of all spins up and all spins random. It
-        does not harm to double that value to be save.
+        does not harm to double that value to be save. Particularly because
+        it is a random process, so that there can not be an exact value.
         \begin{figure}[htbp]

### 2013-07-24 Tex/chapters/results.tex
Korrekturen, Ergänzungen, Umformulierungen

@@
                 \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
-            Dotted lines are power law fits.
+            Dotted lines are power law fits \(aL^\frac{\gamma}{\nu}\).
         }
@@
     Here such interpolations are plotted for \(\sigma=0\) and are
-    intersecting at \(\approx 2.27\).
+    intersecting at \(T \approx 2.27\).
     To determine \(T_c\), the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
@@
     expect, that while changing the displacement of the nodes monotonically,
-    the properties of the system will also change monotonically. The
+    the properties of the system will also change monotonically, which is
+    indeed the case on a RNG but not on a GG. The
     maximum at \(\sigma \approx 0.15\) on the GG will be discussed later.
@@
     distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
-    \(\sigma \gg 1\).\\
+    \(\sigma \gg 1\). Regarding this both meet the expectations.\\
     Another strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
@@
     One basic property of a graph is its degree \(K\) -- sometimes
-    called \emph{coordination number} -- is defined as the mean count of
-    neighbors per node
+    called \emph{coordination number}. \(K\) is defined as the mean count
+    of neighbors per node.
     \begin{equation}
@@
     \end{figure}\\
-    Though the eq. \eqref{eq:exactHCTc} shows, that there does not have
+    Though eq. \eqref{eq:exactHCTc} shows, that there does not have
     to be a linear connection between \(J\) and \(T_c\), the best guess

### 2013-07-29 Tex/chapters/model.tex
Korrekturen, Ergänzungen, Umformulierungen
Beschreibung des Torus geändert

@@
     top and bottom edges are connected. One can imagine that the model
-    lives on the surface of a torus like in fig. \ref{fig:torusRNG}.
+    lives on the surface of a torus as pictured in fig. \ref{fig:torusRNG}.
     In subsequent graphics, the graphs will be unwrapped to rectangular
@@
             a height to width ratio of 1:4. At 1:1 the torus would cut
-            itself. Also the shades are of course only a guide to the eye.
+            itself. Hence, the torus represents the geometry of the model
+            not perfectly, but gives very quick the right idea.
+            %Also the shades are of course only a guide to the eye.
         }
@@
     \(\sigma \gtrsim 1\) the nodes are distributed randomly. This case
-    is studied for constant \(J\) on the Delaunay triangulation\cite{Janke1994}.\\
+    is already studied for constant \(J\) on the Delaunay triangulation
+    in \cite{Janke1994}.\\
 

### 2013-07-29 Tex/chapters/introduction.tex
Brennwert Kessel durch Kühlschrank ersetzt
Spacing nach i.e. und e.g. korrigiert

@@
 But computers are not only able to process measured data, but
-also to generate data by simulations of e.g. statistical systems, where
+also to generate data by simulations of e.g.\ statistical systems, where
 the rules for each subsystem are well defined but the behavior of the
@@
 For example to examine phase transitions, which are defined by the abrupt
-change of an observable e.g. the change of the density of water near
+change of an observable e.g.\ the change of the density of water near
 boiling or the change of the magnetization of a ferromagnet near the
@@
 important phenomenons. The understanding allows applications from the
-condensing boiler to shatter resistant mobile phone glass \cite{PJournalGlass}.
+refrigerator to shatter resistant mobile phone glass \cite{PJournalGlass}.
 One of the simplest models with a second order
-phase transition, i.e. a continuous transition without discontinuities of
+phase transition, i.e.\ a continuous transition without discontinuities of
 the order parameter, is the Ising model \cite{Ising1925} in \(d \ge 2\)

### 2013-07-29 Tex/chapters/methods.tex
Spacing nach i.e. und e.g. korrigiert

@@
     To examine the disordered Ising model in Equilibrium, one can use
-    methods of statistical physics. It is a canonical ensemble i.e. the
-    temperature \(T\) is kept constant e.g. by a heat bath.
+    methods of statistical physics. It is a canonical ensemble i.e.\ the
+    temperature \(T\) is kept constant e.g.\ by a heat bath.
     In a canonical ensemble the probability \(p_i\) of a state
@@
     in a straight forward way, as stated in every textbook about
-    statistical physics (e.g. \cite{nolting2005}).\\
+    statistical physics (e.g.\ \cite{nolting2005}).\\
     Because of \(F=U-TS\) where \(U=\avg{H}\) is the internal energy and
@@
     Monte Carlo simulations, which are introduced in the next chapter.\\
-    %~ Once one has obtained values for e.g. the magnetization \(m\), one
+    %~ Once one has obtained values for e.g.\ the magnetization \(m\), one
     %~ can easily calculate the susceptibility
@@
     But it is difficult to create a random state of a physical system
-    e.g. the Ising system according to a given distribution. The simple
+    e.g.\ the Ising system according to a given distribution. The simple
     method of creating uniformly distributed random states and reject

### 2013-07-29 Tex/chapters/methods.tex
Theorie leicht umsortiert und etwas mehr Erläuterungen

@@
 \label{ssec:theory}
-    To examine the disordered Ising model in Equilibrium, one can use
-    methods of statistical physics. It is a canonical ensemble i.e.\ the
-    temperature \(T\) is kept constant e.g.\ by a heat bath.
+    The disordered Ising model will be examined as a \emph{canonical system} in
+    \emph{equilibrium}. A canonical system can exchange energy with a
+    heat bath, thus has a constant temperature -- the temperature of the
+    heat bath.
+    Equilibrium is defined as a steady state, where
+    the observables are only fluctuating but not changing in any
+    particular direction. For example thermal equilibrium denotes the
+    condition, that the system under scrutiny has reached the temperature
+    of the heat bath. This is the case, once no energy is exchanged
+    between them, thus the energy of the simulated system reaches a
+    steady state.
     In a canonical ensemble the probability \(p_i\) of a state
@@
     \end{equation}
-    Further the free energy \(F\) of a canonical
-    ensemble is minimized and all observables can be derived from \(F\)
+    Further the free energy \(F\) of a canonical ensemble is minimized
+    in equilibrium and all observables can be derived from \(F\)
     in a straight forward way, as stated in every textbook about
@@
     will be low, and for big \(T\) the entropy will be high, to minimize
-    \(F\). The Hamiltonian of the Ising model creates an conflict between
-    \(U\) and \(S\) by assigning low energies to states with high order.
-    So \(U\) is low if all spins are aligned, while \(S\) as a measure of
-    disorder is low. This preliminary considerations make a phase
-    transition at some \(T\), where a high entropy lowers \(F\) more than
-    a low internal energy, very plausible.\\
+    \(F\). The Hamiltonian of the Ising model connects \(U\) and \(S\)
+    by assigning low energies to states with high order. So \(U\) is low
+    if all spins are aligned. In this case \(S\) as a measure of
+    disorder is also low. Analogical the state of maximum \(U\) is also
+    the state of maximum \(S\).
+    This preliminary considerations make a phase transition at some
+    \(T\), where the influence of the entropy on \(F\) becomes the same
+    order of magnitude as the influence of the internal energy on \(F\),
+    very plausible.\\
     To determine
@@
         given temperature \(T\), one starts with an arbitrary state
-        and waits until it reaches thermal \emph{equilibrium}. Thermal
-        equilibrium denotes the condition, that the system under scrutiny
-        has reached the temperature of the heat bath. This is the case,
-        once no energy is exchanged between them, such that the energy
-        of the simulated system reaches a steady state as pictured in
-        fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
+        and waits until it reaches thermal \emph{equilibrium}. Because
+        equilibrium is defined as a steady state, one can determine if it
+        is reached, by observing the change of the observables over the
+        progressing simulation, as pictured in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
         The count of sweeps till

### 2013-07-29 Tex/chapters/results.tex
Spacing nach i.e. und e.g. korrigiert
Kurz erläutert, wie das mittlere Kantengewicht ermittelt wird

@@
     plateaus at low and high \(T\) do not influence the interpolation in
-    the vicinity of \(T_c\) -- in contrast to e.g. an polynom fit of
+    the vicinity of \(T_c\) -- in contrast to e.g.\ an polynom fit of
     degree 4, which has to be restricted to the vincinity of \(T_c\) to
@@
     is plotted. This is a number which should combine the dependence on
-    the degree and the coupling constant.
+    the degree and the coupling constant. It is determined by summing
+    over the edge weights of all edges connected to a node and averaging
+    this value over all nodes. Alternatively it is the average edge weight
+    of all edges multiplied by the degree.
     The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}

### 2013-07-29 Tex/chapters/results.tex
Evolution des RNG kurz erläutert

@@
     \end{figure}\\
-    The explanation for the plateau of the RNG at low \(\sigma\) is similar.
-    On the RNG no new edges arise at small displacements of the nodes\footnote{See appendix \ref{appendix:RNGDisplacement} for a graphic.}\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.}.
+    The evolution of the RNG with increasing \(\sigma\) can be made plausible
+    with the same arguments. Fig. \ref{fig:RNG_sigma}
+    shows, that for \(\sigma \lesssim 0.1\) the square lattice character is
+    preserved -- no new edges arise neither many existing edges vanish, which
+    explains the plateau in the \(T_{c}\) diagram. With
+    increasing \(\sigma\), more and more edges vanish\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.},
+    thus reducing the degree and \(T_{c}\).
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][$\sigma = 0.09$]
+        {
+            \label{sfig:RNG_sigma:0.09}
+            \includegraphics[width=0.30\textwidth]{images/RNG/out009}
+        }
+        \subfigure[][$\sigma = 0.15$]
+        {
+            \label{sfig:RNG_sigma:0.15}
+            \includegraphics[width=0.30\textwidth]{images/RNG/out015}
+        }
+        \subfigure[][$\sigma = 0.21$]
+        {
+            \label{sfig:RNG_sigma:0.21}
+            \includegraphics[width=0.30\textwidth]{images/RNG/out021}
+        }
+
+        \caption[Anomaly of the RNG for Small $\sigma$]
+        {
+            RNG with periodic boundary conditions for different \(\sigma = 0\)
+        }
+        \label{fig:RNG_sigma}
+    \end{figure}\\
     But the degree does not alone influence the behavior of \(T_c\).

### 2013-07-29 Tex/chapters/model.tex
Spacing nach i.e. und e.g. korrigiert
Displacement Beschreibung leicht verbessert
Bildverweise präzisiert
Erwartungen etwas ausführlicher formuliert

@@
     The displacement is randomly Gauß distributed with the standard
-    deviation \(\sigma\), i.e. the \(x\) and \(y\) coordinates of the
+    deviation \(\sigma\), i.e.\ the \(x\) and \(y\) coordinates of the
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
@@
     \end{equation}
-    \[x \to x + \Delta x\]
-    \[y \to y + \Delta y\]
     \begin{figure}[htbp]
@@
     \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.
-    The boundary is periodic e.g. nodes near the right edge can be
+    The boundary is periodic e.g.\ nodes near the right edge can be
     connected to nodes near the left edge and vice versa. Analogous the
@@
     For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
-    for which exists an analytic solution \cite{Onsager1944}. And for
-    \(\sigma \gtrsim 1\) the nodes are distributed randomly. This case
-    is already studied for constant \(J\) on the Delaunay triangulation
-    in \cite{Janke1994}.\\
+    for which exists an analytic solution \cite{Onsager1944} for the
+    critical temperature
+    \begin{equation}
+        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
+        \label{eq:exactTc}
+    \end{equation}
+    and the critical exponents \(\alpha = 0\), \(\beta = \frac{1}{8}\)
+    and \(\gamma = -\frac{7}{4}\).\\
+    The case for randomly distributed sites \(\sigma \gtrsim 1\) is
+    already studied on a Delaunay triangulation. \cite{Janke1994} examines
+    this for constant \(J\) and \cite{Lima2000} for \(J_{ij} = e^{-\alpha d_{ij}}\).
+    Both articles conclude, that this model lies within the universality
+    class of the standard Ising model, i.e.\ has the same critical
+    exponents.
 
@@
     \(r = \frac d 2\) contains no other nodes. This area will be
-    called \emph{lune} in the following. See also Figure
-    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
+    called \emph{lune} in the following. See also the cross hatched region
+    from fig. \ref{fig:lunes}\subref{sfig:lunes:def}.\\
     The Relative Neighborhood graph (RNG) \cite{Toussaint1980} is a
@@
     circles with radius \(r = d\) and centers on \(i\) and \(j\).
-    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
+    See also the hatched region in fig. \ref{fig:lunes}\subref{sfig:lunes:def}.
     \begin{figure}[htbp]

### 2013-07-29 Tex/chapters/results.tex
Erwartungen etwas ausführlicher formuliert
Bild label korrigiert

@@
     gets \(T_c = 2.2689(2)\), which is in good agreement with the
-    exact solution from eq. \eqref{eq:exactTc} \cite{Onsager1944}.
-    \begin{equation}
-        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
-        \label{eq:exactTc}
-    \end{equation}
+    exact solution from eq. \eqref{eq:exactTc}.
     This test suggests, that measuring \(T_c\) this way is yields
@@
 
-        \caption[Anomaly of the GG for Small $\sigma$]
+        \caption[Examples of GG for different $\sigma$]
         {
@@
 
-        \caption[Anomaly of the RNG for Small $\sigma$]
+        \caption[Examples of RNG for different $\sigma$]
         {

### 2013-07-30 Tex/chapters/methods.tex
Ergänzungen zur autokorrelationszeit und dynamischem exponent

@@
         are independent, one calculates the normalized autocorrelation function
-        \(\frac{\chi(t)}{\chi(0)}\), which should decay exponentially
+        \(\frac{\chi(t)}{\chi(0)}\) with
+        \begin{equation}
+            \chi(t) = \int \de t' [m(t') -\avg{m}][m(t'+t)-\avg{m}]
+        \end{equation}
+        which should decay exponentially
         \(\chi(t) \propto \exp(t/\tau)\). This is visible in the half
@@
         \cite{SwendsenWang1987}. The dependence of the autocorrelation time
-        \(\tau\) on the system size \(L\) is then given by \(\tau \propto L^z\).
+        \(\tau\) on the system size \(L\) is at \(T_{c}\) given by \(\tau \propto L^z\).
+        More general the power law \(\tau \propto \xi^z\) holds true, where
+        \(\xi\) is the \emph{correlation length}, which diverges at
+        \(T_{c}\) and is then limited by the size of the simulated lattice.
         As mentioned in section \ref{sssec:wolff}, the Wolff cluster algorithm
@@
         time in dependence on temperature to change significantly as shown in
-        section \ref{sec:results}.
+        section \ref{ssec:results:autocorr}. Also according to \cite{NewmanBarkema1999}
+        \(z\) is independent of the lattice structure, which ensures that
+        the simulation will benefit from the Wolff cluster algorithm at
+        any \(\sigma\).

### 2013-07-30 Tex/chapters/results.tex
Ergänzungen zur autokorrelationszeit und dynamischem exponent

@@
 \subsection{Short Analysis of the Autocorrelation Time  $\tau$}
+\label{ssec:results:autocorr}
     % Sollte das hier rein?
@@
     temperature. The cause is probably the effectiveness of the Wolff cluster
-    algorithm at \(T_c\).
+    algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
     Obviously the autocorrelation time \(\tau\) increases with the system
-    size. In fact it obeys a power law, which is the expected behaivior of
-    a dynamical critical exponent \(z\) as mentioned in section \ref{sssec:eqtime}.
+    size. In fact it obeys a power law \(\tau \propto \L^z\), which is
+    the expected behavior of a dynamical exponent \(z\) as mentioned in
+    section \ref{sssec:eqtime}.
     In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
-    over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
-    This exponent is much higher than the one of Wolff cluster
-    algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
-    So it represents the dynamical exponent for parallel tempering with
-    Metropolis above criticality and thus is not exactly a critical exponent.
-    Nevertheless it is interesting, that it obeys a power law just the same.
-    Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
-    at criticality.
+    over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
+    not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
+    for the Wolff cluster algorithm. On the one hand the number of sweeps
+    in which \(\tau\) is measured in this thesis are more than a standard
+    Metropolis sweep to which \(z\) normally corresponds, thus \(z'\) would
+    need to be normalized by some factor \(>1\), because each sweep
+    alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
+    flipped. On the other hand the \(\tau\) used for the fit are not the
+    \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
+    Nevertheless it is interesting, that it obeys a power law
+    \(\tau \propto L^{z'}\) just the same. This suggests, that \(\xi \gtrsim L\)
+    is satisfied at the temperature of maximum \(\tau\) and that \(z'\) is a
+    valid upper bound of \(z\).
+    This proofs the effectiveness of the Wolff cluster algorithm at
+    criticality.\\
+    This is of course only a rough analysis of existing data which was
+    generated for another purpose. For a more in depth inspection, one
+    would perform the simulation at the critical point, which will be
+    determined in the next sections.
 

### 2013-07-30 Tex/chapters/acknowledgements.tex
dummy acknowledgement hinzugefügt

\addcontentsline{toc}{section}{Acknowledgements}
\section*{Acknowledgements}
Danke

### 2013-07-30 Tex/chapters/results.tex
ausführlichere Überleitung
Korrekturen vorheriger Irrtümer

@@
     in which \(\tau\) is measured in this thesis are more than a standard
-    Metropolis sweep to which \(z\) normally corresponds, thus \(z'\) would
-    need to be normalized by some factor \(>1\), because each sweep
+    Metropolis sweep to which \(z\) normally corresponds, because each sweep
     alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
@@
     \(\tau \propto L^{z'}\) just the same. This suggests, that \(\xi \gtrsim L\)
-    is satisfied at the temperature of maximum \(\tau\) and that \(z'\) is a
-    valid upper bound of \(z\).
-    This proofs the effectiveness of the Wolff cluster algorithm at
-    criticality.\\
+    is satisfied at the temperature of maximum \(\tau\), which is plausible,
+    because the peak in fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
+    is near \(T_{c}\).\\
+    Anyhow, fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
+    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
     This is of course only a rough analysis of existing data which was
@@
     methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
-    exponents.
+    exponents, which is performed in the next section. Also in \ref{ssec:binderIntersections}
+    an easier approach, which yields better values for \(T_{c}\), is presented.
 

### 2013-07-31 Tex/chapters/results.tex
Vorzeichen der Kritischen Exponenten korrigiert (hoffentlich)
finite size scaling und critical exponents  ausführlicher

@@
     Despite of this one can obtain \(T_c\) by finite size scaling
-    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
-    exponents, which is performed in the next section. Also in \ref{ssec:binderIntersections}
-    an easier approach, which yields better values for \(T_{c}\), is presented.
+    methods \cite[S. ??]{NewmanBarkema1999}, which also yield the critical
+    exponents. This will be performed in the next section.
+    Though there is an easier approach, which yields even more
+    precise values for \(T_{c}\), which is presented in \ref{ssec:binderIntersections}.
 
 \subsection{Critical Exponents}
+    The critical exponents define the course of an observable near its
+    divergence. For instance the vicinity of the divergence of the susceptibility
+    can be approximated by
+    \begin{equation}
+        \chi \propto \abs{T-T_{c}}^{-\beta}
+        \label{eq:critExp:beta}
+    \end{equation}
+    As the name critical \emph{exponent} suggests, this will often
+    be a power law. But not obligatory e.g.\ the critical "exponent" \(\alpha\)
+    corresponding to the divergence of the specific heat \(c\) for the two dimensional
+    Ising model diverges logarithmic and is nominally \(\alpha = 0\).
+    Because of this, \(\alpha\) will not be considered in this section.\\
+    The important property of the critical exponents is, that they are
+    universal for a model i.e.\ they are independent of the size, the structure
+    or the coupling constant \(J\) \cite{NewmanBarkema1999} of the lattice,
+    therefore they should also be independent of \(\sigma\).
     Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
-    varying coupling constants \(J\) suggest, that the
-    critical exponents should not be influenced by the disorder parameter
-    \(\sigma\). So they will be used for consistency cross checking and
-    comparison with the known exact values \cite[S. 59]{Pelissetto2002}.\\
+    varying coupling constants \(J\) confirm, that the
+    critical exponents are not influenced by an random lattice.
+    So they will be used for consistency cross checking and
+    comparison with the known exact values \cite[S. 59]{Pelissetto2002}.
+    If the critical exponents can be reproduced, the determined critical
+    temperatures are probably correct too.\\
     % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
-    For a more in depth look at finite size scaling, \cite{Norrenbrock2011}
-    offers an explanation.
-    It is known, that for large \(L\) near the critical temperature the
-    equations \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
-    \eqref{eq:fsscaling:g} apply.
+    To determine the critical exponents, the finite size scaling method
+    will be used. The here given explanation will give a rough idea, how
+    the method works, for a more in depth explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.
+    The crucial element is that there exists a \emph{scaling function},
+    which is valid for sufficiently large \(L\) near the critical
+    temperature \(T_{c}\) and has only an explicit \(L\) dependence.
+    One can then express some observables like in eq. \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
+    \eqref{eq:fsscaling:g}.
     \begin{align}
         \label{eq:fsscaling:m}
-        \avg{m_L} &= L^\frac{\beta}{\nu} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \avg{m_L} &= L^{-\frac{\beta}{\nu}} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
         \label{eq:fsscaling:chi}
-        \chi_L    &= L^\frac{\gamma}{\nu} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \chi_L    &= L^{\frac{\gamma}{\nu}} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
         \label{eq:fsscaling:g}
@@
     Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
-    are unknown scaling functions. To find the exponents
-    \(\beta, \gamma, \nu\) and the critical temperature \(T_c\), one
-    varies them until the measured values of the observables collapse on
-    one curve. Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
+    are the scaling functions.
+    To find the exponent e.g. \(\nu\), one takes \eqref{eq:fsscaling:g},
+    solves for \(\tilde{G}\), adjusts the axis to represent \(y=\tilde{G}(x)\),
+    and plots the measured observables for all \(L\).
+    Then one varies \(\nu\) and \(T_{c}\) until the plotted observables
+    collapse on one curve -- the scaling function.
+    Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
     collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
     %\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
+    The same principle can be used to determine the other two exponents.
     Note that \(L=16\) is not used for the collapse, because it is a
@@
     \end{figure}\\
-
     A finite size scaling analysis was
@@
             \midrule
-            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
+            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
             \midrule
-            GG           & 0.0 & 0.998(8) & -1.735(2) & 0.1262(4)\\
-                         & 0.1 & 0.999(19)& -1.744(5) & 0.133(6) \\
-                         & 0.3 & 1.029(30)& -1.724(16)& 0.129(12)\\
-                         & 0.5 & 1.006(5) & -1.750(12)& 0.125(13)\\
-                         & 1.0 & 1.038(32)& -1.743(17)& 0.123(16)\\
+            GG           & 0.0 & 0.998(8) & 1.735(2) & 0.1262(4)\\
+                         & 0.1 & 0.999(19)& 1.744(5) & 0.133(6) \\
+                         & 0.3 & 1.029(30)& 1.724(16)& 0.129(12)\\
+                         & 0.5 & 1.006(5) & 1.750(12)& 0.125(13)\\
+                         & 1.0 & 1.038(32)& 1.743(17)& 0.123(16)\\
             \midrule
-            RNG          & 0.0 & 0.992(11)& -1.740(2) & 0.130(1) \\
-                         & 0.1 & 0.987(12)& -1.746(5) & 0.133(4) \\
-                         & 0.2 & 1.010(9) & -1.756(14)& 0.123(10)\\
-                         & 0.5 & 1.010(16)& -1.750(16)& 0.143(13)\\
-                         & 1.0 & 1.013(6) & -1.758(16)& 0.138(13)\\
+            RNG          & 0.0 & 0.992(11)& 1.740(2) & 0.130(1) \\
+                         & 0.1 & 0.987(12)& 1.746(5) & 0.133(4) \\
+                         & 0.2 & 1.010(9) & 1.756(14)& 0.123(10)\\
+                         & 0.5 & 1.010(16)& 1.750(16)& 0.143(13)\\
+                         & 1.0 & 1.013(6) & 1.758(16)& 0.138(13)\\
             \bottomrule

### 2013-08-01 Tex/chapters/results.tex
Tc Werte mit ausgewiesen
Tabelle der Tc eingefügt

@@
     exponents. This will be performed in the next section.
-    Though there is an easier approach, which yields even more
-    precise values for \(T_{c}\), which is presented in \ref{ssec:binderIntersections}.
+    Though there is an easier approach, which yields comparable precise
+    values for \(T_{c}\) in a much faster and more robust way, which is
+    presented in \ref{ssec:binderIntersections}.
 
@@
     chapter in fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
+    The determined values are displayed in tab. \ref{tab:critExp}.
     The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
-    and the error of \(\nu\) is the standard deviation of the three obtained
-    values of \(\nu\).\\
+    and the error of \(T_c\) and \(\nu\) is the standard deviation of the
+    three obtained values.\\
     \begin{table}[htbp]
         \center
-        \begin{tabular}{l l l l l}
+        \begin{tabular}{l l l l l l}
             \toprule
-             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
+             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
             \midrule
-            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
+            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & 2.2691... & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
             \midrule
-            GG           & 0.0 & 0.998(8) & 1.735(2) & 0.1262(4)\\
-                         & 0.1 & 0.999(19)& 1.744(5) & 0.133(6) \\
-                         & 0.3 & 1.029(30)& 1.724(16)& 0.129(12)\\
-                         & 0.5 & 1.006(5) & 1.750(12)& 0.125(13)\\
-                         & 1.0 & 1.038(32)& 1.743(17)& 0.123(16)\\
+            GG           & 0.0 & 2.2687(5)& 0.998(8) & 1.735(2) & 0.1262(4)\\
+                         & 0.1 & 2.895(4) & 0.999(19)& 1.744(5) & 0.133(6) \\
+                         & 0.3 & 2.527(1) & 1.029(30)& 1.724(16)& 0.129(12)\\
+                         & 0.5 & 2.238(1) & 1.006(5) & 1.750(12)& 0.125(13)\\
+                         & 1.0 & 2.128(2) & 1.038(32)& 1.743(17)& 0.123(16)\\
             \midrule
-            RNG          & 0.0 & 0.992(11)& 1.740(2) & 0.130(1) \\
-                         & 0.1 & 0.987(12)& 1.746(5) & 0.133(4) \\
-                         & 0.2 & 1.010(9) & 1.756(14)& 0.123(10)\\
-                         & 0.5 & 1.010(16)& 1.750(16)& 0.143(13)\\
-                         & 1.0 & 1.013(6) & 1.758(16)& 0.138(13)\\
+            RNG          & 0.0 & 2.2689(7)& 0.992(11)& 1.740(2) & 0.130(1) \\
+                         & 0.1 & 2.2058(8)& 0.987(12)& 1.746(5) & 0.133(4) \\
+                         & 0.2 & 1.627(2) & 1.010(9) & 1.756(14)& 0.123(10)\\
+                         & 0.5 & 1.2825(7)& 1.010(16)& 1.750(16)& 0.143(13)\\
+                         & 1.0 & 1.2123(3)& 1.013(6) & 1.758(16)& 0.138(13)\\
             \bottomrule
@@
     Like in tab. \ref{tab:critExp} to see, most values
-    are matching the expectations. Especially \(\nu\) and \(\gamma\)
-    are always in very good agreement with their exact values. Because
-    there can never be to much cross- and consistency checks, the ratio
-    \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
+    are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
+    agreement with the known value. Especially \(\nu\) and \(\gamma\)
+    are always in very good agreement with their exact values. Besides the
+    good agreement of the by data collapse obtained values of \(\nu\) and \(\gamma\),
+    the ratio \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
     the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
@@
     left side and the GG on the right side.
-    In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).
+    And in tab. \ref{tab:critTemp} the values are displayed together with the
+    values obtained by the data collapse from the section before.
+    \begin{table}[htbp]
+        \center
+        \begin{tabular}{l @{\quad} l l @{\quad} l l}
+            \toprule
+             & \multicolumn{2}{c}{GG} & \multicolumn{2}{c}{RNG}\\
+            \midrule
+            \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)}\\
+            \midrule
+            0.00 & 2.2689(2)& 2.2687(5) & 2.2690(2)& 2.2689(7)\\
+            0.03 & 2.851(1) &           & 2.2679(4)&          \\
+            0.05 & 2.863(1) &           & 2.2662(5)&          \\
+            0.08 & 2.882(2) &           & 2.2548(6)&          \\
+            0.10 & 2.893(2) & 2.895(4)  & 2.205(1) & 2.2058(8)\\
+            0.12 & 2.903(3) &           & 2.1010(5)&          \\
+            0.15 & 2.903(3) &           & 1.898(2) &          \\
+            0.20 & 2.8274(6)&           & 1.624(1) & 1.627(2) \\
+            0.25 & 2.676(2) &           & 1.4812(5)&          \\
+            0.30 & 2.526(4) & 2.527(1)  & 1.407(2) &          \\
+            0.40 & 2.332(4) &           & 1.327(4) &          \\
+            0.50 & 2.233(7) & 2.238(1)  & 1.2818(2)& 1.2825(7)\\
+            0.60 & 2.183(3) &           & 1.252(2) &          \\
+            0.70 & 2.154(8) &           & 1.234(1) &          \\
+            0.80 & 2.140(3) &           & 1.223(1) &          \\
+            0.90 & 2.132(1) &           & 1.214(4) &          \\
+            1.00 & 2.121(8) & 2.128(2)  & 1.208(5) & 1.2123(3)\\
+            1.10 & 2.116(11)&           & 1.206(1) &          \\
+            1.20 & 2.113(4) &           & 1.204(2) &          \\
+            \bottomrule
+        \end{tabular}
+        \caption{Critical temperatures for different $\sigma$}
+        \label{tab:critTemp}
+    \end{table}\\
+    The values obtained through the data collapse and the values obtained
+    through the intersection of the binder cumulant are always in good
+    agreement and of comparable precision.\\
+    These values of \(T_c\) are plotted over \(\sigma\) in fig. \ref{fig:Tc}.
     \begin{figure}[htbp]

### 2013-08-01 Tex/chapters/methods.tex
Fehler und inkonsistenzen behoben
Überblick über die Observablen gegeben

@@
     \end{equation}
+    or any expected value of an observable
+    \begin{equation}
+        \avg{O} = \frac{1}{Z} \sum_i O_i e^{-\beta H_i}
+    \end{equation}
     one has to know the partition function
@@
     Monte Carlo simulations, which are introduced in the next chapter.\\
-    %~ Once one has obtained values for e.g.\ the magnetization \(m\), one
-    %~ can easily calculate the susceptibility
-    %~ \begin{equation}
-        %~ \chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}
-    %~ \end{equation}
-    % Bisschen erklæren, dass man aus m auch chi machen kann und auf literatur verweisen
+
+    The observables which are measured in this thesis, are the mean
+    magnetization per spin
+    \begin{equation}
+        m = \frac{1}{N} \sum_i s_i
+    \end{equation}
+    and the mean energy per spin
+    \begin{equation}
+        E = \frac{1}{N} \avg{H}
+    \end{equation}
+    As mentioned before, properties near the phase transition and the
+    critical temperature \(T_c\), where the phase transition occurs, will
+    be examined. The Ising system in two dimensions shows a second order
+    phase transition, hence \(m\) and \(E\) are continous, but show at
+    \(T_c\) an infinitly sharp slope i.e.\ the first derivative diverges.
+    From statistical physics (compare \cite{nolting2005}) is known, that
+    these derivatives can be expressed by fluctuations e.g.\ the specific
+    heat can be expressed as
+    \begin{equation}
+        c = \frac{\partial \avg{H}}{\partial T} = k_B \beta^2 \avg{\brac{H-\avg{H}}^2}
+    \end{equation}
+    The specific heat is a measure for how much energy is needed to change
+    the temperature of the system.
+    Analogical the susceptibility
+    \begin{equation}
+        \chi = N \beta \avg{\brac{m-\avg{m}}^2}
+    \end{equation}
+    is a measure for how strong an outer magnetic field changes the
+    magnetization of the system.
+    Beside these observables from classical physics, a fifth observable
+    the binder cumulant \cite{Binder1981}
+    \begin{equation}
+        g = \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}}
+        \label{eq:binder}
+    \end{equation}
+    is considered.
+    This is a dimensionless value, which can be used to determine the
+    critical point. These five observables will be sufficient to analyse
+    the phase transition in the scope of this bachelor thesis. All of them
+    can be easily computed when \(m\) and \(E\) are measured. The next
+    chapter will show, how to get estimates for them through Monte Carlo
+    simulations.
 
@@
     the observable, which should be measured, and estimate the mean of the observable from
-    this samples. In example the Monte Carlo integration chooses random
+    this samples. As an example the Monte Carlo integration chooses random
     points within the bounding box of the function and estimates the integral
@@
     In statistical physics the expected value of an observable \(O\)
-    is calculated by
+    is -- as also noted above -- calculated by
     \begin{equation}
@@
         is reached, by observing the change of the observables over the
-        progressing simulation, as pictured in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
+        progressing simulation, as pictured in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
         The count of sweeps till
@@
         In fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
-        the equilibrium is reached after approximately \(N=50\) sweeps for
+        the equilibrium is reached after approximately \(N_{s} \approx 50\) sweeps for
         either an initial condition of all spins up and all spins random. It

### 2013-08-01 Tex/chapters/model.tex
Vorzeichen fehler in gamma korrigiert (hoffentlich)
Graphen etwas weiter ausgeführt

@@
     and the critical exponents \(\alpha = 0\), \(\beta = \frac{1}{8}\)
-    and \(\gamma = -\frac{7}{4}\).\\
+    and \(\gamma = \frac{7}{4}\).\\
     The case for randomly distributed sites \(\sigma \gtrsim 1\) is
@@
 \label{ssec:graphtypes}
-    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\).\\
+    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\). In the
+    scope of this model, the nodes get identified with the sites of the
+    lattice and the edges signal the neighbor status of two sites. If the
+    corresponding nodes are connected, the sites are neighbors.\\
     All here mentioned graph types are \emph{proximity graphs}. They are
@@
     resemble a rectangular bounding box of the lune. Most pairs will be
-    far away from each other and the cells in the middle of the bounding
-    box are completely inside the lune so that only one node has to be
-    tested to discard an edge between them. Connected nodes are near to
-    each other so that only very few cells have to be tested.\\
+    far away from each other and there will be one or more cells in the
+    middle of the bounding box, which are completely inside the lune so.
+    Then only one node has to be tested from such a cell to discard an
+    edge between the nodes. On the other hand nodes, that will be connected,
+    are near to each other so that only very few cells intersect the bounding
+    box of their lune and consequently only very few nodes have to be tested.\\
     Indeed this method reduced the time needed to construct a RNG with

### 2013-08-01 Tex/chapters/results.tex
Überblick über die Observablen gegeben
Kleinere Fehlerbereinigungen

@@
     \begin{equation}
-        \chi \propto \abs{T-T_{c}}^{-\beta}
+        \chi \propto \abs{T-T_{c}}^{-\gamma}
+        \label{eq:critExp:gamma}
+    \end{equation}
+    And the infinite slope of the magnetization can be approximated in
+    the direction of lower \(T\) by
+    \begin{equation}
+        m \propto \abs{T-T_{c}}^{-\beta}
         \label{eq:critExp:beta}
@@
     As the name critical \emph{exponent} suggests, this will often
-    be a power law. But not obligatory e.g.\ the critical "exponent" \(\alpha\)
-    corresponding to the divergence of the specific heat \(c\) for the two dimensional
-    Ising model diverges logarithmic and is nominally \(\alpha = 0\).
-    Because of this, \(\alpha\) will not be considered in this section.\\
+    be a power law, as in the both examples above. But not obligatory e.g.\
+    the critical "exponent" \(\alpha\) corresponding to the divergence of
+    the specific heat \(c\) diverges logarithmic for the two dimensional
+    Ising model and is nominally \(\alpha = 0\).
+    For that reason, \(\alpha\) will not be considered in this section.\\
     The important property of the critical exponents is, that they are
@@
         \label{eq:fsscaling:g}
-        g          &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}} \propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
+        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
     \end{align}
     Where \(g\) from eq. \eqref{eq:fsscaling:g} is a normalized
-    Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
+    Binder cumulant (see eq. \eqref{eq:binder}) and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
     are the scaling functions.
@@
     Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
-    shows the collapse for the mean absolute magnetisation per site \(\avg{\abs{m}}\) for \(\sigma=0\),
+    shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=0\),
     to determine the exponents \(\beta\) and \(\nu\).
@@
         }
-        \subfigure[Magnetisation $\avg{\abs{m}}$][]
+        \subfigure[Magnetization $\avg{\abs{m}}$][]
         {
@@
         }
-        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
+        \subfigure[Finite Size Scaling of the Magnetization $\avg{\abs{m}}$][]
         {
@@
         \end{tabular}
-        \caption{Critical exponents for different $\sigma$}
+        \caption[Critical Exponents for Different $\sigma$]{Critical exponents for different $\sigma$}
         \label{tab:critExp}
@@
         \end{tabular}
-        \caption{Critical temperatures for different $\sigma$}
+        \caption[Critical Temperatures for Different $\sigma$]{Critical temperatures for different $\sigma$}
         \label{tab:critTemp}

### 2013-08-01 Tex/chapters/results.tex
Tabelle leicht verschönert
Ergänzung zum Grad K

@@
         \center
-        \begin{tabular}{l @{\quad} l l @{\quad} l l}
+        \begin{tabular}{l l l l l}
             \toprule
              & \multicolumn{2}{c}{GG} & \multicolumn{2}{c}{RNG}\\
-            \midrule
+            \cmidrule(rl){2-3} \cmidrule(rl){4-5}
             \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)}\\
@@
     \begin{equation}
-        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}
+        K = \frac{1}{N} \sum_{\avg{i,j}} 1
         \label{eq:degree}
@@
     one recognizes, that \(T_c\) and \(K\) are evidently correlated.
+    The values for \(K\) are obtained as an average over \(100\)
+    realizations of each graph type for \(L=16\) and \(L=32\) lattices.
+    In fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
+    one can see, that these curves are almost identical and the small
+    errorbars suggest, that they are sufficiently precise for this purpose.
     It seems reasonable to normalize \(T_c\) by the degree of the underlying
-    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
+    graph. This is done in fig. \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
     Indeed the normalization eliminates the jump and reduces the

### 2013-08-02 Tex/chapters/results.tex
Kleine Erklärung yu Fehlerwerten

@@
 to simulate enough uncorrelated states for each realization, to keep
-the \(\Delta \overline{\avg{O}}\) small.
+the \(\Delta \overline{\avg{O}}\) small. For every determined value an
+error is calculated and given in the form \texttt{value(error of last digit)}.
+The error given for fits are the asymptotic standard errors as calculated
+by gnuplot\footnote{An open source plotting program, used for all plots and fits in this thesis. \url{http://gnuplot.info/}.}.
 
@@
             \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
-                size scaling
+                size scaling (errors are for clarity not given, see \ref{tab:critExp})
         }

### 2013-08-02 Tex/chapters/results.tex
Collapse Besipiele nicht nur für sigma = 0

@@
     The values for \(\nu\) are yielded by every collapse and are therefore
-    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_sus}\subref{sfig:gettingCrit:collapse_s_0_sus}
+    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_sus}\subref{sfig:gettingCrit:collapse_s_1_sus}
     show an example collapse for \(\sigma=0\) of the magnetic susceptibility
@@
     This way the exponents \(\gamma\) and \(\nu\) are determined.
-    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
+    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
     shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=0\),
@@
         {
-            \label{sfig:gettingCrit:s_0_sus}
-            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
+            \label{sfig:gettingCrit:s_1_sus}
+            \includegraphics[width=0.47\textwidth]{plots/s_1_sus}
         }
@@
         {
-            \label{sfig:gettingCrit:collapse_s_0_sus}
-            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
+            \label{sfig:gettingCrit:collapse_s_1_sus}
+            \includegraphics[width=0.47\textwidth]{plots/collapse_s_1_sus}
         }
@@
         {
-            \label{sfig:gettingCrit:s_0_meanM}
-            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
+            \label{sfig:gettingCrit:s_1_meanM}
+            \includegraphics[width=0.47\textwidth]{plots/s_1_meanM}
         }
@@
         {
-            \label{sfig:gettingCrit:collapse_s_0_meanM}
-            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
+            \label{sfig:gettingCrit:collapse_s_1_meanM}
+            \includegraphics[width=0.47\textwidth]{plots/collapse_s_1_meanM}
         }
@@
         {
-            \subref{sfig:gettingCrit:s_0_sus} The susceptibility \(\chi\)
-                of an square lattice Ising model (\(\sigma=0\))\\
-            \subref{sfig:gettingCrit:collapse_s_0_sus} collapsed by finite
-                size scaling\\
-            \subref{sfig:gettingCrit:s_0_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
-                of an square lattice Ising model (\(\sigma=0\))\\
-            \subref{sfig:gettingCrit:collapse_s_0_meanM} collapsed by finite
-                size scaling
+            \subref{sfig:gettingCrit:s_1_sus} The susceptibility \(\chi\)
+                of an Ising model on an RNG \(\sigma=1\)\\
+            \subref{sfig:gettingCrit:collapse_s_1_sus} collapsed by finite
+                size scaling (for error estimates see \ref{tab:critExp})\\
+            \subref{sfig:gettingCrit:s_1_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
+                of an Ising model on an GG \(\sigma=1\)\\
+            \subref{sfig:gettingCrit:collapse_s_1_meanM} collapsed by finite
+                size scaling (for error estimates see \ref{tab:critExp})
         }

### 2013-08-02 Tex/chapters/conclusion.tex
Tippfehler beseitigt
Etwas ausführlicher beschrieben, was getan wurde

@@
-In this thesis the properties of the disordered Ising ferromagnet on two
-proximity graphs was studied. This model is within the universality of
-the standard Ising ferromagnet. Its critical temperature decreases with
-increasing disorder on a RNG. On a GG it first jumps, increases up to
-a maximum and decreases after that. The course of the critical
-temperatures can be made plausible observing the degree of the underlying
-graph, but no explicit formular was found.
+In this thesis the properties of an Ising ferromagnet, which nodes are
+moved by an gauss distributed displacement, is studied. The neighbor
+relationship is provided by two proximity graphs -- the RNG and the GG.
+The coupling constants are distance dependend. This model is within the
+universality of the standard Ising ferromagnet. Its critical temperature
+decreases with increasing disorder on a RNG. On a GG it first jumps,
+increases up to a maximum and decreases after that. The course of the
+critical temperatures can be made plausible observing the degree of the
+underlying graph, but no explicit formular was found.
 
@@
     more universal property.\\
-    Also it would be interesting to compare this results with a the
+    Also it would be interesting to compare this results with the
     results obtained by the same experiments with \(\alpha = 0\), which

### 2013-08-02 Tex/chapters/results.tex
fehlendes tab. ergänyt
Fehlerkorrekturen, Verbesserungen

@@
     In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
-    the autocorrelation time for the magnetization per site \(m\) at \(\sigma=0\) is plotted.
+    the autocorrelation time for the magnetization per site \(m\) at
+    \(\sigma=0\) is plotted. Note, that these are the unrounded values
+    of tab. \ref{tab:tauAndTeq}
     \begin{figure}[htbp]
@@
     Obviously the autocorrelation time \(\tau\) increases with the system
-    size. In fact it obeys a power law \(\tau \propto \L^z\), which is
+    size. In fact it obeys a power law \(\tau \propto L^z\), which is
     the expected behavior of a dynamical exponent \(z\) as mentioned in
@@
             \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
-                size scaling (errors are for clarity not given, see \ref{tab:critExp})
+                size scaling (errors are for clarity not given, see tab. \ref{tab:critExp})
         }
@@
             \subref{sfig:gettingCrit:collapse_s_1_sus} collapsed by finite
-                size scaling (for error estimates see \ref{tab:critExp})\\
+                size scaling (for error estimates see tab. \ref{tab:critExp})\\
             \subref{sfig:gettingCrit:s_1_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
@@
             \subref{sfig:gettingCrit:collapse_s_1_meanM} collapsed by finite
-                size scaling (for error estimates see \ref{tab:critExp})
+                size scaling (for error estimates see tab. \ref{tab:critExp})
         }

### 2013-08-13 Tex/chapters/appendix.tex
Evolution des RNG kurz erläutert
Kontinuität: c jetzt immer klein
Anhang mit Ergebnissen für alpha=0, normierung mit K

@@
-\section{Finite Size Effects at the Example of the Specific Heat}
+\section{Appendix}
+\subsection{Finite Size Effects at the Example of the Specific Heat}
 \label{appendix:finiteSizeEffects}
@@
     \begin{equation}
-        C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
+        c = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
     \end{equation}
@@
 
-\section{Effect of $\sigma$ on the RNG}
-\label{appendix:RNGDisplacement}
-    todo: RNG Bilder mit versch. sigma
+\subsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
+\label{appendix:fixedCoupling}
+    A quick analysis of this model with fixed coupling constants \(J = 1\)
+    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in fig. \ref{fig:Tc_deg_A0}.
+    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in fig. \ref{fig:Tc_deg}
+    for variable \(J\) (i.e.\ \(\alpha=0.5\)). This suggests, that the
+    disappearance of the jump is a random special case for the function
+    \(J_{ij}=e^{\alpha(1-d)}\).\\
+    The simulations were carried out on \(L \in \{16,32,64\}\) lattices
+    for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
+    Every other parameter was kept. Also note that the degree \(K\) is
+    the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
+    because it is obviously independent of \(J\).
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[][]
+        {
+            \label{sfig:Tc:RNG_A0}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:Tc:GG_A0}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
+        }
+
+        \subfigure[][]
+        {
+            \label{sfig:Tc_norm_deg:RNG_A0}
+            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_A0}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:Tc_norm_deg:GG_A0}
+            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_A0}
+        }
+
+        \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
+        {
+            Top: Critical Temperature \(T_c\) of the graph over different
+            disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
+            \subref{sfig:deg:RNG} the RNG and
+            \subref{sfig:deg:GG} the GG.\\
+            Bottom: Critical temperatures normalized by degree \(K\) over
+            different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
+            \subref{sfig:Tc_norm_deg:RNG} the RNG and
+            \subref{sfig:Tc_norm_deg:GG} the GG.
+        }
+        \label{fig:Tc_deg_A0}
+    \end{figure}\\

### 2013-08-13 Tex/chapters/results.tex
Anmerkung zum chi max fit
Anhang mit Ergebnissen für alpha=0, normierung mit K

@@
     the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
+    Note that the maximum of the measured \(\chi\). Because there were
+    many measurements in the vicinity of \(T_c\) (compare fig. \ref{sfig:gettingCrit:s_1_sus}),
+    this should give a reasonable estimate, without the need to
+    interpolate a maximum.
     The results are displayed in fig. \ref{fig:susCrossCheck}. The ratios
@@
     realizations of each graph type for \(L=16\) and \(L=32\) lattices.
+    Note that \(K\) is independent of \(L\) because of the periodic boundary.
     In fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
@@
     slope of the rising on the GG. Hence it reduces differences
-    between the RNG and the GG.
+    between the RNG and the GG. But the elimination of the jump is
+    unfortunately random and probably caused by a lucky choice of the
+    function, which determines the coupling constants \(J\). As proof for
+    this claim in appendix \ref{appendix:fixedCoupling} the same analysis
+    is performed for a model with fixed \(J\). There the jump gets narrower
+    but is still existent. Anyway, the degree seems to have an impact on
+    the critical temperature \(T_c\) but it is not a trivial one.
     \begin{figure}[htbp]

### 2013-08-13 Tex/chapters/appendix.tex
abstand hinter fig. und tab. korrigiert

@@
 \label{appendix:finiteSizeEffects}
-    In fig. \ref{fig:smeared_out_appendix} the specific heat
+    In fig.\ \ref{fig:smeared_out_appendix} the specific heat
     \begin{equation}
@@
     A quick analysis of this model with fixed coupling constants \(J = 1\)
-    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in fig. \ref{fig:Tc_deg_A0}.
-    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in fig. \ref{fig:Tc_deg}
+    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in fig.\ \ref{fig:Tc_deg_A0}.
+    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in fig.\ \ref{fig:Tc_deg}
     for variable \(J\) (i.e.\ \(\alpha=0.5\)). This suggests, that the

### 2013-08-13 Tex/chapters/methods.tex
Abstand dt zu Integral korrigiert
Fehlerkorrekturen, Verbesserungen
abstand hinter fig. und tab. korrigiert

@@
         Z = \sum_i p_i = \sum_i e^{-\beta H_i}
+        \label{eq:partitionFunction}
     \end{equation}
@@
     Because every site can have two states, there are \(2^N\) different
-    states of the system, which have to be summed up to gain \(Z\).
+    states of the system. For each the energy \(H_i\) has to be calculated
+    to solve the sum from eq. \eqref{eq:partitionFunction} to gain \(Z\).
     Hence for small \(N\) the partition function is computable, but the system
@@
         is reached, by observing the change of the observables over the
-        progressing simulation, as pictured in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
+        progressing simulation, as pictured in fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
         The count of sweeps till
@@
         All measurements should start after this time.\\
-        In fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
+        In fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
         the equilibrium is reached after approximately \(N_{s} \approx 50\) sweeps for
@@
         \begin{equation}
-            \chi(t) = \int \de t' [m(t') -\avg{m}][m(t'+t)-\avg{m}]
+            \chi(t) = \int \mathrm{d} t' \, [m(t') -\avg{m}][m(t'+t)-\avg{m}]
         \end{equation}

### 2013-08-13 Tex/chapters/results.tex
abstand hinter fig. und tab. korrigiert

@@
 (see also \ref{sssec:eqtime}). The used values for different system sizes
-are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
+are listed in tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
 the \(t_{eq}\) values are generously rounded up to be on the safe side
@@
     \(\sigma=0\) is plotted. Note, that these are the unrounded values
-    of tab. \ref{tab:tauAndTeq}
+    of tab.\ \ref{tab:tauAndTeq}
     \begin{figure}[htbp]
@@
     section \ref{sssec:eqtime}.
-    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
+    In fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
     over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
@@
     is satisfied at the temperature of maximum \(\tau\), which is plausible,
-    because the peak in fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
+    because the peak in fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
     is near \(T_{c}\).\\
-    Anyhow, fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
+    Anyhow, fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
     proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
@@
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
+    will diverge. In fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
     it is easy to see that the steep decline of \(\avg{|m|}\)
@@
     transition. This is stronger for smaller system sizes, as is visible
-    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
+    in fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
     Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
@@
     collapse on one curve -- the scaling function.
-    Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
-    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
+    Like the obersables from fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
+    collapse in fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
     %\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
@@
             \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
-                size scaling (errors are for clarity not given, see tab. \ref{tab:critExp})
+                size scaling (errors are for clarity not given, see tab.\ \ref{tab:critExp})
         }
@@
     This way the exponents \(\gamma\) and \(\nu\) are determined.
-    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
+    Analogical fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
     shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=0\),
@@
     Also the collapse of the binder cumulant as mentioned before and shown
-    in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
+    in fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
     is used to get a further value of \(\nu\).
@@
             \subref{sfig:gettingCrit:collapse_s_1_sus} collapsed by finite
-                size scaling (for error estimates see tab. \ref{tab:critExp})\\
+                size scaling (for error estimates see tab.\ \ref{tab:critExp})\\
             \subref{sfig:gettingCrit:s_1_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
@@
             \subref{sfig:gettingCrit:collapse_s_1_meanM} collapsed by finite
-                size scaling (for error estimates see tab. \ref{tab:critExp})
+                size scaling (for error estimates see tab.\ \ref{tab:critExp})
         }
@@
     decline at \(\sigma = 0.5\). This will be shown in the next
-    chapter in fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
-    The determined values are displayed in tab. \ref{tab:critExp}.
+    chapter in fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
+    The determined values are displayed in tab.\ \ref{tab:critExp}.
     The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
@@
     \end{table}\\
-    Like in tab. \ref{tab:critExp} to see, most values
+    Like in tab.\ \ref{tab:critExp} to see, most values
     are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
@@
     Note that the maximum of the measured \(\chi\). Because there were
-    many measurements in the vicinity of \(T_c\) (compare fig. \ref{sfig:gettingCrit:s_1_sus}),
+    many measurements in the vicinity of \(T_c\) (compare fig.\ \ref{sfig:gettingCrit:s_1_sus}),
     this should give a reasonable estimate, without the need to
     interpolate a maximum.
-    The results are displayed in fig. \ref{fig:susCrossCheck}. The ratios
+    The results are displayed in fig.\ \ref{fig:susCrossCheck}. The ratios
     determined by this method confirm the values obtained by collapse.
@@
     \end{figure}\\
-    As an example take fig. \ref{fig:gettingCrit:binder_fit_s_0}.
+    As an example take fig.\ \ref{fig:gettingCrit:binder_fit_s_0}.
     Here such interpolations are plotted for \(\sigma=0\) and are
@@
     left side and the GG on the right side.
-    And in tab. \ref{tab:critTemp} the values are displayed together with the
+    And in tab.\ \ref{tab:critTemp} the values are displayed together with the
     values obtained by the data collapse from the section before.
@@
     agreement and of comparable precision.\\
-    These values of \(T_c\) are plotted over \(\sigma\) in fig. \ref{fig:Tc}.
+    These values of \(T_c\) are plotted over \(\sigma\) in fig.\ \ref{fig:Tc}.
     \begin{figure}[htbp]
@@
     If one plots the degree of the graphs at different \(\sigma\) like
-    in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
+    in fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
     one recognizes, that \(T_c\) and \(K\) are evidently correlated.
@@
     Note that \(K\) is independent of \(L\) because of the periodic boundary.
-    In fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
+    In fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
     one can see, that these curves are almost identical and the small
@@
     It seems reasonable to normalize \(T_c\) by the degree of the underlying
-    graph. This is done in fig. \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
+    graph. This is done in fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
     Indeed the normalization eliminates the jump and reduces the
@@
     by the definition of the GG and its aftereffects for
-    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
+    the transition from \(\sigma = 0\). Visible in fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
     a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
@@
     Then more edges disappear, than appear at further displacement. This
-    is not an obvious effect, but can be seen in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
+    is not an obvious effect, but can be seen in fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
     \begin{figure}[htbp]
@@
     which changes with \(\sigma\).
-    Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
+    Therefore  in fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
     the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
@@
     \end{figure}\\
-    Considering both plots in fig. \ref{fig:TcG}, \(g_c\) is for low
+    Considering both plots in fig.\ \ref{fig:TcG}, \(g_c\) is for low
     \(\sigma\) obviously always bigger than the known value. Though the

### 2013-08-13 Tex/chapters/model.tex
Seitenyahlen bei den cite{} korrigiert

@@
     from a Gauß distribution eq. \eqref{eq:gauss}.
-    This is sketched in fig. \ref{fig:displacement}.
+    This is sketched in fig.\ \ref{fig:displacement}.
     \begin{equation}
@@
     top and bottom edges are connected. One can imagine that the model
-    lives on the surface of a torus as pictured in fig. \ref{fig:torusRNG}.
+    lives on the surface of a torus as pictured in fig.\ \ref{fig:torusRNG}.
     In subsequent graphics, the graphs will be unwrapped to rectangular
@@
     called \emph{lune} in the following. See also the cross hatched region
-    from fig. \ref{fig:lunes}\subref{sfig:lunes:def}.\\
+    from fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.\\
     The Relative Neighborhood graph (RNG) \cite{Toussaint1980} is a
@@
     circles with radius \(r = d\) and centers on \(i\) and \(j\).
-    See also the hatched region in fig. \ref{fig:lunes}\subref{sfig:lunes:def}.
+    See also the hatched region in fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.
     \begin{figure}[htbp]

### 2013-08-13 Tex/chapters/results.tex
Seitenyahlen bei den cite{} korrigiert

@@
     Despite of this one can obtain \(T_c\) by finite size scaling
-    methods \cite[S. ??]{NewmanBarkema1999}, which also yield the critical
+    methods \cite[p. 232ff]{NewmanBarkema1999}, which also yield the critical
     exponents. This will be performed in the next section.
@@
     So they will be used for consistency cross checking and
-    comparison with the known exact values \cite[S. 59]{Pelissetto2002}.
+    comparison with the known exact values \cite[p. 59]{Pelissetto2002}.
     If the critical exponents can be reproduced, the determined critical

### 2013-08-13 Tex/chapters/appendix.tex
kleine Korrekturen

@@
         {
-            Effects of different system sizes at \(\sigma = 0\). Dotted lines
-            are guides to the eye.
+            Effects of different system sizes on the specific heat at \(c\)
+            \(\sigma = 0\). Dotted lines are guides to the eye.
         }
@@
     disappearance of the jump is a random special case for the function
-    \(J_{ij}=e^{\alpha(1-d)}\).\\
+    \(J_{ij}=e^{\alpha(1-d_{ij})}\).\\
     The simulations were carried out on \(L \in \{16,32,64\}\) lattices

### 2013-08-13 Tex/chapters/appendix.tex
Klarstellungen

--- 2013-08-13 Tex/chapters/appendix.tex
@@
         {
-            Effects of different system sizes at \(\sigma = 0\). Dotted lines
-            are guides to the eye.
+            Effects of different system sizes on the specific heat \(c\)
+            at \(\sigma = 0\). Dotted lines are guides to the eye.
         }
@@
     The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in fig.\ \ref{fig:Tc_deg}
-    for variable \(J\) (i.e.\ \(\alpha=0.5\)). This suggests, that the
+    for variable \(J\) with \(\alpha=0.5\). This suggests, that the
     disappearance of the jump is a random special case for the function
-    \(J_{ij}=e^{\alpha(1-d)}\).\\
+    \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
     The simulations were carried out on \(L \in \{16,32,64\}\) lattices

### 2013-08-13 Tex/chapters/results.tex
Weitere Verbesserungen der Form

@@
 graphs with the same disorder parameter \(\sigma\) are then averaged to
-\(\overline{\avg{O}}\). Not only the seed to generate the new random
+\(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
+are omitted in the following for the sake of simplicity.\\
+Not only the seed to generate the new random
 realization of the proximity graph gets changed, but also the seed for
@@
 The error given for fits are the asymptotic standard errors as calculated
-by gnuplot\footnote{An open source plotting program, used for all plots and fits in this thesis. \url{http://gnuplot.info/}.}.
+by gnuplot. Gnuplot is an open source plotting program, used for all plots
+and fits in this thesis \footnote{\url{http://gnuplot.info/}.}.
 
@@
     normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
-    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
+    fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
     jump on the GG arises again, but \(T_c\) is now monotonically
@@
     Moreover the forms of both curves are quite similar, but the
-    one for the RNG \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
+    one for the RNG in fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
     is generally lower and spans over a bigger temperature range than
-    the curve of the GG \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
+    the curve of the GG in fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
     Both graph types have a plateau at \(0 < \sigma < 0.1\). So small

### 2013-08-13 Tex/chapters/results.tex
Neues Unterkapitel "Technische Details" zugefügt

@@
+\subsection{Technical Details}
     The generation of the Graphs and the Monte Carlo Simulation are implemented
@@
     All source code is available at \url{https://github.com/surt91/IsingFerromagnet}.\\
+    Most simulations were carried out on HERO, the \emph{H}igh-\emph{E}nd
+    Computing \emph{R}esource \emph{O}ldenburg.\\
 
@@
     \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
-are omitted in the following for the sake of simplicity.\\
+    are omitted in the following for the sake of simplicity, so that the
+    it will be just called \(O\).\\
     Not only the seed to generate the new random

### 2013-08-13 Tex/chapters/results.tex
Korrekturen an der Kontinuität

@@
     values for \(T_{c}\) in a much faster and more robust way, which is
-    presented in \ref{ssec:binderIntersections}.
+    presented in section \ref{ssec:binderIntersections}.
 
@@
     As the name critical \emph{exponent} suggests, this will often
-    be a power law, as in the both examples above. But not obligatory e.g.\
+    be a power law, as in both examples above. But not obligatory e.g.\
     the critical "exponent" \(\alpha\) corresponding to the divergence of
@@
     averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_sus}\subref{sfig:gettingCrit:collapse_s_1_sus}
-    show an example collapse for \(\sigma=0\) of the magnetic susceptibility
+    show an example collapse for \(\sigma=1\) of the magnetic susceptibility
     \begin{equation}
@@
     Analogical fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
-    shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=0\),
+    shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\),
     to determine the exponents \(\beta\) and \(\nu\).
@@
             \midrule
+            RNG          & 0.0 & 2.2689(7)& 0.992(11)& 1.740(2) & 0.130(1) \\
+                         & 0.1 & 2.2058(8)& 0.987(12)& 1.746(5) & 0.133(4) \\
+                         & 0.2 & 1.627(2) & 1.010(9) & 1.756(14)& 0.123(10)\\
+                         & 0.5 & 1.2825(7)& 1.010(16)& 1.750(16)& 0.143(13)\\
+                         & 1.0 & 1.2123(3)& 1.013(6) & 1.758(16)& 0.138(13)\\
+            \midrule
             GG           & 0.0 & 2.2687(5)& 0.998(8) & 1.735(2) & 0.1262(4)\\
@@
                          & 1.0 & 2.128(2) & 1.038(32)& 1.743(17)& 0.123(16)\\
-            \midrule
-            RNG          & 0.0 & 2.2689(7)& 0.992(11)& 1.740(2) & 0.130(1) \\
-                         & 0.1 & 2.2058(8)& 0.987(12)& 1.746(5) & 0.133(4) \\
-                         & 0.2 & 1.627(2) & 1.010(9) & 1.756(14)& 0.123(10)\\
-                         & 0.5 & 1.2825(7)& 1.010(16)& 1.750(16)& 0.143(13)\\
-                         & 1.0 & 1.2123(3)& 1.013(6) & 1.758(16)& 0.138(13)\\
+
             \bottomrule
@@
     the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
-    Note that the maximum of the measured \(\chi\). Because there were
+    %~ Note that the maximum of the measured \(\chi\).
+    Because there were
     many measurements in the vicinity of \(T_c\) (compare fig.\ \ref{sfig:gettingCrit:s_1_sus}),
@@
             \toprule
-             & \multicolumn{2}{c}{GG} & \multicolumn{2}{c}{RNG}\\
+             & \multicolumn{2}{c}{RNG} & \multicolumn{2}{c}{GG}\\
             \cmidrule(rl){2-3} \cmidrule(rl){4-5}
@@
             \midrule
-            0.00 & 2.2689(2)& 2.2687(5) & 2.2690(2)& 2.2689(7)\\
-            0.03 & 2.851(1) &           & 2.2679(4)&          \\
-            0.05 & 2.863(1) &           & 2.2662(5)&          \\
-            0.08 & 2.882(2) &           & 2.2548(6)&          \\
-            0.10 & 2.893(2) & 2.895(4)  & 2.205(1) & 2.2058(8)\\
-            0.12 & 2.903(3) &           & 2.1010(5)&          \\
-            0.15 & 2.903(3) &           & 1.898(2) &          \\
-            0.20 & 2.8274(6)&           & 1.624(1) & 1.627(2) \\
-            0.25 & 2.676(2) &           & 1.4812(5)&          \\
-            0.30 & 2.526(4) & 2.527(1)  & 1.407(2) &          \\
-            0.40 & 2.332(4) &           & 1.327(4) &          \\
-            0.50 & 2.233(7) & 2.238(1)  & 1.2818(2)& 1.2825(7)\\
-            0.60 & 2.183(3) &           & 1.252(2) &          \\
-            0.70 & 2.154(8) &           & 1.234(1) &          \\
-            0.80 & 2.140(3) &           & 1.223(1) &          \\
-            0.90 & 2.132(1) &           & 1.214(4) &          \\
-            1.00 & 2.121(8) & 2.128(2)  & 1.208(5) & 1.2123(3)\\
-            1.10 & 2.116(11)&           & 1.206(1) &          \\
-            1.20 & 2.113(4) &           & 1.204(2) &          \\
+            0.00 & 2.2690(2)& 2.2689(7)& 2.2689(2)& 2.2687(5\\
+            0.03 & 2.2679(4)&          & 2.851(1) &         \\
+            0.05 & 2.2662(5)&          & 2.863(1) &         \\
+            0.08 & 2.2548(6)&          & 2.882(2) &         \\
+            0.10 & 2.205(1) & 2.2058(8)& 2.893(2) & 2.895(4)\\
+            0.12 & 2.1010(5)&          & 2.903(3) &         \\
+            0.15 & 1.898(2) &          & 2.903(3) &         \\
+            0.20 & 1.624(1) & 1.627(2) & 2.8274(6)&         \\
+            0.25 & 1.4812(5)&          & 2.676(2) &         \\
+            0.30 & 1.407(2) &          & 2.526(4) & 2.527(1)\\
+            0.40 & 1.327(4) &          & 2.332(4) &         \\
+            0.50 & 1.2818(2)& 1.2825(7)& 2.233(7) & 2.238(1)\\
+            0.60 & 1.252(2) &          & 2.183(3) &         \\
+            0.70 & 1.234(1) &          & 2.154(8) &         \\
+            0.80 & 1.223(1) &          & 2.140(3) &         \\
+            0.90 & 1.214(4) &          & 2.132(1) &         \\
+            1.00 & 1.208(5) & 1.2123(3)& 2.121(8) & 2.128(2)\\
+            1.10 & 1.206(1) &          & 2.116(11)&         \\
+            1.20 & 1.204(2) &          & 2.113(4) &         \\
             \bottomrule
@@
     \end{figure}\\
-    To understand the jump of \(T_c\), it seems to be sufficient to
+    To understand the jump of \(T_c\), it seems to be necessary to
     understand the jump of \(K\), which is easily explained

### 2013-08-13 Tex/chapters/model.tex
Klarere Formulierung
Reduktion von disordered auf standrd etwas erklärt

@@
     \(j\). If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
+    For the standard Ising model \(J_{ij}=1 \forall i,j\) applies.
     \(\tilde{H}_i\) denotes the outer magnetic field at the position of
-    site \(i\).\\
-    In this thesis \(\tilde{H}_i=0 \ \forall i\). The most important
-    modification is, that the sites of the square lattice are displaced.
+    site \(i\). For the standard Ising model \(\tilde{H}_i=0 \ \forall i\)
+    applies.\\
+    The most important modification of the standard Ising modell in this
+    thesis is, that the sites of the square lattice are displaced.
     The displacement is randomly Gauß distributed with the standard
@@
     of the lattice is preserved. The coupling constant \(J\) gets
-    identified with edge weights. The weight of an edge \(E_{ij}\) is
-    \(J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean
+    identified with edge weights. The weight of an edge \(E_{ij} =
+    J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean
     distance between the nodes \(i\) and \(j\). The free parameter
@@
     \end{figure}\\
-    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
-    for which exists an analytic solution \cite{Onsager1944} for the
+    Note that for \(\sigma = 0\) all \(d_{ij} = 1\) and therefore all
+    \(J_{ij} = 1\), so that the disordered Ising model is reduced to the
+    standard Ising model. For this exists an analytic solution \cite{Onsager1944} for the
     critical temperature

### 2013-08-13 Tex/chapters/methods.tex
Seitenyahlen bei den cite{} korrigiert
peinlichen Rechtschreibfehler korrigiert

@@
         to add, the spin of every site in the cluster is flipped
-        \cite[S. ??]{NewmanBarkema1999} \cite[S. 151f]{Katzgraber2011}.
+        \cite[p. 91ff]{NewmanBarkema1999} \cite[p. 151f]{Katzgraber2011}.
         This leads fast to new uncorrelated states at the critical
@@
         between two neighboring temperatures with probability \(P\) from
-        eq. \eqref{eq:partemp} \cite[S. ??]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+        eq. \eqref{eq:partemp} \cite[p. 169ff]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
         \begin{equation}
@@
         to determine the critical temperature. The additional calculations
-        to determine weather to swap configurations or not are small in
+        to determine whether to swap configurations or not are small in
         comparison with those that would be needed to generate a new
@@
         \(\tau\) is an estimate after which time two samples are not
-        correlated anymore. \cite[S. ??]{NewmanBarkema1999} \cite[S. 150f]{Katzgraber2011}.
+        correlated anymore. \cite[p. 59ff]{NewmanBarkema1999} \cite[p. 150f]{Katzgraber2011}.
         To make sure that the error is not underestimated one should wait

### 2013-08-13 Tex/chapters/results.tex
Zeichensetzung
Punkte hinter fig ergänzt

@@
     of all edges multiplied by the degree.
-    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
+    The plots fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
     show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
@@
     Also both graph types have a steep decline after the plateau before
-    they approach an asymptotic limit for \(\sigma \gg 1\)\\\\
+    they approach an asymptotic limit for \(\sigma \gg 1\).\\
 

### 2013-08-13 Tex/chapters/methods.tex
Punkte hinter fig ergänzt
Sachlichen Fehler(?) korrigiert

@@
     if all spins are aligned. In this case \(S\) as a measure of
-    disorder is also low. Analogical the state of maximum \(U\) is also
-    the state of maximum \(S\).
+    disorder is also low. Analogical a state of high \(U\) is also
+    a state of high \(S\).
     This preliminary considerations make a phase transition at some
@@
         To get the autocorrelation time one can either fit a exponential
-        function \(\exp(-t/\tau)\) like in fig \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
+        function \(\exp(-t/\tau)\) like in fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
         or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).

### 2013-08-15 Tex/chapters/model.tex
Bild zum Cell Algorithmus hinzugefügt

@@
     for each cell a list with nodes lying inside it like presented in
-    \cite{RNGCell}.
+    \cite{RNGCell}.\\
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Definition of the Lunes][]{
+            \label{sfig:cell:big}
+            \input{images/CellBig}
+        }
+        \subfigure[RNG example][]{
+            \label{sfig:cell:small}
+            \input{images/CellSmall}
+        }
+        \caption[Sketch how the Cell Method Works]
+        {
+            Sketch how the cell algorithm for the construction of the
+            RNG and GG works. Here with the lune definition of the GG.
+            The bounding box of the lune which determines which cells have
+            to be tested, is marked with thick colored lines.\\
+            \subref{sfig:cell:big} shows that it is sufficient to find a
+            single node in an inner cell of the bounding box to discard
+            the edge between two distant nodes.\\
+            \subref{sfig:cell:small} shows that only the nodes inside the
+            marked cell have to be tested, because there are no other nodes,
+            the edge can be drawn.
+        }
+        \label{fig:cell}
+    \end{figure}\\
     Now it is just necessary to test the nodes in the cells which

### 2013-08-15 Tex/chapters/appendix.tex
fig. usw. durch Fig.\ ersetzt

@@
 \label{appendix:finiteSizeEffects}
-    In fig.\ \ref{fig:smeared_out_appendix} the specific heat
+    In Fig.\ \ref{fig:smeared_out_appendix} the specific heat
     \begin{equation}
@@
     A quick analysis of this model with fixed coupling constants \(J = 1\)
-    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in fig.\ \ref{fig:Tc_deg_A0}.
-    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in fig.\ \ref{fig:Tc_deg}
+    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
+    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
     for variable \(J\) with \(\alpha=0.5\). This suggests, that the

### 2013-08-15 Tex/chapters/introduction.tex
fig. usw. durch Fig.\ ersetzt

@@
 on some irregular lattices corresponding to proximity graphs
-(see section \ref{ssec:graphtypes}) will be examined using the Monte
-Carlo simulations described in section \ref{ssec:montecarlo}.
+(see Sec.\ \ref{ssec:graphtypes}) will be examined using the Monte
+Carlo simulations described in Sec.\ \ref{ssec:montecarlo}.
 
@@
 of the system in the thermodynamic limit. These deviations are called
-\emph{finite size effects} and in section \ref{ssec:finitesize} will be
+\emph{finite size effects} and in Sec.\ \ref{ssec:finitesize} will be
 discussed how to manage them.\\

### 2013-08-15 Tex/chapters/methods.tex
fig. usw. durch Fig.\ ersetzt

@@
     states of the system. For each the energy \(H_i\) has to be calculated
-    to solve the sum from eq. \eqref{eq:partitionFunction} to gain \(Z\).
+    to solve the sum from Eq.\ \eqref{eq:partitionFunction} to gain \(Z\).
     Hence for small \(N\) the partition function is computable, but the system
@@
         Ising model will choose a random spin, calculate the energy change
-        \(\Delta H\) defined in eq. \eqref{eq:dH} that would result
+        \(\Delta H\) defined in Eq.\ \eqref{eq:dH} that would result
         from a flip of that spin and execute the flip with the probability \(A\)
-        eq. \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
+        Eq.\ \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
         \begin{equation}
@@
         starting with a random site and adding neighboring sites of the
-        same spin with probability \(P_{\mathrm{add}}\) from eq. \eqref{eq:wolffAdd}
+        same spin with probability \(P_{\mathrm{add}}\) from Eq.\ \eqref{eq:wolffAdd}
         \begin{equation}
@@
         between two neighboring temperatures with probability \(P\) from
-        eq. \eqref{eq:partemp} \cite[p. 169ff]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+        Eq.\ \eqref{eq:partemp} \cite[p. 169ff]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
         \begin{equation}
@@
         is reached, by observing the change of the observables over the
-        progressing simulation, as pictured in fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
+        progressing simulation, as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
         The count of sweeps till
@@
         All measurements should start after this time.\\
-        In fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
+        In Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
         the equilibrium is reached after approximately \(N_{s} \approx 50\) sweeps for
@@
         To get the autocorrelation time one can either fit a exponential
-        function \(\exp(-t/\tau)\) like in fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
+        function \(\exp(-t/\tau)\) like in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
         or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
@@
         \(T_{c}\) and is then limited by the size of the simulated lattice.
-        As mentioned in section \ref{sssec:wolff}, the Wolff cluster algorithm
+        As mentioned in Sec.\ \ref{sssec:wolff}, the Wolff cluster algorithm
         decreases \(z\) dramatically. This causes the course of the autocorrelation
         time in dependence on temperature to change significantly as shown in
-        section \ref{ssec:results:autocorr}. Also according to \cite{NewmanBarkema1999}
+        Sec.\ \ref{ssec:results:autocorr}. Also according to \cite{NewmanBarkema1999}
         \(z\) is independent of the lattice structure, which ensures that

### 2013-08-15 Tex/chapters/model.tex
fig. usw. durch Fig.\ ersetzt

@@
     spin can take a value \(s \in \{-1,+1\}\) and interacts with its
-    nearest neighbors described by the Hamiltonian from eq. \eqref{eq:hamiltonian}
+    nearest neighbors described by the Hamiltonian from Eq.\ \eqref{eq:hamiltonian}
     \begin{equation}
@@
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
-    from a Gauß distribution eq. \eqref{eq:gauss}.
-    This is sketched in fig.\ \ref{fig:displacement}.
+    from a Gauß distribution Eq.\ \eqref{eq:gauss}.
+    This is sketched in Fig.\ \ref{fig:displacement}.
     \begin{equation}
@@
     by an edge. The edges are constructed according to
-    one of the two in section \ref{ssec:graphtypes} defined rules,
+    one of the two in Sec.\ \ref{ssec:graphtypes} defined rules,
     so that the lattice represents a proximity graph. Note that edges
@@
     top and bottom edges are connected. One can imagine that the model
-    lives on the surface of a torus as pictured in fig.\ \ref{fig:torusRNG}.
+    lives on the surface of a torus as pictured in Fig.\ \ref{fig:torusRNG}.
     In subsequent graphics, the graphs will be unwrapped to rectangular
@@
     lattices with nearest neighbor relationships, like the Ising model
-    from the section \ref{ssec:isingmodel}.
+    from the Sec.\ \ref{ssec:isingmodel}.
     In this thesis the distance is always determined by the Euclidean
@@
     called \emph{lune} in the following. See also the cross hatched region
-    from fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.\\
+    from Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.\\
     The Relative Neighborhood graph (RNG) \cite{Toussaint1980} is a
@@
     distance \(d_{ij}\) are connected, if no other node is in the
-    \emph{lune}. The lune is defined as the intersection of two
+    \emph{lune}. The lune is defined as the interSec.\ of two
     circles with radius \(r = d\) and centers on \(i\) and \(j\).
-    See also the hatched region in fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.
+    See also the hatched region in Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.
     \begin{figure}[htbp]

### 2013-08-15 Tex/chapters/results.tex
fig. usw. durch Fig.\ ersetzt

@@
     (see also \ref{sssec:eqtime}). The used values for different system sizes
-    are listed in tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
+    are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
     the \(t_{eq}\) values are generously rounded up to be on the safe side
@@
     \(\sigma=0\) is plotted. Note, that these are the unrounded values
-    of tab.\ \ref{tab:tauAndTeq}
+    of Tab.\ \ref{tab:tauAndTeq}
     \begin{figure}[htbp]
@@
     the expected behavior of a dynamical exponent \(z\) as mentioned in
-    section \ref{sssec:eqtime}.
-    In fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
+    Sec.\ \ref{sssec:eqtime}.
+    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
     over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
@@
     is satisfied at the temperature of maximum \(\tau\), which is plausible,
-    because the peak in fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
+    because the peak in Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
     is near \(T_{c}\).\\
-    Anyhow, fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
+    Anyhow, Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
     proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
@@
     \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
-    will diverge. In fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
+    will diverge. In Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
     it is easy to see that the steep decline of \(\avg{|m|}\)
@@
     transition. This is stronger for smaller system sizes, as is visible
-    in fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
+    in Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
     Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
@@
     values for \(T_{c}\) in a much faster and more robust way, which is
-    presented in section \ref{ssec:binderIntersections}.
+    presented in Sec.\ \ref{ssec:binderIntersections}.
 
@@
     temperature \(T_{c}\) and has only an explicit \(L\) dependence.
-    One can then express some observables like in eq. \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
+    One can then express some observables like in Eq.\ \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
     \eqref{eq:fsscaling:g}.
@@
     \end{align}
-    Where \(g\) from eq. \eqref{eq:fsscaling:g} is a normalized
-    Binder cumulant (see eq. \eqref{eq:binder}) and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
+    Where \(g\) from Eq.\ \eqref{eq:fsscaling:g} is a normalized
+    Binder cumulant (see Eq.\ \eqref{eq:binder}) and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
     are the scaling functions.
@@
     collapse on one curve -- the scaling function.
-    Like the obersables from fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
-    collapse in fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
+    Like the obersables from Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
+    collapse in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
     %\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
@@
             \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
-                size scaling (errors are for clarity not given, see tab.\ \ref{tab:critExp})
+                size scaling (errors are for clarity not given, see Tab.\ \ref{tab:critExp})
         }
@@
     performed to determine the critical exponents \(\beta, \gamma, \nu\)
-    using \texttt{autoscale.py} \cite{autoscale2009} and eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
+    using \texttt{autoscale.py} \cite{autoscale2009} and Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
     The values for \(\nu\) are yielded by every collapse and are therefore
@@
     This way the exponents \(\gamma\) and \(\nu\) are determined.
-    Analogical fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
+    Analogical Fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
     shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\),
@@
     Also the collapse of the binder cumulant as mentioned before and shown
-    in fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
+    in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
     is used to get a further value of \(\nu\).
@@
             \subref{sfig:gettingCrit:collapse_s_1_sus} collapsed by finite
-                size scaling (for error estimates see tab.\ \ref{tab:critExp})\\
+                size scaling (for error estimates see Tab.\ \ref{tab:critExp})\\
             \subref{sfig:gettingCrit:s_1_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
@@
             \subref{sfig:gettingCrit:collapse_s_1_meanM} collapsed by finite
-                size scaling (for error estimates see tab.\ \ref{tab:critExp})
+                size scaling (for error estimates see Tab.\ \ref{tab:critExp})
         }
@@
     values for all other \(\sigma\) are expected be the same as for
-    \(\sigma = 0\) like mentioned before in section \ref{ssec:finitesize}.
+    \(\sigma = 0\) like mentioned before in Sec.\ \ref{ssec:finitesize}.
     Therefore it is sufficient to take a few samples to test if the
@@
     decline at \(\sigma = 0.5\). This will be shown in the next
-    chapter in fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
-    The determined values are displayed in tab.\ \ref{tab:critExp}.
+    chapter in Fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
+    The determined values are displayed in Tab.\ \ref{tab:critExp}.
     The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
@@
     \end{table}\\
-    Like in tab.\ \ref{tab:critExp} to see, most values
+    Like in Tab.\ \ref{tab:critExp} to see, most values
     are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
@@
     Because there were
-    many measurements in the vicinity of \(T_c\) (compare fig.\ \ref{sfig:gettingCrit:s_1_sus}),
+    many measurements in the vicinity of \(T_c\) (compare Fig.\ \ref{sfig:gettingCrit:s_1_sus}),
     this should give a reasonable estimate, without the need to
     interpolate a maximum.
-    The results are displayed in fig.\ \ref{fig:susCrossCheck}. The ratios
+    The results are displayed in Fig.\ \ref{fig:susCrossCheck}. The ratios
     determined by this method confirm the values obtained by collapse.
@@
     \end{figure}\\
-    As an example take fig.\ \ref{fig:gettingCrit:binder_fit_s_0}.
+    As an example take Fig.\ \ref{fig:gettingCrit:binder_fit_s_0}.
     Here such interpolations are plotted for \(\sigma=0\) and are
@@
     gets \(T_c = 2.2689(2)\), which is in good agreement with the
-    exact solution from eq. \eqref{eq:exactTc}.
+    exact solution from Eq.\ \eqref{eq:exactTc}.
     This test suggests, that measuring \(T_c\) this way is yields
@@
     deviations.\\
-    In this section these \(T_c\) on either the RNG or the GG are
+    In this Sec.\ these \(T_c\) on either the RNG or the GG are
     compared. In the following figures, the RNG will always be on the
     left side and the GG on the right side.
-    And in tab.\ \ref{tab:critTemp} the values are displayed together with the
-    values obtained by the data collapse from the section before.
+    And in Tab.\ \ref{tab:critTemp} the values are displayed together with the
+    values obtained by the data collapse from the Sec.\ before.
     \begin{table}[htbp]
@@
     The values obtained through the data collapse and the values obtained
-    through the intersection of the binder cumulant are always in good
+    through the interSec.\ of the binder cumulant are always in good
     agreement and of comparable precision.\\
-    These values of \(T_c\) are plotted over \(\sigma\) in fig.\ \ref{fig:Tc}.
+    These values of \(T_c\) are plotted over \(\sigma\) in Fig.\ \ref{fig:Tc}.
     \begin{figure}[htbp]
@@
     and there exists an analytic solution \cite{Wannier1945}.
-    Its critical temperature is determined by eq. \eqref{eq:exactHCTc}.
+    Its critical temperature is determined by Eq.\ \eqref{eq:exactHCTc}.
     \begin{equation}
@@
     If one plots the degree of the graphs at different \(\sigma\) like
-    in fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
+    in Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
     one recognizes, that \(T_c\) and \(K\) are evidently correlated.
@@
     Note that \(K\) is independent of \(L\) because of the periodic boundary.
-    In fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
+    In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
     one can see, that these curves are almost identical and the small
@@
     It seems reasonable to normalize \(T_c\) by the degree of the underlying
-    graph. This is done in fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
+    graph. This is done in Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
     Indeed the normalization eliminates the jump and reduces the
@@
     by the definition of the GG and its aftereffects for
-    the transition from \(\sigma = 0\). Visible in fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
+    the transition from \(\sigma = 0\). Visible in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
     a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
@@
     Then more edges disappear, than appear at further displacement. This
-    is not an obvious effect, but can be seen in fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
+    is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
     \begin{figure}[htbp]
@@
     Further \(T_c\) depends on the coupling constant \(J\), which is
-    obvious in eq. \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
+    obvious in Eq.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
     coupling constant in turn is depending on the length of the edges,
     which changes with \(\sigma\).
-    Therefore  in fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
+    Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
     the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
@@
     of all edges multiplied by the degree.
-    The plots fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
+    The plots Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
     show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
@@
     \end{figure}\\
-    Though eq. \eqref{eq:exactHCTc} shows, that there does not have
+    Though Eq.\ \eqref{eq:exactHCTc} shows, that there does not have
     to be a linear connection between \(J\) and \(T_c\), the best guess
@@
     normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
-    fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
+    Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
     jump on the GG arises again, but \(T_c\) is now monotonically
@@
     Moreover the forms of both curves are quite similar, but the
-    one for the RNG in fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
+    one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
     is generally lower and spans over a bigger temperature range than
-    the curve of the GG in fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
+    the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
     Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
@@
             to match its definition in this thesis.}.
-    Because the analysis of section \ref{ssec:binderIntersections}
+    Because the analysis of Sec.\ \ref{ssec:binderIntersections}
     yields \(g_c\) anyway, it is easy to check the consistency and
@@
     \end{figure}\\
-    Considering both plots in fig.\ \ref{fig:TcG}, \(g_c\) is for low
+    Considering both plots in Fig.\ \ref{fig:TcG}, \(g_c\) is for low
     \(\sigma\) obviously always bigger than the known value. Though the

### 2013-08-15 Tex/chapters/conclusion.tex
Christophs Verbesserungsvorschläge Umgesetzt, Form, Rechtschreibung

@@
-In this thesis the properties of an Ising ferromagnet, which nodes are
-moved by an gauss distributed displacement, is studied. The neighbor
+In this thesis the properties of an Ising ferromagnet which nodes are
+moved by a Gaussian distributed displacement is studied. The neighbor
 relationship is provided by two proximity graphs -- the RNG and the GG.
 The coupling constants are distance dependend. This model is within the
-universality of the standard Ising ferromagnet. Its critical temperature
+universality of the square lattice Ising ferromagnet. Its critical temperature
 decreases with increasing disorder on a RNG. On a GG it first jumps,
@@
     of other proximity graphs like the minimum spanning tree or the
-    Delaunay triangulation, to examine if it is also similar. Further
-    one could examine other graph ensembles to determine, if this is a
-    more universal property.\\
+    Delaunay triangulation to examine if it is also similar.\\
     Also it would be interesting to compare this results with the
@@
     on the sites. That way the critical temperature would be more
-    straight forward normalized by the degree of the graph. This way it
+    straight forward normalized by the degree of the graph. It
     could be determined if the qualitative similarities of the

### 2013-08-15 Tex/chapters/introduction.tex
Christophs Verbesserungsvorschläge Umgesetzt, Form, Rechtschreibung

@@
 For example to examine phase transitions, which are defined by the abrupt
-change of an observable e.g.\ the change of the density of water near
+change of an observable, e.g.\ the change of the density of water near
 boiling or the change of the magnetization of a ferromagnet near the
 Curie temperature.
-Different phases of an material and the transitions between them were
-always of greatest interest. The ancient greek thought, that everything
+Different phases of a material and the transitions between them were
+always of greatest interest. The ancient greek thought that everything
 consists of fire, water, air and earth, which are the archetypes of
@@
 model of a ferromagnet and will be explained in more detail in section
-\ref{ssec:isingmodel}. It is analytically solved for two dimensions on
+\ref{ssec:isingmodel}. It is analytically solved in two dimension on
 some regular lattices \cite{Onsager1944} \cite{Wannier1945}.
-In this thesis its behavior near the Curie temperature -- also called
-critical temperature -- and the behavior of the Curie temperature itself
+In this thesis its behavior near the critical temperature -- also called
+Curie temperature -- and the behavior of the critical temperature itself
 on some irregular lattices corresponding to proximity graphs
@@
 
-Unfortunately the memory of any computer is small in comparison with the
-thermodynamic limit. So there can only be a very small number of
-subsystems simulated in comparison to the actual number of subsystems
+Unfortunately the memory of any computer is small in comparison with what
+would be needed for a simulation of a system in the
+thermodynamic limit. So only a very small number of subsystems can be
+simulated in comparison to the actual number of subsystems
 of the system in nature. This leads to deviations from the real behavior
@@
 
-Note that in the scope of this thesis the Boltzmann constant \(k_{B}=1\)
+Note that in the scope of this thesis the Boltzmann constant is \(k_{B}=1\)
 for the sake of simplicity.

### 2013-08-15 Tex/chapters/methods.tex
Christophs Verbesserungsvorschläge Umgesetzt, Form, Rechtschreibung

@@
     condition, that the system under scrutiny has reached the temperature
-    of the heat bath. This is the case, once no energy is exchanged
-    between them, thus the energy of the simulated system reaches a
-    steady state.
+    of the heat bath. This is the case, once there is no directed energy
+    exchange between them, thus the energy of the simulated system reaches
+    a steady state, where only fluctuations occur.
     In a canonical ensemble the probability \(p_i\) of a state
@@
     statistical physics (e.g.\ \cite{nolting2005}).\\
-    Because of \(F=U-TS\) where \(U=\avg{H}\) is the internal energy and
-    \(S\) entropy, one can guess, that for low \(T\) the internal energy
-    will be low, and for big \(T\) the entropy will be high, to minimize
-    \(F\). The Hamiltonian of the Ising model connects \(U\) and \(S\)
-    by assigning low energies to states with high order. So \(U\) is low
-    if all spins are aligned. In this case \(S\) as a measure of
-    disorder is also low. Analogical a state of high \(U\) is also
-    a state of high \(S\).
-    This preliminary considerations make a phase transition at some
+    Because of
+    \begin{equation}
+        F = U - TS
+    \end{equation}
+    where \(S\) is the entropy, \(U=\avg{H}\) the internal energy and
+    \(\avg{\cdot}\) declares the expected value of an observable.
+    One can guess that for low \(T\) the internal energy
+    will be low, and for high \(T\) the entropy will be high, to minimize
+    \(F\).
+    Considering the Hamiltonian of the Ising model, a spin configuration
+    of high order, where most spins are aligned with their neighbors,
+    leads to a low \(H\) and therefore a low \(U\). Simultaneously, this
+    state of high order corresponds to a low entropy \(S\).
+    Analogically a state of high \(U\) is also a state of high \(S\).
+    These preliminary considerations make a phase transition at some
     \(T\), where the influence of the entropy on \(F\) becomes the same
@@
     \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_i O_i e^{-\beta H_i}
+        \avg{O} = \frac{1}{Z} \sum_i O_i e^{-\beta H_i},
     \end{equation}
@@
     \begin{equation}
-        Z = \sum_i p_i = \sum_i e^{-\beta H_i}
+        Z = \sum_i p_i = \sum_i e^{-\beta H_i},
         \label{eq:partitionFunction}
@@
     systems with large \(N\). But \(2^N\) is a very rapidly increasing
-    number, so there are next to infinity many different states, such
-    that it is unfeasible to calculate the energy for each state, except
+    number, so for large \(N\) it is unfeasible to calculate the energy for each state, except
     for cases, where it is possible to solve it analytically.\\
@@
 
-    The observables which are measured in this thesis, are the mean
+    The observables which are measured in this thesis are the mean
     magnetization per spin
@@
     \begin{equation}
-        E = \frac{1}{N} \avg{H}
+        E = \frac{1}{N} \avg{H}.
     \end{equation}
@@
     phase transition, hence \(m\) and \(E\) are continous, but show at
-    \(T_c\) an infinitly sharp slope i.e.\ the first derivative diverges.
-    From statistical physics (compare \cite{nolting2005}) is known, that
+    \(T_c\) an infinitly sharp slope in the thermodynamic limit i.e.\
+    the first derivative diverges.
+    From statistical physics (compare \cite{nolting2005}) is known that
     these derivatives can be expressed by fluctuations e.g.\ the specific
@@
     the temperature of the system.
-    Analogical the susceptibility
+    Analogically the susceptibility
     \begin{equation}
@@
     The idea behind Monte Carlo simulations is to take random samples of
-    the observable, which should be measured, and estimate the mean of the observable from
-    this samples. As an example the Monte Carlo integration chooses random
-    points within the bounding box of the function and estimates the integral
-    as the fraction of points below the function and points above multiplied
-    by the area of the bounding box \cite{Katzgraber2011}.\\
-    Analogical the technique can be applied to statistical ensembles,
-    but instead of sampling points on an area, one samples states of the
-    system.\\
+    the observable, which should be measured, and estimate the mean of
+    the observable from this samples. To apply this technique to statistical
+    ensembles, one creates sample states of the system, measures the
+    observables calculates the expected value through averaging.\\
     In statistical physics the expected value of an observable \(O\)
@@
     It is however possible, that there are few states that contribute
-    massively more than others. Think of a canonical system at low \(T\),
-    where \(p_i\) with low \(H_i\) contribute much more than high \(H_i\).
+    massively more than others. In canonical systems at low \(T\),
+    states with low values of \(H\) contribute much more than states with
+    high values of \(H\).
     But if one samples the \(2^N\) states evenly, it is probable to miss
-    them, which possibly introduces big errors to the estimate of \(\avg{O}\).
+    them. this is called \emph{simple sampling} and results in large
+    errorbars for any observable.
     It is therefore desirable to sample only the states with high
@@
     As noted before the system under scrutiny is canonical and therefore
-    \(p_i\) is known. The states are distributed according to the Boltzman
+    \(p_i\) is known. The states are distributed according to the Boltzmann
     distribution. Hence \emph{Importance Sampling} can be utilized.\\
-    Instead of sampling uniformly distributed random states, one samples
-    states, which energies are distributed according to a Boltzman distribution.
-    In fact this reduces the estimator to
+    Instead of sampling uniformly distributed random states, one should sample
+    states, according to their occurence probability given by the Boltzmann
+    distribution. In fact this reduces the estimator to
     \begin{equation}
-        O_M = \frac{1}{M} \sum_{i=0}^M O_i
+        O_M = \frac{1}{M} \sum_{i=0}^M O_i,
     \end{equation}
-    as shown in \cite{NewmanBarkema1999}. This is a very convenient form.\\
-    But it is difficult to create a random state of a physical system
-    e.g.\ the Ising system according to a given distribution. The simple
-    method of creating uniformly distributed random states and reject
+    where \(M\) is the number of samples, as shown in \cite{NewmanBarkema1999}.
+    This is a very convenient form.\\
+    But it is difficult to create a random state of a physical system,
+    e.g.\ the Ising system, according to a given distribution. The simple
+    approach of creating uniformly distributed random states and reject
     them with probability \(p_i^{-1}\) depending on their energy is not
@@
     And \emph{Ergodicity} requires that every possible state is reachable
-    from every other state in finite time. \cite{NewmanBarkema1999} \cite{Katzgraber2011}
+    from every other state in finite time \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
     Otherwise the samples might not be representative for the whole system.\\
@@
     \subsubsection{Metropolis}
-        A Metropolis Monte Carlo\cite{Metropolis1953} simulation of an
+        A Metropolis Monte Carlo \cite{Metropolis1953} simulation of an
         Ising model will choose a random spin, calculate the energy change
-        \(\Delta H\) defined in Eq.\ \eqref{eq:dH} that would result
-        from a flip of that spin and execute the flip with the probability \(A\)
-        Eq.\ \eqref{eq:metropolis} \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
         \begin{equation}
@@
         \end{equation}
+        that would result from a flip of that spin and execute the flip
+        with the probability \cite{NewmanBarkema1999} \cite{Katzgraber2011}
         \begin{equation}
@@
                 \exp{\brac{-\beta \Delta H}} & \Delta H > 0
-            \end{cases}
+            \end{cases}.
             \label{eq:metropolis}
         \end{equation}
-        So if a transition lowers the energy it is always done. This
+        So if a transition lowers the energy it will be always done. This
         results in a high ratio between chosen spins and flipped spins.
@@
         gets slower. This is called \emph{critical slowing} down.\\
-        Using a cluster algorithm like the Wolff
-        algorithm \cite{Wolff1989} speeds things up.
+        In order to circumvent this a cluster algorithm like the Wolff
+        algorithm \cite{Wolff1989} can be used.
         For an Ising model the Wolff algorithm builds a cluster of sites
         starting with a random site and adding neighboring sites of the
-        same spin with probability \(P_{\mathrm{add}}\) from Eq.\ \eqref{eq:wolffAdd}
+        same spin with probability
         \begin{equation}
-            P_{\mathrm{add}} = 1-\exp\brac{-2\beta J}
+            P_{\mathrm{add}} = 1-\exp\brac{-2\beta J},
             \label{eq:wolffAdd}
         \end{equation}
-        Where \(J\) is the coupling constant (explained in section
-        \ref{ssec:isingmodel}). The neighboring sites of the added sites
+        where \(J\) is the coupling constant (c.f.\ Sec.\ \ref{ssec:isingmodel}).
+        The neighboring sites of the added sites
         are also considered and so forth. When there are no more sites
@@
         So one would activate this algorithm near the critical temperature
-        but use a simple Metropolis algorithm at high and low temperatures.
+        but would use a simple Metropolis algorithm at high and low temperatures.
 
     \subsubsection{Parallel Tempering}
-        Parallel Tempering\cite{ParallelTempering1986} simulates many identical systems at different
-        temperatures and periodically swaps the spin configurations
-        between two neighboring temperatures with probability \(P\) from
-        Eq.\ \eqref{eq:partemp} \cite[p. 169ff]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}.
+        In simulations using \emph{parallel tempering} \cite{ParallelTempering1986}
+        many identical systems at different temperatures are simulated and
+        the spin configurations between two neighboring temperatures are
+        swapped periodically with probability \cite[p. 169ff]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}
         \begin{equation}
-            P((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}}
+            P((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}}.
             \label{eq:partemp}
         \end{equation}
-        This has the advantages that correlation times of single
-        temperatures are far smaller because their spin configuration
+        This has the advantage that correlation times of single
+        temperatures are far smaller, because their spin configuration
         gets often replaced by another uncorrelated configuration. In
-        many cases the more important advantage is, that a system which
-        is trapped in a local minimum at a given temperature, can travel
+        many cases the more important advantage is that a system which
+        is trapped in a local minimum at a given temperature can travel
         to higher temperatures, leave its local minimum and cool down
         again in a lower minimum.\\
+        % Bild !! Schematisch und Energielandschaft
         In the case of a ferromagnetic Ising model the risk to get trapped
-        in an local energy minimum is very low. Though the autocorrelation
+        in an local energy minimum is very low. Consequently the autocorrelation
         decreases significantly. In the scope of this thesis this comes
@@
         Here a mixture of the above three algorithms is used.
-        Each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
+        For each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
         and one parallel tempering swap are performed. Where \(N\) is the
-        count of sites.\\
+        number of sites.\\
         Because it is not known before, where the critical temperatures
         \(T_c\) are located, the Wolff cluster algorithm is used for
-        every temperature. The speed up at criticality is worth the
+        every temperature. The speed up near criticality is worth the
         moderate slow down at other temperatures.
@@
     \label{sssec:eqtime}
-        To generate states acoording to the Boltzman distribution at a
+        To generate states acoording to the Boltzmann distribution at a
         given temperature \(T\), one starts with an arbitrary state
         and waits until it reaches thermal \emph{equilibrium}. Because
-        equilibrium is defined as a steady state, one can determine if it
-        is reached, by observing the change of the observables over the
-        progressing simulation, as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
+        equilibrium is defined as a steady state, one can determine it by
+        observing the change of the observables over the progressing
+        simulation, as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
         The count of sweeps till
@@
         the equilibrium is reached after approximately \(N_{s} \approx 50\) sweeps for
-        either an initial condition of all spins up and all spins random. It
-        does not harm to double that value to be save. Particularly because
+        both an initial condition of all spins up and all spins random. It
+        does not harm to double that value to be save. Particularly, because
         it is a random process, so that there can not be an exact value.
@@
         \begin{equation}
-            \chi(t) = \int \mathrm{d} t' \, [m(t') -\avg{m}][m(t'+t)-\avg{m}]
+            \chi(t) = \int \mathrm{d} t' \, [m(t') -\avg{m}][m(t'+t)-\avg{m}],
         \end{equation}
-        which should decay exponentially
+        which decays exponentially
         \(\chi(t) \propto \exp(t/\tau)\). This is visible in the half
@@
         or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
-        \(\tau\) is an estimate after which time two samples are not
-        correlated anymore. \cite[p. 59ff]{NewmanBarkema1999} \cite[p. 150f]{Katzgraber2011}.
-        To make sure that the error is not underestimated one should wait
+        \(\tau\) is an estimate that specifies the time after which two
+        samples are not correlated anymore \cite[p. 59ff]{NewmanBarkema1999} \cite[p. 150f]{Katzgraber2011}.
+        To ensure that the error is not underestimated one should wait
         \(2\tau\) sweeps between two measurements.
-        The autocorrelation time is of course dependent on the temperature.
+        The autocorrelation time is dependent on the temperature.
         For example for the standard Metropolis algorithm the fluctuations

### 2013-08-15 Tex/chapters/model.tex
Christophs Verbesserungsvorschläge Umgesetzt, Form, Rechtschreibung

@@
 \label{ssec:isingmodel}
-    The examined model is a modified 2D Ising model.
+    The examined model is a 2D Ising model.
     The most common definition of the Ising model, to which will be referred
-    as the \emph{standard Ising model}, is a square lattice with edge length \(L\) and
+    as the \emph{square lattice Ising model}, is a square lattice with edge length \(L\) and
     \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
     spin can take a value \(s \in \{-1,+1\}\) and interacts with its
-    nearest neighbors described by the Hamiltonian from Eq.\ \eqref{eq:hamiltonian}
+    nearest neighbors described by the Hamiltonian
     \begin{equation}
-        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i \tilde{H}_i s_i
+        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i h_i s_i.
         \label{eq:hamiltonian}
@@
     \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are nearest
-    neighbors. And \(J_{ij}\) is the coupling constant between \(i\) and
-    \(j\). If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
-    For the standard Ising model \(J_{ij}=1 \forall i,j\) applies.
-    \(\tilde{H}_i\) denotes the outer magnetic field at the position of
-    site \(i\). For the standard Ising model \(\tilde{H}_i=0 \ \forall i\)
+    neighbors, so that they are directly coupled to each other. The
+    coupling between \(i\) and \(j\) is characterized by \(J_{ij}\),
+    the coupling constant. If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
+    For the square lattice Ising model \(J_{ij}=1 \forall i,j\) applies.
+    \(h_i\) denotes the outer magnetic field at the position of
+    site \(i\). For the square lattice Ising model \(h_i=0 \ \forall i\)
     applies.\\
-    The most important modification of the standard Ising modell in this
+    The most important modification of the square lattice Ising modell in this
     thesis is, that the sites of the square lattice are displaced.
-    The displacement is randomly Gauß distributed with the standard
+    The displacement is randomly Gaussian distributed with the standard
     deviation \(\sigma\), i.e.\ the \(x\) and \(y\) coordinates of the
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
-    from a Gauß distribution Eq.\ \eqref{eq:gauss}.
-    This is sketched in Fig.\ \ref{fig:displacement}.
+    from a Gaussian distribution
     \begin{equation}
-        f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}
+        f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}.
         \label{eq:gauss}
     \end{equation}
+    This is sketched in Fig.\ \ref{fig:displacement}.
     \begin{figure}[htbp]
@@
     \end{figure}\\
-    This \(\sigma\) is also called \emph{disorder parameter} in the following.
-    Because most sites will only have one nearest neighbor after the
-    displacement, the lattice would collapse to many very small clusters.
-    To avoid this, the new "nearest" neighbors are those sites connected
-    by an edge. The edges are constructed according to
+    \(\sigma\) is also called \emph{disorder parameter} in the following.
+    Most sites will only have one nearest neighbor after the
+    displacement. If only the edges between these neighbors remain,
+    the lattice would collapse to many very small clusters. But if one
+    leaves the edges as the were before the displacement, the edges would
+    cross -- at least for big displacements. The crossing of edges then
+    would destroy the two dimensional character of the model and the results
+    would not be compareable with known results for the two dimensional
+    Ising model.
+    To avoid this, a new edge set will be etablished after the displacement.
+    The edges are constructed according to
     one of the two in Sec.\ \ref{ssec:graphtypes} defined rules,
-    so that the lattice represents a proximity graph. Note that edges
-    of a proximity graph do not cross each other, hence the 2D character
-    of the lattice is preserved. The coupling constant \(J\) gets
+    so that the lattice represents a proximity graph. Edges
+    of the used proximity graph do not cross each other, hence the 2D
+    character of the lattice is preserved. The coupling constant \(J\) gets
     identified with edge weights. The weight of an edge \(E_{ij} =
@@
     \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.
-    The boundary is periodic e.g.\ nodes near the right edge can be
+    The boundary is periodic, i.e.\ nodes near the right edge can be
     connected to nodes near the left edge and vice versa. Analogous the
@@
     shapes. Connections which cross a periodic boundary are indicated
-    by edges which connect to an dashed node.
+    by edges which connect a solid node to a dashed node.
     \begin{figure}[htbp]
@@
     \(J_{ij} = 1\), so that the disordered Ising model is reduced to the
-    standard Ising model. For this exists an analytic solution \cite{Onsager1944} for the
-    critical temperature
+    square lattice Ising model. For this exists an analytic solution \cite{Onsager1944}.
+    The critical temperature is
     \begin{equation}
@@
     and the critical exponents \(\alpha = 0\), \(\beta = \frac{1}{8}\)
-    and \(\gamma = \frac{7}{4}\).\\
+    and \(\gamma = \frac{7}{4}\). These values are universal for the Ising
+    model. Their meaning will be explained in Sec.\ \ref{ssec:critExp} in more detail.\\
     The case for randomly distributed sites \(\sigma \gtrsim 1\) is
@@
     Both articles conclude, that this model lies within the universality
-    class of the standard Ising model, i.e.\ has the same critical
+    class of the square lattice Ising model, i.e.\ has the same critical
     exponents.
@@
     corresponding nodes are connected, the sites are neighbors.\\
-    All here mentioned graph types are \emph{proximity graphs}. They are
-    connecting nodes which are by some metric near to each other.
+    All here mentioned graph types are \emph{proximity graphs}.
+    The edges of these graphs connect nodes which are by some metric near
+    to each other.
     Hence they are suited to generalize problems defined on regular
-    lattices with nearest neighbor relationships, like the Ising model
-    from the Sec.\ \ref{ssec:isingmodel}.
+    lattices with nearest neighbor relationships.
     In this thesis the distance is always determined by the Euclidean
@@
     there are \(N(N-1)\) pairs and for each \(N-2\) nodes to test. So
-    the product is of order \(O(N^3)\)\\
+    the running time of a straight forward implementation would be of
+    order \(O(N^3)\).\\
     To reduce the complexity one can first create a Delaunay
@@
     near the lune one can subdivide the area in \emph{cells} and save
-    for each cell a list with nodes lying inside it like presented in
+    for each cell a list with nodes lying inside like presented in
     \cite{RNGCell}.\\
@@
     Then only one node has to be tested from such a cell to discard an
-    edge between the nodes. On the other hand nodes, that will be connected,
+    edge between the nodes. On the other hand, nodes that will be connected
     are near to each other so that only very few cells intersect the bounding

### 2013-08-15 Tex/chapters/results.tex
Christophs Verbesserungsvorschläge Umgesetzt, Form, Rechtschreibung

@@
     in C, all needed random numbers are generated by the GSL \cite{GSL}
-    implementation of the \emph{Mersenne Twister} \cite{Matsumoto1998} and
+    implementation of \emph{Mersenne Twister} \cite{Matsumoto1998} and
     the generated data is evaluated via Python scripts.
-    All source code is available at \url{https://github.com/surt91/IsingFerromagnet}.\\
+    The entire source code is available at \url{https://github.com/surt91/IsingFerromagnet}.\\
     Most simulations were carried out on HERO, the \emph{H}igh-\emph{E}nd
@@
     per site \(E=\frac{1}{N} H\) are calculated and saved for every
-    \(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
+    \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
     (see also \ref{sssec:eqtime}). The used values for different system sizes
@@
     calculated sweeps totals to
-    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
+    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\].
     The expected values \(\avg{O}\) for \(100\) different random proximity
@@
     Not only the seed to generate the new random
-    realization of the proximity graph gets changed, but also the seed for
+    realization of the proximity graph is changed, but also the seed for
     the random numbers used in the Monte Carlo simulation and during the
@@
     The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
-    \cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
-    Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
+    \cite{Bootstrap}\\
+    The bootstrapping method estimates error \(\Delta \overline{\avg{O}}\)
+    by taking \(M\) random samples from the \(M\) measured values of \(O\),
+    where the same value can be chosen more than once, calculating the
+    estimator \(\avg{O_b}\) of this bootstrap sample and doing this \(k\)
+    times. Then the standard deviation of of the \(k\) calculated \(\avg{O_b}\)
+    is taken as an estimate for \(\Delta \overline{\avg{O}}\).
+    In this thesis the number of bootstrap samples is \(k = 200\).\\
+    Note that while the error of \(\avg{O}\), \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
     \(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
@@
     necessary to determine \(\tau\) for each observable. Therefore a good
-    error estimate can be achieved by simple bootstrapping. Though one has
-    to simulate enough uncorrelated states for each realization, to keep
+    error estimate can be achieved by simple bootstrapping. Nevertheless one has
+    to simulate enough uncorrelated states for each realization to keep
     the \(\Delta \overline{\avg{O}}\) small. For every determined value an
     error is calculated and given in the form \texttt{value(error of last digit)}.
-    The error given for fits are the asymptotic standard errors as calculated
+    The errors of fit parameters are the asymptotic standard errors as calculated
     by gnuplot. Gnuplot is an open source plotting program, used for all plots
@@
     Before the results are presented, a short analysis of the
-    autocorrelation time \(\tau\) is given, to illustrate the benefits
+    autocorrelation time \(\tau\) is given to illustrate the benefits
     of the used Wolff cluster algorithm.\\
-    In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
+    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
     the autocorrelation time for the magnetization per site \(m\) at
-    \(\sigma=0\) is plotted. Note, that these are the unrounded values
-    of Tab.\ \ref{tab:tauAndTeq}
+    \(\sigma=0\) is plotted. Note that these are the unrounded values
+    of Tab.\ \ref{tab:tauAndTeq}.
     \begin{figure}[htbp]
@@
     spin in every step, thus the correlation drops to zero after one sweep.
-    Alternatively the parallel tempering algorithm swaps spin configurations
-    with possibly different signs, thus having the same effect.
+    (Note that this is not the only explanation for the course of \(\tau\).
+    The parallel tempering algorithm swaps spin configurations
+    with possibly different signs, thus having the same effect.)
     Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
@@
     Nevertheless it is interesting, that it obeys a power law
-    \(\tau \propto L^{z'}\) just the same. This suggests, that \(\xi \gtrsim L\)
+    \(\tau \propto L^{z'}\). This suggests that \(\xi \gtrsim L\)
     is satisfied at the temperature of maximum \(\tau\), which is plausible,
@@
     of the disordered Ising model in dependence of the disorder parameter
-    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
+    \(\sigma\). At \(T_c\) the mean magnetization \(\avg{|m|}\) of
     the system will show a steep decline to zero and the susceptibility
@@
     \end{figure}\\
-    But in the shown plots there occurs no steep decline to zero, but a
+    In the shown plots there occurs no steep decline to zero, but a
     smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
@@
 \subsection{Critical Exponents}
-    The critical exponents define the course of an observable near its
+\label{ssec:critExp}
+    The critical exponents define the behavior of an observable near its
     divergence. For instance the vicinity of the divergence of the susceptibility
@@
     \begin{equation}
-        \chi \propto \abs{T-T_{c}}^{-\gamma}
+        \chi \propto \abs{T-T_{c}}^{-\gamma}.
         \label{eq:critExp:gamma}
@@
     \begin{equation}
-        m \propto \abs{T-T_{c}}^{-\beta}
+        m \propto \abs{T-T_{c}}^{-\beta}.
         \label{eq:critExp:beta}
     \end{equation}
-    As the name critical \emph{exponent} suggests, this will often
-    be a power law, as in both examples above. But not obligatory e.g.\
-    the critical "exponent" \(\alpha\) corresponding to the divergence of
-    the specific heat \(c\) diverges logarithmic for the two dimensional
+    As the name critical \emph{exponent} suggests, the curve progression
+    of respective observables will often be a power law close to the critical
+    point, as in both examples above. But this is not imperative.
+    E.g.\ the critical "exponent" \(\alpha\) corresponding to the divergence of
+    the specific heat \(c\) diverges logarithmically for the two dimensional
     Ising model and is nominally \(\alpha = 0\).
     For that reason, \(\alpha\) will not be considered in this section.\\
-    The important property of the critical exponents is, that they are
-    universal for a model i.e.\ they are independent of the size, the structure
+    The important property of the critical exponents is that they are
+    universal for a model, i.e.\ they are independent of the size, the structure
     or the coupling constant \(J\) \cite{NewmanBarkema1999} of the lattice,
-    therefore they should also be independent of \(\sigma\).
-    Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
-    varying coupling constants \(J\) confirm, that the
+    therefore they should also be independent of \(\sigma\). But they are
+    not universal regarding the dimension of the model.
+    Studies on random lattices with \cite{Lima2000} and without \cite{Janke1994}
+    varying coupling constants \(J\) confirm that the
     critical exponents are not influenced by an random lattice.
@@
     If the critical exponents can be reproduced, the determined critical
-    temperatures are probably correct too.\\
+    temperatures are probably correct, too.\\
     % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
@@
     will be used. The here given explanation will give a rough idea, how
-    the method works, for a more in depth explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.
+    the method works. For a more in depth explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.
     The crucial element is that there exists a \emph{scaling function},
@@
     One can then express some observables like in Eq.\ \eqref{eq:fsscaling:m}, \eqref{eq:fsscaling:chi} and
-    \eqref{eq:fsscaling:g}.
+    \eqref{eq:fsscaling:g}:
     \begin{align}
         \label{eq:fsscaling:m}
-        \avg{m_L} &= L^{-\frac{\beta}{\nu}} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \avg{m_L} &= L^{-\frac{\beta}{\nu}} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}},\\
         \label{eq:fsscaling:chi}
-        \chi_L    &= L^{\frac{\gamma}{\nu}} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
+        \chi_L    &= L^{\frac{\gamma}{\nu}} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}},\\
         \label{eq:fsscaling:g}
-        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}
+        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}.
     \end{align}
-    Where \(g\) from Eq.\ \eqref{eq:fsscaling:g} is a normalized
+    Where \(g\) in Eq.\ \eqref{eq:fsscaling:g} is the normalized
     Binder cumulant (see Eq.\ \eqref{eq:binder}) and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)
-    are the scaling functions.
-    To find the exponent e.g. \(\nu\), one takes \eqref{eq:fsscaling:g},
+    are scaling functions.
+    To find the exponent, e.g.\ \(\nu\), one takes \eqref{eq:fsscaling:g},
     solves for \(\tilde{G}\), adjusts the axis to represent \(y=\tilde{G}(x)\),
@@
     \emph{corrections to scaling} terms, which are not considered here.\\
-    To accomplish the collapse in an semi-automatic and reproduceable
+    To accomplish the collapse in a semi-automatic and reproduceable
     way with an error estimate, the program
@@
     using \texttt{autoscale.py} \cite{autoscale2009} and Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
-    The values for \(\nu\) are yielded by every collapse and are therefore
+    The values for \(\nu\) are obtained by every collapse and are therefore
     averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_sus}\subref{sfig:gettingCrit:collapse_s_1_sus}
@@
     \begin{equation}
-        \chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}
+        \chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}.
     \end{equation}
     This way the exponents \(\gamma\) and \(\nu\) are determined.
-    Analogical Fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
-    shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\),
+    Analogically Fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
+    shows the collapse for the mean magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\),
     to determine the exponents \(\beta\) and \(\nu\).
@@
     Therefore it is sufficient to take a few samples to test if the
-    expectations are met. Hence 5 values of \(\sigma\) are analyzed.
+    expectations match. Hence 5 values of \(\sigma\) are analyzed.
     The analytically known values for \(\sigma = 0\) and the in \cite{Janke1994}
@@
     The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
-    and the error of \(T_c\) and \(\nu\) is the standard deviation of the
+    and the errors of \(T_c\) and \(\nu\) are the standard deviations of
     three obtained values.\\
@@
     \end{table}\\
-    Like in Tab.\ \ref{tab:critExp} to see, most values
+    As can be seen in Tab.\ \ref{tab:critExp}, most values
     are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
@@
     good agreement of the by data collapse obtained values of \(\nu\) and \(\gamma\),
-    the ratio \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
+    the ratio \(\frac{\gamma}{\nu}\) is also determined by fitting the maxima of
     the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
-    %~ Note that the maximum of the measured \(\chi\).
-    Because there were
-    many measurements in the vicinity of \(T_c\) (compare Fig.\ \ref{sfig:gettingCrit:s_1_sus}),
-    this should give a reasonable estimate, without the need to
-    interpolate a maximum.
+    Because there were many measurements in the vicinity of \(T_c\)
+    (c.f.\ Fig.\ \ref{sfig:gettingCrit:s_1_sus}), it should give a
+    reasonable estimate to take their maximum, without the need to
+    interpolate.
     The results are displayed in Fig.\ \ref{fig:susCrossCheck}. The ratios
@@
     Anyway, two critical exponents are sufficient to determine the
-    universality class \cite[p. 145]{Katzgraber2011}. Therefore this
-    disordered Ising model is for every \(\sigma\) in the same universality
-    class as the standard Ising ferromagnet.
+    universality class \cite[p. 145]{Katzgraber2011}. Therefore
+    the Ising model on a proximity graph is for every \(\sigma\) in the
+    same universality class as the square lattice Ising ferromagnet.
 
@@
 \label{ssec:binderIntersections}
-    Though if one is just interested in the critical Temperature, an
+    Though if one is just interested in the critical temperature, an
     easier approach is to find the intersections of the Binder cumulants
-    \(g\) of different system sizes \(L\) which are intersecting at
-    \(T_c\) \cite{Binder1981}.
+    \(g\) of different system sizes \(L\), which intersect at \(T_c\) \cite{Binder1981}.
     Because the magnetization \(m\) is only measured for discrete values
@@
     plateaus at low and high \(T\) do not influence the interpolation in
-    the vicinity of \(T_c\) -- in contrast to e.g.\ an polynom fit of
+    the vicinity of \(T_c\) -- in contrast to, e.g.\ an polynom fit of
     degree 4, which has to be restricted to the vincinity of \(T_c\) to
@@
     exact solution from Eq.\ \eqref{eq:exactTc}.
-    This test suggests, that measuring \(T_c\) this way is yields
+    This test suggests that measuring \(T_c\) this way yields
     adequat results and the interpolation does not lead to major
     deviations.\\
-    In this Sec.\ these \(T_c\) on either the RNG or the GG are
+    In this section \(T_c\) for both the RNG or the GG are
     compared. In the following figures, the RNG will always be on the
@@
     monotonically while \(T_c\) of the GG rises at first. Naively one would
-    expect, that while changing the displacement of the nodes monotonically,
+    expect that while changing the displacement of the nodes monotonically,
     the properties of the system will also change monotonically, which is
@@
     \end{equation}
-    It is known, that the degree has an impact on the critical Temperature.
+    It is known that the degree has an impact on the critical temperature.
     For example the Honeycomb lattice is of degree \(K=3\)
     and there exists an analytic solution \cite{Wannier1945}.
-    Its critical temperature is determined by Eq.\ \eqref{eq:exactHCTc}.
+    Its critical temperature is determined by Eq.\ \eqref{eq:exactHCTc}:
     \begin{equation}
@@
     in Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
-    one recognizes, that \(T_c\) and \(K\) are evidently correlated.
+    one recognizes that \(T_c\) and \(K\) are evidently correlated.
     The values for \(K\) are obtained as an average over \(100\)
@@
     In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
-    one can see, that these curves are almost identical and the small
-    errorbars suggest, that they are sufficiently precise for this purpose.
+    one can see that these curves are almost identical and the small
+    errorbars suggest that they are sufficiently precise for this purpose.
     It seems reasonable to normalize \(T_c\) by the degree of the underlying
@@
     Further the increase of \(T_c\) on the GG can be made plausible.
-    Though it is not removed by the normalization, it is reduced. Also
-    the maximum of the \(K\) is at the same \(\sigma\), as the maximum
+    %~ Though it is not removed by the normalization, it is reduced.
+    Also the maximum of the \(K\) is at the same \(\sigma\), as the maximum
     of \(T_c\). So while displacing the nodes, there arise more edges
@@
             \label{sfig:GG_sigma:0.15}
-            \includegraphics[width=0.30\textwidth]{images/GG/out015}
+            \includegraphics[width=0.30\textwidth]{images/GG/out015}Bild: parallel tmepering
+Bild: cross edge GG
+Bildunterschriften ausführlicher
         }
@@
     with the same arguments. Fig. \ref{fig:RNG_sigma}
-    shows, that for \(\sigma \lesssim 0.1\) the square lattice character is
+    shows that for \(\sigma \lesssim 0.1\) the square lattice character is
     preserved -- no new edges arise neither many existing edges vanish, which
@@
     \end{figure}\\
-    Though Eq.\ \eqref{eq:exactHCTc} shows, that there does not have
+    Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
     to be a linear connection between \(J\) and \(T_c\), the best guess
@@
 \subsection{Critical Value of the Binder Cumulant}
-    The value of the Binder cumulant at the critical point \(g_c\) is
+    The value of the Binder cumulant at the critical point \(g_c\)
     depends strongly on boundary conditions but only weakly on the lattice
@@
     beyond the scope of this thesis. Anyway the results are the expected
-    behaivior, because no major deviations from the value of \(g_c\) at
+    behavior, because no major deviations from the value of \(g_c\) at
     \(\sigma = 0\) occur at larger \(\sigma\).

### 2013-08-15 Tex/chapters/results.tex
kleinere Korrekturen

@@
     calculated sweeps totals to
-    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\].
+    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}.\]
     The expected values \(\avg{O}\) for \(100\) different random proximity

### 2013-08-15 Tex/chapters/results.tex
Bild, warum die Querverbindungen beim GG entstehen

@@
     to get smaller, hence no other nodes are inside or on the edge of
-    the lune anymore and the edge appears.\\
+    the lune anymore and the edge appears. This process is sketched in
+    Fig.\ \ref{fig:GGEdge}
+    \begin{figure}[htbp]
+        \centering
+        \subfigure[Definition of the Lunes][]{
+            \label{sfig:GGEdge:before}
+            \input{images/GGEdgeBefore}
+        }
+        \subfigure[RNG example][]{
+            \label{sfig:GGEdge:after}
+            \input{images/GGEdgeAfter}
+        }
+        \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
+        {
+            \subref{sfig:GGEdge:before} The edge across does not exist,
+            because the other two nodes are on the edge of the lune.
+            \subref{sfig:GGEdge:after} Moving one node slightly into the
+            square, causes the lune to get smaller, hence no other nodes
+            are inside or on the edge of the lune anymore and the edge
+            appears.
+        }
+        \label{fig:GGEdge}
+    \end{figure}\\
     Further the increase of \(T_c\) on the GG can be made plausible.
@@
             \label{sfig:GG_sigma:0.15}
-            \includegraphics[width=0.30\textwidth]{images/GG/out015}Bild: parallel tmepering
-Bild: cross edge GG
-Bildunterschriften ausführlicher
+            \includegraphics[width=0.30\textwidth]{images/GG/out015}
         }

### 2013-08-16 Tex/chapters/methods.tex
Skizzen zum parallel tempering

@@
         \begin{equation}
-            P((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}}.
+            P((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}},
             \label{eq:partemp}
         \end{equation}
+        as schematically pictured in Fig.\ \ref{fig:parTemp}\subref{sfig:parTemp:schema}.
         This has the advantage that correlation times of single
@@
         to higher temperatures, leave its local minimum and cool down
-        again in a lower minimum.\\
-        % Bild !! Schematisch und Energielandschaft
+        again in a lower minimum. If a system is trapped in such a
+        metastable state, ergodicity is not guaranteed anymore.
+        This is schematically pictured in Fig.\ \ref{fig:parTemp}\subref{sfig:parTemp:E}.
+        \begin{figure}[htbp]
+            \centering
+            \subfigure[Schematic Diagramm of the Algorithm][]{
+                \label{sfig:parTemp:schema}
+                \input{images/parTempSchema}
+            }
+            \subfigure[Schematic Diagramm of the Energy Landscape][]{
+                \label{sfig:parTemp:E}
+                \input{images/parTempE}
+            }
+            \caption[Visualisation of the Parallel Tempering Algorithm]
+            {
+                \subref{sfig:parTemp:schema} schematic representation of
+                the swapping of spin configurations of different simulations \(S_i\)
+                between temperatures.\\
+                \subref{sfig:parTemp:E} sketch of an energy landscape, where
+                the state of the system (filled dot) is trapped in an local
+                minimum. At low temperatures it is very unlikley that it
+                overcomes the energy barrier \(\Delta E\) to the minimum.
+                After a swap to higher energies, the barrier can be overcome
+                and after a swap to lower energies again, the state in
+                the minimum can be reached (hollow dot).
+            }
+            \label{fig:parTemp}
+        \end{figure}\\
         In the case of a ferromagnetic Ising model the risk to get trapped

### 2013-08-16 Tex/chapters/results.tex
Bildunterschriften ausführlicher und einige ergänzungen

@@
         \end{tabular}
-        \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
+        \caption[Autocorrelation Times $\tau$ and Equilibration Times
+            $t_{eq}$ for Different System Sizes $L$]{
+            Autocorrelation times $\tau$ and equilibration times
+            $t_{eq}$ for different system sizes $L$. All values are generously
+            rounded up and are determined as the maximum over all \(\sigma\).
+        }
         \label{tab:tauAndTeq}
@@
                 $\sigma=0$ and
-            \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
-                are the standard error determined by bootstrapping)
+            \subref{fig:autocorr:powerLaw} the system size $L$. Plotted on
+                double logarithmic axis with a power law fit \(\tau \propto L^z\)
+                to determine the dynamical exponent \(z'\).
+                (Errorbars are the standard error estimated by bootstrapping.)
         }
@@
         {
-            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
+            \subref{sfig:smeared_out:meanM_L} Effects of the disorder
             parameter $\sigma$ on the phase transition
-            for an underlying RNG with $L=128$.\\
-            \subref{sfig:smeared_out:meanM}: Effects of different system
+            for an underlying RNG with $L=128$. The position of the slope,
+            and hence the critical temperature, moves to lower temperatures
+            with increasing \(\sigma\)\\
+            \subref{sfig:smeared_out:meanM} Effects of different system
             sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
+            The \(L=16\) curve is much less steep than the \(L=128\) curve.
         }
@@
             \subref{sfig:gettingCrit:binder_s_0} The Binder cumulant \(g\)
-                of an square lattice Ising model (\(\sigma=0\))\\
-            \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
-                size scaling (errors are for clarity not given, see Tab.\ \ref{tab:critExp})
+                of an square lattice Ising model (\(\sigma=0\)).\\
+            \subref{sfig:gettingCrit:collapse_s_0} The curve from \subref{sfig:gettingCrit:binder_s_0}
+                collapsed by finite size scaling (errors are for clarity
+                not given, see Tab.\ \ref{tab:critExp})
         }
@@
         {
+            Examples for the method of finite size scaling, which was used
+            to determine the critical exponents \(\nu, \gamma, \beta\) and
+            the critical temperature \(T_c\).\\
             \subref{sfig:gettingCrit:s_1_sus} The susceptibility \(\chi\)
@@
             \subref{sfig:gettingCrit:collapse_s_1_sus} collapsed by finite
-                size scaling (for error estimates see Tab.\ \ref{tab:critExp})\\
-            \subref{sfig:gettingCrit:s_1_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
+                size scaling, to determine \(\gamma\) (for error estimates see Tab.\ \ref{tab:critExp}).\\
+            \subref{sfig:gettingCrit:s_1_meanM} The mean magnetization \(\avg{\abs{m}}\)
                 of an Ising model on an GG \(\sigma=1\)\\
             \subref{sfig:gettingCrit:collapse_s_1_meanM} collapsed by finite
-                size scaling (for error estimates see Tab.\ \ref{tab:critExp})
+                size scaling, to determine \(\beta\) (for error estimates see Tab.\ \ref{tab:critExp}).
         }
@@
         \end{tabular}
-        \caption[Critical Exponents for Different $\sigma$]{Critical exponents for different $\sigma$}
+        \caption[Critical Exponents for Different $\sigma$]{
+            Critical exponents for different $\sigma$. A finite size
+            scaling analysis was performed to determine the critical
+            exponents \(\beta, \gamma, \nu\) and the critical temperature
+            \(T_c\). The errors for \(beta\) and \(\gamma\) are estimates
+            by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
+            \(\nu\) and \(T_c\) are the standard deviation of three obtained
+            values through different collapses.
+        }
         \label{tab:critExp}
@@
         }
-        \caption[Alternative Way Determining $\gamma$]
+        \caption[Alternative Way Determining $\gamma / \nu$]
         {
-            Cross checking the critical exponent $\gamma$ for
+            Cross checking the ratio critical exponents $\gamma$ and $\nu$ for
                 \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
                 \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
+            The plotted values are the maxima of all measured \(\chi\).
             Dotted lines are power law fits \(aL^\frac{\gamma}{\nu}\).
@@
             The Binder cumulant \(g\) of an square lattice Ising model
-            (\(\sigma=0\)) interpolated with cubic splines
-            (the errorbars are too small to see)\\
+            (\(\sigma=0\)) interpolated with cubic splines, to determine
+            the intersection, which is at \(T_c\)
+            (the errorbars are too small to see).\\
         }
@@
         \end{tabular}
-        \caption[Critical Temperatures for Different $\sigma$]{Critical temperatures for different $\sigma$}
+        \caption[Critical Temperatures for Different $\sigma$]{
+            Critical temperatures for different $\sigma$. For both graph
+            types, GG and RNG. \(T_c^{\mathrm{collapse}}\) denotes the
+            values of \(T_c\) which were determined before via finte
+            size scaling analysis. The other values are determined by
+            the intersection of the binder cumulants \(g\) for different
+            system sizes. The values of both methods match.
+        }
         \label{tab:critTemp}
@@
             \subref{sfig:Tc:GG} the GG.\\
+            Interesting points are the jump and rise of the GG at small
+            \(\sigma\). And the plateau on the RNG for small \(\sigma\).
         }
@@
     This is lower than for the square lattice with degree 4.\\
+    This is plausible, because more edges lead to more neighbors. The energy
+    which is necessary to flip a spins down which neighbors spins are up,
+    gets higher with the number of neighbors. So the more edges are in
+    the graph, the more stable the system becomes and \(T_c\) is higher.
+    This is also an explanation why the \(T_c\) of the RNG is always
+    lower than that of the GG: The degree of the \(T_c\) is lower.\\
     If one plots the degree of the graphs at different \(\sigma\) like
@@
         {
-            GG with periodic boundary conditions for different \(\sigma = 0\)
+            GG with periodic boundary conditions for different \(\sigma = 0\).
+            The number of edges increases from \subref{sfig:GG_sigma:0.00}
+            to \subref{sfig:GG_sigma:0.01} significantly. Until \subref{sfig:GG_sigma:0.15}
+            it increases and after that the number of edges decreases.
         }
@@
         {
-            RNG with periodic boundary conditions for different \(\sigma = 0\)
+            RNG with periodic boundary conditions for different \(\sigma = 0\).
+            \subref{sfig:RNG_sigma:0.09} has still almost the square lattice
+            configuration of edges, which is why the plateau from Fig.\ \ref{sfig:Tc}\subref{sfig:Tc:RNG}
+            exsists. In the next two pictures one sees the fast disappearance
+            of edges.
         }

### 2013-08-16 Tex/chapters/conclusion.tex
Conclusion angepasst... muss wohl noch ausgebaut werden

@@
-In this thesis the properties of an Ising ferromagnet which nodes are
-moved by a Gaussian distributed displacement is studied. The neighbor
-relationship is provided by two proximity graphs -- the RNG and the GG.
-The coupling constants are distance dependend. This model is within the
-universality of the square lattice Ising ferromagnet. Its critical temperature
-decreases with increasing disorder on a RNG. On a GG it first jumps,
-increases up to a maximum and decreases after that. The course of the
-critical temperatures can be made plausible observing the degree of the
-underlying graph, but no explicit formular was found.
+In this thesis the properties of an Ising ferromagnet, which nodes are
+moved by a Gaussian distributed displacement, is studied with Monte Carlo
+Simulations. The neighbor relationship is provided by two proximity graphs
+-- the RNG and the GG. These graphs conserve the two dimensional character
+of the lattice, because their edges do not cross. The coupling constants
+are distance dependend, they are getting exponential weaker at higher distances.\\
+This model is within the universality of the square lattice Ising
+ferromagnet. Its critical temperature decreases with increasing disorder
+on a RNG. On a GG it first jumps, increases up to a maximum and decreases
+after that. At high disorder it approaches the limit of randomly generated
+graphs of the respective type. The course of the critical temperatures
+can be made plausible observing the degree of the underlying graph, but
+no explicit formular was found.
 
@@
     Delaunay triangulation to examine if it is also similar.\\
-    Also it would be interesting to compare this results with the
-    results obtained by the same experiments with \(\alpha = 0\), which
-    implies that the coupling constant is independent from the distance
-    on the sites. That way the critical temperature would be more
-    straight forward normalized by the degree of the graph. It
-    could be determined if the qualitative similarities of the
-    normalized temperatures over the disorder parameter of different
-    graph types are related to the choice of the function determining the
-    coupling constant.

### 2013-08-21 Tex/chapters/acknowledgements.tex
Entwurf für die Danksagungen

@@
 \section*{Acknowledgements}
-Danke
+    I would like to thank Christoph Norrenbrock and Dr. Oliver Melchert
+    in whose office I worked on this thesis. Whenever I had a problem,
+    it was no long way to ask one of them and their suggestions were
+    always helpful. I am also grateful for the interesting subject, which
+    was suggested by Christoph.\\
+    Further I want to thank Prof. Dr. Alexander Hartmann, who offered the
+    possibility to write this thesis in this working group,
+    and the other members of this working group for the pleasant working
+    atmosphere and conversations at lunch.\\
+    This acknowledgement would not be complete if I had not thanked my
+    parents. Whenever I told them about this thesis or showed some weird
+    graphs, they were listening and truly interested.

### 2013-08-21 Tex/chapters/results.tex
kleiner Verbesserungen: Formel beschriftet, Akronym deutlicher

@@
     the generated data is evaluated via Python scripts.
+    Most simulations were carried out on HERO, the \textbf{H}igh-\textbf{E}nd
+    Computing \textbf{R}esource \textbf{O}ldenburg.
     The entire source code is available at \url{https://github.com/surt91/IsingFerromagnet}.\\
-    Most simulations were carried out on HERO, the \emph{H}igh-\emph{E}nd
-    Computing \emph{R}esource \emph{O}ldenburg.\\
 

### 2013-08-21 Tex/chapters/model.tex
kleinere Korrekturen
Bildunterschriften ausführlicher und einige ergänzungen
Cell Methode etwas mehr erläutert.

@@
         {
-            \subref{sfig:lunes:def} Lunes of RNG (hatched region) and
-                GG (cross hatched region)
+            \subref{sfig:lunes:def} Lunes, which define where an edge
+                exsist, of RNG (hatched region) and GG (cross hatched region)
             \subref{sfig:lunes:rng} Example of a RNG on periodic
@@
     for each cell a list with nodes lying inside like presented in
-    \cite{RNGCell}.\\
+    \cite{RNGCell} and sketched in Fig.\ \ref{fig:cell}.
     \begin{figure}[htbp]
         \centering
-        \subfigure[Definition of the Lunes][]{
+        \subfigure[not Connected Nodes][]{
             \label{sfig:cell:big}
@@
         }
-        \subfigure[RNG example][]{
+        \subfigure[Connected Nodes][]{
             \label{sfig:cell:small}
@@
             single node in an inner cell of the bounding box to discard
-            the edge between two distant nodes.\\
+            the edge between two distant nodes. The nodes inside the
+            other 8 marked cells do not have to be tested anymore.\\
             \subref{sfig:cell:small} shows that only the nodes inside the
@@
     box of their lune and consequently only very few nodes have to be tested.\\
+    Here the number of cells equals the number of nodes.
     Indeed this method reduced the time needed to construct a RNG with

### 2013-08-21 Tex/chapters/methods.tex
Bildunterschriften ausführlicher und einige ergänzungen
kleiner Verbesserungen: Formel beschriftet, Akronym deutlicher
Grenzen einer Summation korrigiert
Kursiv etwas durchgängiger

@@
     \begin{equation}
-        O_M = \frac{1}{M} \sum_{i=0}^M O_i,
+        O_M = \frac{1}{M} \sum_{i=1}^M O_i,
     \end{equation}
@@
     \subsubsection{Metropolis}
-        A Metropolis Monte Carlo \cite{Metropolis1953} simulation of an
+        A \emph{Metropolis} Monte Carlo \cite{Metropolis1953} simulation of an
         Ising model will choose a random spin, calculate the energy change
@@
         gets slower. This is called \emph{critical slowing} down.\\
-        In order to circumvent this a cluster algorithm like the Wolff
+        In order to circumvent this a cluster algorithm like the \emph{Wolff}
         algorithm \cite{Wolff1989} can be used.
@@
         \begin{equation}
-            P((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}},
+            P_{i,i+1}((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}},
             \label{eq:partemp}
@@
             {
-                \subref{sfig:equiandauto:equiE} Example of a Ising system
-                    \(L=64\) reaching equilibrium at \(T=2.36\) and
-                \subref{sfig:equiandauto:autoM} the autocorrelation of an
+                \subref{sfig:equiandauto:equiE} Example of an Ising system
+                    \(L=64\) reaching thermal equilibrium at \(T=2.36\) after
+                    approximately \(n=50\) sweeps.\\
+                \subref{sfig:equiandauto:autoM} The autocorrelation of an
                     Ising system \(L=64\) at \(T=2.40\) (only Metropolis

### 2013-08-21 Tex/chapters/acknowledgements.tex
Wortabstand hinter Dr. korrigiert

--- 2013-07-30 Tex/chapters/acknowledgements.tex
@@
 \section*{Acknowledgements}
-Danke
+    I would like to thank Christoph Norrenbrock and Dr.\ Oliver Melchert
+    in whose office I worked on this thesis. Whenever I had a problem,
+    it was no long way to ask one of them and their suggestions were
+    always helpful. I am also grateful for the interesting subject, which
+    was suggested by Christoph.\\
+    Further I want to thank Prof.\ Dr.\ Alexander Hartmann, who offered the
+    possibility to write this thesis in this working group,
+    and the other members of this working group for the pleasant working
+    atmosphere and conversations at lunch.\\
+    This acknowledgement would not be complete if I had not thanked my
+    parents. Whenever I told them about this thesis or showed some weird
+    graphs, they were listening and truly interested.

### 2013-08-31 Tex/chapters/appendix.tex
Rechtschreib- und Kommafehler
außerdem kleiner Formulierungsverbesserungen

@@
     is plotted for different system sizes. The finite size effects are obvious.
-    The divergence is finite, and gets shallower with smaller \(L\). Besides
+    The divergence is finite and gets shallower with smaller \(L\). Besides
     the maximum moves away from the critical temperature with smaller \(L\).
@@
     The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
-    for variable \(J\) with \(\alpha=0.5\). This suggests, that the
+    for variable \(J\) with \(\alpha=0.5\). This suggests that the
     disappearance of the jump is a random special case for the function

### 2013-08-31 Tex/chapters/introduction.tex
Rechtschreib- und Kommafehler
außerdem kleiner Formulierungsverbesserungen

@@
 whole system is not easy to predict because of the interactions of the
-subsystems. For those systems there often exist no analytic solutions
+subsystems. For those systems there often exists no analytic solutions
 or only for very simplified or special cases. But one can simulate all
@@
 Different phases of a material and the transitions between them were
-always of greatest interest. The ancient greek thought that everything
+always of greatest interest. The ancient Greek thought that everything
 consists of fire, water, air and earth, which are the archetypes of
@@
 model of a ferromagnet and will be explained in more detail in section
-\ref{ssec:isingmodel}. It is analytically solved in two dimension on
+\ref{ssec:isingmodel}. It is analytically solved in two dimensions on
 some regular lattices \cite{Onsager1944} \cite{Wannier1945}.
@@
 
-Unfortunately the memory of any computer is small in comparison with what
+Unfortunately the memory of any computer is small in comparison to what
 would be needed for a simulation of a system in the

### 2013-08-31 Tex/chapters/methods.tex
Rechtschreib- und Kommafehler
außerdem kleiner Formulierungsverbesserungen

@@
     \emph{equilibrium}. A canonical system can exchange energy with a
-    heat bath, thus has a constant temperature -- the temperature of the
+    heat bath, thus it has a constant temperature equal to the temperature of the
     heat bath.
-    Equilibrium is defined as a steady state, where
+    Equilibrium is defined as a steady state, wherein
     the observables are only fluctuating but not changing in any
@@
     These preliminary considerations make a phase transition at some
-    \(T\), where the influence of the entropy on \(F\) becomes the same
+    \(T\) where the influence of the entropy on \(F\) becomes the same
     order of magnitude as the influence of the internal energy on \(F\),
@@
     may show very different properties than in the thermodynamic limit.
-    To minimize these finite size effects, it is desirable to examine
+    To minimize these finite size effects it is desirable to examine
     systems with large \(N\). But \(2^N\) is a very rapidly increasing
     number, so for large \(N\) it is unfeasible to calculate the energy for each state, except
-    for cases, where it is possible to solve it analytically.\\
+    for cases where it is possible to solve it analytically.\\
     If not, one can get estimates of the observables for big \(N\) using
@@
     The idea behind Monte Carlo simulations is to take random samples of
-    the observable, which should be measured, and estimate the mean of
+    the observable, which should be measured, and to estimate the mean of
     the observable from this samples. To apply this technique to statistical
@@
     \end{equation}
-    It is however possible, that there are few states that contribute
+    It is however possible that there are few states contributing
     massively more than others. In canonical systems at low \(T\),
@@
     contributions to the sum.
-    As noted before the system under scrutiny is canonical and therefore
+    As noted before, the system under scrutiny is canonical and therefore
     \(p_i\) is known. The states are distributed according to the Boltzmann
@@
     Instead of sampling uniformly distributed random states, one should sample
-    states, according to their occurence probability given by the Boltzmann
+    states according to their occurence probability given by the Boltzmann
     distribution. In fact this reduces the estimator to
@@
     \end{equation}
-    where \(M\) is the number of samples, as shown in \cite{NewmanBarkema1999}.
+    where \(M\) is the number of samples. The proof is shown in \cite{NewmanBarkema1999}.
     This is a very convenient form.\\
@@
     efficient, because many generated states will be discarded and the
-    computing time to generate them and caluculating their energy will
+    computing time to generate them and calculating their energy will
     be wasted.
     Hence one uses \emph{Markov Chains} to generate new states \(\nu\)
-    from old ones \(\mu\). It is important that the transition probabilities
+    from former ones \(\mu\). It is important that the transition probabilities
     \(A(\mu \to \nu)\) obey \emph{Detailed Balance} and \emph{Ergodicity}.
@@
         where \(J\) is the coupling constant (c.f.\ Sec.\ \ref{ssec:isingmodel}).
-        The neighboring sites of the added sites
-        are also considered and so forth. When there are no more sites
-        to add, the spin of every site in the cluster is flipped
+        For every site that is added, the neighboring sites of it are
+        also considered for addition. (In the case that they are added,
+        they are "added sites" and thus their neighbors get a chance to be
+        added too.)
+        This procedure continues until there are no more sites to add.
+        Then the spin of every site in the cluster is flipped
         \cite[p. 91ff]{NewmanBarkema1999} \cite[p. 151f]{Katzgraber2011}.
@@
         temperatures are far smaller, because their spin configuration
-        gets often replaced by another uncorrelated configuration. In
-        many cases the more important advantage is that a system which
-        is trapped in a local minimum at a given temperature can travel
+        often gets replaced by another uncorrelated configuration. In
+        many cases the more important advantage is that a system, which
+        is trapped in a local minimum at a given temperature, can travel
         to higher temperatures, leave its local minimum and cool down
@@
         In the case of a ferromagnetic Ising model the risk to get trapped
-        in an local energy minimum is very low. Consequently the autocorrelation
-        decreases significantly. In the scope of this thesis this comes
+        in a local energy minimum is very low. Consequently the autocorrelation
+        decreases significantly. In the scope of this thesis parallel tempering comes
         for no cost, because one has to simulate for many temperatures
         to determine the critical temperature. The additional calculations
-        to determine whether to swap configurations or not are small in
+        to determine whether to swap configurations or not, are small in
         comparison with those that would be needed to generate a new
@@
         For each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
-        and one parallel tempering swap are performed. Where \(N\) is the
+        and one parallel tempering swap are performed, where \(N\) is the
         number of sites.\\
@@
         observing the change of the observables over the progressing
-        simulation, as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
+        simulation as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
         The count of sweeps till
@@
         logarithmic plot \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
-        To get the autocorrelation time one can either fit a exponential
+        To get the autocorrelation time one can either fit an exponential
         function \(\exp(-t/\tau)\) like in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
@@
         samples are not correlated anymore \cite[p. 59ff]{NewmanBarkema1999} \cite[p. 150f]{Katzgraber2011}.
-        To ensure that the error is not underestimated one should wait
+        To ensure that the error is not underestimated, one should wait
         \(2\tau\) sweeps between two measurements.
@@
         \(\tau\) on the system size \(L\) is at \(T_{c}\) given by \(\tau \propto L^z\).
-        More general the power law \(\tau \propto \xi^z\) holds true, where
+        More general, the power law \(\tau \propto \xi^z\) holds true, where
         \(\xi\) is the \emph{correlation length}, which diverges at

### 2013-08-31 Tex/chapters/model.tex
Rechtschreib- und Kommafehler
außerdem kleiner Formulierungsverbesserungen

@@
     as the \emph{square lattice Ising model}, is a square lattice with edge length \(L\) and
-    \(N=L^2\) sites. Each site has a magnetic moment, the spin. Each
+    \(N=L^2\) sites. Each site has a magnetic moment, which is called the spin. Each
     spin can take a value \(s \in \{-1,+1\}\) and interacts with its
@@
         \input{images/Displacement}
-        \caption[Sketch how the Displacement Works]
+        \caption[Sketch how the Displacement works]
         {
@@
     \end{figure}\\
-    \(\sigma\) is also called \emph{disorder parameter} in the following.
+    \(\sigma\) will also be called \emph{disorder parameter} in the following.
     Most sites will only have one nearest neighbor after the
@@
     the lattice would collapse to many very small clusters. But if one
-    leaves the edges as the were before the displacement, the edges would
+    leaves the edges as they were before the displacement, the edges would
     cross -- at least for big displacements. The crossing of edges then
     would destroy the two dimensional character of the model and the results
-    would not be compareable with known results for the two dimensional
+    would not be compareable with known results of the two dimensional
     Ising model.
@@
     The boundary is periodic, i.e.\ nodes near the right edge can be
-    connected to nodes near the left edge and vice versa. Analogous the
+    connected to nodes near the left edge and vice versa. Analogously the
     top and bottom edges are connected. One can imagine that the model
     lives on the surface of a torus as pictured in Fig.\ \ref{fig:torusRNG}.
-    In subsequent graphics, the graphs will be unwrapped to rectangular
+    In subsequent graphics the graphs will be unwrapped to rectangular
     shapes. Connections which cross a periodic boundary are indicated
@@
     this for constant \(J\) and \cite{Lima2000} for \(J_{ij} = e^{-\alpha d_{ij}}\).
-    Both articles conclude, that this model lies within the universality
+    Both articles conclude that this model lies within the universality
     class of the square lattice Ising model, i.e.\ has the same critical
@@
     \end{figure}\\
-    To construct these graphs the simple way is to test for each
+    To construct these graphs the most simple way is to test for each
     pair of nodes if any other node lies in
@@
         }
-        \caption[Sketch how the Cell Method Works]
+        \caption[Sketch how the Cell Method works]
         {

### 2013-08-31 Tex/chapters/results.tex
fehlende Klammer korrigiert
Rechtschreib- und Kommafehler
außerdem kleiner Formulierungsverbesserungen

@@
             $t_{eq}$ for different system sizes $L$. All values are generously
-            rounded up and are determined as the maximum over all \(\sigma\).
+            rounded up and determined as the maximum over all \(\sigma\).
         }
@@
     \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
-    are omitted in the following for the sake of simplicity, so that the
+    are omitted in the following for the sake of simplicity so that the
     it will be just called \(O\).\\
@@
     necessary to determine \(\tau\) for each observable. Therefore a good
-    error estimate can be achieved by simple bootstrapping. Nevertheless one has
+    error estimate can be achieved by simple bootstrapping. Nevertheless, one has
     to simulate enough uncorrelated states for each realization to keep
@@
     The errors of fit parameters are the asymptotic standard errors as calculated
-    by gnuplot. Gnuplot is an open source plotting program, used for all plots
-    and fits in this thesis \footnote{\url{http://gnuplot.info/}.}.
+    by gnuplot. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
+    source plotting program used for all plots and fits in this thesis.
 
@@
     not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
-    for the Wolff cluster algorithm. On the one hand the number of sweeps
-    in which \(\tau\) is measured in this thesis are more than a standard
+    for the Wolff cluster algorithm. On the one hand the number of sweeps,
+    in which \(\tau\) is measured in this thesis, are more than a standard
     Metropolis sweep to which \(z\) normally corresponds, because each sweep
@@
     This is of course only a rough analysis of existing data which was
-    generated for another purpose. For a more in depth inspection, one
+    generated for another purpose. For a more detailed inspection, one
     would perform the simulation at the critical point, which will be
@@
     In the shown plots there occurs no steep decline to zero, but a
-    smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
+    smooth one. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
     systems, hence no computer simulation will show the exact behavior in the
@@
     These finite size effects cause a "smearing out" of the phase
-    transition. This is stronger for smaller system sizes, as is visible
+    transition. This is stronger for smaller system sizes, as shown
     in Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
@@
     \end{equation}
-    As the name critical \emph{exponent} suggests, the curve progression
+    As the name "critical \emph{exponent}" suggests, the curve progression
     of respective observables will often be a power law close to the critical
-    point, as in both examples above. But this is not imperative.
+    point as in both examples above. But this is not imperative.
     E.g.\ the critical "exponent" \(\alpha\) corresponding to the divergence of
@@
     universal for a model, i.e.\ they are independent of the size, the structure
-    or the coupling constant \(J\) \cite{NewmanBarkema1999} of the lattice,
-    therefore they should also be independent of \(\sigma\). But they are
+    or the coupling constant \(J\) \cite{NewmanBarkema1999} of the lattice.
+    Therefore they should also be independent of \(\sigma\). But they are
     not universal regarding the dimension of the model.
@@
     varying coupling constants \(J\) confirm that the
-    critical exponents are not influenced by an random lattice.
+    critical exponents are not influenced by a random lattice.
     So they will be used for consistency cross checking and
@@
     will be used. The here given explanation will give a rough idea, how
-    the method works. For a more in depth explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.
+    the method works. For a more detailed explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.
     The crucial element is that there exists a \emph{scaling function},
@@
     Analogically Fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
-    shows the collapse for the mean magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\),
+    show the collapse for the mean magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\)
     to determine the exponents \(\beta\) and \(\nu\).
-    Also the collapse of the binder cumulant as mentioned before and shown
-    in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
+    Also the collapse of the binder cumulant, as mentioned before and shown
+    in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0},
     is used to get a further value of \(\nu\).
@@
     \(\sigma = 0\) like mentioned before in Sec.\ \ref{ssec:finitesize}.
-    Therefore it is sufficient to take a few samples to test if the
+    Therefore it is sufficient to take a few samples to test, if the
     expectations match. Hence 5 values of \(\sigma\) are analyzed.
     The analytically known values for \(\sigma = 0\) and the in \cite{Janke1994}
-    examined limit of an random lattice \(\sigma \gtrsim 1\) are natural
+    examined limit of a random lattice \(\sigma \gtrsim 1\) are natural
     choices.
-    The other \(\sigma\) are chosen to represent regions, where the behavior of
+    The other \(\sigma\) are chosen to represent regions where the behavior of
     \(T_c\) shows some characteristics. (Namely there is a plateau at small
@@
     \end{table}\\
-    As can be seen in Tab.\ \ref{tab:critExp}, most values
+    According to Tab.\ \ref{tab:critExp}, most values
     are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
@@
     Maybe their deviations can be explained by the fact that small
-    systems (\(L=32,64\)) were used for the analysis, and no corrections
+    systems (\(L=32,64\)) were used for the analysis and no corrections
     to scaling terms were considered.
     Anyway, two critical exponents are sufficient to determine the
-    universality class \cite[p. 145]{Katzgraber2011}. Therefore
+    universality class \cite[p. 145]{Katzgraber2011}. Therefore,
     the Ising model on a proximity graph is for every \(\sigma\) in the
@@
 \label{ssec:binderIntersections}
-    Though if one is just interested in the critical temperature, an
+    Though, if one is just interested in the critical temperature, an
     easier approach is to find the intersections of the Binder cumulants
@@
     of \(T\), \(g\) is also only known for these discrete values and the
-    analytical course of the curve is not known, and hence has
+    analytical course of the curve is not known and hence has
     to be interpolated to find the intersection. Therefore a \emph{cubic spline}
@@
     \end{figure}\\
-    As an example take Fig.\ \ref{fig:gettingCrit:binder_fit_s_0}.
+    Take Fig.\ \ref{fig:gettingCrit:binder_fit_s_0} as an example.
     Here such interpolations are plotted for \(\sigma=0\) and are
@@
     To determine \(T_c\), the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
-    are averaged and the standard error is calculated. In this case one
+    are averaged and the standard error is calculated. In this case, one
     gets \(T_c = 2.2689(2)\), which is in good agreement with the
@@
     In this section \(T_c\) for both the RNG or the GG are
-    compared. In the following figures, the RNG will always be on the
+    compared. In the following figures the RNG will always be on the
     left side and the GG on the right side.
@@
             \midrule
-            0.00 & 2.2690(2)& 2.2689(7)& 2.2689(2)& 2.2687(5\\
+            0.00 & 2.2690(2)& 2.2689(7)& 2.2689(2)& 2.2687(5)\\
             0.03 & 2.2679(4)&          & 2.851(1) &         \\
@@
     Another strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
-    of \(T_c\) on the GG. To understand that, one has to
+    of \(T_c\) on the GG. To understand that one has to
     consider the influence of the graph properties on the critical
@@
     This is plausible, because more edges lead to more neighbors. The energy
-    which is necessary to flip a spins down which neighbors spins are up,
+    which is necessary to flip a spins down whose neighbors spins are up,
     gets higher with the number of neighbors. So the more edges are in
@@
     but is still existent. Anyway, the degree seems to have an impact on
-    the critical temperature \(T_c\) but it is not a trivial one.
+    the critical temperature \(T_c\), but it is not a trivial one.
     \begin{figure}[htbp]
@@
     \end{figure}\\
-    To understand the jump of \(T_c\), it seems to be necessary to
+    To understand the jump of \(T_c\) it seems to be necessary to
     understand the jump of \(K\), which is easily explained
@@
     the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
-    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
-    disorder has little influence on this normalized critical temperature.
+    Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
+    is that small disorder has little influence on this normalized critical
+    temperature.
     Also both graph types have a steep decline after the plateau before
@@
     lattice structure has a minor effect on \(g_c\), the uncertainty of
-    \(g_c\) is too big, to show it. For a more in depth analysis, new
+    \(g_c\) is too big, to show it. For a more exact analysis, new
     Monte Carlo simulations at \(T_c\) would be needed. But this is
-    beyond the scope of this thesis. Anyway the results are the expected
+    beyond the scope of this thesis. Anyway, the results are the expected
     behavior, because no major deviations from the value of \(g_c\) at

### 2013-09-03 Tex/chapters/introduction.tex
Rechtschreibfehler und Kleinigkeiten

@@
 But computers are not only able to process measured data, but
-also to generate data by simulations of e.g.\ statistical systems, where
+also to generate data by simulations of, e.g., statistical systems, where
 the rules for each subsystem are well defined but the behavior of the
@@
 system.
-For example to examine phase transitions, which are defined by the abrupt
-change of an observable, e.g.\ the change of the density of water near
+For example one can examine phase transitions, which are defined by the abrupt
+change of an observable, e.g., the change of the density of water near
 boiling or the change of the magnetization of a ferromagnet near the
@@
 consists of fire, water, air and earth, which are the archetypes of
-phases. Still phase transitions are alone on the basis of their ubiquity
-important phenomenons. The understanding allows applications from the
+phases. Still phase transitions are important phenomenons, because they
+are ubiquitious. The understanding allows applications from the
 refrigerator to shatter resistant mobile phone glass \cite{PJournalGlass}.
@@
 dimensions. This is a simple
-model of a ferromagnet and will be explained in more detail in section
+model of a ferromagnet and will be explained in more detail in Sec.\
 \ref{ssec:isingmodel}. It is analytically solved in two dimensions on

### 2013-09-03 Tex/chapters/methods.tex
Rechtschreibfehler und Kleinigkeiten

@@
     particular direction. For example thermal equilibrium denotes the
-    condition, that the system under scrutiny has reached the temperature
+    condition that the system under scrutiny has reached the temperature
     of the heat bath. This is the case, once there is no directed energy
@@
     where \(S\) is the entropy, \(U=\avg{H}\) the internal energy and
-    \(\avg{\cdot}\) declares the expected value of an observable.
+    \(\avg{\cdot}\) declares the expectation value of an observable.
     One can guess that for low \(T\) the internal energy
-    will be low, and for high \(T\) the entropy will be high, to minimize
+    will be low, and for high \(T\) the entropy will be high to minimize
     \(F\).
@@
     of high order, where most spins are aligned with their neighbors,
-    leads to a low \(H\) and therefore a low \(U\). Simultaneously, this
-    state of high order corresponds to a low entropy \(S\).
+    leads to a low value of \(H\) and therefore a low value of \(U\).
+    Simultaneously, this state of high order corresponds to a low entropy \(S\).
     Analogically a state of high \(U\) is also a state of high \(S\).
@@
     phase transition, hence \(m\) and \(E\) are continous, but show at
-    \(T_c\) an infinitly sharp slope in the thermodynamic limit i.e.\
+    \(T_c\) an infinitly sharp slope in the thermodynamic limit, i.e.\
     the first derivative diverges.
-    From statistical physics (compare \cite{nolting2005}) is known that
-    these derivatives can be expressed by fluctuations e.g.\ the specific
+    From statistical physics (compare \cite{nolting2005}) it is known that
+    these derivatives can be expressed by fluctuations, e.g.\ the specific
     heat can be expressed as
     \begin{equation}
-        c = \frac{\partial \avg{H}}{\partial T} = k_B \beta^2 \avg{\brac{H-\avg{H}}^2}
+        c = \frac{\partial \avg{H}}{\partial T} = k_B \beta^2 \avg{\brac{H-\avg{H}}^2}.
     \end{equation}
@@
     ensembles, one creates sample states of the system, measures the
-    observables calculates the expected value through averaging.\\
+    observables and calculates the expected value through averaging.\\
     In statistical physics the expected value of an observable \(O\)
@@
     \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_i p_i O_i
+        \avg{O} = \frac{1}{Z} \sum_i p_i O_i.
     \end{equation}
@@
     But if one samples the \(2^N\) states evenly, it is probable to miss
-    them. this is called \emph{simple sampling} and results in large
+    them. This is called \emph{simple sampling} and results in large
     errorbars for any observable.
@@
         simulation as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
-        The count of sweeps till
+        The count of sweeps until
         equilibrium is called \emph{equilibration time} \(t_{eq}\).

### 2013-09-03 Tex/chapters/model.tex
Rechtschreibfehler und Kleinigkeiten

@@
     the coupling constant. If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
-    For the square lattice Ising model \(J_{ij}=1 \forall i,j\) applies.
+    For the square lattice Ising model \(J_{ij} = 1 \ \forall i,j\) applies.
     \(h_i\) denotes the outer magnetic field at the position of
@@
     applies.\\
-    The most important modification of the square lattice Ising modell in this
-    thesis is, that the sites of the square lattice are displaced.
-    The displacement is randomly Gaussian distributed with the standard
+    The most important modification of the square lattice Ising model in this
+    thesis is that the sites of the square lattice are displaced.
+    The displacement is randomly Gaussian distributed with standard
     deviation \(\sigma\), i.e.\ the \(x\) and \(y\) coordinates of the
@@
     Most sites will only have one nearest neighbor after the
-    displacement. If only the edges between these neighbors remain,
+    displacement. If only the edges between these neighbors remained,
     the lattice would collapse to many very small clusters. But if one
-    leaves the edges as they were before the displacement, the edges would
+    left the edges as the were before the displacement, the edges would
     cross -- at least for big displacements. The crossing of edges then
     would destroy the two dimensional character of the model and the results
-    would not be compareable with known results of the two dimensional
+    would not be comparable with known results for the two dimensional
     Ising model.
@@
     \(J_{ij} = 1\), so that the disordered Ising model is reduced to the
-    square lattice Ising model. For this exists an analytic solution \cite{Onsager1944}.
+    square lattice Ising model. For this an analytic solution exists \cite{Onsager1944}.
     The critical temperature is
@@
     \end{equation}
-    and the critical exponents \(\alpha = 0\), \(\beta = \frac{1}{8}\)
+    and the critical exponents are \(\alpha = 0\), \(\beta = \frac{1}{8}\)
     and \(\gamma = \frac{7}{4}\). These values are universal for the Ising
@@
     lattice and the edges signal the neighbor status of two sites. If the
-    corresponding nodes are connected, the sites are neighbors.\\
+    corresponding nodes are connected, the sites will be neighbors.\\
     All here mentioned graph types are \emph{proximity graphs}.
@@
     Delaunay triangulation. Two nodes \(i\) and \(j\) with distance
-    \(d_{ij}\) are connected with an edge, if a circle with its
+    \(d_{ij}\) will be connected with an edge, if a circle with its
     center on half way between \(i\) and \(j\) and radius
@@
     subgraph of the GG. Two nodes \(i\) and \(j\) with
-    distance \(d_{ij}\) are connected, if no other node is in the
-    \emph{lune}. The lune is defined as the interSec.\ of two
+    distance \(d_{ij}\) will be connected, if no other node is in the
+    \emph{lune}. The lune is defined as the intersection of two
     circles with radius \(r = d\) and centers on \(i\) and \(j\).
@@
     \end{figure}\\
-    To construct these graphs the most simple way is to test for each
+    The simplest way to construct these graphs is to test for each
     pair of nodes if any other node lies in

### 2013-09-03 Tex/chapters/results.tex
Rechtschreibfehler und Kleinigkeiten

@@
     \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
-    are omitted in the following for the sake of simplicity so that the
+    are omitted in the following for the sake of simplicity so
     it will be just called \(O\).\\
@@
     estimator \(\avg{O_b}\) of this bootstrap sample and doing this \(k\)
-    times. Then the standard deviation of of the \(k\) calculated \(\avg{O_b}\)
+    times. Then the standard deviation of the \(k\) calculated \(\avg{O_b}\)
     is taken as an estimate for \(\Delta \overline{\avg{O}}\).
@@
     \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
-    Nevertheless it is interesting, that it obeys a power law
+    Nevertheless it is interesting that it obeys a power law
     \(\tau \propto L^{z'}\). This suggests that \(\xi \gtrsim L\)
@@
     times continuously differentiable. This interpolation type has the
-    advantage, that it is only influenced by local points so that the
+    advantage that it is only influenced by local points so that the
     plateaus at low and high \(T\) do not influence the interpolation in
@@
     And in Tab.\ \ref{tab:critTemp} the values are displayed together with the
-    values obtained by the data collapse from the Sec.\ before.
+    values obtained by the data collapse from the section before.
     \begin{table}[htbp]
@@
     The values obtained through the data collapse and the values obtained
-    through the interSec.\ of the binder cumulant are always in good
+    through the intersection of the binder cumulant are always in good
     agreement and of comparable precision.\\
@@
     maximum at \(\sigma \approx 0.15\) on the GG will be discussed later.
-    For big \(\sigma\) the displaced nodes approach the limit of randomly
+    For large values of \(\sigma\) the displaced nodes approach the limit of randomly
     distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
@@
     This is plausible, because more edges lead to more neighbors. The energy
-    which is necessary to flip a spins down whose neighbors spins are up,
+    which is necessary to flip a spin down while the spins of its neighbors are up,
     gets higher with the number of neighbors. So the more edges are in
-    the graph, the more stable the system becomes and \(T_c\) is higher.
+    the graph the more stable the system becomes and \(T_c\) is higher.
     This is also an explanation why the \(T_c\) of the RNG is always
@@
     To fully understand this, take four nodes forming a square. The edge
-    across does not exist, because the other two nodes are on the edge
+    across does not exist, because the other two nodes are on the border
     of the lune. Moving one node slightly into the square, causes the lune
-    to get smaller, hence no other nodes are inside or on the edge of
+    to get smaller, hence no other nodes are inside or on the border of
     the lune anymore and the edge appears. This process is sketched in
-    Fig.\ \ref{fig:GGEdge}
+    Fig.\ \ref{fig:GGEdge}.
     \begin{figure}[htbp]
         \centering
-        \subfigure[Definition of the Lunes][]{
+        \subfigure[][]{
             \label{sfig:GGEdge:before}
@@
         }
-        \subfigure[RNG example][]{
+        \subfigure[][]{
             \label{sfig:GGEdge:after}
@@
     Then more edges disappear, than appear at further displacement. This
-    is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
+    is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
     \begin{figure}[htbp]
@@
             \subref{sfig:RNG_sigma:0.09} has still almost the square lattice
-            configuration of edges, which is why the plateau from Fig.\ \ref{sfig:Tc}\subref{sfig:Tc:RNG}
-            exsists. In the next two pictures one sees the fast disappearance
+            configuration of edges, which is why the plateau from Fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}
+            exists. In the next two pictures one sees the fast disappearance
             of edges.

### 2013-09-03 Tex/chapters/introduction.tex
Formulierungs und Inhaltskorrekturen

@@
 the rules for each subsystem are well defined but the behavior of the
-whole system is not easy to predict because of the interactions of the
+whole system is not easy to predict because of the nontrivial interactions of the
 subsystems. For those systems there often exists no analytic solutions
@@
 the interactions of the subsystems and observe the behavior of the whole
-system.
+system using computational experiments.
 For example one can examine phase transitions, which are defined by the abrupt
@@
 refrigerator to shatter resistant mobile phone glass \cite{PJournalGlass}.
-One of the simplest models with a second order
-phase transition, i.e.\ a continuous transition without discontinuities of
-the order parameter, is the Ising model \cite{Ising1925} in \(d \ge 2\)
-dimensions. This is a simple
+There are different kinds of phase transitions which are distinguished by
+the behavior of their order parameter and characterized by a set of
+critical exponents \cite{yeomans}. If it shows a discontinuity at
+the phase transition, it is a \emph{first order} phase transition, e.g.\ Water at boiling.
+A \emph{second order} phase transition is characterized by a continuous
+transition without discontinuities of the order parameter.\\
+One of the simplest models with a second order phase transition is the
+Ising model \cite{Ising1925} in \(d \ge 2\) dimensions. This is a simple
 model of a ferromagnet and will be explained in more detail in Sec.\
@@
 (see Sec.\ \ref{ssec:graphtypes}) will be examined using the Monte
-Carlo simulations described in Sec.\ \ref{ssec:montecarlo}.
+Carlo simulations described in Sec.\ \ref{ssec:montecarlo}.\\
+Proximity graphs establish a lattice by connecting sites which are "near"
+to each other. The exact definition of "near" is dependend on the proximity
+graph.\\
+Because the Ising model on a regular square lattice is well understood,
+the here investigated irregular lattices will be constructed starting from
+a square lattice and displacing the sites governed by an parameter \(\sigma\).
+Then the influence of \(\sigma\) on the critical temperature will be
+analyzed. A crossover of the critical temperature from the square lattice
+to the corresponding proximity graph is expected.\\
 
@@
 would be needed for a simulation of a system in the
-thermodynamic limit. So only a very small number of subsystems can be
-simulated in comparison to the actual number of subsystems
+thermodynamic limit. So only a very small number of elementary subsystems can be
+simulated in comparison to the actual number of elementary subsystems
 of the system in nature. This leads to deviations from the real behavior

### 2013-09-03 Tex/chapters/methods.tex
Formulierungs und Inhaltskorrekturen

@@
     in a straight forward way, as stated in every textbook about
-    statistical physics (e.g.\ \cite{nolting2005}).\\
+    statistical physics (e.g.\ Ref.\ \cite{nolting2005}).\\
     Because of
@@
     \end{equation}
-    or any expected value of an observable
-    \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_i O_i e^{-\beta H_i},
-    \end{equation}
     one has to know the partition function
@@
     where the sum goes over all possible states \(i\) of the system.
+    Then, averages can be computed according to
+    \begin{equation}
+        \avg{O} = \frac{1}{Z} \sum_i O_i e^{-\beta H_i},
+    \end{equation}
     Because every site can have two states, there are \(2^N\) different
@@
 
-    The observables which are measured in this thesis are the mean
+    The observables which are measured in this thesis are the
     magnetization per spin
@@
     \end{equation}
-    and the mean energy per spin
+    and the energy per spin
     \begin{equation}
-        E = \frac{1}{N} \avg{H}.
+        E = \frac{1}{N} H.
     \end{equation}
@@
     the first derivative diverges.
-    From statistical physics (compare \cite{nolting2005}) it is known that
+    From statistical physics (See Ref.\ \cite{nolting2005}) it is known that
     these derivatives can be expressed by fluctuations, e.g.\ the specific
@@
     desired distribution in equilibrium \cite{NewmanBarkema1999}.
-    And \emph{Ergodicity} requires that every possible state is reachable
-    from every other state in finite time \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
+    \emph{Ergodicity} requires that every possible state is reachable
+    from every other state in finite time, see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
     Otherwise the samples might not be representative for the whole system.\\
@@
     were used. They will be shortly described in the following subsections.
+    But first equilibration- and autocorrelation time will be discussed.
 
-    \subsubsection{Metropolis}
+    \subsubsection{Equilibration- and Autocorrelation Time}
+    \label{sssec:eqtime}
+        To generate states acoording to the Boltzmann distribution at a
+        given temperature \(T\), one starts with an arbitrary state
+        and waits until it reaches thermal \emph{equilibrium}. Because
+        equilibrium is defined as a steady state, one can determine it by
+        observing the change of the observables over the progressing
+        simulation as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
+        The count of sweeps until
+        equilibrium is reached, is called \emph{equilibration time} \(t_{eq}\).
+        All measurements should start after this time.\\
+        In Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
+        the equilibrium is reached after approximately \(N_{s} \approx 100\) sweeps for
+        both an initial condition of all spins up and all spins random. It
+        does not harm to double that value to be save. Particularly, because
+        it is a random process, so that there can not be an exact value.
+        \begin{figure}[htbp]
+            \centering
+            \subfigure[Example of an Equilibrating Ising System][]{
+                    \label{sfig:equiandauto:equiE}
+                    \includegraphics[width=0.47\textwidth]{plots/equiE}
+            }
+            \subfigure[Example of the Autocorrelation of an Ising System][]{
+                    \label{sfig:equiandauto:autoM}
+                    \includegraphics[width=0.47\textwidth]{plots/autoM}
+            }
+            \caption[Examples for Equilibration and Autocorrelation]
+            {
+                \subref{sfig:equiandauto:equiE} Example of an Ising system
+                    \(L=64\) reaching thermal equilibrium at \(T=2.36\) after
+                    approximately \(n=100\) sweeps.\\
+                \subref{sfig:equiandauto:autoM} The autocorrelation of an
+                    Ising system \(L=64\) at \(T=2.40\) (only Metropolis
+                    sweeps -- otherwise the decline is too steep to show)
+                    on half logarithmic axis.
+                    The straight line is an exponential fit \(\exp(-t/\tau)\)
+                    with \(\tau = 342(1)\).
+            }
+            \label{fig:equiandauto}
+        \end{figure}\\
+        Because every state is generated from the preceding state, measurements
+        of subsequent states are correlated. To determine when two states
+        are independent, one calculates the normalized autocorrelation function
+        \(\frac{\chi(t)}{\chi(0)}\) with
+        \begin{equation}
+            \chi(t) = \int \mathrm{d} t' \, [m(t') -\avg{m}][m(t'+t)-\avg{m}],
+        \end{equation}
+        which is expected to decay exponentially
+        \(\chi(t) \propto \exp(t/\tau)\). This is visible in the semilogarithmic
+        plot shown in  Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
+        To get the autocorrelation time one can either fit an exponential
+        function \(\exp(-t/\tau)\) like in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
+        or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
+        \(\tau\) is an estimate that specifies the time after which two
+        samples are not correlated anymore, see Refs.\ \cite[p. 59ff]{NewmanBarkema1999} \cite[p. 150f]{Katzgraber2011}.
+        To ensure that the error is not underestimated, one should wait
+        \(2\tau\) sweeps between two measurements.
+        The autocorrelation time is dependent on the temperature.
+        For example for the standard Metropolis algorithm the fluctuations
+        are strong at high temperatures and subsequent
+        states are more dissimilar and therefore less correlated than at low
+        temperatures, where less spins are flipping. But the longest
+        autocorrelation times are encountered at the critical temperature.
+        This effect is called \emph{critical slowing down} and is
+        characterized by the \emph{dynamical critical exponent} \(z\)
+        \cite{SwendsenWang1987}. The dependence of the autocorrelation time
+        \(\tau\) on the system size \(L\) is at \(T_{c}\) given by \(\tau \propto L^z\).
+        More general, the power law scaling \(\tau \propto \xi^z\) holds, where
+        \(\xi\) is the \emph{correlation length}. It diverges at
+        \(T_{c}\) and is then limited by the size of the simulated lattice.
+        As mentioned in Sec.\ \ref{sssec:wolff}, the Wolff cluster algorithm
+        decreases \(z\) dramatically. This causes the course of the autocorrelation
+        time in dependence on temperature to change significantly as shown in
+        Sec.\ \ref{ssec:results:autocorr}. Also according to Ref.\ \cite{NewmanBarkema1999}
+        \(z\) is independent of the lattice structure, which ensures that
+        the simulation will benefit from the Wolff cluster algorithm at
+        any \(\sigma\).
+
+    \subsubsection{Single Spin Flip Metropolis Update}
         A \emph{Metropolis} Monte Carlo \cite{Metropolis1953} simulation of an
@@
         that would result from a flip of that spin and execute the flip
-        with the probability \cite{NewmanBarkema1999} \cite{Katzgraber2011}
+        with the probability, see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}
         \begin{equation}
@@
 
-    \subsubsection{Wolff}
+    \subsubsection{Wolff Cluster Update}
     \label{sssec:wolff}
-        Close to the critical temperature \(T_c\) the Metropolis
-        gets slower. This is called \emph{critical slowing} down.\\
+        Close to the critical temperature \(T_c\) the efficiency of the
+        single spin flip Metropolis update decreases significantly, i.e.\ the
+        autocorrelation time \(\tau\) diverges.
+        This is called \emph{critical slowing} down.\\
         In order to circumvent this a cluster algorithm like the \emph{Wolff}
@@
         will only contain very few sites.
-        Both situations have no advantage against the Metropolis algorithm.\\
+        Both situations have no advantage over the Metropolis algorithm.\\
         So one would activate this algorithm near the critical temperature
@@
                 \subref{sfig:parTemp:E} sketch of an energy landscape, where
-                the state of the system (filled dot) is trapped in an local
+                the state of the system (filled circle) is trapped in an local
                 minimum. At low temperatures it is very unlikley that it
@@
                 and after a swap to lower energies again, the state in
-                the minimum can be reached (hollow dot).
+                the minimum can be reached (open circle).
             }
@@
         in a local energy minimum is very low. Consequently the autocorrelation
-        decreases significantly. In the scope of this thesis parallel tempering comes
-        for no cost, because one has to simulate for many temperatures
+        decreases significantly. In the scope of this thesis it is benefical
+        to use parallel tempering, because one has to simulate at many temperatures
         to determine the critical temperature. The additional calculations
@@
     \subsubsection{Implementation Details}
-        Here a mixture of the above three algorithms is used.
-        For each sweep \(N\) Metropolis spin flips, one Wolff cluster flip
-        and one parallel tempering swap are performed, where \(N\) is the
-        number of sites.\\
+        Here, a mixture of the above three algorithms is used.
+        For each sweep \(N\) single spin flip Metropolis updates, one
+        Wolff cluster update and one parallel tempering swap are
+        performed.\\
         Because it is not known before, where the critical temperatures
         \(T_c\) are located, the Wolff cluster algorithm is used for
-        every temperature. The speed up near criticality is worth the
-        moderate slow down at other temperatures.
-
-    \subsubsection{Equilibration- and Autocorrelation Time}
-    \label{sssec:eqtime}
-        To generate states acoording to the Boltzmann distribution at a
-        given temperature \(T\), one starts with an arbitrary state
-        and waits until it reaches thermal \emph{equilibrium}. Because
-        equilibrium is defined as a steady state, one can determine it by
-        observing the change of the observables over the progressing
-        simulation as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
-        The count of sweeps until
-        equilibrium is called \emph{equilibration time} \(t_{eq}\).
-        All measurements should start after this time.\\
-        In Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
-        the equilibrium is reached after approximately \(N_{s} \approx 50\) sweeps for
-        both an initial condition of all spins up and all spins random. It
-        does not harm to double that value to be save. Particularly, because
-        it is a random process, so that there can not be an exact value.
-        \begin{figure}[htbp]
-            \centering
-            \subfigure[Example of an Equilibrating Ising System][]{
-                    \label{sfig:equiandauto:equiE}
-                    \includegraphics[width=0.47\textwidth]{plots/equiE}
-            }
-            \subfigure[Example of the Autocorrelation of an Ising System][]{
-                    \label{sfig:equiandauto:autoM}
-                    \includegraphics[width=0.47\textwidth]{plots/autoM}
-            }
-            \caption[Examples for Equilibration and Autocorrelation]
-            {
-                \subref{sfig:equiandauto:equiE} Example of an Ising system
-                    \(L=64\) reaching thermal equilibrium at \(T=2.36\) after
-                    approximately \(n=50\) sweeps.\\
-                \subref{sfig:equiandauto:autoM} The autocorrelation of an
-                    Ising system \(L=64\) at \(T=2.40\) (only Metropolis
-                    sweeps -- otherwise the decline is too steep to show)
-                    on half logarithmic axis.
-                    The straight line is an exponential fit \(\exp(-t/\tau)\)
-                    with \(\tau = 342(1)\).
-            }
-            \label{fig:equiandauto}
-        \end{figure}\\
-        Because every state is generated from the state before, measurements
-        of subsequent states are correlated. To determine when two states
-        are independent, one calculates the normalized autocorrelation function
-        \(\frac{\chi(t)}{\chi(0)}\) with
-        \begin{equation}
-            \chi(t) = \int \mathrm{d} t' \, [m(t') -\avg{m}][m(t'+t)-\avg{m}],
-        \end{equation}
-        which decays exponentially
-        \(\chi(t) \propto \exp(t/\tau)\). This is visible in the half
-        logarithmic plot \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
-        To get the autocorrelation time one can either fit an exponential
-        function \(\exp(-t/\tau)\) like in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
-        or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
-        \(\tau\) is an estimate that specifies the time after which two
-        samples are not correlated anymore \cite[p. 59ff]{NewmanBarkema1999} \cite[p. 150f]{Katzgraber2011}.
-        To ensure that the error is not underestimated, one should wait
-        \(2\tau\) sweeps between two measurements.
-        The autocorrelation time is dependent on the temperature.
-        For example for the standard Metropolis algorithm the fluctuations
-        are strong at high temperatures and subsequent
-        states are more dissimilar and therefore less correlated than at low
-        temperatures, where less spins are flipping. But the longest
-        autocorrelation times are encountered at the critical temperature.
-        This effect is called \emph{critical slowing down} and is
-        characterized by the \emph{dynamical critical exponent} \(z\)
-        \cite{SwendsenWang1987}. The dependence of the autocorrelation time
-        \(\tau\) on the system size \(L\) is at \(T_{c}\) given by \(\tau \propto L^z\).
-        More general, the power law \(\tau \propto \xi^z\) holds true, where
-        \(\xi\) is the \emph{correlation length}, which diverges at
-        \(T_{c}\) and is then limited by the size of the simulated lattice.
-        As mentioned in Sec.\ \ref{sssec:wolff}, the Wolff cluster algorithm
-        decreases \(z\) dramatically. This causes the course of the autocorrelation
-        time in dependence on temperature to change significantly as shown in
-        Sec.\ \ref{ssec:results:autocorr}. Also according to \cite{NewmanBarkema1999}
-        \(z\) is independent of the lattice structure, which ensures that
-        the simulation will benefit from the Wolff cluster algorithm at
-        any \(\sigma\).
+        every temperature. Albeit the efficiency of the algorithmic procedure
+        was not dissected for every temperature, I feel that the speed up
+        near criticality is worth the moderate slow down at other temperatures.

### 2013-09-03 Tex/chapters/model.tex
Formulierungs und Inhaltskorrekturen

@@
     The examined model is a 2D Ising model.
-    The most common definition of the Ising model, to which will be referred
-    as the \emph{square lattice Ising model}, is a square lattice with edge length \(L\) and
-    \(N=L^2\) sites. Each site has a magnetic moment, which is called the spin. Each
+    The most common definition of the Ising model, to which will be referred to
+    as the \emph{square lattice Ising model}, is a square lattice with
+    edge length \(L\) and \(N=L^2\) sites with periodic boundary conditions.
+    Note that \(N\) always refers to the number of sites in this thesis.
+    Each site has a magnetic moment, which is called the spin. Each
     spin can take a value \(s \in \{-1,+1\}\) and interacts with its
@@
     \begin{equation}
-        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i h_i s_i.
+        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
         \label{eq:hamiltonian}
@@
     coupling between \(i\) and \(j\) is characterized by \(J_{ij}\),
-    the coupling constant. If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
-    For the square lattice Ising model \(J_{ij} = 1 \ \forall i,j\) applies.
-    \(h_i\) denotes the outer magnetic field at the position of
-    site \(i\). For the square lattice Ising model \(h_i=0 \ \forall i\)
-    applies.\\
+    the coupling constant. If \(J_{ij} > 0 \ \forall \avg{i,j}\) the model resembles a ferromagnet.
+    For the square lattice Ising model \(J_{ij} = 1 \ \forall \avg{i,j}\) applies.\\
     The most important modification of the square lattice Ising model in this
-    thesis is that the sites of the square lattice are displaced.
+    thesis is that the sites of the square lattice are displaced introducing
+    geometric disorder resulting in a non regular graph structure.
     The displacement is randomly Gaussian distributed with standard
@@
     \end{figure}\\
-    \(\sigma\) will also be called \emph{disorder parameter} in the following.
-    Most sites will only have one nearest neighbor after the
+    In the following \(\sigma\) will also be called \emph{disorder parameter}.
+    If we take "nearest neighbor" in the Euclidean meaning, most sites
+    will only have one nearest neighbor after the
     displacement. If only the edges between these neighbors remained,
@@
     cross -- at least for big displacements. The crossing of edges then
-    would destroy the two dimensional character of the model and the results
-    would not be comparable with known results for the two dimensional
-    Ising model.
+    would destroy the planar character of the model.
     To avoid this, a new edge set will be etablished after the displacement.
@@
     one of the two in Sec.\ \ref{ssec:graphtypes} defined rules,
-    so that the lattice represents a proximity graph. Edges
-    of the used proximity graph do not cross each other, hence the 2D
-    character of the lattice is preserved. The coupling constant \(J\) gets
-    identified with edge weights. The weight of an edge \(E_{ij} =
-    J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean
-    distance between the nodes \(i\) and \(j\). The free parameter
-    \(\alpha\) is set to \(\alpha = 0.5\) inspired by \cite{Lima2000}.
+    so that for a given configuration of points the resulting graph is an
+    instance of a proximity graph. The coupling constant \(J\) gets
+    identified with edge weights. \(J\) will be changed to depend on the
+    geometric distance between the connected pair of sites. More precise,
+    the weight of an edge is \(E_{ij} = J_{ij} = \exp (\alpha (1-d_{ij}))\)
+    where \(d_{ij}\) is the Euclidean
+    distance between the nodes \(i\) and \(j\). Following Ref.\ \cite{Lima2000}
+    the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
     The boundary is periodic, i.e.\ nodes near the right edge can be
@@
             A graph on a torus to visualize periodic boundary conditions.
-            Note that the lattice on this torus is not a square but has
-            a height to width ratio of 1:4. At 1:1 the torus would cut
+            On this torus, for a more clear presentation, the underlying
+            graph exhibits a height to width ratio of 1:4. At 1:1 the torus would cut
             itself. Hence, the torus represents the geometry of the model
             not perfectly, but gives very quick the right idea.
-            %Also the shades are of course only a guide to the eye.
+            Also the shades are of course only a guide to the eye.
         }
@@
     The case for randomly distributed sites \(\sigma \gtrsim 1\) is
-    already studied on a Delaunay triangulation. \cite{Janke1994} examines
-    this for constant \(J\) and \cite{Lima2000} for \(J_{ij} = e^{-\alpha d_{ij}}\).
+    already studied on a Delaunay triangulation. Ref.\ \cite{Janke1994} examines
+    this for constant \(J\) and Ref.\ \cite{Lima2000} for \(J_{ij} = e^{-\alpha d_{ij}}\).
     Both articles conclude that this model lies within the universality
     class of the square lattice Ising model, i.e.\ has the same critical
-    exponents.
+    exponents, as can be expected since the underlying graph structure can
+    be embedded in 2D. Hence, due to universality it should exhibit the same
+    critical exponents as the basic square lattice Ising ferromagnet.
 
@@
     dimension can be used.\\
-
-    The Gabriel graph (GG) \cite{Gabriel1969} is a subgraph of the
-    Delaunay triangulation. Two nodes \(i\) and \(j\) with distance
+    \paragraph{The Delaunay triangulation} (DT) TODO!!
+    \paragraph{The Gabriel graph} (GG) \cite{Gabriel1969} is a subgraph of the
+    DT. Two nodes \(i\) and \(j\) with distance
     \(d_{ij}\) will be connected with an edge, if a circle with its
@@
     from Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.\\
-    The Relative Neighborhood graph (RNG) \cite{Toussaint1980} is a
+    \paragraph{The Relative Neighborhood graph} (RNG) \cite{Toussaint1980} is a
     subgraph of the GG. Two nodes \(i\) and \(j\) with
@@
             \subref{sfig:lunes:def} Lunes, which define where an edge
-                exsist, of RNG (hatched region) and GG (cross hatched region)
+                exist, of RNG (hatched region) and GG (cross hatched region)
             \subref{sfig:lunes:rng} Example of a RNG on periodic
@@
     the lune of the pair. That is of complexity \(O (N^3)\), because
-    there are \(N(N-1)\) pairs and for each \(N-2\) nodes to test. So
+    there are \(N(N-1)\) pairs and for each \((N-2)\) nodes to test. So
     the running time of a straight forward implementation would be of
     order \(O(N^3)\).\\
-    To reduce the complexity one can first create a Delaunay
-    Triangulation in complexity \(O (N \log N)\)
-    \cite{RNGCell} and test the criterion for each edge, because
-    the Delaunay triangulation is a supergraph of both. But the
-    implementation of a Delaunay triangulation algorithm is not trivial
-    and the generation of the graphs is not time critical in the scope
+    To reduce the complexity one can first create a DT in complexity \(O (N \log N)\)
+    \cite{RNGCell} and test the connectedness for each edge contained
+    therein, because the DT is a supergraph of both.
+    For the construction of the DT for a given set of points one might
+    use existing software libraries, e.g.\ the qHull\footnote{http://www.qhull.org} library.
+    However, generation of the graphs is not time critical in the scope
     of this bachelor thesis.\\
     So a trade off is to use basically the simple method but only test
-    the criterion for nodes which are near to the lune and abort if
+    the connectedness for nodes which are near to the lune and abort if
     one node inside the lune is found. To determine which nodes are
-    near the lune one can subdivide the area in \emph{cells} and save
-    for each cell a list with nodes lying inside like presented in
-    \cite{RNGCell} and sketched in Fig.\ \ref{fig:cell}.
+    near the lune one can subdivide the area in \(M\) \emph{cells} of size
+    \(L_c \times L_c\) and save for each cell a list with nodes lying
+    inside like presented in Ref.\ \cite{RNGCell} and sketched in Fig.\ \ref{fig:cell}.
+    The implementation of this thesis uses \(M=N\).
     \begin{figure}[htbp]
@@
     \end{figure}\\
-    Now it is just necessary to test the nodes in the cells which
+    Given the discretized cell structure it is just necessary to test the nodes in the cells which
     resemble a rectangular bounding box of the lune. Most pairs will be

### 2013-09-03 Tex/chapters/introduction.tex
Phasenübergang mit beispielen

@@
 change of an observable, e.g., the change of the density of water near
-boiling or the change of the magnetization of a ferromagnet near the
-Curie temperature.
+boiling, which is liquid at \(T < T_c\) and gaseous at \(T > T_c\). Or
+the change of the magnetization of a ferromagnet near the Curie temperature,
+which is ferromagnetic at \(T < T_c\) and paramagnetic at \(T > T_c\).
+This can be observed by heating some refrigerator magnet by a candle --
+after this treatment it will no longer stick on the refrigerator.
 Different phases of a material and the transitions between them were

### 2013-09-03 Tex/chapters/model.tex
Delaunay Triangulierung hinzu, und Struktur geändert

@@
 
-\subsection{Gabriel- and Relative Neighborhood Graph}
+\subsection{Proximity Graphs}
 \label{ssec:graphtypes}
@@
     dimension can be used.\\
-    \paragraph{The Delaunay triangulation} (DT) TODO!!
-    \paragraph{The Gabriel graph} (GG) \cite{Gabriel1969} is a subgraph of the
-    DT. Two nodes \(i\) and \(j\) with distance
+
+    \subsubsection{Delaunay Triangulation}
+        The Delaunay triangulation (DT) is an undirected graph. An edge
+        between two nodes \(i\) and \(j\) will be drawn, if there exists
+        a circle passing through \(i\) and \(j\), which does not contain
+        any other node in its interior, see Ref.\ \cite{Katajainen}.
+        To make this clear a the construction of a four node DT is sketched
+        in Fig.\ \ref{fig:def:DT} in the appendix Sec. \ref{appendix:DT_def}.
+
+    \subsubsection{Gabriel Graph}
+        The Gabriel graph (GG) \cite{Gabriel1969}
+        is a subgraph of the DT, i.e.\ for the same set of nodes
+        \(V\) the edge set of the DT is a superset of the edge set of the
+        GG \(E_{DT} \supseteq E_{GG}\). Two nodes \(i\) and \(j\) with distance
         \(d_{ij}\) will be connected with an edge, if a circle with its
@@
         called \emph{lune} in the following. See also the cross hatched region
-    from Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.\\
-    \paragraph{The Relative Neighborhood graph} (RNG) \cite{Toussaint1980} is a
-    subgraph of the GG. Two nodes \(i\) and \(j\) with
+        from Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.
+
+    \subsubsection{Relative Neighborhood Graph}
+        The Relative Neighborhood
+        graph (RNG) \cite{Toussaint1980} is a subgraph of the GG. Two nodes \(i\) and \(j\) with
         distance \(d_{ij}\) will be connected, if no other node is in the
@@
         See also the hatched region in Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.
+
     \begin{figure}[htbp]
@@
         \label{fig:lunes}
-    \end{figure}\\
+    \end{figure}
+
+    \subsubsection{Construction}
         The simplest way to construct these graphs is to test for each
@@
         For the construction of the DT for a given set of points one might
-    use existing software libraries, e.g.\ the qHull\footnote{http://www.qhull.org} library.
+        use existing software libraries, e.g.\ the \texttt{qHull}\footnote{\url{http://www.qhull.org}} library.
         However, generation of the graphs is not time critical in the scope

### 2013-09-03 Tex/chapters/appendix.tex
Im Appendix ein Bsp. DT gezeichnet

@@
 \section{Appendix}
+\subsection{Example for a Small Delaunay Triangulation}
+\label{appendix:DT_def}
+    The Delaunay triangulation (DT) is an undirected graph. An edge
+    between two nodes \(i\) and \(j\) will be drawn, if there exists
+    a circle passing through \(i\) and \(j\), which does not contain
+    any other node in its interior
+    \begin{figure}[htbp]
+    \centering
+        \input{images/DT_def}
+        \label{sfig:def:DT}
+        \caption[Example for a Small Delaunay Triangulation]
+        {
+            Circles, which contain nodes are dashed.
+            Circles, which contain no nodes are not dashed.
+            Consequently nodes on the border of not dashed circles are
+            connected. Note that in contrast to the GG the circles do not
+            have to be centered on the middle point between the nodes.
+        }
+    \end{figure}
+
 \subsection{Finite Size Effects at the Example of the Specific Heat}

### 2013-09-03 Tex/chapters/appendix.tex
Plausibel, warum DT > GG

@@
     a circle passing through \(i\) and \(j\), which does not contain
-    any other node in its interior
+    any other node in its interior.
     \begin{figure}[htbp]
@@
             Consequently nodes on the border of not dashed circles are
-            connected. Note that in contrast to the GG the circles do not
-            have to be centered on the middle point between the nodes.
+            connected. Note that the drawn cricles are only examples
+            as there there is an infinitive number of alternative not
+            dashed circles, which contain no other node.
+            Note also that in contrast to the GG the circles do not
+            have to be centered on the middle point between the nodes, if
+            however, the centered circle does not contain any node, the
+            resulting edge will be present in DT and GG. Therefore GG is
+            a subgraph of DT.
         }

### 2013-09-04 Tex/chapters/conclusion.tex
Rechtschreib- und Kommafehler
außerdem kleiner Formulierungsverbesserungen
Fehlerbehehungen und Ergänzungen

@@
 In this thesis the properties of an Ising ferromagnet, which nodes are
-moved by a Gaussian distributed displacement, is studied with Monte Carlo
+moved by a Gaussian distributed displacement up to the limiting case of
+a Poisson process, is studied with Monte Carlo
 Simulations. The neighbor relationship is provided by two proximity graphs
 -- the RNG and the GG. These graphs conserve the two dimensional character
-of the lattice, because their edges do not cross. The coupling constants
-are distance dependend, they are getting exponential weaker at higher distances.\\
+of the lattice. The coupling constants
+are distance dependent, with increasing distance the coupling strength
+decreases exponentially.
 This model is within the universality of the square lattice Ising
 ferromagnet. Its critical temperature decreases with increasing disorder
-on a RNG. On a GG it first jumps, increases up to a maximum and decreases
-after that. At high disorder it approaches the limit of randomly generated
+on a RNG. Since effectively, the decreasing avergae coordination number
+of the underlying graphs lowers the resistance to spin flips within
+strongly polarized configurations at low temperatures.
+ On a GG it first jumps, increases up to a maximum and decreases
+afterwards. At high disorder it approaches the limit of randomly generated
 graphs of the respective type. The course of the critical temperatures
-can be made plausible observing the degree of the underlying graph, but
-no explicit formular was found.
+can be made plausible observing the degree of the underlying graph, an
+approximate analytic statement as reason for the observed behavior was
+also presented.
 
@@
     on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
-    are qualitative similar to each other. One could study the behavior
+    are qualitatively similar to each other. One could study the behavior
     of other proximity graphs like the minimum spanning tree or the

### 2013-09-04 Tex/chapters/results.tex
Olivers Dissertation zitiert
Fehlerbehehungen und Ergänzungen

@@
     \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
-    (see also \ref{sssec:eqtime}). The used values for different system sizes
+    (see also Sec.\ \ref{sssec:eqtime}). The used values for different system sizes
     are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
@@
             $t_{eq}$ for different system sizes $L$. All values are generously
-            rounded up and determined as the maximum over all \(\sigma\).
+            rounded up and determined as the maximum over all \(\sigma\) and \(T\).
         }
@@
     generation of the random start configuration of the spins.\\
-    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
-    \cite{Bootstrap}\\
-    The bootstrapping method estimates error \(\Delta \overline{\avg{O}}\)
+    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrap resampling
+    \cite{Bootstrap}.\\
+    The bootstrapping method estimates the error \(\Delta \overline{\avg{O}}\)
     by taking \(M\) random samples from the \(M\) measured values of \(O\),
@@
     Before the results are presented, a short analysis of the
-    autocorrelation time \(\tau\) is given to illustrate the benefits
-    of the used Wolff cluster algorithm.\\
+    autocorrelation time \(\tau\) according to Eq.\ \ref{eq:tau} is given to
+    illustrate the benefits of the used Wolff cluster algorithm.\\
     In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
@@
                 to determine the dynamical exponent \(z'\).
-                (Errorbars are the standard error estimated by bootstrapping.)
+                (Errorbars are the standard error estimated by bootstrap resampling.)
         }
@@
     The plateau at low temperatures is easy to understand considering the
-    effects of the Wolff algorithm. At low temperatures it flips nearly every
+    effects of the Wolff cluster algorithm. At low temperatures it flips nearly every
     spin in every step, thus the correlation drops to zero after one sweep.
-    (Note that this is not the only explanation for the course of \(\tau\).
+    (Note that this is not the only explanation for the small values of \(\tau\).
     The parallel tempering algorithm swaps spin configurations
@@
     algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
+    But it is also possible that these are again finite size effects.
     Obviously the autocorrelation time \(\tau\) increases with the system
@@
     not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
-    for the Wolff cluster algorithm. On the one hand the number of sweeps,
+    expected for the Wolff cluster algorithm at \(T_c\). On the one hand the number of sweeps,
     in which \(\tau\) is measured in this thesis, are more than a standard
@@
     would perform the simulation at the critical point, which will be
-    determined in the next sections.
+    determined subsequently.
 
@@
     occurs at lower temperatures \(T\) for higher
-    disorder parameters \(\sigma\) (here with a RNG).
+    disorder parameters \(\sigma\).
     \begin{figure}[htbp]
@@
             and hence the critical temperature, moves to lower temperatures
-            with increasing \(\sigma\)\\
+            with increasing \(\sigma\) (\(0.0 \le \sigma \le 1.2\))\\
             \subref{sfig:smeared_out:meanM} Effects of different system
-            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
+            sizes at \(\sigma = 0\), i.e.\ the square lattice Ising ferromagnet.
+            Dotted lines are guides to the eye.
             The \(L=16\) curve is much less steep than the \(L=128\) curve.
@@
     \end{figure}\\
-    In the shown plots there occurs no steep decline to zero, but a
+    As evident from the figure there occurs no steep decline to zero, but a
     smooth one. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
     systems, hence no computer simulation will show the exact behavior in the
-    thermodynamic limit. It will always show some \emph{finte size effects}.
+    thermodynamic limit. It will always show some \emph{finite size effects}.
     These finite size effects cause a "smearing out" of the phase
@@
     in Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
-    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
-    Despite of this one can obtain \(T_c\) by finite size scaling
+    Clearly, the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
+    Despite of this one can obtain \(T_c\) by finite size scaling (FSS)
     methods \cite[p. 232ff]{NewmanBarkema1999}, which also yield the critical
-    exponents. This will be performed in the next section.
+    exponents. Such a FSS analysis will be performed in the next section.
     Though there is an easier approach, which yields comparable precise
@@
     The important property of the critical exponents is that they are
-    universal for a model, i.e.\ they are independent of the size, the structure
-    or the coupling constant \(J\) \cite{NewmanBarkema1999} of the lattice.
+    universal for a model with respect to certain model characteristics.
+    I.e.\ for a given dimension they are independent of the precise lattice
+    structure and the magnitude of the coupling constant \(J\).
     Therefore they should also be independent of \(\sigma\). But they are
     not universal regarding the dimension of the model.
-    Studies on random lattices with \cite{Lima2000} and without \cite{Janke1994}
+    Studies on random lattices with (Ref.\ \cite{Lima2000}) and without (Ref.\ \cite{Janke1994})
     varying coupling constants \(J\) confirm that the
-    critical exponents are not influenced by a random lattice.
+    critical exponents are not influenced by a random structure of the lattice.
     So they will be used for consistency cross checking and
@@
     temperatures are probably correct, too.\\
-    % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse
-    To determine the critical exponents, the finite size scaling method
-    will be used. The here given explanation will give a rough idea, how
-    the method works. For a more detailed explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.
+    To determine the critical exponents, the FSS method
+    will be used. The explanation below will give a rough idea how
+    the method works. A more detailed explanation can be found in Refs.\ \cite{Norrenbrock2011}, \cite{DMelchert2009} or \cite{Binder2010}.
     The crucial element is that there exists a \emph{scaling function},
@@
     collapse on one curve -- the scaling function.
-    Like the obersables from Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
-    collapse in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
-    %\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.
+    A data collapse of the curves showed in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
+    is illustrated in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
     The same principle can be used to determine the other two exponents.
     Note that \(L=16\) is not used for the collapse, because it is a
-    rather small value. Eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
+    rather small value of \(L\) for which deviations from the assumed
+    scaling behavior might be expected. I.e.\ Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
     are approximations for big \(L\). For small \(L\) one needs some
@@
             \subref{sfig:gettingCrit:collapse_s_0} The curve from \subref{sfig:gettingCrit:binder_s_0}
-                collapsed by finite size scaling (errors are for clarity
+                collapsed by FSS (errors are for clarity
                 not given, see Tab.\ \ref{tab:critExp})
@@
     \end{figure}\\
-    A finite size scaling analysis was
+    A FSS analysis was
     performed to determine the critical exponents \(\beta, \gamma, \nu\)
     using \texttt{autoscale.py} \cite{autoscale2009} and Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
-    The values for \(\nu\) are obtained by every collapse and are therefore
-    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_sus}\subref{sfig:gettingCrit:collapse_s_1_sus}
-    show an example collapse for \(\sigma=1\) of the magnetic susceptibility
+    The values for \(\nu\) are obtained by data collapse for each observable.
+    As a final result, the arithmetic mean of these values is presented.
+    Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_sus}\subref{sfig:gettingCrit:collapse_s_1_sus}
+    show an examplary collapse for \(\sigma=1\) of the magnetic susceptibility
     \begin{equation}
@@
     This way the exponents \(\gamma\) and \(\nu\) are determined.
-    Analogically Fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
+    Similarly Fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}
     show the collapse for the mean magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\)
@@
     in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0},
-    is used to get a further value of \(\nu\).
+    is used to get a further estimate of \(\nu\).
     \begin{figure}[htbp]
@@
         {
-            Examples for the method of finite size scaling, which was used
+            Examples for the method of FSS, which was used
             to determine the critical exponents \(\nu, \gamma, \beta\) and
@@
             \subref{sfig:gettingCrit:s_1_sus} The susceptibility \(\chi\)
-                of an Ising model on an RNG \(\sigma=1\)\\
-            \subref{sfig:gettingCrit:collapse_s_1_sus} collapsed by finite
-                size scaling, to determine \(\gamma\) (for error estimates see Tab.\ \ref{tab:critExp}).\\
+                of an Ising model on an RNG at \(\sigma=1\).\\
+            \subref{sfig:gettingCrit:collapse_s_1_sus} data collapse, to determine \(\gamma\) (for error estimates see Tab.\ \ref{tab:critExp}).\\
             \subref{sfig:gettingCrit:s_1_meanM} The mean magnetization \(\avg{\abs{m}}\)
-                of an Ising model on an GG \(\sigma=1\)\\
-            \subref{sfig:gettingCrit:collapse_s_1_meanM} collapsed by finite
-                size scaling, to determine \(\beta\) (for error estimates see Tab.\ \ref{tab:critExp}).
+                of an Ising model on an GG at \(\sigma=1\).\\
+            \subref{sfig:gettingCrit:collapse_s_1_meanM} data collapse, to determine \(\beta\) (for error estimates see Tab.\ \ref{tab:critExp}).
         }
@@
     \end{figure}\\
-    The values for
-    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
+    The values for \(\sigma = 0\), i.e.\ the critical temperature and
+    critical exponents for the square lattice Ising model,
+    are analytically known \cite{Pelissetto2002}. Due to universality, the
     values for all other \(\sigma\) are expected be the same as for
@@
     expectations match. Hence 5 values of \(\sigma\) are analyzed.
-    The analytically known values for \(\sigma = 0\) and the in \cite{Janke1994}
-    examined limit of a random lattice \(\sigma \gtrsim 1\) are natural
-    choices.
+    The analytically known values for \(\sigma = 0\) and the
+    limit of a random lattice \(\sigma \gtrsim 1\), examined in
+    Ref.\ \cite{Janke1994}, are natural choices.
     The other \(\sigma\) are chosen to represent regions where the behavior of
-    \(T_c\) shows some characteristics. (Namely there is a plateau at small
-    \(\sigma\), a steep decline at medium \(\sigma\) and a shallow
+    \(T_c\) shows some characteristics. (As we will see later, there is a plateau at small
+    \(\sigma\), a steep decline at intermediate values of \(\sigma\) and a shallow
     decline at \(\sigma = 0.5\). This will be shown in the next
     chapter in Fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
+    The range \(\Delta x\) which specifies the mesurements used for the
+    data collapse, was restricted to the in Tab.\ \ref{tab:FSS_range}
+    listed ranges.
+    \begin{table}[htbp]
+        \center
+        \begin{tabular}{l l l@{, }r}
+            \toprule
+                                & \multicolumn{1}{c}{\(\sigma\) }   & \multicolumn{2}{c}{\(\Delta x\)}\\
+            \midrule
+            \(\avg{\abs{m}}\)   & \(0.0, 0.1\)                      & \([-2.5\) & \( 7]\)\\
+                                & \(0.2, ,0.3, 0.5, 1.0\)           & \([-1.5\) & \(10]\)\\
+            \(\chi\)            & \(0.0, 0.1\)                      & \([-2.0\) & \( 7]\)\\
+                                & \(0.2, ,0.3, 0.5, 1.0\)           & \([-1.5\) & \( 7]\)\\
+            \(g\)               & \(0.0, 0.1\)                      & \([-3.5\) & \(12]\)\\
+                                & \(0.2, ,0.3, 0.5, 1.0\)           & \([-1.5\) & \(10]\)\\
+            \bottomrule
+        \end{tabular}
+        \caption[Ranges of the Data Collapse]{
+            The range \(\Delta x\) specifies the mesurements used for the
+            data collapse.
+        }
+        \label{tab:FSS_range}
+    \end{table}\\
     The determined values are displayed in Tab.\ \ref{tab:critExp}.
@@
         \caption[Critical Exponents for Different $\sigma$]{
-            Critical exponents for different $\sigma$. A finite size
+            Critical exponents for different values of \(\sigma\). A finite size
             scaling analysis was performed to determine the critical
             exponents \(\beta, \gamma, \nu\) and the critical temperature
-            \(T_c\). The errors for \(beta\) and \(\gamma\) are estimates
+            \(T_c\). The errors for \(\beta\) and \(\gamma\) are estimated
             by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
             \(\nu\) and \(T_c\) are the standard deviation of three obtained
-            values through different collapses.
+            values through different collapses (see text).
         }
@@
     are always in very good agreement with their exact values. Besides the
-    good agreement of the by data collapse obtained values of \(\nu\) and \(\gamma\),
+    good agreement of the values of \(\nu\) and \(\gamma\) obtained by data collapse,
     the ratio \(\frac{\gamma}{\nu}\) is also determined by fitting the maxima of
-    the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
+    the susceptibility \(\chi_{\mathrm{max}}\) to the power law function \(aL^\frac{\gamma}{\nu}\).
     Because there were many measurements in the vicinity of \(T_c\)
@@
         {
-            Cross checking the ratio critical exponents $\gamma$ and $\nu$ for
+            Cross checking the ratio of the critical exponents $\gamma$ and $\nu$ for
                 \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
@@
     And in Tab.\ \ref{tab:critTemp} the values are displayed together with the
-    values obtained by the data collapse from the section before.
+    values obtained by the data collapse from the previous section.
     \begin{table}[htbp]
@@
             Interesting points are the jump and rise of the GG at small
-            \(\sigma\). And the plateau on the RNG for small \(\sigma\).
+            \(\sigma\) and the plateau on the RNG for small \(\sigma\).
         }
@@
     distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
-    \(\sigma \gg 1\). Regarding this both meet the expectations.\\
+    \(\sigma \gg 1\). Regarding this both graph types meet the expectations.\\
     Another strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
@@
     consider the influence of the graph properties on the critical
-    temperature.\\
-    One basic property of a graph is its degree \(K\) -- sometimes
-    called \emph{coordination number}. \(K\) is defined as the mean count
+    temperature.
+    \subsubsection{Influence of the Average Degree on the Critical Temperature}
+        One basic property of a graph is its average degree \(K\) -- sometimes
+        called average \emph{coordination number}. \(K\) is defined as the mean count
         of neighbors per node.
         \begin{equation}
-        K = \frac{1}{N} \sum_{\avg{i,j}} 1
+            K = \frac{1}{N} \sum_{\avg{i,j}} 1.
             \label{eq:degree}
         \end{equation}
-    It is known that the degree has an impact on the critical temperature.
-    For example the Honeycomb lattice is of degree \(K=3\)
-    and there exists an analytic solution \cite{Wannier1945}.
-    Its critical temperature is determined by Eq.\ \eqref{eq:exactHCTc}:
+        It is well known that the degree has an impact on the critical temperature.
+        For example the Honeycomb lattice is of degree \(K=3\) and the
+        respective critical temperature can be obtained by analytic means \cite{Wannier1945},
+        yielding
         \begin{equation}
-        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
+            \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52.
             \label{eq:exactHCTc}
         \end{equation}
-    This is lower than for the square lattice with degree 4.\\
-    This is plausible, because more edges lead to more neighbors. The energy
-    which is necessary to flip a spin down while the spins of its neighbors are up,
-    gets higher with the number of neighbors. So the more edges are in
-    the graph the more stable the system becomes and \(T_c\) is higher.
+        Note that this is lower than the critical temperature \(T_c = 2.269...\)
+        characteristic for the square lattice with degree \(K=4\).\\
+        This is plausible, because more edges lead to more neighbors.
+        Consider, e.g., a fully polarized spin configuration. Now, the
+        energy needed to flip a spin so that it assumes an orientation opposite
+        to the orientation of its neighbors increases with the number of
+        its neighbors. So the more edges are in
+        the graph the more stable the system becomes with respect to spin flips
+        at low \(T\), leading to an increasing value of \(T_c\).
         This is also an explanation why the \(T_c\) of the RNG is always
-    lower than that of the GG: The degree of the \(T_c\) is lower.\\
+        lower than that of the GG: The degree of the RNG is lower.\\
         If one plots the degree of the graphs at different \(\sigma\) like
@@
         realizations of each graph type for \(L=16\) and \(L=32\) lattices.
-    Note that \(K\) is independent of \(L\) because of the periodic boundary.
+        %~ Note that \(K\) is independent of \(L\) because of the periodic boundary.
         In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
@@
         Indeed the normalization eliminates the jump and reduces the
-    slope of the rising on the GG. Hence it reduces differences
-    between the RNG and the GG. But the elimination of the jump is
-    unfortunately random and probably caused by a lucky choice of the
+        slope of the \(T_c\) curve for the GG. Hence it reduces differences
+        between the RNG and the GG. However the elimination of the jump is
+        unfortunately a coincidence and probably caused by a lucky choice of the
         function, which determines the coupling constants \(J\). As proof for
@@
         the critical temperature \(T_c\), but it is not a trivial one.
+        Note that even after the normalization, the values of \(T_c / K\)
+        for the RNG are smaller than those for the GG.
         \begin{figure}[htbp]
@@
         understand the jump of \(K\), which is easily explained
-    by the definition of the GG and its aftereffects for
-    the transition from \(\sigma = 0\). Visible in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
+        by the definition of the GG. As evident from Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
         a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
         To fully understand this, take four nodes forming a square. The edge
-    across does not exist, because the other two nodes are on the border
+        across the diagonal of the plaquette does not exist, because the
+        other two nodes are located exactly on the border
         of the lune. Moving one node slightly into the square, causes the lune
         to get smaller, hence no other nodes are inside or on the border of
-    the lune anymore and the edge appears. This process is sketched in
+        the lune anymore and the new diagonal edge appears. This process is sketched in
         Fig.\ \ref{fig:GGEdge}.
@@
         \end{figure}\\
-    Further the increase of \(T_c\) on the GG can be made plausible.
-    %~ Though it is not removed by the normalization, it is reduced.
-    Also the maximum of the \(K\) is at the same \(\sigma\), as the maximum
-    of \(T_c\). So while displacing the nodes, there arise more edges
+        Further, the increase of \(T_c\) on the GG can be made plausible.
+        Also, the maximum value of \(K\) and the minimum value of \(T_c\)
+        are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
         than edges are vanishing until \(\sigma \approx 0.15\) is reached.
@@
             {
-            GG with periodic boundary conditions for different \(\sigma = 0\).
+                GG with periodic boundary conditions for different \(\sigma\).
                 The number of edges increases from \subref{sfig:GG_sigma:0.00}
@@
         shows that for \(\sigma \lesssim 0.1\) the square lattice character is
-    preserved -- no new edges arise neither many existing edges vanish, which
+        preserved -- no new edges arise and only a few existing edges vanish, which
         explains the plateau in the \(T_{c}\) diagram. With
         increasing \(\sigma\), more and more edges vanish\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.},
-    thus reducing the degree and \(T_{c}\).
+        thus reducing the degree and consequently the corresponding value of \(T_{c}\).
         \begin{figure}[htbp]
@@
             {
-            RNG with periodic boundary conditions for different \(\sigma = 0\).
+                RNG with periodic boundary conditions for different \(\sigma\).
                 \subref{sfig:RNG_sigma:0.09} has still almost the square lattice
@@
                 exists. In the next two pictures one sees the fast disappearance
-            of edges.
+                of edges, chracteristic for the RNG for a set of randomly
+                distributed points (i.e.\ Poisson process).
             }
@@
         \end{figure}\\
-    But the degree does not alone influence the behavior of \(T_c\).
+    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}
+        However, note that the degree does not alone influence the behavior of \(T_c\).
         Further \(T_c\) depends on the coupling constant \(J\), which is
-    obvious in Eq.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
+        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
         coupling constant in turn is depending on the length of the edges,
@@
         Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
-    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+        the mean sum of the coupling constants to all neighbors
+        \begin{equation}
+            \avg{\sum_{\avg{i,j}} J_{ij}}
+        \end{equation}
         is plotted. This is a number which should combine the dependence on
@@
         this value over all nodes. Alternatively it is the average edge weight
-    of all edges multiplied by the degree.
+        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
         The plots Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
@@
         temperature.
-    Also both graph types have a steep decline after the plateau before
+        Also both graph types exhibit a steep decline after the plateau before
         they approach an asymptotic limit for \(\sigma \gg 1\).\\
@@
         The value of the Binder cumulant at the critical point \(g_c\)
-    depends strongly on boundary conditions but only weakly on the lattice
+        depends strongly on boundary conditions but only weakly on the precise lattice
         structure \cite{BinderValue}. For periodic boundary conditions on a
@@
                 the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
-            to match its definition in this thesis.}.
+                to match the definition in this thesis.}.
         Because the analysis of Sec.\ \ref{ssec:binderIntersections}
         yields \(g_c\) anyway, it is easy to check the consistency and
-    behavior of \(g_c\) in the disordered Ising model.\\
+        behavior of \(g_c\) in the geometrically disordered Ising model.
+        The error bars are the standard error of the six values obtained
+        through the intersections.\\
         \begin{figure}[htbp]
@@
         by the cubic spline interpolation used to acquire these \(g_c\) values.
+        Or this are again finite size effects which would disappear for
+        larger system sizes.
         For bigger \(\sigma\) the uncertainty gets greater, but the values
@@
         definition of nearest neighbors via a proximity graph does not change
-    \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
+        the value of \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
         lattice structure has a minor effect on \(g_c\), the uncertainty of
-    \(g_c\) is too big, to show it. For a more exact analysis, new
+        \(g_c\) is too large to observe this. For a more exact analysis, new
         Monte Carlo simulations at \(T_c\) would be needed. But this is
@@
         behavior, because no major deviations from the value of \(g_c\) at
-    \(\sigma = 0\) occur at larger \(\sigma\).
+        \(\sigma = 0\) occur at larger \(\sigma\). Within error bars the
+        values are all in reasonable agreement with \(g_c\).

### 2013-09-04 Tex/chapters/appendix.tex
Fehlerbehehungen und Ergänzungen
Analytische Abschätzung für kleine sigma

@@
     is plotted for different system sizes. The finite size effects are obvious.
-    The divergence is finite and gets shallower with smaller \(L\). Besides
-    the maximum moves away from the critical temperature with smaller \(L\).
+    The divergence is finite and gets steeper with larger \(L\). Besides
+    the maximum moves to the critical temperature with larger \(L\).
     \begin{figure}[htbp]
@@
     for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
-    Every other parameter was kept. Also note that the degree \(K\) is
+    Also note that the degree \(K\) is
     the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
     because it is obviously independent of \(J\).
+    Further, note that for small values of \(\sigma < 0.3\), \(T_c / K\)
+    obtained using the fixed coupling strength \(J=1\) coincides with
+    \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
+    dependent coupling strength, Eq.\ \ref{eq:coupling}.
+    This can be expected from the approximate analytic statement presented
+    in Sec.\ \ref{sssec:J}.
     \begin{figure}[htbp]
@@
             \subref{sfig:Tc_norm_deg:RNG} the RNG and
-            \subref{sfig:Tc_norm_deg:GG} the GG.
+            \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
+            are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
+            from Sec.\ \ref{sssec:J}.
         }

### 2013-09-04 Tex/chapters/results.tex
Analytische Abschätzung für kleine sigma

@@
             \label{fig:RNG_sigma}
-        \end{figure}\\
+        \end{figure}
+
     \subsubsection{Influence of the Coupling Constant on the Critical Temperature}
+    \label{sssec:J}
         However, note that the degree does not alone influence the behavior of \(T_c\).
@@
         they approach an asymptotic limit for \(\sigma \gg 1\).\\
+        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\) the
+        following approximation is valid.
+        \begin{equation}
+            \abs{1-d_{ij}} := \varepsilon \ll 1
+        \end{equation}
+        \begin{equation}
+            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
+        \end{equation}
+        \begin{align}
+            \avg{\sum_{\avg{i,j}} J_{ij}} &= \frac{\pm \varepsilon}{N} \avg{\sum_{\avg{i,j}} 1} \\
+                                          &= K(1 \pm \varepsilon) \approx K
+        \end{align}
+        Therefore this normalization is independent of the choice of \(\alpha\)
+        at small values of \(\sigma\). In Appendix \ref{appendix:fixedCoupling}
+        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
+        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
+        are compared to \(T / K\) for \(\alpha = 0\).
 

### 2013-09-04 Tex/chapters/appendix.tex
Kapitel aus Anhang nach vorne verschoben

--- 2013-09-03 Tex/chapters/appendix.tex
@@
     \end{figure}
-
-\subsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
-\label{appendix:fixedCoupling}
-    A quick analysis of this model with fixed coupling constants \(J = 1\)
-    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
-    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
-    for variable \(J\) with \(\alpha=0.5\). This suggests that the
-    disappearance of the jump is a random special case for the function
-    \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
-    The simulations were carried out on \(L \in \{16,32,64\}\) lattices
-    for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
-    Every other parameter was kept. Also note that the degree \(K\) is
-    the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
-    because it is obviously independent of \(J\).
-    \begin{figure}[htbp]
-        \centering
-        \subfigure[][]
-        {
-            \label{sfig:Tc:RNG_A0}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
-        }
-        \subfigure[][]
-        {
-            \label{sfig:Tc:GG_A0}
-            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
-        }
-
-        \subfigure[][]
-        {
-            \label{sfig:Tc_norm_deg:RNG_A0}
-            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_A0}
-        }
-        \subfigure[][]
-        {
-            \label{sfig:Tc_norm_deg:GG_A0}
-            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_A0}
-        }
-
-        \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
-        {
-            Top: Critical Temperature \(T_c\) of the graph over different
-            disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
-            \subref{sfig:deg:RNG} the RNG and
-            \subref{sfig:deg:GG} the GG.\\
-            Bottom: Critical temperatures normalized by degree \(K\) over
-            different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
-            \subref{sfig:Tc_norm_deg:RNG} the RNG and
-            \subref{sfig:Tc_norm_deg:GG} the GG.
-        }
-        \label{fig:Tc_deg_A0}
-    \end{figure}\\

### 2013-09-04 Tex/chapters/results.tex
Einrückungsfehler behoben
Kapitel aus Anhang nach vorne verschoben

@@
         function, which determines the coupling constants \(J\). As proof for
-        this claim in appendix \ref{appendix:fixedCoupling} the same analysis
+        this claim in Sec.\ \ref{appendix:fixedCoupling} the same analysis
         is performed for a model with fixed \(J\). There the jump gets narrower
@@
         Therefore this normalization is independent of the choice of \(\alpha\)
-        at small values of \(\sigma\). In Appendix \ref{appendix:fixedCoupling}
+        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
         in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
@@
         are compared to \(T / K\) for \(\alpha = 0\).
+
+    \subsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
+    \label{appendix:fixedCoupling}
+        A quick analysis of this model with fixed coupling constants \(J = 1\)
+        (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
+        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
+        for variable \(J\) with \(\alpha=0.5\). This suggests that the
+        disappearance of the jump is a random special case for the function
+        \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
+        The simulations were carried out on \(L \in \{16,32,64\}\) lattices
+        for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
+        Also note that the degree \(K\) is
+        the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
+        because it is obviously independent of \(J\).
+        Further, note that for small values of \(\sigma < 0.3\), \(T_c / K\)
+        obtained using the fixed coupling strength \(J=1\) coincides with
+        \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
+        dependent coupling strength, Eq.\ \ref{eq:coupling}.
+        This can be expected from the approximate analytic statement presented
+        in Sec.\ \ref{sssec:J}.
+        \begin{figure}[htbp]
+            \centering
+            \subfigure[][]
+            {
+                \label{sfig:Tc:RNG_A0}
+                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
+            }
+            \subfigure[][]
+            {
+                \label{sfig:Tc:GG_A0}
+                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
+            }
+
+            \subfigure[][]
+            {
+                \label{sfig:Tc_norm_deg:RNG_A0}
+                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_A0}
+            }
+            \subfigure[][]
+            {
+                \label{sfig:Tc_norm_deg:GG_A0}
+                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_A0}
+            }
+
+            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
+            {
+                Top: Critical Temperature \(T_c\) of the graph over different
+                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
+                \subref{sfig:deg:RNG} the RNG and
+                \subref{sfig:deg:GG} the GG.\\
+                Bottom: Critical temperatures normalized by degree \(K\) over
+                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
+                \subref{sfig:Tc_norm_deg:RNG} the RNG and
+                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
+                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
+                from Sec.\ \ref{sssec:J}.
+            }
+            \label{fig:Tc_deg_A0}
+        \end{figure}
 

### 2013-09-04 Tex/chapters/results.tex
Containment Theorem

@@
     One sees that the RNG on the left has generally a lower critical
-    temperature than the GG. Also \(T_c\) of the RNG decreases
+    temperature than the GG.
+    Also \(T_c\) of the RNG decreases
     monotonically while \(T_c\) of the GG rises at first. Naively one would
@@
     temperature.
+
     \subsubsection{Influence of the Average Degree on the Critical Temperature}
@@
             \label{fig:Tc_deg_A0}
-        \end{figure}
+        \end{figure}\\
+        Because Ref.\ \cite{Janke1994} gives for the DT with \(J=1\) a
+        critical temperature \(T_{c,DT} = 3.80\), the obtained \(T_{c,GG} = 2.19\)
+        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should be very
+        similar to a Poisson distributed set of nodes, can be compared.
+        Note that while for the graph ensembles as mentioned in Sec. \ref{ssec:graphtypes}
+        the relation \(DT \supseteq GG \supseteq RNG\) holds, also the
+        relation \(T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}\) holds.
+        Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)
+        was true for \(\alpha = 0.5\) in the preceding sections.
+        This phenomenon is also known from percolation where the relation
+        \(p_{c,DT} \ge p_{c,GG} \ge p_{c,RNG}\) holds for the percolation
+        threshold \(p_c\) -- the critical point of the percolation problem.
+        That the subgraph hierachy can be translated to
+        the sequence of \(p_c\) for the subgraphs, is known as the containment
+        theorem \cite{fisher}.
+        Possibly the containment theorem is also applicable on this kind of
+        problem.
 

### 2013-09-04 Tex/chapters/results.tex
Ergänzung zu Delta x

@@
         \caption[Ranges of the Data Collapse]{
-            The range \(\Delta x\) specifies the mesurements used for the
-            data collapse.
+            The range \(\Delta x\) specifies a range on the \(x\)-axis of
+            the plots after the collapse. Values inside this range are
+            considered to judge the quality of the collapse. I.e.\ only
+            the data points inside this range have to collapse on each
+            other -- data points beyond do not have to. This accounts
+            for the fact, that FSS is only near the critical point a good
+            approximation.
         }

### 2013-09-05 Tex/chapters/results.tex
Fehlerabhängigkeit von tau klarer formuliert

@@
     In this thesis the number of bootstrap samples is \(k = 200\).\\
-    Note that while the error of \(\avg{O}\), \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
-    \(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
-    over different realizations of the random proximity graph, which are
-    surely uncorrelated.
+    Note that the error of \(\avg{O}\), which is the standard error\footnote{for the arthmetic mean: standard deviation divided by \(\sqrt M\), where \(M\) is the number of samples}
+    of different states on one instance of a proximity graph \(\Delta \avg{O}\),
+    is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}.
+    However \(\Delta \overline{\avg{O}}\), which is the the error of the
+    observable averaged over different instances of the proximity graphs,
+    is not dependend on \(\tau\), because different realizations of the
+    random proximity graph are surely uncorrelated.
     Because every error mentioned in this thesis is of this type, it is not

### 2013-09-05 Tex/chapters/results.tex
avg Degree hinzugefügt

@@
     \subsubsection{Influence of the Average Degree on the Critical Temperature}
-        One basic property of a graph is its average degree \(K\) -- sometimes
+        One basic property of a graph is its average \emph{degree} \(K\) -- sometimes
         called average \emph{coordination number}. \(K\) is defined as the mean count
@@
         \end{equation}
+        For a Poisson point process, i.e.\ for \(\sigma \gtrsim 1\),
+        the average degree of the mentioned graph types are known.
+        \(K_{DT} = 6\) \cite{DelaunayDegree}, \(K_{DT} = 4\) \cite{notPChristoph} and \(K_{RNG} = 2.5576(3)\) \cite{RNGCell}.
+        Indeed, for \(\sigma \gtrsim 1\) Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:GG}\subref{sfig:deg:RNG}
+        confirm the last two values.\\
         It is well known that the degree has an impact on the critical temperature.

### 2013-09-05 Tex/chapters/results.tex
Rechenfehler behoben
Detailverbesserungen

@@
     the system will show a steep decline to zero and the susceptibility
-    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
+    \begin{equation}
+        \chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}
+    \end{equation}
     will diverge. In Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
@@
         \center
-        \begin{tabular}{l l l@{, }r}
+        \begin{tabular}{c l l@{, }r}
             \toprule
-                                & \multicolumn{1}{c}{\(\sigma\) }   & \multicolumn{2}{c}{\(\Delta x\)}\\
+            collapsed observable & \multicolumn{1}{c}{\(\sigma\) }   & \multicolumn{2}{c}{\(\Delta x\)}\\
             \midrule
             \(\avg{\abs{m}}\)    & \(0.0, 0.1\)                      & \([-2.5\) & \( 7]\)\\
-                                & \(0.2, ,0.3, 0.5, 1.0\)           & \([-1.5\) & \(10]\)\\
+                                 & \(0.2, 0.3, 0.5, 1.0\)           & \([-1.5\) & \(10]\)\\
             \(\chi\)             & \(0.0, 0.1\)                      & \([-2.0\) & \( 7]\)\\
-                                & \(0.2, ,0.3, 0.5, 1.0\)           & \([-1.5\) & \( 7]\)\\
+                                 & \(0.2, 0.3, 0.5, 1.0\)           & \([-1.5\) & \( 7]\)\\
             \(g\)                & \(0.0, 0.1\)                      & \([-3.5\) & \(12]\)\\
-                                & \(0.2, ,0.3, 0.5, 1.0\)           & \([-1.5\) & \(10]\)\\
+                                 & \(0.2, 0.3, 0.5, 1.0\)           & \([-1.5\) & \(10]\)\\
             \bottomrule
@@
 
+        \clearpage
+
     \subsubsection{Influence of the Coupling Constant on the Critical Temperature}
@@
         \begin{align}
-            \avg{\sum_{\avg{i,j}} J_{ij}} &= \frac{\pm \varepsilon}{N} \avg{\sum_{\avg{i,j}} 1} \\
+            \avg{\sum_{\avg{i,j}} J_{ij}} &= \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
+                                          &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
                                           &= K(1 \pm \varepsilon) \approx K
@@
         Because Ref.\ \cite{Janke1994} gives for the DT with \(J=1\) a
-        critical temperature \(T_{c,DT} = 3.80\), the obtained \(T_{c,GG} = 2.19\)
+        critical temperature of \(T_{c,DT} = 3.80\)\footnote{more precise: a value of \(\frac{1}{T_c} \approx 0.263\) is given},
+        it can be compared to the obtained \(T_{c,GG} = 2.19\)
         and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should be very
-        similar to a Poisson distributed set of nodes, can be compared.
+        similar to a Poisson distributed set of nodes.
         Note that while for the graph ensembles as mentioned in Sec. \ref{ssec:graphtypes}
-        the relation \(DT \supseteq GG \supseteq RNG\) holds, also the
-        relation \(T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}\) holds.
+        the relation
+        \begin{equation}
+            DT \supseteq GG \supseteq RNG
+        \end{equation}
+        holds, also the
+        relation
+        \begin{equation}
+            T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}
+        \end{equation}
+        holds.
         Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)

### 2013-09-05 Tex/chapters/model.tex
Fehlerbehehungen und Ergänzungen
Analytische Abschätzung für kleine sigma
Figure captions angepasst

@@
     already studied on a Delaunay triangulation. Ref.\ \cite{Janke1994} examines
-    this for constant \(J\) and Ref.\ \cite{Lima2000} for \(J_{ij} = e^{-\alpha d_{ij}}\).
+    this for constant \(J\) and Ref.\ \cite{Lima2000} for
+    \begin{equation}
+        J_{ij} = e^{-\alpha d_{ij}}.
+        \label{eq:coupling}
+    \end{equation}
     Both articles conclude that this model lies within the universality
@@
                 The bounding box of the lune which determines which cells have
-                to be tested, is marked with thick colored lines.\\
+                to be tested, is marked with thick colored lines.
                 \subref{sfig:cell:big} shows that it is sufficient to find a
@@
                 the edge between two distant nodes. The nodes inside the
-                other 8 marked cells do not have to be tested anymore.\\
+                other 8 marked cells do not have to be tested anymore.
                 \subref{sfig:cell:small} shows that only the nodes inside the

### 2013-09-05 Tex/chapters/results.tex
Figure captions angepasst

@@
     source plotting program used for all plots and fits in this thesis.
+    Also note that dotted lines in the plots are -- if not noted otherwise --
+    cubic spline interpolations purely meant to be guides to the eye.
 
@@
             \subref{fig:autocorr:powerLaw} the system size $L$. Plotted on
-                double logarithmic axis with a power law fit \(\tau \propto L^z\)
+                double logarithmic axis with a power law fit \(\tau \propto L^z\) (dotted line)
                 to determine the dynamical exponent \(z'\).
@@
             and hence the critical temperature, moves to lower temperatures
-            with increasing \(\sigma\) (\(0.0 \le \sigma \le 1.2\))\\
+            with increasing \(\sigma\) (\(0.0 \le \sigma \le 1.2\))
             \subref{sfig:smeared_out:meanM} Effects of different system
             sizes at \(\sigma = 0\), i.e.\ the square lattice Ising ferromagnet.
-            Dotted lines are guides to the eye.
             The \(L=16\) curve is much less steep than the \(L=128\) curve.
@@
             \subref{sfig:gettingCrit:binder_s_0} The Binder cumulant \(g\)
-                of an square lattice Ising model (\(\sigma=0\)).\\
+                of an square lattice Ising model (\(\sigma=0\)).
             \subref{sfig:gettingCrit:collapse_s_0} The curve from \subref{sfig:gettingCrit:binder_s_0}
@@
             to determine the critical exponents \(\nu, \gamma, \beta\) and
-            the critical temperature \(T_c\).\\
+            the critical temperature \(T_c\).
             \subref{sfig:gettingCrit:s_1_sus} The susceptibility \(\chi\)
-                of an Ising model on an RNG at \(\sigma=1\).\\
-            \subref{sfig:gettingCrit:collapse_s_1_sus} data collapse, to determine \(\gamma\) (for error estimates see Tab.\ \ref{tab:critExp}).\\
+                of an Ising model on an RNG at \(\sigma=1\).
+            \subref{sfig:gettingCrit:collapse_s_1_sus} data collapse, to determine \(\gamma\) (for error estimates see Tab.\ \ref{tab:critExp}).
             \subref{sfig:gettingCrit:s_1_meanM} The mean magnetization \(\avg{\abs{m}}\)
-                of an Ising model on an GG at \(\sigma=1\).\\
+                of an Ising model on an GG at \(\sigma=1\).
             \subref{sfig:gettingCrit:collapse_s_1_meanM} data collapse, to determine \(\beta\) (for error estimates see Tab.\ \ref{tab:critExp}).
@@
             The plotted values are the maxima of all measured \(\chi\).
-            Dotted lines are power law fits \(aL^\frac{\gamma}{\nu}\).
+            Dotted lines are fits to the power law function \(aL^\frac{\gamma}{\nu}\).
         }
@@
             the intersection, which is at \(T_c\)
-            (the errorbars are too small to see).\\
+            (the errorbars are too small to see).
         }
@@
             \subref{sfig:Tc:RNG} the RNG and
-            \subref{sfig:Tc:GG} the GG.\\
+            \subref{sfig:Tc:GG} the GG.
             Interesting points are the jump and rise of the GG at small
@@
                 \subref{sfig:deg:RNG} the RNG and
-                \subref{sfig:deg:GG} the GG.\\
+                \subref{sfig:deg:GG} the GG.
                 Bottom: Critical temperatures normalized by degree over different
@@
                 \subref{sfig:sumJ:RNG} the RNG and
-                \subref{sfig:sumJ:GG} the GG.\\
+                \subref{sfig:sumJ:GG} the GG.
                 Bottom: Critical temperatures normalized by mean sum of the
@@
         in Sec.\ \ref{sssec:J}.
-        \begin{figure}[htbp]
+        \begin{figure}[htb]
             \centering
@@
                 \subref{sfig:deg:RNG} the RNG and
-                \subref{sfig:deg:GG} the GG.\\
+                \subref{sfig:deg:GG} the GG.
                 Bottom: Critical temperatures normalized by degree \(K\) over
@@
             Values of the Binder cumulant at the critical point \(g_c\)
-            for\\
-            \subref{sfig:TcG:RNG} a RNG and\\
+            for
+            \subref{sfig:TcG:RNG} a RNG and
             \subref{sfig:TcG:GG} a GG for different \(\sigma\).

### 2013-09-05 Tex/chapters/results.tex
Formulierung hoffentlich klarer

@@
         similar to a Poisson distributed set of nodes.
-        Note that while for the graph ensembles as mentioned in Sec. \ref{ssec:graphtypes}
-        the relation
+        Note that while for the graph ensembles the relation
         \begin{equation}
@@
         \end{equation}
-        holds, also the
-        relation
+        holds (see Sec. \ref{ssec:graphtypes}), the relation for the
+        critical points on these graphs
         \begin{equation}
@@
         \end{equation}
-        holds.
+        is also true.
         Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)
@@
         threshold \(p_c\) -- the critical point of the percolation problem.
-        That the subgraph hierachy can be translated to
+        The fact that the subgraph hierachy can be translated to
         the sequence of \(p_c\) for the subgraphs, is known as the containment

### 2013-09-05 Tex/chapters/model.tex
Erläuterung warum GG > RNG

@@
             \subref{sfig:lunes:def} Lunes, which define where an edge
-                exist, of RNG (hatched region) and GG (cross hatched region)
+                exist, of RNG (hatched region) and GG (cross hatched region).
+                It is evident from this sketch that the GG is a supergraph
+                of the RNG. If there is an edge in the RNG, the hatched
+                region contains no node, the of course also the double
+                hatched region contains no node and thus this edge appears
+                also in the GG. So every egde of the RNG is also present
+                in a GG on the same node set.
             \subref{sfig:lunes:rng} Example of a RNG on periodic

### 2013-09-05 Tex/chapters/results.tex
Tippfehler
subsec to subsubsec korrigiert

@@
         the average degree of the mentioned graph types are known.
-        \(K_{DT} = 6\) \cite{DelaunayDegree}, \(K_{DT} = 4\) \cite{notPChristoph} and \(K_{RNG} = 2.5576(3)\) \cite{RNGCell}.
+        \(K_{DT} = 6\) \cite{DelaunayDegree}, \(K_{GG} = 4\) \cite{notPChristoph} and \(K_{RNG} = 2.5576(3)\) \cite{RNGCell}.
         Indeed, for \(\sigma \gtrsim 1\) Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:GG}\subref{sfig:deg:RNG}
@@
 
-    \subsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
+    \subsubsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
     \label{appendix:fixedCoupling}

### 2013-09-05 Tex/chapters/results.tex
Kontinuität in den Überschriften
polarisierte spin cfg. beschrieben

@@
 
-\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
+\subsection{Short Analysis of the Autocorrelation Time}
 \label{ssec:results:autocorr}
@@
         This is plausible, because more edges lead to more neighbors.
-        Consider, e.g., a fully polarized spin configuration. Now, the
-        energy needed to flip a spin so that it assumes an orientation opposite
-        to the orientation of its neighbors increases with the number of
-        its neighbors. So the more edges are in
+        Consider, e.g.\ a fully polarized spin configuration, e.g.\ all
+        spins are pointing up. Now, the energy needed to flip a spin so
+        that it assumes an orientation opposite to the orientation of its
+        neighbors increases with the number of its neighbors. So the more edges are in
         the graph the more stable the system becomes with respect to spin flips
@@
 
-    \subsubsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
+    \subsubsection{Course of the Critical Temperature with Fixed Coupling Constants}
     \label{appendix:fixedCoupling}

### 2013-09-05 Tex/chapters/introduction.tex
Kurze definition von ad-hoc Netzwerk

@@
 Carlo simulations described in Sec.\ \ref{ssec:montecarlo}.\\
-Proximity graphs establish a lattice by connecting sites which are "near"
-to each other. The exact definition of "near" is dependend on the proximity
-graph.\\
+Proximity graphs are canditates for ad-hoc networks. As an example of an
+Ad-hoc network take a wifi network without central devices, but the every
+participant (e.g.\ a laptop) works as a relay to get a data package to its
+destination. To minimize the needed energy the packages will be routed
+over small distances from one node to another. This behavior is well mapped
+by proximity graphs. They establish a lattice by connecting sites which
+are "near" to each other. The exact definition of "near" is dependend on
+the proximity graph.\\
 Because the Ising model on a regular square lattice is well understood,

### 2013-09-05 Tex/chapters/appendix.tex
ref repariert
Kleine Tipp- und Formulierungsfehler behoben

@@
         \input{images/DT_def}
-        \label{sfig:def:DT}
+        \label{fig:def:DT}
         \caption[Example for a Small Delaunay Triangulation]
         {
-            Circles, which contain nodes are dashed.
-            Circles, which contain no nodes are not dashed.
+            Circles which contain nodes are dashed.
+            Circles which contain no nodes are not dashed.
             Consequently nodes on the border of not dashed circles are
             connected. Note that the drawn cricles are only examples
-            as there there is an infinitive number of alternative not
-            dashed circles, which contain no other node.
+            as there is an infinitive number of alternative not
+            dashed circles which contain no other node.
             Note also that in contrast to the GG the circles do not
             have to be centered on the middle point between the nodes, if
-            however, the centered circle does not contain any node, the
+            however the centered circle does not contain any node, the
             resulting edge will be present in DT and GG. Therefore GG is

### 2013-09-05 Tex/chapters/conclusion.tex
Kleine Tipp- und Formulierungsfehler behoben

@@
 ferromagnet. Its critical temperature decreases with increasing disorder
-on a RNG. Since effectively, the decreasing avergae coordination number
-of the underlying graphs lowers the resistance to spin flips within
+on a RNG. Since effectively, the decreasing average coordination number
+of the underlying graph lowers the resistance to spin flips within
 strongly polarized configurations at low temperatures.

### 2013-09-05 Tex/chapters/introduction.tex
Kleine Tipp- und Formulierungsfehler behoben

@@
 Proximity graphs are canditates for ad-hoc networks. As an example of an
-Ad-hoc network take a wifi network without central devices, but the every
+ad-hoc network take a wifi network without central devices, but the every
 participant (e.g.\ a laptop) works as a relay to get a data package to its

### 2013-09-05 Tex/chapters/model.tex
Kleine Tipp- und Formulierungsfehler behoben

@@
         any other node in its interior, see Ref.\ \cite{Katajainen}.
-        To make this clear a the construction of a four node DT is sketched
-        in Fig.\ \ref{fig:def:DT} in the appendix Sec. \ref{appendix:DT_def}.
+        To make this clear the construction of a four node DT is sketched
+        in Fig.\ \ref{fig:def:DT} in the appendix Sec.\ \ref{appendix:DT_def}.
 
@@
                 of the RNG. If there is an edge in the RNG, the hatched
-                region contains no node, the of course also the double
+                region contains no node, then of course also the double
                 hatched region contains no node and thus this edge appears
                 also in the GG. So every egde of the RNG is also present
-                in a GG on the same node set.
+                in a GG on the same set of nodes.
             \subref{sfig:lunes:rng} Example of a RNG on periodic
@@
         inside like presented in Ref.\ \cite{RNGCell} and sketched in Fig.\ \ref{fig:cell}.
-        The implementation of this thesis uses \(M=N\).
+        The implementation of this thesis uses \(M = N\) (\(L_c = L\)).
         \begin{figure}[htbp]
@@
         far away from each other and there will be one or more cells in the
-        middle of the bounding box, which are completely inside the lune so.
+        middle of the bounding box, which are completely inside the lune.
         Then only one node has to be tested from such a cell to discard an

### 2013-09-05 Tex/chapters/results.tex
Kleine Tipp- und Formulierungsfehler behoben

@@
     \cite{Bootstrap}.\\
-    The bootstrapping method estimates the error \(\Delta \overline{\avg{O}}\)
+    The bootstrap method estimates the error \(\Delta \overline{\avg{O}}\)
     by taking \(M\) random samples from the \(M\) measured values of \(O\),
@@
     rather small value of \(L\) for which deviations from the assumed
-    scaling behavior might be expected. I.e.\ Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
+    scaling behavior might be expected, i.e.\ Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
     are approximations for big \(L\). For small \(L\) one needs some
@@
         thus reducing the degree and consequently the corresponding value of \(T_{c}\).
-        \begin{figure}[htbp]
+        \begin{figure}[htb]
             \centering
@@
         \end{figure}
-
         \clearpage
 
-    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}
+    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
     \label{sssec:J}
@@
         show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
-        \begin{figure}[htbp]
+        \begin{figure}[hbtp]
             \centering
@@
         If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
-        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\) the
+        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\), the
         following approximation is valid.
@@
         because it is obviously independent of \(J\).
-        Further, note that for small values of \(\sigma < 0.3\), \(T_c / K\)
+        Further, note that for small values of \(\sigma\), \(T_c / K\)
         obtained using the fixed coupling strength \(J=1\) coincides with
         \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
-        dependent coupling strength, Eq.\ \ref{eq:coupling}.
+        dependent coupling strength (see Eq.\ \ref{eq:coupling}).
         This can be expected from the approximate analytic statement presented
@@
         \end{figure}\\
-        Because Ref.\ \cite{Janke1994} gives for the DT with \(J=1\) a
-        critical temperature of \(T_{c,DT} = 3.80\)\footnote{more precise: a value of \(\frac{1}{T_c} \approx 0.263\) is given},
-        it can be compared to the obtained \(T_{c,GG} = 2.19\)
-        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should be very
-        similar to a Poisson distributed set of nodes.
+        Ref.\ \cite{Janke1994} gives a critical temperature for the DT with \(J=1\)
+        \(T_{c,DT} = 3.80\)\footnote{more precise: a value of \(\frac{1}{T_c} \approx 0.263\) is given}.
+        It can be compared to the obtained \(T_{c,GG} = 2.19\)
+        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should
+        ensure a set of nodes very similar to a Poisson process.
         Note that while for the graph ensembles the relation

### 2013-09-06 Tex/chapters/introduction.tex
etwas mehr zu 2ter Ordnung Phasenübergang

@@
 A \emph{second order} phase transition is characterized by a continuous
-transition without discontinuities of the order parameter.\\
+transition without discontinuities of the order parameter but a discontinuity
+in its first derivative.\\
 One of the simplest models with a second order phase transition is the

### 2013-09-23 Tex/chapters/introduction.tex
Verbesserungsvorschläge umgesetzt

@@
 change of an observable, e.g., the change of the density of water near
-boiling, which is liquid at \(T < T_c\) and gaseous at \(T > T_c\). Or
-the change of the magnetization of a ferromagnet near the Curie temperature,
-which is ferromagnetic at \(T < T_c\) and paramagnetic at \(T > T_c\).
+boiling, which is liquid at \(T < T_c\) and gaseous at \(T > T_c\). Also
+the change of the magnetization of a ferromagnet near the Curie temperature
+is a phase transition from ferromagnetic at \(T < T_c\) to paramagnetic at \(T > T_c\).
 This can be observed by heating some refrigerator magnet by a candle --
@@
 of the system in the thermodynamic limit. These deviations are called
-\emph{finite size effects} and in Sec.\ \ref{ssec:finitesize} will be
+\emph{finite-size effects} and in Sec.\ \ref{ssec:finitesize} will be
 discussed how to manage them.\\

### 2013-09-23 Tex/chapters/methods.tex
Fehlerbehehungen und Ergänzungen
Verbesserungsvorschläge umgesetzt

@@
     condition that the system under scrutiny has reached the temperature
-    of the heat bath. This is the case, once there is no directed energy
-    exchange between them, thus the energy of the simulated system reaches
-    a steady state, where only fluctuations occur.
-    In a canonical ensemble the probability \(p_i\) of a state
-    \(i\) is distributed according to a Boltzman distribution
+    of the heat bath. This is the case, once there is only energy fluctuating
+    between them but no net energy exchange, thus the energy of the
+    simulated system reaches a steady state, where only fluctuations occur.
+    In a canonical ensemble the probability \(p_\nu\) of a state
+    \(\nu\) is distributed according to a Boltzman distribution
     \begin{equation}
-        p_i \propto e^{-\beta H_i}
+        p_\nu = \frac{1}{Z} e^{-\beta H_\nu}
     \end{equation}
@@
     \end{equation}
+    Where \(Z\) is the partition function, which normalizes \(p_\nu\) to
+    a probability: \(\sum_\nu p_\nu = 1\).
     Further the free energy \(F\) of a canonical ensemble is minimized
@@
     \begin{equation}
-        Z = \sum_i p_i = \sum_i e^{-\beta H_i},
+        Z = \sum_\nu e^{-\beta H_\nu},
         \label{eq:partitionFunction}
@@
     \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_i O_i e^{-\beta H_i},
+        \avg{O} = \frac{1}{Z} \sum_\nu O_\nu e^{-\beta H_\nu},
     \end{equation}
     Because every site can have two states, there are \(2^N\) different
-    states of the system. For each the energy \(H_i\) has to be calculated
+    states of the system. For each the energy \(H_\nu\) has to be calculated
     to solve the sum from Eq.\ \eqref{eq:partitionFunction} to gain \(Z\).
@@
     \begin{equation}
-        O_M = \frac{1}{M} \sum_{i=1}^M O_i,
+        O_M = \frac{1}{M} \sum_{\nu=1}^M O_\nu,
     \end{equation}
@@
     approach of creating uniformly distributed random states and reject
-    them with probability \(p_i^{-1}\) depending on their energy is not
+    them with probability \(p_\nu^{-1}\) depending on their energy is not
     efficient, because many generated states will be discarded and the
@@
     \(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\) with \(p_\mu\) the
-    probability to be in state \(\mu\). This ensures that the system can
-    equilibrate and that the states are distributed according to the
-    desired distribution in equilibrium \cite{NewmanBarkema1999}.
+    probability to be in state \(\mu\).
     \emph{Ergodicity} requires that every possible state is reachable
     from every other state in finite time, see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
-    Otherwise the samples might not be representative for the whole system.\\
+    This ensures that the system can equilibrate and that the states are
+    distributed according to the desired distribution in equilibrium
+    \cite{NewmanBarkema1999}. Otherwise the samples might not be representative
+    for the whole system.\\
     In this thesis three algorithms, which fulfill all requirements,
@@
         simulation as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
-        The count of sweeps until
+        The progression of a Monte Carlo simulation is measured in \emph{sweeps},
+        which denote some operation. The count of sweeps until
         equilibrium is reached, is called \emph{equilibration time} \(t_{eq}\).
@@
                     \(L=64\) reaching thermal equilibrium at \(T=2.36\) after
-                    approximately \(n=100\) sweeps.\\
+                    approximately \(N_s=100\) sweeps.\\
                 \subref{sfig:equiandauto:autoM} The autocorrelation of an
@@
         function \(\exp(-t/\tau)\) like in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
-        or integrate \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
+        or integrate
+        \begin{equation}
+            \tau = \int \frac{\chi(t)}{\chi(0)} \de t.
+            \label{eq:tau}
+        \end{equation}
         \(\tau\) is an estimate that specifies the time after which two
@@
         \begin{equation}
-            \Delta H = H(\nu) - H(\mu)\\
+            \Delta H = H_\nu - H_\mu
             \label{eq:dH}
         \end{equation}
-        that would result from a flip of that spin and execute the flip
-        with the probability, see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}
+        that would result from a flip of that spin. Where \(\mu\) is the
+        state before the flip and \(\nu\) after the flip. The flip is then executed
+        with the probability
         \begin{equation}
@@
         \end{equation}
+        see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
         So if a transition lowers the energy it will be always done. This
-        results in a high ratio between chosen spins and flipped spins.
+        results in a high ratio between flipped spins and chosen spins.
         Therefore it minimizes the calculations needed for a change of
@@
         This is called \emph{critical slowing} down.\\
-        In order to circumvent this a cluster algorithm like the \emph{Wolff}
+        In order to circumvent this, a cluster algorithm like the \emph{Wolff}
         algorithm \cite{Wolff1989} can be used.
         For an Ising model the Wolff algorithm builds a cluster of sites
-        starting with a random site and adding neighboring sites of the
-        same spin with probability
+        starting with a random site and adding neighboring sites exhibiting the
+        same spin orientation with probability
         \begin{equation}
@@
         temperature because big clusters are flipped. But there are not
-        much advantages at high or low temperatures. At low temperatures
-        the cluster will consist of almost all sites such that all but
-        very few spins will be flipped. At high temperatures the cluster
-        will only contain very few sites.
-        Both situations have no advantage over the Metropolis algorithm.\\
+        much advantages at high or low temperatures. At high temperatures the cluster
+        will only contain very few sites, so only few spins will be flipped.
+        At low temperatures the cluster will consist of almost all sites
+        such that all but very few spins will be flipped. Altough the equilibrium
+        will be reached sooner at low temperatures than with the Metropolis
+        algorithm, situations have no advantage after equilibration.\\
         So one would activate this algorithm near the critical temperature
@@
         \begin{equation}
-            P_{i,i+1}((E_i,T_i) \to (E_{i+1},T_{i+1})) = \min\brac{1,\exp\brac{\brac{E_{i+1}-E_i}\brac{\frac{1}{T_{i+1}}-\frac{1}{T_i}}}},
+            P_{\nu,\nu+1}(S_\nu \leftrightarrow S_{\nu+1}) = \min\brac{1,\exp\brac{\brac{E_{\nu+1}-E_\nu}\brac{\frac{1}{T_{\nu+1}}-\frac{1}{T_\nu}}}},
             \label{eq:partemp}

### 2013-09-23 Tex/chapters/model.tex
Verbesserungsvorschläge umgesetzt

@@
     as the \emph{square lattice Ising model}, is a square lattice with
-    edge length \(L\) and \(N=L^2\) sites with periodic boundary conditions.
+    lateral length \(L\) and \(N=L^2\) sites with periodic boundary conditions.
     Note that \(N\) always refers to the number of sites in this thesis.
@@
     \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are nearest
-    neighbors, so that they are directly coupled to each other. The
+    neighbors, so that they are directly coupled to each other. This will
+    be called an edge. The
     coupling between \(i\) and \(j\) is characterized by \(J_{ij}\),
@@
     \begin{equation}
-        f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}.
+        f(\Delta x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{\Delta x^2}{2\sigma^2}}.
         \label{eq:gauss}
@@
     so that for a given configuration of points the resulting graph is an
-    instance of a proximity graph. The coupling constant \(J\) gets
+    instance of a so called proximity graph. The coupling constant \(J\) gets
     identified with edge weights. \(J\) will be changed to depend on the
@@
             Also the shades are of course only a guide to the eye.
+            This model was created using \texttt{Blender}\footnote{Blender is an open source 3D modelling tool. \url{http://www.blender.org/}}.
         }
@@
 \label{ssec:graphtypes}
-    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\). In the
+    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E \subset V^(2)\). In the
     scope of this model, the nodes get identified with the sites of the
@@
         To make this clear the construction of a four node DT is sketched
-        in Fig.\ \ref{fig:def:DT} in the appendix Sec.\ \ref{appendix:DT_def}.
+        in Fig.\ \ref{fig:def:DT} (see appendix).
 
@@
         graph (RNG) \cite{Toussaint1980} is a subgraph of the GG. Two nodes \(i\) and \(j\) with
-        distance \(d_{ij}\) will be connected, if no other node is in the
-        \emph{lune}. The lune is defined as the intersection of two
+        distance \(d_{ij}\) will be connected again, if no other node is in the
+        \emph{lune}, which is different from the lune of the GG. The lune
+        is defined as the intersection of two
         circles with radius \(r = d\) and centers on \(i\) and \(j\).
@@
     \subsubsection{Construction}
+        In this thesis only GG and RNG are examined.
         The simplest way to construct these graphs is to test for each
@@
         inside like presented in Ref.\ \cite{RNGCell} and sketched in Fig.\ \ref{fig:cell}.
-        The implementation of this thesis uses \(M = N\) (\(L_c = L\)).
+        The implementation of this thesis uses \(M = N\) (\(L_c = 1\)).
         \begin{figure}[htbp]

### 2013-09-23 Tex/chapters/results.tex
Verbesserungsvorschläge umgesetzt

@@
 \subsection{Technical Details}
-    The generation of the Graphs and the Monte Carlo Simulation are implemented
+    The generation of the graphs and the Monte Carlo simulation are implemented
     in C, all needed random numbers are generated by the GSL \cite{GSL}
@@
     The bootstrap method estimates the error \(\Delta \overline{\avg{O}}\)
-    by taking \(M\) random samples from the \(M\) measured values of \(O\),
-    where the same value can be chosen more than once, calculating the
+    by taking \(M\) random samples from the \(M\) measurements of \(O\),
+    where the same measurement can be chosen more than once, calculating the
     estimator \(\avg{O_b}\) of this bootstrap sample and doing this \(k\)
@@
     The errors of fit parameters are the asymptotic standard errors as calculated
-    by gnuplot. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
+    by gnuplot divded by root of the chi-squared per degree of freedom
+    as stated in \cite{young2012everything}. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
     source plotting program used for all plots and fits in this thesis.
@@
     effects of the Wolff cluster algorithm. At low temperatures it flips nearly every
-    spin in every step, thus the correlation drops to zero after one sweep.
+    spin in every step, thus the autocorrelation time is one sweep.
     (Note that this is not the only explanation for the small values of \(\tau\).
@@
 
-\subsection{Finite Size Effects}
+\subsection{Finite-Size Effects}
 \label{ssec:finitesize}
@@
             The \(L=16\) curve is much less steep than the \(L=128\) curve.
+            Note that the \(L=\infty\) curve has not an infinite slope but
+            follows a power law function near \(T_c\).
         }
@@
     systems, hence no computer simulation will show the exact behavior in the
-    thermodynamic limit. It will always show some \emph{finite size effects}.
-    These finite size effects cause a "smearing out" of the phase
+    thermodynamic limit. It will always show some \emph{finite-size effects}.
+    These finite-size effects cause a "smearing out" of the phase
     transition. This is stronger for smaller system sizes, as shown
@@
     \begin{equation}
-        m \propto \abs{T-T_{c}}^{-\beta}.
+        m \propto \abs{T-T_{c}}^{\beta}.
         \label{eq:critExp:beta}
@@
         \label{eq:fsscaling:m}
-        \avg{m_L} &= L^{-\frac{\beta}{\nu}} \tilde{M}\brac{L^\frac{1}{\nu}\brac{T-T_c}},\\
+        \avg{m_L} &= L^{-{\beta/\nu}} \tilde{M}\brac{L^{1/\nu}\brac{T-T_c}},\\
         \label{eq:fsscaling:chi}
-        \chi_L    &= L^{\frac{\gamma}{\nu}} \tilde{C}\brac{L^\frac{1}{\nu}\brac{T-T_c}},\\
+        \chi_L    &= L^{{\gamma/\nu}} \tilde{C}\brac{L^{1/\nu}\brac{T-T_c}},\\
         \label{eq:fsscaling:g}
-        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}.
+        g         &\propto \tilde{G}\brac{L^{1/\nu}\brac{T-T_c}}.
     \end{align}
@@
     are scaling functions.
-    To find the exponent, e.g.\ \(\nu\), one takes \eqref{eq:fsscaling:g},
-    solves for \(\tilde{G}\), adjusts the axis to represent \(y=\tilde{G}(x)\),
+    To find the exponent, e.g.\ \(\nu\), one takes \eqref{eq:fsscaling:m},
+    solves for \(\tilde{M}\), adjusts the axis to represent \(y=\tilde{M}(x)\),
     and plots the measured observables for all \(L\).
-    Then one varies \(\nu\) and \(T_{c}\) until the plotted observables
+    Then one varies \(\beta\), \(\nu\) and \(T_{c}\) until the plotted observables
     collapse on one curve -- the scaling function.
@@
     the susceptibility \(\chi_{\mathrm{max}}\) to the power law function \(aL^\frac{\gamma}{\nu}\).
-    Because there were many measurements in the vicinity of \(T_c\)
-    (c.f.\ Fig.\ \ref{sfig:gettingCrit:s_1_sus}), it should give a
-    reasonable estimate to take their maximum, without the need to
-    interpolate.
+    Because this should only be a rough check, if the exponents obtained
+    by the collapse are valid, it should give a
+    reasonable estimate to take their maximum, without any kind of interpolation.
     The results are displayed in Fig.\ \ref{fig:susCrossCheck}. The ratios

### 2013-09-24 Tex/chapters/results.tex
Falsche Formulierung behoben
Komma eingefügt

@@
     E.g.\ the critical "exponent" \(\alpha\) corresponding to the divergence of
-    the specific heat \(c\) diverges logarithmically for the two dimensional
-    Ising model and is nominally \(\alpha = 0\).
+    the specific heat \(c\) for the two dimensional Ising model is nominally \(\alpha = 0\),
+    because \(c\) diverges logarithmically and not exponentially.
     For that reason, \(\alpha\) will not be considered in this section.\\
@@
     universal for a model with respect to certain model characteristics.
-    I.e.\ for a given dimension they are independent of the precise lattice
+    I.e., for a given dimension they are independent of the precise lattice
     structure and the magnitude of the coupling constant \(J\).

### 2013-09-25 Tex/chapters/conclusion.tex
Korrekturen und Ergänzungen

@@
 Simulations. The neighbor relationship is provided by two proximity graphs
--- the RNG and the GG. These graphs conserve the two dimensional character
-of the lattice. The coupling constants
+-- the RNG and the GG. These graphs conserve the two-dimensional, planar
+character of the lattice. The coupling constants
 are distance dependent, with increasing distance the coupling strength
@@
 ferromagnet. Its critical temperature decreases with increasing disorder
-on a RNG. Since effectively, the decreasing average coordination number
+on a RNG. The reason is that the decreasing average coordination number
 of the underlying graph lowers the resistance to spin flips within
 strongly polarized configurations at low temperatures.
- On a GG it first jumps, increases up to a maximum and decreases
+On a GG \(T_c\) first jumps, increases up to a maximum and decreases
 afterwards. At high disorder it approaches the limit of randomly generated

### 2013-09-25 Tex/chapters/results.tex
Korrekturen und Ergänzungen

@@
     intersecting at \(T \approx 2.27\).
-    To determine \(T_c\), the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
+    To determine \(T_c\), the six unique intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}} \(\in \{(16,32),(16,64),(16,128),(32,64),(32,128),(64,128)\}\)
     are averaged and the standard error is calculated. In this case, one
@@
     values obtained by the data collapse from the previous section.
-    \begin{table}[htbp]
+    \begin{table}[htb]
         \center
@@
     agreement and of comparable precision.\\
-    These values of \(T_c\) are plotted over \(\sigma\) in Fig.\ \ref{fig:Tc}.
+    These values of \(T_c\) are plotted as a function of \(\sigma\) in Fig.\ \ref{fig:Tc}.
     \begin{figure}[htbp]
@@
         %~ Note that \(K\) is independent of \(L\) because of the periodic boundary.
-        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
-        one can see that these curves are almost identical and the small
-        errorbars suggest that they are sufficiently precise for this purpose.
+        %~ In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
+        %~ one can see that these curves are almost identical and the small
+        %~ errorbars suggest that they are sufficiently precise for this purpose.
+        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
+        But the discontinuity at \(K \approx 4\) and slight curvature at
+        \(K \approx 5\) proof that it is not the only influence.
+        \begin{figure}[htb]
+            \centering
+            \includegraphics[width=0.45\textwidth]{plots/Tc_K}
+            \caption[Critical Temperature as a Function of the Degree of the Graph]
+            {
+                The critical temperature is plotted as a function of the
+                degree. There seems to be an in first approximation linear
+                dependency. But at \(K \approx 4\) the jump also seen in
+                Fig.\ \ref{fig:Tc} occurs. Also slight curvature can be
+                recognized and is further examined in Fig.\ \ref{fig:Tc_deg}.
+            }
+            \label{fig:Tc_K}
+        \end{figure}\\
         It seems reasonable to normalize \(T_c\) by the degree of the underlying
@@
         unfortunately a coincidence and probably caused by a lucky choice of the
-        function, which determines the coupling constants \(J\). As proof for
+        function, which determines the local coupling constants \(J_{ij}\). As proof for
         this claim in Sec.\ \ref{appendix:fixedCoupling} the same analysis
@@
         for the RNG are smaller than those for the GG.
-        \begin{figure}[htbp]
+        \begin{figure}[htb]
             \centering
@@
         Fig.\ \ref{fig:GGEdge}.
-        \begin{figure}[htbp]
+        \begin{figure}[htb]
             \centering
@@
         Further, the increase of \(T_c\) on the GG can be made plausible.
-        Also, the maximum value of \(K\) and the minimum value of \(T_c\)
+        Also, the maximum value of \(K\) and the maximum value of \(T_c\)
         are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
         than edges are vanishing until \(\sigma \approx 0.15\) is reached.
-        Then more edges disappear, than appear at further displacement. This
+        Then more edges disappear than appear at further displacement. This
         is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
-        \begin{figure}[htbp]
+        \begin{figure}[htb]
             \subfigure[][$\sigma = 0.00$]
@@
         However, note that the degree does not alone influence the behavior of \(T_c\).
-        Further \(T_c\) depends on the coupling constant \(J\), which is
+        Further \(T_c\) depends on the coupling constant \(J_{ij}\), which is
         obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
@@
         of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
-        The plots Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
-        show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
-        \begin{figure}[hbtp]
+        The plot Fig.\ \ref{fig:Tc_J} shows that
+        there is a less obvious dependency between \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_K}).
+        \begin{figure}[htbp]
+            \centering
+            \includegraphics[width=0.45\textwidth]{plots/Tc_J}
+            \caption[Critical Temperature as a Function of the Degree of the Graph]
+            {
+                The critical temperature is plotted as a function of the
+                average edge weight. T
+            }
+            \label{fig:Tc_J}
+        \end{figure}\\
+        Though Eq.\ \eqref{eq:exactHCTc} and Fig.\ \ref{fig:Tc_J} show
+        that there is no linear connection between \(J\) and \(T_c\), the best guess
+        is a linear connection, because this model is derived from the
+        square lattice, where the connection is linear. Therefore, one
+        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
+        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
+        jump on the GG arises again, but \(T_c\) is now monotonically
+        decreasing with increasing disorder parameter \(\sigma\).
+        \begin{figure}[hbt]
             \centering
@@
         \end{figure}\\
-        Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
-        to be a linear connection between \(J\) and \(T_c\), the best guess
-        is a linear connection, because this model is derived from the
-        square lattice, where the connection is linear. Therefore, one
-        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
-        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
-        jump on the GG arises again, but \(T_c\) is now monotonically
-        decreasing with increasing disorder parameter \(\sigma\).
         %~ This is a strong hint, that the change of the \(T_c\) with changing
@@
         \begin{align}
-            \avg{\sum_{\avg{i,j}} J_{ij}} &= \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
+            \avg{\sum_{\avg{i,j}} J_{ij}} &\approx \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
                                           &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
@@
     lattice structure has a minor effect on \(g_c\), the uncertainty of
-    \(g_c\) is too large to observe this. For a more exact analysis, new
+    \(g_c\) is too large to confirm this. For a more exact analysis, new
     Monte Carlo simulations at \(T_c\) would be needed. But this is
-    beyond the scope of this thesis. Anyway, the results are the expected
+    beyond the scope of this thesis. Anyway, the results show the expected
     behavior, because no major deviations from the value of \(g_c\) at

### 2013-09-25 auswertung/getJ.py
Distanz der Knoten wird gemessen und ausgegeben

@@ -8,6 +8,7 @@ def getJFromDat(dataPath, outPath, L):
     J = {}
     sumJ = {}
     deg = {}
+    d = {}
     if not os.path.exists(outPath):
         os.makedirs(outPath)
 
@@ -30,6 +31,10 @@ def getJFromDat(dataPath, outPath, L):
             deg[r.sigma].append(float(r.deg))
         except KeyError:
             deg.update({r.sigma:[float(r.deg)]})
+        try:
+            d[r.sigma].append(float(r.d))
+        except KeyError:
+            d.update({r.sigma:[float(r.d)]})
 
     #~ print d
     for key in J.keys():
@@ -38,6 +43,8 @@ def getJFromDat(dataPath, outPath, L):
         sumJ[key] = [mean(sumJ[key]), std(sumJ[key])/sqrt(len(sumJ[key]))]
     for key in deg.keys():
         deg[key] = [mean(deg[key]), std(deg[key])/sqrt(len(deg[key]))]
+    for key in d.keys():
+        d[key] = [mean(d[key]), std(d[key])/sqrt(len(d[key]))]
 
     print dataPath
     print "<J>"
@@ -57,6 +64,13 @@ def getJFromDat(dataPath, outPath, L):
     print "deg"
     with open(os.path.join(outPath, "deg_L{0}.dat".format(L)), "w") as f:
         for [key, val] in sorted(deg.items()):
+            print key, " : ", val[0], "+-", val[1]
+            f.write("{0} {1} {2}\n".format(key,val[0],val[1]))
+    print " "
+
+    print "d"
+    with open(os.path.join(outPath, "d_L{0}.dat".format(L)), "w") as f:
+        for [key, val] in sorted(d.items()):
             print key, " : ", val[0], "+-", val[1]
             f.write("{0} {1} {2}\n".format(key,val[0],val[1]))
     print " "

### 2013-09-25 auswertung/reader.py

@@ -28,6 +28,9 @@ class output_reader():
     ## @var sigma
     # Unordnungsparameter (double)
 
+    ## @var d
+    # mittlerer Knotenabstand (double)
+
     ## @var J
     # mittleres J (double)
 
@@ -73,6 +76,7 @@ class output_reader():
             self.J = " ".join(header).rpartition("<J>=")[2].partition (" #")[0]
             self.sumJ = " ".join(header).rpartition("sumJ=")[2].partition (" #")[0]
             self.deg = " ".join(header).rpartition("deg=")[2].partition (" #")[0]
+            self.d = " ".join(header).rpartition("d=")[2].partition (" #")[0]
 
             # Zwischenspeichern, da Einträge im Reader verbraucht werden
             alle = [i for i in reader]

### 2013-09-25 graph_modify.c

@@ -475,6 +475,29 @@ node_t * gs_depth_first_search(gs_graph_t *g, int node, int target, node_t *tree
     return tree_of_tested_nodes;
 }
 
+/*! \fn double get_mean_dist(gs_graph_t *g)
+    \brief Diese Funktion gibt den Mittelwert der Knotendistanzen im
+            Graphen g aus indem er eine Umkehrfunktion auf die einzelnen
+            Gewichte anwendet
+
+    \param [in] g Graph über den gemittelt wird
+    \return Mittelwert der Knotendistanzen
+*/
+double get_mean_dist(gs_graph_t *g)
+{
+    int n, i;
+    double sum = 0;
+    int count = 0;
+    for(n=0;n<g->num_nodes; n++)
+        for(i=0;i<g->node[n].num_neighbors;i++)
+        {
+            sum += -log(g->node[n].neighbors[i].weight)*2+1;
+            count++;
+        }
+    /* Es sollte egal sein, dass über jede Kante zweimal summiert wird */
+    return (sum / count);
+}
+
 /*! \fn double get_mean_weight(gs_graph_t *g)
     \brief Diese Funktion gibt den Mittelwert der Kantengewichte im
             Graphen g aus

### 2013-09-25 graph_modify.h

@@ -33,6 +33,7 @@ inline void get_cell_border_gabriel(gs_node_t node1, gs_node_t node2, double dis
 void delete_random_edges_till_percolation(gs_graph_t *g, gsl_rng *rng);
 int test_connectivity_between_nodes(gs_graph_t *g, int node1, int node2);
 node_t * gs_depth_first_search(gs_graph_t *g, int node, int target, node_t *tree_of_tested_nodes, int *status);
+double get_mean_dist(gs_graph_t *g);
 double get_mean_weight(gs_graph_t *g);
 double get_mean_deg(gs_graph_t *g);
 double get_sum_weight(gs_graph_t *g);

### 2013-09-25 spin.c

@@ -354,7 +354,7 @@ void do_mc_simulation(gs_graph_t **list_of_graphs, const options_t o)
         exit(-1);
     }
     /* Schreibe Header */
-    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # r=%d # <J>=%.6f # deg=%.6f # sumJ=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, o.percolation, get_mean_weight(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]), get_sum_weight(list_of_graphs[0]));
+    fprintf(data_out_file, "# N E M # sigma=%.3f # x=%d # L=%d # type=%d # r=%d # <J>=%.6f # d=%.6f # deg=%.6f # sumJ=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, o.percolation, get_mean_weight(list_of_graphs[0]), get_mean_dist(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]), get_sum_weight(list_of_graphs[0]));
     for(nT=0;nT<o.num_temps;nT++)
         fprintf(data_out_file, "%.3f, ", list_of_graphs[nT]->T);
     fprintf(data_out_file, "\n");

### 2013-09-25 Tex/chapters/results.tex
Unmissverständliche Def. von K
Vorläufige Bemerkung zu Fehlerbalkenbestimmung

@@
     According to Tab.\ \ref{tab:critExp}, most values
-    are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
+    are matching the expectations.\\
+    Note that the large deviations in comparison to the given error for
+    \(\gamma\) and \(\beta\) at \(\sigma = 0\) might be caused by the
+    determination of the errorbars which neglects the thermal fluctuations
+    and mainly accounts for fluctuations induced by variing graph instances.
+    Those are according to my tests of greater importance except for
+    \(\sigma =0\) where they do not occur. Hence the errorbars at \(\sigma = 0\)
+    are underestimated. The quality parameter \(S\) of \texttt{autoscale.py}
+    showed for the \(\sigma = 0\) collapses a bad value, too. That is a strong
+    hint for underestimated errorbars.
+    As a conclusion, the method for the determination of the errorbars
+    has to be optimized to also account for the thermal fluctuations which
+    are important for \(\sigma=0\) and possibly \(\sigma\approx 0\).
+    In spite of this flaw, the second method for determining \(T_{c}\),
+    which is performed in the next section, does not utilize the errorbars
+    and is therefore unaffected for all \(\sigma\).\\
+    \(T_c\) for \(\sigma = 0\) is in good
     agreement with the known value. Especially \(\nu\) and \(\gamma\)
@@
         \begin{equation}
-            K = \frac{1}{N} \sum_{\avg{i,j}} 1.
+            K = \frac{2}{N} \sum_{E} 1.
             \label{eq:degree}
         \end{equation}
+        Where \(E\) is the set of edges.
         For a Poisson point process, i.e.\ for \(\sigma \gtrsim 1\),

### 2013-09-26 Tex/chapters/results.tex
Neue, bessere Bootstrap Methode zur Fehlerfindung

--- 2013-09-25 Tex/chapters/results.tex
@@
     \cite{Bootstrap}.\\
-    The bootstrap method estimates the error \(\Delta \overline{\avg{O}}\)
-    by taking \(M\) random samples from the \(M\) measurements of \(O\),
-    where the same measurement can be chosen more than once, calculating the
-    estimator \(\avg{O_b}\) of this bootstrap sample and doing this \(k\)
-    times. Then the standard deviation of the \(k\) calculated \(\avg{O_b}\)
-    is taken as an estimate for \(\Delta \overline{\avg{O}}\).
-    In this thesis the number of bootstrap samples is \(k = 200\).\\
-    Note that the error of \(\avg{O}\), which is the standard error\footnote{for the arthmetic mean: standard deviation divided by \(\sqrt M\), where \(M\) is the number of samples}
-    of different states on one instance of a proximity graph \(\Delta \avg{O}\),
-    is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}.
-    However \(\Delta \overline{\avg{O}}\), which is the the error of the
-    observable averaged over different instances of the proximity graphs,
-    is not dependend on \(\tau\), because different realizations of the
-    random proximity graph are surely uncorrelated.
-    Because every error mentioned in this thesis is of this type, it is not
-    necessary to determine \(\tau\) for each observable. Therefore a good
-    error estimate can be achieved by simple bootstrapping. Nevertheless, one has
-    to simulate enough uncorrelated states for each realization to keep
-    the \(\Delta \overline{\avg{O}}\) small. For every determined value an
+    There are two kinds of errors in this simulations. On the one hand
+    there are thermal fluctuations in the simulation of one graph realization and
+    on the other hand there are fluctuations in the structure of the realizations.
+    To account for both, first a resampling of the "timeline" of one
+    realization is performed. From these resamples the expected values of
+    the observables \(\avg\abs{m}, \chi\) and \(g\) are estimated for each
+    realization. Those are then resampled and from the resampled values
+    one bootstrap average \(\avg{O}b\) is calculated. This procedure is
+    repeated until 20 different bootstrap averages are present. Their
+    mean and standard deviation are the used as \(\overline{\avg{O}}\) and
+    its standard error \(\Delta \overline{\avg{O}}\). A shematic figure of
+    this is shown in Fig.\ \ref{fig:bootstrap}.
+    % TODO
+    For every determined value an
     error is calculated and given in the form \texttt{value(error of last digit)}.
@@
     According to Tab.\ \ref{tab:critExp}, most values
-    are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
+    are matching the expectations.
+    \(T_c\) for \(\sigma = 0\) is in good
     agreement with the known value. Especially \(\nu\) and \(\gamma\)

### 2013-09-26 auswertung/db.py

@@ -159,7 +159,15 @@ class Database():
         return tau
 
     @staticmethod
-    def bootstrap_stderr(x, n_resample, f):
+    def bootstrap_stderr(xRaw, n_resample, f):
+        #~ for i in range(n_resample):
+            #~ mittelwerteForRealisations = [f([choice(xRealisierung) for _ in xRealisierung]) for xRealisierung in xRaw]
+            #~ meanmean[i] = mean([choice(mittelwerteForRealisations) for _ in mittelwerteForRealisations])
+        bootstrapSample = [mean([choice([f([choice(xRealisierung) for _ in xRealisierung]) for xRealisierung in xRaw]) for _ in xRaw]) for i in range(n_resample)]
+        return mean(bootstrapSample), std(bootstrapSample)
+
+    @staticmethod
+    def bootstrap_stderr_old(x, n_resample, f):
         h = [f([choice(x) for _ in x]) for _ in range(n_resample)]
         return std(h)
 
@@ -481,21 +489,21 @@ class Database():
         c.close()
         # Berechne die Erwartungswerte
         if signed:
-            M = [f(list(self.getVal(i[0])),T,L) for i in lst]
+            M = [list(self.getVal(i[0])),T,L for i in lst]
         else:
-            M = [f(list(map(abs,self.getVal(i[0]))),T,L) for i in lst]
+            M = [list(map(abs,self.getVal(i[0]))),T,L for i in lst]
 
         # berechne den Mittelwert der Erwartungswerte
-        return mean(M), self.bootstrap_stderr(M, 200, mean)
+        return self.bootstrap_stderr(M, 20, lambda x: f(x,L,T))
 
     def getAverageE(self, f, sigma, L, T):
         """! Liefert den über verschiedene Realisierungen gemittelten
         Erwartungswert von f(E) aus: mean(<f(E)>) """
         c = self.connRaw.cursor()
         c.execute('SELECT E FROM rawdata WHERE sigma = ? AND L = ? AND T = ?', (sigma, L, T))
-        E = [f(self.getVal(i[0]),T,L) for i in c.fetchall()]
+        E = [self.getVal(i[0]),T,L for i in c.fetchall()]
         c.close()
-        return mean(E), self.bootstrap_stderr(E, 200, mean)
+        return self.bootstrap_stderr(E, 20, lambda x: f(x,L,T))
 
 if __name__ == '__main__':
     a=Database( dbPath = "dataRNG.db", dataPath = "../dataRNG", graphType=1)

### 2013-09-26 Tex/chapters/results.tex
fehlerkorrektur

@@
     The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrap resampling
-    \cite{Bootstrap}.\\
+    \cite{Bootstrap}.
     There are two kinds of errors in this simulations. On the one hand
@@
     realization is performed. From these resamples the expected values of
-    the observables \(\avg\abs{m}, \chi\) and \(g\) are estimated for each
+    the observables \(\avg{\abs{m}}, \chi\) and \(g\) are estimated for each
     realization. Those are then resampled and from the resampled values
-    one bootstrap average \(\avg{O}b\) is calculated. This procedure is
+    one bootstrap average \(\avg{O}_b\) is calculated. This procedure is
     repeated until 20 different bootstrap averages are present. Their
-    mean and standard deviation are the used as \(\overline{\avg{O}}\) and
-    its standard error \(\Delta \overline{\avg{O}}\). A shematic figure of
-    this is shown in Fig.\ \ref{fig:bootstrap}.
-    % TODO
+    mean and standard deviation are used as \(\overline{\avg{O}}\) and
+    its standard error \(\Delta \overline{\avg{O}}\).
     For every determined value an

### 2013-09-26 Tex/chapters/results.tex
Betrachtung der mittleren Kantelänge d hinzugefügt

@@
         they approach an asymptotic limit for \(\sigma \gg 1\).\\
+        Although one could assume, that the course of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
+        should be strongly influenced by the mean length of the edges, because \(J_{ij}\)
+        is a function on the edge length \(d_{ij}\), this is not the case.
+        As shown in Fig.\ \ref{fig:TcD}, it shows especially at low \(\sigma\)
+        a more complicated course than both \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
+        This is a hint that the influence of \(K\) on \(T_c\) is much more
+        important than the influence of \(d\) and therefore the influence
+        of \(J_{i,j}\) on \(T_c\). At least with the chosen function for \(J_{ij}\).
+        \begin{figure}[hbt]
+            \centering
+            \subfigure[][]
+            {
+                \label{sfig:TcD:RNG}
+                \includegraphics[width=0.45\textwidth]{plots/RNG_d}
+            }
+            \subfigure[][]
+            {
+                \label{sfig:TcD:GG}
+                \includegraphics[width=0.45\textwidth]{plots/GG_d}
+            }
+
+            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
+            {
+                The mean length of all edges \(d\) for
+                \subref{sfig:TcD:RNG} RNG
+                and \subref{sfig:TcD:GG} GG for different system sizes \(L\)
+                averaged over 100 different realizations.
+            }
+            \label{fig:TcD}
+        \end{figure}\\
         If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)

### 2013-09-26 Tex/chapters/results.tex
power law fit benutzt zur K-normalisierung

@@
         The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
+        In fact one can fit
         But the discontinuity at \(K \approx 4\) and slight curvature at
@@
                 The critical temperature is plotted as a function of the
-                degree. There seems to be an in first approximation linear
-                dependency. But at \(K \approx 4\) the jump also seen in
-                Fig.\ \ref{fig:Tc} occurs. Also slight curvature can be
-                recognized and is further examined in Fig.\ \ref{fig:Tc_deg}.
+                degree. At \(K \approx 4\) the jump also seen in Fig.\ \ref{fig:Tc} occurs.
+                There seems to be an in first approximation linear
+                dependency. The dotted lines are fits to a power law function \(T_c = aK^b\)
+                ignoring the point at \(K=4\) on the GG.
+                As a approximation it seems suited but besides the bad
+                \(\chi^2\) values are hints that there is some finer
+                structure which is not fitted by a power law function.
+                This is further examined in Fig.\ \ref{fig:Tc_deg}.
             }
@@
         is performed for a model with fixed \(J\). There the jump gets narrower
-        but is still existent. Anyway, the degree seems to have an impact on
+        but is still existent.\\
+        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
+        the normalization is done using the found power law function.
+        The amplitude of the curve shrinks which is a hint, that this is a good
+        approximation. But it is not a constant, so there have to be other
+        influences.
+        Anyway, the degree seems to have a major impact on
         the critical temperature \(T_c\), but it is not a trivial one.
@@
             }
+            \subfigure[][]
+            {
+                \label{sfig:Tc_norm_deg_fit:RNG}
+                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_fit}
+            }
+            \subfigure[][]
+            {
+                \label{sfig:Tc_norm_deg_fit:GG}
+                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_fit}
+            }
 
@@
                 \subref{sfig:deg:GG} the GG.
-                Bottom: Critical temperatures normalized by degree over different
+                Middle: Critical temperatures normalized by degree over different
                 disorder parameters for
@@
                 \subref{sfig:Tc_norm_deg:GG} the GG.
+                Bottom: Critical temperatures normalized by the in Fig.\ \ref{fig:Tc_K}
+                determined power law function over different
+                disorder parameters for
+                \subref{sfig:Tc_norm_deg:RNG} the RNG and
+                \subref{sfig:Tc_norm_deg:GG} the GG.
+                Note that the \(\sigma = 0\) point of the GG is not displayed.
+                The found power law function seems to be a good approximation.
+                But at least for the RNG and at least for small values of
+                \(\sigma\) on the GG it can not explain everything.
             }

### 2013-09-26 Tex/chapters/results.tex
Bruchstriche in Exponenten entfernt

@@
     the ratio \(\frac{\gamma}{\nu}\) is also determined by fitting the maxima of
-    the susceptibility \(\chi_{\mathrm{max}}\) to the power law function \(aL^\frac{\gamma}{\nu}\).
+    the susceptibility \(\chi_{\mathrm{max}}\) to the power law function \(aL^{\gamma/\nu}\).
     Because this should only be a rough check, if the exponents obtained
@@
             The plotted values are the maxima of all measured \(\chi\).
-            Dotted lines are fits to the power law function \(aL^\frac{\gamma}{\nu}\).
+            Dotted lines are fits to the power law function \(aL^{\gamma/\nu}\).
         }

### 2013-09-26 Tex/chapters/results.tex
andere Schreibweise zur Kantenzahl
Fehlerkorrekturen, Formulierung und Positionierung

@@
         \begin{equation}
-            K = \frac{2}{N} \sum_{E} 1.
+            K = \frac{2}{N} \# E.
             \label{eq:degree}
         \end{equation}
-        Where \(E\) is the set of edges.
+        Where \(\# E\) is the number of edges of the graph.
         For a Poisson point process, i.e.\ for \(\sigma \gtrsim 1\),
@@
         In Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
-        the normalization is done using the found power law function.
+        the normalization is done using power law function obtained through the fit from Fig.\ \ref{fig:Tc_K}.
         The amplitude of the curve shrinks which is a hint, that this is a good
@@
         influences.
-        Anyway, the degree seems to have a major impact on
-        the critical temperature \(T_c\), but it is not a trivial one.
         Note that even after the normalization, the values of \(T_c / K\)
-        for the RNG are smaller than those for the GG.
-        \begin{figure}[htb]
+        for the RNG are smaller than those for the GG.\\
+        Anyway, this analysis shows that the degree has a major impact on
+        the critical temperature \(T_c\), but it also shows that there
+        have to be other graph properties having a minor influence on \(T_{c}\).
+        \begin{figure}[htbp]
             \centering
@@
                 disorder parameters for
-                \subref{sfig:Tc_norm_deg:RNG} the RNG and
-                \subref{sfig:Tc_norm_deg:GG} the GG.
+                \subref{sfig:Tc_norm_deg_fit:RNG} the RNG and
+                \subref{sfig:Tc_norm_deg_fit:GG} the GG.
                 Note that the \(\sigma = 0\) point of the GG is not displayed.
@@
         \end{figure}\\
-        To understand the jump of \(T_c\) it seems to be necessary to
+        To understand the jump of \(T_c\) on a GG it seems to be necessary to
         understand the jump of \(K\), which is easily explained
@@
                 The critical temperature is plotted as a function of the
-                average edge weight. T
+                average edge weight. The curve shows a less straight line
+                than Fig.\ \ref{fig:Tc_K}.
             }
@@
         decreasing with increasing disorder parameter \(\sigma\).
-        \begin{figure}[hbt]
+        \begin{figure}[hbtp]
             \centering
@@
                 \includegraphics[width=0.45\textwidth]{plots/GG_Tc_normJ}
+            }
+
+            \subfigure[][]
+            {
+                \label{sfig:TcD:RNG}
+                \includegraphics[width=0.45\textwidth]{plots/RNG_d}
+            }
+            \subfigure[][]
+            {
+                \label{sfig:TcD:GG}
+                \includegraphics[width=0.45\textwidth]{plots/GG_d}
             }
@@
                 \subref{sfig:sumJ:GG} the GG.
-                Bottom: Critical temperatures normalized by mean sum of the
+                Middle: Critical temperatures normalized by mean sum of the
                 coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
@@
                 \subref{sfig:Tc_normJ:GG} the GG.
+                Bottom: The mean length of all edges \(d\) for
+                \subref{sfig:TcD:RNG} RNG
+                and \subref{sfig:TcD:GG} GG for different system sizes \(L\)
+                averaged over 100 different realizations.
             }
@@
         \end{figure}\\
-        %~ This is a strong hint, that the change of the \(T_c\) with changing
-        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
-        %~ expected conclusion.\\
         Moreover the forms of both curves are quite similar, but the
@@
         is a function on the edge length \(d_{ij}\), this is not the case.
-        As shown in Fig.\ \ref{fig:TcD}, it shows especially at low \(\sigma\)
+        As shown in Fig.\ \ref{fig:TcJ}\subref{sfig:TcD:RNG}\subref{sfig:TcD:GG}, it shows especially at low \(\sigma\)
         a more complicated course than both \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
@@
         of \(J_{i,j}\) on \(T_c\). At least with the chosen function for \(J_{ij}\).
-        \begin{figure}[hbt]
-            \centering
-            \subfigure[][]
-            {
-                \label{sfig:TcD:RNG}
-                \includegraphics[width=0.45\textwidth]{plots/RNG_d}
-            }
-            \subfigure[][]
-            {
-                \label{sfig:TcD:GG}
-                \includegraphics[width=0.45\textwidth]{plots/GG_d}
-            }
-
-            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
-            {
-                The mean length of all edges \(d\) for
-                \subref{sfig:TcD:RNG} RNG
-                and \subref{sfig:TcD:GG} GG for different system sizes \(L\)
-                averaged over 100 different realizations.
-            }
-            \label{fig:TcD}
-        \end{figure}\\
         If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)

### 2013-09-26 Tex/chapters/results.tex
besserer Text zu power law fit

@@
         %~ errorbars suggest that they are sufficiently precise for this purpose.
-        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
-        In fact one can fit
-        But the discontinuity at \(K \approx 4\) and slight curvature at
-        \(K \approx 5\) proof that it is not the only influence.
         \begin{figure}[htb]
@@
                 ignoring the point at \(K=4\) on the GG.
-                As a approximation it seems suited but besides the bad
+                As a approximation it seems suited but the bad
                 \(\chi^2\) values are hints that there is some finer
@@
         \end{figure}\\
+        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
+        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
+        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
+        seem to indicate that this is only a approximation which does not
+        account for every detail of the curve. These details will be
+        investigated.\\
         It seems reasonable to normalize \(T_c\) by the degree of the underlying
@@
         approximation. But it is not a constant, so there have to be other
-        influences.
+        influences as supposed before.
         Note that even after the normalization, the values of \(T_c / K\)

### 2013-09-26 Tex/chapters/results.tex
textverbesserungen

@@
         should be strongly influenced by the mean length of the edges, because \(J_{ij}\)
-        is a function on the edge length \(d_{ij}\), this is not the case.
-        As shown in Fig.\ \ref{fig:TcJ}\subref{sfig:TcD:RNG}\subref{sfig:TcD:GG}, it shows especially at low \(\sigma\)
-        a more complicated course than both \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
+        is a function on the edge length \(d_{ij}\), this is not exactly the case.
+        As shown in Fig.\ \ref{fig:TcJ}\subref{sfig:TcD:RNG}\subref{sfig:TcD:GG}, the
+        coarse course is similar but \(d\) shows especially at low \(\sigma\)
+        a more complicated course than \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
         This is a hint that the influence of \(K\) on \(T_c\) is much more
         important than the influence of \(d\) and therefore the influence
-        of \(J_{i,j}\) on \(T_c\). At least with the chosen function for \(J_{ij}\).
+        of \(J_{i,j}\) on \(T_c\). At least with the chosen function for \(J_{ij}\).\\
         If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)

### 2013-09-26 auswertung/db.py
viel schnelleres resample mit Ersetzung dank numpy

@@ -9,9 +9,9 @@ import logging
 import array
 from numpy import mean, var
 from numpy import std
+from numpy.random import choice
 import numpy
 
-from random import choice
 
 from reader import *
 
@@ -163,7 +163,7 @@ class Database():
         #~ for i in range(n_resample):
             #~ mittelwerteForRealisations = [f([choice(xRealisierung) for _ in xRealisierung]) for xRealisierung in xRaw]
             #~ meanmean[i] = mean([choice(mittelwerteForRealisations) for _ in mittelwerteForRealisations])
-        bootstrapSample = [mean([choice([f([choice(xRealisierung) for _ in xRealisierung]) for xRealisierung in xRaw]) for _ in xRaw]) for i in range(n_resample)]
+        bootstrapSample = [mean(choice([f(choice(xRealisierung, len(xRealisierung))) for xRealisierung in xRaw], len(xRaw))) for i in range(n_resample)]
         return mean(bootstrapSample), std(bootstrapSample)
 
     @staticmethod
@@ -489,10 +489,11 @@ class Database():
         c.close()
         # Berechne die Erwartungswerte
         if signed:
-            M = [list(self.getVal(i[0])),T,L for i in lst]
+            M = [list(self.getVal(i[0])) for i in lst]
         else:
-            M = [list(map(abs,self.getVal(i[0]))),T,L for i in lst]
-
+            M = [list(map(abs,self.getVal(i[0]))) for i in lst]
+        if not M:
+            return None, None
         # berechne den Mittelwert der Erwartungswerte
         return self.bootstrap_stderr(M, 20, lambda x: f(x,L,T))
 
@@ -501,10 +502,12 @@ class Database():
         Erwartungswert von f(E) aus: mean(<f(E)>) """
         c = self.connRaw.cursor()
         c.execute('SELECT E FROM rawdata WHERE sigma = ? AND L = ? AND T = ?', (sigma, L, T))
-        E = [self.getVal(i[0]),T,L for i in c.fetchall()]
+        E = [self.getVal(i[0]) for i in c.fetchall()]
         c.close()
+        if not E:
+            return None, None
         return self.bootstrap_stderr(E, 20, lambda x: f(x,L,T))
 
 if __name__ == '__main__':
-    a=Database( dbPath = "dataRNG.db", dataPath = "../dataRNG", graphType=1)
[…]

### 2013-09-27 Tex/chapters/conclusion.tex
Ausblick auf g(xi) hinzugefügt

@@
     Delaunay triangulation to examine if it is also similar.\\
+    Also the approach of investigating the Binder Cumulant as a function
+    of the correlation length \(g(\xi)\), which is more
+    sensitive detecting nonuniversalities\cite{Hartmann2013}, could be considered.

### 2013-09-30 Tex/chapters/appendix.tex
Verbesserungsvorschläge umgesetzt
Test, ob max. der spez. Wärme logarithmisch mit L steigt

@@
         \input{images/DT_def}
-        \label{fig:def:DT}
         \caption[Example for a Small Delaunay Triangulation]
@@
         }
+        \label{fig:def:DT}
     \end{figure}
@@
 \label{appendix:finiteSizeEffects}
-    In Fig.\ \ref{fig:smeared_out_appendix} the specific heat
+    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:c} the specific heat
     \begin{equation}
@@
     The divergence is finite and gets steeper with larger \(L\). Besides
-    the maximum moves to the critical temperature with larger \(L\).
+    the maximum moves to the critical temperature with larger \(L\).\\
+    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:logL} the maxima of a
+    cubic spline interpolation of \(c\) is plotted. Note that no errorbars
+    are estimated. As mentioned before,
+    this maximum increases logarithmically. One sees that a logarithmic
+    fit is not worse than the power law fit. But to confirm the expected
+    logarithmic growth, one would need much larger systems. Also the one
+    would estimate the maximum by other means than an interpolation.
     \begin{figure}[htbp]
         \centering
+        \subfigure[][]
+        {
+            \label{sfig:smeared_out_appendix:c}
             \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
+        }
+        \subfigure[][]
+        {
+            \label{sfig:smeared_out_appendix:logL}
+            \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0_log}
+        }
         \caption[Finite Size Effects by Example of the Specific Heat]
         {
-            Effects of different system sizes on the specific heat \(c\)
+            \subref{sfig:smeared_out_appendix:c} Effects of different system sizes on the specific heat \(c\)
             at \(\sigma = 0\). Dotted lines are guides to the eye.
+            \subref{sfig:smeared_out_appendix:logL} maxima of \(c\) fitted
+            with a power law function and a logarithm.
         }

### 2013-10-04 Tex/chapters/introduction.tex
Rechtschreibfehler und so

@@
 whole system is not easy to predict because of the nontrivial interactions of the
-subsystems. For those systems there often exists no analytic solutions
+subsystems. For those systems there often exists no analytic solution
 or only for very simplified or special cases. But one can simulate all
@@
 Proximity graphs are canditates for ad-hoc networks. As an example of an
-ad-hoc network take a wifi network without central devices, but the every
+ad-hoc network take a wifi network without central devices, but every
 participant (e.g.\ a laptop) works as a relay to get a data package to its
@@
 the here investigated irregular lattices will be constructed starting from
-a square lattice and displacing the sites governed by an parameter \(\sigma\).
+a square lattice and displacing the sites governed by a parameter \(\sigma\).
 Then the influence of \(\sigma\) on the critical temperature will be

### 2013-10-04 Tex/chapters/methods.tex
Rechtschreibfehler und so

@@
     condition that the system under scrutiny has reached the temperature
-    of the heat bath. This is the case, once there is only energy fluctuating
-    between them but no net energy exchange, thus the energy of the
-    simulated system reaches a steady state, where only fluctuations occur.
+    of the heat bath. This is the case once no net energy exchange occurs,
+    thus the energy of the simulated system reaches a steady state, where
+    only fluctuations occur.
     In a canonical ensemble the probability \(p_\nu\) of a state
@@
     \end{equation}
-    where the sum goes over all possible states \(i\) of the system.
-    Then, averages can be computed according to
+    where the sum goes over all possible states \(\nu\) of the system.
+    Then averages can be computed according to
     \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_\nu O_\nu e^{-\beta H_\nu},
+        \avg{O} = \frac{1}{Z} \sum_\nu O_\nu e^{-\beta H_\nu}.
     \end{equation}
@@
     Beside these observables from classical physics, a fifth observable
-    the binder cumulant \cite{Binder1981}
+    the Binder cumulant \cite{Binder1981}
     \begin{equation}
@@
     \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_i p_i O_i.
+        \avg{O} = \frac{1}{Z} \sum_\nu p_\nu O_\nu.
+        \label{eq:estim}
     \end{equation}
     It is however possible that there are few states contributing
-    massively more than others. In canonical systems at low \(T\),
+    massively more than others. In canonical systems at low \(T\)
     states with low values of \(H\) contribute much more than states with
@@
     As noted before, the system under scrutiny is canonical and therefore
-    \(p_i\) is known. The states are distributed according to the Boltzmann
+    \(p_\nu\) is known. The states are distributed according to the Boltzmann
     distribution. Hence \emph{Importance Sampling} can be utilized.\\
@@
     states according to their occurence probability given by the Boltzmann
-    distribution. In fact this reduces the estimator to
+    distribution. In fact this reduces the estimator Eq.\ \eqref{eq:estim} to
     \begin{equation}
@@
         At low temperatures the cluster will consist of almost all sites
-        such that all but very few spins will be flipped. Altough the equilibrium
+        such that all but very few spins will be flipped. Through this effect the equilibrium
         will be reached sooner at low temperatures than with the Metropolis
-        algorithm, situations have no advantage after equilibration.\\
+        algorithm, but after equilibration the Wolff cluster update has no
+        advantage compared to the Metropolis at high or low temperatures.\\
         So one would activate this algorithm near the critical temperature
@@
         the spin configurations between two neighboring temperatures are
-        swapped periodically with probability \cite[p. 169ff]{NewmanBarkema1999} \cite[S. 155ff]{Katzgraber2011}
+        swapped periodically with probability \cite[p. 169ff]{NewmanBarkema1999} \cite[p. 155ff]{Katzgraber2011}
         \begin{equation}
@@
             {
-                \subref{sfig:parTemp:schema} schematic representation of
+                \subref{sfig:parTemp:schema} Schematic representation of
                 the swapping of spin configurations of different simulations \(S_i\)
                 between temperatures.\\
-                \subref{sfig:parTemp:E} sketch of an energy landscape, where
+                \subref{sfig:parTemp:E} Sketch of an energy landscape, where
                 the state of the system (filled circle) is trapped in an local
@@
         In the case of a ferromagnetic Ising model the risk to get trapped
-        in a local energy minimum is very low. Consequently the autocorrelation
-        decreases significantly. In the scope of this thesis it is benefical
+        in a local energy minimum is very low. In the scope of this thesis it is benefical
         to use parallel tempering, because one has to simulate at many temperatures
@@
         to determine whether to swap configurations or not, are small in
-        comparison with those that would be needed to generate a new
-        uncorrelated state without \emph{parallel tempering}.
+        comparison with the much lower autocorrelation times which are
+        achieved with parallel tempering.
 

### 2013-10-04 Tex/chapters/model.tex
Rechtschreibfehler und so

@@
     geometric distance between the connected pair of sites. More precise,
-    the weight of an edge is \(E_{ij} = J_{ij} = \exp (\alpha (1-d_{ij}))\)
+    the weight of an edge is
+    \begin{equation}
+        E_{ij} = J_{ij} = \exp (\alpha (1-d_{ij}))
+        \label{eq:coupling}
+    \end{equation}
     where \(d_{ij}\) is the Euclidean
@@
     already studied on a Delaunay triangulation. Ref.\ \cite{Janke1994} examines
-    this for constant \(J\) and Ref.\ \cite{Lima2000} for
-    \begin{equation}
-        J_{ij} = e^{-\alpha d_{ij}}.
-        \label{eq:coupling}
-    \end{equation}
+    this for constant \(J\) and Ref.\ \cite{Lima2000} for \(J_{ij} = e^{-\alpha d_{ij}}\).
     Both articles conclude that this model lies within the universality
@@
 \label{ssec:graphtypes}
-    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E \subset V^(2)\). In the
+    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E \subset V^{(2)}\). In the
     scope of this model, the nodes get identified with the sites of the
     lattice and the edges signal the neighbor status of two sites. If the
-    corresponding nodes are connected, the sites will be neighbors.\\
+    corresponding nodes are connected, the sites are neighbors.\\
     All here mentioned graph types are \emph{proximity graphs}.
@@
         {
-            \subref{sfig:lunes:def} Lunes, which define where an edge
+            \subref{sfig:lunes:def} Lunes, which define whether an edge
                 exist, of RNG (hatched region) and GG (cross hatched region).
@@
                 RNG and GG works. Here with the lune definition of the GG.
-                The bounding box of the lune which determines which cells have
+                The bounding box of the lune, which determines which cells have
                 to be tested, is marked with thick colored lines.

### 2013-10-04 Tex/chapters/results.tex
Daten mit den Werten der neuen Bootstrap Methode aktualisiert
es hat sich relativ wenig getan, vorherige Beschreibung passt immer
noch so gut, wie vorher
markierung von T_c hinzugefügt
Erscheinungsbild der Tabellen konsistenter
alle Werte gleiche Anzahl an Nachkommastellen
Rechtschreibfehler und so

@@
     The errors of fit parameters are the asymptotic standard errors as calculated
-    by gnuplot divded by root of the chi-squared per degree of freedom
+    by gnuplot divded by the root of the chi-squared per degree of freedom
     as stated in \cite{young2012everything}. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
@@
             \subref{fig:autocorr:powerLaw} the system size $L$. Plotted on
-                double logarithmic axis with a power law fit \(\tau \propto L^z\) (dotted line)
+                double logarithmic axis with a power law fit \(\tau \propto L^{z'}\) (dotted line)
                 to determine the dynamical exponent \(z'\).
@@
     This is of course only a rough analysis of existing data which was
-    generated for another purpose. For a more detailed inspection, one
-    would perform the simulation at the critical point, which will be
+    generated for another purpose. For a more detailed inspection one
+    would perform the simulation at the critical point which will be
     determined subsequently.
@@
             The \(L=16\) curve is much less steep than the \(L=128\) curve.
-            Note that the \(L=\infty\) curve has not an infinite slope but
-            follows a power law function near \(T_c\).
+            Note that the \(L=\infty\) curve follows a power law function near \(T_c\).
         }
@@
     the specific heat \(c\) for the two dimensional Ising model is nominally \(\alpha = 0\),
-    because \(c\) diverges logarithmically and not exponentially.
+    because \(c\) diverges logarithmically and not following a power law.
     For that reason, \(\alpha\) will not be considered in this section.\\
@@
     is illustrated in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.
-    The same principle can be used to determine the other two exponents.
     Note that \(L=16\) is not used for the collapse, because it is a
@@
     to determine the exponents \(\beta\) and \(\nu\).
-    Also the collapse of the binder cumulant, as mentioned before and shown
+    Also the collapse of the Binder cumulant, as mentioned before and shown
     in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0},
     is used to get a further estimate of \(\nu\).
-    \begin{figure}[htbp]
+    \begin{figure}[htb]
         \centering
@@
             \subref{sfig:gettingCrit:s_1_sus} The susceptibility \(\chi\)
-                of an Ising model on an RNG at \(\sigma=1\).
+                of an Ising model on RNG at \(\sigma=1\).
             \subref{sfig:gettingCrit:collapse_s_1_sus} data collapse, to determine \(\gamma\) (for error estimates see Tab.\ \ref{tab:critExp}).
             \subref{sfig:gettingCrit:s_1_meanM} The mean magnetization \(\avg{\abs{m}}\)
-                of an Ising model on an GG at \(\sigma=1\).
+                of an Ising model on GG at \(\sigma=1\).
             \subref{sfig:gettingCrit:collapse_s_1_meanM} data collapse, to determine \(\beta\) (for error estimates see Tab.\ \ref{tab:critExp}).
@@
             \midrule
-            RNG          & 0.0 & 2.2689(7)& 0.992(11)& 1.740(2) & 0.130(1) \\
-                         & 0.1 & 2.2058(8)& 0.987(12)& 1.746(5) & 0.133(4) \\
-                         & 0.2 & 1.627(2) & 1.010(9) & 1.756(14)& 0.123(10)\\
-                         & 0.5 & 1.2825(7)& 1.010(16)& 1.750(16)& 0.143(13)\\
-                         & 1.0 & 1.2123(3)& 1.013(6) & 1.758(16)& 0.138(13)\\
+            RNG          & 0.0 & 2.2688(7) & 0.997(11)& 1.737(3) & 0.131(1) \\
+                         & 0.1 & 2.2053(6) & 0.994(10)& 1.745(5) & 0.128(3) \\
+                         & 0.2 & 1.6265(19)& 1.017(16)& 1.758(14)& 0.157(12)\\
+                         & 0.5 & 1.2825(9) & 1.011(18)& 1.746(16)& 0.146(13)\\
+                         & 1.0 & 1.2125(5) & 1.010(2) & 1.764(14)& 0.133(12)\\
             \midrule
-            GG           & 0.0 & 2.2687(5)& 0.998(8) & 1.735(2) & 0.1262(4)\\
-                         & 0.1 & 2.895(4) & 0.999(19)& 1.744(5) & 0.133(6) \\
-                         & 0.3 & 2.527(1) & 1.029(30)& 1.724(16)& 0.129(12)\\
-                         & 0.5 & 2.238(1) & 1.006(5) & 1.750(12)& 0.125(13)\\
-                         & 1.0 & 2.128(2) & 1.038(32)& 1.743(17)& 0.123(16)\\
+            GG           & 0.0 & 2.2688(6) & 0.999(13)& 1.739(3) & 0.128(1)\\
+                         & 0.1 & 2.8944(43)& 1.001(12)& 1.745(6) & 0.135(6) \\
+                         & 0.3 & 2.5281(27)& 1.034(29)& 1.718(15)& 0.118(11)\\
+                         & 0.5 & 2.2388(9) & 1.006(5) & 1.747(12)& 0.125(11)\\
+                         & 1.0 & 2.1275(20)& 1.036(31)& 1.750(16)& 0.125(15)\\
 
@@
     degree 4, which has to be restricted to the vincinity of \(T_c\) to
-    yield meaningful results.
+    yield meaningful results. An even better method would be the
+    \emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
+    But the simple cubic spline interpolation seems to deliver results
+    that are good enough, because the temperatures of the measurements are
+    sufficiently near to each other. Also cubic spline interpolation is
+    far easier to obtain.
     \begin{figure}[htbp]
@@
             (the errorbars are too small to see).
+            The vertical line marks the known critical temperature for the
+            square lattice Ising model \(T_{c} = 2.2691...\).
         }
@@
         \center
-        \begin{tabular}{l l l l l}
+        \begin{tabular}{l l@{}l l@{}l l@{}l l@{}l}
             \toprule
-             & \multicolumn{2}{c}{RNG} & \multicolumn{2}{c}{GG}\\
-            \cmidrule(rl){2-3} \cmidrule(rl){4-5}
-            \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)}\\
+             & \multicolumn{4}{c}{RNG} & \multicolumn{4}{c}{GG}\\
+            \cmidrule(rl){2-5} \cmidrule(rl){6-9}
+            \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{2}{c}{\(T_c\)} & \multicolumn{2}{c}{\(T_c^{\mathrm{collapse}}\)} & \multicolumn{2}{c}{\(T_c\)} & \multicolumn{2}{c}{\(T_c^{\mathrm{collapse}}\)}\\
             \midrule
-            0.00 & 2.2690(2)& 2.2689(7)& 2.2689(2)& 2.2687(5)\\
-            0.03 & 2.2679(4)&          & 2.851(1) &         \\
-            0.05 & 2.2662(5)&          & 2.863(1) &         \\
-            0.08 & 2.2548(6)&          & 2.882(2) &         \\
-            0.10 & 2.205(1) & 2.2058(8)& 2.893(2) & 2.895(4)\\
-            0.12 & 2.1010(5)&          & 2.903(3) &         \\
-            0.15 & 1.898(2) &          & 2.903(3) &         \\
-            0.20 & 1.624(1) & 1.627(2) & 2.8274(6)&         \\
-            0.25 & 1.4812(5)&          & 2.676(2) &         \\
-            0.30 & 1.407(2) &          & 2.526(4) & 2.527(1)\\
-            0.40 & 1.327(4) &          & 2.332(4) &         \\
-            0.50 & 1.2818(2)& 1.2825(7)& 2.233(7) & 2.238(1)\\
-            0.60 & 1.252(2) &          & 2.183(3) &         \\
-            0.70 & 1.234(1) &          & 2.154(8) &         \\
-            0.80 & 1.223(1) &          & 2.140(3) &         \\
-            0.90 & 1.214(4) &          & 2.132(1) &         \\
-            1.00 & 1.208(5) & 1.2123(3)& 2.121(8) & 2.128(2)\\
-            1.10 & 1.206(1) &          & 2.116(11)&         \\
-            1.20 & 1.204(2) &          & 2.113(4) &         \\
+            0.00 & 2.2689& (2)& 2.2688&(7) & 2.2689& (2) & 2.2688&(6) \\
+            0.03 & 2.2679& (3)&       &    & 2.8510& (7) &       &    \\
+            0.05 & 2.2661& (5)&       &    & 2.8629&(10) &       &    \\
+            0.08 & 2.2548& (5)&       &    & 2.8824&(17) &       &    \\
+            0.10 & 2.2049& (9)& 2.2053&(6) & 2.8933&(22) & 2.8944&(43)\\
+            0.12 & 2.1012& (4)&       &    & 2.9034&(20) &       &    \\
+            0.15 & 1.8980&(21)&       &    & 2.9036&(21) &       &    \\
+            0.20 & 1.6239&(21)& 1.6265&(19)& 2.8272&(12) &       &    \\
+            0.25 & 1.4816& (7)&       &    & 2.6760&(21) &       &    \\
+            0.30 & 1.4071&(20)&       &    & 2.5260&(51) & 2.5281&(27)\\
+            0.40 & 1.3267&(28)&       &    & 2.3317&(44) &       &    \\
+            0.50 & 1.2817& (2)& 1.2825&(9) & 2.2322&(83) & 2.2388&(9) \\
+            0.60 & 1.2519&(16)&       &    & 2.1841&(26) &       &    \\
+            0.70 & 1.2337&(14)&       &    & 2.1540&(79) &       &    \\
+            0.80 & 1.2224&(16)&       &    & 2.1410&(19) &       &    \\
+            0.90 & 1.2142&(35)&       &    & 2.1320& (5) &       &    \\
+            1.00 & 1.2083&(48)& 1.2125&(5) & 2.1208&(82) & 2.1275&(20)\\
+            1.10 & 1.2055&(15)&       &    & 2.1164&(85) &       &    \\
+            1.20 & 1.2034&(12)&       &    & 2.1133&(45) &       &    \\
             \bottomrule
@@
             types, GG and RNG. \(T_c^{\mathrm{collapse}}\) denotes the
-            values of \(T_c\) which were determined before via finte
-            size scaling analysis. The other values are determined by
-            the intersection of the binder cumulants \(g\) for different
-            system sizes. The values of both methods match.
+            values of \(T_c\) which were determined before via finte-size
+            scaling analysis. The other values are determined by
+            the intersections of the Binder cumulants \(g\) for different
+            the intersections of the Binder cumulants \(g\) for different
+            system sizes. The values of both methods match within errorbars.
         }
@@
     The values obtained through the data collapse and the values obtained
-    through the intersection of the binder cumulant are always in good
+    through the intersections of the Binder cumulants are always in good
     agreement and of comparable precision.\\
@@
         %~ errorbars suggest that they are sufficiently precise for this purpose.
-        \begin{figure}[htb]
-            \centering
-            \includegraphics[width=0.45\textwidth]{plots/Tc_K}
-            \caption[Critical Temperature as a Function of the Degree of the Graph]
-            {
-                The critical temperature is plotted as a function of the
-                degree. At \(K \approx 4\) the jump also seen in Fig.\ \ref{fig:Tc} occurs.
-                There seems to be an in first approximation linear
-                dependency. The dotted lines are fits to a power law function \(T_c = aK^b\)
-                ignoring the point at \(K=4\) on the GG.
-                As a approximation it seems suited but the bad
-                \(\chi^2\) values are hints that there is some finer
-                structure which is not fitted by a power law function.
-                This is further examined in Fig.\ \ref{fig:Tc_deg}.
-            }
-            \label{fig:Tc_K}
-        \end{figure}\\
-        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
-        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
-        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
-        seem to indicate that this is only a approximation which does not
-        account for every detail of the curve. These details will be
-        investigated.\\
         It seems reasonable to normalize \(T_c\) by the degree of the underlying
@@
         but is still existent.\\
-        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
-        the normalization is done using power law function obtained through the fit from Fig.\ \ref{fig:Tc_K}.
-        The amplitude of the curve shrinks which is a hint, that this is a good
-        approximation. But it is not a constant, so there have to be other
-        influences as supposed before.
-        Note that even after the normalization, the values of \(T_c / K\)
-        for the RNG are smaller than those for the GG.\\
-        Anyway, this analysis shows that the degree has a major impact on
-        the critical temperature \(T_c\), but it also shows that there
-        have to be other graph properties having a minor influence on \(T_{c}\).
         \begin{figure}[htbp]
@@
             \label{fig:Tc_deg}
+        \end{figure}\\
+        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
+        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
+        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
+        seem to indicate that this is only an approximation which does not
+        account for every detail of the curve. These details will be
+        investigated.\\
+        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
+        the normalization is done using the power law function obtained through the fit from Fig.\ \ref{fig:Tc_K}.
+        The amplitude of the curve shrinks which is a hint, that this is a good
+        approximation. But it is not a constant, so there have to be other
+        influences as supposed before.
+        Note that even after the normalization, the values of \(T_c / K\)
+        for the RNG are smaller than those for the GG.\\
+        Anyway, this analysis shows that the degree has a major impact on
+        the critical temperature \(T_c\), but it also shows that there
+        have to be other graph properties having a minor influence on \(T_{c}\).
+        \begin{figure}[htb]
+            \centering
+            \includegraphics[width=0.45\textwidth]{plots/Tc_K}
+            \caption[Critical Temperature as a Function of the Degree of the Graph]
+            {
+                The critical temperature is plotted as a function of the
+                degree. At \(K \approx 4\) the jump also seen in Fig.\ \ref{fig:Tc} occurs.
+                There seems to be an in first approximation linear
+                dependency. The dotted lines are fits to a power law function \(T_c = aK^b\)
+                ignoring the point at \(K=4\) on the GG.
+                As an approximation it seems suited but the bad
+                \(\chi^2\) values are hints that there is some finer
+                structure which is not fitted by a power law function.
+                This is further examined in Fig.\ \ref{fig:Tc_deg}.
+            }
+            \label{fig:Tc_K}
         \end{figure}\\

### 2013-10-04 Tex/chapters/appendix.tex
Korrekturen von Rechtschreib- und Formulierungsfehlern

@@
     the maximum moves to the critical temperature with larger \(L\).\\
-    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:logL} the maxima of a
-    cubic spline interpolation of \(c\) is plotted. Note that no errorbars
-    are estimated. As mentioned before,
+    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:logL} the maxima of the
+    cubic spline interpolation of \(c\) are plotted as a function of the
+    system size \(L\). Note that no errorbars
+    are estimated. As mentioned before
     this maximum increases logarithmically. One sees that a logarithmic
@@
             at \(\sigma = 0\). Dotted lines are guides to the eye.
-            \subref{sfig:smeared_out_appendix:logL} maxima of \(c\) fitted
+            \subref{sfig:smeared_out_appendix:logL} Maxima of \(c\) fitted
             with a power law function and a logarithm.

### 2013-10-04 Tex/chapters/conclusion.tex
Korrekturen von Rechtschreib- und Formulierungsfehlern

--- 2013-09-25 Tex/chapters/conclusion.tex
@@
 ferromagnet. Its critical temperature decreases with increasing disorder
-on a RNG. The reason is that the decreasing average coordination number
-of the underlying graph lowers the resistance to spin flips within
-strongly polarized configurations at low temperatures.
+on a RNG.
 On a GG \(T_c\) first jumps, increases up to a maximum and decreases
@@
 graphs of the respective type. The course of the critical temperatures
-can be made plausible observing the degree of the underlying graph, an
-approximate analytic statement as reason for the observed behavior was
-also presented.
+can be made plausible observing the degree of the underlying graph.
+The decreasing average coordination number
+of the underlying graph lowers the resistance to spin flips within
+strongly polarized configurations at low temperatures.
+An approximation of the critical temperature from the degree of the graph
+an the type of the graph was given.
 
 \subsection{Outlook}
-    The behavior of the normalized critical temperatures in dependence
-    on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
-    are qualitatively similar to each other. One could study the behavior
-    of other proximity graphs like the minimum spanning tree or the
-    Delaunay triangulation to examine if it is also similar.\\
+    The curves of an \(T(K)\) plot for the RNG and GG are distinct. One
+    could study the behavior of other proximity graphs like the minimum
+    spanning tree or the Delaunay triangulation to examine if their critical
+    temperatures would fall on other curves or lie on the curve of e.g.\ the RNG.\\
+    Also the approach of investigating the Binder Cumulant as a function
+    of the correlation length \(g(\xi)\), which is more
+    sensitive detecting nonuniversalities\cite{Hartmann2013}, could be considered.\\
+    It would also be interesting if one could find a better approximation
+    of \(T_c\) considering not only the degree but also other graph
+    properties like the mean edge length or edge weight.

### 2013-10-04 Tex/chapters/results.tex
Korrekturen von Rechtschreib- und Formulierungsfehlern

@@
             the intersections of the Binder cumulants \(g\) for different
-            the intersections of the Binder cumulants \(g\) for different
             system sizes. The values of both methods match within errorbars.
@@
         \label{tab:critTemp}
-    \end{table}\\
-    The values obtained through the data collapse and the values obtained
-    through the intersections of the Binder cumulants are always in good
-    agreement and of comparable precision.\\
-    These values of \(T_c\) are plotted as a function of \(\sigma\) in Fig.\ \ref{fig:Tc}.
-    \begin{figure}[htbp]
+    \end{table}
+    \begin{figure}[h!]
         \centering
@@
     \end{figure}\\
+    The values obtained through the data collapse and the values obtained
+    through the intersections of the Binder cumulants are always in good
+    agreement and of comparable precision. These values of \(T_c\) are
+    plotted as a function of \(\sigma\) in Fig.\ \ref{fig:Tc}.
     One sees that the RNG on the left has generally a lower critical
@@
             }
-            \subfigure[][]
-            {
-                \label{sfig:Tc_norm_deg_fit:RNG}
-                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_fit}
-            }
-            \subfigure[][]
-            {
-                \label{sfig:Tc_norm_deg_fit:GG}
-                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_fit}
-            }
 
@@
             {
-                Top: Degree \(K\) of graph over different
+                Top: Degree \(K\) of the graph over different
                 disorder parameters \(\sigma\) for
@@
                 \subref{sfig:deg:GG} the GG.
-                Middle: Critical temperatures normalized by degree over different
+                Bottom: Critical temperatures normalized by degree over different
                 disorder parameters for
@@
                 \subref{sfig:Tc_norm_deg:GG} the GG.
-                Bottom: Critical temperatures normalized by the in Fig.\ \ref{fig:Tc_K}
+            }
+            \label{fig:Tc_deg}
+        \end{figure}\\
+        The great influence of \(K\) on \(T_c\) becomes even more obvious
+        by plotting \(T_{c}\) as a function of \(K\) as done in Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}.
+        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
+        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
+        seem to indicate that this is only an approximation which does not
+        account for every detail of the curve. These details will be
+        investigated.\\
+        In Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
+        the normalization is done using the power law function obtained through the fit from Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}.
+        The amplitude of the curve shrinks which is a hint, that this is a good
+        approximation. But it is not a constant, so there have to be other
+        influences as supposed before.
+        Note that even after the normalization, the values of \(T_c / K\)
+        for the RNG are smaller than those for the GG.\\
+        \begin{figure}[htbp]
+            %~ \centering
+            \subfigure[][]
+            {
+                \label{sfig:Tc_K}
+                \includegraphics[width=0.45\textwidth]{plots/Tc_K}
+            }
+
+            \subfigure[][]
+            {
+                \label{sfig:Tc_norm_deg_fit:RNG}
+                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_fit}
+            }
+            \subfigure[][]
+            {
+                \label{sfig:Tc_norm_deg_fit:GG}
+                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_fit}
+            }
+
+            \caption[Critical Temperature Normalized by Degree of the Graph]
+            {
+                \subref{sfig:Tc_K} The critical temperature is plotted as a function of the
+                degree. At \(K \approx 4\) the jump also seen in Fig.\ \ref{fig:Tc} occurs.
+                There seems to be an in first approximation linear
+                dependency. The dotted lines are fits to a power law function \(T_c = aK^b\)
+                ignoring the point at \(K=4\) on the GG.
+                As an approximation it seems suited but the bad
+                \(\chi^2\) values are hints that there is some finer
+                structure which is not fitted by a power law function.
+                This is further examined in \subref{sfig:Tc_norm_deg_fit:RNG}
+                and \subref{sfig:Tc_norm_deg_fit:GG} where the
+                critical temperatures are normalized by the
                 determined power law function over different
@@
             }
-            \label{fig:Tc_deg}
-        \end{figure}\\
-        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
-        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
-        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
-        seem to indicate that this is only an approximation which does not
-        account for every detail of the curve. These details will be
-        investigated.\\
-        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
-        the normalization is done using the power law function obtained through the fit from Fig.\ \ref{fig:Tc_K}.
-        The amplitude of the curve shrinks which is a hint, that this is a good
-        approximation. But it is not a constant, so there have to be other
-        influences as supposed before.
-        Note that even after the normalization, the values of \(T_c / K\)
-        for the RNG are smaller than those for the GG.\\
+            \label{fig:Tc_deg_fit}
+        \end{figure}\\
         Anyway, this analysis shows that the degree has a major impact on
@@
         have to be other graph properties having a minor influence on \(T_{c}\).
-        \begin{figure}[htb]
-            \centering
-            \includegraphics[width=0.45\textwidth]{plots/Tc_K}
-            \caption[Critical Temperature as a Function of the Degree of the Graph]
-            {
-                The critical temperature is plotted as a function of the
-                degree. At \(K \approx 4\) the jump also seen in Fig.\ \ref{fig:Tc} occurs.
-                There seems to be an in first approximation linear
-                dependency. The dotted lines are fits to a power law function \(T_c = aK^b\)
-                ignoring the point at \(K=4\) on the GG.
-                As an approximation it seems suited but the bad
-                \(\chi^2\) values are hints that there is some finer
-                structure which is not fitted by a power law function.
-                This is further examined in Fig.\ \ref{fig:Tc_deg}.
-            }
-            \label{fig:Tc_K}
-        \end{figure}\\
+        The most promising candidate is the coupling constant \(J_{i,j}\), i.e.\ the
+        distance of the nodes of the graph.
+        Also the fact that the fits for the RNG and the GG yield other exponents,
+        i.e.\ they are on different lines, proofs that the graph type has
+        also an major influence beyond the degree.\\
         To understand the jump of \(T_c\) on a GG it seems to be necessary to
@@
         The evolution of the RNG with increasing \(\sigma\) can be made plausible
-        with the same arguments. Fig. \ref{fig:RNG_sigma}
+        with the same arguments. Fig.\ \ref{fig:RNG_sigma}
         shows that for \(\sigma \lesssim 0.1\) the square lattice character is
@@
         there is a less obvious dependency between \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
-        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_K}).
+        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}.).
         \begin{figure}[htbp]
@@
                 average edge weight. The curve shows a less straight line
-                than Fig.\ \ref{fig:Tc_K}.
+                than Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}..
             }
@@
         (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
-        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
+        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:GG}
         for variable \(J\) with \(\alpha=0.5\). This suggests that the

### 2013-10-08 Tex/chapters/results.tex
Überflüssigen Punkt entfernt
Letzter Schliff

@@
         \label{fig:autocorr}
-    \end{figure}
-    The plateau at low temperatures is easy to understand considering the
-    effects of the Wolff cluster algorithm. At low temperatures it flips nearly every
-    spin in every step, thus the autocorrelation time is one sweep.
-    (Note that this is not the only explanation for the small values of \(\tau\).
-    The parallel tempering algorithm swaps spin configurations
-    with possibly different signs, thus having the same effect.)
+    \end{figure}\\
+    %~ The plateau at low temperatures is easy to understand considering the
+    %~ effects of the Wolff cluster algorithm. At low temperatures it flips nearly every
+    %~ spin in every step.
     Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
@@
     Anyhow, Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
-    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
+    proofs the effectiveness of the Wolff cluster algorithm at criticality.
+    Also note that this is not the only explanation for the small values of \(\tau\).
+    The parallel tempering algorithm swaps often spin configurations
+    which are uncorrelated, this in turn decreases \(\tau\).\\
     This is of course only a rough analysis of existing data which was
@@
             The \(L=16\) curve is much less steep than the \(L=128\) curve.
-            Note that the \(L=\infty\) curve follows a power law function near \(T_c\).
+            Note that the \(L=\infty\) curve follows a power law function near \(T_c\) for \(T < T_{c}\).
         }
@@
                 average edge weight. The curve shows a less straight line
-                than Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}..
+                than Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}.
             }

### 2013-11-14 Tex/paper.tex
Gerüst für ein Paper auf alter infrastruktur

\documentclass[a4paper,headsepline,bibtotocnumbered,12pt,titlepage,twoside]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[english]{babel}

\usepackage{graphicx}
\usepackage{upgreek}
\usepackage{float}
\usepackage{units}
\usepackage{url}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}

\usepackage{longtable}

\usepackage[FIGTOPCAP,tight,raggedright,nooneline]{subfigure}
\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}

\usepackage[automark]{scrpage2}
\pagestyle{scrheadings}
\clearscrheadfoot
\ohead{\pagemark}
\ihead{\headmark}
\usepackage{setspace}
\linespread{1.25}
\usepackage{geometry}
%~ \geometry{a4paper, top=21mm, left=30mm, right=30mm, bottom=21mm,
          %~ headsep=10mm, footskip=12mm}
\geometry{a4paper, top=21mm, bottom=21mm, headsep=10mm, footskip=12mm}

\addtokomafont{sectioning}{\rmfamily}
\usepackage[bf]{caption}
\captionsetup{format=plain}
\setlength{\parindent}{0pt}
\fussy

\newcommand{\change}[1]{{#1}}

\usepackage{ae}
\usepackage{booktabs}

\usepackage{tikz}
\usetikzlibrary{patterns}

%\abs{Ausdruck} %Betragsstriche, die skalieren - abgekürzt
\newcommand{\abs}[1]{\ensuremath{\left\vert#1\right\vert}}
% und das gleiche füur große Klammern
\newcommand{\brac}[1]{\ensuremath{\left(#1\right)}}
% Erwartungswert skalierend
\newcommand{\avg}[1]{\left< #1 \right>}
% ein nicht kursives d für Ableitungen/Integrale, mit etwas Platz davor, um sich etwas abzusetzten
\newcommand{\de}{\ensuremath{\,\mathrm{d}}}
% Für Einheiten: schreibt sie nicht kursiv und lässt etwas Platz zur Zahl vorher
\newcommand{\eh}[1]{\ensuremath{\,\mathrm{#1}}}
% einfaches Gradzeichen
\newcommand{\gr}{\ensuremath{^{\circ}}}
% Fehlerfortpfanzung
% dy/dz * delta z
\newcommand{\fehler}[2]%
{\ensuremath{\abs{\frac{\partial #1}{\partial #2}}\cdot \Delta #2}}

\hyphenation{}
\setcounter{lofdepth}{2}

\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}

\begin{document}
    \tableofcontents
    \newpage
    \listoffigures
    \listoftables

    \section{Introduction}
        \input{paper/introduction}

    \section{Model}
        \input{paper/model}

    \section{Methods}
        \input{paper/methods}

    \section{Results}
        \input{paper/results}

    \section{Conclusion}
        \input{paper/conclusion}

    \clearpage
    \pagestyle{empty}
    \input{chapters/acknowledgements}

    \clearpage
    \bibliography{lit}
    \bibliographystyle{alpha}
    %~ \bibliographystyle{amsplain}
\end{document}

### 2013-11-14 spin.c
header Daten korrigiert

@@ -354,7 +354,7 @@ void do_mc_simulation(gs_graph_t **list_of_graphs, const options_t o)
         exit(-1);
     }
     /* Schreibe Header */
-    fprintf(data_out_file, "# N E M R_s chi_0 chi_k # sigma=%.3f # x=%d # L=%d # type=%d # r=%d # <J>=%.6f # d=%.6f # deg=%.6f # sumJ=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, o.percolation, get_mean_weight(list_of_graphs[0]), get_mean_dist(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]), get_sum_weight(list_of_graphs[0]));
+    fprintf(data_out_file, "# N E M chi_0 chi_k # sigma=%.3f # x=%d # L=%d # type=%d # r=%d # <J>=%.6f # d=%.6f # deg=%.6f # sumJ=%.6f # T= ", o.sigma, o.seed, list_of_graphs[0]->L, o.graph_type, o.percolation, get_mean_weight(list_of_graphs[0]), get_mean_dist(list_of_graphs[0]), get_mean_deg(list_of_graphs[0]), get_sum_weight(list_of_graphs[0]));
     for(nT=0;nT<o.num_temps;nT++)
         fprintf(data_out_file, "%.3f, ", list_of_graphs[nT]->T);
     fprintf(data_out_file, "\n");

### 2013-11-21 Tex/paper/abstract.tex
Abstract hinzugefügt, makefile korrigiert

I perform Monte Carlo simulations using a combination of the single spin
flip Metropolis, Wolff Cluster update and Parallel Tempering algorithms
to study determine the critical temperatures of an Ising Ferromagnet on
the Relative Neighborhood graph and Gabriel graph which are subgraphs of
the Delaunay Triangulation and proximity graphs. The graphs are derived
from square lattices which nodes are displaced by a Gaussian distributed
random variable. The coupling is set to be depended on the distance of
the nodes. The deviation of the proximity graph from a square lattice is
governed by the width of the Gaussian distribution \(\sigma\). Because
only the lattice structure and coupling is changed, it is expected that
this model lies within the square lattice Ising Ferromagnet universality
class. This expectation is confirmed.
The critical temperatures are shown to depend mainly on the average degree
and the type of the underlying proximity graph.

### 2013-11-22 Tex/paper.tex
Abstract hinzugefügt, makefile korrigiert
PRB Gerüst für den Artikel
abhängigkeit: REVTeX

@@
-\documentclass[a4paper,headsepline,bibtotocnumbered,12pt,titlepage,twoside]{scrartcl}
-
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-
-\usepackage[english]{babel}
+\documentclass[prl,twocolumn,groupedaddress,showpacs,showkeys,amsmath,amssymb,floatfix]{revtex4-1}
 
 \usepackage{graphicx}
-\usepackage{upgreek}
-\usepackage{float}
-\usepackage{units}
-\usepackage{url}
+\usepackage{dcolumn}
+\usepackage{bm}
 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-
-\usepackage{longtable}
-
-\usepackage[FIGTOPCAP,tight,raggedright,nooneline]{subfigure}
-\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
-
-\usepackage[automark]{scrpage2}
-\pagestyle{scrheadings}
-\clearscrheadfoot
-\ohead{\pagemark}
-\ihead{\headmark}
-\usepackage{setspace}
-\linespread{1.25}
-\usepackage{geometry}
-%~ \geometry{a4paper, top=21mm, left=30mm, right=30mm, bottom=21mm,
-          %~ headsep=10mm, footskip=12mm}
-\geometry{a4paper, top=21mm, bottom=21mm, headsep=10mm, footskip=12mm}
-
-\addtokomafont{sectioning}{\rmfamily}
-\usepackage[bf]{caption}
-\captionsetup{format=plain}
-\setlength{\parindent}{0pt}
-\fussy
-
-\newcommand{\change}[1]{{#1}}
-
-\usepackage{ae}
-\usepackage{booktabs}
-
-\usepackage{tikz}
-\usetikzlibrary{patterns}
-
-%\abs{Ausdruck} %Betragsstriche, die skalieren - abgekürzt
-\newcommand{\abs}[1]{\ensuremath{\left\vert#1\right\vert}}
-% und das gleiche füur große Klammern
-\newcommand{\brac}[1]{\ensuremath{\left(#1\right)}}
-% Erwartungswert skalierend
-\newcommand{\avg}[1]{\left< #1 \right>}
-% ein nicht kursives d für Ableitungen/Integrale, mit etwas Platz davor, um sich etwas abzusetzten
-\newcommand{\de}{\ensuremath{\,\mathrm{d}}}
-% Für Einheiten: schreibt sie nicht kursiv und lässt etwas Platz zur Zahl vorher
-\newcommand{\eh}[1]{\ensuremath{\,\mathrm{#1}}}
-% einfaches Gradzeichen
-\newcommand{\gr}{\ensuremath{^{\circ}}}
-% Fehlerfortpfanzung
-% dy/dz * delta z
-\newcommand{\fehler}[2]%
-{\ensuremath{\abs{\frac{\partial #1}{\partial #2}}\cdot \Delta #2}}
-
-\hyphenation{}
-\setcounter{lofdepth}{2}
-
-\numberwithin{equation}{section}
-\numberwithin{figure}{section}
-\numberwithin{table}{section}
+% \newcommand{\change}[1]{{\bf #1}}
+% \newcommand{\changeAH}[1]{{\bf #1}}
 
 \begin{document}
-    \tableofcontents
-    \newpage
-    \listoffigures
-    \listoftables
+
+    \title{Critical Temperature of the Ising Ferromagnet on from Square Lattices by Site Displacement derived Proximity Graphs}
+    \author{H. Schawe}
+    \email{hendrik.schawe@uni-oldenburg.de}
+    \affiliation{Institut f\"ur Physik, Universit\"at Oldenburg, 26111 Oldenbug, Germany}
+    \date{\today}
+
+    \begin{abstract}
+    \input{paper/abstract}
+    \end{abstract}
+
+    \pacs{64.60.ah}
+    \maketitle
 
@@
 
-    \clearpage
-    \pagestyle{empty}
-    \input{chapters/acknowledgements}
+    \input{paper/acknowledgements}
 
-    \clearpage
     \bibliography{lit}
-    \bibliographystyle{alpha}
-    %~ \bibliographystyle{amsplain}
 \end{document}

### 2013-11-22 Tex/paper/results.tex
PRB Gerüst für den Artikel
abhängigkeit: REVTeX

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
    \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
    \caption[Critical Temperature over Different Disorder Parameters]
    {
        Critical temperatures \(T_c\) over different
        disorder parameters \(\sigma\) for
        Interesting points are the jump and rise of the GG at small
        \(\sigma\) and the plateau on the RNG for small \(\sigma\).
    }
    \label{fig:Tc}
\end{figure}

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=\textwidth]{plots/Binder_over_Correlation_All}
    \caption[Binder Cumulant over two-point finite-size correlation function divided by system size]
    {
        Binder Cumulant over two-point finite-size correlation function
        divided by system size. The datapoints for different system sizes
        are drawn with different symbols, while the datapoints for different
        graph ensembles are drawn with different colors.
        The inset zooms into the plot to show that
        all datapoints fall within errorbars onto one curve.
    }
    \label{fig:binderOverCorr}
\end{figure}

### 2013-11-25 Tex/paper/abstract.tex
Umformulierungen, Korrketuren

@@
-I perform Monte Carlo simulations using a combination of the single spin
-flip Metropolis, Wolff Cluster update and Parallel Tempering algorithms
-to study determine the critical temperatures of an Ising Ferromagnet on
-the Relative Neighborhood graph and Gabriel graph which are subgraphs of
-the Delaunay Triangulation and proximity graphs. The graphs are derived
+Monte Carlo simulations are performed
+to determine the critical temperatures of an Ising Ferromagnet on
+proximity graphs Relative Neighborhood graph and Gabriel graph which are
+subgraphs of the Delaunay Triangulation. The graphs are derived
 from square lattices which nodes are displaced by a Gaussian distributed
-random variable. The coupling is set to be depended on the distance of
+random variable to the limit of a Poisson point process. The coupling is
+set to be depended on the distance of
 the nodes. The deviation of the proximity graph from a square lattice is

### 2013-11-26 Tex/paper/abstract.tex

@@
-Monte Carlo simulations are performed
-to determine the critical temperatures of an Ising Ferromagnet on
-proximity graphs Relative Neighborhood graph and Gabriel graph which are
-subgraphs of the Delaunay Triangulation. The graphs are derived
-from square lattices which nodes are displaced by a Gaussian distributed
-random variable to the limit of a Poisson point process. The coupling is
-set to be depended on the distance of
-the nodes. The deviation of the proximity graph from a square lattice is
-governed by the width of the Gaussian distribution \(\sigma\). Because
-only the lattice structure and coupling is changed, it is expected that
-this model lies within the square lattice Ising Ferromagnet universality
-class. This expectation is confirmed.
+We perform Monte Carlo simulations to determine the critical temperatures
+of an Ising Ferromagnet (IFM) coupled to different types of 2D proximity
+graphs.
+%~ In particular we consider Relative Neighborhood graphs and Gabriel graphs
+%~ which are subgraphs of the Delaunay Triangulation for a given set of points.
+The graphs are derived from square lattices where nodes are displaced by
+a Gaussian distributed random variable.
+%~ The limit of maximal disorder thus corresponds to a Poisson point process.
+The deviation of the proximity graph from a square lattice is
+governed by the width \(\sigma\) of the Gaussian distribution.
+In our model, the coupling strength depends on the euclidian distance
+between the coupled spins.
 The critical temperatures are shown to depend mainly on the average degree
 and the type of the underlying proximity graph.
+We further verify that the model lies within the universality class of
+the 2D IFM.

### 2013-11-26 Tex/paper/abstract.tex
Um Alex' Vorschläge ergänzt

@@
 We perform Monte Carlo simulations to determine the critical temperatures
-of an Ising Ferromagnet (IFM) coupled to different types of 2D proximity
-graphs.
+of an Ising Ferromagnet (IFM) located on the sites of different types of
+2D proximity graphs.
 %~ In particular we consider Relative Neighborhood graphs and Gabriel graphs
@@
 governed by the width \(\sigma\) of the Gaussian distribution.
-In our model, the coupling strength depends on the euclidian distance
+In our model, the coupling strength depends on the Euclidean distance
 between the coupled spins.
+The simulations are carried out on graphs with \(N=16^{2}\) to \(N=128^{2}\)
+nodes utilizing the Wolff cluster algorithm and parallel tempering in a
+wide temperature range around the critical point to measure the Binder Cumulant.
 The critical temperatures are shown to depend mainly on the average degree
@@
 We further verify that the model lies within the universality class of
-the 2D IFM.
+the 2D IFM using finite-size scaling methods.

### 2013-11-28 Tex/paper/model.tex
mit paperangefangen, provisorische Bilder aus tikz, plots leicht verbessert, eigentlich sollten das 3 commits sein

--- 2013-10-04 Tex/chapters/model.tex
@@
 \subsection{The Disordered Ising Model}
-\label{ssec:isingmodel}
-    The examined model is a 2D Ising model.
-    The most common definition of the Ising model, to which will be referred to
-    as the \emph{square lattice Ising model}, is a square lattice with
-    lateral length \(L\) and \(N=L^2\) sites with periodic boundary conditions.
-    Note that \(N\) always refers to the number of sites in this thesis.
-    Each site has a magnetic moment, which is called the spin. Each
-    spin can take a value \(s \in \{-1,+1\}\) and interacts with its
+The model under scrutiny in this article is the \emph{disordered Ising Ferromagnet}
+which is derived from the well understood \emph{square lattice Ising Ferromagnet} \cite{Onsager1944}.
+That is a square lattice with lateral length \(L\) and \(N=L^2\)
+sites with periodic boundary conditions.
+Each site has an Ising spin \(s \in \{-1,+1\}\) and interacts with its
 nearest neighbors described by the Hamiltonian
 \begin{equation}
-        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
+    \mathcal{H} = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
     \label{eq:hamiltonian}
@@
 \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are nearest
-    neighbors, so that they are directly coupled to each other. This will
-    be called an edge. The
-    coupling between \(i\) and \(j\) is characterized by \(J_{ij}\),
-    the coupling constant. If \(J_{ij} > 0 \ \forall \avg{i,j}\) the model resembles a ferromagnet.
-    For the square lattice Ising model \(J_{ij} = 1 \ \forall \avg{i,j}\) applies.\\
-    The most important modification of the square lattice Ising model in this
-    thesis is that the sites of the square lattice are displaced introducing
-    geometric disorder resulting in a non regular graph structure.
+neighbors, so that they are directly coupled to each other.
+This will be called an edge.
+The coupling between \(i\) and \(j\) is characterized by \(J_{ij} = J\),
+the coupling constant.
+
+The most important difference of the square lattice Ising model to the
+disordered Ising Ferromagnet is that the sites of the square lattice are
+displaced introducing geometric disorder resulting in a non regular graph
+structure.
 The displacement is randomly Gaussian distributed with standard
@@
     \centering
-        \input{images/Displacement}
+    \includegraphics[width=0.45\textwidth]{images/displacement}
     \caption[Sketch how the Displacement works]
@@
     \label{fig:displacement}
-    \end{figure}\\
+\end{figure}
 In the following \(\sigma\) will also be called \emph{disorder parameter}.
@@
 the lattice would collapse to many very small clusters. But if one
-    left the edges as the were before the displacement, the edges would
+left the edges as they were before the displacement, the edges would
 cross -- at least for big displacements. The crossing of edges then
@@
 To avoid this, a new edge set will be etablished after the displacement.
-    The edges are constructed according to
-    one of the two in Sec.\ \ref{ssec:graphtypes} defined rules,
+The edges are constructed
 so that for a given configuration of points the resulting graph is an
-    instance of a so called proximity graph. The coupling constant \(J\) gets
-    identified with edge weights. \(J\) will be changed to depend on the
+instance of a so called proximity graph. The coupling constant \(J_{ij}\) gets
+identified with edge weights. \(J_{ij}\) will be changed to depend on the
 geometric distance between the connected pair of sites. More precise,
@@
 \begin{equation}
-        E_{ij} = J_{ij} = \exp (\alpha (1-d_{ij}))
+    E_{ij} = J_{ij} = \mathrm{e}^{(\alpha (1-d_{ij}))}
     \label{eq:coupling}
@@
 connected to nodes near the left edge and vice versa. Analogously the
-    top and bottom edges are connected. One can imagine that the model
-    lives on the surface of a torus as pictured in Fig.\ \ref{fig:torusRNG}.
+top and bottom edges are connected as if the graph lives on a torus.
 In subsequent graphics the graphs will be unwrapped to rectangular
@@
 by edges which connect a solid node to a dashed node.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width=0.45\textwidth]{images/torus}
-        \caption[A Graph on a Torus to Visualise Periodic Boundary Conditions]
-        {
-            A graph on a torus to visualize periodic boundary conditions.
-            On this torus, for a more clear presentation, the underlying
-            graph exhibits a height to width ratio of 1:4. At 1:1 the torus would cut
-            itself. Hence, the torus represents the geometry of the model
-            not perfectly, but gives very quick the right idea.
-            Also the shades are of course only a guide to the eye.
-            This model was created using \texttt{Blender}\footnote{Blender is an open source 3D modelling tool. \url{http://www.blender.org/}}.
-        }
-        \label{fig:torusRNG}
-    \end{figure}\\
 Note that for \(\sigma = 0\) all \(d_{ij} = 1\) and therefore all
 \(J_{ij} = 1\), so that the disordered Ising model is reduced to the
-    square lattice Ising model. For this an analytic solution exists \cite{Onsager1944}.
-    The critical temperature is
-    \begin{equation}
-        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
-        \label{eq:exactTc}
-    \end{equation}
-    and the critical exponents are \(\alpha = 0\), \(\beta = \frac{1}{8}\)
-    and \(\gamma = \frac{7}{4}\). These values are universal for the Ising
-    model. Their meaning will be explained in Sec.\ \ref{ssec:critExp} in more detail.\\
-    The case for randomly distributed sites \(\sigma \gtrsim 1\) is
-    already studied on a Delaunay triangulation. Ref.\ \cite{Janke1994} examines
-    this for constant \(J\) and Ref.\ \cite{Lima2000} for \(J_{ij} = e^{-\alpha d_{ij}}\).
-    Both articles conclude that this model lies within the universality
-    class of the square lattice Ising model, i.e.\ has the same critical
-    exponents, as can be expected since the underlying graph structure can
-    be embedded in 2D. Hence, due to universality it should exhibit the same
-    critical exponents as the basic square lattice Ising ferromagnet.
+square lattice Ising model.
 
+% TODO: alles hierdrunter
 \subsection{Proximity Graphs}
@@
         any other node in its interior, see Ref.\ \cite{Katajainen}.
-        To make this clear the construction of a four node DT is sketched
-        in Fig.\ \ref{fig:def:DT} (see appendix).
 
@@
         called \emph{lune} in the following. See also the cross hatched region
-        from Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.
+        from Fig.\ \ref{fig:lunes}.
 
@@
         circles with radius \(r = d\) and centers on \(i\) and \(j\).
-        See also the hatched region in Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}.
+        See also the hatched region in Fig.\ \ref{fig:lunes}.
 
@@
         \centering
-        \subfigure[Definition of the Lunes][]{
-            \label{sfig:lunes:def}
-            \input{images/GG_RNG_def}
-        }
-        \subfigure[RNG example][]{
-            \label{sfig:lunes:rng}
-            \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
-        }
-        \subfigure[GG example][]{
-            \label{sfig:lunes:gg}
-            \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
-        }
-        \caption[Gabriel - and Relative Neighborhood Graph]
+        \includegraphics[width=0.15\textwidth]{images/GG_RNG_def}
+        \includegraphics[width=0.15\textwidth]{images/RNG/L12S03.pdf}
+        \includegraphics[width=0.15\textwidth]{images/GG/L12S03.pdf}
+        \caption[Gabriel- and Relative Neighborhood Graph]
         {
-            \subref{sfig:lunes:def} Lunes, which define whether an edge
+            Left: Lunes, which define whether an edge
             exist, of RNG (hatched region) and GG (cross hatched region).
@@
             in a GG on the same set of nodes.
-            \subref{sfig:lunes:rng} Example of a RNG on periodic
-                boundary conditions. Periodic nodes are dashed.
-            \subref{sfig:lunes:gg} Example of a GG on
-                periodic boundary conditions. Periodic nodes are dashed.
+            Example of a RNG (center) and GG (right) on periodic boundary conditions.
+            Periodic nodes are dashed.
         }
@@
         \cite{RNGCell} and test the connectedness for each edge contained
-        therein, because the DT is a supergraph of both.
+        therein in \(O (N)\), because the DT is a supergraph of both.
+        This results in a complexity of \(O (N^2 \log N)\)
         For the construction of the DT for a given set of points one might
-        use existing software libraries, e.g.\ the \texttt{qHull}\footnote{\url{http://www.qhull.org}} library.
+        use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.
         However, generation of the graphs is not time critical in the scope
@@
             \centering
-            \subfigure[not Connected Nodes][]{
-                \label{sfig:cell:big}
             \input{images/CellBig}
-            }
-            \subfigure[Connected Nodes][]{
-                \label{sfig:cell:small}
             \input{images/CellSmall}
-            }
             \caption[Sketch how the Cell Method works]
@@
                 to be tested, is marked with thick colored lines.
-                \subref{sfig:cell:big} shows that it is sufficient to find a
+                Left: shows that it is sufficient to find a
                 single node in an inner cell of the bounding box to discard
@@
                 other 8 marked cells do not have to be tested anymore.
-                \subref{sfig:cell:small} shows that only the nodes inside the
+                Right: shows that only the nodes inside the
                 marked cell have to be tested, because there are no other nodes,

### 2013-12-02 Tex/paper/model.tex
Proximity graph abschnitt

@@
 
-% TODO: alles hierdrunter
 \subsection{Proximity Graphs}
 \label{ssec:graphtypes}
-    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E \subset V^{(2)}\). In the
-    scope of this model, the nodes get identified with the sites of the
-    lattice and the edges signal the neighbor status of two sites. If the
-    corresponding nodes are connected, the sites are neighbors.\\
+    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E \subset V^{2}\).
+    In the scope of this model, the nodes get identified with the sites of the
+    lattice. If two nodes are connected by an edge, the sites are neighbors.\\
     All here mentioned graph types are \emph{proximity graphs}.
@@
     lattices with nearest neighbor relationships.
-    In this thesis the distance is always determined by the Euclidean
-    metric in two dimensions, though in principle every metric in any
+    To determine the distance we use the Euclidean
+    metric on two-dimensional graphs, though in principle every metric in any
     dimension can be used.\\
-
-    \subsubsection{Delaunay Triangulation}
-        The Delaunay triangulation (DT) is an undirected graph. An edge
-        between two nodes \(i\) and \(j\) will be drawn, if there exists
-        a circle passing through \(i\) and \(j\), which does not contain
-        any other node in its interior, see Ref.\ \cite{Katajainen}.
 
@@
         The Gabriel graph (GG) \cite{Gabriel1969}
-        is a subgraph of the DT, i.e.\ for the same set of nodes
+        is a subgraph of the Delaunay triangulation (DT) (for a definition
+        see e.g.\ Ref.\ \cite{Katajainen}), i.e.\ for the same set of nodes
         \(V\) the edge set of the DT is a superset of the edge set of the
@@
         called \emph{lune} in the following. See also the cross hatched region
-        from Fig.\ \ref{fig:lunes}.
+        from Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}. An Example is
+        given in Fig.\ ref{fig:lunes}\subref{sfig:lunes:gg}.
 
@@
         circles with radius \(r = d\) and centers on \(i\) and \(j\).
-        See also the hatched region in Fig.\ \ref{fig:lunes}.
+        See also the hatched region in Fig.\ \ref{fig:lunes}. An Example is
+        given in Fig.\ ref{fig:lunes}\subref{sfig:lunes:rng}.
 
@@
         \centering
-        \includegraphics[width=0.15\textwidth]{images/GG_RNG_def}
-        \includegraphics[width=0.15\textwidth]{images/RNG/L12S03.pdf}
-        \includegraphics[width=0.15\textwidth]{images/GG/L12S03.pdf}
-        \caption[Gabriel- and Relative Neighborhood Graph]
+        \subfigure[Definition of the Lunes][]{
+            \label{sfig:lunes:def}
+            \includegraphics[width=0.14\textwidth]{images/GG_RNG_def}
+        }
+        \subfigure[RNG example][]{
+            \label{sfig:lunes:rng}
+            \includegraphics[width=0.14\textwidth]{images/RNG/L12S03.pdf}
+        }
+        \subfigure[GG example][]{
+            \label{sfig:lunes:gg}
+            \includegraphics[width=0.14\textwidth]{images/GG/L12S03.pdf}
+        }
+        \caption[Gabriel - and Relative Neighborhood Graph]
         {
-            Left: Lunes, which define whether an edge
+            \subref{sfig:lunes:def} Lunes, which define whether an edge
                 exist, of RNG (hatched region) and GG (cross hatched region).
@@
                 in a GG on the same set of nodes.
-            Example of a RNG (center) and GG (right) on periodic boundary conditions.
-            Periodic nodes are dashed.
+            \subref{sfig:lunes:rng} Example of a RNG on periodic
+                boundary conditions.
+            \subref{sfig:lunes:gg} Example of a GG on
+                periodic boundary conditions. Periodic nodes are dashed.
         }
@@
 
+    % TODO: alles hierdrunter
     \subsubsection{Construction}
-        In this thesis only GG and RNG are examined.
         The simplest way to construct these graphs is to test for each
@@
         For the construction of the DT for a given set of points one might
-        use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.
-        However, generation of the graphs is not time critical in the scope
-        of this bachelor thesis.\\
+        use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.\\
         So a trade off is to use basically the simple method but only test
@@
             \centering
-            \input{images/CellBig}
-            \input{images/CellSmall}
+            %~ \input{images/CellBig}
+            %~ \input{images/CellSmall}
             \caption[Sketch how the Cell Method works]
@@
         box of their lune and consequently only very few nodes have to be tested.\\
-        Here the number of cells equals the number of nodes.
-        Indeed this method reduced the time needed to construct a RNG with
-        \(N=32^2\) and \(N=64^2\) by a factor of
-        over \(15\) respectively \(40\). Though the complexity is still of
-        order \(O(N^2)\) in the best case, because for every pair at least
-        one check has to be performed.
+        %~ Here the number of cells equals the number of nodes.
+        The complexity of this method should be between \(O(N^2)\) in the
+        best case, because for every pair at least one check has to be performed,
+        and \(O(N^3)\) in the worst case, e.g.\ all nodes are inside one
+        cell.\\
+        Combining both algorithms yields a blazing fast algorithm in complexity
+        \(O(N \log N)\) for nodes which are evenly spread across the cells.\\
+        However, generation of the graphs is not time critical, because
+        the MC simulations take much longer. So only the cell algorithm
+        was used to gegnerate the graphs.\\

### 2013-12-12 Tex/paper/methods.tex
weiter im Text... ist aber noch zu ausführlich

--- 2013-10-04 Tex/chapters/methods.tex
@@
-\subsection{Thermodynamic Theory}
-\label{ssec:theory}
-    The disordered Ising model will be examined as a \emph{canonical system} in
-    \emph{equilibrium}. A canonical system can exchange energy with a
-    heat bath, thus it has a constant temperature equal to the temperature of the
-    heat bath.
-    Equilibrium is defined as a steady state, wherein
-    the observables are only fluctuating but not changing in any
-    particular direction. For example thermal equilibrium denotes the
-    condition that the system under scrutiny has reached the temperature
-    of the heat bath. This is the case once no net energy exchange occurs,
-    thus the energy of the simulated system reaches a steady state, where
-    only fluctuations occur.
-    In a canonical ensemble the probability \(p_\nu\) of a state
-    \(\nu\) is distributed according to a Boltzman distribution
-    \begin{equation}
-        p_\nu = \frac{1}{Z} e^{-\beta H_\nu}
-    \end{equation}
-    \begin{equation}
-        \beta = \frac{1}{k_B T}
-    \end{equation}
-    Where \(Z\) is the partition function, which normalizes \(p_\nu\) to
-    a probability: \(\sum_\nu p_\nu = 1\).
-    Further the free energy \(F\) of a canonical ensemble is minimized
-    in equilibrium and all observables can be derived from \(F\)
-    in a straight forward way, as stated in every textbook about
-    statistical physics (e.g.\ Ref.\ \cite{nolting2005}).\\
-    Because of
-    \begin{equation}
-        F = U - TS
-    \end{equation}
-    where \(S\) is the entropy, \(U=\avg{H}\) the internal energy and
-    \(\avg{\cdot}\) declares the expectation value of an observable.
-    One can guess that for low \(T\) the internal energy
-    will be low, and for high \(T\) the entropy will be high to minimize
-    \(F\).
-    Considering the Hamiltonian of the Ising model, a spin configuration
-    of high order, where most spins are aligned with their neighbors,
-    leads to a low value of \(H\) and therefore a low value of \(U\).
-    Simultaneously, this state of high order corresponds to a low entropy \(S\).
-    Analogically a state of high \(U\) is also a state of high \(S\).
-    These preliminary considerations make a phase transition at some
-    \(T\) where the influence of the entropy on \(F\) becomes the same
-    order of magnitude as the influence of the internal energy on \(F\),
-    very plausible.\\
-    To determine
-    \begin{equation}
-        F=-k_{B}T \ln{Z}
-    \end{equation}
-    one has to know the partition function
-    \begin{equation}
-        Z = \sum_\nu e^{-\beta H_\nu},
-        \label{eq:partitionFunction}
-    \end{equation}
-    where the sum goes over all possible states \(\nu\) of the system.
-    Then averages can be computed according to
-    \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_\nu O_\nu e^{-\beta H_\nu}.
-    \end{equation}
-    Because every site can have two states, there are \(2^N\) different
-    states of the system. For each the energy \(H_\nu\) has to be calculated
-    to solve the sum from Eq.\ \eqref{eq:partitionFunction} to gain \(Z\).
-    Hence for small \(N\) the partition function is computable, but the system
-    may show very different properties than in the thermodynamic limit.
-    To minimize these finite size effects it is desirable to examine
-    systems with large \(N\). But \(2^N\) is a very rapidly increasing
-    number, so for large \(N\) it is unfeasible to calculate the energy for each state, except
-    for cases where it is possible to solve it analytically.\\
-    If not, one can get estimates of the observables for big \(N\) using
-    Monte Carlo simulations, which are introduced in the next chapter.\\
+The results are obtained through Monte Carlo simulations.
+For each sweep \(N\) single spin flip Metropolis updates, one
+Wolff cluster update and one parallel tempering swap are
+performed. These algorithms will be outlined short in the following.\\
+Because it is not known before, where the critical temperatures
+\(T_c\) are located, the Wolff cluster algorithm is used for
+every temperature. Albeit the efficiency of the algorithmic procedure
+was not dissected for every temperature, the speed up
+near criticality should be worth the moderate slow down at other temperatures.
 
-    The observables which are measured in this thesis are the
-    magnetization per spin
-    \begin{equation}
-        m = \frac{1}{N} \sum_i s_i
-    \end{equation}
-    and the energy per spin
-    \begin{equation}
-        E = \frac{1}{N} H.
-    \end{equation}
-    As mentioned before, properties near the phase transition and the
-    critical temperature \(T_c\), where the phase transition occurs, will
-    be examined. The Ising system in two dimensions shows a second order
-    phase transition, hence \(m\) and \(E\) are continous, but show at
-    \(T_c\) an infinitly sharp slope in the thermodynamic limit, i.e.\
-    the first derivative diverges.
-    From statistical physics (See Ref.\ \cite{nolting2005}) it is known that
-    these derivatives can be expressed by fluctuations, e.g.\ the specific
-    heat can be expressed as
-    \begin{equation}
-        c = \frac{\partial \avg{H}}{\partial T} = k_B \beta^2 \avg{\brac{H-\avg{H}}^2}.
-    \end{equation}
-    The specific heat is a measure for how much energy is needed to change
-    the temperature of the system.
-    Analogically the susceptibility
-    \begin{equation}
-        \chi = N \beta \avg{\brac{m-\avg{m}}^2}
-    \end{equation}
-    is a measure for how strong an outer magnetic field changes the
-    magnetization of the system.
-    Beside these observables from classical physics, a fifth observable
-    the Binder cumulant \cite{Binder1981}
-    \begin{equation}
-        g = \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}}
-        \label{eq:binder}
-    \end{equation}
-    is considered.
-    This is a dimensionless value, which can be used to determine the
-    critical point. These five observables will be sufficient to analyse
-    the phase transition in the scope of this bachelor thesis. All of them
-    can be easily computed when \(m\) and \(E\) are measured. The next
-    chapter will show, how to get estimates for them through Monte Carlo
-    simulations.
-
-\subsection{Monte Carlo Simulations}
-\label{ssec:montecarlo}
-    The idea behind Monte Carlo simulations is to take random samples of
-    the observable, which should be measured, and to estimate the mean of
-    the observable from this samples. To apply this technique to statistical
-    ensembles, one creates sample states of the system, measures the
-    observables and calculates the expected value through averaging.\\
-    In statistical physics the expected value of an observable \(O\)
-    is -- as also noted above -- calculated by
-    \begin{equation}
-        \avg{O} = \frac{1}{Z} \sum_\nu p_\nu O_\nu.
-        \label{eq:estim}
-    \end{equation}
-    It is however possible that there are few states contributing
-    massively more than others. In canonical systems at low \(T\)
-    states with low values of \(H\) contribute much more than states with
-    high values of \(H\).
-    But if one samples the \(2^N\) states evenly, it is probable to miss
-    them. This is called \emph{simple sampling} and results in large
-    errorbars for any observable.
-    It is therefore desirable to sample only the states with high
-    contributions to the sum.
-    As noted before, the system under scrutiny is canonical and therefore
-    \(p_\nu\) is known. The states are distributed according to the Boltzmann
-    distribution. Hence \emph{Importance Sampling} can be utilized.\\
-    Instead of sampling uniformly distributed random states, one should sample
-    states according to their occurence probability given by the Boltzmann
-    distribution. In fact this reduces the estimator Eq.\ \eqref{eq:estim} to
-    \begin{equation}
-        O_M = \frac{1}{M} \sum_{\nu=1}^M O_\nu,
-    \end{equation}
-    where \(M\) is the number of samples. The proof is shown in \cite{NewmanBarkema1999}.
-    This is a very convenient form.\\
-    But it is difficult to create a random state of a physical system,
-    e.g.\ the Ising system, according to a given distribution. The simple
-    approach of creating uniformly distributed random states and reject
-    them with probability \(p_\nu^{-1}\) depending on their energy is not
-    efficient, because many generated states will be discarded and the
-    computing time to generate them and calculating their energy will
-    be wasted.
-    Hence one uses \emph{Markov Chains} to generate new states \(\nu\)
-    from former ones \(\mu\). It is important that the transition probabilities
-    \(A(\mu \to \nu)\) obey \emph{Detailed Balance} and \emph{Ergodicity}.
-    \emph{Detailed Balance} means that the probability to leave a state is
-    the same as the probability to enter the state in equilibrium
-    \(p_\mu A(\mu \to \nu) = p_\nu A(\nu \to \mu)\) with \(p_\mu\) the
-    probability to be in state \(\mu\).
-    \emph{Ergodicity} requires that every possible state is reachable
-    from every other state in finite time, see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
-    This ensures that the system can equilibrate and that the states are
-    distributed according to the desired distribution in equilibrium
-    \cite{NewmanBarkema1999}. Otherwise the samples might not be representative
-    for the whole system.\\
-    In this thesis three algorithms, which fulfill all requirements,
-    were used. They will be shortly described in the following subsections.
-    But first equilibration- and autocorrelation time will be discussed.
-
-    \subsubsection{Equilibration- and Autocorrelation Time}
-    \label{sssec:eqtime}
-        To generate states acoording to the Boltzmann distribution at a
-        given temperature \(T\), one starts with an arbitrary state
-        and waits until it reaches thermal \emph{equilibrium}. Because
-        equilibrium is defined as a steady state, one can determine it by
-        observing the change of the observables over the progressing
-        simulation as pictured in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}.
-        The progression of a Monte Carlo simulation is measured in \emph{sweeps},
-        which denote some operation. The count of sweeps until
-        equilibrium is reached, is called \emph{equilibration time} \(t_{eq}\).
-        All measurements should start after this time.\\
-        In Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
-        the equilibrium is reached after approximately \(N_{s} \approx 100\) sweeps for
-        both an initial condition of all spins up and all spins random. It
-        does not harm to double that value to be save. Particularly, because
-        it is a random process, so that there can not be an exact value.
-        \begin{figure}[htbp]
-            \centering
-            \subfigure[Example of an Equilibrating Ising System][]{
-                    \label{sfig:equiandauto:equiE}
-                    \includegraphics[width=0.47\textwidth]{plots/equiE}
-            }
-            \subfigure[Example of the Autocorrelation of an Ising System][]{
-                    \label{sfig:equiandauto:autoM}
-                    \includegraphics[width=0.47\textwidth]{plots/autoM}
-            }
-            \caption[Examples for Equilibration and Autocorrelation]
-            {
-                \subref{sfig:equiandauto:equiE} Example of an Ising system
-                    \(L=64\) reaching thermal equilibrium at \(T=2.36\) after
-                    approximately \(N_s=100\) sweeps.\\
-                \subref{sfig:equiandauto:autoM} The autocorrelation of an
-                    Ising system \(L=64\) at \(T=2.40\) (only Metropolis
-                    sweeps -- otherwise the decline is too steep to show)
-                    on half logarithmic axis.
-                    The straight line is an exponential fit \(\exp(-t/\tau)\)
-                    with \(\tau = 342(1)\).
-            }
-            \label{fig:equiandauto}
-        \end{figure}\\
-        Because every state is generated from the preceding state, measurements
-        of subsequent states are correlated. To determine when two states
-        are independent, one calculates the normalized autocorrelation function
-        \(\frac{\chi(t)}{\chi(0)}\) with
-        \begin{equation}
-            \chi(t) = \int \mathrm{d} t' \, [m(t') -\avg{m}][m(t'+t)-\avg{m}],
-        \end{equation}
-        which is expected to decay exponentially
-        \(\chi(t) \propto \exp(t/\tau)\). This is visible in the semilogarithmic
-        plot shown in  Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}.
-        To get the autocorrelation time one can either fit an exponential
-        function \(\exp(-t/\tau)\) like in Fig.\ \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
-        or integrate
-        \begin{equation}
-            \tau = \int \frac{\chi(t)}{\chi(0)} \de t.
-            \label{eq:tau}
-        \end{equation}
-        \(\tau\) is an estimate that specifies the time after which two
-        samples are not correlated anymore, see Refs.\ \cite[p. 59ff]{NewmanBarkema1999} \cite[p. 150f]{Katzgraber2011}.
-        To ensure that the error is not underestimated, one should wait
-        \(2\tau\) sweeps between two measurements.
-        The autocorrelation time is dependent on the temperature.
-        For example for the standard Metropolis algorithm the fluctuations
-        are strong at high temperatures and subsequent
-        states are more dissimilar and therefore less correlated than at low
-        temperatures, where less spins are flipping. But the longest
-        autocorrelation times are encountered at the critical temperature.
-        This effect is called \emph{critical slowing down} and is
-        characterized by the \emph{dynamical critical exponent} \(z\)
-        \cite{SwendsenWang1987}. The dependence of the autocorrelation time
-        \(\tau\) on the system size \(L\) is at \(T_{c}\) given by \(\tau \propto L^z\).
-        More general, the power law scaling \(\tau \propto \xi^z\) holds, where
-        \(\xi\) is the \emph{correlation length}. It diverges at
-        \(T_{c}\) and is then limited by the size of the simulated lattice.
-        As mentioned in Sec.\ \ref{sssec:wolff}, the Wolff cluster algorithm
-        decreases \(z\) dramatically. This causes the course of the autocorrelation
-        time in dependence on temperature to change significantly as shown in
-        Sec.\ \ref{ssec:results:autocorr}. Also according to Ref.\ \cite{NewmanBarkema1999}
-        \(z\) is independent of the lattice structure, which ensures that
-        the simulation will benefit from the Wolff cluster algorithm at
-        any \(\sigma\).
-
-    \subsubsection{Single Spin Flip Metropolis Update}
+\subsection{Single Spin Flip Metropolis Update}
     A \emph{Metropolis} Monte Carlo \cite{Metropolis1953} simulation of an
@@
 
-    \subsubsection{Wolff Cluster Update}
+\subsection{Wolff Cluster Update}
 \label{sssec:wolff}
@@
     \end{equation}
-        where \(J\) is the coupling constant (c.f.\ Sec.\ \ref{ssec:isingmodel}).
+    where \(J\) is the coupling constant.
     For every site that is added, the neighboring sites of it are
@@
 
-    \subsubsection{Parallel Tempering}
+\subsection{Parallel Tempering}
     In simulations using \emph{parallel tempering} \cite{ParallelTempering1986}
@@
     swapped periodically with probability \cite[p. 169ff]{NewmanBarkema1999} \cite[p. 155ff]{Katzgraber2011}
-        \begin{equation}
-            P_{\nu,\nu+1}(S_\nu \leftrightarrow S_{\nu+1}) = \min\brac{1,\exp\brac{\brac{E_{\nu+1}-E_\nu}\brac{\frac{1}{T_{\nu+1}}-\frac{1}{T_\nu}}}},
+    \begin{align}
+        \nonumber
+        P_{\nu,\nu+1}&(S_\nu \leftrightarrow S_{\nu+1}) \\
+        &= \min\brac{1,\exp\brac{\brac{E_{\nu+1}-E_\nu}\brac{\frac{1}{T_{\nu+1}}-\frac{1}{T_\nu}}}},
         \label{eq:partemp}
-        \end{equation}
+    \end{align}
     as schematically pictured in Fig.\ \ref{fig:parTemp}\subref{sfig:parTemp:schema}.
@@
             \label{sfig:parTemp:schema}
-                \input{images/parTempSchema}
+            \includegraphics[width=0.22\textwidth]{images/parTempSchema}
         }
@@
             \label{sfig:parTemp:E}
-                \input{images/parTempE}
+            \includegraphics[width=0.22\textwidth]{images/parTempE}
         }
@@
     achieved with parallel tempering.
-
-    \subsubsection{Implementation Details}
-        Here, a mixture of the above three algorithms is used.
-        For each sweep \(N\) single spin flip Metropolis updates, one
-        Wolff cluster update and one parallel tempering swap are
-        performed.\\
-        Because it is not known before, where the critical temperatures
-        \(T_c\) are located, the Wolff cluster algorithm is used for
-        every temperature. Albeit the efficiency of the algorithmic procedure
-        was not dissected for every temperature, I feel that the speed up
-        near criticality is worth the moderate slow down at other temperatures.

### 2013-12-12 Tex/paper/model.tex
TikZ wird standalone gerendert und als Graphik eingefügt
weiter im Text... ist aber noch zu ausführlich

@@
     \centering
-    \includegraphics[width=0.45\textwidth]{images/displacement}
+    \includegraphics[width=0.45\textwidth]{images/Displacement}
     \caption[Sketch how the Displacement works]
@@
         the running time of a straight forward implementation would be of
-        order \(O(N^3)\).\\
-        To reduce the complexity one can first create a DT in complexity \(O (N \log N)\)
-        \cite{RNGCell} and test the connectedness for each edge contained
-        therein in \(O (N)\), because the DT is a supergraph of both.
-        This results in a complexity of \(O (N^2 \log N)\)
-        For the construction of the DT for a given set of points one might
-        use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.\\
-        So a trade off is to use basically the simple method but only test
+        order \(O(N^3)\).
+        To reduce the running time one can basically use this simple method but only test
         the connectedness for nodes which are near to the lune and abort if
@@
         \(L_c \times L_c\) and save for each cell a list with nodes lying
-        inside like presented in Ref.\ \cite{RNGCell} and sketched in Fig.\ \ref{fig:cell}.
-        The implementation of this thesis uses \(M = N\) (\(L_c = 1\)).
+        inside like presented in Ref.\ \cite{RNGCell} for the RNG and sketched in Fig.\ \ref{fig:cell}.
+        For this research \(M = N\) is used.\\
         \begin{figure}[htbp]
             \centering
-            %~ \input{images/CellBig}
-            %~ \input{images/CellSmall}
+            \subfigure[not Connected Nodes][]{
+                \label{sfig:cell:big}
+                \includegraphics[width=0.2\textwidth]{images/CellBig}
+            }
+            \subfigure[Connected Nodes][]{
+                \label{sfig:cell:small}
+                \includegraphics[width=0.2\textwidth]{images/CellSmall}
+            }
             \caption[Sketch how the Cell Method works]
@@
         box of their lune and consequently only very few nodes have to be tested.\\
-        %~ Here the number of cells equals the number of nodes.
         The complexity of this method should be between \(O(N^2)\) in the
@@
         cell.\\
-        Combining both algorithms yields a blazing fast algorithm in complexity
-        \(O(N \log N)\) for nodes which are evenly spread across the cells.\\
+        Note that even faster algorithms exsist for two dimensional RNG and GG, which require to first
+        generate a DT and use the fact, that the RNG and GG are subgraphs.
+        (For the construction of the DT for a given set of points one might
+        use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.)\\
         However, generation of the graphs is not time critical, because
-        the MC simulations take much longer. So only the cell algorithm
+        the MC simulations take much longer. So only the simple cell algorithm
         was used to gegnerate the graphs.\\

### 2013-12-19 Tex/paper/methods.tex
Metropolis entfernt

@@
 The results are obtained through Monte Carlo simulations.
-For each sweep \(N\) single spin flip Metropolis updates, one
-Wolff cluster update and one parallel tempering swap are
-performed. These algorithms will be outlined short in the following.\\
+For each sweep \(N\) single spin flip Metropolis updates \cite{Metropolis1953}, one
+Wolff cluster update \cite{Wolff1989} and one parallel tempering swap \cite{ParallelTempering1986} are
+performed. The latter two algorithms will be outlined short in the following.\\
 Because it is not known before, where the critical temperatures
@@
 near criticality should be worth the moderate slow down at other temperatures.
-
-\subsection{Single Spin Flip Metropolis Update}
-    A \emph{Metropolis} Monte Carlo \cite{Metropolis1953} simulation of an
-    Ising model will choose a random spin, calculate the energy change
-    \begin{equation}
-        \Delta H = H_\nu - H_\mu
-        \label{eq:dH}
-    \end{equation}
-    that would result from a flip of that spin. Where \(\mu\) is the
-    state before the flip and \(\nu\) after the flip. The flip is then executed
-    with the probability
-    \begin{equation}
-        A(\mu \to \nu) =
-        \begin{cases}
-            1                            & \Delta H \le 0 \\
-            \exp{\brac{-\beta \Delta H}} & \Delta H > 0
-        \end{cases}.
-        \label{eq:metropolis}
-    \end{equation}
-    see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
-    So if a transition lowers the energy it will be always done. This
-    results in a high ratio between flipped spins and chosen spins.
-    Therefore it minimizes the calculations needed for a change of
-    the state. Also note that \(\Delta H\) is easy to calculate,
-    because it is only affected by the spin of the neighbors of the
-    chosen site.
 

### 2014-06-14 Tex/paper/model.tex
Struktur leicht geändert, Wichtige Plots aufgenommen

@@
     metric on two-dimensional graphs, though in principle every metric in any
-    dimension can be used.\\
+    dimension can be used.
 
-    \subsubsection{Gabriel Graph}
+    %~ \subsubsection{Gabriel Graph}
         The Gabriel graph (GG) \cite{Gabriel1969}
@@
 
-    \subsubsection{Relative Neighborhood Graph}
+    %~ \subsubsection{Relative Neighborhood Graph}
         The Relative Neighborhood
@@
     % TODO: alles hierdrunter
-    \subsubsection{Construction}
+    %~ \subsubsection{Construction}
         The simplest way to construct these graphs is to test for each

### 2014-06-14 Tex/paper/results.tex
mit paperangefangen, provisorische Bilder aus tikz, plots leicht verbessert, eigentlich sollten das 3 commits sein
Bilder kleiner gemacht
Struktur leicht geändert, Wichtige Plots aufgenommen

@@
-\begin{figure}[hbtp]
+The results are obtained through Monte Carlo simulations.
+For each sweep \(N\) single spin flip Metropolis updates \cite{Metropolis1953}, one
+Wolff cluster update \cite{Wolff1989} and one parallel tempering swap \cite{ParallelTempering1986} are
+performed. The latter two algorithms will be outlined short in the following.\\
+Because it is not known before, where the critical temperatures
+\(T_c\) are located, the Wolff cluster algorithm is used for
+every temperature. Albeit the efficiency of the algorithmic procedure
+was not dissected for every temperature, the speed up
+near criticality should be worth the moderate slow down at other temperatures.
+
+\begin{figure}[htb]
     \centering
-    \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
-    \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
-    \caption[Critical Temperature over Different Disorder Parameters]
+    \includegraphics[width=0.47\textwidth]{plots/collapse_s_1_sus}
+    \caption[Examples of Determining Critical Temperature and Exponents]
     {
-        Critical temperatures \(T_c\) over different
-        disorder parameters \(\sigma\) for
-        Interesting points are the jump and rise of the GG at small
-        \(\sigma\) and the plateau on the RNG for small \(\sigma\).
+        Examples for the method of FSS, which was used
+        to determine the critical exponents \(\nu, \gamma, \beta\) and
+        the critical temperature \(T_c\).
+        data collapse, to determine \(\gamma\).
     }
-    \label{fig:Tc}
+    \label{fig:gettingCrit2}
 \end{figure}
+
+\begin{table}[htbp]
+    \center
+    \begin{tabular}{l l l l l l}
+        \toprule
+         & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
+        \midrule
+        exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & 2.2691... & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
+        \midrule
+        RNG          & 0.0 & 2.2688(7) & 0.997(11)& 1.737(3) & 0.131(1) \\
+                     & 0.1 & 2.2053(6) & 0.994(10)& 1.745(5) & 0.128(3) \\
+                     & 0.2 & 1.6265(19)& 1.017(16)& 1.758(14)& 0.157(12)\\
+                     & 0.5 & 1.2825(9) & 1.011(18)& 1.746(16)& 0.146(13)\\
+                     & 1.0 & 1.2125(5) & 1.010(2) & 1.764(14)& 0.133(12)\\
+        \midrule
+        GG           & 0.0 & 2.2688(6) & 0.999(13)& 1.739(3) & 0.128(1)\\
+                     & 0.1 & 2.8944(43)& 1.001(12)& 1.745(6) & 0.135(6) \\
+                     & 0.3 & 2.5281(27)& 1.034(29)& 1.718(15)& 0.118(11)\\
+                     & 0.5 & 2.2388(9) & 1.006(5) & 1.747(12)& 0.125(11)\\
+                     & 1.0 & 2.1275(20)& 1.036(31)& 1.750(16)& 0.125(15)\\
+
+        \bottomrule
+    \end{tabular}
+    \caption[Critical Exponents for Different $\sigma$]{
+        Critical exponents for different values of \(\sigma\). A finite size
+        scaling analysis was performed to determine the critical
+        exponents \(\beta, \gamma, \nu\) and the critical temperature
+        \(T_c\). The errors for \(\beta\) and \(\gamma\) are estimated
+        by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
+        \(\nu\) and \(T_c\) are the standard deviation of three obtained
+        values through different collapses (see text).
+    }
+    \label{tab:critExp}
+\end{table}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/Binder_over_Correlation_All}
+    \includegraphics[width=.45\textwidth]{plots/Binder_over_Correlation_All}
     \caption[Binder Cumulant over two-point finite-size correlation function divided by system size]
@@
 \end{figure}
+
+\begin{figure*}[hbtp]
+    \centering
+    \includegraphics[scale=0.6]{plots/RNG_Tc} \quad
+    \includegraphics[scale=0.6]{plots/GG_Tc} \quad
+    \includegraphics[scale=0.6]{plots/Tc_K_goodChi}
+    \caption[Critical Temperature over Different Disorder Parameters]
+    {
+        Critical temperatures \(T_c\) over different
+        disorder parameters \(\sigma\) for
+        Interesting points are the jump and rise of the GG at small
+        \(\sigma\) and the plateau on the RNG for small \(\sigma\).
+        Further \(T_c\)  is plotted as a function of the degree.
+        The dotted lines are fits to a power law function \(T_c = aK^b\)
+        ignoring the "bulk" of points in the lower left and upper right, where
+        deviations from the power law become obvious.
+    }
+    \label{fig:Tc}
+\end{figure*}

### 2015-08-31 Tex/paper.tex
Umformulierungen, Korrketuren
mit paperangefangen, provisorische Bilder aus tikz, plots leicht verbessert, eigentlich sollten das 3 commits sein
Proximity graph abschnitt
TikZ wird standalone gerendert und als Graphik eingefügt
weiter im Text... ist aber noch zu ausführlich
Struktur leicht geändert, Wichtige Plots aufgenommen
Paper Entwurf 1. Iteration

@@
-\documentclass[prl,twocolumn,groupedaddress,showpacs,showkeys,amsmath,amssymb,floatfix]{revtex4-1}
+\documentclass[prb,twocolumn,groupedaddress,showpacs,showkeys,amsmath,amssymb,floatfix]{revtex4-1}
 
@@
 \usepackage{bm}
+
+\usepackage{subfigure}
+
+\newcommand{\avg}[1]{\ensuremath{\left< #1 \right>}}
+\newcommand{\avgR}[1]{\ensuremath{\left[ #1 \right] _{\mathrm{avg}}}}
+\newcommand{\abs}[1]{\ensuremath{\left\vert#1\right\vert}}
+\newcommand{\brac}[1]{\ensuremath{\left(#1\right)}}
 
@@
 
-    \title{Critical Temperature of the Ising Ferromagnet on from Square Lattices by Site Displacement derived Proximity Graphs}
-    \author{H. Schawe}
+    \title{Critical Temperature of the Ising Ferromagnet on Proximity Graphs derived from Square Lattices by Site Displacement}
+    \author{Hendrik Schawe}
     \email{hendrik.schawe@uni-oldenburg.de}
+    \author{Christoph Norrenbrock}
+    \email{christoph.norrenbrock@uni-oldenburg.de}
     \affiliation{Institut f\"ur Physik, Universit\"at Oldenburg, 26111 Oldenbug, Germany}
@@
 
-    \pacs{64.60.ah}
+    % TODO: recherchieren und ändern
+    %~ \pacs{64.60.ah}
     \maketitle
@@
 
-    \section{Methods}
-        \input{paper/methods}
-
     \section{Results}
@@
 
+    \section{Acknowledgements}
         \input{paper/acknowledgements}

### 2015-08-31 Tex/paper/conclusion.tex
Paper Entwurf 1. Iteration

\label{sec:conclusion}
This study shows that universality of the Ising model is preserved for
irregular graphs on a wide range of configurations which are intermediate
between the square lattice ising model and a random Poisson point process.
Also the critical temperature was measured over this range and determined
that it shows in first approximation a power law behavior with the mean
number of neighbors as the base and an exponent dependent on the
graph type that defines the neighbor relationships.

[ideas -- have to be formulated better]

The next step would be the extension of this model to three and higher
dimensions, where the used proximity graphs are still well defined. It
would also be worthwhile to study properties of the graph ensembles itself,
because -- to our knowledge -- they are mostly studied in 2D \cite{RNGCell}.

### 2015-08-31 Tex/paper/introduction.tex
Paper Entwurf 1. Iteration

%~ Hallo Welt \cite{Ising1925}
%~ \blindtext
%~ ising wichtig, drosophila und so
%~ Janke und Lima haben das auch gemacht
%~ TODO: mehr finden

[todo: geo und bio cites] \cite{Karp2000} \cite{Santi2005} \cite{Bose2001} \cite{Kuhn2003} \cite{Selander1975} \cite{Sokal1978} \cite{Sokal1980}

The Ising model for a ferromagnet \cite{Ising1925} is
perhaps the most extensive studied model in statistical mechanics.
It consists of spins wich can point up or down and interact with
neighboring spins. It shows a second order phase transition between
a ferromagnetic, i.e.~all spins having the same value, and
paramagnetic phase. While there exist analytic solutions\cite{Onsager1944,Wannier1945}
describing the phase transition for Ising models on
regular lattices in two dimensions, higher dimensional lattices or
non-regular lattices are the domain of Monte Carlo simulations.

Some work \cite{Janke1994,Lima2000,Lima2008} was done to determine
the critcal temperatures and confirm the universality of 2D IFM
where the spins are arranged randomly in the unit square by a
Poisson point process and neighbor relationships are determined by a
Delaunay triangulation to maintain the planarity of the system.
This article extends the former research to other
irregular lattice types closely related to the Delaunay triangulation and
provides an interpolation between the square lattice IFM
and spins distributed randomly in the plane.
For a range of this interpolation the critcal temperatures are determined
and it is confirmed that configurations from this range belong to the
IFM universality class.

In section \ref{ssec:model} the method to distribute the sites of the
irregular lattice and in \ref{ssec:graphtypes} the rules to establish the
bonds between them is explained, section \ref{sec:results} will show the
details and results of our simulations, before section \ref{sec:conclusion}
closes this article with the conclusions and an outlook.

### 2015-08-31 Tex/paper/model.tex
Paper Entwurf 1. Iteration

@@
 \subsection{The Disordered Ising Model}
-The model under scrutiny in this article is the \emph{disordered Ising Ferromagnet}
-which is derived from the well understood \emph{square lattice Ising Ferromagnet} \cite{Onsager1944}.
+\label{ssec:model}
+    We call the model under scrutiny in this article the \emph{disordered IFM}
+    which is derived from the well understood \emph{square lattice IFM} \cite{Onsager1944}.
     That is a square lattice with lateral length \(L\) and \(N=L^2\)
     sites with periodic boundary conditions.
-Each site has an Ising spin \(s \in \{-1,+1\}\) and interacts with its
+    Each site $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
     nearest neighbors described by the Hamiltonian
@@
 
-The most important difference of the square lattice Ising model to the
-disordered Ising Ferromagnet is that the sites of the square lattice are
+    The most important difference of the square lattice IFM to the
+    disordered IFM is that the sites of the square lattice are
     displaced introducing geometric disorder resulting in a non regular graph
@@
     The displacement is randomly Gaussian distributed with standard
-deviation \(\sigma\), i.e.\ the \(x\) and \(y\) coordinates of the
+    deviation \(\sigma\), i.e.~the \(x\) and \(y\) coordinates of the
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
-from a Gaussian distribution
-\begin{equation}
-    f(\Delta x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{\Delta x^2}{2\sigma^2}}.
-    \label{eq:gauss}
-\end{equation}
-This is sketched in Fig.\ \ref{fig:displacement}.
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{images/Displacement}
-    \caption[Sketch how the Displacement works]
-    {
-        Sketch how the displacement of the nodes works. The nodes
-        get displaced by \(\Delta x\) and \(\Delta y\) drawn from the
-        distributions displayed next to the points. The original
-        square lattice is indicated by dashed lines.
-    }
-    \label{fig:displacement}
-\end{figure}
+    from a Gaussian distribution.
+    %~ \begin{equation}
+        %~ f(\Delta x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{\Delta x^2}{2\sigma^2}}.
+        %~ \label{eq:gauss}
+    %~ \end{equation}
+    %~ This is sketched in Fig.\ \ref{fig:displacement}.
+    %~ \begin{figure}[htbp]
+        %~ \centering
+        %~ \includegraphics[width=0.45\textwidth]{images/Displacement}
+        %~ \caption[Sketch how the Displacement works]
+        %~ {
+            %~ Sketch how the displacement of the nodes works. The nodes
+            %~ get displaced by \(\Delta x\) and \(\Delta y\) drawn from the
+            %~ distributions displayed next to the points. The original
+            %~ square lattice is indicated by dashed lines.
+        %~ }
+        %~ \label{fig:displacement}
+    %~ \end{figure}
     In the following \(\sigma\) will also be called \emph{disorder parameter}.
-If we take "nearest neighbor" in the Euclidean meaning, most sites
+    If we take ``nearest neighbor" in the Euclidean meaning, most sites
     will only have one nearest neighbor after the
@@
     would destroy the planar character of the model.
-To avoid this, a new edge set will be etablished after the displacement.
+    To avoid this, a new edge set will be established after the displacement
+    as shown in Fig.~\ref{fig:RNG_sigma} for example.
+    \begin{figure}[htb]
+        \centering
+        \subfigure[$\sigma = 0.09$]
+        {
+            \label{sfig:RNG_sigma:0.09}
+            \includegraphics[width=0.14\textwidth]{images/RNG/out009}
+        }
+        \subfigure[$\sigma = 0.15$]
+        {
+            \label{sfig:RNG_sigma:0.15}
+            \includegraphics[width=0.14\textwidth]{images/RNG/out015}
+        }
+        \subfigure[$\sigma = 0.21$]
+        {
+            \label{sfig:RNG_sigma:0.21}
+            \includegraphics[width=0.14\textwidth]{images/RNG/out021}
+        }
+        \caption[Examples of RNG for different $\sigma$]
+        {
+            Examples of proximity graphs (more precise, Relative Neighborhood
+            graph see Sec. \ref{ssec:graphtypes}) for different $\sigma$.
+            Connections which cross a periodic boundary are indicated
+            by edges which connect a solid node to a dashed node.
+        }
+        \label{fig:RNG_sigma}
+    \end{figure}
     The edges are constructed
     so that for a given configuration of points the resulting graph is an
-instance of a so called proximity graph. The coupling constant \(J_{ij}\) gets
-identified with edge weights. \(J_{ij}\) will be changed to depend on the
+    instance of a so called proximity graph, which will be explained in Sec.~\ref{ssec:graphtypes}.
+    The coupling constant \(J_{ij}\) gets
+    identified with edge weights. \(J_{ij}\) depends on the
     geometric distance between the connected pair of sites. More precise,
@@
     \begin{equation}
-    E_{ij} = J_{ij} = \mathrm{e}^{(\alpha (1-d_{ij}))}
+        E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})}
         \label{eq:coupling}
@@
     where \(d_{ij}\) is the Euclidean
-distance between the nodes \(i\) and \(j\). Following Ref.\ \cite{Lima2000}
+    distance between the nodes \(i\) and \(j\). Following Ref.~\cite{Lima2000}
     the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
-The boundary is periodic, i.e.\ nodes near the right edge can be
-connected to nodes near the left edge and vice versa. Analogously the
-top and bottom edges are connected as if the graph lives on a torus.
-In subsequent graphics the graphs will be unwrapped to rectangular
-shapes. Connections which cross a periodic boundary are indicated
-by edges which connect a solid node to a dashed node.
     Note that for \(\sigma = 0\) all \(d_{ij} = 1\) and therefore all
-\(J_{ij} = 1\), so that the disordered Ising model is reduced to the
-square lattice Ising model.
+    \(J_{ij} = 1\), so that the disordered IFM is reduced to the
+    square lattice IFM.
 
@@
     lattice. If two nodes are connected by an edge, the sites are neighbors.\\
-    All here mentioned graph types are \emph{proximity graphs}.
-    The edges of these graphs connect nodes which are by some metric near
-    to each other.
-    Hence they are suited to generalize problems defined on regular
+    The edges of \emph{proximity graphs} connect nodes which are by some metric near
+    to each other. Hence they are suited to generalize problems defined on regular
     lattices with nearest neighbor relationships.
@@
 
-    %~ \subsubsection{Gabriel Graph}
-        The Gabriel graph (GG) \cite{Gabriel1969}
-        is a subgraph of the Delaunay triangulation (DT) (for a definition
-        see e.g.\ Ref.\ \cite{Katajainen}), i.e.\ for the same set of nodes
-        \(V\) the edge set of the DT is a superset of the edge set of the
-        GG \(E_{DT} \supseteq E_{GG}\). Two nodes \(i\) and \(j\) with distance
-        \(d_{ij}\) will be connected with an edge, if a circle with its
-        center on half way between \(i\) and \(j\) and radius
-        \(r = \frac d 2\) contains no other nodes. This area will be
-        called \emph{lune} in the following. See also the cross hatched region
-        from Fig.\ \ref{fig:lunes}\subref{sfig:lunes:def}. An Example is
-        given in Fig.\ ref{fig:lunes}\subref{sfig:lunes:gg}.
-
-    %~ \subsubsection{Relative Neighborhood Graph}
-        The Relative Neighborhood
-        graph (RNG) \cite{Toussaint1980} is a subgraph of the GG. Two nodes \(i\) and \(j\) with
-        distance \(d_{ij}\) will be connected again, if no other node is in the
-        \emph{lune}, which is different from the lune of the GG. The lune
-        is defined as the intersection of two
-        circles with radius \(r = d\) and centers on \(i\) and \(j\).
-        See also the hatched region in Fig.\ \ref{fig:lunes}. An Example is
-        given in Fig.\ ref{fig:lunes}\subref{sfig:lunes:rng}.
+    The \emph{Relative Neighborhood graph} (RNG) \cite{Toussaint1980} is
+    a proximity graph. Two nodes \(i\) and \(j\) with distance $d_{ij}$
+    will be connected, if no other node is in the \emph {lune}. The lune
+    is defined as the intersection of two circles with radius \(r =
+    d_{ij}\) and centers on \(i\) and \(j\). See also the hatched region
+    in Fig.~\ref{fig:lunes}. An Example is given in Fig.~\ref{sfig:lunes:rng}.
 
@@
         \centering
-        \subfigure[Definition of the Lunes][]{
+        \subfigure[]{
             \label{sfig:lunes:def}
@@
         }
-        \subfigure[RNG example][]{
+        \subfigure[]{
             \label{sfig:lunes:rng}
@@
         }
-        \subfigure[GG example][]{
+        \subfigure[]{
             \label{sfig:lunes:gg}
@@
         }
-        \caption[Gabriel - and Relative Neighborhood Graph]
+        \caption[Gabriel and Relative Neighborhood Graph]
         {
@@
 
+    The \emph{Gabriel graph} (GG) \cite{Gabriel1969} is a subgraph
+    of the Delaunay triangulation \cite{Delaunay1934,Katajainen}
+    (DT), i.e.~for the same set of nodes \(V\) the edge set of the
+    DT is a superset of the edge set of the GG. Two nodes \(i\) and
+    \(j\) with distance \(d_{ij}\) will be connected with an edge,
+    if a circle with its center on half way between \(i\) and \(j\)
+    and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes. See
+    also the cross hatched region from Fig.~\ref{sfig:lunes:def}. An
+    Example is given in Fig.~\ref {sfig:lunes:gg}. Note that the
+    lune of the GG is completely enclosed in the lune of the RNG,
+    therefore the RNG is a subgraph of the GG.
+
+    To construct these graphs there is an algorithm\cite{RNGCell} with
+    a time complexity of \(\mathcal{O}(N \log N)\) for nodes on a two
+    dimensional plane.
+
     % TODO: alles hierdrunter
     %~ \subsubsection{Construction}
-        The simplest way to construct these graphs is to test for each
-        pair of nodes if any other node lies in
-        the lune of the pair. That is of complexity \(O (N^3)\), because
-        there are \(N(N-1)\) pairs and for each \((N-2)\) nodes to test. So
-        the running time of a straight forward implementation would be of
-        order \(O(N^3)\).
-        To reduce the running time one can basically use this simple method but only test
-        the connectedness for nodes which are near to the lune and abort if
-        one node inside the lune is found. To determine which nodes are
-        near the lune one can subdivide the area in \(M\) \emph{cells} of size
-        \(L_c \times L_c\) and save for each cell a list with nodes lying
-        inside like presented in Ref.\ \cite{RNGCell} for the RNG and sketched in Fig.\ \ref{fig:cell}.
-        For this research \(M = N\) is used.\\
-        \begin{figure}[htbp]
-            \centering
-            \subfigure[not Connected Nodes][]{
-                \label{sfig:cell:big}
-                \includegraphics[width=0.2\textwidth]{images/CellBig}
-            }
-            \subfigure[Connected Nodes][]{
-                \label{sfig:cell:small}
-                \includegraphics[width=0.2\textwidth]{images/CellSmall}
-            }
-            \caption[Sketch how the Cell Method works]
-            {
-                Sketch how the cell algorithm for the construction of the
-                RNG and GG works. Here with the lune definition of the GG.
-                The bounding box of the lune, which determines which cells have
-                to be tested, is marked with thick colored lines.
-                Left: shows that it is sufficient to find a
-                single node in an inner cell of the bounding box to discard
-                the edge between two distant nodes. The nodes inside the
-                other 8 marked cells do not have to be tested anymore.
-                Right: shows that only the nodes inside the
-                marked cell have to be tested, because there are no other nodes,
-                the edge can be drawn.
-            }
-            \label{fig:cell}
-        \end{figure}\\
-        Given the discretized cell structure it is just necessary to test the nodes in the cells which
-        resemble a rectangular bounding box of the lune. Most pairs will be
-        far away from each other and there will be one or more cells in the
-        middle of the bounding box, which are completely inside the lune.
-        Then only one node has to be tested from such a cell to discard an
-        edge between the nodes. On the other hand, nodes that will be connected
-        are near to each other so that only very few cells intersect the bounding
-        box of their lune and consequently only very few nodes have to be tested.\\
-        The complexity of this method should be between \(O(N^2)\) in the
-        best case, because for every pair at least one check has to be performed,
-        and \(O(N^3)\) in the worst case, e.g.\ all nodes are inside one
-        cell.\\
-        Note that even faster algorithms exsist for two dimensional RNG and GG, which require to first
-        generate a DT and use the fact, that the RNG and GG are subgraphs.
-        (For the construction of the DT for a given set of points one might
-        use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.)\\
-        However, generation of the graphs is not time critical, because
-        the MC simulations take much longer. So only the simple cell algorithm
-        was used to gegnerate the graphs.\\
+        %~ The simplest way to construct these graphs is to test for each
+        %~ pair of nodes if any other node lies in
+        %~ the lune of the pair. That is of complexity \(O (N^3)\), because
+        %~ there are \(N(N-1)\) pairs and for each \((N-2)\) nodes to test. So
+        %~ the running time of a straight forward implementation would be of
+        %~ order \(O(N^3)\).
+        %~ To reduce the running time one can basically use this simple method but only test
+        %~ the connectedness for nodes which are near to the lune and abort if
+        %~ one node inside the lune is found. To determine which nodes are
+        %~ near the lune one can subdivide the area in \(M\) \emph{cells} of size
+        %~ \(L_c \times L_c\) and save for each cell a list with nodes lying
+        %~ inside like presented in Ref.\ \cite{RNGCell} for the RNG and sketched in Fig.\ \ref{fig:cell}.
+        %~ For this research \(M = N\) is used.\\
+        %~ \begin{figure}[htbp]
+            %~ \centering
+            %~ \subfigure[not Connected Nodes][]{
+                %~ \label{sfig:cell:big}
+                %~ \includegraphics[width=0.2\textwidth]{images/CellBig}
+            %~ }
+            %~ \subfigure[Connected Nodes][]{
+                %~ \label{sfig:cell:small}
+                %~ \includegraphics[width=0.2\textwidth]{images/CellSmall}
+            %~ }
+            %~ \caption[Sketch how the Cell Method works]
+            %~ {
+                %~ Sketch how the cell algorithm for the construction of the
+                %~ RNG and GG works. Here with the lune definition of the GG.
+                %~ The bounding box of the lune, which determines which cells have
+                %~ to be tested, is marked with thick colored lines.
+                %~ Left: shows that it is sufficient to find a
+                %~ single node in an inner cell of the bounding box to discard
+                %~ the edge between two distant nodes. The nodes inside the
+                %~ other 8 marked cells do not have to be tested anymore.
+                %~ Right: shows that only the nodes inside the
+                %~ marked cell have to be tested, because there are no other nodes,
+                %~ the edge can be drawn.
+            %~ }
+            %~ \label{fig:cell}
+        %~ \end{figure}\\
+        %~ Given the discretized cell structure it is just necessary to test the nodes in the cells which
+        %~ resemble a rectangular bounding box of the lune. Most pairs will be
+        %~ far away from each other and there will be one or more cells in the
+        %~ middle of the bounding box, which are completely inside the lune.
+        %~ Then only one node has to be tested from such a cell to discard an
+        %~ edge between the nodes. On the other hand, nodes that will be connected
+        %~ are near to each other so that only very few cells intersect the bounding
+        %~ box of their lune and consequently only very few nodes have to be tested.\\
+        %~ The complexity of this method should be between \(O(N^2)\) in the
+        %~ best case, because for every pair at least one check has to be performed,
+        %~ and \(O(N^3)\) in the worst case, e.g.\ all nodes are inside one
+        %~ cell.\\
+        %~ Note that even faster algorithms exsist for two dimensional RNG and GG, which require to first
+        %~ generate a DT and use the fact, that the RNG and GG are subgraphs.
+        %~ (For the construction of the DT for a given set of points one might
+        %~ use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.)\\
+        %~ However, generation of the graphs is not time critical, because
+        %~ the MC simulations take much longer. So only the simple cell algorithm
+        %~ was used to gegnerate the graphs.\\

### 2015-08-31 Tex/paper/results.tex
Paper Entwurf 1. Iteration

--- 2013-11-22 Tex/paper/results.tex
@@
-\begin{figure}[hbtp]
+\label{sec:results}
+The results are obtained through Monte Carlo simulations. For each
+sweep \(N\) single spin flip Metropolis updates \cite{Metropolis1953},
+one Wolff cluster update \cite{Wolff1989} and one
+parallel tempering swap \cite{ParallelTempering1986} are performed.
+For every systemsize $L \in \{16,32,64,128\}$ and 19 different
+$\sigma \in [0,1.2]$ on $100$ different realizations at least $5000$
+independent measurements are taken in equilibrium.\\
+Because it is not known before, where the critical temperatures \(T_c\)
+are located, the Wolff cluster algorithm is used at every
+temperature. Albeit the efficiency of the algorithmic procedure was
+not dissected for every temperature, the speed up near criticality
+should be worth the moderate slow down at other temperatures.\\
+
+The differences of this model and the 2D IFM are only details,
+it is therefore expected that both are in the same universality class.
+To proof this, the critical exponents are determined by a finite-size
+scaling (FSS) analysis
+using the well kown scaling bahaviors of the magnetization, the susceptiblity and the Binder parameter
+in an automated and reproducable way using the
+\texttt{autoscale.py} \cite{autoscale2009} tool.
+In Fig.~\ref{fig:collapse}
+\begin{figure}[htb]
+    \includegraphics[scale=1]{plots/col_s1_sus}
+    \caption[Examples of Determining Critical Temperature and Exponents]
+    {
+        Example for a collapse of the susceptiblity \(\chi\) on a RNG at
+        \(\sigma = 1\) to get the corresponding critical exponent $\gamma$.
+        The same procedure is used on the Binder parameter $g$ and the
+        magnetization $|m|$ to to determine the critical exponents
+        \(\nu\) and \(\beta\) and the critical temperature \(T_c\).
+        The inset shows the same data with unscaled axes.
+    }
+    \label{fig:collapse}
+\end{figure}
+%~ two examples collapses at $\sigma = 1$ for the
+%~ magnetization
+%~ \[\abs{m} = \avgR{\avg{\abs{\frac{1}{N}\sum_{i=1}^N s_i}}}\]
+ %~ -- with $\avg{\cdot}$ being the thermal average and $\avgR{\cdot}$ being the
+%~ average over the random realizations -- and the susceptiblity
+%~ \[\chi = \frac{N}{T}\brac{\avgR{\avg{m^2}}-\avgR{\avg{m}}^2}\]
+%~ are plotted.
+an example collapse at $\sigma = 1$ for the susceptiblity
+\[\chi = \frac{N}{T}\brac{\avgR{\avg{m^2}}-\avgR{\avg{m}}^2}\]
+with $\avg{\cdot}$ being the thermal average and $\avgR{\cdot}$ being the
+average over the random realizations, is plotted.
+%~ The collapse happens because $\chi$ should scale according to
+%~ \[\chi_L = L^{\gamma / \nu} \tilde{C}\brac{L^{1/\nu}\brac{T-T_c}}\]
+All obtained values for different $\sigma$ are visualized in Tab.~\ref{tab:critExp}
+\begin{table}[htb]
+    \begin{ruledtabular}
+        \begin{tabular}{l l l l l l}
+             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
+            %~ \colrule
+            \hline
+            exact        & 0   & 2.2691... & \(1\)    & \(1.75\) & \(0.125\)\\
+            %~ \colrule
+            \hline
+            RNG          & 0.0 & 2.2688(7) & 1.00(1) & 1.741(2) & 0.125(1) \\
+                         & 0.1 & 2.2053(6) & 0.99(1) & 1.745(5) & 0.128(3) \\
+                         & 0.2 & 1.6265(19)& 1.02(2) & 1.758(14)& 0.122(7)\\
+                         & 0.5 & 1.2825(9) & 1.01(2) & 1.746(16)& 0.128(8)\\
+                         & 1.0 & 1.2125(5) & 1.01(1) & 1.764(14)& 0.125(6)\\
+            %~ \colrule
+            \hline
+            GG           & 0.0 & 2.2688(6) & 1.00(1) & 1.738(22)& 0.127(4)\\
+                         & 0.1 & 2.8944(43)& 1.00(1) & 1.745(6) & 0.135(6) \\
+                         & 0.3 & 2.5281(27)& 1.03(3) & 1.718(15)& 0.118(11)\\
+                         & 0.5 & 2.2388(9) & 1.01(1) & 1.747(12)& 0.125(11)\\
+                         & 1.0 & 2.1275(20)& 1.04(3) & 1.750(16)& 0.125(15)\\
+        \end{tabular}
+    \end{ruledtabular}
+    \caption[Critical Exponents for Different $\sigma$]{
+        Critical exponents for different values of \(\sigma\). A finite size
+        scaling analysis was performed to determine the critical
+        exponents \(\beta, \gamma, \nu\) and the critical temperature
+        \(T_c\). The errors for \(\beta\) and \(\gamma\) are estimated
+        by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
+        \(\nu\) and \(T_c\) are the standard deviation of three obtained
+        values through different collapses. The critical exponents
+        are in reasonable agreement with the exact kown values for the 2D Ising
+        universality class. The critical temperatures $T_c$ are shifting
+        as expected.
+    }
+    \label{tab:critExp}
+\end{table}
+and are within errorbars consistent with the exactly kown values for the
+two dimensional IFM.
+A newer method\cite{chiCollapse,Hartmann2013} to test if two models are in
+the same universality class is the analysis of the two-point finite-size
+correlation function
+\[\xi = \frac{1}{2\sin(\abs{\vec{k}_{\mathrm{min}}}/2)} \sqrt{\frac{\chi(\vec{0})}{\chi(\vec{k}_{\mathrm{min}})} - 1}\]
+where $\vec{k}_{min}=(2\pi / L, 0)$ and $\chi(\vec{k})$ is the wave vector
+dependent susceptiblity
+\[\chi(\vec{k}) = \avgR{\avg{\abs{\brac{\frac{1}{N}\sum_j s_j \exp(ikx_j)}^2}}}\]
+which is in this case only evaluated over the x-dimension thus $x_j$ is the
+position of the node in the x-dimension.
+
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
-    \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
-    \caption[Critical Temperature over Different Disorder Parameters]
-    {
-        Critical temperatures \(T_c\) over different
-        disorder parameters \(\sigma\) for
-        Interesting points are the jump and rise of the GG at small
-        \(\sigma\) and the plateau on the RNG for small \(\sigma\).
-    }
-    \label{fig:Tc}
-\end{figure}
-
-\begin{figure}[hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{plots/Binder_over_Correlation_All}
+    \includegraphics[scale=1]{plots/Binder_over_Correlation_All}
     \caption[Binder Cumulant over two-point finite-size correlation function divided by system size]
@@
         are drawn with different symbols, while the datapoints for different
-        graph ensembles are drawn with different colors.
-        The inset zooms into the plot to show that
-        all datapoints fall within errorbars onto one curve.
+        graph ensembles are drawn with different colors. Anyway, all points
+        fall on one curve within errorbars.
+        %~ The inset zooms into the plot to show that
+        %~ all datapoints fall within errorbars onto one curve.
     }
@@
 \end{figure}
+If the Binder parameter
+\[g = \frac{3}{2}\brac{1-\frac{\avgR{\avg{m^4}}}{3\avgR{\avg{m^2}^2}}}\]
+is plotted over $\xi$ for different $\sigma$, $L$ and $T$ as shown in
+Fig.~\ref{fig:binderOverCorr} all data points fall on the
+same curve, which confirms that this model is in the same universality
+class as the square lattice Ising ferromagnet, i.e.~$\sigma=0$.
+
+This study examines the critical temperatures $T_c$ for different $\sigma$.
+Therefore the knowledge that the Binder parameters $g$ for different
+system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
+%~ \begin{figure*}[hbtp]
+    %~ \centering
+    %~ \subfigure{
+        %~ \label{sfig:Tc:binder}
+        %~ \includegraphics[scale=1]{plots/binder}
+    %~ }
+    %~ \subfigure{
+        %~ \label{sfig:Tc:RNG}
+        %~ \includegraphics[scale=1]{plots/Tc_RNG}
+    %~ }
+    %~ \subfigure{
+        %~ \label{sfig:Tc:GG}
+        %~ \includegraphics[scale=1]{plots/Tc_GG}
+    %~ }
+    %~ \caption[Critical Temperature over Different Disorder Parameters]
+    %~ {
+        %~ Critical temperatures \(T_c\) are obtained by finding the intersections
+        %~ of the Binder parameters $g$ for different system sizes $L$.
+        %~ They are plotted over different disorder parameters \(\sigma\).
+        %~ Interesting points are the jump and rise of the GG at small
+        %~ \(\sigma\) and the plateau on the RNG for small \(\sigma\).
+    %~ }
+    %~ \label{fig:Tc}
+%~ \end{figure*}
+\begin{figure*}[hbtp]
+    \subfigure[]{
+        \label{sfig:Tc:binder}
+        \includegraphics[scale=1]{plots/binder}
+    }
+    \subfigure[]{
+        \label{sfig:Tc:RNG}
+        \label{sfig:Tc:GG}
+        \includegraphics[scale=1]{plots/Tc_both}
+    }
+    \subfigure[]{
+        \label{fig:TcK}
+        \includegraphics[scale=1]{plots/TcK}
+    }
+    \caption[Critical Temperature over Different Disorder Parameters]
+    {
+        \subref{sfig:Tc:binder} Critical temperatures \(T_c\) are obtained by finding the intersections
+        of the Binder parameters $g$ for different system sizes $L$.
+        \subref{sfig:Tc:RNG} They are plotted over different disorder parameters \(\sigma\).
+        Interesting points are the jump and rise of the GG at small
+        \(\sigma\) and the plateau on the RNG for small \(\sigma\).
+        \subref{fig:TcK} \(T_c\) is plotted in a log-log plot as a function of the degree $K$.
+        The lines are fits to a power law function \(T_c = aK^b\)
+        ignoring the ``bulk" of points in the lower left and upper right, where
+        deviations from the power law become obvious.
+        For the RNG the fit yields $b = 1.349(2)$ with $\chi_\mathrm{red}^2 = 1.9$
+        and for the GG  $b = 1.300(5)$ with $\chi_\mathrm{red}^2 = 0.8$
+    }
+    \label{fig:Tc}
+\end{figure*}
+is used.
+Because \(g\) is only measured for discrete values of \(T\),
+the points have to be interpolated to find the intersection. Therefore
+a \emph{cubic spline} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+is calculated for the measured points.
+%~ Cubic spline interpolation is a piece-wise fitting of polynoms of
+%~ degree three which are joined under the condition to be at least two
+%~ times continuously differentiable.
+%~ This interpolation type has the
+%~ advantage that it is only influenced by local points so that the
+%~ plateaus at low and high \(T\) do not influence the interpolation in
+%~ the vicinity of \(T_c\) -- in contrast to, e.g.\ an polynom fit of
+%~ degree 4, which has to be restricted to the vincinity of \(T_c\) to
+%~ yield meaningful results.
+An even better method would be the
+\emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
+But the simple cubic spline interpolation seems to deliver results that
+are good enough, because the temperatures of the measurements are
+sufficiently near to each other. Also a cubic spline interpolation is
+far easier to obtain.
+
+The first oddity in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is
+the jump of $T_c$ from $\sigma = 0$ to $\sigma > 0$. This is easily explainable
+because the square lattice at $\sigma = 0$ is a very special case for the
+GG and at smallest deviations from the square lattice new edges arise in
+the GG, which lead a stronger coupling of spins such that the system stays
+ferromagnetic at higher temperatures.
+
+For big $\sigma$ the configurations approach the limit of a Poisson point
+process, hence $T_c$ approaches its limit value.
+
+The critical temperature $T_c$ decreases with increasing $\sigma$, which
+is expected, because the edges get fewer as can be seen in
+Fig.~\ref{fig:RNG_sigma} and with loosely coupled spins, the temperature
+needed to disturb the ferromagnetic phase is lower than with strong coupled
+spins. To quantify the influence of this, $T_c$ is plotted over the
+degree $K$, i.e.~the mean number of neighbors each spin has, in Fig.~\ref{fig:TcK}.
+%~ \begin{figure}[hbtp]
+    %~ \includegraphics[scale=1]{plots/TcK}
+    %~ \caption
+    %~ {
+        %~ \(T_c\) is plotted in a log-log plot as a function of the degree.
+        %~ The lines are fits to a power law function \(T_c = aK^b\)
+        %~ ignoring the ``bulk" of points in the lower left and upper right, where
+        %~ deviations from the power law become obvious.
+        %~ For the RNG the fit yields $b = 1.349(2)$ with $\chi_\mathrm{red}^2 = 1.9$
+        %~ and for the GG  $b = 1.300(5)$ with $\chi_\mathrm{red}^2 = 0.8$
+    %~ }
+    %~ \label{fig:TcK}
+%~ \end{figure}
+In first approximation $T_c$ can be derived by a power law from $K$ and the
+graph type. But there are deviations from this behavior, which reflect
+at least the influence of the coupling constant $J$.

### 2015-08-31 Tex/paper/abstract.tex
Paper Entwurf 2. Iteration (Christophs Anmerkungen)

@@
 We perform Monte Carlo simulations to determine the critical temperatures
-of an Ising Ferromagnet (IFM) located on the sites of different types of
-2D proximity graphs.
-%~ In particular we consider Relative Neighborhood graphs and Gabriel graphs
-%~ which are subgraphs of the Delaunay Triangulation for a given set of points.
-The graphs are derived from square lattices where nodes are displaced by
-a Gaussian distributed random variable.
-%~ The limit of maximal disorder thus corresponds to a Poisson point process.
-The deviation of the proximity graph from a square lattice is
-governed by the width \(\sigma\) of the Gaussian distribution.
-In our model, the coupling strength depends on the Euclidean distance
-between the coupled spins.
+of Ising Ferromagnets (IFM) on proximity graphs with different underlying
+node-sets, which can be governed by a parameter $\sigma$.
+The coupling strengths arise from the Euclidean distance
+between coupled spins.
 The simulations are carried out on graphs with \(N=16^{2}\) to \(N=128^{2}\)
@@
 and the type of the underlying proximity graph.
-We further verify that the model lies within the universality class of
-the 2D IFM using finite-size scaling methods.
+We further verify using finite-size scaling methods that the IFM on proximity
+graphs is in the same universality class as the IFM on a two-dimensional
+square lattice.

### 2015-08-31 Tex/paper/introduction.tex
Paper Entwurf 2. Iteration (Christophs Anmerkungen)

@@
-%~ Hallo Welt \cite{Ising1925}
-%~ \blindtext
-%~ ising wichtig, drosophila und so
-%~ Janke und Lima haben das auch gemacht
-%~ TODO: mehr finden
-
-[todo: geo und bio cites] \cite{Karp2000} \cite{Santi2005} \cite{Bose2001} \cite{Kuhn2003} \cite{Selander1975} \cite{Sokal1978} \cite{Sokal1980}
-
-The Ising model for a ferromagnet \cite{Ising1925} is
-perhaps the most extensive studied model in statistical mechanics.
-It consists of spins wich can point up or down and interact with
-neighboring spins. It shows a second order phase transition between
-a ferromagnetic, i.e.~all spins having the same value, and
-paramagnetic phase. While there exist analytic solutions\cite{Onsager1944,Wannier1945}
-describing the phase transition for Ising models on
-regular lattices in two dimensions, higher dimensional lattices or
-non-regular lattices are the domain of Monte Carlo simulations.
+The Ising model for a ferromagnet \cite{Ising1925} is perhaps the
+most extensive studied model in statistical mechanics. It consists
+of spins which can point up or down and interact with neighboring
+spins. It shows a second order phase transition separating a
+ferromagnetic and a paramagnetic phase. While there exist analytic
+solutions\cite{Onsager1944,Wannier1945} describing the phase
+transition for Ising models on regular lattices in two dimensions,
+higher dimensional lattices and non-regular lattices are primarily studied
+by Monte Carlo simulations.
 
 Some work \cite{Janke1994,Lima2000,Lima2008} was done to determine
-the critcal temperatures and confirm the universality of 2D IFM
+the critcal temperatures and confirm the universality of two-dimensional IFM
 where the spins are arranged randomly in the unit square by a
 Poisson point process and neighbor relationships are determined by a
-Delaunay triangulation to maintain the planarity of the system.
+Delaunay triangulation that maintains the planarity of the system.
 This article extends the former research to other
-irregular lattice types closely related to the Delaunay triangulation and
-provides an interpolation between the square lattice IFM
-and spins distributed randomly in the plane.
-For a range of this interpolation the critcal temperatures are determined
-and it is confirmed that configurations from this range belong to the
-IFM universality class.
+irregular lattices, namely the Relative Neighborhood graph (RNG) and
+Gabriel graph (GG), which belong, as the Delaunay triangulation, to the
+family of \emph{proximity graphs}. To get some intuition for proximity
+graphs, their purpose is to connect nodes which are close to each other.
+Hence they are suited to generalize problems defined on regular lattices
+with nearest neighbor relationships.
+[todo: geo und bio cites] \cite{Karp2000} \cite{Santi2005} \cite{Bose2001} \cite{Kuhn2003} \cite{Selander1975} \cite{Sokal1978} \cite{Sokal1980}
+This family of graphs have been applied in geographic variation studies in
+biology and as potential candidate for ``virtual backbones'' in ad-hoc
+networks. % also machine learning
 
-In section \ref{ssec:model} the method to distribute the sites of the
-irregular lattice and in \ref{ssec:graphtypes} the rules to establish the
-bonds between them is explained, section \ref{sec:results} will show the
-details and results of our simulations, before section \ref{sec:conclusion}
-closes this article with the conclusions and an outlook.
+Beginning with a square lattice the nodes can be shifted randomly governed
+by a tunable parameter $\sigma$ until the distribution of the nodes is
+indistinguishable from a Poisson point process.
+For every realization of nodes, the construction rules for the proximity
+graph at hand define an edge-set.
+%~ The edge-set for any realization of node-placements is well defined by
+%~ the construction rules of the
+We measure the critical temperatures by varying $\sigma$ and confirm that
+the universality class does not change in the process.
+
+%~
+ %~ closely related to the Delaunay triangulation and
+%~ provides an interpolation between the square lattice IFM
+%~ and spins distributed randomly in the plane.
+%~ For a range of this interpolation the critcal temperatures are determined
+%~ and it is confirmed that configurations from this range belong to the
+%~ IFM universality class.
+
+In Sec. \ref{ssec:model} the model and the underlying proximity graphs
+are explained. Sec. \ref{sec:results} will show the
+details and results of our simulations. Sec. \ref{sec:conclusion}
+closes this article with the conclusion and an outlook.

### 2015-08-31 Tex/paper/model.tex
Paper Entwurf 2. Iteration (Christophs Anmerkungen)

@@
-\subsection{The Disordered Ising Model}
+\subsection{The Ising Model}
 \label{ssec:model}
-    We call the model under scrutiny in this article the \emph{disordered IFM}
-    which is derived from the well understood \emph{square lattice IFM} \cite{Onsager1944}.
-    That is a square lattice with lateral length \(L\) and \(N=L^2\)
-    sites with periodic boundary conditions.
+% \cite{Onsager1944}
+    Commonly, the IFM is studies on a square lattice with lateral length
+    \(L\) and \(N=L^2\) nodes with periodic boundary conditions.
     Each site $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
@@
     \end{equation}
-    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are nearest
-    neighbors, so that they are directly coupled to each other.
-    This will be called an edge.
-    The coupling between \(i\) and \(j\) is characterized by \(J_{ij} = J\),
-    the coupling constant.
+    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are
+    nearest neighbors, i.e.~they are connected by an edge.
+    The coupling strength between \(i\) and \(j\) is given by
+    \(J_{ij}\).
 
-    The most important difference of the square lattice IFM to the
-    disordered IFM is that the sites of the square lattice are
+    In this article the nodes of the square lattice are
     displaced introducing geometric disorder resulting in a non regular graph
@@
     sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
-    from a Gaussian distribution.
-    %~ \begin{equation}
-        %~ f(\Delta x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{\Delta x^2}{2\sigma^2}}.
-        %~ \label{eq:gauss}
-    %~ \end{equation}
-    %~ This is sketched in Fig.\ \ref{fig:displacement}.
-    %~ \begin{figure}[htbp]
-        %~ \centering
-        %~ \includegraphics[width=0.45\textwidth]{images/Displacement}
-        %~ \caption[Sketch how the Displacement works]
-        %~ {
-            %~ Sketch how the displacement of the nodes works. The nodes
-            %~ get displaced by \(\Delta x\) and \(\Delta y\) drawn from the
-            %~ distributions displayed next to the points. The original
-            %~ square lattice is indicated by dashed lines.
-        %~ }
-        %~ \label{fig:displacement}
-    %~ \end{figure}
-    In the following \(\sigma\) will also be called \emph{disorder parameter}.
-    If we take ``nearest neighbor" in the Euclidean meaning, most sites
-    will only have one nearest neighbor after the
+    from a Gaussian distribution with zero mean.
+    In the following \(\sigma\) will be called \emph{disorder parameter}.
+    If we took ``nearest neighbor" in the Euclidean meaning, most sites
+    would only have one nearest neighbor after the
     displacement. If only the edges between these neighbors remained,
-    the lattice would collapse to many very small clusters. But if one
-    left the edges as they were before the displacement, the edges would
-    cross -- at least for big displacements. The crossing of edges then
-    would destroy the planar character of the model.
+    the lattice would collapse to many very small clusters. If on the
+    other hand all edges remained as they were before the displacement,
+    edges might cross each other -- at least for big displacements.
+    The crossing of edges would destroy the planar character of the graph.
     To avoid this, a new edge set will be established after the displacement
-    as shown in Fig.~\ref{fig:RNG_sigma} for example.
+    as shown in Fig.~\ref{fig:RNG_sigma}.
     \begin{figure}[htb]
@@
     \end{figure}
-    The edges are constructed
-    so that for a given configuration of points the resulting graph is an
+    For a given configuration of points the resulting graph is an
     instance of a so called proximity graph, which will be explained in Sec.~\ref{ssec:graphtypes}.
-    The coupling constant \(J_{ij}\) gets
-    identified with edge weights. \(J_{ij}\) depends on the
+    The coupling constants \(J_{ij}\), i.e.~edge weights, depend on the
     geometric distance between the connected pair of sites. More precise,
@@
     \begin{equation}
-        E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})}
+        E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})},
         \label{eq:coupling}
@@
     where \(d_{ij}\) is the Euclidean
-    distance between the nodes \(i\) and \(j\). Following Ref.~\cite{Lima2000}
+    distance between node \(i\) and \(j\). Following Ref.~\cite{Lima2000}
     the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
-    Note that for \(\sigma = 0\) all \(d_{ij} = 1\) and therefore all
-    \(J_{ij} = 1\), so that the disordered IFM is reduced to the
-    square lattice IFM.
+    Note that for \(\sigma = 0\) the resulting \(d_{ij} = 1\) and therefore
+    \(J_{ij} = 1\) for every edge $\{i,j\}$. Consequently, in this case
+    the graph is a common square lattice.
 
@@
 \label{ssec:graphtypes}
-    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E \subset V^{2}\).
-    In the scope of this model, the nodes get identified with the sites of the
-    lattice. If two nodes are connected by an edge, the sites are neighbors.\\
-    The edges of \emph{proximity graphs} connect nodes which are by some metric near
-    to each other. Hence they are suited to generalize problems defined on regular
-    lattices with nearest neighbor relationships.
-    To determine the distance we use the Euclidean
-    metric on two-dimensional graphs, though in principle every metric in any
-    dimension can be used.
+    A graph \(G(V,E)\) consists of a set of nodes \(V\) and edges \(E \subset V^{2}\).
+    Two nodes connected by an edge are neighbors.
+    Proximity graphs are defined in a metric space. In this article a
+    two-dimensional space with the Euclidean metric is chosen, because
+    it is the most common case and easy to visualize, though in principle
+    every metric in any dimension can be used.
 
@@
     is defined as the intersection of two circles with radius \(r =
-    d_{ij}\) and centers on \(i\) and \(j\). See also the hatched region
-    in Fig.~\ref{fig:lunes}. An Example is given in Fig.~\ref{sfig:lunes:rng}.
+    d_{ij}\) and centers on \(i\) and \(j\). That means that the edge
+    $\{ij\}$ is part of the graph, if the condition
+    \[d_{ij} \le \max\left{ d_{ik} + d_{kj} \right} \forall k \in V\setminus\{i,j\}\]
+    is fulfilled. See also the hatched region
+    in Fig.~\ref{fig:lunes}. An example is given in Fig.~\ref{sfig:lunes:rng}.
 
@@
     if a circle with its center on half way between \(i\) and \(j\)
-    and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes. See
+    and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes, i.e.~the
+    condition
+    \[d_{ij} < d_{ik} + d_{kj} \forall k \in V\setminus\{i,j\}\]
+    is fulfilled. See
     also the cross hatched region from Fig.~\ref{sfig:lunes:def}. An
-    Example is given in Fig.~\ref {sfig:lunes:gg}. Note that the
+    example is given in Fig.~\ref {sfig:lunes:gg}. Note that the
     lune of the GG is completely enclosed in the lune of the RNG,
@@
     dimensional plane.
-
-    % TODO: alles hierdrunter
-    %~ \subsubsection{Construction}
-        %~ The simplest way to construct these graphs is to test for each
-        %~ pair of nodes if any other node lies in
-        %~ the lune of the pair. That is of complexity \(O (N^3)\), because
-        %~ there are \(N(N-1)\) pairs and for each \((N-2)\) nodes to test. So
-        %~ the running time of a straight forward implementation would be of
-        %~ order \(O(N^3)\).
-        %~ To reduce the running time one can basically use this simple method but only test
-        %~ the connectedness for nodes which are near to the lune and abort if
-        %~ one node inside the lune is found. To determine which nodes are
-        %~ near the lune one can subdivide the area in \(M\) \emph{cells} of size
-        %~ \(L_c \times L_c\) and save for each cell a list with nodes lying
-        %~ inside like presented in Ref.\ \cite{RNGCell} for the RNG and sketched in Fig.\ \ref{fig:cell}.
-        %~ For this research \(M = N\) is used.\\
-        %~ \begin{figure}[htbp]
-            %~ \centering
-            %~ \subfigure[not Connected Nodes][]{
-                %~ \label{sfig:cell:big}
-                %~ \includegraphics[width=0.2\textwidth]{images/CellBig}
-            %~ }
-            %~ \subfigure[Connected Nodes][]{
-                %~ \label{sfig:cell:small}
-                %~ \includegraphics[width=0.2\textwidth]{images/CellSmall}
-            %~ }
-            %~ \caption[Sketch how the Cell Method works]
-            %~ {
-                %~ Sketch how the cell algorithm for the construction of the
-                %~ RNG and GG works. Here with the lune definition of the GG.
-                %~ The bounding box of the lune, which determines which cells have
-                %~ to be tested, is marked with thick colored lines.
-                %~ Left: shows that it is sufficient to find a
-                %~ single node in an inner cell of the bounding box to discard
-                %~ the edge between two distant nodes. The nodes inside the
-                %~ other 8 marked cells do not have to be tested anymore.
-                %~ Right: shows that only the nodes inside the
-                %~ marked cell have to be tested, because there are no other nodes,
-                %~ the edge can be drawn.
-            %~ }
-            %~ \label{fig:cell}
-        %~ \end{figure}\\
-        %~ Given the discretized cell structure it is just necessary to test the nodes in the cells which
-        %~ resemble a rectangular bounding box of the lune. Most pairs will be
-        %~ far away from each other and there will be one or more cells in the
-        %~ middle of the bounding box, which are completely inside the lune.
-        %~ Then only one node has to be tested from such a cell to discard an
-        %~ edge between the nodes. On the other hand, nodes that will be connected
-        %~ are near to each other so that only very few cells intersect the bounding
-        %~ box of their lune and consequently only very few nodes have to be tested.\\
-        %~ The complexity of this method should be between \(O(N^2)\) in the
-        %~ best case, because for every pair at least one check has to be performed,
-        %~ and \(O(N^3)\) in the worst case, e.g.\ all nodes are inside one
-        %~ cell.\\
-        %~ Note that even faster algorithms exsist for two dimensional RNG and GG, which require to first
-        %~ generate a DT and use the fact, that the RNG and GG are subgraphs.
-        %~ (For the construction of the DT for a given set of points one might
-        %~ use existing software libraries, e.g.\ the \texttt{qHull}\cite{qhull} library.)\\
-        %~ However, generation of the graphs is not time critical, because
-        %~ the MC simulations take much longer. So only the simple cell algorithm
-        %~ was used to gegnerate the graphs.\\

### 2015-08-31 Tex/paper/results.tex
Paper Entwurf 2. Iteration (Christophs Anmerkungen)

@@
 parallel tempering swap \cite{ParallelTempering1986} are performed.
-For every systemsize $L \in \{16,32,64,128\}$ and 19 different
+For every system size $L \in \{16,32,64,128\}$ and 19 different
 $\sigma \in [0,1.2]$ on $100$ different realizations at least $5000$
 independent measurements are taken in equilibrium.\\
-Because it is not known before, where the critical temperatures \(T_c\)
+Since it is not known beforehand, where the critical temperatures \(T_c\)
 are located, the Wolff cluster algorithm is used at every
 temperature. Albeit the efficiency of the algorithmic procedure was
-not dissected for every temperature, the speed up near criticality
+not examined for every temperature, the speed up near criticality
 should be worth the moderate slow down at other temperatures.\\
 
-The differences of this model and the 2D IFM are only details,
-it is therefore expected that both are in the same universality class.
+It is not expected that the universality class depends on the graph
+structure unless the dimension is changed.
 To proof this, the critical exponents are determined by a finite-size
-scaling (FSS) analysis
-using the well kown scaling bahaviors of the magnetization, the susceptiblity and the Binder parameter
+scaling (FSS) analysis using the well kown scaling bahaviors of the
+magnetization, the susceptiblity and the Binder parameter
 in an automated and reproducable way using the
-\texttt{autoscale.py} \cite{autoscale2009} tool.
+method from Ref.~\cite{autoscale2009}.
 In Fig.~\ref{fig:collapse}
@@
 \end{figure}
-%~ two examples collapses at $\sigma = 1$ for the
-%~ magnetization
-%~ \[\abs{m} = \avgR{\avg{\abs{\frac{1}{N}\sum_{i=1}^N s_i}}}\]
- %~ -- with $\avg{\cdot}$ being the thermal average and $\avgR{\cdot}$ being the
-%~ average over the random realizations -- and the susceptiblity
-%~ \[\chi = \frac{N}{T}\brac{\avgR{\avg{m^2}}-\avgR{\avg{m}}^2}\]
-%~ are plotted.
-an example collapse at $\sigma = 1$ for the susceptiblity
+a data collapse at $\sigma = 1$ for the susceptiblity
 \[\chi = \frac{N}{T}\brac{\avgR{\avg{m^2}}-\avgR{\avg{m}}^2}\]
@@
 average over the random realizations, is plotted.
-%~ The collapse happens because $\chi$ should scale according to
-%~ \[\chi_L = L^{\gamma / \nu} \tilde{C}\brac{L^{1/\nu}\brac{T-T_c}}\]
 All obtained values for different $\sigma$ are visualized in Tab.~\ref{tab:critExp}
@@
         \(T_c\). The errors for \(\beta\) and \(\gamma\) are estimated
-        by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
+        with the method from Ref.~\cite{autoscale2009}. The errors of
         \(\nu\) and \(T_c\) are the standard deviation of three obtained
         values through different collapses. The critical exponents
-        are in reasonable agreement with the exact kown values for the 2D Ising
+        are in reasonable agreement with the exact known values for the 2D Ising
         universality class. The critical temperatures $T_c$ are shifting
@@
 \end{table}
-and are within errorbars consistent with the exactly kown values for the
-two dimensional IFM.
-A newer method\cite{chiCollapse,Hartmann2013} to test if two models are in
+and are within errorbars consistent with the exactly known values for the
+square lattice IFM.
+A newer method \cite{chiCollapse,Hartmann2013} to test whether two models are in
 the same universality class is the analysis of the two-point finite-size
@@
 \[\chi(\vec{k}) = \avgR{\avg{\abs{\brac{\frac{1}{N}\sum_j s_j \exp(ikx_j)}^2}}}\]
-which is in this case only evaluated over the x-dimension thus $x_j$ is the
-position of the node in the x-dimension.
+which is in this case only evaluated over one direction thus $x_j$ is the
+position of the node in the x-direction.
 
@@
 Fig.~\ref{fig:binderOverCorr} all data points fall on the
-same curve, which confirms that this model is in the same universality
-class as the square lattice Ising ferromagnet, i.e.~$\sigma=0$.
+same curve, which confirms that this IFM on proximity graphs is in the
+same universality class as on the square lattice, i.e.~$\sigma=0$.
 
@@
 is used.
-Because \(g\) is only measured for discrete values of \(T\),
+Since \(g\) is only measured for discrete values of \(T\),
 the points have to be interpolated to find the intersection. Therefore
-a \emph{cubic spline} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+a \emph{cubic spline} \cite{press2007numerical} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
 is calculated for the measured points.
@@
 The first oddity in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is
-the jump of $T_c$ from $\sigma = 0$ to $\sigma > 0$. This is easily explainable
+the jump of $T_c$ close to $\sigma = 0$, where it jumps from $T_c(0) = 2.269(1)$
+to $T_c(0.03) = 2.851(1)$ at the next measured temperature. This is easily explainable,
 because the square lattice at $\sigma = 0$ is a very special case for the
 GG and at smallest deviations from the square lattice new edges arise in
-the GG, which lead a stronger coupling of spins such that the system stays
+the GG, which lead to a stronger coupling of spins such that the system stays
 ferromagnetic at higher temperatures.
 
-For big $\sigma$ the configurations approach the limit of a Poisson point
-process, hence $T_c$ approaches its limit value.
+For large values of $\sigma$ the configurations approach the limit of a
+Poisson point process, hence $T_c$ approaches its limit value.
 
 The critical temperature $T_c$ decreases with increasing $\sigma$, which
-is expected, because the edges get fewer as can be seen in
+is expected, since the number of edges decreases, which can be seen in
 Fig.~\ref{fig:RNG_sigma} and with loosely coupled spins, the temperature
@@
 degree $K$, i.e.~the mean number of neighbors each spin has, in Fig.~\ref{fig:TcK}.
-%~ \begin{figure}[hbtp]
-    %~ \includegraphics[scale=1]{plots/TcK}
-    %~ \caption
-    %~ {
-        %~ \(T_c\) is plotted in a log-log plot as a function of the degree.
-        %~ The lines are fits to a power law function \(T_c = aK^b\)
-        %~ ignoring the ``bulk" of points in the lower left and upper right, where
-        %~ deviations from the power law become obvious.
-        %~ For the RNG the fit yields $b = 1.349(2)$ with $\chi_\mathrm{red}^2 = 1.9$
-        %~ and for the GG  $b = 1.300(5)$ with $\chi_\mathrm{red}^2 = 0.8$
-    %~ }
-    %~ \label{fig:TcK}
-%~ \end{figure}
-In first approximation $T_c$ can be derived by a power law from $K$ and the
-graph type. But there are deviations from this behavior, which reflect
+For a given graph type, $T_c$ can be derived approximately by a power law
+from $K$. But there are deviations from this behavior, which reflect
 at least the influence of the coupling constant $J$.

### 2015-11-25 Tex/paper/introduction.tex
mehr Zitate

@@
 with nearest neighbor relationships.
-[todo: geo und bio cites] \cite{Karp2000} \cite{Santi2005} \cite{Bose2001} \cite{Kuhn2003} \cite{Selander1975} \cite{Sokal1978} \cite{Sokal1980}
 This family of graphs have been applied in geographic variation studies in
-biology and as potential candidate for ``virtual backbones'' in ad-hoc
-networks. % also machine learning
+biology \cite{Sokal1978,Sokal1980,Selander1975} and as potential candidate for ``virtual backbones'' in ad-hoc
+networks \cite{Kuhn2003,Bose2001,Santi2005,Karp2000,jennings2002topology}. % also machine learning
 
@@
 
-In Sec. \ref{ssec:model} the model and the underlying proximity graphs
-are explained. Sec. \ref{sec:results} will show the
-details and results of our simulations. Sec. \ref{sec:conclusion}
+In Sec.~\ref{sec:model} proximity graphs and the Ising model
+are explained. Sec.~\ref{sec:results} will show the
+details and results of our simulations. Sec.~\ref{sec:conclusion}
 closes this article with the conclusion and an outlook.

### 2015-11-25 Tex/paper/model.tex
mehr Zitate

@@
-\subsection{The Ising Model}
-\label{ssec:model}
-% \cite{Onsager1944}
-    Commonly, the IFM is studies on a square lattice with lateral length
-    \(L\) and \(N=L^2\) nodes with periodic boundary conditions.
-    Each site $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
-    nearest neighbors described by the Hamiltonian
-    \begin{equation}
-        \mathcal{H} = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
-        \label{eq:hamiltonian}
-    \end{equation}
-    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are
-    nearest neighbors, i.e.~they are connected by an edge.
-    The coupling strength between \(i\) and \(j\) is given by
-    \(J_{ij}\).
-
-    In this article the nodes of the square lattice are
-    displaced introducing geometric disorder resulting in a non regular graph
-    structure.
-    The displacement is randomly Gaussian distributed with standard
-    deviation \(\sigma\), i.e.~the \(x\) and \(y\) coordinates of the
-    sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
-    from a Gaussian distribution with zero mean.
-    In the following \(\sigma\) will be called \emph{disorder parameter}.
-    If we took ``nearest neighbor" in the Euclidean meaning, most sites
-    would only have one nearest neighbor after the
-    displacement. If only the edges between these neighbors remained,
-    the lattice would collapse to many very small clusters. If on the
-    other hand all edges remained as they were before the displacement,
-    edges might cross each other -- at least for big displacements.
-    The crossing of edges would destroy the planar character of the graph.
-    To avoid this, a new edge set will be established after the displacement
-    as shown in Fig.~\ref{fig:RNG_sigma}.
-    \begin{figure}[htb]
-        \centering
-        \subfigure[$\sigma = 0.09$]
-        {
-            \label{sfig:RNG_sigma:0.09}
-            \includegraphics[width=0.14\textwidth]{images/RNG/out009}
-        }
-        \subfigure[$\sigma = 0.15$]
-        {
-            \label{sfig:RNG_sigma:0.15}
-            \includegraphics[width=0.14\textwidth]{images/RNG/out015}
-        }
-        \subfigure[$\sigma = 0.21$]
-        {
-            \label{sfig:RNG_sigma:0.21}
-            \includegraphics[width=0.14\textwidth]{images/RNG/out021}
-        }
-        \caption[Examples of RNG for different $\sigma$]
-        {
-            Examples of proximity graphs (more precise, Relative Neighborhood
-            graph see Sec. \ref{ssec:graphtypes}) for different $\sigma$.
-            Connections which cross a periodic boundary are indicated
-            by edges which connect a solid node to a dashed node.
-        }
-        \label{fig:RNG_sigma}
-    \end{figure}
-    For a given configuration of points the resulting graph is an
-    instance of a so called proximity graph, which will be explained in Sec.~\ref{ssec:graphtypes}.
-    The coupling constants \(J_{ij}\), i.e.~edge weights, depend on the
-    geometric distance between the connected pair of sites. More precise,
-    the weight of an edge is
-    \begin{equation}
-        E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})},
-        \label{eq:coupling}
-    \end{equation}
-    where \(d_{ij}\) is the Euclidean
-    distance between node \(i\) and \(j\). Following Ref.~\cite{Lima2000}
-    the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
-    Note that for \(\sigma = 0\) the resulting \(d_{ij} = 1\) and therefore
-    \(J_{ij} = 1\) for every edge $\{i,j\}$. Consequently, in this case
-    the graph is a common square lattice.
-
+\label{sec:model}
 \subsection{Proximity Graphs}
@@
     $\{ij\}$ is part of the graph, if the condition
-    \[d_{ij} \le \max\left{ d_{ik} + d_{kj} \right} \forall k \in V\setminus\{i,j\}\]
+    \[d_{ij} \le \max\left\{ d_{ik} + d_{kj} \right\} \forall k \in V\setminus\{i,j\}\]
     is fulfilled. See also the hatched region
@@
             \label{sfig:lunes:rng}
-            \includegraphics[width=0.14\textwidth]{images/RNG/L12S03.pdf}
+            \includegraphics[width=0.14\textwidth]{images/RNG/L12S03}
         }
@@
             \label{sfig:lunes:gg}
-            \includegraphics[width=0.14\textwidth]{images/GG/L12S03.pdf}
+            \includegraphics[width=0.14\textwidth]{images/GG/L12S03}
         }
@@
     dimensional plane.
+
+\subsection{The Ising Model}
+\label{ssec:model}
+    Commonly, the IFM is studies on a square lattice with lateral length
+    \(L\) and \(N=L^2\) nodes with periodic boundary conditions.
+    Each site $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
+    nearest neighbors described by the Hamiltonian
+    \begin{equation}
+        \mathcal{H} = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
+        \label{eq:hamiltonian}
+    \end{equation}
+    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are
+    nearest neighbors, i.e.~they are connected by an edge.
+    The coupling strength between \(i\) and \(j\) is given by
+    \(J_{ij}\).
+
+    In this article the nodes of the square lattice are
+    displaced, introducing geometric disorder resulting in a non regular graph
+    structure.
+    The displacement is randomly Gaussian distributed with standard
+    deviation \(\sigma\), i.e.~the \(x\) and \(y\) coordinates of the
+    sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
+    from a Gaussian distribution with zero mean.
+    In the following \(\sigma\) will be called \emph{disorder parameter}.
+    If we took ``nearest neighbor" in the Euclidean meaning, most sites
+    would only have one nearest neighbor after the
+    displacement. If only the edges between these neighbors remained,
+    the lattice would collapse to many very small clusters. If on the
+    other hand all edges remained as they were before the displacement,
+    edges might cross each other -- at least for big displacements.
+    The crossing of edges would destroy the planar character of the graph.
+    To avoid this, a new edge-set will be established after the displacement
+    to form a proximity graph. The influence of $\sigma$ on the
+    structure of a proximity graph is shown in Fig.~\ref{fig:RNG_sigma}
+    for a RNG.
+    \begin{figure}[htb]
+        \centering
+        \subfigure[$\sigma = 0.09$]
+        {
+            \label{sfig:RNG_sigma:0.09}
+            \includegraphics[width=0.14\textwidth]{images/RNG/out009}
+        }
+        \subfigure[$\sigma = 0.15$]
+        {
+            \label{sfig:RNG_sigma:0.15}
+            \includegraphics[width=0.14\textwidth]{images/RNG/out015}
+        }
+        \subfigure[$\sigma = 0.21$]
+        {
+            \label{sfig:RNG_sigma:0.21}
+            \includegraphics[width=0.14\textwidth]{images/RNG/out021}
+        }
+        \caption[Examples of RNG for different $\sigma$]
+        {
+            Examples of proximity graphs (more precise, Relative Neighborhood
+            graph see Sec. \ref{ssec:graphtypes}) for different $\sigma$.
+            Connections which cross a periodic boundary are indicated
+            by edges which connect a solid node to a dashed node.
+        }
+        \label{fig:RNG_sigma}
+    \end{figure}
+    The coupling constants \(J_{ij}\), i.e.~edge weights, depend on the
+    geometric distance between the connected pair of sites. More precise,
+    the weight of an edge is
+    \begin{equation}
+        E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})},
+        \label{eq:coupling}
+    \end{equation}
+    where \(d_{ij}\) is the Euclidean
+    distance between node \(i\) and \(j\). Following Ref.~\cite{Lima2000}
+    the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
+    Note that for \(\sigma = 0\) the resulting \(d_{ij} = 1\) and therefore
+    \(J_{ij} = 1\) for every edge $\{i,j\}$. Consequently, in this case
+    the graph is a common square lattice.

### 2015-12-02 Tex/paper/abstract.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

@@
 of Ising Ferromagnets (IFM) on proximity graphs with different underlying
-node-sets, which can be governed by a parameter $\sigma$.
+node sets, which can be governed by a parameter $\sigma$.
 The coupling strengths arise from the Euclidean distance
@@
 nodes utilizing the Wolff cluster algorithm and parallel tempering in a
-wide temperature range around the critical point to measure the Binder Cumulant.
+wide temperature range around the critical point to measure
+the Binder cumulant as means to obtain the critical temperature.
 The critical temperatures are shown to depend mainly on the average degree

### 2015-12-02 Tex/paper/conclusion.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

@@
 irregular graphs on a wide range of configurations which are intermediate
-between the square lattice ising model and a random Poisson point process.
+between the square lattice Ising model and a random Poisson point process.
 Also the critical temperature was measured over this range and determined
-that it shows in first approximation a power law behavior with the mean
+that it shows approximately a power law behavior with the mean
 number of neighbors as the base and an exponent dependent on the
@@
 
-The next step would be the extension of this model to three and higher
+The next step would be the extension to three and higher
 dimensions, where the used proximity graphs are still well defined. It
-would also be worthwhile to study properties of the graph ensembles itself,
+would also be worthwhile to study properties of the graph ensembles themselves,
 because -- to our knowledge -- they are mostly studied in 2D \cite{RNGCell}.

### 2015-12-02 Tex/paper/introduction.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

@@
 spins. It shows a second order phase transition separating a
-ferromagnetic and a paramagnetic phase. While there exist analytic
+ferromagnetic from a paramagnetic phase. While there exist analytic
 solutions\cite{Onsager1944,Wannier1945} describing the phase
@@
 irregular lattices, namely the Relative Neighborhood graph (RNG) and
-Gabriel graph (GG), which belong, as the Delaunay triangulation, to the
-family of \emph{proximity graphs}. To get some intuition for proximity
-graphs, their purpose is to connect nodes which are close to each other.
-Hence they are suited to generalize problems defined on regular lattices
-with nearest neighbor relationships.
+Gabriel graph (GG), which belong together with the Delaunay triangulation,
+to the family of \emph{proximity graphs}. The purpose of proximity graphs
+is to connect nodes which are close to each other, hence they are suited
+to generalize problems defined on regular lattices with nearest neighbor
+relationships.
 This family of graphs have been applied in geographic variation studies in
-biology \cite{Sokal1978,Sokal1980,Selander1975} and as potential candidate for ``virtual backbones'' in ad-hoc
+biology \cite{Sokal1978,Sokal1980,Selander1975} and as potential candidates for ``virtual backbones'' in ad-hoc
 networks \cite{Kuhn2003,Bose2001,Santi2005,Karp2000,jennings2002topology}. % also machine learning
@@
 For every realization of nodes, the construction rules for the proximity
-graph at hand define an edge-set.
+graph at hand define an edge set.
 %~ The edge-set for any realization of node-placements is well defined by
 %~ the construction rules of the
-We measure the critical temperatures by varying $\sigma$ and confirm that
+We measure the critical temperatures for a range of $\sigma$ and confirm that
 the universality class does not change in the process.

### 2015-12-02 Tex/paper/model.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

@@
     A graph \(G(V,E)\) consists of a set of nodes \(V\) and edges \(E \subset V^{2}\).
-    Two nodes connected by an edge are neighbors.
+    Two nodes connected by an edge are called neighbors.
     Proximity graphs are defined in a metric space. In this article a
@@
     d_{ij}\) and centers on \(i\) and \(j\). That means that the edge
-    $\{ij\}$ is part of the graph, if the condition
-    \[d_{ij} \le \max\left\{ d_{ik} + d_{kj} \right\} \forall k \in V\setminus\{i,j\}\]
+    $\{i,j\}$ is part of the graph, if the condition
+    \begin{align*}
+        d_{ij} &\le \max\left\{ d_{ik} + d_{kj} \right\} &\forall k \in V\setminus\{i,j\}
+    \end{align*}
     is fulfilled. See also the hatched region
@@
             \subref{sfig:lunes:def} Lunes, which define whether an edge
-                exist, of RNG (hatched region) and GG (cross hatched region).
+                exists, of RNG (hatched region) and GG (cross hatched region).
                 It is evident from this sketch that the GG is a supergraph
@@
     condition
-    \[d_{ij} < d_{ik} + d_{kj} \forall k \in V\setminus\{i,j\}\]
+    \begin{align*}
+        d_{ij} &< d_{ik} + d_{kj} &\forall k \in V\setminus\{i,j\}
+    \end{align*}
     is fulfilled. See
@@
 \label{ssec:model}
-    Commonly, the IFM is studies on a square lattice with lateral length
+    Commonly, the IFM is studied on a square lattice with lateral length
     \(L\) and \(N=L^2\) nodes with periodic boundary conditions.
-    Each site $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
+    Each node $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
     nearest neighbors described by the Hamiltonian
@@
     In this article the nodes of the square lattice are
-    displaced, introducing geometric disorder resulting in a non regular graph
+    displaced, introducing geometric disorder resulting in a non-regular graph
     structure.
@@
     deviation \(\sigma\), i.e.~the \(x\) and \(y\) coordinates of the
-    sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
+    nodes are displaced by random \(\Delta x\) and \(\Delta y\) drawn
     from a Gaussian distribution with zero mean.
-    In the following \(\sigma\) will be called \emph{disorder parameter}.
-    If we took ``nearest neighbor" in the Euclidean meaning, most sites
+    In the following, \(\sigma\) will be called \emph{disorder parameter}.
+    If we took ``nearest neighbor" in the Euclidean meaning, most nodes
     would only have one nearest neighbor after the
     displacement. If only the edges between these neighbors remained,
-    the lattice would collapse to many very small clusters. If on the
-    other hand all edges remained as they were before the displacement,
+    the lattice would collapse to many very small clusters. If, on the
+    other hand, all edges remained as they were before the displacement,
     edges might cross each other -- at least for big displacements.
     The crossing of edges would destroy the planar character of the graph.
-    To avoid this, a new edge-set will be established after the displacement
+    To avoid this, a new edge set will be established after the displacement
     to form a proximity graph. The influence of $\sigma$ on the
@@
             Examples of proximity graphs (more precise, Relative Neighborhood
-            graph see Sec. \ref{ssec:graphtypes}) for different $\sigma$.
+            graph see Sec. \ref{ssec:graphtypes}) for different values of $\sigma$.
             Connections which cross a periodic boundary are indicated
@@
     The coupling constants \(J_{ij}\), i.e.~edge weights, depend on the
-    geometric distance between the connected pair of sites. More precise,
+    geometric distance between the connected pair of nodes. More precise,
     the weight of an edge is

### 2015-12-02 Tex/paper/results.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

@@
 parallel tempering swap \cite{ParallelTempering1986} are performed.
-For every system size $L \in \{16,32,64,128\}$ and 19 different
+For every system size $L \in \{16,32,64,128\}$ and 19 different values of
 $\sigma \in [0,1.2]$ on $100$ different realizations at least $5000$
@@
 scaling (FSS) analysis using the well kown scaling bahaviors of the
-magnetization, the susceptiblity and the Binder parameter
+magnetization, the susceptiblity and the Binder cumulant
 in an automated and reproducable way using the
@@
         \(\sigma = 1\) to get the corresponding critical exponent $\gamma$.
-        The same procedure is used on the Binder parameter $g$ and the
-        magnetization $|m|$ to to determine the critical exponents
+        The same procedure is used on the Binder cumulant $g$ and the
+        magnetization $|m|$ to determine the critical exponents
         \(\nu\) and \(\beta\) and the critical temperature \(T_c\).
@@
     \includegraphics[scale=1]{plots/Binder_over_Correlation_All}
-    \caption[Binder Cumulant over two-point finite-size correlation function divided by system size]
+    \caption[Binder cumulant over two-point finite-size correlation function divided by system size]
     {
-        Binder Cumulant over two-point finite-size correlation function
-        divided by system size. The datapoints for different system sizes
+        Binder cumulant $g$ over two-point finite-size correlation function
+        divided by system size $L$. The datapoints for different system sizes
         are drawn with different symbols, while the datapoints for different
@@
 \end{figure}
-If the Binder parameter
+If the Binder cumulant
 \[g = \frac{3}{2}\brac{1-\frac{\avgR{\avg{m^4}}}{3\avgR{\avg{m^2}^2}}}\]
 is plotted over $\xi$ for different $\sigma$, $L$ and $T$ as shown in
-Fig.~\ref{fig:binderOverCorr} all data points fall on the
+Fig.~\ref{fig:binderOverCorr}, all data points fall on the
 same curve, which confirms that this IFM on proximity graphs is in the
@@
 
-This study examines the critical temperatures $T_c$ for different $\sigma$.
-Therefore the knowledge that the Binder parameters $g$ for different
+This study examines the critical temperatures $T_c$ for different values of $\sigma$.
+Therefore the knowledge that the Binder cumulants $g$ for different
 system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
@@
 
-The first oddity in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is
+The first oddity of the GG in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is
 the jump of $T_c$ close to $\sigma = 0$, where it jumps from $T_c(0) = 2.269(1)$
@@
 is expected, since the number of edges decreases, which can be seen in
-Fig.~\ref{fig:RNG_sigma} and with loosely coupled spins, the temperature
-needed to disturb the ferromagnetic phase is lower than with strong coupled
+Fig.~\ref{fig:RNG_sigma}. With loosely coupled spins, the temperature
+needed to disturb the ferromagnetic phase is lower than with strongly coupled
 spins. To quantify the influence of this, $T_c$ is plotted over the

### 2016-03-04 Tex/paper/introduction.tex
changes to the article

@@
-The Ising model for a ferromagnet \cite{Ising1925} is perhaps the
-most extensive studied model in statistical mechanics. It consists
-of spins which can point up or down and interact with neighboring
-spins. It shows a second order phase transition separating a
-ferromagnetic from a paramagnetic phase. While there exist analytic
-solutions\cite{Onsager1944,Wannier1945} describing the phase
-transition for Ising models on regular lattices in two dimensions,
-higher dimensional lattices and non-regular lattices are primarily studied
-by Monte Carlo simulations.
+The Ising model of ferromagnetism \cite{Ising1925} is one of the
+most extensively studied models in statistical mechanics, because it
+features a continuous phase transition while being simple.
+The model consists of discrete variables, called spins, which can be in
+one of two different states.
+The neighbor relationships, which define the interactions of spins, can be expressed by graphs and
+thus there is a constant interest in the critical behavior of this model
+on different graph ensembles. The research provides the whole range
+from analytical results for regular lattices \cite{Onsager1944,Wannier1945}
+to numerical results for complex networks \cite{Aleksiejuk2002260,Herrero2002SmallWorld,Herrero2004ScaleFree,Herrero2015ScaleFree}.
 
-Some work \cite{Janke1994,Lima2000,Lima2008} was done to determine
-the critcal temperatures and confirm the universality of two-dimensional IFM
-where the spins are arranged randomly in the unit square by a
-Poisson point process and neighbor relationships are determined by a
-Delaunay triangulation that maintains the planarity of the system.
+An important graph is the Delaunay triangulation that finds application in ....
+For a system of randomly placed spins on a two-dimensional surface
+with neighbor relationships derived from a Delaunay triangulation,
+the critical temperature has been obtained
+and it has been confirmed that it is in the same universality class as the
+two-dimensional Ising model on a square lattice \cite{Janke1994,Lima2000,Lima2008}.
 This article extends the former research to other
 irregular lattices, namely the Relative Neighborhood graph (RNG) and
-Gabriel graph (GG), which belong together with the Delaunay triangulation,
-to the family of \emph{proximity graphs}. The purpose of proximity graphs
-is to connect nodes which are close to each other, hence they are suited
+Gabriel graph (GG), which are subgraphs of the Delaunay triangulation
+and belong to the family of \emph{proximity graphs}.
+%~ Since in proximity graphs nodes which are
+%~ spatially close to each other are connected, they are well suited
+%~ to generalize problems defined on regular lattices with nearest neighbor
+%~ relationships.
+The objective of proximity graphs is to connect nodes which are
+spatially close to each other, hence they are suited
 to generalize problems defined on regular lattices with nearest neighbor
 relationships.
-This family of graphs have been applied in geographic variation studies in
-biology \cite{Sokal1978,Sokal1980,Selander1975} and as potential candidates for ``virtual backbones'' in ad-hoc
-networks \cite{Kuhn2003,Bose2001,Santi2005,Karp2000,jennings2002topology}. % also machine learning
+This family of graphs finds application in geographic variation studies in
+biology \cite{Sokal1978,Sokal1980,Selander1975}, as potential candidates for ``virtual backbones'' in ad-hoc
+networks \cite{Kuhn2003,Bose2001,Santi2005,Karp2000,jennings2002topology}
+and in machine learning and pattern recognition \cite{bhattacharya1981application}.
+Also, their statistical properties have been under scrutiny recently \cite{RNGCell,norrenbrock2014percolation}.
 
-Beginning with a square lattice the nodes can be shifted randomly governed
-by a tunable parameter $\sigma$ until the distribution of the nodes is
-indistinguishable from a Poisson point process.
-For every realization of nodes, the construction rules for the proximity
-graph at hand define an edge set.
+Here, we consider an ensemble depending on a tunable parameter $\sigma$.
+By changing this parameter we can interpolate the configurations
+between nodes on a square lattice and nodes distributed by a Poisson point process.
+For any node set the construction rule of a proximity
+graph defines the corresponding edge set.
 %~ The edge-set for any realization of node-placements is well defined by
 %~ the construction rules of the
-We measure the critical temperatures for a range of $\sigma$ and confirm that
-the universality class does not change in the process.
-
+We measure the critical temperatures for a range of $\sigma$ and find
+a power-law relationship for the GG between the critcal temperature and
+the average degree, for the RNG we cannot observe a power law.
+Additionally we verify that the universality class does not change by
+varying $\sigma$.
 %~
@@
 In Sec.~\ref{sec:model} proximity graphs and the Ising model
-are explained. Sec.~\ref{sec:results} will show the
+are explained. Sec.~\ref{sec:results} shows the
 details and results of our simulations. Sec.~\ref{sec:conclusion}

### 2016-03-04 Tex/paper/model.tex
changes to the article

@@
     \begin{align*}
-        d_{ij} &\le \max\left\{ d_{ik} + d_{kj} \right\} &\forall k \in V\setminus\{i,j\}
+        d_{ij} &\le \max\left\{ d_{ik}, d_{kj} \right\} &\forall k \in V\setminus\{i,j\}
     \end{align*}
@@
     \begin{align*}
-        d_{ij} &< d_{ik} + d_{kj} &\forall k \in V\setminus\{i,j\}
+        d^{2}_{ij} &< d^{2}_{ik} + d^{2}_{kj} &\forall k \in V\setminus\{i,j\}
     \end{align*}
@@
 
-    To construct these graphs there is an algorithm\cite{RNGCell} with
+    To construct these graphs there is an algorithm with
     a time complexity of \(\mathcal{O}(N \log N)\) for nodes on a two
-    dimensional plane.
+    dimensional plane \cite{RNGCell}.
 

### 2016-03-04 Tex/paper/results.tex
changes to the article

@@
         \label{fig:TcK}
-        \includegraphics[scale=1]{plots/TcK}
+        \includegraphics[scale=1]{plots/K_sigma_inset_both}
     }
@@
 
+\begin{figure}[hbtp]
+\label{fig:TcK}
+        \includegraphics[scale=1]{plots/K_sigma_inset_both}
+\end{figure}
 The first oddity of the GG in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is

### 2016-03-14 Tex/paper/model.tex
korrekturen und Erweiterungen

@@
     a proximity graph. Two nodes \(i\) and \(j\) with distance $d_{ij}$
-    will be connected, if no other node is in the \emph {lune}. The lune
+    will be connected, if no other node is in their \emph {lune}. The lune
     is defined as the intersection of two circles with radius \(r =
@@
     of the Delaunay triangulation \cite{Delaunay1934,Katajainen}
-    (DT), i.e.~for the same set of nodes \(V\) the edge set of the
+    (DT), i.e., for the same set of nodes \(V\) the edge set of the
     DT is a superset of the edge set of the GG. Two nodes \(i\) and
@@
     if a circle with its center on half way between \(i\) and \(j\)
-    and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes, i.e.~the
+    and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes, i.e., the
     condition
@@
     \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are
-    nearest neighbors, i.e.~they are connected by an edge.
+    nearest neighbors, i.e., they are connected by an edge.
     The coupling strength between \(i\) and \(j\) is given by
@@
     The displacement is randomly Gaussian distributed with standard
-    deviation \(\sigma\), i.e.~the \(x\) and \(y\) coordinates of the
+    deviation \(\sigma\), i.e., the \(x\) and \(y\) coordinates of the
     nodes are displaced by random \(\Delta x\) and \(\Delta y\) drawn
@@
     \end{figure}
-    The coupling constants \(J_{ij}\), i.e.~edge weights, depend on the
+    The coupling constants \(J_{ij}\), i.e., edge weights, depend on the
     geometric distance between the connected pair of nodes. More precise,

### 2016-03-14 Tex/paper/results.tex
korrekturen und Erweiterungen

@@
 correlation function
-\[\xi = \frac{1}{2\sin(\abs{\vec{k}_{\mathrm{min}}}/2)} \sqrt{\frac{\chi(\vec{0})}{\chi(\vec{k}_{\mathrm{min}})} - 1}\]
-where $\vec{k}_{min}=(2\pi / L, 0)$ and $\chi(\vec{k})$ is the wave vector
+\[\xi = \frac{1}{2\sin\brac{\abs{\vec{k}_{\mathrm{min}}}/2}} \sqrt{\frac{\chi(\vec{0})}{\chi(\vec{k}_{\mathrm{min}})} - 1}\]
+where $\vec{k}_{\mathrm{min}}=(2\pi / L, 0)$ and $\chi(\vec{k})$ is the wave vector
 dependent susceptiblity
@@
 same curve, which confirms that this IFM on proximity graphs is in the
-same universality class as on the square lattice, i.e.~$\sigma=0$.
+same universality class as on the square lattice, i.e., $\sigma=0$.
 
@@
 system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
-%~ \begin{figure*}[hbtp]
-    %~ \centering
-    %~ \subfigure{
-        %~ \label{sfig:Tc:binder}
-        %~ \includegraphics[scale=1]{plots/binder}
-    %~ }
-    %~ \subfigure{
-        %~ \label{sfig:Tc:RNG}
-        %~ \includegraphics[scale=1]{plots/Tc_RNG}
-    %~ }
-    %~ \subfigure{
-        %~ \label{sfig:Tc:GG}
-        %~ \includegraphics[scale=1]{plots/Tc_GG}
-    %~ }
-    %~ \caption[Critical Temperature over Different Disorder Parameters]
-    %~ {
-        %~ Critical temperatures \(T_c\) are obtained by finding the intersections
-        %~ of the Binder parameters $g$ for different system sizes $L$.
-        %~ They are plotted over different disorder parameters \(\sigma\).
-        %~ Interesting points are the jump and rise of the GG at small
-        %~ \(\sigma\) and the plateau on the RNG for small \(\sigma\).
-    %~ }
-    %~ \label{fig:Tc}
-%~ \end{figure*}
+is used.
 \begin{figure*}[hbtp]
@@
         \(\sigma\) and the plateau on the RNG for small \(\sigma\).
-        \subref{fig:TcK} \(T_c\) is plotted in a log-log plot as a function of the degree $K$.
-        The lines are fits to a power law function \(T_c = aK^b\)
-        ignoring the ``bulk" of points in the lower left and upper right, where
-        deviations from the power law become obvious.
-        For the RNG the fit yields $b = 1.349(2)$ with $\chi_\mathrm{red}^2 = 1.9$
-        and for the GG  $b = 1.300(5)$ with $\chi_\mathrm{red}^2 = 0.8$
+        \subref{fig:TcK} The average degree \(K\) is plotted over $\sigma$ and
+        the similarity to \subref{sfig:Tc:RNG} shows that the degree is the single
+        most important influence on $T_c$. The inset shows that for the GG there
+        is actually in good approximation a power-law relationship \(T_c = aK^b\)
+        The upper curve is for an ensemble where the edges have unit weight and
+        yields an exponent $b_1=1.321(1)$ with $\chi_{\mathrm{red}}^2 = 2.5$.
+        The ensemble with length dependent weigth is the lower curve with
+        $b = 1.305(2)$, $\chi_{\mathrm{red}}^2 = 4.9$.
+        The bad $\chi_\mathrm{red}^2$ are caused by the region in the upper right,
+        where $T_c$ is rising with $\sigma$ and hint at other influences.
     }
@@
 \end{figure*}
-is used.
 Since \(g\) is only measured for discrete values of \(T\),
@@
 \begin{figure}[hbtp]
-\label{fig:TcK}
-        \includegraphics[scale=1]{plots/K_sigma_inset_both}
+    \includegraphics[width=0.15\textwidth]{images/GGEdgeAfter}
+    \caption
+    {
+        Smallest movement of nodes in a square lead to a new edge across the
+        facet. This effect leads to the discontinuity in Fig.~\ref{sfig:Tc:RNG} and
+        Fig.~\ref{fig:TcK}.
+    }
+    \label{fig:GGEdgeAfter}
 \end{figure}
@@
 GG and at smallest deviations from the square lattice new edges arise in
-the GG, which lead to a stronger coupling of spins such that the system stays
-ferromagnetic at higher temperatures.
+the GG, this is visualized in Fig.~\ref{fig:GGEdgeAfter}. These new edges lead
+to a stronger coupling of spins such that the system stays ferromagnetic at
+higher temperatures.
 
 For large values of $\sigma$ the configurations approach the limit of a
-Poisson point process, hence $T_c$ approaches its limit value.
+Poisson point process, hence $T_c$ approaches its limit value. Note that
 
@@
 needed to disturb the ferromagnetic phase is lower than with strongly coupled
-spins. To quantify the influence of this, $T_c$ is plotted over the
-degree $K$, i.e.~the mean number of neighbors each spin has, in Fig.~\ref{fig:TcK}.
-For a given graph type, $T_c$ can be derived approximately by a power law
-from $K$. But there are deviations from this behavior, which reflect
-at least the influence of the coupling constant $J$.
+spins.
+For the GG there is a power-law relationship between the degree $K$ and
+the critical temperature $T_c$ for both the distance dependent coupling constant
+and a constant $J=1$ as shown in the inset of Fig.~\ref{fig:TcK}. The exponents
+and goodness of fit are shown in the caption.
+Also here the square lattice $\sigma = 0$ is a special case, as it is incompatible with the
+power law. Also note that the points for small $\sigma$ in the top right of the
+inset are the ones wich worsen the goodness of fit. For the RNG this power law
+is not observable.
+A further interesting feature which highlights the immportance of the structure
+of the graph for the critical temperature is the fact that the square lattice
+has a different critical temperature than the GG in the Poisson point process
+limit although they share the same average degree of $K=4$. ($T_c/K$ als Wert einer Kante)
+%To quantify the influence of this, $T_c$ is plotted over the
+%degree $K$, i.e., the mean number of neighbors each spin has, in Fig.~\ref{fig:TcK}.
+%For a given graph type, $T_c$ can be derived approximately by a power law
+%from $K$. But there are deviations from this behavior, which reflect
+%at least the influence of the coupling constant $J$.

### 2016-03-14 Tex/paper.tex
changes to the article
merge text into one file

@@
-\documentclass[prb,twocolumn,groupedaddress,showpacs,showkeys,amsmath,amssymb,floatfix]{revtex4-1}
+\documentclass[pre,twocolumn,groupedaddress,showpacs,showkeys,amsmath,amssymb,floatfix]{revtex4-1}
 
@@
     \email{christoph.norrenbrock@uni-oldenburg.de}
+    \author{Alexander K. Hartmann}
+    \email{a.hartmann@uni-oldenburg.de}
     \affiliation{Institut f\"ur Physik, Universit\"at Oldenburg, 26111 Oldenbug, Germany}
@@
     \begin{abstract}
-    \input{paper/abstract}
+        We perform Monte Carlo simulations to determine the critical temperatures
+        of Ising Ferromagnets (IFM) on proximity graphs with different underlying
+        node sets, which can be governed by a parameter $\sigma$.
+        The coupling strengths arise from the Euclidean distance
+        between coupled spins.
+        The simulations are carried out on graphs with \(N=16^{2}\) to \(N=128^{2}\)
+        nodes utilizing the Wolff cluster algorithm and parallel tempering in a
+        wide temperature range around the critical point to measure
+        the Binder cumulant as means to obtain the critical temperature.
+        The critical temperatures are shown to depend mainly on the average degree
+        and the type of the underlying proximity graph.
+        We further verify using finite-size scaling methods that the IFM on proximity
+        graphs is in the same universality class as the IFM on a two-dimensional
+        square lattice.
     \end{abstract}
@@
     \section{Introduction}
-        \input{paper/introduction}
+        The Ising model of ferromagnetism \cite{Ising1925} is one of the
+        most extensively studied models in statistical mechanics, because it
+        features a continuous phase transition while being simple.
+        The model consists of discrete variables, called spins, which can be in
+        one of two different states.
+        The neighbor relationships, which define the interactions of spins, can be expressed by graphs and
+        thus there is a constant interest in the critical behavior of this model
+        on different graph ensembles. The research provides the whole range
+        from analytical results for regular lattices \cite{Onsager1944,Wannier1945}
+        to numerical results for complex networks \cite{Aleksiejuk2002260,Herrero2002SmallWorld,Herrero2004ScaleFree,Herrero2015ScaleFree}.
+
+        An important graph is the Delaunay triangulation that finds application
+        in, e.g., finite volume methods.
+        For a system of randomly placed spins on a two-dimensional surface
+        with neighbor relationships derived from a Delaunay triangulation,
+        the critical temperature has been obtained
+        and it has been confirmed that it is in the same universality class as the
+        two-dimensional Ising model on a square lattice \cite{Janke1994,Lima2000,Lima2008}.
+        This article extends the former research to other
+        irregular lattices, namely the Relative Neighborhood graph (RNG) and
+        Gabriel graph (GG), which are subgraphs of the Delaunay triangulation
+        and belong to the family of \emph{proximity graphs}.
+        The objective of proximity graphs is to connect nodes which are
+        spatially close to each other, hence they are suited
+        to generalize problems defined on regular lattices with nearest neighbor
+        relationships.
+        This family of graphs finds application in geographic variation studies in
+        biology \cite{Sokal1978,Sokal1980,Selander1975}, as potential candidates for ``virtual backbones'' in ad-hoc
+        networks \cite{Kuhn2003,Bose2001,Santi2005,Karp2000,jennings2002topology}
+        and in machine learning and pattern recognition \cite{bhattacharya1981application}.
+        Also, their statistical properties have been under scrutiny recently \cite{RNGCell,norrenbrock2014percolation}.
+
+        Here, we consider an ensemble depending on a tunable parameter $\sigma$.
+        By changing this parameter we can interpolate the configurations
+        between nodes on a square lattice and nodes distributed by a Poisson point process.
+        For any node set the construction rule of a proximity
+        graph defines the corresponding edge set.
+        We measure the critical temperatures for a range of $\sigma$ and find
+        a power-law relationship for the GG between the critcal temperature and
+        the average degree, for the RNG we cannot observe a power law.
+        Additionally we verify that the universality class does not change by
+        varying $\sigma$.
+
+        In Sec.~\ref{sec:model} proximity graphs and the Ising model
+        are explained. Sec.~\ref{sec:results} shows the
+        details and results of our simulations. Sec.~\ref{sec:conclusion}
+        closes this article with the conclusion and an outlook.
 
     \section{Model}
-        \input{paper/model}
+        \label{sec:model}
+        \subsection{Proximity Graphs}
+        \label{ssec:graphtypes}
+            A graph \(G(V,E)\) consists of a set of nodes \(V\) and edges \(E \subset V^{2}\).
+            Two nodes connected by an edge are called neighbors.
+            Proximity graphs are defined in a metric space. In this article a
+            two-dimensional space with the Euclidean metric is chosen, because
+            it is the most common case and easy to visualize, though in principle
+            every metric in any dimension can be used.
+
+            The \emph{Relative Neighborhood graph} (RNG) \cite{Toussaint1980} is
+            a proximity graph. Two nodes \(i\) and \(j\) with distance $d_{ij}$
+            will be connected, if no other node is in their \emph {lune}. The lune
+            is defined as the intersection of two circles with radius \(r =
+            d_{ij}\) and centers on \(i\) and \(j\). That means that the edge
+            $\{i,j\}$ is part of the graph, if the condition
+            \begin{align*}
+                d_{ij} &\le \max\left\{ d_{ik}, d_{kj} \right\} &\forall k \in V\setminus\{i,j\}
+            \end{align*}
+            is fulfilled. See also the hatched region
+            in Fig.~\ref{fig:lunes}. An example is given in Fig.~\ref{sfig:lunes:rng}.
+
+            \begin{figure}[htbp]
+                \centering
+                \subfigure[]{
+                    \label{sfig:lunes:def}
+                    \includegraphics[width=0.14\textwidth]{images/GG_RNG_def}
+                }
+                \subfigure[]{
+                    \label{sfig:lunes:rng}
+                    \includegraphics[width=0.14\textwidth]{images/RNG/L12S03}
+                }
+                \subfigure[]{
+                    \label{sfig:lunes:gg}
+                    \includegraphics[width=0.14\textwidth]{images/GG/L12S03}
+                }
+                \caption[Gabriel and Relative Neighborhood Graph]
+                {
+                    \subref{sfig:lunes:def} Lunes, which define whether an edge
+                        exists, of RNG (hatched region) and GG (cross hatched region).
+                        It is evident from this sketch that the GG is a supergraph
+                        of the RNG. If there is an edge in the RNG, the hatched
+                        region contains no node, then of course also the double
+                        hatched region contains no node and thus this edge appears
+                        also in the GG. So every egde of the RNG is also present
+                        in a GG on the same set of nodes.
+                    \subref{sfig:lunes:rng} Example of a RNG on periodic
+                        boundary conditions.
+                    \subref{sfig:lunes:gg} Example of a GG on
+                        periodic boundary conditions. Periodic nodes are dashed.
+                }
+                \label{fig:lunes}
+            \end{figure}
+
+            The \emph{Gabriel graph} (GG) \cite{Gabriel1969} is a subgraph
+            of the Delaunay triangulation \cite{Delaunay1934,Katajainen}
+            (DT), i.e., for the same set of nodes \(V\) the edge set of the
+            DT is a superset of the edge set of the GG. Two nodes \(i\) and
+            \(j\) with distance \(d_{ij}\) will be connected with an edge,
+            if a circle with its center on half way between \(i\) and \(j\)
+            and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes, i.e., the
+            condition
+            \begin{align*}
+                d^{2}_{ij} &< d^{2}_{ik} + d^{2}_{kj} &\forall k \in V\setminus\{i,j\}
+            \end{align*}
+            is fulfilled. See
+            also the cross hatched region from Fig.~\ref{sfig:lunes:def}. An
+            example is given in Fig.~\ref {sfig:lunes:gg}. Note that the
+            lune of the GG is completely enclosed in the lune of the RNG,
+            therefore the RNG is a subgraph of the GG.
+
+            To construct these graphs there is an algorithm with
+            a time complexity of \(\mathcal{O}(N \log N)\) for nodes on a two
+            dimensional plane \cite{RNGCell}.
+
+        \subsection{The Ising Model}
+        \label{ssec:model}
+            Commonly, the IFM is studied on a square lattice with lateral length
+            \(L\) and \(N=L^2\) nodes with periodic boundary conditions.
+            Each node $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
+            nearest neighbors described by the Hamiltonian
+            \begin{equation}
+                \mathcal{H} = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
+                \label{eq:hamiltonian}
+            \end{equation}
+            \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are
+            nearest neighbors, i.e., they are connected by an edge.
+            The coupling strength between \(i\) and \(j\) is given by
+            \(J_{ij}\).
+
+            In this article the nodes of the square lattice are
+            displaced, introducing geometric disorder resulting in a non-regular graph
+            structure.
+            The displacement is randomly Gaussian distributed with standard
+            deviation \(\sigma\), i.e., the \(x\) and \(y\) coordinates of the
+            nodes are displaced by random \(\Delta x\) and \(\Delta y\) drawn
+            from a Gaussian distribution with zero mean.
+            In the following, \(\sigma\) will be called \emph{disorder parameter}.
+            If we took ``nearest neighbor" in the Euclidean meaning, most nodes
+            would only have one nearest neighbor after the
+            displacement. If only the edges between these neighbors remained,
+            the lattice would collapse to many very small clusters. If, on the
+            other hand, all edges remained as they were before the displacement,
+            edges might cross each other -- at least for big displacements.
+            The crossing of edges would destroy the planar character of the graph.
+            To avoid this, a new edge set will be established after the displacement
+            to form a proximity graph. The influence of $\sigma$ on the
+            structure of a proximity graph is shown in Fig.~\ref{fig:RNG_sigma}
+            for a RNG.
+            \begin{figure}[htb]
+                \centering
+                \subfigure[$\sigma = 0.09$]
+                {
+                    \label{sfig:RNG_sigma:0.09}
+                    \includegraphics[width=0.14\textwidth]{images/RNG/out009}
+                }
+                \subfigure[$\sigma = 0.15$]
+                {
+                    \label{sfig:RNG_sigma:0.15}
+                    \includegraphics[width=0.14\textwidth]{images/RNG/out015}
+                }
+                \subfigure[$\sigma = 0.21$]
+                {
+                    \label{sfig:RNG_sigma:0.21}
+                    \includegraphics[width=0.14\textwidth]{images/RNG/out021}
+                }
+                \caption[Examples of RNG for different $\sigma$]
+                {
+                    Examples of proximity graphs (more precise, Relative Neighborhood
+                    graph see Sec. \ref{ssec:graphtypes}) for different values of $\sigma$.
+                    Connections which cross a periodic boundary are indicated
+                    by edges which connect a solid node to a dashed node.
+                }
+                \label{fig:RNG_sigma}
+            \end{figure}
+            The coupling constants \(J_{ij}\), i.e., edge weights, depend on the
+            geometric distance between the connected pair of nodes. More precise,
+            the weight of an edge is
+            \begin{equation}
+                E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})},
+                \label{eq:coupling}
+            \end{equation}
+            where \(d_{ij}\) is the Euclidean
+            distance between node \(i\) and \(j\). Following Ref.~\cite{Lima2000}
+            the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
+            Note that for \(\sigma = 0\) the resulting \(d_{ij} = 1\) and therefore
+            \(J_{ij} = 1\) for every edge $\{i,j\}$. Consequently, in this case
+            the graph is a common square lattice.
 
     \section{Results}
-        \input{paper/results}
+        \label{sec:results}
+        The results are obtained through Monte Carlo simulations. For each
+        sweep \(N\) single spin flip Metropolis updates \cite{Metropolis1953},
+        one Wolff cluster update \cite{Wolff1989} and one
+        parallel tempering swap \cite{ParallelTempering1986} are performed.
+        For every system size $L \in \{16,32,64,128\}$ and 19 different values of
+        $\sigma \in [0,1.2]$ on $100$ different realizations at least $5000$
+        independent measurements are taken in equilibrium.\\
+        Since it is not known beforehand, where the critical temperatures \(T_c\)
+        are located, the Wolff cluster algorithm is used at every
+        temperature. Albeit the efficiency of the algorithmic procedure was
+        not examined for every temperature, the speed up near criticality
+        should be worth the moderate slow down at other temperatures.\\
+
+        It is not expected that the universality class depends on the graph
+        structure unless the dimension is changed.
+        To proof this, the critical exponents are determined by a finite-size
+        scaling (FSS) analysis using the well kown scaling bahaviors of the
+        magnetization, the susceptiblity and the Binder cumulant
+        in an automated and reproducable way using the
+        method from Ref.~\cite{autoscale2009}.
+        In Fig.~\ref{fig:collapse}
+        \begin{figure}[htb]
+            \includegraphics[scale=1]{plots/col_s1_sus}
+            \caption[Examples of Determining Critical Temperature and Exponents]
+            {
+                Example for a collapse of the susceptiblity \(\chi\) on a RNG at
+                \(\sigma = 1\) to get the corresponding critical exponent $\gamma$.
+                The same procedure is used on the Binder cumulant $g$ and the
+                magnetization $|m|$ to determine the critical exponents
+                \(\nu\) and \(\beta\) and the critical temperature \(T_c\).
+                The inset shows the same data with unscaled axes.
+            }
+            \label{fig:collapse}
+        \end{figure}
+        a data collapse at $\sigma = 1$ for the susceptiblity
+        \[\chi = \frac{N}{T}\brac{\avgR{\avg{m^2}}-\avgR{\avg{m}}^2}\]
+        with $\avg{\cdot}$ being the thermal average and $\avgR{\cdot}$ being the
+        average over the random realizations, is plotted.
+        All obtained values for different $\sigma$ are visualized in Tab.~\ref{tab:critExp}
+        \begin{table}[htb]
+            \begin{ruledtabular}
+                \begin{tabular}{l l l l l l}
+                     & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
+                    %~ \colrule
+                    \hline
+                    exact        & 0   & 2.2691... & \(1\)    & \(1.75\) & \(0.125\)\\
+                    %~ \colrule
+                    \hline
+                    RNG          & 0.0 & 2.2688(7) & 1.00(1) & 1.741(2) & 0.125(1) \\
+                                 & 0.1 & 2.2053(6) & 0.99(1) & 1.745(5) & 0.128(3) \\
+                                 & 0.2 & 1.6265(19)& 1.02(2) & 1.758(14)& 0.122(7)\\
+                                 & 0.5 & 1.2825(9) & 1.01(2) & 1.746(16)& 0.128(8)\\
+                                 & 1.0 & 1.2125(5) & 1.01(1) & 1.764(14)& 0.125(6)\\
+                    %~ \colrule
+                    \hline
+                    GG           & 0.0 & 2.2688(6) & 1.00(1) & 1.738(22)& 0.127(4)\\
+                                 & 0.1 & 2.8944(43)& 1.00(1) & 1.745(6) & 0.135(6) \\
+                                 & 0.3 & 2.5281(27)& 1.03(3) & 1.718(15)& 0.118(11)\\
+                                 & 0.5 & 2.2388(9) & 1.01(1) & 1.747(12)& 0.125(11)\\
+                                 & 1.0 & 2.1275(20)& 1.04(3) & 1.750(16)& 0.125(15)\\
+                \end{tabular}
+            \end{ruledtabular}
+            \caption[Critical Exponents for Different $\sigma$]{
+                Critical exponents for different values of \(\sigma\). A finite size
+                scaling analysis was performed to determine the critical
+                exponents \(\beta, \gamma, \nu\) and the critical temperature
+                \(T_c\). The errors for \(\beta\) and \(\gamma\) are estimated
+                with the method from Ref.~\cite{autoscale2009}. The errors of
+                \(\nu\) and \(T_c\) are the standard deviation of three obtained
+                values through different collapses. The critical exponents
+                are in reasonable agreement with the exact known values for the 2D Ising
+                universality class. The critical temperatures $T_c$ are shifting
+                as expected.
+            }
+            \label{tab:critExp}
+        \end{table}
+        and are within errorbars consistent with the exactly known values for the
+        square lattice IFM.
+        A newer method \cite{chiCollapse,Hartmann2013} to test whether two models are in
+        the same universality class is the analysis of the two-point finite-size
+        correlation function
+        \[\xi = \frac{1}{2\sin\brac{\abs{\vec{k}_{\mathrm{min}}}/2}} \sqrt{\frac{\chi(\vec{0})}{\chi(\vec{k}_{\mathrm{min}})} - 1}\]
+        where $\vec{k}_{\mathrm{min}}=(2\pi / L, 0)$ and $\chi(\vec{k})$ is the wave vector
+        dependent susceptiblity
+        \[\chi(\vec{k}) = \avgR{\avg{\abs{\brac{\frac{1}{N}\sum_j s_j \exp(ikx_j)}^2}}}\]
+        which is in this case only evaluated over one direction thus $x_j$ is the
+        position of the node in the x-direction.
+
+        \begin{figure}[htbp]
+            \centering
+            \includegraphics[scale=1]{plots/Binder_over_Correlation_All}
+            \caption[Binder cumulant over two-point finite-size correlation function divided by system size]
+            {
+                Binder cumulant $g$ over two-point finite-size correlation function
+                divided by system size $L$. The datapoints for different system sizes
+                are drawn with different symbols, while the datapoints for different
+                graph ensembles are drawn with different colors. Anyway, all points
+                fall on one curve within errorbars.
+                %~ The inset zooms into the plot to show that
+                %~ all datapoints fall within errorbars onto one curve.
+            }
+            \label{fig:binderOverCorr}
+        \end{figure}
+        If the Binder cumulant
+        \[g = \frac{3}{2}\brac{1-\frac{\avgR{\avg{m^4}}}{3\avgR{\avg{m^2}^2}}}\]
+        is plotted over $\xi$ for different $\sigma$, $L$ and $T$ as shown in
+        Fig.~\ref{fig:binderOverCorr}, all data points fall on the
+        same curve, which confirms that this IFM on proximity graphs is in the
+        same universality class as on the square lattice, i.e., $\sigma=0$.
+
+        This study examines the critical temperatures $T_c$ for different values of $\sigma$.
+        Therefore the knowledge that the Binder cumulants $g$ for different
+        system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
+        is used.
+        \begin{figure*}[hbtp]
+            \subfigure[]{
+                \label{sfig:Tc:binder}
+                \includegraphics[scale=1]{plots/binder}
+            }
+            \subfigure[]{
+                \label{sfig:Tc:RNG}
+                \label{sfig:Tc:GG}
+                \includegraphics[scale=1]{plots/Tc_both}
+            }
+            \subfigure[]{
+                \label{fig:TcK}
+                \includegraphics[scale=1]{plots/K_sigma_inset_both}
+            }
+            \caption[Critical Temperature over Different Disorder Parameters]
+            {
+                \subref{sfig:Tc:binder} Critical temperatures \(T_c\) are obtained by finding the intersections
+                of the Binder parameters $g$ for different system sizes $L$.
+                \subref{sfig:Tc:RNG} They are plotted over different disorder parameters \(\sigma\).
+                Interesting points are the jump and rise of the GG at small
+                \(\sigma\) and the plateau on the RNG for small \(\sigma\).
+                \subref{fig:TcK} The average degree \(K\) is plotted over $\sigma$ and
+                the similarity to \subref{sfig:Tc:RNG} shows that the degree is the single
+                most important influence on $T_c$. The inset shows that for the GG there
+                is actually in good approximation a power-law relationship \(T_c = aK^b\)
+                The upper curve is for an ensemble where the edges have unit weight and
+                yields an exponent $b_1=1.321(1)$ with $\chi_{\mathrm{red}}^2 = 2.5$.
+                The ensemble with length dependent weigth is the lower curve with
+                $b = 1.305(2)$, $\chi_{\mathrm{red}}^2 = 4.9$.
+                The bad $\chi_\mathrm{red}^2$ are caused by the region in the upper right,
+                where $T_c$ is rising with $\sigma$ and hint at other influences.
+            }
+            \label{fig:Tc}
+        \end{figure*}
+        Since \(g\) is only measured for discrete values of \(T\),
+        the points have to be interpolated to find the intersection. Therefore
+        a \emph{cubic spline} \cite{press2007numerical} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
+        is calculated for the measured points.
+        %~ Cubic spline interpolation is a piece-wise fitting of polynoms of
+        %~ degree three which are joined under the condition to be at least two
+        %~ times continuously differentiable.
+        %~ This interpolation type has the
+        %~ advantage that it is only influenced by local points so that the
+        %~ plateaus at low and high \(T\) do not influence the interpolation in
+        %~ the vicinity of \(T_c\) -- in contrast to, e.g.\ an polynom fit of
+        %~ degree 4, which has to be restricted to the vincinity of \(T_c\) to
+        %~ yield meaningful results.
+        An even better method would be the
+        \emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
+        But the simple cubic spline interpolation seems to deliver results that
+        are good enough, because the temperatures of the measurements are
+        sufficiently near to each other. Also a cubic spline interpolation is
+        far easier to obtain.
+
+        \begin{figure}[hbtp]
+            \includegraphics[width=0.15\textwidth]{images/GGEdgeAfter}
+            \caption
+            {
+                Smallest movement of nodes in a square lead to a new edge across the
+                facet. This effect leads to the discontinuity in Fig.~\ref{sfig:Tc:RNG} and
+                Fig.~\ref{fig:TcK}.
+            }
+            \label{fig:GGEdgeAfter}
+        \end{figure}
+        The first oddity of the GG in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is
+        the jump of $T_c$ close to $\sigma = 0$, where it jumps from $T_c(0) = 2.269(1)$
+        to $T_c(0.03) = 2.851(1)$ at the next measured temperature. This is easily explainable,
+        because the square lattice at $\sigma = 0$ is a very special case for the
+        GG and at smallest deviations from the square lattice new edges arise in
+        the GG, this is visualized in Fig.~\ref{fig:GGEdgeAfter}. These new edges lead
+        to a stronger coupling of spins such that the system stays ferromagnetic at
+        higher temperatures.
+
+        For large values of $\sigma$ the configurations approach the limit of a
+        Poisson point process, hence $T_c$ approaches its limit value. Note that
+
+        The critical temperature $T_c$ decreases with increasing $\sigma$, which
+        is expected, since the number of edges decreases, which can be seen in
+        Fig.~\ref{fig:RNG_sigma}. With loosely coupled spins, the temperature
+        needed to disturb the ferromagnetic phase is lower than with strongly coupled
+        spins.
+        For the GG there is a power-law relationship between the degree $K$ and
+        the critical temperature $T_c$ for both the distance dependent coupling constant
+        and a constant $J=1$ as shown in the inset of Fig.~\ref{fig:TcK}. The exponents
+        and goodness of fit are shown in the caption.
+        Also here the square lattice $\sigma = 0$ is a special case, as it is incompatible with the
+        power law. Also note that the points for small $\sigma$ in the top right of the
+        inset are the ones wich worsen the goodness of fit. For the RNG this power law
+        is not observable.
+        A further interesting feature which highlights the immportance of the structure
+        of the graph for the critical temperature is the fact that the square lattice
+        has a different critical temperature than the GG in the Poisson point process
+        limit although they share the same average degree of $K=4$. ($T_c/K$ als Wert einer Kante)
+        %To quantify the influence of this, $T_c$ is plotted over the
+        %degree $K$, i.e., the mean number of neighbors each spin has, in Fig.~\ref{fig:TcK}.
+        %For a given graph type, $T_c$ can be derived approximately by a power law
+        %from $K$. But there are deviations from this behavior, which reflect
+        %at least the influence of the coupling constant $J$.
 
     \section{Conclusion}
-        \input{paper/conclusion}
+        \label{sec:conclusion}
+        This study shows that universality of the Ising model is preserved for
+        irregular graphs on a wide range of configurations which are intermediate
+        between the square lattice Ising model and a random Poisson point process.
+        Also the critical temperature was measured over this range and determined
+        that it shows approximately a power law behavior with the mean
+        number of neighbors as the base and an exponent dependent on the
+        graph type that defines the neighbor relationships.
+
+        The next step would be the extension to three and higher
+        dimensions, where the used proximity graphs are still well defined. It
+        would also be worthwhile to study properties of the graph ensembles themselves,
+        because -- to our knowledge -- they are mostly studied in 2D \cite{RNGCell}.
 
     \section{Acknowledgements}
-        \input{paper/acknowledgements}
+        The simulations were performed at the HPC Cluster HERO, located at
+        the University of Oldenburg (Germany) and funded by the DFG through
+        its Major Research Instrumentation Programme (INST 184/108-1 FUGG)
+        and the Ministry of Science and Culture (MWK) of the Lower Saxony
+        State.
+        The authors would also like to thank O. Melchert and T. Dewenter
+        for the fruitful discussions.
 

### 2016-03-14 Tex/paper.tex
truncated precision in table
tweaks to diagrams

@@
                     \hline
-                    RNG          & 0.0 & 2.2688(7) & 1.00(1) & 1.741(2) & 0.125(1) \\
-                                 & 0.1 & 2.2053(6) & 0.99(1) & 1.745(5) & 0.128(3) \\
-                                 & 0.2 & 1.6265(19)& 1.02(2) & 1.758(14)& 0.122(7)\\
-                                 & 0.5 & 1.2825(9) & 1.01(2) & 1.746(16)& 0.128(8)\\
-                                 & 1.0 & 1.2125(5) & 1.01(1) & 1.764(14)& 0.125(6)\\
+                    RNG          & 0.0 & 2.2688(7) & 1.00(1) & 1.74(1) & 0.125(1) \\
+                                 & 0.1 & 2.2053(6) & 0.99(1) & 1.75(1) & 0.128(3) \\
+                                 & 0.2 & 1.6265(19)& 1.02(2) & 1.76(1) & 0.122(7)\\
+                                 & 0.5 & 1.2825(9) & 1.01(2) & 1.75(2) & 0.128(8)\\
+                                 & 1.0 & 1.2125(5) & 1.01(1) & 1.76(1) & 0.125(6)\\
                     %~ \colrule
                     \hline
-                    GG           & 0.0 & 2.2688(6) & 1.00(1) & 1.738(22)& 0.127(4)\\
-                                 & 0.1 & 2.8944(43)& 1.00(1) & 1.745(6) & 0.135(6) \\
-                                 & 0.3 & 2.5281(27)& 1.03(3) & 1.718(15)& 0.118(11)\\
-                                 & 0.5 & 2.2388(9) & 1.01(1) & 1.747(12)& 0.125(11)\\
-                                 & 1.0 & 2.1275(20)& 1.04(3) & 1.750(16)& 0.125(15)\\
+                    GG           & 0.0 & 2.2688(6) & 1.00(1) & 1.74(2) & 0.127(4)\\
+                                 & 0.1 & 2.8944(43)& 1.00(1) & 1.75(1) & 0.135(6) \\
+                                 & 0.3 & 2.5281(27)& 1.03(3) & 1.72(2) & 0.118(11)\\
+                                 & 0.5 & 2.2388(9) & 1.01(1) & 1.75(1) & 0.125(11)\\
+                                 & 1.0 & 2.1275(20)& 1.04(3) & 1.75(2) & 0.125(15)\\
                 \end{tabular}
@@
                 most important influence on $T_c$. The inset shows that for the GG there
-                is actually in good approximation a power-law relationship \(T_c = aK^b\)
+                is actually in good approximation a power-law relationship \(T_c = aK^b\).
                 The upper curve is for an ensemble where the edges have unit weight and

### 2016-03-14 graph_modify.c
added Minimum Spanning Tree (MST)

@@ -23,7 +23,10 @@ gs_graph_t **init_graphs(const options_t o)
     move_graph_nodes(g, o.moving_fkt, o.rng, o.sigma);
 
     /* Verknüpfe die Knoten */
-    create_edges(g, o);
+    if(o.graph_type == 3) // MST
+        create_edges_mst(g, o);
+    else // GG or RNG
+        create_edges(g, o);
 
     if(o.percolation)
         delete_random_edges_till_percolation(g, o.rng);
@@ -267,6 +270,91 @@ void create_edges_regular(gs_graph_t *g)
             gs_insert_edge(g, i, i+L, weight);  /*oben*/
         else
             gs_insert_edge(g, i, i%L, weight);
+    }
+}
+
+typedef struct
+{
+    int i, j;
+    double l;
+}
+len_t;
+
+int compare(const void * a, const void * b)
+{
+    if((*(len_t*)a).l < (*(len_t*)b).l) return -1;
+    if((*(len_t*)a).l > (*(len_t*)b).l) return 1;
+    return 0;
+}
+
+double dist(double x1, double y1, double x2, double y2)
+{
+    return sqrt((x1-x2)*(x1-x2) + (y1-y2)*(y1-y2));
+}
+
+/*! \fn void create_edges_mst(gs_graph_t *g)
+    \brief Fügt Kanten zu einem Graphen hinzu, wodurch ein minimum
+            spanning tree erzeugt werden soll.
+
+    \param [in,out]    g    Graph, der modifiziert werden soll
+*/
+void create_edges_mst(gs_graph_t *g, const options_t o)
+{
+    int i, j, k, t;
+    int num_nodes, L, num_lengths;
+    double weight;
+    len_t *lengths;
+    gs_node_t n1, n2;
+    double min_dist;
+    union_find_t *uf;
+
+    num_nodes = g->num_nodes;
+    L         = g->L;
+    num_lengths = (num_nodes*num_nodes - num_nodes)/2;
+    lengths   = (len_t*) malloc(sizeof(len_t) * (num_lengths));
+
+    k = 0;
+    for(i=0; i<num_nodes; ++i)
+        for(j=0; j<i; ++j)
+        {
+            n1 = g->node[i];
+            n2 = g->node[j];
+
+            lengths[k].i = i;
+            lengths[k].j = j;
+
+            static const int m = 9;
+            static const int X[] = {0, -1,  0,  1, -1,  1, -1,  0,  1};
[…]

### 2016-03-14 graph_modify.h

@@ -11,6 +11,7 @@
 #include "spin.h"
 #include "list.h"
 #include "tree.h"
+#include "union_find.h"
 
 /*! \def MIN(X,Y)
  * Minimum von zwei Zahlen
@@ -26,6 +27,7 @@ gs_graph_t **init_graphs(const options_t options);
 void move_graph_nodes(gs_graph_t *g, double (*f)(const gsl_rng *, double), gsl_rng *rng, const double sigma);
 
 void create_edges(gs_graph_t *g, const options_t o);
+void create_edges_mst(gs_graph_t *g, const options_t o);
 inline int check_relative_neighborhood(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);
 inline void get_cell_border_relative_neighborhood(gs_node_t node1, gs_node_t node2, double dist12, int L, int *x0, int *x1, int *y0, int *y1);
 inline int check_gabriel(double dist12, gs_node_t node1, gs_node_t node2, gs_node_t node3);

### 2016-03-14 spin.c

@@ -195,7 +195,7 @@ options_t get_cl_args(int argc, char *argv[])
                 fprintf(stdout,"    -ix    autokorrelationszeit                 (int)\n");
                 fprintf(stdout,"    -sx    sigma x                           (double)\n");
                 fprintf(stdout,"    -ax    alpha x                           (double)\n");
-                fprintf(stdout,"    -tx    Graphtyp: (1: RNG, 2: Gabriel)       (int)\n");
+                fprintf(stdout,"    -tx    Graphtyp: (1: RNG, 2: Gabriel, 3: MST)(int)\n");
                 fprintf(stdout,"    -ox    filename (max. 79 Zeichen)        (string)\n");
                 fprintf(stdout,"    -gx    SVG Filename (max. 79 Zeichen)    (string)\n");
                 fprintf(stdout,"    -ux    Ordnung x (0: zufällig, 1: alle up)  (int)\n");

### 2016-03-14 union_find.c

@@ -1,0 +1,91 @@
+#include "union_find.h"
+
+// forest[x] < 0 -> root mit abs(forest[x]) Knoten
+// forest[x] >= 0 -> parent ist an forest[forest[x]]
+
+/*! \fn union_find_t *uf_create(int N)
+    \brief Erstellt eine neue Union Find Struktur
+
+    \param [in]     N   Anzahl der Elemente
+    \return erzeugte Union Find Struktur
+*/
+union_find_t *uf_create(int N)
+{
+    int i;
+    union_find_t *uf;
+
+    uf = (union_find_t*) malloc(sizeof(union_find_t));
+    uf->N = N;
+    uf->forest = (int*) malloc(N*sizeof(int));
+
+    for(i=0; i<N; ++i)
+        uf->forest[i] = -1;
+
+    return uf;
+}
+
+/*! \fn void uf_delete(union_find_t *uf)
+    \brief Löscht die Union Find Struktur
+
+    \param [in,out] uf   Struktur, die gelöscht werden soll
+*/
+void uf_delete(union_find_t *uf)
+{
+    free(uf->forest);
+    free(uf);
+}
+
+/*! \fn void uf_union(union_find_t *uf, int x, int y)
+    \brief Vereinigt zwei Baume in der Union Find Struktur
+
+    \param [in,out] uf   Struktur, die geandert werden soll
+    \param [in]     x    Element 1, das vereinigt werden soll
+    \param [in]     y    Element 2, das vereinigt werden soll
+*/
+void uf_union(union_find_t *uf, int x, int y)
+{
+    int root1 = uf_find(uf, x);
+    int root2 = uf_find(uf, y);
+
+    // are already in one Cluster
+    if(root1 == root2)
+        return;
+
+    // weighted -> append shorter Tree to longer
+    // negative Zahlen -> Vergleichszeichen unintuitiv
+    int p, c;
+    if(uf->forest[root1] < uf->forest[root2])
+    {
+        p = root1;
+        c = root2;
+    }
+    else
+    {
+        p = root2;
+        c = root1;
+    }
+
+    uf->forest[p] += uf->forest[c];
+    uf->forest[c] = p;
+}
+
+/*! \fn int uf_find(union_find_t *uf, int x)
+    \brief Findet Reprasentanten von Element x
+
+    \param [in,out] uf   Struktur, die durchsucht werden soll
+    \param [in]     x    Element, dessen Reprasentatn gefunden werden soll
+*/
[…]

### 2016-03-14 union_find.h

@@ -1,0 +1,24 @@
+/*! \file */
+#ifndef _UNIONFIND_H
+#define _UNIONFIND_H
+
+#include <stdio.h>
+#include <stdlib.h>
+
+/*! \struct union_find_t;
+    \brief Union Find Datenstruktur
+*/
+typedef struct
+{
+    int N;                                        //!< Anzahl der Knoten
+    int* forest;               //!< Darstellung des Disjoint Set Forests
+} union_find_t;
+
+union_find_t *uf_create(int N);
+void uf_delete(union_find_t *uf);
+
+void uf_add(union_find_t *uf, int x);
+void uf_union(union_find_t *uf, int x, int y);
+int uf_find(union_find_t *uf, int x);
+
+#endif
